### 2017-10-16 NRF_Final_Report/report.tex
started writing NRF Fellowship Final Report Abstract

                %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Live Time Monitoring and D(e,e'p)n Experimental Run Plan
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Carlos Yero \\
October 30, 2017}

\begin{document}

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      Three separate topics, all of equal importance, are briefly discussed. The new (12 GeV Era) HMS Drift Chambers are ready to be put in the HMS
      detector stack, in place of the old HMS Chambers. Several efficcinecy tests were performed on one of the chambers during the second week of October
      2017. The efficcinecies were determined to be better than 99$\%$. The second chamber has not been tested yet, but it is
      expected to behave the same since both chambers were tested under similar conditions in the past. Live time studies are currently in progress to
      determine how many physics events (triggers) are actually lost due to computer and electronic deadtime inherent in our experimental equipment. 
      There had been some technical issues found related to these studies that are being addressed by the Jefferson Lab DAQ group. The experimental run
      plan of my thesis experiment, the electro-disintegration of deuteron (D(e,e'p)n), is briefly discussed as there has been some small changes in
      the kinematic settings. \\

    \end{abstract}
  \end{@twocolumnfalse}
  ]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

This template, modified in MS Word 2003 and saved as ÒWord 97-2003 \& 6.0/95 Ð RTFÓ for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{MATH}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as Ò3.5-inch disk driveÓ.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ÒWb/m2Ó or Òwebers per square meterÓ, not Òwebers/m2Ó.  Spell out units when they appear in text: Ò. . . a few henriesÓ, not Ò. . . a few HÓ.
\item Use a zero before decimal points: Ò0.25Ó, not Ò.25Ó. Use Òcm3Ó, not ÒccÓ. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use Ò(1)Ó, not ÒEq. (1)Ó or Òequation (1)Ó, except at the beginning of a sentence: ÒEquation (1) is . . .Ó

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word ÒdataÓ is plural, not singular. \cite{Leo}
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ÒoÓ.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ÒinsetÓ, not an ÒinsertÓ. The word alternatively is preferred to the word ÒalternatelyÓ (unless you really mean something that alternates).
\item Do not use the word ÒessentiallyÓ to mean ÒapproximatelyÓ or ÒeffectivelyÓ.
\item In your paper title, if the words Òthat usesÓ can accurately replace the word ÒusingÓ, capitalize the ÒuÓ; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ÒaffectÓ and ÒeffectÓ, ÒcomplementÓ and ÒcomplimentÓ, ÒdiscreetÓ and ÒdiscreteÓ, ÒprincipalÓ and ÒprincipleÓ.
\item Do not confuse ÒimplyÓ and ÒinferÓ.
\item The prefix ÒnonÓ is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ÒetÓ in the Latin abbreviation Òet al.Ó.
\item The abbreviation Òi.e.Ó means Òthat isÓ, and the abbreviation Òe.g.Ó means Òfor exampleÓ.

\end{itemize}

\section{USING THE TEMPLATE}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. {\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output. }

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named ÒHeading 1Ó, ÒHeading 2Ó, ÒHeading 3Ó, and ÒHeading 4Ó are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation ÒFig. 1Ó, even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity ÒMagnetizationÓ, or ÒMagnetization, MÓ, not just ÒMÓ. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write ÒMagnetization (A/m)Ó or ÒMagnetization {A[m(1)]}Ó, not just ÒA/mÓ. Do not label axes with a ratio of quantities and units. For example, write ÒTemperature (K)Ó, not ÒTemperature/K.Ó

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\newpage
\onecolumn
\bibliography{report.bib}
\bibliographystyle{ieeetr}

\end{document}

### 2017-10-17 NRF_Final_Report/report.tex
started writing introduction

@@
 \title{\LARGE \bf
-On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Live Time Monitoring and D(e,e'p)n Experimental Run Plan
-}
+  On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Live Time Monitoring
+  and Overview of the D(e,e'p)n Experimental Run Plan}
 
@@
       detector stack, in place of the old HMS Chambers. Several efficcinecy tests were performed on one of the chambers during the second week of October
-      2017. The efficcinecies were determined to be better than 99$\%$. The second chamber has not been tested yet, but it is
+      2017. The efficciecies were determined to be better than 99$\%$. The second chamber has not been tested yet, but it is
       expected to behave the same since both chambers were tested under similar conditions in the past. Live time studies are currently in progress to
       determine how many physics events (triggers) are actually lost due to computer and electronic deadtime inherent in our experimental equipment. 
-      There had been some technical issues found related to these studies that are being addressed by the Jefferson Lab DAQ group. The experimental run
-      plan of my thesis experiment, the electro-disintegration of deuteron (D(e,e'p)n), is briefly discussed as there has been some small changes in
-      the kinematic settings. \\
+      There had been some technical issues found related to the computer livetime that are being addressed by the Jefferson Lab DAQ group. The experimental run
+      plan of my thesis experiment, the electro-disintegration of deuteron (D(e,e'p)n), is briefly discussed as the kinematics have slightly changed and new
+      simulations had to be done. \\
 
@@
 \section{INTRODUCTION}
-
-This template, modified in MS Word 2003 and saved as ÒWord 97-2003 \& 6.0/95 Ð RTFÓ for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
+On March 7-10 of 2017, a 5 $\mu$A electron beam was delivered to a BeO and Carbon targets for the first time to experimental
+Hall C since the 12 GeV upgrade. The beam was delivered as part of the Key Performance Parameters (KPP) required by the
+Department of Energy (DOE) to demonstrate the operability of the High Momentum Spectrometer (HMS) and Super HMS (SHMS). 
+Hall C was able to demonstrate KPP in four days of beam time before an important component of the accelerator was damaged which
+caused to accelerator to shut down for repair. The accelerator is expected to be operational starting December 4, 2017. As a
+result of this delay, the commissioning experiments that were scheduled to run on Fall 2017 have now shifted to Spring 2018.
+This time window has allowed the Hall C collaboration to work extensively in preparation for the commissioning of the
+spectrometers on December. \\
+\indent One of the projects I have been involved in is the ongoing work on testing and commissioning the 12 GeV HMS Drift
+Chambers. The chambers were constructed at Hampton University by Dr. Lyuang Tang and his graduate student Bishnu Pandey in 2016.
+They were made the same design as the SHMS chambers, but smaller in size. The chambers we transported to Jefferson Lab on November 2016,
+where they underwent extensive tests as part of conditioning the chambers to sustain High Voltages using a gas mixture\footnote{This gas mixture is
+at lower cost compared to the gas mixture that the chambers run on during an experiment, which is why it is preferred during stress testing this detector.}
+of 75:25 Argon/CO$_{2}$ by volume.  The chambers were found to be operational at 1860 V which is below the expected value. The chambers often drew significant
+amount of current ($\sim$ few $\mu$A) which caused the High Voltage to shut down as a safety mechanism. It was determined that the most likely cause of not
+being able to raise the High Voltage was the gas mixture being used, so one of the chambers was transported to the experimental Hall C where a gas mixture of
+50:50 Argon/Ethane by volume was used. A test stand for the chamber was set up in the HMS hut, where it has been tested and verified to be operational with the
+new gas mixture.
+\indent A second project I am currently involve in is the determination of electronic and computer dead times by a different method than was previously used in
+Hall C.
 

### 2017-10-22 NRF_Final_Report/report.tex
started 2nd page of NRF report

--- 2017-10-16 NRF_Final_Report/report.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
-                                                          % paper
+\usepackage{url}
+\usepackage[font=footnotesize,labelfont=bf]{caption}
+\usepackage{graphicx}
+\usepackage[scientific-notation=true]{siunitx}
+\usepackage{subcaption}
+\usepackage{setspace}
+\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
+\usepackage{blindtext}
+\usepackage[utf8]{inputenc}
+\usepackage{setspace}
+\usepackage{vector}
+\usepackage{amsmath}
+\usepackage{empheq}
+\usepackage{amssymb}
+\usepackage{tgtermes}
+\usepackage{gensymb}
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
+\usepackage{epstopdf}
+\usepackage[singlelinecheck=false]{caption}
+\usepackage{datetime}
+\usepackage[hyperfootnotes=false, pdfnewwindow, colorlinks=true]{hyperref}
+
+\AtBeginDocument{% optionally set colors to your liking
+  \hypersetup{
+    urlcolor=red,
+    citecolor=green,
+    linkcolor=blue,
+  }%
+}                                                         % paper
 
@@
 \overrideIEEEmargins
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
 
 \title{\LARGE \bf
-On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Live Time Monitoring and D(e,e'p)n Experimental Run Plan
-}
-
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
+  On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Dead Time Monitoring
+  and Overview of the D(e,e'p)n Experimental Run Plan}
 
@@
       detector stack, in place of the old HMS Chambers. Several efficcinecy tests were performed on one of the chambers during the second week of October
-      2017. The efficcinecies were determined to be better than 99$\%$. The second chamber has not been tested yet, but it is
-      expected to behave the same since both chambers were tested under similar conditions in the past. Live time studies are currently in progress to
+      2017. The efficciecies were determined to be better than 99$\%$. The second chamber has not been tested yet, but it is
+      expected to behave the same since both chambers were tested under similar conditions in the past. Dead time studies are currently in progress to
       determine how many physics events (triggers) are actually lost due to computer and electronic deadtime inherent in our experimental equipment. 
-      There had been some technical issues found related to these studies that are being addressed by the Jefferson Lab DAQ group. The experimental run
-      plan of my thesis experiment, the electro-disintegration of deuteron (D(e,e'p)n), is briefly discussed as there has been some small changes in
-      the kinematic settings. \\
-
+      There had been some technical issues found related to the computer livetime that are being addressed by the Jefferson Lab DAQ group. The experimental run
+      plan of my thesis experiment, the electro-disintegration of Deuteron, is briefly discussed as the kinematics have slightly changed and new
+      simulations had to be done. \\      
     \end{abstract}
@@
 \section{INTRODUCTION}
+On March 7-10 of 2017, a 5 $\mu$A electron beam was delivered to a BeO and Carbon targets for the first time to experimental
+Hall C since the 12 GeV upgrade. The beam was delivered as part of the Key Performance Parameters (KPP) required by the
+Department of Energy (DOE) to demonstrate the operability of the High Momentum Spectrometer (HMS) and Super HMS (SHMS). 
+Hall C was able to demonstrate KPP in four days of beam time before an important component of the accelerator was damaged which
+caused to accelerator to shut down for repair. The accelerator is expected to be operational starting December 4, 2017. As a
+result of this delay, the commissioning experiments that were scheduled to run on Fall 2017 have now shifted to Spring 2018.
+This time window has allowed the Hall C collaboration to work extensively in preparation for the commissioning of the
+spectrometers on December. \\
+\indent One of the projects I have been involved in is the ongoing work on testing and commissioning the 12 GeV HMS Drift
+Chambers. The chambers were constructed at Hampton University by Dr. Liguang Tang and his graduate students in 2016.
+They were made the same design as the SHMS chambers, but slightly different size. The chambers were transported to Jefferson Lab on November 2016,
+where they underwent extensive tests as part of conditioning the chambers to sustain High Voltages using a gas mixture\footnote{This gas mixture is non-flammable and
+at lower cost compared to the gas mixture that the chambers run on during an experiment, which is why it is preferred during the testing phase of the detector.}
+of 75:25 Argon/CO$_{2}$ by volume. The chambers were found to be operational below 1850 V which is below the expected value\footnote{The HMS chambers
+are the same design as the SHMS chambers, which operate at $\sim$ 1940 V.} of 1940 V. At high voltages above 1850 V, the chambers drew a significant amount of
+dark current which made the signals from the chamber noisy.
+It was determined that the most likely cause of the large currents drawn was the gas mixture[Ar/CO$_{2}$] being used, so the one of the chambers (HMS DC II) was transported to the
+experimental Hall C where a gas mixture of 50:50 Argon/Ethane by volume was used. A test stand for the chamber was set up in the HMS hut, where it has been tested and
+verified to be operational with the new gas mixture. The other chamber (HMS DC I) exhibited similar symptoms as the first with the addition that it had a few missing channels
+due to a bad connection between the sense wires and the discriminator cards. The second chamber is now ready to be transported to Hall C for further tests with the
+Argon/Ethane gas mixture before it can be put in the detector stack.\\
+\indent A second project I am currently involved in is the determination of electronic and computer dead times. In nuclear/particle physics experiments,
+the number of physics events (triggers) are counted via nuclear electronic modules. These triggers ultimately get processed by the DAQ before being
+written to tape. The deadtime refers to the time window in which the modules are unable to process triggers and physics events are lost.
+The electronic deadtime contribution comes from the electronic modules having a maximum rate capability. Typically,
+the electronic modules in Hall C can achieve rates from a few MHz to few hundred MHz. Once the modules reach their limit, a pileup of signals can occur which
+contributes to the total dead time. The computer deadtime contribution comes from finite processing time of the DAQ. These rates are typically on the order of
+a few kHz, therefore, the dominant contribution of total dead time comes from the DAQ, since it takes a few kHz of data before physics events
+are lost. These measurements are important for the determination of high precision cross section measurements in Hall C, since knowing how many events
+are actually lost can make a significant difference in the uncertainty of the cross section. \\
+\indent My thesis experiment, the \textit{Electro-Disintegration of Deuteron at Very High Missing Momenta} is projected to run towards the end of
+February 2018, and will receive a total of six days of beam time. The experiment will be done at four different spectrometer configurations. The kinematic
+setting have changed slightly from the original proposal, and will be briefly discussed in this paper.
 
-This template, modified in MS Word 2003 and saved as ÒWord 97-2003 \& 6.0/95 Ð RTFÓ for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
+\section{12 GeV HMS Drift Chambers}
 
-\section{PROCEDURE FOR PAPER SUBMISSION}
-
-\subsection{Selecting a Template (Heading 2)}
-
-First, confirm that you have the correct template for your paper size.
-This template has been tailored for output on the US-letter paper size.
-Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.
+\subsection{Design and Operation of the Chambers}
+The new HMS Drift Chambers were designed to be geometrically the same as the SHMS Drift Chambers. Each chamber consists of 6 wire planes and each wire
+plane is located between two cathode planes. The wire planes consist of alternating field and sense wires. The U, U', V and V' planes consist of
+96 sense wires each and are oriented 60$^{o}$ relative to the +x-coordinate. The X and X' planes consist of 102 sense wires and are oriented perpendicular to the x-axis (See
+Figures \ref{fig:dc1_planes} and \ref{fig:dc_wires}).
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.0in, height=2.5in]{dc2_tests/HMS_DC1_Planes.pdf}
+  \caption{HMS Drift Chamber 1 wire planes.}
+  \label{fig:dc1_planes}
+\end{figure}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.0in, height=1.5in]{dc2_tests/HMS_DC_Wires.pdf}
+  \caption{HMS Drift Chamber wire orientation for planes a) U, U', b) V, V' and c) X, X' where
+  the direction of the beam (+z) is into the plane of the paper.}
+  \label{fig:dc_wires}
+\end{figure}
+The cathode planes and field wires are held at a negative high voltage and the sense wires are grounded which establihses a potential gradient causing an electric field
+between high voltage and grounded wires. Each chamber is filled with a gas mixture\footnote{Argon is mixed with CO$_{2}$ or Ethane, where Argon is the ionizing agent the
+particles interact with, and Ethane/CO$_{2}$ are the quenching elements to control avalanche produced by secondary ionization} of Argon with either CO$_{2}$ or Ethane.
+As the particles traverse the chamber, the free electrons from ionized Argon drift towards the sense wires producing a detectable signal which is read out via discriminator
+cards and into electronic modules.
 

### 2017-10-22 chamber.cc

@@ -1,0 +1,68 @@
+// 10/03/2017. here I want to compare the dark current drawn by hms ( with ARCO2) shms(ArCO2) and hms (ArC2H5)
+
+
+
+#include <iostream>
+#include <string>
+#include "TGraph.h"
+#include "TCanvas.h"
+using namespace std;
+void chamber()
+{
+  gStyle->SetOptStat(0);
+  TCanvas *c1=new TCanvas("c1","",1800,1800);
+  TMultiGraph *mg = new TMultiGraph();
+  c1->cd();
+
+  // Hms with ArCO2
+  mg->SetTitle("Comparison of Current Drawn with Different Gas Mixtures");
+  Double_t x1[7]={1750,1775,1800,1825,1850,1875,1900};
+  Double_t y1[7] ={3.9,4.2,4.7,5.5,7.2,29,105};
+  TGraph *gr1 = new TGraph(7,x1,y1);
+  gr1->SetMarkerStyle(kFullCircle);
+  gr1->SetMarkerColor(4);
+  mg->Add(gr1); 
+  // SHMS ArCO2
+  Double_t x2[9]={1750,1800,1825,1850,1875,1900,1925,1950,1962};
+  Double_t y2[9] ={0.7,0.9,1.0,1.1,1.3,1.5,2.3,18,45};
+  TGraph *gr2 = new TGraph(9,x2,y2);
+  gr2->SetMarkerStyle(kFullSquare);
+  gr2->SetMarkerColor(kBlack);
+  mg->Add(gr2);
+  //HMS Ar:Ethane 50:50
+  Double_t x3[17]={1800,1825,1850,1875,1900,1925,1950,1975,2000,2025,2050,2075,2100,2125,2150,2175,2200};
+  Double_t y3[17] ={0.015,0.02,0.02,0.02,0.02,0.025,0.03,0.035,0.04,0.065,0.085,0.1,0.11,0.125,0.17,0.3,21.1};
+ TGraph *gr3 = new TGraph(17,x3,y3);
+
+ gr3->SetMarkerStyle(kFullTriangleUp);
+  gr3->SetMarkerColor(2);
+  mg->Add(gr3);
+  mg->Draw("alp");
+
+  
+  TLegend *leg = new TLegend(0.1, 0.7, 0.3, 0.9);
+  leg->SetFillColor(0);
[…]

### 2017-10-25 NRF_Final_Report/report.tex
started writing hms dc subsections
updated report

@@
 plane is located between two cathode planes. The wire planes consist of alternating field and sense wires. The U, U', V and V' planes consist of
-96 sense wires each and are oriented 60$^{o}$ relative to the +x-coordinate. The X and X' planes consist of 102 sense wires and are oriented perpendicular to the x-axis (See
+96 sense wires each and are oriented 60$^{o}$ relative to the +y-coordinate. The X and X' planes consist of 102 sense wires and are oriented perpendicular to the x-axis (See
 Figures \ref{fig:dc1_planes} and \ref{fig:dc_wires}).
@@
 
-\subsection{Maintaining the Integrity of the Specifications}
-
-The template is used to format your paper and style the text.
-All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them.
-You may note peculiarities.
-For example, the head margin in this template measures proportionately more than is customary.
-This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations
-
+\subsection{HMS Drift Chamber Cosmic Tests}
+To determine the operatility of the HMS Drift Chambers, several cosmic tests were performed on the chambers in the Experimental Storage Building (ESB) before being transported
+to Hall C. The chambers did not held the High Voltage beyond 1850 V without drawing a significant amount of current ($\geq$ 10 $\mu$A ) using a gas mixture of 75:25 Ar/CO$_{2}$ by
+volume. When Drift Chamber II (DCII) was transported to Hall C, the gas mixture was changed to 50:50 Ar/Ethane and a High Voltage scan was done (See Figure \ref{fig:current_draw})  
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=4.0in, height=2.4in]{dc2_tests/gas_mix_current_drawn.pdf}
+  \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures. The subplot shows a zoomed version of the HMS DC II plot on a small scale.}
+  \label{fig:current_draw}
+\end{figure} \\
+Figure \ref{fig:current_draw} shows a decrease is the current drawn by the HMS chambers by three orders of magnitude smaller, from a few $\mu$A to a few nA of current drawn. This
+indicates that Ethane is a better quenching gas, as it kept the secondary electron ionization small for a broader range of High Voltages, up to $\sim$2100 Volts. There is still the
+unresolved issue of why the HMS and SHMS chambers behave differently with the same gas mixture, since they both have the same design. The broad High Voltage range achieved by DC II without
+significant current drawn allows for a better determination of the \textit{Plateau Region} of the chambers, which is a region in which the chamber efficinecies have little sensitivity
+to relatively large High Voltage variations of $\sim$40 V. \\
+\indent To determine the plateau region of HMS DC II,  a cosmic test stand was set up in the HMS detector hut (See Figure \ref{fig:cosmic_stand}).
+The setup consists of two scintillator paddles on the top
+and two on bottom of the chamber.
+The top two are completely overlapped while the bottom two are only partially overlapped.
+Each scintillator paddle is wrapped around a light tight material known as Tedlar,
+and is coupled to a Photomultiplier Tube (PMT) via a light guide.
+To ensure that only cosmic rays pass through the chamber, a coincidence between the top and bottom PMTs is made.
+It is required that the top
+two PMTs detect a signal to reduce the probability of instrinsic noise being interpreted as a cosmic signal.
+The bottom scintillators are partially overlapped to achieve full coverage of the chamber active
+area, and a less restrictive requirement was made by requiring that either of the bottom PMTs detect a signal.
+A final requirement was made so that the top and bottom PMTs would detect a signal within a
+certain time window. This requirement ensures a correlation between the top and bottom PMT signals, making it highly probable that the signal was produced by a cosmic ray. 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.4in, height=2.4in]{dc2_tests/dc2_teststand_03.jpg}
+  \caption{Cosmic test stand setup in Hall C detector hut.}
+  \label{fig:cosmic_stand}
+\end{figure} \\
+When cosmic data was taken, to ensure that all (or at leas most) of the sense wires in each plane were present (and had not been damaged by transporting the chamber), the wiremap distribution was
+a looked at first. The distributions show full occupancy for all wire planes in DC II (See Figure \ref{fig:hdc2_wiremap}).  
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.8in, height=2.2in]{dc2_tests/hdc2_xmap.pdf}
+  \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
+  \label{fig:hdc2_wiremap}
+\end{figure} \\
+Once all planes of the chamber were verified to have full occupancy, a High Voltage and threshold\footnote{The threshold set on the chamber is used to filter cosmic signals from noise by requiring that
+  the signals to be a certain size before discriminating them as logic signals, which are read out by the electronic modules.} scan was done to determine the plateau region.
+A high voltage scan was done first
+by setting the threshold fixed at 4.5 V.
+The optimal HV setting was determined to be 1940 V.
+A threshold scan was then performed at 1940 V to determine the optimal threshold.
+The results are shown in Figures
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_hvscan_thrs45.pdf}
+  \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
+  \label{fig:hdc2_wire}
+\end{figure} \\
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_thrsscan_HV_1940V.pdf}
+  \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
+  \label{fig:hdc2_wire}
+\end{figure} \\
 \section{MATH}

### 2017-10-25 make_plots/plot_eff.C

@@ -1,0 +1,94 @@
+void plot_eff()
+{
+//Plot Efficiency Curve for HV scan of DC2, at a threshold = 4.5 V:
+  //HMS Runs 673 (HV = -1940, 435 evts) 
+  //         674 (HV = -1840, 557 evts)
+  //         675 (HV = -1740, 554 evts)
+  //         676 (HV = -1640, 523 evts)   //not enough statistics
+  //         677 (HV = -1970, 547 evts)
+  //         678 (HV = -1700, 1294 evts)
+  //         683 (HV = -1900, 725 evts )
+  // create first graph
+
+  const Int_t n = 6;
+  
+  //Read in the data
+  Double_t HV[] = {1700, 1740, 1840, 1900, 1940, 1970};   //X-axis (High Voltage)
+  Double_t ex[] = {0.0,0.0,0.0,0.0,0.0,0.0};            // no error in X
+  
+  //HMS DC2 Plane Efficiency
+  Double_t eff_u1[] = {0.72, 0.79  , 0.974, 0.998, 1.0, 1.0};               
+  Double_t err_u1[] = {0.06, 0.0452, 0.0069,0.00139, 0.0, 0.0};    //uncertainty is given in percent    
+  
+  Double_t eff_u2[] = {0.72, 0.853 , 0.986, 0.998,  1.0, 1.0};            
+  Double_t err_u2[] = {0.06, 0.0408, 0.0052, 0.00139, 0.0, 0.0};      
+
+  Double_t eff_x1[] = {0.8, 0.771 , 0.978, 0.998, 1.0, 1.0};               
+  Double_t err_x1[] = {0.059, 0.0461, 0.0064, 0.00139, 0.0, 0.0};      
+  
+  Double_t eff_x2[] = {0.8, 0.888,  0.968, 0.9958, 0.995, 0.994};            
+  Double_t err_x2[] = {0.059, 0.037,  0.00768, 0.00241, 0.00328, 0.00319};      
+
+  Double_t eff_v1[] = {0.923, 0.901,  0.990, 1.0,  1.0, 1.0};               
+  Double_t err_v1[] = {0.042, 0.0353, 0.0044,0.0, 0.0, 0.0};      
+  
+  Double_t eff_v2[] = {0.9, 0.864,  1.0, 1.0, 1.0, 1.0};            
[…]

### 2017-10-25 make_plots/plot_eff_threshold_scan.C

@@ -1,0 +1,107 @@
+void plot_eff_threshold_scan()
+{
+//Plot Efficiency Curve for Threshold scan of DC2, at HV = -1940 V:
+  //HMS Runs 682 (Thrs = 3.5V,  1082 evts )
+  //         673 (Thrs = 4.5V,  435 evts)
+  //         679 (Thsr = 5.5V , 1209 evts) 
+  //         680 (Thrs = 6.5V,  1680 evts)
+  //         681 (Thrs = 7.5V,  1177 evts) 
+  //         689 (Thrs = 8.5V,  1434 evts)
+  //         690 (Thrs = 9.4V)
+
+  // create first graph
+
+  const Int_t n = 6;
+  
+  //Read in the data
+  Double_t Thrs[] = {3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.4};   //X-axis (High Voltage)
+  Double_t ex[] = {0.0,0.0,0.0,0.0,0.0,0.0,0.0};            // no error in X
+  
+  //HMS DC2 Plane Efficiency
+  Double_t eff_u1[] = {1.0, 1.0, 0.999, 0.996, 0.995, 0.987,0.978};               
+  Double_t err_u1[] = {0.0, 0.00, 0.000845, 0.00135, 0.00194, 0.00296, 0.0033};    //uncertainty is given in percent    
+  
+  Double_t eff_u2[] = {1.0, 1.0, 1.0, 1.0, 0.998, 0.998, 0.990};            
+  Double_t err_u2[] = {0.0, 0.0, 0.0, 0.0, 0.00123, 0.00103, 0.00223};      
+
+  Double_t eff_x1[] = {1.0, 1.0, 1.0, 0.998, 1.0, 0.992, 0.983};               
+  Double_t err_x1[] = {0.0, 0.0, 0.0, 0.000862, 0.0, 0.00239, 0.00287};      
+  
+  Double_t eff_x2[] = {0.996, 0.995, 0.989, 0.989, 0.991, 0.995, 0.992};            
+  Double_t err_x2[] = {0.00186, 0.00328, 0.0030, 0.00247, 0.00273, 0.00178, 0.00199};      
+
+  Double_t eff_v1[] = {1.0, 1.0, 1.0, 0.999, 0.997, 0.995, 0.988};               
[…]

### 2017-10-25 make_plots/plot_eff_threshold_scan_HV1875.C

@@ -1,0 +1,104 @@
+void plot_eff_threshold_scan_HV1875()
+{
+
+
+//Plot Efficiency Curve for Threshold scan of DC2, at HV = -1875 V:
+  //HMS Runs 693 (Thrs = 10.5V,  490 evts )
+  //694 (Thrs = 8.5, 506 evts)
+  // 695 (Thrs = 6.5, )
+  // 696 (Thrs = 4.5, )
+
+  const Int_t n = 4;
+  
+  //Read in the data
+ Double_t Thrs[] = {4.5, 6.5, 8.5,10.5};   //X-axis (High Voltage)
+ Double_t ex[] = {0.0, 0.0, 0.0, 0.0};            // no error in X
+  
+  //HMS DC2 Plane Efficiency
+ Double_t eff_u1[] = {0.986, 0.955, 0.896, 0.819};               
+ Double_t err_u1[] = {0.00465, 0.00969, 0.0163, 0.0268};    //uncertainty is given in percent    
+  
+ Double_t eff_u2[] = {0.998, 0.984, 0.953, 0.938};            
+ Double_t err_u2[] = {0.00167, 0.00599, 0.0116, 0.0179};      
+
+ Double_t eff_x1[] = {0.996, 0.981, 0.914, 0.848};               
+ Double_t err_x1[] = {0.00236, 0.00638, 0.0151, 0.0254};      
+  
+ Double_t eff_x2[] = {0.998, 0.979, 0.942, 0.893};            
+ Double_t err_x2[] = {0.00167, 0.00674, 0.0128, 0.0224};      
+
+ Double_t eff_v1[] = {0.996, 0.990, 0.953, 0.918};               
+ Double_t err_v1[] = {0.00236, 0.00457, 0.0116, 0.0202};      
+  
+ Double_t eff_v2[] = {0.998, 0.986, 0.965, 0.933};            
+ Double_t err_v2[] = {0.00167, 0.00556, 0.0101, 0.0185};      
+
+
+  TCanvas *c1 = new TCanvas("c1", "", 2000,500);
+  c1->SetGrid();
+  
+  // draw a frame to define the range
+  TMultiGraph *mg = new TMultiGraph();
+  
[…]

### 2017-10-25 make_plots/plot_eff_threshold_scan_HV1940.C

@@ -1,0 +1,108 @@
+void plot_eff_threshold_scan_HV1940()
+{
+//Plot Efficiency Curve for Threshold scan of DC2, at HV = -1940 V:
+  //HMS Runs 682 (Thrs = 3.5V,  1082 evts )
+  //         673 (Thrs = 4.5V,  435 evts)
+  //         679 (Thsr = 5.5V , 1209 evts) 
+  //         680 (Thrs = 6.5V,  1680 evts)
+  //         681 (Thrs = 7.5V,  1177 evts) 
+  //         689 (Thrs = 8.5V,  1434 evts)
+  //         690 (Thrs = 9.4V)
+  //         692 (Thrs = 10.5,   1619 evts)
+
+  // create first graph
+
+  const Int_t n = 8;
+  
+  //Read in the data
+  Double_t Thrs[] = {3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.4, 10.4};   //X-axis (High Voltage)
+  Double_t ex[] = {0.0,0.0,0.0,0.0,0.0,0.0,0.0};            // no error in X
+  
+  //HMS DC2 Plane Efficiency
+  Double_t eff_u1[] = {1.0, 1.0, 0.999, 0.996, 0.995, 0.987,0.978, 0.969};               
+  Double_t err_u1[] = {0.0, 0.00, 0.000845, 0.00135, 0.00194, 0.00296, 0.0033, 0.00453};    //uncertainty is given in percent    
+  
+  Double_t eff_u2[] = {1.0, 1.0, 1.0, 1.0, 0.998, 0.998, 0.990, 0.985};            
+  Double_t err_u2[] = {0.0, 0.0, 0.0, 0.0, 0.00123, 0.00103, 0.00223, 0.00317};      
+
+  Double_t eff_x1[] = {1.0, 1.0, 1.0, 0.998, 1.0, 0.992, 0.983, 0.977};               
+  Double_t err_x1[] = {0.0, 0.0, 0.0, 0.000862, 0.0, 0.00239, 0.00287, 0.00387};      
+  
+  Double_t eff_x2[] = {0.996, 0.995, 0.989, 0.989, 0.991, 0.995, 0.992, 0.975};            
[…]

### 2017-10-25 NRF_Final_Report/report.tex
finished section on drft chambers

@@
   \includegraphics[width=4.0in, height=2.4in]{dc2_tests/gas_mix_current_drawn.pdf}
-  \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures. The subplot shows a zoomed version of the HMS DC II plot on a small scale.}
+  \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures.
+The subplot shows a zoomed version of the Argon/Ethane gas mixture used in HMS DC II plot on a nanoampere scale.}
   \label{fig:current_draw}
@@
 unresolved issue of why the HMS and SHMS chambers behave differently with the same gas mixture, since they both have the same design. The broad High Voltage range achieved by DC II without
-significant current drawn allows for a better determination of the \textit{Plateau Region} of the chambers, which is a region in which the chamber efficinecies have little sensitivity
-to relatively large High Voltage variations of $\sim$40 V. \\
+significant current drawn allows for a better determination of the \textit{Plateau Region} of the chambers, which is a region in which the chamber efficiencies have little sensitivity
+to relatively large High Voltage variations. \\
 \indent To determine the plateau region of HMS DC II,  a cosmic test stand was set up in the HMS detector hut (See Figure \ref{fig:cosmic_stand}).
@@
 A final requirement was made so that the top and bottom PMTs would detect a signal within a
-certain time window. This requirement ensures a correlation between the top and bottom PMT signals, making it highly probable that the signal was produced by a cosmic ray. 
+certain time window.
+This requirement ensures a correlation between the top and bottom PMT signals, making it highly probable that the signal was produced by a cosmic ray.
+The correlated signal between the top and
+bottom PMTs is defined as the \textit{trigger}. The efficiency of the \textit{i$^{th}$} plane, $\epsilon_{i}$, can then be defined as follows,
+\begin{equation}
+\epsilon_{i} = \frac{\# \text{ triggers that \textit{did} hit the \textit{i$^{th}$} plane } }{\# \text{ triggers that \textit{should} have hit the \textit{i$^{th}$} plane} } 
+\end{equation}
+given that the other five planes received at least one hit from the cosmic. \\
+\indent To make a reliable efficiency measurement, it has to be ensured from the geometry of the cosmic set-up, that any cosmic passing though the top and bottom scintillators also traverses every plane in the chamber
+to make the efficiency measurements unbiased to the scintllators orientation. 
 \begin{figure}[h!]
@@
 \end{figure} \\
-When cosmic data was taken, to ensure that all (or at leas most) of the sense wires in each plane were present (and had not been damaged by transporting the chamber), the wiremap distribution was
+When cosmic data was taken, to ensure that all (or at least most) of the sense wires in each plane were present (and had not been damaged by transporting the chamber), the wiremap distribution was
 a looked at first. The distributions show full occupancy for all wire planes in DC II (See Figure \ref{fig:hdc2_wiremap}).  
@@
 A high voltage scan was done first
-by setting the threshold fixed at 4.5 V.
-The optimal HV setting was determined to be 1940 V.
+by setting the threshold fixed at 4.5 V to determine the optimal HV setting.
 A threshold scan was then performed at 1940 V to determine the optimal threshold.
-The results are shown in Figures
+The results are shown in Figures \ref{fig:hdc2_hvscan}
+and \ref{fig:hdc2_thrsscan}.
+The high voltage scan in Figure \ref{fig:hdc2_hvscan} shows the plateau region starting at 1900 V.
+The chamber operational high voltage was chosen to be 1940 V since the efficiencies seem
+to be stable and better than 99$\%$ over a $\sim\pm$40 Volt range about this central setting.
 \begin{figure}[h!]
@@
   \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_hvscan_thrs45.pdf}
-  \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
-  \label{fig:hdc2_wire}
-\end{figure} \\
+  \caption{High Voltage scan of DC II over a broad range at a Threshold of 4.5 Volts.}
+  \label{fig:hdc2_hvscan}
+\end{figure} 
 \begin{figure}[h!]
@@
   \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_thrsscan_HV_1940V.pdf}
-  \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
-  \label{fig:hdc2_wire}
+  \caption{Threshold scan over a broad range at a HV setting of 1940 V.}
+  \label{fig:hdc2_thrsscan}
 \end{figure} \\
+From the threshold scan results in Figure \ref{fig:hdc2_thrsscan}, there is a 3$\%$ decrease in the plane efficiencies over a
+6 Volt range. The operational threshold voltage was determined to be 4.5 Volts, where the efficiencies are better than 99$\%$, over a $\sim$ 1 Volt range.
+The high voltage and threshold settings determined from the scans were chosen based on the high efficiency region and its small sensitivity over a voltage range.
+
 \section{MATH}

### 2017-10-26 NRF_Final_Report/report.tex
started adding edtm section

@@
 \end{figure} \\
-Once all planes of the chamber were verified to have full occupancy, a High Voltage and threshold\footnote{The threshold set on the chamber is used to filter cosmic signals from noise by requiring that
-the signals to be a certain size before discriminating them as logic signals, which are read out by the electronic modules.} scan was done to determine the plateau region.
+Once all planes of the chamber were verified to have full occupancy, a High Voltage and threshold\footnote{The threshold set on the chamber is used to filter cosmic signals from noise by requiring 
+the signal amplitude to cross a threshold before discriminating them to produce logic signals, which are read out by the electronic modules.} scan was done to determine the plateau region.
 A high voltage scan was done first
@@
 
-\section{MATH}
+\section{Electronic and Computer Deadtime Studies}
+The procedure to determine the computer and electronic dead times is currently in the development stage in Hall C. The general idea is to use a pulse generator to produce
+a fixed frequency pulse and feed it as early as possible into the electronic modules being used in the experimental setup. This pulse will interfere wth the actual signals
+produced by physics, but its rate can be set orders of magnitude smaller such that its interference will be minimal and will have insignificant contribution to the deadtime.
+By counting the number of pulses generated before sending them to the electronics chain, compared to the number of pulses that actually make it to the end of the chain and
+are accepted by the TI (Trigger Interface) module, one may determine the dead time as follows:
+\begin{equation}
+  \text{dead time} = 1 - \frac{\# \text{ of accepted pulses}}{\# \text{ of generated pulses}}
+\end{equation}
+This is the total deadtime from the electronics and computer (TI module) that arises due to the finite processing time of the modules.
+The computer live time alone is calculated by the TI module since it has an
+internal scaler which counts the number of input and output signals, and takes the ratio to determine the computer live time.
+This calculation can also be done externally as a cross-check by counting the number of signals that make it to the
+TI via a scaler module, and comparing it to the number of accepted signals which is outputted by the TI and determined during the data analysis stage.
+The electronics deadtime is investigated by keeping the computer live time near 100$\%$ and
+increasing the pulse generator rate to probe the rate limits of the electronics modules.
+One might argue that such high rates can reduce the computer live time itself which is true, however, such high rates can be pre-scaled by the TI by orders
+of magnitude, such that the computer live time is preserved.
+For example, for every 10,000 counts/sec., (10 KHz), the TI counts 100 Hz., so that the rate is pre-scaled by a factor of 10$^{3}$.
+Using this technique, one can investigate the
+effects of high rates on the electronic modules. In this limitng case, the total live time measured will be the electronics live time, since the computer live time will be fixed. \\
+\indent The electronic and computer live time measurements have not been completed as there had been some issues encountered with the TI module that is currently being investgated by DAQ experts.
+These issues were uncovered during the
+initial stages of the deadtime studies in which a pulse generator at various rates was used to probe the limits of the modules.
 

### 2017-10-29 NRF_Final_Report/report.tex
finished NRC 10-page report

--- 2017-10-25 NRF_Final_Report/report.tex
@@
 
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
+\documentclass[letterpaper, 12 pt, conference]{ieeeconf}  % Comment this line out
                                                           % if you need a4paper
@@
 \overrideIEEEmargins
-
+\pagestyle{plain}
 \title{\LARGE \bf
@@
 
-\author{Carlos Yero \\
+\author{\normalsize Carlos Yero \\
+  Major Advisor: Dr. Werner Boeglin\\
   October 30, 2017}
@@
     \maketitle
+
+    \pagestyle{plain}
+    \thispagestyle{plain}
+
     \begin{abstract}
@@
 \section{INTRODUCTION}
-On March 7-10 of 2017, a 5 $\mu$A electron beam was delivered to a BeO and Carbon targets for the first time to experimental
+\noindent On March 7-10 of 2017, a 5 $\mu$A electron beam was delivered for the first time to experimental
 Hall C since the 12 GeV upgrade. The beam was delivered as part of the Key Performance Parameters (KPP) required by the
@@
 \indent One of the projects I have been involved in is the ongoing work on testing and commissioning the 12 GeV HMS Drift
-Chambers. The chambers were constructed at Hampton University by Dr. Liguang Tang and his graduate students in 2016.
+Chambers. The chambers were constructed at Hampton University by Dr. Liguang Tang and his graduate students in 2016\cite{bishnu}.
 They were made the same design as the SHMS chambers, but slightly different size. The chambers were transported to Jefferson Lab on November 2016,
 where they underwent extensive tests as part of conditioning the chambers to sustain High Voltages using a gas mixture\footnote{This gas mixture is non-flammable and
-at lower cost compared to the gas mixture that the chambers run on during an experiment, which is why it is preferred during the testing phase of the detector.}
+safer to use outside the Hall, compared than the gas mixture that the chambers run on during an experiment, which is why it is preferred during the testing phase of the detector.}
 of 75:25 Argon/CO$_{2}$ by volume. The chambers were found to be operational below 1850 V which is below the expected value\footnote{The HMS chambers
@@
 verified to be operational with the new gas mixture. The other chamber (HMS DC I) exhibited similar symptoms as the first with the addition that it had a few missing channels
-due to a bad connection between the sense wires and the discriminator cards. The second chamber is now ready to be transported to Hall C for further tests with the
+due to a bad connection between the sense wires and external connector. The second chamber is now ready to be transported to Hall C for further tests with the
 Argon/Ethane gas mixture before it can be put in the detector stack.\\
 \indent A second project I am currently involved in is the determination of electronic and computer dead times. In nuclear/particle physics experiments,
-the number of physics events (triggers) are counted via nuclear electronic modules. These triggers ultimately get processed by the DAQ before being
+the number of physics events (or triggers\footnote{A condition that is imposed on the detected signals to determine whether or not it corresponds to a physics event.}  are counted via nuclear electronic modules.
+These triggers ultimately get processed by the DAQ before being
 written to tape. The deadtime refers to the time window in which the modules are unable to process triggers and physics events are lost.
@@
 \subsection{Design and Operation of the Chambers}
-The new HMS Drift Chambers were designed to be geometrically the same as the SHMS Drift Chambers. Each chamber consists of 6 wire planes and each wire
+\noindent The new HMS Drift Chambers were designed to be geometrically the same as the SHMS Drift Chambers. Each chamber consists of 6 wire planes and each wire
 plane is located between two cathode planes. The wire planes consist of alternating field and sense wires. The U, U', V and V' planes consist of
@@
 \subsection{HMS Drift Chamber Cosmic Tests}
-To determine the operatility of the HMS Drift Chambers, several cosmic tests were performed on the chambers in the Experimental Storage Building (ESB) before being transported
+\noindent To determine the operatility of the HMS Drift Chambers, several cosmic tests were performed on the chambers in the Experimental Storage Building (ESB) before being transported
 to Hall C. The chambers did not held the High Voltage beyond 1850 V without drawing a significant amount of current ($\geq$ 10 $\mu$A ) using a gas mixture of 75:25 Ar/CO$_{2}$ by
@@
   \centering
-  \includegraphics[width=4.0in, height=2.4in]{dc2_tests/gas_mix_current_drawn.pdf}
+  \includegraphics[width=3.5in, height=2.4in]{dc2_tests/gas_mix_current_drawn.pdf}
   \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures.
@@
 The correlated signal between the top and
-bottom PMTs is defined as the \textit{trigger}. The efficiency of the \textit{i$^{th}$} plane, $\epsilon_{i}$, can then be defined as follows,
-\begin{equation}
-\epsilon_{i} = \frac{\# \text{ triggers that \textit{did} hit the \textit{i$^{th}$} plane } }{\# \text{ triggers that \textit{should} have hit the \textit{i$^{th}$} plane} } 
-\end{equation}
+bottom PMTs is defined as the \textit{trigger}. The efficiency of the \textit{i$^{th}$} plane, $\epsilon_{i}$, can then be defined as follows, \\
+\begin{align*}
+\epsilon_{i} = \frac{\# \text{ triggers that hit the \textit{i$^{th}$} plane } }{\# \text{ triggers that \textit{should} have hit the \textit{i$^{th}$} plane} } 
+\end{align*} \\
 given that the other five planes received at least one hit from the cosmic. \\
@@
   \centering
-  \includegraphics[width=3.8in, height=2.2in]{dc2_tests/hdc2_xmap.pdf}
+  \includegraphics[width=3.7in, height=2.2in]{dc2_tests/hdc2_xmap.pdf}
   \caption{Wiremap distribution of the X Plane in DC II shows occupancy in all wires.}
@@
   \centering
-  \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_hvscan_thrs45.pdf}
+  \includegraphics[width=3.8in, height=2.2in]{dc2_tests/dc2_hvscan_thrs45.pdf}
   \caption{High Voltage scan of DC II over a broad range at a Threshold of 4.5 Volts.}
@@
   \centering
-  \includegraphics[width=4.1in, height=2.2in]{dc2_tests/dc2_thrsscan_HV_1940V.pdf}
+  \includegraphics[width=3.8in, height=2.2in]{dc2_tests/dc2_thrsscan_HV_1940V.pdf}
   \caption{Threshold scan over a broad range at a HV setting of 1940 V.}
@@
 
-\section{MATH}
-
-Before you begin to format your paper, first write and save the content as a separate text file.
-Keep your text and graphic files separate until after the text has been formatted and styled.
-Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph.
-Do not add any kind of pagination anywhere in the paper.
-Do not number text heads-the template will do that for you.
-
-Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:
-
-\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract.
-Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined.
-Do not use abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
+\section{Electronic and Computer Deadtime Studies}
+\subsection{Dead Time Measurements Procedure}
+\noindent The procedure to determine the computer and electronic dead times is currently in the development stage in Hall C. The general idea is to use a pulse generator to produce
+a fixed frequency pulse and feed it as early as possible into the electronic modules being used in the experimental setup. This pulse will interfere wth the actual signals
+produced by physics, but its rate can be set orders of magnitude smaller such that its interference will be minimal and will have insignificant contribution to the deadtime.
+By counting the number of pulses generated before sending them to the electronics chain, compared to the number of pulses that actually make it to the end of the chain and
+are accepted by the TI (Trigger Interface) module\cite{TI}, one may determine the dead time as follows:
+\begin{equation} \label{deadtime}
+  \text{total D.T.} = 1 - \underbrace{\frac{\# \text{ of accepted pulses}}{\# \text{ of generated pulses}}}_{\text{\normalsize total L.T.}} 
+\end{equation}
+This is the total deadtime from the electronics and computer (TI module) that arises due to the finite processing time of the modules.
+From Eq.
+\ref{deadtime},  the total live time has contributions from the computer and electronics, which can
+be calculated separately. \\
+\indent The computer live time is calculated by the TI module since it has an
+internal scaler which counts the number of input and accepted triggers, and takes the ratio.
+This calculation can also be done externally as a cross-check by counting the number of signals that make it to the
+TI via an external scaler module, and comparing it to the number of accepted triggers which is outputted by the TI and determined during the data analysis stage. \\
+\indent The electronics livetime cannot be determined directly,  but it can be determined by keeping the computer live time fixed near 100$\%$ and
+increasing the pulse generator rate to probe the capability of the electronics modules to handle high rates.
+This way, if there is a decrease in the total live time which can be measured directly, then it must have been caused by the
+electronics, since the computer live time is kept fixed. \\
+\indent One might argue that such high rates can reduce the computer live time itself which is true, however, such high rates can be pre-scaled by the TI by orders
+of magnitude, such that the computer live time is kept fixed.
+For example, the TI can be pre-scaled by 10$^{2}$ such that for a rate of 100,000 counts/sec.
+(100 KHz), the TI accepts 1 kHz.
+Using this technique, one can investigate the
+effects of high rates on the electronic modules without having a significant contribution from the computer live time. \\
+\subsection{Basic Concepts on Computer Live Time}
+\noindent To better understand how the computer live time is determined, I will introduce some basic concepts about how the TI module does this calculation.
+The main functionality of the TI is to process and distribute triggers and initiate data readout in fast electronics modules.
+Due to the finite processing time of these modules, the TI has a \textit{deadtime} in which it is unable to process any more triggers until after all other fast electronics modules have finished processing the current trigger.
+During this time, the TI generates a BUSY signal typically on the order of a few microseconds ($\mu$s) during which
+all other input triggers are rejected. \\
+\indent To understand computer live time experimentally, one can use a pulse generator to feed a controlled pulse into the TI and explore the effect of
+various pulse rates on the deadtime. Based on the periodicity of the input pulse and the output BUSY signal width of the TI, three limiting cases arise:
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.4in, height=2.8in]{edtm/edtm_cases.pdf}
+  \caption{Three limiting cases on TI computer live time based on the input signal.}
+  \label{fig:edtm_cases}
+\end{figure} \\
 
 \begin{itemize}
-
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as Ò3.5-inch disk driveÓ.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ÒWb/m2Ó or Òwebers per square meterÓ, not Òwebers/m2Ó.
-Spell out units when they appear in text: Ò.
-.
-.
-a few henriesÓ, not Ò.
-.
-.
-a few HÓ.
-\item Use a zero before decimal points: Ò0.25Ó, not Ò.25Ó. Use Òcm3Ó, not ÒccÓ. (bullet list)
-
+\item Case 1: The pulse periodicity falls outside the TI BUSY window so the ratio of accepted signals to input signals is unity and the live time is 100$\%$\\
+\item Case 2: The pulse periodicity is equal to the width of the BUSY window, so every two input pulses, the first one wll open a BUSY window and the second will be blocked by the BUSY so the TI accepts only 1/2 the input signals and the live time is 50$\%$.
+\\
+\item Case 3: The pulse periodicity is smaller than the BUSY window so the live time is 50$\%$ or less. 
 \end{itemize}
-
-\subsection{Equations}
-
-The equations are an exception to the prescribed specifications of this template.
-You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font).
-To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled.
-Number equations consecutively.
-Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop.
-To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents.
-Italicize Roman symbols for quantities and variables, but not Greek symbols.
-Use a long dash rather than a hyphen for a minus sign.
-Punctuate equations with commas or periods when they are part of a sentence, as in
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-Note that the equation is centered using a center tab stop.
-Be sure that the symbols in your equation have been defined before or immediately following the equation.
-Use Ò(1)Ó, not ÒEq.
-(1)Ó or Òequation (1)Ó, except at the beginning of a sentence: ÒEquation (1) is .
-.
-.Ó
-
-\subsection{Some Common Mistakes}
-\begin{itemize}
-
-\item The word ÒdataÓ is plural, not singular. \cite{Leo}
-\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ÒoÓ.
-\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ÒinsetÓ, not an ÒinsertÓ. The word alternatively is preferred to the word ÒalternatelyÓ (unless you really mean something that alternates).
-\item Do not use the word ÒessentiallyÓ to mean ÒapproximatelyÓ or ÒeffectivelyÓ.
-\item In your paper title, if the words Òthat usesÓ can accurately replace the word ÒusingÓ, capitalize the ÒuÓ; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ÒaffectÓ and ÒeffectÓ, ÒcomplementÓ and ÒcomplimentÓ, ÒdiscreetÓ and ÒdiscreteÓ, ÒprincipalÓ and ÒprincipleÓ.
-\item Do not confuse ÒimplyÓ and ÒinferÓ.
-\item The prefix ÒnonÓ is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ÒetÓ in the Latin abbreviation Òet al.Ó.
-\item The abbreviation Òi.e.Ó means Òthat isÓ, and the abbreviation Òe.g.Ó means Òfor exampleÓ.
-
-\end{itemize}
-
-\section{USING THE TEMPLATE}
-
-Use this sample document as your LaTeX source file to create your document.
-Save this file as {\bf root.tex}.
-You have to make sure to use the cls file that came with this distribution.
-If you use a different style file, you cannot expect to get required margins.
-Note also that when you are creating your out PDF file, the source file is only part of the equation.
-{\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size.
-Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output.
-}
-
-It is impossible to account for all possible situation, one would encounter using \TeX.
-If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.
-
-\subsection{Headings, etc}
-
-Text heads organize the topics on a relational, hierarchical basis.
-For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic.
-If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced.
-Styles named ÒHeading 1Ó, ÒHeading 2Ó, ÒHeading 3Ó, and ÒHeading 4Ó are prescribed.
-
-\subsection{Figures and Tables}
-
-Positioning Figures and Tables: Place figures and tables at the top and bottom of columns.
-Avoid placing them in the middle of columns.
-Large figures and tables may span across both columns.
-Figure captions should be below the figures; table heads should appear above the tables.
-Insert figures and tables after they are cited in the text.
-Use the abbreviation ÒFig.
-1Ó, even at the beginning of a sentence.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{table_example}
-\begin{center}
-\begin{tabular}{|c||c|}
+For the second and third case, a general expression for the computer live time can be obtained by expressing the pulse periodicity $T$ as a fraction
+of the BUSY width, $w$. For a pulse period
+\begin{equation}\label{eq:period}
+T = \frac{1}{n}w, \text{ where n = 1, 2, 3, . . .} 
+\end{equation}
+the computer live time can be shown to be 
+\begin{equation}\label{eq:L.T.}
+ \text{computer L.T. } = \frac{1}{n+1}
+\end{equation}
+For example, if the period is one-half of the BUSY width, then the first pulse that comes initiates the BUSY, the second pulse will arrive half way, and
+the third pulse will be at the end of the BUSY, so only 1/3 (33$\%$ live time) of the pulses will be accepted by the TI as the other two will be rejected since they did
+not arrived outside the window. \\
+\indent In the previous discussions, I have used the example of a pulse generator that produces periodic pulses in time. In reality, during a physics experiment, the physics events
+that are detected follow poisson statistics, which is a random process. This means that pulses arrive random in time, and so it becomes impossible to predict exactly what the computer
+live time will be (See Figure \ref{fig:poisson_pulse}).
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.1in, height=0.9in]{edtm/poisson_pulse.pdf}
+  \caption{Random pulses in time due to physics events follow poisson statistics.}
+  \label{fig:poisson_pulse}
+\end{figure}\\
+In Figure \ref{fig:poisson_pulse}, the first pulse initiates a BUSY signal, the following pulses then arrive at random times which may or may not be within the BUSY width so achieving a live
+time of 100$\%$ becomes highly improbable during an experimental run.
+\subsection{Computer Live Time Measurements}
+\noindent Initial measurements of the computer live time were performed and the results of these measurements uncovered several issues associated with the
+TI module and the DAQ which required the help from experts.
+The first set of measurements were done using a pulse generator at various rates up to 10 kHz.
+The pulses were fed to the electronics modules in both the HMS and SHMS and the BUSY signal widths were measured.
+The results are shown in Table \ref{table:cp_LT}.
+\\
+\begin{table}[ht]
+\caption{Measured Computer Live Times with Pulse Generator}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c c c}
+\hline\hline
+Pulse Rate & HMS & SHMS & BUSY width \\ [0.5ex] % inserts table %heading
 \hline
-One & Two\\
-\hline
-Three & Four\\
+100 Hz & 98.85$\%$ & 99.84 $\%$ &HMS: 2.2 ms \\
+500 Hz & 50.07$\%$ & 98.30 $\%$  &SHMS: 2.2 $\mu$s \\
+1 kHz  & 33.44$\%$ & 99.21 $\%$  \\
+5 kHz  & 8.33$\%$ & 45.2 $\%$ \\
+10 kHz & 4.30$\%$ & 30.49 $\%$ \\ [1ex]
 \hline
 \end{tabular}
-\end{center}
+}
+\label{table:cp_LT}
 \end{table} 
+\indent From Eqs.
+\ref{eq:period} and \ref{eq:L.T.}, and the BUSY widths in Table \ref{table:cp_LT}, the expected computerlive times for certain frequencies can be calculated and the results are shown in
+Tables \ref{table:expected_hmscp_LT} and \ref{table:expected_shmscp_LT}. \\
+\begin{table}[ht]
+\caption{Expected HMS Computer Live Times with Pulse Generator}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c c}
+\hline\hline
+($T=\frac{1}{n}w$) & Pulse Rate ($f = \frac{1}{T}$) & HMS ($\frac{1}{1+n}$) \\ [0.5ex] % inserts table %heading
+\hline
+$>w$             & $<$ 500 Hz & 100 $\%$ \\
+$w$              & 500 Hz & 50  $\%$ \\
+$\frac{1}{2}w$   & 1 kHz & 33.3 $\%$  \\
+$\frac{1}{4}w$   & 2 kHz & 20.0 $\%$  \\
+$\frac{1}{10}w$  & 5 kHz & 9.09 $\%$ \\
+$\frac{1}{20}w$  & 10 kHz & 4.76 $\%$ \\ [1ex]
+\hline
+\end{tabular}
+}
+\label{table:expected_hmscp_LT}
+\end{table} 
+\begin{table}[ht]
+\caption{Expected SHMS Computer Live Times with Pulse Generator}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c c}
+\hline\hline
+($T=\frac{1}{n}w$) & Pulse Rate ($f = \frac{1}{T}$) &  SHMS ($\frac{1}{1+n}$) \\ [0.5ex] % inserts table %heading
+\hline
+$>w$             & $<$ 454 kHz & 100 $\%$ \\
+$w$              & 454 kHz & 50  $\%$ \\
+$\frac{1}{2}w$   & 909 kHz & 33.3 $\%$  \\
+$\frac{1}{4}w$   & 1.81 MHz & 20.0 $\%$  \\ [1ex]
+\hline
+\end{tabular}
+}
+\label{table:expected_shmscp_LT}
+\end{table} 
+\indent A comparison between the expected and measured computer live times in the HMS shows a discrepancy of $<$1$\%$ for rates $>500$Hz.
+In the SHMS, however, since the BUSY signal is 10$^{3}$ orders of magnitude smaller than the HMS, a much high rate of 454 kHz is
+expected before a dropping below 100$\%$ computer live times. Since the maximum rate measured in the SHMS was only 10 kHz, it was
+expected that computer live times should have stayed at 100$\%$, but this was not the case. \\
+\indent In addition to these measurements, to simulate physics events, a poisson pulse generator was also used to observe the
+effects on the computer live times and view the signals on the Oscilloscope for instructional purposes (See Figure \ref{fig:scope_edtm}), but extensive measurements were
+not done since the discrepancy between expected and measured livetimes using a pulse generator was a significant problem that needed to be
+resolved. 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.4in, height=2.6in]{edtm/EDTM_Oscope.pdf}
+  \caption{Random (Poisson) and periodic (EDTM - elecreonic dead time monitoring) pulses initiating a TI BUSY as viewed in an
+    Oscilloscope. The pulses appear as a line because the horizontal scale is set to 100 $\mu$s / division, and the pulses have
+  widths on the order of tens of nanoseconds, so they appear $10^{3}$ smaller.}
+  \label{fig:scope_edtm}
+\end{figure}\\
+Figure \ref{fig:scope_edtm} is a visual representation of how the TI module responds to various input signals. The yellow signals were produced by
+a random pulse generator to replicate physics events, and the blue pulse is periodic. The first pulse (yellow) initiates a BUSY (pink) signal from the
+TI, but no other signals arrived during that time. A second pulse (blue) initiates a second BUSY signals, and during the 220 $\mu$s that the window
+is open, two other random pulses arrived, but are rejected by the TI BUSY, since the other pulse was still being processed.
 
-   \begin{figure}[thpb]
+\subsection{Technical Issues with the DAQ and Trigger Interface Module}
+\noindent The discrepancies found in the computer live times using periodic pulse generator shed light on unknown problems regarding the DAQ and TI
+module that required the intervention of experts. One of the problems had to do with SYNCHRONIZATION issues between the TI and external scaler modules
+which are used to count triggers. When taking experimental data, one must go over a series of steps in order to initiate and end the run. These steps
+involve the communication between the TI and Scaler modules during a START/END of run processes (See Figure \ref{fig:TI_sync}). 
+\begin{figure}[h!]
   \centering
-      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-}}
-      %\includegraphics[scale=1.0]{figurefile}
-      \caption{Inductance of oscillation winding on amorphous
-       magnetic core versus DC bias magnetic field}
-      \label{figurelabel}
+  \includegraphics[width=3.4in, height=1.5in]{edtm/TI_Scaler_SYNC.pdf}
+  \caption{Diagram showing unsynchronized TI and scaler modules.}
+  \label{fig:TI_sync}
+\end{figure}\\
+When a run is started, a signal is sent to the TI module to initiate data processing, but the TI must also communicate with the scalers so that both
+modules start counting simultaneously (in SYNC). The problem was that the TI and Scalers were not synchronized, so when a run was started, the scalers
+would start counting events before the TI which caused a discrepancy in the live time calculations when a pulse generator was used. A second problem
+was that the TI module internal scalers kept counting triggers after the END of run, which lead to an incorrect calculation of the computer live time
+reported by the TI. \\
+\indent These issues have been resolved, and the computer live time tests will continue on the near future to confirm that there are no other problems
+with the live time calculations.
+\section{D(e,e'p)n Experimental Run Plan}
+\noindent My thesis subject, \textit{Deuteron Electro-Disintegration at Very High Missing Momenta} experiment is projected to run from February 26 to
+March 3, 2017. The experiment consists of breaking the deuteron apart into a proton and neutron with an electron beam. The scattered electron and proton
+will be detected by the SHMS and HMS, respectively, and the neutron will be reconstructed from mass-energy conservation laws. There will be a total of
+five kinematics settings to be explored, two of which will be for spectrometer check and calibration purposes, and the other three settings will be the main
+experimental settings that will explore the deuteron cross-section in unexplored regions of missing momentum with reduced final state interactions between
+the proton and neutron. \\
+\subsection{Spectrometer Settings: H(e,e'p) Scattering}
+\noindent The first spectrometer setting will be to check that the spectrometers are pointing in the correct orientation in terms of angle and central
+momentum. This is done via the elastic scattering of electrons off a 10 cm liquid Hydrogen target. In elastic scattering, e+p$\rightarrow$ e'+p, the
+proton remains unchanged and re-scatters at a certain angle and momentum. By conservation laws, the final electron energy, $E'$, is determined to be
+\begin{equation}\label{eq:h_elastic}
+E'(\theta_{e}) = \frac{E_{e}}{1 + \frac{2E_{e}}{M_{p}}\sin^{2}\frac{\theta_{e}}{2}}
+\end{equation}
+where $E_{e}$ is the initial electron energy, $M_{p}$ is the proton mass and $\theta_{e}$ is the electron scattering angle. From Eq. \ref{eq:h_elastic},
+once the electron angle, $\theta_{e}$ is determined, the electron scattering energy as well as the proton scattering angle and momentum, $\theta_{p}$ and $P_{p}$
+are also fixed. The D(e,e'p)n kinematics at high missing momentum require the electron angle to be fixed at $\theta_{e}$= 12.189$^{o}$, as it is the most
+sensitive kinematic variable to the cross sections we want to measure. This way, one does not run the risk of changing the SHMS spectrometer angle during the
+experimental run. The kinematics are summarized in Table \ref{Table:h_elastic_kin}.
+\begin{table}[ht]
+\caption{Hydrogen Elastic Kinematics}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c c}
+\hline\hline
+\textbf{Spectrometer Settings} & \textbf{HMS} & \textbf{SHMS} \\ [0.5ex] % inserts table %heading
+\hline
+particles                  & protons & electrons \\
+Central Angle (deg)        & 37.339 & 12.169  \\
+Central Momentum (GeV/c)   & 2.938 & 8.700  \\ [1ex]
+\hline
+\end{tabular}
+}
+\label{Table:h_elastic_kin}
+\end{table} \\
+\subsection{Spectrometer Settings: D(e,e'p)n Kinematics}
+The spectrometers will be set to measure D(e,e'p)n kinematics at low missing momentum setting first,
+since there exist similar data from which we can compare results and apply any
+corrections needed before exploring the high missing momentum region. Three high missing momentum values will then be explored,
+each corresponding to a different HMS spectrometer setting. During the entire D(e,e'p)n runs, the SHMS spectrometer must stay at a
+fixed angle and central momentumn. The SHMS settings for detecting electrons are:
+\begin{table}[ht]
+\caption{SHMS Central Kinematic Settings}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c}
+\hline\hline
+\textbf{Spectrometer Settings} & \textbf{SHMS} \\ [0.5ex] % inserts table %heading
+\hline
+particles detected                  & electrons \\
+Central Angle (deg)        & 12.169  \\
+Central Momentum (GeV/c)   & 8.700  \\ [1ex]
+\hline
+\end{tabular}
+}
+\label{Table:shms_d2_kin}
+\end{table} \\
+The HMS settings for detecting protons at low and high missing momentum of neutron are:
+\begin{table}[ht]
+\caption{HMS Central Kinematic Settings}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=2pt
+\begin{tabular}{c c c c c}
+\hline\hline
+\textbf{Spectrometer Settings} & \textbf{HMS} \\ [0.5ex] % inserts table %heading
+\hline
+particles  detected                &           &    protons &  \\
+\hline
+$P_{miss}$ (GeV/c)           & 0.08     &  0.500  & 0.650 & 0.800\\
+$\theta_{HMS}$ (deg)       & 40.061   & 53.252    & 56.401 & 59.388  \\    
+$P_{HMS}$ (GeV/c)            & 2.435    & 2.305    & 2.220 & 2.120  \\
+\hline
+\end{tabular}
+}
+\label{Table:hms_d2_kin}
+\end{table} \\
+\subsection{Reaction Kinematics}
+\indent The true electron reaction kinematics differ from the spectrometer settings described in Tables
+\ref{Table:h_elastic_kin} and \ref{Table:shms_d2_kin}. The kinematics for the scattered electron are
+\begin{table}[ht]
+\caption{Electron Kinematic Settings}
+\centering
+{\def\arraystretch{1.6}\tabcolsep=5pt
+\begin{tabular}{c c c}
+\hline\hline
+& \textbf{H(e,e'p)} & \textbf{D(e,e'p)n} \\ [0.5ex] % inserts table %heading
+\hline
+$\theta_{e}$ (deg)    & 12.169 & 12.169 \\           
+$P^{'}_{e}$  (GeV/c)   & 8.454 & 8.922 \\
+\hline
+\end{tabular}
+}
+\label{Table:elec_kin}
+\end{table} \\
+In going from Hydrogen to Deuteron kinematics in the experimental run plan, the electron
+momentum actually increases as shown in table \ref{Table:elec_kin}. We could have chosen the
+SHMS central momentum settings to match the reaction kinematics, however, changing the central
+momentum settings from low to high momentum in the quadrupole magnets leads to a phenomenon
+known as \textit{magnetic hysteresis}, which refers to the irreversibility of the magnetization process while ramping upthe current in the magnets. Due to this phenomenon, the central momentum
+settings will have to be increased to above the established value due to a lagging of the
+magnetization of a ferromagnetic material, such as iron in the quadrupoles \cite{hysteresis}. 
+\subsection{ Monte Carlo Simulations on the Momentum Acceptance }
+\noindent Since the central settings of the SHMS differ from the reaction kinematics, the detected particles are
+offset from the center of the spectrometer momentum acceptance. A Monte Carlo simulation had to be done to verify
+that the particles detected are within the spectrometer acceptance.
+For this purpose, events were randomly \textit{generated} over some large volume in which the spectrometer boundaries are defined.
+The \text{accepted} events landed within the
+spectrometer boundaries (or phase space), each event with an equal probability or weight. The results are shown in Figure \ref{fig:h_elastics}. 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.3in, height=4.1in]{deut_kin/h_elast.pdf}
+  \caption{Hydrogen Elastics simulation at difference central momenta.}
+  \label{fig:h_elastics}
+\end{figure} \\
+The momentum acceptance is defined as
+\begin{equation}
+\delta = \frac{P - P_{0}}{P_{0}}
+\end{equation}
+where $P_{0}$ is the central momentum and $P$ is an arbitrary momentum within the acceptance. \\
+\indent The Hydrogen elastics simulation results show that there is $\sim$3$\%$ shift in the SHMS momentum acceptance
+if the central momentum were to be increased to 8.7 GeV/c. This means that the scattered electrons will now
+be detected $3\%$ away from the center of the acceptance, which is not a significant offset given that the
+full SHMS acceptance ranges from -10$\%$ to 25$\%$.
+\indent A simulation was also done for the D(e,e'p)n reaction, where the central momentum of the SHMS was
+also varied. The results are shown only for missing momentum $P_{miss}$ = 800 MeV/c.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=3.5in, height=1.9in]{deut_kin/d2_acceptance.pdf}
+  \caption{D(e,e'p)n simulation at missing momentum of 800 MeV/c, for two different SHMS central momentum settings.}
+  \label{fig:deut_pmiss800}
 \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels.
-Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader.
-As an example, write the quantity ÒMagnetizationÓ, or ÒMagnetization, MÓ, not just ÒMÓ.
-If including units in the label, present them within parentheses.
-Do not label axes only with units.
-In the example, write ÒMagnetization (A/m)Ó or ÒMagnetization {A[m(1)]}Ó, not just ÒA/mÓ.
-Do not label axes with a ratio of quantities and units.
-For example, write ÒTemperature (K)Ó, not ÒTemperature/K.Ó
-
-\section{CONCLUSIONS}
-
-A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+\indent From Figure \ref{fig:deut_pmiss800}, the majority of the electron-proton coincidence events represented by the yellow band
+shifted by $\sim$ 2$\%$ towards the center of the SHMS acceptance when the central momentum was decreased to 8.7 GeV/c. Similar shifts
+also occurred for the other momentum settings. \\
+\indent The results from the simulations done on H(e,e'p) and D(e,e'p)n reactions demonstrate that by setting a common central momentum setting
+of 8.7 GeV/c for the SHMS, the coincidence events are shifted by only $\sim$2$\%$ in the SHMS momentum acceptance.
+\indent From the simulation results it has been determined that the SHMS should be set to a common central angle and momentum settings during the
+entire experimental run, as the SHMS angle is the most sensitive to the D(e,e'p)n cross-section, changes in the central momentum setting would
+lead to hysteresis in the magnets\cite{priv_comm}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{APPENDIX}
+\section*{ACKNOWLEDGMENT}
+I would like to thank Drs. Werner Boeglin and Mark Jones for their constant support and guidance in writing this
+paper. I would also like to give many thanks to Dr. Kavallieratos and the Nuclear Regulatory Commission Fellowship for supporting me throughout the Spring, Summer and Fall Terms of 2017.
 
-Appendixes should appear before the acknowledgment.
+%\section*{APPENDIX}
 
-\section*{ACKNOWLEDGMENT}
-
-The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
-.
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
+%Appendixes should appear before the acknowledgment.
 
@@
 
-References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
+%References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
 

### 2017-10-29 HallC_12GeV_Trigger/trigger.tex
Added directory containing Hall C Trigger SetUp

\documentclass[11pt]{article}

\usepackage{url}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{graphicx}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{empheq}
\usepackage{amssymb}
\usepackage{tgtermes}
\usepackage{gensymb}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{epstopdf}
\usepackage[singlelinecheck=false]{caption}
\usepackage{datetime}
\usepackage[hyperfootnotes=false, pdfnewwindow, colorlinks=true]{hyperref}

\AtBeginDocument{% optionally set colors to your liking
  \hypersetup{
    urlcolor=red,
    citecolor=green,
    linkcolor=blue,
  }%
}

\begin{document}

%GLOBAL VARIABLE DEFINITIONS
\newcommand{\hhodthrs}{-44.5 mV }       %define HMS Hodo threholds in case they change later on, only change this line!!!
\newcommand{\hhodgate}{60 ns }
\newcommand{\hPrShLo}{-40 mV }
\newcommand{\hPrShHi}{-60 mV }
\newcommand{\hSHLo}{-45 mV }
\newcommand{\hPrShLogate}{30 ns }
\newcommand{\hPrShHigate}{30 ns }
\newcommand{\hSHLogate}{30 ns }
\newcommand{\hcerthrs}{-50 mV }
\newcommand{\hcergate}{30 ns }

\newcommand{\shodthrs}{-30 mV }
\newcommand{\quartzthrs}{-60 mV }
\newcommand{\shodgate}{60 ns } 
\newcommand{\sngcthrs}{-50 mV}
\newcommand{\sngcgate}{30 ns}
\newcommand{\shgcthrs}{-50 mV}
\newcommand{\shgcgate}{30 ns}
\newcommand{\saerthrs}{-50 mV}
\newcommand{\saergate}{30 ns}

\title{\Large \bf{Hall C 12 GeV Trigger Set-Up}}

\author{Carlos Yero}

\date{\today}
\maketitle

%*****************************************************************************************************************************************************
\section{Detector Electronics Racks and Patch Panel Diagrams}
The majority of the detector electronics in the HMS/SHMS detector huts are read out in the Counting Room except for the HMS/SHMS Drift
Chambers and the SHMS Shower Counter signals which are read in their respective detector huts. In HMS/SHMS huts, the Drift
Chamber signals are output by 20-25 feet long ribbon cables which are read in the hut electronics rack (See Figure \ref{fig:hms_hut_rack}). On the SHMS
side, the Shower Counter consists of 224 signal cables which would take up most of the space available for other detectors
in the Counting Room, so they are read directly in the hut electronics rack.

\subsection{HMS Detector Hut}
The HMS Drift Chambers are read out through a VXS Crate (ROC3) in the detector hut electronics rack. The signals are carried through 16-channel ribbon cables
which are fed in various CAEN1190 TDC modules. The \textbf{TI} (or Trigger Interface) module at the front end of the crate distributes the readout
trigger throughout all modules in the crate and initiates data readout.
\begin{figure}[h!]
  \centering
  \includegraphics[width=5.0in, height=4.0in]{HMS_stack.pdf}
  \caption{HMS detector stack.}
  \label{fig:hms_stack}
\end{figure}
\begin{figure}[h]
  \centering
  \includegraphics[width=5.0in, height=4.0in]{HMS_Hut_Rack.pdf}
  \caption{HMS detector hut electronic rack and patch panels.}
  \label{fig:hms_hut_rack}
\end{figure}
The rest of the HMS detector signals(Gas \c{C}erenkov, Hodoscope, Calorimeter) are sent to the Hall C Floor Patch Panel via the hut Patch, with the exception
of the Aerogel, which is sent directly from the detector to the Floor Patch.

\newpage
All the signals are then sent to the Counting Room Patch Panel to be processed
by the electronics. (See Figure \ref{fig:hms_patch})

\begin{figure}[h]
  \centering
  \includegraphics[width=6.0in, height=2.0in]{HMS_patch.pdf}
  \caption{HMS Patch Diagram from detectors to Counting Room.}
  \label{fig:hms_patch}
\end{figure}

\subsection{SHMS Detector Hut}
Similarly to the HMS Drift Chambers, the SHMS Drift Chambers are also read out by TDCs in a VXS Crate in the SHMS electronics hut (See Figure \ref{fig:shms_hut_rack2}).
The Shower Counter 224 signals are fed directly into the Flash ADC (fADC-250) modules in a VXS Crate (ROC4). The Pre-Shower signals (x14/side) pass
through a 50:50 splitter and a part is fed into fADCs. The other part is partially summed in the hut and sent via the hut patch panel to the
Counting Room Patch (See Figure \ref{fig:shms_hut_rack1}). 
\begin{figure}[h!]
  \centering
  \includegraphics[width=6.0in, height=4.0in]{SHMS_stack.pdf}
  \caption{SHMS detector stack.}
  \label{fig:shms_stack}
\end{figure}
\begin{figure}[h!]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=3.0in, height=4.0in]{SHMS_Hut_Rack01.pdf}
  \captionof{figure}{SHMS Hut Patch Panel (left) and Electronics Rack (right).}
  \label{fig:shms_hut_rack1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=2.0in, height=4.0in]{SHMS_Hut_Rack02.pdf}
  \caption{SHMS Drift Chamber Electronics Rack.}
  \label{fig:shms_hut_rack2}
\end{minipage}
\end{figure}
\newpage
The rest of the SHMS detector signals (HGC/NGC, Hodoscope, Aerogel) are sent to the Counting Room via the hut patch panel (See Figure \ref{fig:shms_patch}). 
\begin{figure}[h!]
  \centering
  \includegraphics[width=6.0in, height=2.0in]{SHMS_patch.pdf}
  \caption{SHMS Patch Diagram from detectors to Counting Room.}
  \label{fig:shms_patch}
\end{figure}

\newpage
\subsection{Hall C Counting Room}
Once the detector signals arrive at the Counting Room Patch (See Figure \ref{fig:cr_patch}), they are processed by the NIM/CAMAC electronics (See Figure \ref{fig:cr_racks}) to form the single arm and coincidence triggers
for each spectrometer. The signals are also sent to ADCs/TDCs to determine energy and timing information for individual detectors as well as trigger TDC information.

\begin{figure}[h!]
  \centering
  \includegraphics[width=3.0in, height=4.0in]{CR_Patch.pdf}
  \caption{Counting Room Patch Panels.}
  \label{fig:cr_patch}
\end{figure}

\newpage

\begin{figure}[h!]
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=2.0in, height=4.0in]{CR_rack4.pdf}
\end{subfigure}%
\begin{subfigure}{.2\textwidth}
  \centering
  \includegraphics[width=2.0in, height=4.0in]{CR_rack5.pdf}
\end{subfigure}
\caption{Counting Room main Electronic Racks for HMS/SHMS detectors.}
\label{fig:cr_racks}
\end{figure}

\section{HMS Trigger Set-Up} 
\indent The XY scintillator arrays (hodoscope planes) will form part of the standard HMS trigger configuration.  
Additional particle detectors may also be incorporated into the HMS trigger as required by different experiments. The Gas \v{C}erenkov and Calorimeter triggers will be
used for e/$\pi$ separation, whereas the Aerogel \v{C}erenkov trigger will be used for $\pi$/K/p separation.

\subsection{Hodoscope Pre-Trigger}

\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=3.2in]{HMS_HODO_TRIGGER.pdf}
  \caption{HMS Hodoscope Electronics Diagram.}
  \label{fig:hms_hod_trg}
\end{figure}

\indent Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:hms_stack}), so each bar reads out two signals. As shown in Figure \ref{fig:hms_hod_trg},
for example, hodoscope plane h1X consists of 32 signals (16 bars) read out in the Counting House (CH) patch. Each side of the plane (x16 signals/side) is fed into a 64-channel input passive splitter (16 Ch./set).
One-third (33\%) of the signal amplitude is sent via a 16-channel ribbon cable to a 64 Ch. input Ribbon-to-BNC converter (16 Ch./set) which outputs are fed into a 16-channel NIM input flash ADC (fADC). The remaining two-thirds (66\%)
of the signal amplitude is sent to a 16-Ch. input CAMAC Discriminator unit. The HMS discriminators thresholds and gate widths were set to \hhodthrs and \hhodgate, respectively.\\
\indent The discriminated signals are sent via two ribbon-cable outputs to CAEN1190 TDCs/Scalers (daisy-chained) and to a LeCroy 4564 CAMAC Logic unit to form the plane pre-triggers.
The Logic Unit takes four sets of 16-Ch. input ribbon cable and forms a 16-fold OR for each set by default. Further boolean operations are done through the module backplane by connecting a twisted pair cable to the pin corresponding to the
desired boolean operation. For hodoscope plane pre-triggers, the boolean operations are as follows:
\begin{empheq}[box=\fbox]{align*}
& \text{h1X = h1X+ (16-fold OR) \textit{AND} h1X- (16-fold OR)} \\ 
& \text{h1Y = h1Y+ (10-fold OR) \textit{AND} h1Y- (10-fold OR)} \\
& \text{h2X = h2X+ (16-fold OR) \textit{AND} h2X- (16-fold OR)} \\ 
& \text{h2Y = h2Y+ (10-fold OR) \textit{AND} h2Y- (10-fold OR)} 
\end{empheq}

\indent Once a pre-trigger has been made for each plane, they are sent to a NIM/ECL converter (Level Translator - Phillips Scientific (or P/S) Model 7126) via twisted pair cables to convert the ECL signal (twisted pair)
to a NIM signal. The NIM output is then sent to individual sets of a P/S Model 752 NIM Logic unit to adjust the widths of each of the plane pre-triggers as necessary before making a coincidence. An X-Y hodoscope plane
coincidence (h1 = h1X \textit{AND} h1Y, h2 = h2X \textit{AND} h2Y) is then made by feeding each hodoscope X-Y plane pair into a P/S Model 755 Nim Logic unit. A copy of each of the four individual plane pre-triggers is also sent to another set of P/S Model 755 to make a 3/4 or
4/4 plane coincidence (via a front-panel knob) which defines the production hodoscope pre-trigger. A copy of all the pre-triggers discussed above are sent to TDCs/Scalers via a NIM/ECL converter for timing and counting rate information. (See Figure \ref{fig:hms_hod_trg}) \\

\subsection{Calorimeter Pre-Trigger}
The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
read out 13 signals/layer on one side. The first two layers form the Pre-Shower Counter while all four layers (A, B, C and D) form the Shower Counter.  
Each layer is read out in the Counting Room patch and fed into 50:50 splitters. One output of the splitter is fed to fADCs via a Ribbon-to-BNC converter (same as hodoscopes)
while the other output is sent to a P/S Model 740 NIM Linear FI/FO summing modules. Each side of a layer is summed first (hA+, hA-, hB+, hB-, hC and hD sums). The sums are fed into
a LeCroy Model 428F summing module where layers hA+/- and hB+/- are summed to form hA and hB sums. A copy of each layer sum is sent to fADCs. The Pre-Shower SUM is then made from the sum of layers A and B, while the Shower SUM is made by summing all four layers. A copy of the PreShower and Shower sums is also sent to fADCs. The Pre-Shower and Shower sums are then sent to a P/S Model 715
NIM Discriminator unit to form the PreShower Low/High (LO/HI) and Shower Low pre-triggers with thresholds \hPrShLo, \hPrShHi and \hSHLo, respectively with all gate widths set to 30 ns. A copy of the pre-triggers is sent to TDCs/Scaler modules for trigger timing and counting rate
information.
\newpage
\begin{figure}[h!]
  \centering
  \includegraphics[width=6.5in, height=4.5in]{HMS_Cal_Trigger.pdf}
  \caption{HMS Calorimeter Electronics Diagram.}
  \label{fig:hms_cal_trg}
\end{figure}

\subsection{Gas \v{C}erenkov Pre-Trigger} \label{hms_cer_section}

\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=2.0in]{HMS_Cer_trig.pdf}
  \caption{HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
  \label{fig:hms_gas_cer_trg}
\end{figure}

\indent The HMS Gas \v{C}erenkov detector consists of a 1.5 m long cylindrical tank between the first and second set of hodoscope planes (See Figure \ref{fig:hms_stack}).
The tank is filled with a gas and has two spherical mirrors that focus the \v{C}erenkov photons towards two 5-inch PMTs\cite{hms_cer_article}. The
signals are read out in the Counting Room patch and pass through a 50:50 splitter. One output is fed into
an fADC module via a Ribbon-to-BNC converter. The other output is sent to a LeCroy Model 428F summing module, and a copy of the sum is fed to an fADC. The sum is
also sent to a P/S Model 715 NIM discriminator to form the \v{C}erenkov pre-trigger with a threshold and gate width set to \hcerthrs and \hcergate. A copy of the discriminated signal is also sent to TDCs/Scalers via a NIM/ECL converter for trigger and counting rate information.

\subsection{Aerogel \v{C}erenkov Pre-Trigger}

\begin{figure}[h!]
  \centering
  \includegraphics[width=6.5in, height=2.1in]{HMS_Aero_trig.pdf}
  \caption{Aerogel \v{C}erenkovs Electronics Diagram. Same electronics diagram applies for SHMS Aerogel.}
  \label{fig:hms_aero_trg}
\end{figure}

\indent The HMS Aerogel \v{C}erenkov detector consists of a 120cm x 70cm rectangular aerogel tray coupled to a diffusion box\cite{hms_aero_article} and is located
between the second Drift Chamber and first set of hodoscope planes. The diffusion box has 8 PMTs on each side
which detect \v{C}erenkov light produced by interactions with the Aerogel material. The signals are sent directly to the Hall C Floor Patch Panel, and then
read out in the Counting Room patch and pass through a 50:50 splitter. One output is fed into an fADC module via a Ribbon-to-BNC converter. The other output is
sent to a summing module, and a copy of the sum is fed to an fADC. The sum is also sent to a NIM discriminator to form the Aerogel pre-trigger.
A copy of the discriminated signal is also sent to TDCs/Scalers via a NIM/ECL converter for trigger and counting rate information.

\subsection{HMS Single Arm Trigger}\label{ssec:hms_single_arm_sec}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=3.8in]{HMS_SingleArm_Trigger.pdf}
  \caption{HMS Single Arm Trigger Electronics Diagram}
  \label{fig:hms_one_arm_trg}
\end{figure}

\indent The HMS single arm pre-trigger will be formed from the standard pre-trigger (hodoscopes) and a combination of other detector pre-triggers as required by the
experiment. The standard and other \textit{experiment-specific} pre-triggers are sent to a P/S  Model 755 NIM Logic unit to form a single-arm coincidence.
Once the HMS pre-trigger is formed, a copy is sent to Scalers/TDCs. The other copy is sent to a NIM/ECL converter, where three copies of the HMS pre-trigger are sent
via ECL twisted pairs to two CAEN 1190 TDC modules and an input on the TI\footnote{In single-arm mode, the TI in ROC 01 is known as \textit{TM or Trigger Master}, and its main operation is to distribute a copy
of the accepted triggers to all ROCs related to the HMS via fiber optic lines. The same applies to the SHMS when operated in single-arm mode.} known as the \textit{Trigger Supervisor or TS} (up to six trigger inputs). The copies sent to
the TDCs are fed externally through the 16th pin of a 16-channel input ribbon cable adaptor\footnote{Each TDC module in the readout crate (ROC 01) must receive a copy of the HMS pre-trigger known as
the \textit{reference time} via twisted pairs. The reference time in each TDC module functions as a common stop for all detector signals being fed to the TDC.} The pre-trigger
copy sent to the Trigger Supervisor is processed, accepted and disseminated throgh the crate backplane to all modules (except TDCs) in the crate. The TDCs are NOT configured to not receive a copy
of the accepted triggers, therefore, a copy must be sent from the ``TRG'' ECL output in TI front panel to the TDC ``TRG'' NIM input\footnote{A copy of the accepted triggers is needed by ADCs/TDCs in order to initiate
readout in all channels of the respective modules.} via a NIM/ECL converter. The inputs are daisy-chained
with other TDCs present in the crate. A copy of the accepted triggers is also sent to Scalers/TDCs.

\section{SHMS Trigger Set-Up}
\indent The three planes (X1, Y1, X2) of scintillator arrays and the Quartz plane (Y2) will form part of the standard SHMS trigger configuration (See Figure \ref{fig:shms_stack}).  
Additional particle detectors may also be incorporated into the SHMS trigger as required by different experiments. The Noble Gas \v{C}erenkov \footnote{Noble Gas \v{C}er: e/$\pi$ separation $\geq$ 6 GeV/c} and
Calorimeter triggers will be used for e/$\pi$ separation, whereas the Heavy Gas\footnote{Heavy Gas \v{C}er: $\pi$/K separation above 3.4 GeV/c} and Aerogel \v{C}erenkov trigger will be used for $\pi$/K/p
separation\cite{SHMS_PID}.

\subsection{Hodoscope Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=4.3in]{SHMS_HODO_TRIGGER.pdf}
  \caption{SHMS Hodoscope Electronics Diagram.}
  \label{fig:shms_hod_trg}
\end{figure}

Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:shms_stack}), so each bar reads out two signals. As shown in Figure \ref{fig:shms_hod_trg},
for example, hodoscope plane S1X consists of 26 signals (16 bars) read out in the Counting House (CH) patch. Each side of the plane (x13 signals/side) is fed into a 64-channel input passive splitter (16 Ch./set).
One-third (33\%) of the signal amplitude is sent via a 16-channel ribbon cable to a 64 Ch. input Ribbon-to-BNC converter (16 Ch./set) which outputs are fed into a 16-channel NIM input flash ADC (fADC).
The remaining two-thirds (66\%) of the signal amplitude is sent to a 16-Ch. input CAMAC Discriminator unit. The SHMS discriminators thresholds and gate widths were set to \shodthrs and \shodgate, respectively,
whereas the Quartz Discriminators thresholds and gate widths were set to \quartzthrs and \shodgate, respectively\\
\indent The discriminated signals are sent via two ribbon-cable outputs to CAEN1190 TDCs/Scalers (daisy-chained) and to a LeCroy 4564 CAMAC Logic unit to form the plane pre-triggers.
The Logic Unit takes four sets of 16-Ch. input ribbon cable and forms a 16-fold OR for each set by default. Further boolean operations are done through the module backplane by connecting a twisted pair cable to
the pin corresponding to the desired boolean operation. For hodoscope plane pre-triggers, the boolean operations are as follows:
\begin{empheq}[box=\fbox]{align*}
& \text{S1X = S1XL (13-fold OR) \textit{AND} S1XR (13-fold OR)} \\ 
& \text{S1Y = S1YT (14-fold OR) \textit{AND} S1YB (14-fold OR)} \\
& \text{S2X = S2XL (13-fold OR) \textit{AND} S2XR (13-fold OR)} \\ 
  & \text{S2Y = \big\{S2Y[1-16]T OR S2Y[17-21]T\big\} \textit{AND} \big\{S2Y[1-16]B OR S2Y[17-21]B\big\}}
\end{empheq}

\indent Once a pre-trigger has been made for each plane, they are sent to a NIM/ECL converter (Level Translator - Phillips Scientific (or P/S) Model 7126) via twisted pair cables to convert the ECL signal
(twisted pair) to a NIM signal. The NIM output is then sent to individual sets of a P/S Model 752 NIM Logic unit to adjust the widths of each of the plane pre-triggers as necessary before making a coincidence.
An X-Y hodoscope plane coincidence (S1 = S1X \textit{AND} S1Y, S2 = S2X \textit{AND} S2Y) is then made by feeding each hodoscope X-Y plane pair into a P/S Model 755 Nim Logic unit. A copy of each of the four
individual plane pre-triggers is also sent to another set of P/S Model 755 to make a 3/4 or 4/4 plane coincidence (via a front-panel knob) which defines the production hodoscope pre-trigger. A copy of all the
pre-triggers discussed above are sent to TDCs/Scalers via a NIM/ECL converter for timing and counting rate information. (See Figure \ref{fig:shms_hod_trg}) \\

\subsection{Pre-Shower Calorimeter Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=3.0in]{SHMS_preSh_trigger.pdf}
  \caption{SHMS PreShower Electronics Diagram}
  \label{fig:shms_preSh_trg}
\end{figure}
\newpage
The SHMS Pre-Shower consists of two sets of fourteen (PMT-coupled) lead blocks oriented perpendicular to the Shower Counter blocks\cite{shms_preSh_talk}. The initial sum was done in the SHMS Electronics Hut. PMT signals
from groups of four blocks were summed to form:
\begin{empheq}[box=\fbox]{align*}
& \text{preSh SUM [1-4]: [1-4]L + [1-4]R} \\ 
& \text{preSh SUM [5-8]: [5-8]L + [5-8]R} \\ 
& \text{preSh SUM [9-12]: [9-12]L + [9-12]R} \\ 
& \text{preSh SUM [13-14]: [13-14]L + [13-14]R} 
\end{empheq}
\subsection{Heavy/Noble Gas \v{C}erenkov Pre-Trigger}
\indent The SHMS Heavy Gas \v{C}erenkov detector consists of a 1 m long, 1.6 m in diameter cylindrical tank located between the first set of hodoscope planes and the Aerogel (See Figure \ref{fig:shms_stack}).
The tank is filled with a gas and has four thin spherical mirrors that focus the \v{C}erenkov photons towards four 5-inch PMTs\cite{shms_hgc_talk}. For a description of the electronics diagram, See Section \ref{hms_cer_section} on the HMS Gas \v{C}erenkov.
\newline
\indent The SHMS Noble Gas \v{C}erenkov detector consists of a 2 m long active length of Argon/Neon gas tank located before the first drift chamber (See Figure \ref{fig:shms_stack}).
The tank is filled with a gas and has four overlapping mirrors, that focus the \v{C}erenkov photons towards four 5-inch PMTs\cite{shms_ngc_talk}. For a description of the electronics diagram, See Section \ref{hms_cer_section} on the HMS Gas \v{C}erenkov.
\subsection{Aerogel \v{C}erenkov Pre-Trigger}
\indent The SHMS Aerogel \v{C}erenkov detector consists of a 110 x 100 x 24.5 cm$^{3}$ rectangular aerogel tray coupled to a diffusion box. The diffusion box has seven 5-inch PMTs on each side
which detect \v{C}erenkov light produced by interactions with the Aerogel material\cite{shms_aero_article}. The detector is located between Heavy Gas \v{C}erenkov and second set of hodoscope planes
(See Figure \ref{fig:shms_stack}). For a description of the electronics diagram, see Figure \ref{fig:hms_aero_trg}.
\subsection{SHMS Single Arm Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=3.8in]{SHMS_SingleArm_Trigger.pdf}
  \caption{SHMS Single Arm Trigger Electronics Diagram}
  \label{fig:shms_one_arm_trg}
\end{figure}

\indent The SHMS single arm trigger is be formed exactly as the HMS single arm trigger, with the exception of the detectors involved. Compare the electronics diagrams in Figures \ref{fig:shms_one_arm_trg} and
\ref{fig:hms_one_arm_trg}, and read Section \ref{ssec:hms_single_arm_sec} for a detailed description of the electronic diagrams.

\section{Coincidence Trigger Set-Up}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=3.8in]{Coincidence_Trigger.pdf}
  \caption{Coincidence Trigger Electronics Diagram}
  \label{fig:coin_trg}
\end{figure}
\indent In coincidence mode, the HMS and SHMS pre-triggers are sent to a NIM Logic module, where the first pre-trigger that arrives will open
a coincidence time window during which the second pre-trigger may or may not arrive in time. This will determine whether two events that occurred in
each spectrometer are correlated with the event that originated at the target. If the coincidence pre-trigger is formed, a copy will be sent to
scalers and TDCs, while the other copy is sent to a NIM/ECL converter where three copies (may be more) are sent via twisted pairs to every TDC module and the TI, which will be the \textbf{ONLY} Trigger Master in coincidence mode. Additional copies (not shown) may need to be sent to the HMS readout crate (ROC 01) as well, since the coincidence pre-trigger\footnote{A copy of the coincidence pre-trigger will also need to be sent to the
  HMS/SHMS TDC modules present in the detector huts crates via the patch panel.} is common to all crates. \\
\indent Once the coincidence pre-trigger is processed by the TI Master in ROC 02, it is sent to a NIM/ECL converter, where a copy is sent to scalers and TDCs, and the other copy is sent to the ``TRG'' NIM input in the TDC front panel, and daisy-chained with other TDCs in ROC02 and ROC01. The remaining crates in the HMS/SHMS huts receive a copy of the accepted trigger via fiber optics lines running from the TI Master to the TIs in all other crates. The TIs then distribute the accepted trigger to all modules of their respective crates. 
\newpage
\onecolumn
\bibliography{trigger}
\bibliographystyle{acm}

\end{document}

### 2018-06-04 NRF_Final_Report/report.tex
add coin time module and NRF Final report docs

@@
 96 sense wires each and are oriented 60$^{o}$ relative to the +y-coordinate. The X and X' planes consist of 102 sense wires and are oriented perpendicular to the x-axis (See
-Figures \ref{fig:dc1_planes} and \ref{fig:dc_wires}).
+Figures \ref{fig:dc1_planes} and \ref{fig:dc_wires}).\\
 \begin{figure}[h!]
@@
   \label{fig:dc_wires}
-\end{figure}
-The cathode planes and field wires are held at a negative high voltage and the sense wires are grounded which establihses a potential gradient causing an electric field
+\end{figure}\\
+\indent The cathode planes and field wires are held at a negative high voltage and the sense wires are grounded which establishes a potential gradient causing an electric field
 between high voltage and grounded wires. Each chamber is filled with a gas mixture\footnote{Argon is mixed with CO$_{2}$ or Ethane, where Argon is the ionizing agent the
@@
 \end{figure} \\
-Figure \ref{fig:current_draw} shows a decrease is the current drawn by the HMS chambers by three orders of magnitude smaller, from a few $\mu$A to a few nA of current drawn. This
+Figure \ref{fig:current_draw} shows a decrease in the current drawn by the HMS chambers by three orders of magnitude smaller, from a few $\mu$A to a few nA of current drawn. This
 indicates that Ethane is a better quenching gas, as it kept the secondary electron ionization small for a broader range of High Voltages, up to $\sim$2100 Volts. There is still the
@@
 \end{figure} \\
-From the threshold scan results in Figure \ref{fig:hdc2_thrsscan}, there is a 3$\%$ decrease in the plane efficiencies over a
+\indent From the threshold scan results in Figure \ref{fig:hdc2_thrsscan}, there is a 3$\%$ decrease in the plane efficiencies over a
 6 Volt range. The operational threshold voltage was determined to be 4.5 Volts, where the efficiencies are better than 99$\%$, over a $\sim$ 1 Volt range.
@@
 \noindent My thesis subject, \textit{Deuteron Electro-Disintegration at Very High Missing Momenta} experiment is projected to run from February 26 to
-March 3, 2017. The experiment consists of breaking the deuteron apart into a proton and neutron with an electron beam. The scattered electron and proton
+March 3, 2018. The experiment consists of breaking the deuteron apart into a proton and neutron with an electron beam. The scattered electron and proton
 will be detected by the SHMS and HMS, respectively, and the neutron will be reconstructed from mass-energy conservation laws. There will be a total of

### 2018-08-29 Spring_2018_Run/OutOfSync_TDC/tdc_sync_report.tex
updated repo

\documentclass[11pt]{article}

\usepackage{url}
\usepackage[hyperfootnotes=false]{hyperref}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{graphicx}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tgtermes}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

\usepackage{epstopdf}

\title{On the Out-of-Sync TDC Module on the HMS Chambers}
\author{Carlos Yero}
\date{August 28 2018}

\begin{document}

\maketitle

%*****************************************************************************************************************************************************
During the Fall-2017/Spring-2018 Hall C Commissioning Run Period, it was found that a particular TDC module in the HMS
Drift Chambers Crate (ROC03) was shifting the tdc times of the corresponding groups of wires being fed into it. At that time,
this did not seem to be a serious concern, as this could be fixed in software. There also seem to be no issues with the
residuals per wire after calibration. After the end of the Spring Run, I decided to look at the residuals per wire for a defocused
run in the HMS, and found certaing groups of wire residuals to be significantly smeared compared to adjacent groups of wires.
These were the same group of wires that exhibited the shift in time, which pointed to the same TDC module in ROC03, Slot 2.
In this document I discuss the following: \\
\\
1) the observations made that led to the determination of an out-of-sync TDC module \\
2) what was done to fix this problem in future experiments \\
3) how to minimize the impact on wire residuals for the Spring 2018 Run

\section{Observed Correlations on the Out-of-Sync TDC Module}  
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=4.0in]{shifted_drifttimes.png}
  \caption{The Raw TDC vs. Wire Number Correlations for all 12 planes. An offset of $\sim$ 1000 Channels ($\sim$ 100 ns) is observed
    in wire groups of four distinct planes.}
  \label{fig:shift_dtimes}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[width=7.0in, height=4.0in]{bad_wireresidual.png}
  \caption{Correlation of Residuals vs. Wire Number for all 12 planes. Four wire groups stand out from the rest, with a noticeable smearing.
  The adjacent planes are affected by this smearing as well, even though they are NOT part of the problematic TDC.}
  \label{fig:wire_residual}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[width=6.0in, height=4.0in]{hDC_RefTime_correlation.png}
  \caption{Correlation between the HMS DC reference time and the raw TDC times. The DC 1, V'-Plane raw TDC vs. Wire Number is shown. Adjacent wirgroups which
  are NOT in TDC Slot 2 are compared to the TDC Slot 2 wire group before and after applying the reference time correction to the TDC time.}
  \label{fig:wire_residual}
\end{figure}

\newpage
The figure above is determinant in this study, as it shows the correlation of the reference time with the raw TDC time before and after applying the reference time correction.
As expected from a normal TDC, when tdc times are reference time subtracted, the correlation dissappears. However, in TDC Slot 2, the reference time and raw tdc time appear to be
correlated, which is an indication that its copy of the reference time is Out-of-Sync with the rest of the modules.

\section{Temporary Solution for the Out-Of-Sync TDC}
\indent As a temporary solution, it was decided that a copy of the reference time should be fed independently to the bad TDC module. This way, the TDC can synchronize with its own
reference time, as opposed to receiving an alternate copy from the trigger interface (TI) module. This modification was done on hardware on July 30, 2018. See Log Enrty \url{https://logbooks.jlab.org/entry/3583094}.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{hdcref5_corr.png}
  \caption{TDC Slot 2 Reference Time vs. Raw Uncorrected TDC \\Time for wire group 1V2 (49-64)}
  \label{fig:ref5_correlated}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{hdcref5_uncorr.png}
  \caption{TDC Slot 2 Reference Time vs. Raw Corrected TDC \\Time for wire group 1V2 (49-64)}
  \label{fig:ref5_uncorrelated}
\end{subfigure}
\caption{Results of HMS singles (DAQ in Coincidence Mode) cosmic run 4437 to verify that adding the new reference time to TDC Slot 2 fixes the problem.
  The subfigures above show the correlation between the newly added reference time and raw TDC Time from a group of wires in TDC Slot 2. As shown in subfigure (b), the correlation
  between the new reference time and raw TDC time is NOT present when the raw time is reference time corrected.}
\label{fig:test}
\end{figure}

A modification in software map was also necessary, as the TDC Slot 2 needed to point to the new reference time. This change affects the data replay from the
Spring 2018 Commissioning Run Period since during that time, TDC Slot 2 was pointing to a different reference time in the software. Therefore, if you have the most up-to-date copy of the
hallc replay analyzer, to replay data from the previous run period, make sure to load the correct map into the replay script being used. See Figure \ref{fig:map}

\begin{figure}[h]
  \centering
  \includegraphics[width=5.0in, height=1.0in]{loadmap.png}
  \caption{Snippet of the hms replay script that shows how to load the correct map for Spring 2018 run period.}
  \label{fig:map}
\end{figure}

\section{How to Minimize the impact the Out-of-Sync TDC had on Residuals }
\noindent The group of wires that were affected by the TDC synchronization issue cannot be restored to normal, so their resduals will remain significantly smeared out. Fortunately,
two of the groups are located at the edge of each chamber, so they have minimal impact. The other two groups, even though they are near the center of the chamber, they are
in different chambers, so tracking in NOT severely affected. The group of wires in adjacent planes are affected (See Figure \ref{fig:wire_residual}) by this smearing, since
they depend heavily on their adjacent partners (U,V planes) for the (x,y) coordinate determination from tracking. To minimize this effect, the Hall C source code \textit{hcana}
was modified to read in the sigma parameters on a per-wire basis, if a certain flag is set. Originally, the sigma parameters were read on a per-plane basis, and were assigned a
value of 0.02 by default. If the sigma-per-wire flag is set, then the sigma parameter values are read on a wire-by-wire basis, and the wire groups associated with the
Out-of-Sync TDC are assigned a sigma of 0.06, while the rest are assigne a value of 0.02 so that during the track-fitting algorithm, if a track passes though one of this groups,
they will have a smaller contribution (or weight) to the fit. The results are shown in Figure

\newpage
\onecolumn
\bibliography{template}
\bibliographystyle{acm}

\end{document}

### 2018-08-29 Spring_2018_Run/OutOfSync_TDC/crate03_TDC_sync/checkREF.C

@@ -1,0 +1,54 @@
+void checkREF(Int_t run)
+{
+
+  //gROOT->SetBatch(kTRUE); 
+  
+  TString filename =Form("../../../ROOTfiles/hms_replay_production_all_%d_50000.root", run);                              
+      
+  //read the file and get the tree                     
+  TFile *data_file = new TFile(filename, "READ");                                                     
+  TTree *T = (TTree*)data_file->Get("T");
+
+  //Define Plane Names
+  TString plane_names[12];
+  plane_names[0]="1u1";      //group 81-96 is known to be in the out of sync TDC in HMS crate03 
+  plane_names[1]="1u2";   
+  plane_names[2]="1x1" ;   
+  plane_names[3]="1x2";   
+  plane_names[4]="1v1";   
+  plane_names[5]="1v2";      //group 49-64 is known to be in the out of sync TDC in HMS crate03   
+  plane_names[6]="2v2";    
+  plane_names[7]="2v1";     //group 81-96 is known to be in the out of sync TDC in HMS crate03 
+  plane_names[8]="2x2";   
+  plane_names[9]="2x1";   
+  plane_names[10]="2u2";    //group 49-64 is known to be in the out of sync TDC in HMS crate03
+  plane_names[11]="2u1"; 
+  
+  //User Input
+  string hreftime = "hDCREF1";    //choose which reference time to use (hDCREF1, 2, 3, 4, or 5)
+  string pl_nm = "1v2";   //choose plane name to look at
+  Int_t group_min = 49;     //minimum wire in chosen group
+  Int_t group_max = 64;      //maximum wire in chosen group
+
+  TCanvas *c1 = new TCanvas(Form("Plane %s, REF Time ", pl_nm.c_str()), Form("Plane %s, Wire Group (%d - %d)", pl_nm.c_str(), group_min, group_max),  1500, 1500);
+  c1->Divide(1,2);
+ 
+  //Create Histograms
+  TH2F *H_norefCorr = new TH2F("norefCorr", Form("Run %d: hDCRef vs. %s REF. Uncorrected tdcTime: Wire group: %d-%d", run, pl_nm.c_str(), group_min, group_max), 500, 1000, 6000, 500, 1600, 2000);
[…]

### 2018-08-29 Spring_2018_Run/OutOfSync_TDC/tdc_sync_report.tex
updated directory

@@
 \usepackage[font=footnotesize,labelfont=bf]{caption}
+\usepackage[usenames, dvipsnames]{color}
+\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
 \usepackage{graphicx}
@@
 \section{Temporary Solution for the Out-Of-Sync TDC}
-\indent As a temporary solution, it was decided that a copy of the reference time should be fed independently to the bad TDC module. This way, the TDC can synchronize with its own
+\indent As a temporary solution (until we replace the TDC module), it was decided that a copy of the reference time should be fed independently to the bad TDC module.
+This way, the TDC can synchronize with its own
 reference time, as opposed to receiving an alternate copy from the trigger interface (TI) module.
@@
   between the new reference time and raw TDC time is NOT present when the raw time is reference time corrected.}
-\label{fig:test}
+\label{fig:hdc_Ref5}
 \end{figure}
@@
 Out-of-Sync TDC are assigned a sigma of 0.06, while the rest are assigne a value of 0.02 so that during the track-fitting algorithm, if a track passes though one of this groups,
-they will have a smaller contribution (or weight) to the fit. The results are shown in Figure
+they will have a smaller contribution (or weight) to the fit. The results are shown in Figures \ref{fig:wire_residuals_flag}.
+\begin{figure}[h!]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \hspace*{-5cm}                                                           
+  \centering
+  \includegraphics[width=2.1\linewidth]{2d_residuals_flagOFF.png}
+  \subcaption{Residuals vs. Wire Number for all Chamber planes, with sigma-per-wire flag \textit{OFF}.}
+  \label{fig:2d_res_flagOff}
+\end{subfigure}%
 
+\begin{subfigure}{.5\textwidth}
+\hspace*{-5cm}                                                           
+  \centering
+  \includegraphics[width=2.1\linewidth]{2d_residuals_flagON.png}
+  \caption{Residuals vs. Wire Number for all Chamber planes, with sigma-per-wire flag \textit{ON}.}
+  \label{fig:2d_res_flagON}
+\end{subfigure}
+\caption{Residuals vs. Wire Number for all Chamber planes. The \textcolor{red}{RED BOXES} highlight the group of wires that were affected, but had nothing to do with the
+  out-of-sync TDCs wire groups.}
+\label{fig:wire_residuals_flag}
+\end{figure}\\
+In subfigure (b), when a sigma of 0.06 was applied to the bad groups (Planes 1u1, 1v2, 2v1, 2u2), the adjacent planes (highlighted in \textcolor{red}{RED})
+wire residuals improved significantly. This is due the fact that less weight (larger sigma($\sigma$)) was given to the affected group of wires. \\
+\newpage
+The plane residuals, however, did not have much improvement after increasing the weight factor. At most, there was a 25 $\mu$m improvevent in the Standard Deviation.
+See Figure \ref{fig:plane_residuals}
+\begin{figure}[ht!]
+  \hspace*{-1.5cm}                                                           
+%  \vspace*{10.5cm}                                                           
+  \centering
+  \includegraphics[width=7.0in, height=4.0in]{residuals_compare.pdf}
+  \caption{Plane residuals with the sigma-per-wire flag ON (\textcolor{red}{RED}) and OFF (\textcolor{navyblue}{BLUE})}
+  \label{fig:plane_residuals}
+\end{figure}
+\newline
+\noindent It is importnant to note that the sigma-per-wire flag and the parameter file are NOT included in \texttt{hallc$\_$replay}, since this is a very specific scenario that
+ONLY applies to the Winter-2017/Spring-2018 Run Period. If users who took data during that time, and would like to try adding this flag and the parameter file,
+the instructions are as follows:
+\begin{itemize}
+\item  Create the parameter file in path: \texttt{/PARAM/HMS/DC/hdc$\_$sigma$\_$per$\_$wire.param} \par
+  \begin{minipage}{\linewidth}
+    \centering
+    \includegraphics[width=15cm]{param.png}
+    \captionof{figure}{Snippet of sigma-per-wire parameter file.}
+    \label{fig:param}
+  \end{minipage}
+\item  Include the parameter file in path: \texttt{/DBASE/HMS/general.param} \par
+  \begin{minipage}{\linewidth}                                                          
+    \centering
+    \includegraphics[width=10cm]{gen_parm.png}
+    \captionof{figure}{Snippet of general.param file.}
+    \label{fig:gen_param}
+  \end{minipage}
+\end{itemize}
 \newpage

### 2018-08-29 Spring_2018_Run/OutOfSync_TDC/write_sig_param.C

@@ -1,0 +1,68 @@
+//__________________________________________________________________________
+void write_sig_param()
+{
+
+
+  ofstream ofile;
+  TString filename = "hdc_sigma_per_wire.param";
+  ofile.open(filename);
+
+  TString plane_names[12];
+  Int_t nwires[12];
+
+  plane_names[0]="1u1",  nwires[0] = 96;  
+  plane_names[1]="1u2",  nwires[1] = 96;
+  plane_names[2]="1x1",  nwires[2] = 102;
+  plane_names[3]="1x2",  nwires[3] = 102; 
+  plane_names[4]="1v2",  nwires[4] = 96;
+  plane_names[5]="1v1",  nwires[5] = 96;
+  plane_names[6]="2v1",  nwires[6] = 96;
+  plane_names[7]="2v2",  nwires[7] = 96;
+  plane_names[8]="2x2",  nwires[8] = 102;
+  plane_names[9]="2x1",  nwires[9] = 102;
+  plane_names[10]="2u2", nwires[10] = 96;
+  plane_names[11]="2u1", nwires[11] = 96;
+  
+  ofile << ";Flag to fix HMS TDC Slot 2 Out-of-Sync problem" << endl;
+  ofile << "h_using_sigma_per_wire = 1" << endl;
+  ofile << " " << endl;
+  
+  for (int plane=0; plane<12; plane++) { 
+	  
+    //write plane headers
+    ofile << "hwire_sigma"+plane_names[plane] << "=" << endl;
+
+    Double_t sigma;
+
+    //cout << "Plane: "  << plane << endl;
+   for (int wire_num=1; wire_num<=nwires[plane]; wire_num++) 
+     {
+
+       if(plane == 0 && wire_num>=81 && wire_num<=96) {sigma = 0.06;}
+       else if(plane == 4 && wire_num>=49 && wire_num<=64) {sigma = 0.06;}
+       else if(plane == 6 && wire_num>=81 && wire_num<=96) {sigma = 0.06;}
+       else if(plane == 10 && wire_num>=49 && wire_num<=64) {sigma = 0.06;}
+       else {sigma = 0.02;}
+       
+       cout << "Plane: " << plane << " ::  wire: " << wire_num << " :: " << "sigma: "<< sigma << endl;
+       if (wire_num <= 10) 
+	 { 
+	   ofile << setprecision(6) << sigma << fixed << ",";
+	 }
[…]

### 2018-08-29 Spring_2018_Run/OutOfSync_TDC/tdc_sync_report.tex
finished document on bad TDC

@@
 
-\title{On the Out-of-Sync TDC Module on the HMS Chambers}
+\title{\textbf{Discussion On the Out-of-Sync TDC Module from the HMS Chambers}}
 \author{Carlos Yero}
-\date{August 28 2018}
+\date{August 29 2018}
 
@@
 %*****************************************************************************************************************************************************
-During the Fall-2017/Spring-2018 Hall C Commissioning Run Period, it was found that a particular TDC module in the HMS
+\noindent During the Fall-2017/Spring-2018 Hall C Commissioning Run Period, it was found that a particular TDC module in the HMS
 Drift Chambers Crate (ROC03) was shifting the tdc times of the corresponding groups of wires being fed into it. At that time,
@@
 residuals per wire after calibration. After the end of the Spring Run, I decided to look at the residuals per wire for a defocused
-run in the HMS, and found certaing groups of wire residuals to be significantly smeared compared to adjacent groups of wires.
+run in the HMS (run 1267), and found certain groups of wire residuals to be significantly smeared compared to adjacent groups of wires (smeared
+residuals were being overshadowed by another problem fixed by Mark Jones during Spring 2018 SIDIS, concerning the \texttt{hodoscope starttime}).
 These were the same group of wires that exhibited the shift in time, which pointed to the same TDC module in ROC03, Slot 2.
@@
   \centering
-  \includegraphics[width=7.0in, height=4.0in]{shifted_drifttimes.png}
+  \includegraphics[width=6.5in, height=3.5in]{shifted_drifttimes.png}
   \caption{The Raw TDC vs. Wire Number Correlations for all 12 planes. An offset of $\sim$ 1000 Channels ($\sim$ 100 ns) is observed
@@
 \end{itemize}
+\noindent In case you need help or do NOT have the time to create this parameter file, I have uploaded both the script that produces the parameter file and the parameter file
+itself to my github page. \\
+\textbf{Link to script:} \\ \url{https://github.com/Yero1990/scientific_articles/blob/master/Spring_2018_Run/OutOfSync_TDC/write_sig_param.C} \\
+\textbf{Link to parameter file:} \\\url{https://github.com/Yero1990/scientific_articles/blob/master/Spring_2018_Run/OutOfSync_TDC/hdc_sigma_per_wire.param}
+
 \newpage

### 2018-08-30 Spring_2018_Run/OutOfSync_TDC/tdc_sync_report.tex
corrected report

@@
 \section{Observed Correlations on the Out-of-Sync TDC Module}
+\noindent Figure \ref{fig:shift_dtimes} shows the Drift Chamber raw TDC times vs. Wire Number for all 12 planes. In four of the planes,
+a $\sim$ 100 ns drift for cetrtain groups of wires can clearly be observed. This was the first indication, but NOT with absolute certainty,
+that the TDC module to which these four groups were connected to was problematic.
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=6.5in, height=3.5in]{shifted_drifttimes.png}
+  \includegraphics[width=6.0in, height=3.0in]{shifted_drifttimes.png}
   \caption{The Raw TDC vs. Wire Number Correlations for all 12 planes. An offset of $\sim$ 1000 Channels ($\sim$ 100 ns) is observed
@@
 \end{figure}
+\newpage
+In Figure \ref{fig:wire_residual}, the redisuals for the tracks are plotted as a function of wire number. It can be clearly observed that the same four groups mentioned in
+Figure \ref{fig:shift_dtimes} have smeared out residuals. At this point, I started to consider this issue seriously, as it was NOT simply drifted times which could be fixed in
+software, but now the tarcking had been affected.
 \begin{figure}[h!]
@@
   \centering
-  \includegraphics[width=6.0in, height=4.0in]{hDC_RefTime_correlation.png}
+  \includegraphics[width=5.1in, height=3.1in]{hDC_RefTime_correlation.png}
   \caption{Correlation between the HMS DC reference time and the raw TDC times. The DC 1, V'-Plane raw TDC vs. Wire Number is shown. Adjacent wirgroups which
-  are NOT in TDC Slot 2 are compared to the TDC Slot 2 wire group before and after applying the reference time correction to the TDC time.}
-  \label{fig:wire_residual}
+  are NOT in TDC Slot 2 are compared to the TDC Slot 2 wire group before and after applying the reference time correction to the raw TDC time.}
+  \label{fig:hDC_correlation}
 \end{figure}
-
 \newpage
-The figure above is determinant in this study, as it shows the correlation of the reference time with the raw TDC time before and after applying the reference time correction.
+Figure \ref{fig:hDC_correlation} is determinant in this study, as it shows the correlation of the reference time with the raw TDC time before and after applying the reference time correction.
 As expected from a normal TDC, when tdc times are reference time subtracted, the correlation dissappears. However, in TDC Slot 2, the reference time and raw tdc time appear to be
@@
 \end{figure}
-
-A modification in software map was also necessary, as the TDC Slot 2 needed to point to the new reference time. This change affects the data replay from the
+\noindent To demonstrate that the new reference time added fixed the issue, I decided to take an HMS singles (DAQ in Coincidence Mode) cosmic run to prove that when the
+new reference time was subtracted from the raw TDC time, the correlation that was present originally, dissappeared. This was indeed what happened, as observed in Figure \ref{fig:hdc_Ref5}.\\
+\indent A modification in software map was also necessary, as the TDC Slot 2 needed to point to the new reference time. This change affects the data replay from the
 Spring 2018 Commissioning Run Period since during that time, TDC Slot 2 was pointing to a different reference time in the software. Therefore, if you have the most up-to-date copy of the
@@
 \end{figure}
-
+\newpage
 \section{How to Minimize the impact the Out-of-Sync TDC had on Residuals }
@@
 In subfigure (b), when a sigma of 0.06 was applied to the bad groups (Planes 1u1, 1v2, 2v1, 2u2), the adjacent planes (highlighted in \textcolor{red}{RED})
-wire residuals improved significantly. This is due the fact that less weight (larger sigma($\sigma$)) was given to the affected group of wires. \\
-\newpage
+wire residuals improved significantly. This is due the fact that less weight (larger sigma($\sigma$)) was given to the affected group of wires.
+To quantify by how much the group residuals highlighted in Figure \ref{fig:wire_residuals_flag} have improved, I plotted the 1D-projection of such wire groups.
+There seemed to be a noticable improvement with up to $\sim$ 60 $\mu$m in the residuals. See Figure \ref{fig:group_residuals} below.
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=7.0in, height=4.0in]{group_residuals.pdf}
+  \caption{Residuals of highlighted wire groups in Figure \ref{fig:wire_residuals_flag}}
+  \label{fig:group_residuals}
+\end{figure}\\
 The plane residuals, however, did not have much improvement after increasing the weight factor. At most, there was a 25 $\mu$m improvevent in the Standard Deviation.
@@
 \begin{figure}[ht!]                                                          
-  \hspace*{-1.5cm}                                                           
 %  \vspace*{10.5cm}                                                           
   \centering
-  \includegraphics[width=7.0in, height=4.0in]{residuals_compare.pdf}
+  \includegraphics[width=7.5in, height=3.0in]{residuals_compare.pdf}
   \caption{Plane residuals with the sigma-per-wire flag ON (\textcolor{red}{RED}) and OFF (\textcolor{navyblue}{BLUE})}
@@
 \end{figure}
-\newline
+\newpage
 \noindent It is importnant to note that the sigma-per-wire flag and the parameter file are NOT included in \texttt{hallc$\_$replay}, since this is a very specific scenario that

### 2018-08-30 Spring_2018_Run/OutOfSync_TDC/tdc_sync_report.tex
final modifications to the report

@@
   \caption{Correlation between the HMS DC reference time and the raw TDC times. The DC 1, V'-Plane raw TDC vs. Wire Number is shown. Adjacent wirgroups which
-  are NOT in TDC Slot 2 are compared to the TDC Slot 2 wire group before and after applying the reference time correction to the raw TDC time.}
+    are NOT in TDC Slot 2 are compared to the TDC Slot 2 wire group before and after applying the reference time correction to the raw TDC time. The vertical axis
+  is the HMS DC reference time corrected from itself (ns units). The horizontal axis is the raw TDC time in units of Channel ($\sim$0.1 ns/Channel).}
   \label{fig:hDC_correlation}
@@
 Figure \ref{fig:hDC_correlation} is determinant in this study, as it shows the correlation of the reference time with the raw TDC time before and after applying the reference time correction.
-As expected from a normal TDC, when tdc times are reference time subtracted, the correlation dissappears. However, in TDC Slot 2, the reference time and raw tdc time appear to be
-correlated, which is an indication that its copy of the reference time is Out-of-Sync with the rest of the modules.
+As expected from a normal TDC, when tdc times are reference time subtracted, the correlation dissappears. However, in TDC Slot 2, the reference time and raw tdc time
+are uncorrelated, which is an indication that it is Out-of-Sync with the rest of the modules. When the raw TDC time for Slot 2 is corrected with the reference
+time from another Slot, the corrected TDC time now has a correlation with the reference time which is indicative of a synchronization issue.
+The reference time spans over a 25 ns range, even though it is reference time corrected from itself, which is due to the intrinsic 25 ns jitter coming from the TDC internal 40 MHz clock. The
+raw TDC time spans over a $\sim$ 100 ns range, and at the smallest range, which corresponds to drift times of particles nearest to the sense wires, one can clearly see a
+correlation with the reference time.
 
@@
 \section{How to Minimize the impact the Out-of-Sync TDC had on Residuals }
-\noindent The group of wires that were affected by the TDC synchronization issue cannot be restored to normal, so their resduals will remain significantly smeared out. Fortunately,
+\noindent The group of wires that were affected by the TDC synchronization issue cannot be restored to normal, so their residuals will remain significantly smeared out. Fortunately,
 two of the groups are located at the edge of each chamber, so they have minimal impact. The other two groups, even though they are near the center of the chamber, they are

### 2019-04-06 FIU_Physics_Competition/abstract.tex
FIU Physics Competition

\documentclass[a4paper]{article}
%\usepackage{simplemargins}

%\usepackage[square]{natbib}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[urw-garamond]{mathdesign}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}

\begin{document}
\pagenumbering{gobble}

\Large
 \begin{center}
Deuteron Electro-Disintegration at Very High Missing Momenta\\

\hspace{10pt}

% Author names and affiliations
\large
Carlos Yero \\

\hspace{10pt}

April 07, 2019 \\

\hspace{10pt}

\small  
Florida International University\\

\end{center}

\hspace{10pt}

\normalsize

\noindent The Deuteron Electro-Disintegration experiment (E12-10-003) at Jefferson Lab, Hall C is discussed.  The experiment
consists of using an electron beam to break up the Deuteron into a proton and neutron. The scattered electron is detected in
coincidence with the knocked out proton and the missing neutron is reconstructed from conservation laws. The newly commissioned Super High
Momentum Spectrometer (SHMS) and existing High Momentum Spectrometer (HMS) are used to detect the electron and proton, respectively. The
D(e,e'p)n reaction investigates an unexplored kinematic region in which Final State Interactions (FSI) between the proton and neutron are small. In this
regime, the neutron missing momentum is approximately equal to its internal momentum in the Deuteron, enabling the extraction of momentum distributions
from the measured cross-sections. A general theoretical background of the D(e,e'p) reaction and very preliminary results are presented.

\end{document}

### 2019-05-13 FIU_Physics_Competition/abstract.tex
add boiling studies

@@
 \usepackage{tgbonum}
+\usepackage[left=4cm, right=4cm, top=1cm]{geometry}
 
@@
 
-April 07, 2019 \\
+\small
+April 08, 2019 \\
 
@@
 \noindent The Deuteron Electro-Disintegration experiment (E12-10-003) at Jefferson Lab, Hall C is discussed. The experiment
-consists of using an electron beam to break up the Deuteron into a proton and neutron. The scattered electron is detected in
-coincidence with the knocked out proton and the missing neutron is reconstructed from conservation laws. The newly commissioned Super High
-Momentum Spectrometer (SHMS) and existing High Momentum Spectrometer (HMS) are used to detect the electron and proton, respectively. The
-D(e,e'p)n reaction investigates an unexplored kinematic region in which Final State Interactions (FSI) between the proton and neutron are small. In this
-regime, the neutron missing momentum is approximately equal to its internal momentum in the Deuteron, enabling the extraction of momentum distributions
-from the measured cross-sections. A general theoretical background of the D(e,e'p) reaction and very preliminary results are presented.
+consists of using an electron beam to break up the Deuteron into a proton and neutron. The scattered electron is detected by the Super High
+Momentum Spectrometer (SHMS) in coincidence with the knocked out proton in the High Momentum Spectrometer (HMS) and the missing neutron is reconstructed
+from conservation laws. This experiment investigates an unexplored kinematic region at high missing momentum in which Final State Interactions (FSI)
+between the outgoing proton and neutron are small. In this regime, the neutron missing momentum is approximately equal to its internal momentum in the
+Deuteron enabling the extraction of momentum distributions from the measured cross-sections. A general theoretical background of the D(e,e'p) reaction and
+very preliminary results are presented.
 

### 2019-06-21 MY_THESIS/Coin_Time_Module/coin_time.tex
re-structure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to writeLaTeX --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you give 
% someone the link to this page, they can edit at the same
% time. See the help menu above for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------

\documentclass[14pt]{article}

\usepackage[margin=0.5in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color,soul}
\usepackage{caption}
\usepackage{courier}
\usepackage{listings}
\usepackage{xcolor} % for setting colors

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
\newenvironment{courier}{\ttfamily}{\par}

% set the default code style
\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{orange}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red} % string color
}

\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------

\title{\textbf{Brief Document On the Hall C Coincidence Time Physics Module}}%replace X with the appropriate number
\author{Carlos Yero} %if necessary, replace with your course title

\maketitle
\noindent The Hall C Coincidence Time Physics Module, THcCoinTime.cxx(.h), was created to facilitate the analysis of
coincidence time data by adding coincidence time variables to the ROOT Tree, so that users may apply any
cuts they desise to clean-up the data. This document intends to briefly cover what was done in physics module,
as well as the mathematical background, which was written by Latif Kabir during the start of Commissioning in 2018.\\

\section{Discussion on the Physics of Coincidence Timing}
The coincidence time measured between two spectrometers is defined as the time difference between the
two single-arm spectrometer triggers. The time difference is determined using the raw (uncorrected) TDC times,
therefore, additional corrections will be needed to reduce the natural spread in the coincidence peak.
As pointed out in Latif's paper, the corrections are as follows:
\begin{enumerate}
\item The leading order correction is the time taken by the partilcle to arrive at the focal plane following the
  central path, $L_{0}$, of the spectrometer.
\item The second order correction is due to the fact that the particle may not necessarily follow the central path, therefore,
  the time difference between particle path and central path, $\Delta L$, needs to be accounted for.
\item The third order correction is the fluctuations in the focal plane time with respect to the central time.
\item The last correction has more to do with a general offset of the coincidence peak, rather than an effect on the
  resolution. The peak is typically shifted to zero, to represent the occurrence of a true coincidence event originating
  from the same electron beam bunch.
\end{enumerate}
The raw coincidence times in the physics module were mathematically expressed as
\begingroup
\normalsize
\begin{equation}\label{eq1}
t_{\text{coin, raw}} = (t_{\text{SHMS, raw}} + t_{\text{SHMS, fp}}) - (t_{\text{HMS, raw}} + t_{\text{HMS, fp}})
\end{equation}
\endgroup

\noindent where the focal plane times were included as a correction to the raw tdc trigger times to simplify calculations later on.
The corrected coincidence time can then be expressed as
\begin{equation}\label{eq2}
t_{\text{coin, corr.}} = t_{\text{coin, raw}} \pm (t_{\text{elec. corr}} - t_{\text{hadron corr.}}) - \delta_{\text{offset}}
\end{equation}
where the sign convention is
\[ \text{sign} =
  \begin{cases}
    +  &  \text{SHMS (hadrons), HMS (electrons)}\\
    -  &  \text{SHMS (electrons), HMS (hadrons)}
  \end{cases}
  \]
  \noindent The sign depends on the particle type the spectrometer is set to detect, as we want to ensure the correction is \textit{subtracted off}
  from the right spectrometer raw trigger time. For example, if the SHMS is set to detect electrons, then substituting Eq. \ref{eq1} in Eq. \ref{eq2}, one obtains
  \begin{equation}\label{eq3}
    \begin{aligned}
      t_{\text{coin, corr.}} & = (t_{\text{SHMS, raw}} + t_{\text{SHMS, fp}}) - (t_{\text{HMS, raw}} + t_{\text{HMS, fp}}) - (t_{\text{elec. corr}} - t_{\text{hadron corr.}}) - \delta_{\text{offset}} \\
                          & = (t_{\text{SHMS, raw}} + t_{\text{SHMS, fp}} - \text{\textcolor{red}{$t_{\text{elec. corr}}$}}) - (t_{\text{HMS, raw}} + t_{\text{HMS, fp}} - \text{\textcolor{red}{$t_{\text{hadron corr.}}$}})  - \delta_{\text{offset}}
    \end{aligned}
    \end{equation}  
  \noindent By subtracting the electron/hadron timing corrections, the dependence on the particle pathlength and beta, $\beta$, are
  removed. Therefore, if a \textit{true} coincidence occurs, it will land at the same location in the coincidence timing spectrum, regardless
  of the particle type. See Figure \ref{fig:eH_Coin}. \\ \newline
  \begin{figure}
  \includegraphics[scale=0.3]{eH_Coin.pdf}
  \caption{Electron-hadron coincidence time, assuming proton, $\pi^{+}$ and K$^{+}$ mass.}
  \label{fig:eH_Coin}
  \end{figure}
  \noindent The timing corrections for electrons and hadrons in Eq. \ref{eq3} can be expressed in the general form
  \begin{equation}
    \begin{aligned}
      t_{\text{e(h) corr.}} = \frac{L_{0} + \Delta L}{\beta c}, \text{  where } \beta \equiv \frac{p}{E} = \frac{p}{\sqrt{m^{2} + p^{2}}}
    \end{aligned}
  \end{equation}
  The variables ($L_{0}$, $\Delta L$) are the 1st and 2nd order path length corrections, corresponding to either the HMS or SHMS, depending on which particle
  is assigned to which spectrometer. The variable $\beta$, represents
  the particle fractional velocity relative to the speed of light, and depends on the particle mass and momentum. Therefore, subtracting off all these
  dependences from the raw coincidence time, places the coincidence peak at a certain offset, $\delta_{\text{offset}}$, which can then be determined experimentally, and
  shifted to zero (0 ns). (See Figure \ref{fig:eH_offset})
  \begin{figure}[h]
  \includegraphics[scale=0.5]{ePi_compare.pdf}
  \caption{e$\pi^{+}$ coincidence time, assuming pion mass. A $\delta_{\text{offset}}$ has been determined and applied to several SIDIS runs.}
  \label{fig:eH_offset}
  \end{figure}
  \\
  \noindent A $\delta_{\text{offset}}$ of 9.76 ns was determined from SIDIS run 4145, using clean e$^{-}\pi^{+}$ coincidences. A calorimeter and Cherenkov cut was
  applied on the HMS for selecting electrons, and an Aerogel photoelectron cut was applied on the SHMS
  to eliminate proton contamination showing up in the accidentals. After obtaining a clean sample of e$^{-}\pi^{+}$ coincidences, a fit was done to the main peak to
  determine the offset. The stability of the offset was tested for various SIDIS runs at different SHMS momenta. (See Figure \ref{fig:eH_offset})

  \newpage

  \section{Discussion on Coincidence Time Module Workflow}
  \noindent The coincidence time physics module can be found under hcana/src directory, with the name of \texttt{THcCoinTime.cxx(.h)}. The module
  is a derived class from more general Hall A class \texttt{THaPhysicsModule.C(.h)}, and hence, it also uses all of its member functions/methods. The
  class is called in the main Hall C analysis coincidence replay scripts, located in: \\
  \texttt{/hallc\_replay/SCRIPTS/COIN/PRODUCTION/}. I will start by discussing how the physics module is calle in the analyzer, and then
  briefly discuss the relevant methods used for calculating the coincidence time in chronological order.

  \begin{lstlisting}[language=C++, caption={Adding the Module in the Analyzer}] 
    void replay_production_coin_hElec_pProt(Int_t RunNumber = 0, Int_t MaxEvent = 0) {

      //A few lines later, towards the end of the code (line # are not same) 
      //This replay script is in: /hallc_replay/SCRIPTS/COIN/PRODUCTION/

      THcCoinTime* coinTime = new THcCoinTime("CTime", "Coincidence Time Determination",
      "P", "H", "T.coin"); 
      gHaPhysics->Add(coinTime);

    }
  \end{lstlisting}
  In the snippet of code above (Listing 1), an instance (coinTime) of the class is created and initialized with arguments that will be used
  later on. The order in which the arguments ``P" and ``H" are called is important, as they dictate which spectrometer will be the electron or hadron arm,
  an so they must be consistent with the replay script that is called. \\
  \newline
    \begin{lstlisting}[language=C++, caption={THcCoinTime.cxx, The Constructor Method}] 
      THcCoinTime::THcCoinTime (const char *name, const char* description,
      const char* hadArmName, const char* elecArmName, const char* coinname) :

  THaPhysicsModule(name, description), 
  fCoinDetName(coinname), 
  fhadArmName(hadArmName),                 //initialize spectro names
  felecArmName(elecArmName),
  fhadSpectro(NULL),                      //initialize spectro objects
  felecSpectro(NULL),
  fCoinDet(NULL)
{

}

  \end{lstlisting}

\noindent In the Listing 2 snippet above, the constructor is defined with some arguments, which were called in Listing 1. The first argument, \textit{name},
represents the name of the class and will be the \textit{prefix-} in every ROOT leaf variable that is added in the DefineVariables() method. The
third and fourth arguments, take the char value ``P" or ``H", depending on which spectrometer will be the hadron/electron arm. The arguments in
the constructor are paseed on in lines 4-7. Additional \texttt{THcHallCSpectrometer.cxx} objects are initialized in lines 8-10, and will be used later on.\\

\begin{lstlisting}[language=C++, caption={THcCoinTime.cxx, The Init() Method}] 
  THaAnalysisObject::EStatus THcCoinTime::Init( const TDatime& run_time )
  {
    // Initialize THcCoinTime physics module

  fhadSpectro = dynamic_cast<THcHallCSpectrometer*>
    ( FindModule( fhadArmName.Data(), "THcHallCSpectrometer"));
  if( !fhadSpectro ) {
    cout << "THcCoinTime module  Cannnot find Hadron Arm = " <<  fhadArmName.Data() << endl;
    fStatus = kInitError;
    return fStatus;
  }

  //The other two objects are also casted, but due to space, were not included.

\end{lstlisting}
In the \texttt{Init()} method above, the objects initialized to NULL in the constructor are converted to
\texttt{THcHallCSpectrometer} objects via a \texttt{dynamic\_cast}, which enables the object to use all member functions
of mentioned class. \\

\begin{lstlisting}[language=C++, caption={THcCoinTime.cxx, The ReadDatabase() Method}] 
Int_t THcCoinTime::ReadDatabase( const TDatime& date )
{
  // Read database. Gets variable needed for CoinTime calculation

  DBRequest list[]={
    {"eHadCoinTime_Offset",  &eHad_CT_Offset, kDouble, 0, 1},  
    {"HMS_CentralPathLen",  &HMScentralPathLen, kDouble, 0, 1},
    {"SHMS_CentralPathLen", &SHMScentralPathLen, kDouble, 0, 1},
    {0}
  };

  //Default values if not read from param file
  eHad_CT_Offset = 0.0;

  HMScentralPathLen = 22.0*100.;
  SHMScentralPathLen = 18.1*100.;

  gHcParms->LoadParmValues((DBRequest*)&list, "");

  return kOK;
}
\end{lstlisting}
The \texttt{ReadDatabase()} method searches for a \texttt{coincidence time offset} and \texttt{SHMS/HMS Path Length}
parameters. The \texttt{coincidence time offset} parameter is located in \texttt{/PARAM/TRIG/tcoin.param}, and the
\texttt{SHMS/HMS Path Length} parameters are located in  \texttt{/PARAM/SHMS/GEN/pcana.param} and
\texttt{/PARAM/HMS/GEN/hcana.param} directories, respectively. In the scenario that any of the above parameters
were NOT found, they would be initialized by default under this method. (See line \# 14, 16 and 17 of this method)
\\
\begin{lstlisting}[language=C++, caption={THcCoinTime.cxx, The Process() Method}] 
Int_t THcCoinTime::Process( const THaEvData& evdata )
{

 //Create THaTrack object for hadron/elec arms to get relevant golden track quantities
  if (felecArmName=="H") {
    theSHMSTrack =(fhadSpectro->GetGoldenTrack());     
    theHMSTrack = (felecSpectro->GetGoldenTrack());
  } else{
    theSHMSTrack =(felecSpectro->GetGoldenTrack()); 
    theHMSTrack = (fhadSpectro->GetGoldenTrack());
  }
  //Gather relevant variables for Coincidence time calculation
  lightSpeed = 29.9792; // in cm/ns

  //Particle Masses (HardCoded)
  elecMass =  0.510998/1000.0; // electron mass in GeV/c^2
  positronMass =  0.510998/1000.0;
  protonMass = 938.27208/1000.0; // proton mass in GeV/c^2	
  kaonMass = 493.677/1000.0;    //charged kaon mass in GeV/c^2
  pionMass = 139.570/1000.0;    //charged pion mass in GeV/c^2

      //SHMS arm
      Double_t shms_xptar = theSHMSTrack->GetTTheta();     
      Double_t shms_dP = theSHMSTrack->GetDp();            
      Double_t SHMS_FPtime = theSHMSTrack->GetFPTime();

      //HMS arm
      Double_t hms_xfp = theHMSTrack->GetX();           
      Double_t hms_xpfp = theHMSTrack->GetTheta();      
      Double_t hms_ypfp = theHMSTrack->GetPhi();        
      Double_t HMS_FPtime = theHMSTrack->GetFPTime();

      //Get raw TDC Times for HMS/SHMS (3/4 trigger)
      pTRIG1_rawTdcTime_ROC1 = fCoinDet->Get_pTRG1_ROC1_rawTdctime(); 
      pTRIG4_rawTdcTime_ROC1 = fCoinDet->Get_pTRG4_ROC1_rawTdctime();
      pTRIG1_rawTdcTime_ROC2 = fCoinDet->Get_pTRG1_ROC2_rawTdctime();
      pTRIG4_rawTdcTime_ROC2 = fCoinDet->Get_pTRG4_ROC2_rawTdctime();

	  DeltaSHMSpathLength = -0.11*atan2(shms_xptar,1)*1000 - 0.057*shms_dP;
	  DeltaHMSpathLength = 12.462*hms_xpfp + 0.1138*hms_xpfp*hms_xfp - 0.0154*hms_xfp
          - 72.292*hms_xpfp*hms_xpfp - 0.0000544*hms_xfp*had_xfp - 116.52*hms_ypfp*hms_ypfp;

          // default assume SHMS is electron arm
	  Double_t ElecPathLength=SHMScentralPathLen +  DeltaSHMSpathLength;
	  Double_t HadPathLength=HMScentralPathLen +  DeltaHMSpathLength;

          elec_P = theSHMSTrack->GetP();     //electron golden track arm momentum
          had_P = theHMSTrack->GetP();       //hadron golden track arm momentum

          Int_t sign=-1;

          if (felecArmName=="H") {
             ElecPathLength=HMScentralPathLen +  DeltaHMSpathLength;
	     HadPathLength=SHMScentralPathLen +  DeltaSHMSpathLength;
             elec_P = theHMSTrack->GetP();    //electron golden track arm momentum
             had_P = theSHMSTrack->GetP();    //hadron golden track arm momentum
             sign=1;
	  }

	  //beta calculations beta = v/c = p/E
	  elecArm_BetaCalc = elec_P / sqrt(elec_P*elec_P + elecMass*elecMass);
	  hadArm_BetaCalc_proton = had_P / sqrt(had_P*had_P + protonMass*protonMass);

	  //Coincidence Corrections
	  elec_coinCorr = (ElecPathLength) / (lightSpeed * elecArm_BetaCalc );
	  had_coinCorr_proton = (HadPathLength) / (lightSpeed * hadArm_BetaCalc_proton );

	  //Raw, Uncorrected Coincidence Time
	  fROC1_RAW_CoinTime =  (pTRIG1_rawTdcTime_ROC1*0.1 + SHMS_FPtime)
          - (pTRIG4_rawTdcTime_ROC1*0.1 + HMS_FPtime);

	  //Corrected Coincidence Time for ROC1/ROC2 (ROC1 Should be identical to ROC2)
	  //PROTON
	  fROC1_epCoinTime = fROC1_RAW_CoinTime + sign*( elec_coinCorr-had_coinCorr_proton)
          - eHad_CT_Offset;

  return 0;

}
\end{lstlisting}
The coincidence time calculations are done in the Process() method. It may be
non-trivial to follow everything that is done here, so I will attempt to summarize
it based on the code line numbers.
\begin{itemize}
\item Lines 4-10: Based on whether the electron arm is set to HMS("H") or SHMS("P"),
  then associate the \texttt{GetGoldeTrack()} method with either \texttt{THaTrack.cxx}
  objects for HMS or SHMS. The quantities necessary to do the calculations can then
  be obtained from \texttt{theSHMSTrack} or \texttt{theHMSTrack THaTrack.cxx} objects. 
\item Lines 23-33: The relevant HMS/SHMS variables to be used in the Path Length correction
  are obtained from the track objects mentioned in the first bullet.
\item Lines 34-38: Call functions to get the raw TDC Time from each spectrometer
  single arm triggers, \texttt{pTRIG1(3/4 SHMS)} and \texttt{pTRIG4(3/4 HMS)}. The
  \texttt{fCoinDet} object is an instance of the \texttt{THcTrigDet.cxx} class,
  and calls methods to get these raw times, which had to be added in the abovementioned
  class during the time this module was created.
\item Lines 44-60: Start with the assumption that the SHMS is the electron arm,
  determine the corrected path length and golden track momentum, and most importantly,
  define the sign of the correction to be -1, so that the correction to the
  electron/hadron arms is actually subtracted from the raw times, and eliminating any
  dependence of the coincidence time on the particle type. If the electron arm is the
  HMS, then the corrected path length, golden track momentum and the sign invert roles
  between spectrometers.
\item Lines 61-78: Once the electron and hadron arm are associated with a spectrometer,
  then lines 62-63 determine the velocity of the electron and hadron. (I only included
  the Proton, but the calculation was also done for Kaons, Pions and Positrons.)
  Lines 67-68 determine the time it takes the particle to traverse through the spectrometer
  into the focal plane. Lines 71-72 determine the raw coincidence times by taking the
  difference between the raw TDC times determined in Lines 35-38. The focal plane times
  are also included here, so simplify the calculation later on. Finally, Lines 76-77
  combine the elements in Lines 66-72, along with the sign, to determine the corrected
  coincidence time. An offset is added towards the end in order to shift the coincidence peak
  to zero. This offset is read as a parameter in the \texttt{ReadDatabase()} method.

\end{itemize}

% --------------------------------------------------------------
%     You don't have to mess with anything below this line.
% --------------------------------------------------------------

\end{document}

### 2019-06-21 MY_THESIS/Hodoscope_Calib_Doc/hodo_calib.tex
re-structure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to writeLaTeX --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you give 
% someone the link to this page, they can edit at the same
% time. See the help menu above for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------

\documentclass[14pt]{article}

\usepackage[margin=0.5in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{color,soul}
\usepackage{caption}
\usepackage{courier}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor} % for setting colors

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}

  \item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
\newenvironment{courier}{\ttfamily}{\par}

% set the default code style
\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{orange}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red} % string color
}

\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------

\title{\textbf{Brief Document On the Hall C Hodoscopes Calibration}}%replace X with the appropriate number
\author{Carlos Yero} %if necessary, replace with your course title

\maketitle
\noindent The Hall C Scintillaror Hodoscopes consists on four planes (per spectrometer) of scintillator arrays oriented perpendicular
to the beam direction(See Figure \ref{fig:Hodo}). Each spectrometer has two sets of planes, each set oriented along the +X and +Y in the hut coordinate system.
The hodoscopes form the standard HMS/SHMS trigger in Hall C due to the fast signal rise time produced from the scintillating material.
For a thorough discussion of how the trigger is formed, see . . . \\
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.3]{Hodo.png}
  \caption{HMS Hodoscope 1X and 1Y Planes.}
  \label{fig:Hodo}
\end{figure}
When a particle traverses a plane, depending on the trajectory, any paddle could in principle be hit,
the paddle then scintillates light, which propagates to them photomultiplier tubes (PMTs) at the two ends. The PMTs
convert the incident light to photoelectrons in the photocathode. The photoelectrons then are guided through the various dynodes in the PMT, knocking
out more electrons, creating an avalanche of electrons. The electron avalanche then reaches the anode, producing a measurable current signal.
The signal is sent to the Counting Room, where it is processed by the NIM/CAMAC electronics, and ultimately sent to ADCs, and TDCs. At this stage, the raw tdc signal
has multiple unwanted timing contributions which must be subtracted to obtain the true arrival time at the hodoscope plane. The corrected tdc time is the used to determine
the correct particle velocity, $\beta = \frac{v}{c}$. The determination and correction for the additional timing from the raw tdc is the essence of the hodoscope timing
calibration, and will be discussed next.

\section{Discussion on the Hodoscope Timing Corrections}
The general expression for the corrected TDC time for a hodoscope PMT is
\begin{equation}
t_{Corr} = t_{RAW} - t_{TW} - t_{Cable} - t_{prop.} - t_{\lambda} 
\end{equation}
\newpage
The corrected TDC time represents the particle arrival time at the scintillator paddle.
The corrections are summarized as follows (See Figure \ref{fig:Paddle}):
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.5]{HodoPaddle.pdf}
  \caption{Cartoon of individual scintillator paddles to illustrate the various timing corrections applied. (Graph Source: E. Pooser)}
  \label{fig:Paddle}
\end{figure}
\begin{itemize}
\item \textbf{Time-Walk Corrections}, $t_{TW}$: For analog signals arriving at the \textit{Leading Edge Discriminators}
  at a particular time, depending on the signal \textit{amplitude}, the leading edge of the signal is discriminated,
  which causes the dscriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the
  same time. Analog-to-Digital Converters (ADCs), do not have this disadvantage, since they correct for time-walk internally,
  and as a result, the ADC Pulse Time is not correlated with the signal amplitude. To correct for this correlation in the TDCs,
  the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the ADC amplitude. A model
  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time. (See Figure \ref{fig:TWFit}) The function that is currently
  being used in Hall C has the form:
  \begin{equation}
    f_{TW}(a) = c_{1} + \frac{1}{(\frac{a}{TDC_{Thrs.}})^{c_{2}}}
  \end{equation}
  where $a$ is the ADC amplitude,  $TDC_{Thrs}$ is the TDC threshold which is currently set to 120 mV. \newpage
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.35]{1x7-_TWFit.png}
    \caption{Fitted correlation between TDC pulse Time and ADC Pulse Amplitude.}
    \label{fig:TWFit}
  \end{figure}
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.75]{1x7-_TWCorr.pdf}
    \caption{Corrected TDC Time Walk spectrum, where the correlation with Pulse Amplitude has been removed.}
    \label{fig:TWCorr}
  \end{figure}
\newpage
The plot in Figure \ref{fig:TWFit} shows the correlation between TDC Pulse Time and ADC Pulse Amplitude.  The fit parameters, $c_{1}$, TDC Threshold are read in by hcana, where
the time-walk correction is applied to the raw TDC to obtain the corrected tdc time as shown in Figure \ref{fig:TWCorr}.
\item Cable Time Corrections, $t_{Cable}$: This correction takes into account the fact that the analog signal has
  to propagate across signal cables from the PMT all the way into the Counting House electronics rack into the TDC.
  To determine this correction, a correlation between Time-Walk corrected time and hodoscope paddle track position is fitted
  to extract the velocity of propagation across the paddle, and the cable time offset. Figure \ref{fig:Vp} shows the cartoon of a
  horizontal paddle to illustrate how to determine the propagation velocity.
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.5]{Vp.png}
    \caption{Illustration of how the propagation velocity across a paddle is determined.}
    \label{fig:Vp}
\end{figure}
The propagation velocity is determined from the distance and time of the hit from the center of a paddle.
The time is determined by taking half of the time-walk corrected TDC time difference between the two ends of a paddle.
The \textit{half} is to ensure that if the particle hits the edge of the paddle, half of the total propagation
time across the entire paddle is taken to obtain the time from the edge to the center. The hit distance is
determined by extrapolating the distance determined by the Drift Chambers from tracking. The correlation between
time and distance is fitted to extract the propagation velocity and the cable time difference between the two ends. (See Figure \ref{fig:Vp_fit})
The cable time offset parameter is determined for all paddles and the parameter is read by hcana, and added as a correction
factor to the time-walk corrected TDC time. 
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.5]{1x7_Velocity.png}
    \caption{Illustration of how the propagation velocity across a paddle is determined.}
    \label{fig:Vp_fit}
\end{figure}
\item Hodoscope Planes Time Difference Corrections, $t_{\lambda}$: This correction accounts for any additional time difference (other than the particle propagation
  time to travel across the two paddles) between any two distinct scintillator paddles in different hodoscope planes. Six possible combinations between
  the four hodoscope planes are considered when correcting for the time difference between any two of their paddles (See Figure \ref{fig:hod_planes})
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.5]{hodo_planes.pdf}
    \caption{Illustration of all possible time difference combinations that are considered in this correction.}
    \label{fig:hod_planes}
\end{figure}
Consider the time difference difference between the $(i,j)$ plane, $t_{ij}$, where the time of the $i$ plane is
given by
\begin{equation}\label{eq:3}
  t_{i} = \frac{T^{(+)}_{TW} + T^{(-)}_{TW} - 2t_{Cable}}{2} 
\end{equation}
From Eq. \ref{eq:3}, $t_{i}$ is the average Time-Walk and cable time corrected TDC time at both ends of the paddle,
and represents the particle arrival time at the paddle. The time difference between any two paddles in the $(i,j)$
planes can be expressed as
\begin{equation} \label{eq:4}
\begin{split}
  &(t_{i} + \lambda_{i}) - (t_{j} + \lambda_{j}) = \frac{D_{ij}}{v_{c}} \\
  &\lambda_{i} - \lambda_{j} = \frac{D_{ij}}{v_{c}} - (t_{i} - t_{j}) \equiv b_{ij}
\end{split}
\end{equation}
where the $\lambda'$s represent small time perturbations that ideally, should \textit{not} be present, but in
reality they are present and need to be accounted for. In front of the $\lambda'$s there are the coefficinets (+1, -1) for
every possible $i,j$ combination. To better understand how to solve the generalized system of linear equations in
Eq. \ref{eq:4}, consider a single event in the HMS in which a single paddle in every plane is hit. The system of six linear equations
corresponding to such event can then be expressed as
\begin{equation} \label{eq:5}
\begin{split}
  &c_{1,1}\lambda_{1} +  c_{1,2}\lambda_{2} + . . . + c_{1,j}\lambda_{j} + . . . + c_{1,52}\lambda_{52} =  b_{12} \\
  &c_{2,1}\lambda_{1} +  c_{2,2}\lambda_{2} + . . . + c_{2,j}\lambda_{j} + . . . + c_{2,52}\lambda_{52} =  b_{13} \\
  &c_{3,1}\lambda_{1} +  c_{3,2}\lambda_{2} + . . . + c_{3,j}\lambda_{j} + . . . + c_{3,52}\lambda_{52} =  b_{14} \\
  &c_{4,1}\lambda_{1} +  c_{4,2}\lambda_{2} + . . . + c_{4,j}\lambda_{j} + . . . + c_{4,52}\lambda_{52} =  b_{23} \\
  &c_{5,1}\lambda_{1} +  c_{5,2}\lambda_{2} + . . . + c_{5,j}\lambda_{j} + . . . + c_{5,52}\lambda_{52} =  b_{24} \\
  &c_{6,1}\lambda_{1} +  c_{6,2}\lambda_{2} + . . . + c_{6,j}\lambda_{j} + . . . + c_{6,52}\lambda_{52} =  b_{34}
\end{split}
\end{equation}
Or in matrix notation,
\begin{align}
\bf{C^{[\lambda]}}\lambda &= \left[\begin{array}{cccccc}
  c_{1,1} & c_{1,2} & \hdots & c_{1,j} & \hdots & c_{1,52} \\
  c_{2,1} & c_{2,2} & \hdots & c_{2,j} & \hdots & \vdots \\
    \vdots & \vdots & \ddots & \hdots & \hdots & \vdots \\
  c_{i,1} & \vdots & c_{i,j} & \ddots & \hdots & \vdots \\
    \vdots & \vdots & \hdots & \hdots & \ddots & c_{5,52} \\
    c_{6,1} & c_{6,2} & \hdots & \hdots & \hdots & c_{6,52} \\
  \end{array}\right]
\begin{bmatrix}
  \lambda_{1}  \\
  \lambda_{2}  \\
  \vdots \\
  \vdots \\
  \lambda_{j} \\
  \vdots \\
  \lambda_{52}
\end{bmatrix} 
= \begin{bmatrix}
  \vspace{5px}
  b_{12}  \\
  \vspace{5px}
  b_{13}  \\
  \vspace{5px}
  b_{14}  \\
  \vspace{5px}
  b_{23}  \\
  \vspace{5px}
  b_{24}  \\
  \vspace{5px}
  b_{34}  \\
\end{bmatrix}
\end{align}
where the left-hand side is a linear combination of the possible perturbative times in all paddles. The index $j$ in $\lambda_{j}$
represents the absolute paddle number, as there are 52 paddles in total in the HMS. The conversion from relative to absolute paddle is as
follows,
\begin{align*}
  &\text{Plane h1X}: \text{Paddles } 1-16,  \lambda_{j}\rightarrow j:1-16 \\
  &\text{Plane h1Y}: \text{Paddles } 1-10,  \lambda_{j}\rightarrow j:17-26 \\
  &\text{Plane h2X}: \text{Paddles } 1-16,  \lambda_{j}\rightarrow j:27-42 \\
  &\text{Plane h2Y}: \text{Paddles } 1-10,  \lambda_{j}\rightarrow j:43-52 
\end{align*}

Assume for this particular event, that paddles
7, 5, 8 and 6 in planes h1X, h1Y, h2X and h2Y respectively, get hit. At this point, all coefficients except those corresponding to the paddles that
fired will be \textit{zero}. The coefficient matrix has the following non-zero terms
\begin{align*}
  &c_{1,7} = 1, c_{1, 21} = -1 \\
  &c_{2,7} = 1, c_{2, 34} = -1 \\
  &c_{3,7} = 1, c_{3, 48} = -1 \\
  &c_{4,21} = 1, c_{4,34} = -1 \\
  &c_{5,21} = 1, c_{5,48} = -1 \\
  &c_{6,34} = 1, c_{6,48} = -1
\end{align*}

\begin{align}
\bf{C^{[\lambda]}} &= \left[\begin{array}{cccccc}
  \hdots & 1 & \hdots & -1 & \hdots & \hdots \\
  \hdots & 1 & \hdots & \hdots & -1 & \hdots \\
  \hdots & 1 & \hdots & \hdots & \hdots & -1  \\
  \hdots & \hdots & 1 & \hdots & -1 & \hdots \\
  \hdots & \hdots & 1 & \hdots & \hdots & -1 \\
  \hdots & \hdots & \hdots & 1 & \hdots & -1 
  \end{array}\right]
\end{align}
\newpage
To simultaneously solve this system of equations for the $\lambda$'s, one event
is not sufficient since not all paddles will fire, and the majority of the $\lambda$'s
will be zero. One needs to sum each of the elements over sufficient events to fill all
coefficients in the matrix and find a solution to all $\lambda$'s as follows,
\begin{align}
\bf{C^{[\lambda]}}\lambda &= \left[\begin{array}{cccccc}
  \sum\limits_{k} c_{1,1} & \sum\limits_{k}c_{1,2} & \hdots & \sum\limits_{k}c_{1,j} & \hdots & \sum\limits_{k}c_{1,52} \\
  \sum\limits_{k}c_{2,1} & \sum\limits_{k}c_{2,2} & \hdots & \sum\limits_{k}c_{2,j} & \hdots & \vdots \\
    \vdots & \vdots & \ddots & \hdots & \hdots & \vdots \\
  \sum\limits_{k}c_{i,1} & \vdots &  \sum\limits_{k}c_{i,j} & \ddots & \hdots & \vdots \\
    \vdots & \vdots & \hdots & \hdots & \ddots &  \sum\limits_{k}c_{5,52} \\
     \sum\limits_{k}c_{6,1} &  \sum\limits_{k}c_{6,2} & \hdots & \hdots & \hdots &  \sum\limits_{k}c_{6,52} \\
  \end{array}\right]
\begin{bmatrix}
  \lambda_{1}  \\
  \lambda_{2}  \\
  \vdots \\
  \vdots \\
  \lambda_{j} \\
  \vdots \\
  \lambda_{52}
\end{bmatrix} 
= \begin{bmatrix}
  \vspace{5px}
   \sum\limits_{k}b_{12}  \\
  \vspace{5px}
   \sum\limits_{k}b_{13}  \\
  \vspace{5px}
   \sum\limits_{k}b_{14}  \\
  \vspace{5px}
   \sum\limits_{k}b_{23}  \\
  \vspace{5px}
   \sum\limits_{k}b_{24}  \\
  \vspace{5px}
   \sum\limits_{k}b_{34}  \\
\end{bmatrix}
\end{align}
There are various methods to solve a system of linear equations. Some which might
be more numerically stable than others. For this specific case, Single-Value Decomposition (SVD)
method was used. 
% j=7, 21, 34, 48

\item Propagation Time Corrections, $t_{prop.}$: This correction accounts for the propagation
  time across both ends of the scintillator paddle from the particle hit location. The corrections is
  done in the Hall C Analyzer, \textit{hcana}. Some of the geometrical parameters that are used are shown
  in Figure \ref{fig:propTime}. \\
  \begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.48]{propTime_Corr.png}
    \caption{Scintillator paddle illustrating how to apply the propagation time corrections.}
    \label{fig:propTime}
  \end{figure}
  To derive how this correction is done in hcana, let the time-walk and cable length corrected time be
  defined as
  \begin{equation}
    t^{\pm}_{Corr.} = t_{0} + t^{\pm}_{prop.}
  \end{equation}
  The path length from the center of the paddle to the hit can then be defined as
    \begin{align}
      \Delta L &= \frac{1}{2}(t^{(-)}_{Corr.} - t^{(+)}_{Corr.})v_{p} =  \frac{1}{2}(t^{(-)}_{prop.} - t^{(+)}_{prop.})v_{p}
    \end{align}
    The equations used in hcana are
    \begin{align}\label{eq:11}
      t^{(+)}_{Corr.} = t^{(+)}_{Corr.} - (L_{+} - hit)\frac{1}{v_{p}}, \text{ where } t^{(+)}_{prop.}\equiv(L_{+} - hit)\frac{1}{v_{p}} \nonumber \\
      t^{(-)}_{Corr.} = t^{(-)}_{Corr.} - (hit - L_{-})\frac{1}{v_{p}}, \text{ where } t^{(-)}_{prop.}\equiv(hit - L_{-})\frac{1}{v_{p}}       
    \end{align}
    Substituting the definitions from Figure \ref{fig:propTime}  into Eq.\ref{eq:11}, after some algebra, one is able to prove that
    \begin{equation}
      t_{avgCorr} = \frac{1}{2}( t^{(+)}_{Corr.} +  t^{(-)}_{Corr.}) = \frac{1}{2} (t^{(+)}_{TWC_{orr.}} +  t^{(-)}_{TW_{Corr.}})
    \end{equation}
    where the propagation time has been corrected for.
\end{itemize}

\renewcommand{\labelitemi}{$\blacksquare$}

\section{Hodoscope Calibration Procedure}
In this section I will discuss the procedure to perform the hodoscopes calibration
using the new method.
\begin{itemize}
\item Set the flag \texttt{h(p)tofusinginvadc = 0} to NOT use the hodo parameters from the
  previous hodoscope calibration procedure. This flag is found on \texttt{hallc\_replay/PARAM/H(S)MS/HODO/} directory.
\item Replay the raw data file, typically 1-2 M events is required for a good fit to be done.   
\item In the directory \texttt{hallc\_replay/CALIBRATION/(s)hms\_hodo\_calib/}, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkHistos.C(<run\_num>)''} \\
  This script takes as input the ROOTfile replayed and creates another ROOTfile with histogram
  objects that are used to perform the time-walk correction.}
\item To do the time-walk corrections, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkCalib.C(<run\_num>)''}} \\
  This script takes as input the ROOTfile containing the histogram objects produced by the previous
  script.  A parameter file containing the time-walk parameters will be produced at 
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_TWcalib\_runNUM.param}}
  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
  \texttt{(p)hhodo\_TWcalib.param} .
\item Replay the raw data file, once again (1 - 2 M events), with the updated time-walk parameters.
\item In the hodoscopoe calibration directory, run the following code:
  \subitem $\Diamond$ {\texttt{root -l fitHodoCalib.C}}
  The first part of this script performs a linear fit on the time-walk corrected time vs. hodoscope track
  to determine the propagation velocity and the cable time difference across each paddle. The second part of
  this code solves a matrix equation for the $\lambda$ parameters mentioned in the previous section.
  A parameter file containing the time-walk parameters will be produced at
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_Vpcalib\_runNUM.param}} \\
  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
  \texttt{(p)hhodo\_Vpcalib.param} .
\item {Replay the raw data one last time, and check the hodoscope beta distribution. You may have to apply a calorimeter cut (for example, \texttt{(P)H.cal.etracknorm>0.7})}
  A good calibration should have the beta centered at unity. (See Figure \ref{fig:beta})
\end{itemize}
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.7]{hms_betaCompare.pdf}
    \caption{Comparison between HMS $\beta$ distributions using the original and new calibration procedure.}
    \label{fig:beta}
\end{figure}
%HHODO_vPcalib.param, fitHodoCalib.C

% --------------------------------------------------------------
%     You don't have to mess with anything below this line.
% --------------------------------------------------------------

\end{document}

### 2019-06-21 Fellowships/NRC_report/NRC_report/report(1).tex
update

\newcommand{\CLASSINPUTtoptextmargin}{2cm}
\newcommand{\CLASSINPUTbottomtextmargin}{1in}
\documentclass[journal, a4paper]{IEEEtran}

\usepackage{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage{url}
\usepackage[hyperfootnotes=false]{hyperref}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amssymb}
\usepackage{tgtermes}
\usepackage{gensymb}
\usepackage{multirow}
\usepackage[
singlelinecheck=false % <-- important
]{caption}
\usepackage{datetime}

\DeclareGraphicsExtensions{.pdf,.png,.jpg}

\usepackage{epstopdf}

% Your document starts here!
\begin{document}
% Define document title and author
\title{\huge Calibration of the High Momentum Spectrometer Drift Chambers}
\author{Carlos Yero\\March 20, 2017}
\maketitle
\vspace{1mm}
% Write abstract here
\begin{abstract}
The calibration procedure for \textit{horizontal} drift chambers in the High Momentum Spectrometer (HMS) is outlined. The main
objective of this calibration was to produce a time-to-distance map in order to determine the position of
particle tracks from the measured drift times. Using the calibration results, a brief study about drift velocities was
also done in which it was found that they vary from $\sim$ 40-55$\mu$m/ns in regions of approximately uniform electric fields.
Finally, efficiency and residuals on both chambers was investigated and determined each plane to be better than
94\% efficient, with spatial resolutions better than 420 $\mu$m.
\end{abstract}
\section{Introduction}
% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{A}{s} part of the plan to commission the Super HMS (SHMS) at Hall C - Jefferson Lab, the
HMS also needs to be operational for coincidence experiments. The drift chambers are an essential element
of the spectrometer as they are needed for particle tracking and reconstruction. (See Figure \ref{fig:HMS_carriage}) One of the drift chambers
in the HMS had 97 sense wires and 1 field wire damaged from years of exposure to radiation since it was first
installed in the detector stack in 1995 \cite{baker}. The  wires were replaced on Fall 2016 and both chambers
were verified to be operational by performing several cosmic\footnote{Cosmic tests refers to the detection of cosmic rays or highly energetic particles (mainly
protons) originating mostly outside of the solar system.} tests. On March 2017, as part of the Key Performance Parameters (KPP)
neede to be satisfy by Hall C to demonstrate that the SHMS was in operating conditions, data was taken with actual beam in the
Hall. Data with the HMS was also taken and used to calibrate the drift chambers.
\begin{figure}[h]
  \centering
  \includegraphics[width=2.8in, height=1.8in]{HMS_Carriage.png}
  \caption{HMS carriage showing the magnet elements (Quadrupoles ($Q_{i}$), Dipole (D)). The detector elements are
  after the 25$^{\circ}$ bend, where DC1 and DC2 denotes the drift chamber
  packages 1 and 2.}
  \label{fig:HMS_carriage}
\end{figure}
% Main Part
\section{Principle of Operation}
Each drift chamber consists of 6 planes (X, Y, U, V, Y', X'), where the X(X') are orthogonal to Y(Y') planes, and U and V are
tilted 15\degree  relative to X(X'). (See Figure \ref{fig:wireplanes})
\begin{figure}[h]
  \centering
  \includegraphics[width=2.8in, height=1.8in]{wire_planes.png}
  \caption{Schematic of drift chamber planes. Figure courtesy of C. Armstrong.}
  \label{fig:wireplanes}
\end{figure}
Each plane consists of an array of alternaring field and sense wires\footnote{Total sense wires per plane: X,X'-113, Y,Y'-52, U,V-107} (0.5 cm apart) surrounded by
two arrays of field wires so that each sense wire is surrounded by 8 field wires, forming a cell. (See Figure \ref{fig:wire_cell})
\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in, height=3.0in]{wire_cell.png}
  \caption{Schematics of a single cell in a drift chamber plane. Figure
  courtesy of G. Niculescu and D. Abbot.}
  \label{fig:wire_cell}
\end{figure}
The field wires are kept at a negative potential while the sense wires are grounded (0 V). Due to
the potential difference between the field and sense wires, an electric field is established which causes
free electrons from ionized gas atoms and molecules of
the gas mixture\footnote{Drift chambers are filled with a gas mixture mainly to make the ions drift velocity
as uniform as possible.} to drift towards the sense wires producing a measurable signal.
The sense wire signals are pre-amplified and read by 16-channel input discriminators which produce logic signals that lead into Time-to-Digital
Converters (TDCs) by twisted pair ribbon cables\cite{meekins}. The TDCs registers the total travel time
of the signal since it was created by the passing particle. This time is compared to the surveyed time it would have taken the signal to propagate across
the sense wire, through the ribbon cable into the TDC if the particle would have passed through the sense wire. The time difference
is known as the \textit{drift time}, or the time it takes the free electrons to drift towards the sense wire.
 Mathematically, the drift time can be expressed as,
\begin{equation}
t_{D} = (t_{meas.}-t_{REF}) - [\underbrace{(t_{wire} + t_{cable})}_{t'} - t_{REF}]
\end{equation}
where $t_{meas.}$ is the measured time by the TDC, and $t'$ is the time it takes the signal to propagate
across the sense wire and through the cable into the TDC if the track would have passed through the sense wire. These times
are measured relative to a reference time\footnote{Reference time (trigger) is defined based on certain conditions that
a signal must pass for it to be considered as a physical event. In the HMS in particular, it was defined as a 3/4
hodoscope plane coincidence - or the signal must have been detected in at least 3/4 hodoscopoe planes within a
time window for it to be considered a true event (or trigger).} $t_{REF}$, used by the TDCs in Common Stop Mode (analogous to
a stopwatch). \\
\indent For a charged particle that traverses the drift chamber, only certain sense wires will fire.
If a wire, say in the X-plane fires, one does not know if the particle passed the left or right side of the chamber
relative to the wire. By including the X'-plane, the left-right ambiguity is removed since the particle will fire a wire in X' which
allows one to determine the x-coordinate of the track. Similarly, for the Y (Y') planes, the y-coordinate of the track is
determined and the U (V) planes provide angle information about the track.\\
\indent A coarse track reconstruction can be done with only the knowledge of the wires that fire from a physics
event. Knowing the associated drift times of the wires that were hit, however, allows for a more precise track reconstruction,
as the drift time can be converted to a drift distance from the determination of time to distance maps from calibration. The
drift distances can be added as fine corrections to the coarse track reconstruction.
\section{Calibration Procedure}
\noindent For many events illuminating all cells in any give plane, one obtains a drift time distribution
for each sense wire which are then averaged over the entire plane to form a drift time distribution per plane.(see Figure \ref{fig:hdc2y1_time})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.8in, height=2.3in]{hdc2y1_time.pdf}
  \caption{Averaged and single wire drift time spectra in the Y-plane of drift chamber 2.}
  \label{fig:hdc2y1_time}
\end{figure}

Associated with each drift time spectra is a quantity called $``t_{0}"$. The $``t_{0}"$ corresponds to the
location in the histogram where the ionized particle comes in contact with the wire. If its value is anything other
than zero nanoseconds (0 ns), it is interpreted as the value by which the drift time must be shifted in order to
align the $``t_{0}"$ with 0 ns. All subsequent times in each drift time spectra are measured relative to this time.\\
\indent The $``t_{0}"$ for each plane is determined by calculating the $``t_{0}"$ for individual wires in each plane and taking a
weighted average. The $``t_{0}"$ for individual sense wires is determined by a linear fit of the wire drift time spectra at around 20\% of the peak
$\pm \Delta t$ for each sense wire, where $\Delta t$ is the fit range. The linear fit is then extrapolated to the
horizontal axis (drift time), and this extrapolated value is defined as $``t_{0}"$. (See Figure \ref{fig:wire_fit})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.8in, height=2.3in]{hdc2y1_w14_fit.pdf}
  \caption{Linear fit to drift time of sense wire 14 in the Y-plane of the second drift chamber. The fit is extrapolated to the
  x-axis to determine $``t_{0}"$. }
  \label{fig:wire_fit}
\end{figure} \\
Less than a percent of the total wires in the second drift chamber were found dead\footnote{Wires with no registered hits, except noise from the electronics, are defined as dead.}, while other wires had
low statistics due to the biased direction of the particles entering the detector stack. This effect can be observed
from the wire hitmaps in Figure \ref{fig:hdc2y1_hitmap}.
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.8in, height=2.3in]{hdc2y1_wiremap.pdf}
  \caption{Wire map showing the number of entries (hits from physics events) received by each sense wire in Y-plane of
  the second drift chamber.}
  \label{fig:hdc2y1_hitmap}
\end{figure}
The central wire from the Y-plane has the highest number of entries and fall exponentially for wires further from the
center. This effect is due to the spectrometer magnets focusing the particles that enter the detector stack towards
the center (focal plane) of the two chambers.
The calibration run taken had enough statistics, that even at the edge wires had sufficient events for a linear
fit to be made. Dead wires found in other planes were excluded from the fit, as they would have been outliers in
the data, causing a shift in the weighted average. The weighted average for the Y-plane of drift chamber 2 is shown
in Figure \ref{fig:hdc2y1_wght_avg}.
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.8in, height=2.3in]{hdc2y1_wght_avg.pdf}
  \caption{Weighted average of the $``t_{0}"$ offset for all wires in the Y-plane of drift chamber 2.}
  \label{fig:hdc2y1_wght_avg}
\end{figure}\\
The weighted average over all wires is assigned as the $``t_{0}"$ of the plane. When this procedure is done for all planes
in both chambers, the drift times should be aligned at $t_{0}$=0 ns. (See Figure \ref{fig:t0_corr})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.6in, height=2.7in]{t0_corr_times.pdf}
  \caption{Corrected drift time spectra for all planes in both drift chambers.}
  \label{fig:t0_corr}
\end{figure}\\
\indent To determine the drift distances from drift time spectra, it is assumed that the
drift distance is uniformly distributed across the cell. This assumption is based on the fact that
a cell is uniformly illuminated with particles, and the ions have an approximately uniform drift velocity
which implies there should be no preferred drift distance for any ionized charge.
Mathematically, the drift distance is calculated as follows,
\begin{equation}\label{eq:2}
d_{drift}(\tau = T) = \frac{\Delta}{2} \frac{\int_{t_{0}}^{T<t_{max}}F(\tau)d\tau}{\int_{t_{0}}^{t_{max}}F(\tau)d\tau}
\end{equation}
where $\Delta$ is the cell width and $F(\tau)$ is the drift time distribution integrated from $t_{0} = 0$ ns to some arbitrary time $T<t_{max}$
where $t_{max}$ is maximum drift time within a cell. The normalization constant in front of the integral is the maximum
drift distance (0.5 cm). In the limiting cases of Eq.\ref{eq:2}, the drift distance becomes
\begin{equation}
  d_{drift} =\begin{cases}
               0 \text{ cm}, & \tau = 0 \text{ ns} \\
               0.5 \text{ cm}, & \tau = t_{max}
            \end{cases}
\end{equation}
which is the expected drift distance at the sense wire ($\tau=0 $ns) and at the edges of the cell ($\tau = t_{max}$). \\
\indent Due to the finite resolution of the TDCs and other factors involved, the drift times are not determined to infinite precision and
the integrals in Eq.\ref{eq:2} become a sum over a finite bin width,
\begin{align*}
\int_{\tau}F(\tau)d\tau \longrightarrow \sum_{bin(\tau)} \underbrace{F(\tau)}_{binContent}\cdot\underbrace{\Delta\tau}_{binWidth}
\end{align*}
Re-writing the ratio of integrals Eq.\ref{eq:2} in terms of the finite sums, one obtains
\begin{equation}\label{eq:4}
\frac{\sum\limits_{bin(t_{0})}^{bin(t_{0}+T)}F(\tau)\Delta\tau}{\sum\limits_{bin(t_{0})}^{bin(t_{0}+t_{max})}F(\tau)\Delta\tau} \rightarrow \boxed{\frac{1}{N_{tot.}}\sum\limits_{bin(t_{0})}^{bin(t_{0}+T)}F(\tau)}
\end{equation}
The ratio in Eq.\ref{eq:4} are the lookup values used to convert drift time to distance for an arbitrary drift time. The
numerator represents the sum of all bin contents up to a drift time $T$, and the denominator represents the sum over the
bin contents of all drift times up to $t_{max} $, in a given plane. The bin width, $\Delta\tau$,
is a constant (2 ns) during the sum, therefore it is cancelled, which simplifies the equation as a ratio of the sum of bin contents (up to some drift time) and
the sum over all bin contents (up to a maximum, $t_{max}$), $N_{tot}$.  \\
\indent The results of this calibration are per plane look-up tables that map any given drift time to a drift distance in
that plane. The drift distance for the Y-plane of drift chamber 2 is shown in Figure \ref{fig:hdc_dist}.
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.6in, height=2.7in]{hdc_distance.png}
  \caption{Corrected drift distance spectra for all planes in both drift chambers.}
  \label{fig:hdc_dist}
\end{figure}
As expected, the drift distances for all planes are uniformly distributed across the cell width. A minor problem
encountered during the calibration procedure was that for some of the calculated drift distances, there was either
a large and small number of counts at the edges (0 or 0.5 cm) whereas in the central region ($\sim$ 0.1-0.3cm), the counts
were uniformly distributed.(See Figure \ref{fig:hdc2y1_uncorr})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.6in, height=2.7in]{hdc_2y1_uncorr.pdf}
  \caption{Uncorrected drift distance spectrum.}
  \label{fig:hdc2y1_uncorr}
\end{figure}\\
\indent The weighted $t_{0}$'s determined from calibration had to be manually offset in order to correct
for events accumulating at the edges. This is due to a significant variation ($\sim$ 5-10 ns) in the $t_{0}$'s for groups of wires
in a plane, which affects the weighted average for that plane. To overcome this difficulty, the $t_{0}-$correction
must be applied to individual sense wires rather than taking a weighted average. The procedure to include individual wire
$t_{0}$-offsets is currently in progress.
\section{Drift Velocity Calculation}
Drift velocities of free electrons are sensitive to the gas mixture used in
the chamber as well as the high voltage applied to field wires, as they govern the shape of the electric field that will cause ions to drift. A typical graph
of drift velocities as a function of field strength for various Argon/Ethane mixtures.
mixtures is shown in Figure \ref{fig:drift_vel_vs_Efield}.
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.2in, height=2.3in]{drift_vel_vs_Efield.png}
  \caption{Drift velocity variation with electric field. Figure courtesy of PHOENIX at Brookhaven National Lab (BNL).}
  \label{fig:drift_vel_vs_Efield}
\end{figure}\\
During the calibration run, the HMS drift chambers operated at a 50:50 mixture by volume of Argon/Ethane. The drift velocities
were determined by taking the ratio of drift distance to drift time per plane. The correlation shows a linear relationship
between distance and time indicating a uniform drift velocity throghout all cells conforming a plane. (See Figure \ref{fig:drift_velocity})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.6in, height=2.7in]{drift_velocity.png}
  \caption{Correlation between drift distance and drift time for both drift chambers.}
  \label{fig:drift_velocity}
\end{figure}\\
The Y'-plane in chamber 2 shows a significant deviation from the rest. This could indicate a possible variation in the
high voltage applied to the field wires in that plane which leads to variations in the electric field causing variations
in drift velocities. (See Figures \ref{fig:drift_vel_dc1} and \ref{fig:drift_vel_dc2})
\begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.4\textwidth} % width of left subfigure
		\includegraphics[width=\textwidth]{drift_vel_dc1.pdf}
		\caption{Drift velocity vs. drift distance for all planes in chamber 1.} % subcaption
    \label{fig:drift_vel_dc1}
	\end{subfigure}
	\vspace{1em} % here you can insert horizontal or vertical space
	\begin{subfigure}{0.4\textwidth} % width of right subfigure
		\includegraphics[width=\textwidth]{drift_vel_dc2.pdf}
		\caption{Drift velocity vs. drift distance for all planes in chamber 2.} % subcaption
    \label{fig:drift_vel_dc2}
  \end{subfigure}
	\caption{Drift velocity variation as a function of drift distance for all planes in both chambers.} % caption for whole figure
  \label{fig:drift_vel}
\end{figure}\\
The linear correlation that exists between drift time and distance in Figure \ref{fig:drift_velocity} shows
the drift velocity is mostly constant throughout all planes. The small variations of drift velocity with drift
distance observed in Figure \ref{fig:drift_vel}, however, shows that the drift velocity is not truly a constant,
but varies by a few microns/ns far from the cell edges or center (region II). By performing a linear fit to
the time to distance correlation in steps of 2 ns intervals, the small variations in drift velocity become apparent. The slope
of the linear fit (drift velocity) was plotted versus the drift distance as shown in Figure \ref{fig:drift_vel}.
From Figure \ref{fig:drift_vel}, large variations in the drift velocity can also be observed  at the edges (region III)
and center (region I) of a cell. This effect is due to the non-uniformity of the electric field in these regions.

\section{Drift Chamber Efficiencies and Residuals}
The per plane efficciencies were determined for all planes. The efficinecy of any given plane
in a chamber is defined as the ratio of the number of hits that were detected by the plane to the number of hits that
\textit{should} have been detected by that plane.
Where a \textit{hit} is defined as a detectable signal in the chamber from ionized charges produced by the passage of a
particle. Mathematically, the efficiency of the $i^{th}$ plane is given by \\
\begin{equation*}
\epsilon_{i} = \frac{\# \text{ hits that were detected by the $i^{th}$ plane}}{\# \text{ hits that \textit{should} have been detected by the $i^{th}$ plane}}
\end{equation*}
with the condition that the hit was also detected by the remaining five planes in the chamber. The
efficiencies of both chambers are summarized in Table \ref{tab:eff}.
\begin{table}[!h]
  \scalebox{0.8} {
\begin{tabular}{ |l|l|l| }
\hline
\multicolumn{3}{ |c| }{\textbf{HMS Drift Chamber Efficiencies}} \\
\hline
\textbf{Plane} & \textbf{Chamber 1} (\%) & \textbf{Chamber 2} (\%) \\ \hline
\multirow{6}{*}{}
X  & 95.8 & 99.4  \\ \hline
Y  & 98.7 & 99.7  \\ \hline
U  & 97.7 & 96.6  \\ \hline
V  & 96.5 & 97.7  \\ \hline
Y' & 99.0 & 97.7  \\ \hline
X' & 94.9 & 97.2  \\ \hline
\end{tabular}
}
\caption{Drift chamber plane efficiencies}
\label{tab:eff}
\end{table}\\
\indent The best way to determine the drift chamber performance is by measuring the spatial resolution, or how
well it can measure the position of particle tracks. This measurement is done through the determination of per plane
residuals. For a particle traversing at least 4 planes of the chamber, a collection of space-points (X,Y) is measured based on the
wires that fired. The space points are fitted with a straight line such as to minimize the chi-square, and obtain a best
fit. The line fit is then compared to the meausured space-point from the plane wires that fired, and the difference is called the \textit{residual}
for that plane. The residuals are calculated on an event by event basis, and should be centered around zero. (See Figure \ref{fig:hdc1y1_residual})
\begin{figure}[!ht]
  \centering
  \includegraphics[width=3.6in, height=2.7in]{hdc1y1_residuals.pdf}
  \caption{Residuals for the Y-plane in chamber 1. The Full Width at Half Maximum (FWHM or $\sigma$)  is representative the
  spatial resolution.}
  \label{fig:hdc1y1_residual}
\end{figure}\\
A gaussian fit was done for all planes in both chambers to extract the space resolution of the chambers. The fit results are
summarized in Table \ref{tab:res}
\begin{table}[!h]
\scalebox{0.8} {
\begin{tabular}{ |l|l|l| }
\hline
\multicolumn{3}{ |c| }{\textbf{HMS Drift Chamber Residuals}} \\
\hline
\textbf{Plane} & \textbf{Chamber 1}, $\sigma(\mu m)$ & \textbf{Chamber 2}, $\sigma(\mu m)$ \\ \hline
\multirow{6}{*}{}
X & 416$\pm$1.69 & 388$\pm$1.60 \\ \hline
Y & 360$\pm$1.18 & 408$\pm$1.22 \\ \hline
U & 361$\pm$1.29 & 327$\pm$1.27 \\ \hline
V & 382$\pm$1.47 & 323$\pm$1.28 \\ \hline
Y'& 383$\pm$1.31 & 391$\pm$1.16 \\ \hline
X'& 419$\pm$1.63 & 384$\pm$1.55 \\ \hline
\end{tabular}
}
\caption{Drift chamber plane residuals}
\label{tab:res}
\end{table}

\section{Summary}
This report has outlined the steps taken to calibrate the HMS drift chambers using data taken on March 2017. The outline
also covered some of the difficulties encountered in the calibration procedure, and the steps taken to overcome them. The effects
of the gas mixture and applied high voltage on the drift velocities was also briefly discussed. Finally, two
performance criterions (efficiencies and residuals) used to describe the performance of the drift chambers were investigated. The
efficiencies described how well were the chambers able to detect hits produced by the passage of a particle. The residuals described
how well does the measured particle position in each plane compare to the best track fit through all six planes in each chamber.

%\clearpage
\bibliography{report}
\bibliographystyle{acm}

% Your document ends here!
\end{document}

### 2019-06-21 Fellowships/NRC_report/NRC_report/report.tex
update

--- 2019-06-21 Fellowships/NRC_report/NRC_report/report(1).tex
@@
-\newcommand{\CLASSINPUTtoptextmargin}{2cm}
-\newcommand{\CLASSINPUTbottomtextmargin}{1in}
+\newcommand{\CLASSINPUTtoptextmargin}{1.5cm}
+\newcommand{\CLASSINPUTbottomtextmargin}{1.5cm}
 \documentclass[journal, a4paper]{IEEEtran}
@@
 % Define document title and author
-\title{\huge Calibration of the High Momentum Spectrometer Drift Chambers}
-\author{Carlos Yero\\March 20, 2017}
+\title{\Huge Calibration of the High Momentum Spectrometer Drift Chambers}
+\author{Carlos Yero\\March 22, 2017}
 \maketitle
@@
 protons) originating mostly outside of the solar system.} tests. On March 2017, as part of the Key Performance Parameters (KPP)
-neede to be satisfy by Hall C to demonstrate that the SHMS was in operating conditions, data was taken with actual beam in the
+needed to be satisfy by Hall C to demonstrate that the SHMS was in operating conditions, data was taken with actual beam in the
 Hall. Data with the HMS was also taken and used to calibrate the drift chambers.
@@
 the center (focal plane) of the two chambers.
-The calibration run taken had enough statistics, that even at the edge wires had sufficient events for a linear
+The calibration run taken had enough statistics, that even at the edge, wires had sufficient events for a linear
 fit to be made. Dead wires found in other planes were excluded from the fit, as they would have been outliers in
@@
 \end{figure}\\
-The weighted average over all wires is assigned as the $``t_{0}"$ of the plane. When this procedure is done for all planes
+\indent The weighted average over all wires is assigned as the $``t_{0}"$ of the plane. When this procedure is done for all planes
 in both chambers, the drift times should be aligned at $t_{0}$=0 ns. (See Figure \ref{fig:t0_corr})
@@
 \begin{equation}\label{eq:2}
-d_{drift}(\tau = T) = \frac{\Delta}{2} \frac{\int_{t_{0}}^{T<t_{max}}F(\tau)d\tau}{\int_{t_{0}}^{t_{max}}F(\tau)d\tau}
+d_{drift}(\tau = T) = \frac{\Delta}{2} \frac{\int_{t_{0}}^{T\leq t_{max}}F(\tau)d\tau}{\int_{t_{0}}^{t_{max}}F(\tau)d\tau}
 \end{equation}
@@
 \section{Drift Velocity Calculation}
-Drift velocities of free electrons are sensitive to the gas mixture used in
+\noindent Drift velocities of free electrons are sensitive to the gas mixture used in
 the chamber as well as the high voltage applied to field wires, as they govern the shape of the electric field that will cause ions to drift. A typical graph
@@
 \end{figure}\\
-During the calibration run, the HMS drift chambers operated at a 50:50 mixture by volume of Argon/Ethane. The drift velocities
+\indent During the calibration run, the HMS drift chambers operated at a 50:50 mixture by volume of Argon/Ethane. The drift velocities
 were determined by taking the ratio of drift distance to drift time per plane. The correlation shows a linear relationship
@@
 \end{figure}\\
-The Y'-plane in chamber 2 shows a significant deviation from the rest. This could indicate a possible variation in the
+\indent The Y'-plane in chamber 2 shows a significant deviation from the rest. This could indicate a possible variation in the
 high voltage applied to the field wires in that plane which leads to variations in the electric field causing variations
@@
 \end{figure}\\
-The linear correlation that exists between drift time and distance in Figure \ref{fig:drift_velocity} shows
+\indent The linear correlation that exists between drift time and distance in Figure \ref{fig:drift_velocity} shows
 the drift velocity is mostly constant throughout all planes. The small variations of drift velocity with drift
@@
 \section{Drift Chamber Efficiencies and Residuals}
-The per plane efficciencies were determined for all planes. The efficinecy of any given plane
+\noindent The per plane efficciencies were determined for all planes. The efficinecy of any given plane
 in a chamber is defined as the ratio of the number of hits that were detected by the plane to the number of hits that
@@
 \end{figure}\\
-A gaussian fit was done for all planes in both chambers to extract the space resolution of the chambers. The fit results are
+\indent A gaussian fit was done for all planes in both chambers to extract the space resolution of the chambers. The fit results are
 summarized in Table \ref{tab:res}
@@
 \label{tab:res}
-\end{table}
+\end{table}\\
+The residuals determined in Table \ref{tab:res} include contributions from the residuals of the other five planes in each chamber \cite{baker}.
+From fitted curve in Figure \ref{fig:hdc1y1_residual}, the resolutions of the remaining five planes were added in quadrature.
+In general, the resolution of the $i^{th}$ plane in each chamber can determined by the following equation
+\begin{equation}
+\sigma^{2}_{i} = \sigma^{2}_{1} +\sigma^{2}_{2} +\sigma^{2}_{3} +\sigma^{2}_{4} +\sigma^{2}_{5} = 5\sigma^{2}  
+\end{equation}
+since it was assumed that the other five planes have equal contributions to the
+residual of the sixth plane. 
+The per plane residuals can then be determined by dividing the residual determined from the fit ($\sigma_{i}^{2}$) by 5, and taking the square root.
+For example, the intrinsic resolution of the V-plane in chamber 1 would be $\sigma_{V}=170.8\pm0.657 \mu$m.
+The intrinsic resolutions per plane are summarized in Table \ref{tab:res2}.
+\begin{table}[!h]
+\scalebox{0.8} {
+\begin{tabular}{ |l|l|l| }
+\hline
+\multicolumn{3}{ |c| }{\textbf{HMS Drift Chamber Intrinsic Resolutions}} \\
+\hline
+\textbf{Plane} & \textbf{Chamber 1}, $\sigma(\mu m)$ & \textbf{Chamber 2}, $\sigma(\mu m)$ \\ \hline
+\multirow{6}{*}{}
+X & 186$\pm$0.755 & 173.5$\pm$0.715 \\ \hline
+Y & 160.9$\pm$0.527 & 182.4$\pm$0.545 \\ \hline
+U & 161.4$\pm$0.576 & 146.2$\pm$0.567 \\ \hline
+V & 170.8$\pm$0.657 & 144.4$\pm$0.572 \\ \hline
+Y'& 171.2$\pm$0.585 & 174.8$\pm$0.518 \\ \hline
+X'& 187.3$\pm$0.728 & 171.7$\pm$0.693 \\ \hline
+\end{tabular}
+}
+\caption{Drift chamber intrincis resolutions per plane}
+\label{tab:res2}
+\end{table}\\
 
 \section{Summary}
-This report has outlined the steps taken to calibrate the HMS drift chambers using data taken on March 2017. The outline
+\noindent This report has outlined the steps taken to calibrate the HMS drift chambers using data taken on March 2017. The outline
 also covered some of the difficulties encountered in the calibration procedure, and the steps taken to overcome them. The effects

### 2019-06-21 Fellowships/NRF_Application/RESUME/resume_updated.tex
update

% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage{wasysym}
\usepackage{ marvosym }
\usepackage{csquotes}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Carlos Yero}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:

\address{{\bf Work Address} \\  12006 Rattley Road  \\ Newport News, VA 23606\\
        (786) 387-8667}

\begin{resume}

%\section{OBJECTIVE}  
%     A post-doctoral position in the field of Experimental Nuclear Physics 
%     with emphasis on NIM (Nuclear Instrumentation Modules) and CAMAC (Computer
%     Automated Measurement and Control) data-acquisition system.

\section{\footnotesize EDUCATION} Ph.D, Physics Expected: December, 2019  \\
                                  Florida International University, Miami, FL \\ 
                                  Research Topic:\hspace{1mm}\enquote{Deuteron Electro-Disintegration at Very High Missing Momenta} \\
                                  Major Advisor: Dr. Werner Boeglin

 Magna CUM Laude B.S., Physics (2014)  \\

                %GPA: 3.81/4.0 \\

 \section{\footnotesize RESEARCH\\EXPERIENCE}      {\bf Florida International University, Miami, FL}

                 \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Graduate Research} &   August 2014 - present 
                \end{ncolumn}
                \vspace{1mm}
                \begin{itemize}

               \item  Currently working on hardware as part of Hall C 12 GeV Upgrade. Specifically, on setting up electronics for various detectors in the High Momentum Spectrometer (HMS) arm. 
              Future plans on setting up a coincidence trigger between the two spectrometer arms, HMS and Super HMS.

              \item  Analyzed strangeness photoproduction data for Jefferson Lab, Hall B g12 Experiment. The analysis focused on extraction of
              polarization observables from $\gamma$p $\rightarrow$ K$^{*}$$\Lambda$ reaction.

  \end{itemize}

                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Undergraduate Research}     &      January 2013 - April 2014 
                \vspace{5mm}
                \end{ncolumn}\begin{itemize}
\item Polished and tested scintillator bars for Jefferson Lab, Hall D Start Counter 
 \end{itemize}

 \section{\footnotesize TEACHING\\EXPERIENCE} {\bf Florida International University, Miami, FL}

         \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Recitations} &   August 2015 - April 2016 
                \end{ncolumn}
                \vspace{1mm}

                \begin{itemize}

                \item  Two semesters of Physics I and II teaching assistant, which focused on problem-solving techniques that 
                      complement the lectures.

                \end{itemize}

                 \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Introductory Physics Labs} &   August 2015 - April 2016 
                \end{ncolumn}
                \vspace{1mm}

                  \begin{itemize}

                  \item Two semesters of teaching Physics I and II Laboratory, 
                        in which students develop and strengthen physics 
                        concepts imparted in lectures as well as critical thinking skills.

                  \end{itemize}

 \section{\footnotesize PRESENTATIONS}
\textit{\enquote{Deuteron Electro-Disintegration at Very High Missing Momenta}}, Hampton University
		Graduate Studies (HUGS) Program, NewportNews, VA, June 2016.

\section{\footnotesize SKILLS} Operating Systems: Microsoft Windows Vista/7 and UNIX-Linux \\  
                  Programming Languages: Python and C++  \\
                  Bilingual on English and Spanish

\newpage
\section{REFERENCES}              Dr. Werner U. Boeglin (Major Advisor) \\
                                  Department of Physics \\
                                  Florida International University \\
                                  Miami, FL 33125 \\
                                 \Email \hspace{0.5mm} \href{mailto:boeglinw@fiu.edu}{boeglinw@fiu.edu} \\                           
                                 \phone \hspace{0.5mm} (305) 348-1711

                                  Dr. Joerg Reinhold (Professor) \\
                                  Department of Physics \\
                                  Florida International University \\
                                  Miami, FL 33125 \\
                                 \Email \hspace{0.5mm} \href{mailto:reinhold@fiu.edu}{reinhold@fiu.edu} \\                           
                                 \phone \hspace{0.5mm} (305) 348-6422

                                  Dr. Mark Jones (JLab Staff Scientist) \\
                                  CEBAF Center - Hall C \\
                                  Thomas Jefferson National Laboratory \\
                                  Newport News, VA 23606 \\
                                 \Email \hspace{0.5mm} \href{mailto:jones@jlab.org}{jones@jlab.org} \\                           
                                 \phone \hspace{0.5mm} (757) 269-7733                               
\end{resume} 
\end{document}

### 2019-06-21 Fellowships/NRF_Application/proposal/proposal.tex
update

\documentclass[8pt, twocolumn]{article}

\usepackage{url}
\usepackage[hyperfootnotes=false]{hyperref}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tgtermes}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

\usepackage{epstopdf}

\begin{document}
\title{Deuteron Electro-Disintegration at Very High Missing Momenta}
\author{Carlos Yero \\Major Advisor: Dr. Werner Boeglin}
\date{October 2016}
\maketitle

\section{Motivation} 
The deuteron ($^{2}$H) was discovered in 1931 by Harold Urey, and
it remained a mystery until the discovery of the neutron by 
James Chadwick the following year \cite{boeglin1}. Since then, the deuteron 
has been under intensive research in an attempt to understand 
what binds the atomic nucleus. Being a simple $np$ bound 
state, the deuteron serves as a starting point to study the
strong nuclear force at the subfermi level which is currently
not well understood. At such small internucleon distances 
the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which 
the interacting nucleon pair begins to overlap. The overlap is 
directly related to two-nucleon short range correlations (SRC) observed in $A\geq2$
nuclei \cite{boeglin3}. Short-distance studies of the deuteron are
also important in determining whether or to what extent the
description of nuclei in terms of nucleon/meson degrees of 
freedom must be supplemented by the inclusion of explicit
quark effects \cite{boeglin4}. \\   
\indent In nuclear structure studies in general, electron-nucleon scattering serves as the most valuable 
tool since the interaction is described by Quantum Electro-Dynamics (QED), which is 
well-understood and capable of making accurate predictions. Electron scattering experiments can 
be separated into inclusive or exclusive scattering experiments. In the first of these, only the electron is 
detected in the final state (single-arm experiments), and so one studies the nucleus in question by
integrating over all possible final states \cite{boeglin2}. In the exclusive type, one or more 
particles are detected in coincidence with the scattered electron which allows one to investigate 
properties unique to the specific reaction in question. In deuteron electro-disintegration, for example,
one detects the scattered electron in coincidence with a proton and the missing neutron is 
reconstructed from four-momentum conservation. This reaction proves to be the most direct way of probing the 
internal structure of the deuteron since it is possible to deduce the internal momentum of the nucleons
from the neutron missing momentum. \\ 
\indent With the 12 GeV Upgrade at Jefferson Lab, the short-range ($\leq$ 1 fm) structure of the deuteron will become experimentally 
accessible via data on the deuteron wavefunction beyond relative internal momenta of 400 MeV/c.
At such high energies, one will be able to probe if effects due to 
Quantum Chromodynamics (QCD) start playing a more significant role \cite{boeglin3}. 
\section{Theoretical\hspace{1.5mm}Framework\hspace{1.5mm}of D(e,e'p)n}
Deuteron electro-disintegration can be pictorially described by a Feynmann diagram 
(See Figure \ref{fig:Figure1})
\begin{figure}[h]
  \centering
  \includegraphics[width=2.8in, height=1.8in]{feynmann.pdf}
  \caption{Feynmann diagram of deuteron electro-disintegration}
  \label{fig:Figure1}
\end{figure}
\noindent where the incoming electron interacts with the stationary deuteron to first order approximation via the exchange of a virtual
photon. Given the relatively weak coupling constant for this process, higher order Feynmann diagrams involving multiple photon exchanges 
may be neglected. The interaction of the virtual photon with the deuteron is best described by the general unpolarized (e,e'p) cross section,\cite{boeglin2}
\begin{equation} \label{eq:1}
\begin{aligned}
&\frac{d^{6}\sigma}{d\omega d\Omega_{e}dT_{p}d\Omega_{p}} = \sigma_{Mott}(v_{L}R_{L}+v_{T}R_{T}+ \\
&v_{LT}R_{LT}\cos\phi+v_{TT}R_{TT}\cos 2\phi)
\end{aligned}
\end{equation}
where $\sigma_{Mott}$ is the Mott cross section describing electron scattering off an infinitely massive,
spinless point charge. The quantities ($v_{i}, v_{ij}$) are dependent on electron kinematics (i.e., q, $Q^{2}$, $\theta_{e}$) 
and the functions ($R_{i}, R_{ij}$) are nuclear response functions and depend on nuclear charge and
current density operators \cite{hari}. \\
\indent In the simplest approximation, the virtual photon couples to the proton which is ejected
from the nucleus without further interaction with the recoiling nucleus which carries a momentum $\mathbf{p_{m}}=-\mathbf{p_{i,p}}$. Both final state proton and
neutron are assumed to be plane waves (free particles), hence the name Plane Wave Impulse Approximation (PWIA). (See Figure \ref{fig:Figure2}) 
\begin{figure}[h]
  \centering
  \includegraphics[width=1.5in, height=1in]{PWIA.pdf}
  \caption{Feynmann diagram for PWIA, where the proton(red) is knocked by the photon, and the
neutron(blue) scatters as a spectator}
  \label{fig:Figure2}
\end{figure} \\  
\noindent From the PWIA assumptions, the general (e,e'p) cross section (See Eq.\ref{eq:1}) can be factorized into
\begin{equation} \label{eq:2}
\begin{aligned}
\sigma_{exp}\equiv\frac{d^{6}\sigma}{d\omega d\Omega_{e}dT_{p}d\Omega_{p}} = K \sigma_{ep} S(E_{m}, p_{m}) 
\end{aligned}
\end{equation}
where $K$ is a kinematic factor, $\sigma_{ep}$ describes the elementary electron-proton cross section
for electron scattering off a bound proton, and $S(E_{m},p_{m})$ is a spectral function which
can be interpreted as the probability of finding a recoiling nucleon with missing energy and 
momentum \cite{hari}. \\
%\indent In addition to the PWIA, the virtual photon may also couple to the neutron. This process, known as the
%Plane Wave Born Approximation (PWBA), is enough to break factorization of the (e,e'p) cross section 
%provided the neutron carries a significant portion of the transferred energy and momentum comparable to that of the proton.\\
\indent In reality, the final state particles undergo subsequent interactions resulting in re-scattering of the proton and neutron.
This process is known as Final State Interactions (FSI) (See Figure \ref{fig:Figure3}) and has been shown to have a significant contribution
to the experimental cross section at high missing momenta (See Figure \ref{fig:Figure7}), therefore one cannot be confident that at
large missing momenta, the high momentum component of the deuteron will be probed \cite{ibrahim}.
\begin{figure}[h]
  \centering
  \includegraphics[width=1.8in, height=1in]{FSI.pdf}
  \caption{Feynmann diagram for FSI, where the proton(red), after excitation by the photon, 
undergoes subsequent interactions (orange) with the neutron(blue) resulting in a re-scattering
of both final state particles.}
  \label{fig:Figure3}
\end{figure} \\
\indent Another possibility is that the photon may couple to the virtual 
meson being exchanged between the nucleons (Meson Exchange Currents or MEC). (See Figure \ref{fig:Figure4})
\begin{figure}[h]
  \centering
  \includegraphics[width=1.6in, height=0.8in]{MEC.pdf}
  \caption{Feynmann diagram for MEC, where the virtual photon couples to the
exchange meson (dashed line) causing the spectator neutron(blue) to re-scatter off 
the proton(red)}
  \label{fig:Figure4}
\end{figure}\\
\noindent Or, the photon may excite either nucleon in the deuteron (Isobaric Configuration or IC). (See Figure \ref{fig:Figure5}) 
\begin{figure}[h]
  \centering
  \includegraphics[width=1.8in, height=1in]{IC.pdf}
  \caption{Feynmann diagram for IC, where the proton(red) is excited by the photon
into an intermediate state (orange) R. The excited state decays and rescatters off the
neutron(blue) in the process}
  \label{fig:Figure5}
\end{figure} \\
\indent It is possible to extract the reduced cross section $\sigma_{red}$ by dividing Eq. \ref{eq:2} 
by $K$ and $\sigma_{ep}$ and integrating over the missing energy to obtain
\begin{equation} \label{eq:3}
\sigma_{red} \equiv S(p_{m}) = \frac{\sigma_{exp}}{K\sigma_{ep}}
\end{equation}
If the PWIA were valid, the reduced cross section would be the momentum distribution
inside the deuteron, therefore it is important to study at which kinematic
settings competing processes are suppressed (MEC, IC), or at least 
under control (FSI) \cite{boeglin3}.\\
\indent FSI are well described by the Generalized Eikonal Approximation (GEA) in the high energy limit($Q^{2}\geq1$ (GeV/c)$^{2}$).
The GEA predicts a strong angular dependence of FSI as a function of the scattering angle $\theta_{nq}$
between spectator nucleon and virtual photon, which opens a kinematic window
at which FSI are reduced \cite{boeglin1}. (See Figure \ref{fig:Figure6})
 \begin{figure}[h]
  \centering
  \includegraphics[width=2.9in, height=1.9in]{FSI_ang_dist.eps}
  \caption{Ratio of FSI/PWIA cross-section vs. scattering angle between 
  spectator neutron and virtual photon, $\theta_{nq}$, for various missing momenta up to
  1 GeV/c \cite{boeglin1}.}
  \label{fig:Figure6}
\end{figure}\\
\indent A previous Hall A experiment (E01-020) \cite{ulmer} at $Q^{2}=3.5$ (GeV/c)$^{2}$ 
and various $\theta_{nq}$ examined the effect of FSI for missing momenta 
up to 0.55 GeV/c. The experiment verified the strong anisotropy of FSI 
as predicted by GEA. Furthermore, there was shown to be a good  
agreement between data and theory for reduced cross sections at 
large missing momenta ($\geq$ 300 MeV/c) for smaller $\theta_{nq}$ angles without the 
inclusion of FSI. (See Figure \ref{fig:Figure7} (a) and (b))   
\begin{figure}[h]
  \centering
  \includegraphics[width=3.7in, height=2.0in]{red_cross.pdf}
  \caption{Reduced cross-section $\sigma_{red}$ vs. missing momenta $p_{m}$ for angles (a) $\theta_{nq}=35^{\circ}$, (b) $\theta_{nq}=45^{\circ}$ and (c) $\theta_{nq}=75^{\circ}$ \cite{ulmer}.}
  \label{fig:Figure7}
\end{figure}
\vspace{-0.6cm}
\section{Project Status}
The Deuteron Electro-Disintegration at Very High Missing Momenta  
experiment (E12-10-003) will be the third of four commissioning experiments and
is scheduled to run on April 2017 on Hall C, Jefferson Lab. The experiment will extend the
the missing momentum range studied in E01-020 from  $p_{m}=0.5$ GeV/c to $p_{m}=1.0$ GeV/c
at a $Q^{2}=4.25$ (GeV/c)$^{2}$ and $x_{Bj}$=1.35 for $\theta_{nq}=40^{\circ}$
where FSI are expected to be reduced. (See Figure \ref{fig:Figure6}) The main focus of E12-10-003
will be to extract the unpolarized D(e,e'p)n cross section and momentum distribution for unexplored
large missing momentum regions at high $Q^{2}$. Various physics simulations have been performed
that predict the D(e,e'p)n experimental cross section as a function of missing momenta from 0.44 to 1.0 GeV/c for the abovementioned kinematic settings. 
The expected results and beam times for each momentum
setting are shown in Figure \ref{fig:Figure8}\cite{mark_pres}.
\begin{figure}[h]
  \centering
  \includegraphics[width=3.2in, height=2.6in]{Exptd_Results.png}
  \caption{Expected D(e,e'p)n differential cross section as a function of missing neutron momenta for beam 
  energy/current of 10.6 GeV/c and 70 $\mu$A for E12-10-003.\cite{mark_pres}}
  \label{fig:Figure8}
\end{figure}
To satisfy the E12-10-003 kinematic requirements, the High Momentum Spectrometer (HMS) and Super HMS (SHMS) housed in Hall C will be set to
scattering angle and central momentum of $59.6^{\circ}\geq\theta_{p}\geq53.1^{\circ}$, $2.12\leq$ p$_{cent}\leq2.3$ GeV/c 
and $\theta_{e}=12.17^{\circ}$, p$_{cent}=$ 8.92 GeV/c, respectively. \\  
%Hall C is one of four
%experimental halls, each with its unique characteristics for performing a 
%variety of nuclear/particle physics experiments. Hall C in particular has
%two spectrometers, the High Momentum Spectrometer (HMS) and Super HMS (SHMS)
%(See Figure \ref{fig:Figure8}) 
% \begin{figure}[h]
%  \centering
% \includegraphics[width=2.7in, height=1.7in]{HMS_SHMS.jpg}
%  \caption{Artist view of HMS/SHMS at Hall C}
%  \label{fig:Figure8}
%\end{figure}
%Each spectrometer is composed by four magnets followed by a series of particle
%detectors serving their unique purpose. The magnets serve to steer the stream
%of particles produced following the interaction of the electron beam with the
%target. The detectors then gather information about the particles, such as 
%position, energy and time. This information is then analyzed through software
%in order to extract experimental observables (e.g. cross sections) that reveal
%the underlying physics processes of interest. \\
\indent Each spectrometer is comprised of a series of magnets followed by the detector stack (See Figure \ref{fig:Figure9}). The magnets
are set for a point-to-point tune and transport (focus) the scattered particles
to the detectors. The detectors are then read out by Analog- and Time- to Digital Convertors (ADC/TDC)(See p.281 of \cite{Leo}). 
\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in, height=2.4in]{HMS_SHMS.jpg}
  \caption{Artist view of Hall C HMS/SHMS}
  \label{fig:Figure9}
\end{figure}
To extract meaningful information from the underlying physics, 
magnets and detectors (Hodoscopes, Wire Chambers, \v{C}erenkovs and Calorimeters) must be properly calibrated. \\ 
\indent The magnetic optics calibration main objective is to determine the transport matrix elements relating the
particle coordinates measured in the focal plane to those in the reaction vertex in the target. 
Knowledge of the matrix elements will provide a one-to-one mapping of measured particle tracks
to specific target location where the particle originated. \\
\indent Calibration of every detector element in the stack involves the translation of ADC/TDC hits
to equivalent energies  and times which are used to extract meaningful physics quantities.
Hodoscopes measure particle Time-of-Flight (TOF) from TDC values. These values must be corrected by
accounting for photon propagation time through the scintillator as well as pulse height, given that signals travelling
through a medium are attenuated.\\
\indent Drift Chambers measure particle position and must be calibrated to measure drift distance (distance between grounded sense wires and particle track).
Drift distances are determined from raw TDC hits registered by the sense wires and Hodoscope timing
information. \\ 
\indent Gas \v{C}erenkovs are used to discriminate particles based on threshold energies required to emit \v{C}erenkov radiation in the 
gas. The calibration of such detectors will involve isolating single photoelectron peaks in the ADC spectrum for each phototube.\\  
\indent Calorimeters measure energy deposition of particles and are able to discriminate between particles based on the
amount of energy deposited. To accurately measure energy deposited from raw ADC hits requires that the light attenuated
inside individual calorimeter lead blocks be accounted for. \\
\indent In addition to optics and detector calibrations, Beam Current Monitoring (BCM) and Target Boiling studies must be taken into consideration.
In E12-10-003, since a 15-cm long liquid deuterium target (T$_{\text{freezing}}$ = 18.7 K, T$_{\text{boiling}}$ = 25.3 K) needs to be cooled to 22 K, the power delivered by the beam can cause local
density fluctuations (local boiling) within the target, and so one needs to study the density fluctuations as a function of beam current in
order to correct for target boiling effects \cite{ibrahim}.\\   
\indent I am currently working on setting up a primary trigger in HMS/SHMS by
requiring 3/4 hodoscope planes in each spectrometer to fire (detect a hit) to consider the signal as 
a true event. The trigger then informs other detectors that the detected
signal is indeed a true event coming from the target. Once a primary trigger is set in
each spectrometer, a coincidence trigger (See p.287 of \cite{Leo}) needs 
to be set up between the HMS/SHMS in order to determine whether the detected particles originated
from the same interaction in the target. Depending on the nature of the experiment, additional triggers
may also be incorporated. \\
\indent I have also recently finished restoring one of the HMS Drift Chambers whose
exposure to radiation over a period of 25 years of use resulted in the
deterioration of 97 sense wires. All the broken sense wires
have been recently re-strung and tested. The chamber has been re-installed
in the HMS detector stack and we are currently taking a cosmic run to
monitor the detector response and diagnose any problems that may arise.

\newpage
\onecolumn
\bibliography{proposal}
\bibliographystyle{acm}

\end{document}

### 2019-06-30 DNP_Meetings/abstract_corrected.tex
update

\documentclass[a4paper]{article}
%\usepackage{simplemargins}

%\usepackage[square]{natbib}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[urw-garamond]{mathdesign}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}
\usepackage[left=4cm, right=4cm, top=1cm]{geometry}

\begin{document}
\pagenumbering{gobble}

\Large
 \begin{center}
\textbf{First Cross Section Results of D(e,e'p)n at Very High Recoil Momenta\\}

\hspace{10pt}

% Author names and affiliations
\large
Carlos Yero \\

\hspace{10pt}

\small
for the Hall C Collaboration

\hspace{10pt}

\small
(Dated: July 01, 2019) \\

\hspace{10pt}

\small  
Florida International University\\

\end{center}

\hspace{10pt}

\large
\begin{center}
ABSTRACT
\end{center}
\normalsize

\noindent Preliminary D(e,e'p)n electro-disintegration cross sections at $Q^{2} = 4.25$ GeV$^{2}$ with recoil
momenta up to 900 MeV/c will be presented. The experiment ran for a total of 6 days of beam time in April 2018
at Jefferson Lab in Hall C and it seeks to study the short range structure of the deuteron by probing its high
momentum components beyond 500 MeV/c, where currently no data exists. The experiment was part of a group of Hall C
experiemnts that commissioned the new Hall C Super High Momentum Spectrometer (SHMS). At the selected kinematics,
Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. Final State Interactions (FSI) have also
been suppressed by choosing a kinematic region where the neutron recoil angle is between 35 and 45 degrees with respect
to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment (Boeglin et al. Phys Rev Lett. 2011)
and is also predicted in modern theoretical calculations (W. Boeglin \& M. Sargsian Int.J.Mod.Phys. 2015). In this region,
the Plane Wave Impulse Approximation (PWIA) dominates and comparisions between measured and predicted cross sections are
sensitive to the deuteron momentum distributions. Comparisons between data and different calculations with different NN
potentials will be shown.

\end{document}

### 2019-07-17 MY_THESIS/HallC_12GeV_Trigger/version2/trigger_v2.tex
updated trgger documentation, added hall c analysis procedures documentation

--- 2017-10-29 HallC_12GeV_Trigger/trigger.tex
@@
 \usepackage[singlelinecheck=false]{caption}
-\usepackage{datetime}
 \usepackage[hyperfootnotes=false, pdfnewwindow, colorlinks=true]{hyperref}
+\usepackage[title]{appendix}
+\usepackage[section]{placeins}
+\usepackage{float}
 
@@
   \hypersetup{
-    urlcolor=red,
-    citecolor=green,
+    urlcolor=blue,
+    citecolor=blue,
     linkcolor=blue,
@@
 \newcommand{\saergate}{30 ns}
+\newcommand{\comment}[1]{}
 
-\title{\Large \bf{Hall C 12 GeV Trigger Set-Up}}
+\title{\LARGE \bf{Hall C 12 GeV Trigger Set-Up}}
 
-\author{Carlos Yero}
+\author{Carlos Yero \\ email \href{mailto:cyero002@fiu.edu}{cyero002@fiu.edu}}
 
-\date{\today}
 \maketitle
@@
   \centering
-  \includegraphics[width=5.0in, height=4.0in]{HMS_stack.pdf}
+  \includegraphics[width=5.0in, height=4.0in]{../HMS_stack.pdf}
   \caption{HMS detector stack.}
   \label{fig:hms_stack}
-\end{figure}
-\begin{figure}[h]
+\end{figure}\\
+\newpage
+\noindent The rest of the HMS detector signals(Gas \c{C}erenkov, Hodoscope, Calorimeter) are
+sent to the Hall C Floor Patch Panel via the hut Patch, with the exception
+of the Aerogel, which is sent directly from the detector to the Floor Patch.
+All the signals are then sent to the Counting Room Patch Panel to be processed
+by the electronics. (See Figure \ref{fig:hms_patch})
+
+\begin{figure}[h!]
   \centering
-  \includegraphics[width=5.0in, height=4.0in]{HMS_Hut_Rack.pdf}
+  \includegraphics[width=5.0in, height=4.0in]{../HMS_Hut_Rack.pdf}
   \caption{HMS detector hut electronic rack and patch panels.}
@@
 \end{figure}
-The rest of the HMS detector signals(Gas \c{C}erenkov, Hodoscope, Calorimeter) are sent to the Hall C Floor Patch Panel via the hut Patch, with the exception
-of the Aerogel, which is sent directly from the detector to the Floor Patch.
-
-\newpage
-All the signals are then sent to the Counting Room Patch Panel to be processed
-by the electronics. (See Figure \ref{fig:hms_patch})
 
@@
   \centering
-  \includegraphics[width=6.0in, height=2.0in]{HMS_patch.pdf}
+  \includegraphics[width=6.0in, height=2.0in]{../HMS_patch.pdf}
   \caption{HMS Patch Diagram from detectors to Counting Room.}
@@
 Counting Room Patch (See Figure \ref{fig:shms_hut_rack1}).
+The rest of the SHMS detector signals (HGC/NGC, Hodoscope, Aerogel) are sent to the Counting Room via the hut patch panel (See Figure \ref{fig:shms_patch}).
+\newpage
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=6.0in, height=4.0in]{SHMS_stack.pdf}
+  \includegraphics[width=6.0in, height=4.0in]{../SHMS_stack.pdf}
   \caption{SHMS detector stack.}
@@
 \begin{figure}[h!]
-\centering
 \begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[width=3.0in, height=4.0in]{SHMS_Hut_Rack01.pdf}
+  \includegraphics[width=3.0in, height=4.0in]{../SHMS_Hut_Rack01.pdf}
   \captionof{figure}{SHMS Hut Patch Panel (left) and Electronics Rack (right).}
@@
 \begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[width=2.0in, height=4.0in]{SHMS_Hut_Rack02.pdf}
+  \includegraphics[width=2.0in, height=4.0in]{../SHMS_Hut_Rack02.pdf}
   \caption{SHMS Drift Chamber Electronics Rack.}
@@
 \end{figure}
+
 \newpage
-The rest of the SHMS detector signals (HGC/NGC, Hodoscope, Aerogel) are sent to the Counting Room via the hut patch panel (See Figure \ref{fig:shms_patch}). 
-\begin{figure}[h!]
+
+\begin{figure}[t]
   \centering
-  \includegraphics[width=6.0in, height=2.0in]{SHMS_patch.pdf}
+  \includegraphics[scale=0.8]{../SHMS_patch.pdf}
   \caption{SHMS Patch Diagram from detectors to Counting Room.}
@@
 
-\newpage
 \subsection{Hall C Counting Room}
-Once the detector signals arrive at the Counting Room Patch (See Figure \ref{fig:cr_patch}), they are processed by the NIM/CAMAC electronics (See Figure \ref{fig:cr_racks}) to form the single arm and coincidence triggers
+Once the detector signals arrive at the Counting Room Patch (See Figure \ref{fig:cr_racks_patch}A), they are processed by the NIM/CAMAC electronics (See Figure \ref{fig:cr_racks_patch}B) to form the single arm and coincidence triggers
 for each spectrometer. The signals are also sent to ADCs/TDCs to determine energy and timing information for individual detectors as well as trigger TDC information.
@@
 \begin{figure}[h!]
-  \centering
-  \includegraphics[width=3.0in, height=4.0in]{CR_Patch.pdf}
-  \caption{Counting Room Patch Panels.}
-  \label{fig:cr_patch}
+  \includegraphics[scale=0.5]{../CR_patch_combined.png}
+  \caption{(A) Counting Room Patch Panels (left 2 racks). (B) Counting Room main
+    Electronic Racks for HMS/SHMS detectors (right 2 racks).}
+  \label{fig:cr_racks_patch}
 \end{figure}
-
 \newpage
-
-\begin{figure}[h!]
-\centering
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=2.0in, height=4.0in]{CR_rack4.pdf}
-\end{subfigure}%
-\begin{subfigure}{.2\textwidth}
-  \centering
-  \includegraphics[width=2.0in, height=4.0in]{CR_rack5.pdf}
-\end{subfigure}
-\caption{Counting Room main Electronic Racks for HMS/SHMS detectors.}
-\label{fig:cr_racks}
-\end{figure}
-
 \section{HMS Trigger Set-Up} 
@@
 \subsection{Hodoscope Pre-Trigger}
-
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=7.0in, height=3.2in]{HMS_HODO_TRIGGER.pdf}
-  \caption{HMS Hodoscope Electronics Diagram.}
-  \label{fig:hms_hod_trg}
+  \includegraphics[scale=0.5]{hHODO_diagram.png}
+  \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}
+  \label{fig:hHODO_diagram}
 \end{figure}
-
-\indent Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:hms_stack}), so each bar reads out two signals.
-As shown in Figure \ref{fig:hms_hod_trg},
+\noindent Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:hms_stack}), so each bar reads out two signals.
+As shown in Figure \ref{fig:hHODO_diagram},
 for example, hodoscope plane h1X consists of 32 signals (16 bars) read out in the Counting House (CH) patch.
@@
 A copy of all the pre-triggers discussed above are sent to TDCs/Scalers via a NIM/ECL converter for timing and counting rate information.
-(See Figure \ref{fig:hms_hod_trg}) \\
+(See Figure \ref{fig:hHODO_diagram}) \\
 
 \subsection{Calorimeter Pre-Trigger}
-The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
+\begin{figure}[h!]
+  \centering
+  \includegraphics[scale=0.5]{hCAL_diagram.png}
+  \caption{HMS Calorimeter Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA2}}
+  \label{fig:hCAL_diagram}
+\end{figure}
+\noindent The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
 read out 13 signals/layer on one side. The first two layers form the Pre-Shower Counter while all four layers (A, B, C and D) form the Shower Counter.  
@@
 information.
-\newpage
+
+\subsection{Gas \v{C}erenkov Pre-Trigger} \label{hms_cer_section}
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=6.5in, height=4.5in]{HMS_Cal_Trigger.pdf}
-  \caption{HMS Calorimeter Electronics Diagram.}
-  \label{fig:hms_cal_trg}
-\end{figure}
-
-\subsection{Gas \v{C}erenkov Pre-Trigger} \label{hms_cer_section}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=7.0in, height=2.0in]{HMS_Cer_trig.pdf}
-  \caption{HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
-  \label{fig:hms_gas_cer_trg}
+  \includegraphics[scale=0.5]{hCER_diagram.png}
+  \caption{HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov. For original diagram, see Appendix \ref{appendix:Appx3} }
+  \label{fig:hCER_diagram}
 \end{figure}
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=6.5in, height=2.1in]{HMS_Aero_trig.pdf}
-  \caption{Aerogel \v{C}erenkovs Electronics Diagram. Same electronics diagram applies for SHMS Aerogel.}
-  \label{fig:hms_aero_trg}
-\end{figure}
-
 \indent The HMS Aerogel \v{C}erenkov detector consists of a 120cm x 70cm rectangular aerogel tray coupled to a diffusion box\cite{hms_aero_article} and is located
@@
 A copy of the discriminated signal is also sent to TDCs/Scalers via a NIM/ECL converter for trigger and counting rate information.
+The electronics diagram is the same as in Figure \ref{fig:hCER_diagram}. For the original diagram, see Appendix \ref{appendix:Appx4}
 
-\subsection{HMS Single Arm Trigger}\label{ssec:hms_single_arm_sec}
+\newpage
+\subsection{HMS Single Arm Pre-Trigger}\label{ssec:hms_single_arm_sec}
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{HMS_SingleArm_Trigger.pdf}
-  \caption{HMS Single Arm Trigger Electronics Diagram}
-  \label{fig:hms_one_arm_trg}
+  \includegraphics[scale=0.5]{HMS_SingleArm_diagram.png}
+  \caption{HMS Single Arm Pre-Trigger Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx5}}
+  \label{fig:HMS_SingleArm_diagram}
 \end{figure}
@@
 
+\newpage 
 \section{SHMS Trigger Set-Up}
@@
 
-\subsection{Hodoscope Pre-Trigger}
+\subsection{Hodoscopes Pre-Trigger}
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=7.0in, height=4.3in]{SHMS_HODO_TRIGGER.pdf}
-  \caption{SHMS Hodoscope Electronics Diagram.}
-  \label{fig:shms_hod_trg}
+  \includegraphics[scale=0.5]{pHODO_diagram.png}
+  \caption{SHMS Hodoscopes Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx6}}
+  \label{fig:pHODO_diagram}
 \end{figure}
@@
 A copy of all the
-pre-triggers discussed above are sent to TDCs/Scalers via a NIM/ECL converter for timing and counting rate information. (See Figure \ref{fig:shms_hod_trg}) \\
+pre-triggers discussed above are sent to TDCs/Scalers via a NIM/ECL converter for timing and counting rate information. (See Figure \ref{fig:pHODO_diagram}) \\
 
-\subsection{Pre-Shower Calorimeter Pre-Trigger}
+\subsection{Pre-Shower / Shower Calorimeter Pre-Trigger}
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=7.0in, height=3.0in]{SHMS_preSh_trigger.pdf}
-  \caption{SHMS PreShower Electronics Diagram}
-  \label{fig:shms_preSh_trg}
+  \includegraphics[scale=0.5]{pCAL_diagram.png}
+  \caption{SHMS PreShower / Shower Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx7}}
+  \label{fig:pCAL_diagram}
 \end{figure}
-\newpage
+
 The SHMS Pre-Shower consists of two sets of fourteen (PMT-coupled) lead blocks oriented perpendicular to the Shower Counter blocks\cite{shms_preSh_talk}.
@@
 \end{empheq}
+The Shower counter consists of 224 lead blocks, each coupled to a PMT at the end. Becasue of the high channel density of this detector, its signals are sent
+directly to the ROC 4 fADCs in the SHMS detector hut.
+\newpage
 \subsection{Heavy/Noble Gas \v{C}erenkov Pre-Trigger}
-\indent The SHMS Heavy Gas \v{C}erenkov detector consists of a 1 m long, 1.6 m in diameter cylindrical tank located between the first set of hodoscope planes and the Aerogel (See Figure \ref{fig:shms_stack}).
+\begin{figure}[h!]
+  \centering
+  \includegraphics[scale=0.5]{pCER_diagram.png}
+  \caption{SHMS Gas \v{C}erenkovs Electronics Diagram.}
+  \label{fig:pCER_diagram}
+\end{figure}
+\noindent The SHMS Heavy Gas \v{C}erenkov detector consists of a 1 m long, 1.6 m in diameter cylindrical tank located between the first set of hodoscope planes and the Aerogel (See Figure \ref{fig:shms_stack}).
 The tank is filled with a gas and has four thin spherical mirrors that focus the \v{C}erenkov photons towards four 5-inch PMTs\cite{shms_hgc_talk}. 
-For a description of the electronics diagram, See Section \ref{hms_cer_section} on the HMS Gas \v{C}erenkov.
 \newline
@@
 The tank is filled with a gas and has four overlapping mirrors, that focus the \v{C}erenkov photons towards four 5-inch PMTs\cite{shms_ngc_talk}. 
-For a description of the electronics diagram, See Section \ref{hms_cer_section} on the HMS Gas \v{C}erenkov.
+For the original electronics diagram, See Appendix \ref{appendix:Appx4} on the HMS Gas \v{C}erenkov.
 \subsection{Aerogel \v{C}erenkov Pre-Trigger}
@@
 which detect \v{C}erenkov light produced by interactions with the Aerogel material\cite{shms_aero_article}. The detector is located between Heavy Gas \v{C}erenkov and second set of hodoscope planes
-(See Figure \ref{fig:shms_stack}). For a description of the electronics diagram, see Figure \ref{fig:hms_aero_trg}.
-\subsection{SHMS Single Arm Trigger}
+(See Figure \ref{fig:shms_stack}). The electronics diagram is the same as in Figure \ref{fig:pCER_diagram}. For the original diagram, see Appendix \ref{appendix:Appx4}
+\newpage
+\subsection{SHMS Single Arm Pre-Trigger}
 \begin{figure}[h!]
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{SHMS_SingleArm_Trigger.pdf}
-  \caption{SHMS Single Arm Trigger Electronics Diagram}
-  \label{fig:shms_one_arm_trg}
+  \includegraphics[scale=0.5]{SHMS_SingleArm_diagram.png}
+  \caption{SHMS Single Arm Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx8}.}
+  \label{fig:SHMS_SingleArm_diagram}
 \end{figure}
@@
 \indent The SHMS single arm trigger is be formed exactly as the HMS single arm trigger, with the exception of the detectors involved.
-Compare the electronics diagrams in Figures \ref{fig:shms_one_arm_trg} and
-\ref{fig:hms_one_arm_trg}, and read Section \ref{ssec:hms_single_arm_sec} for a detailed description of the electronic diagrams.
-
+Compare the electronics diagrams in Figures \ref{fig:SHMS_SingleArm_diagram} and
+\ref{fig:HMS_SingleArm_diagram}, and read Section \ref{ssec:hms_single_arm_sec} for a detailed description of the electronic diagrams. 
+\newpage
 \section{Coincidence Trigger Set-Up}
@@
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{Coincidence_Trigger.pdf}
-  \caption{Coincidence Trigger Electronics Diagram}
-  \label{fig:coin_trg}
+  \includegraphics[scale=0.5]{Coin_diagram.png}
+  \caption{Coincidence Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx9}}
+  \label{fig:Coin_TRG}
 \end{figure}
@@
 \onecolumn
-\bibliography{trigger}
+\bibliography{trigger_v2}
 \bibliographystyle{acm}
 
+\newpage
+\begin{appendices}
+\appendix
+\section{Original Electronics Diagrams}
+\subsection{HMS Hodoscopes Electronics Diagram}
+\label{appendix:AppxA1}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=3.2in]{../HMS_HODO_TRIGGER.pdf}
+  \caption{Original HMS Hodoscopes Electronics Diagram.}
+  \label{fig:hms_hod_trg}
+\end{figure}
+\subsection{HMS Calorimeter Electronics Diagram}
+\label{appendix:AppxA2}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=6.in, height=4.in]{../HMS_Cal_Trigger.pdf}
+  \caption{Original HMS Calorimeter Electronics Diagram.}
+  \label{fig:hms_cal_trg}
+\end{figure}
+
+\subsection{HMS Gas \v{C}erenkov Electronics Diagram}
+\label{appendix:Appx3}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=2.0in]{../HMS_Cer_trig.pdf}
+  \caption{Original HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
+  \label{fig:hms_gas_cer_trg}
+\end{figure}
+
+\subsection{HMS Aerogel \v{C}erenkov Electronics Diagram}
+\label{appendix:Appx4}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=6.5in, height=2.1in]{../HMS_Aero_trig.pdf}
+  \caption{Original HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
+  \label{fig:hms_gas_cer_trg}
+\end{figure}
+\newpage
+\subsection{HMS Single Arm Electronics Diagram}
+\label{appendix:Appx5}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=3.8in]{../HMS_SingleArm_Trigger.pdf}
+  \caption{Original HMS Single Arm Trigger Electronics Diagram.}
+  \label{fig:hms_one_arm_trg}
+\end{figure}
+\subsection{SHMS Hodoscopes Pre-Trigger}
+\label{appendix:Appx6}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=6.8in, height=3.9in]{../SHMS_HODO_TRIGGER.pdf}
+  \caption{Original SHMS Hodoscope Electronics Diagram.}
+  \label{fig:shms_hod_trg}
+\end{figure}
+\newpage
+\subsection{SHMS Pre-Shower / Shower Calorimeter Pre-Trigger}
+\label{appendix:Appx7}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=3.0in]{../SHMS_preSh_trigger.pdf}
+  \caption{Original SHMS PreShower Electronics Diagram}
+  \label{fig:shms_preSh_trg}
+\end{figure}
+\subsection{SHMS Single Arm Pre-Trigger}
+\label{appendix:Appx8}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=3.8in]{../SHMS_SingleArm_Trigger.pdf}
+  \caption{Original SHMS Single Arm Trigger Electronics Diagram}
+  \label{fig:shms_one_arm_trg}
+\end{figure}
+\newpage
+\subsection{Coincidence Pre-Trigger}
+\label{appendix:Appx9}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=7.0in, height=3.8in]{../Coincidence_Trigger.pdf}
+  \caption{Original Coincidence Trigger Electronics Diagram}
+  \label{fig:coin_trg}
+\end{figure}
+
+\end{appendices}
+
 \end{document}

### 2019-07-29 MY_THESIS/D2_Optics_Optim/d2_optim.tex
added D2 Optics documrnt

\documentclass[11pt]{article}

\usepackage{url}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{graphicx}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{empheq}
\usepackage{amssymb}
\usepackage{tgtermes}
\usepackage{gensymb}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{epstopdf}
\usepackage[singlelinecheck=false]{caption}
\usepackage[hyperfootnotes=false, pdfnewwindow, colorlinks=true]{hyperref}
\usepackage[title]{appendix}
\usepackage[section]{placeins}
\usepackage{float}

\AtBeginDocument{% optionally set colors to your liking
  \hypersetup{
    urlcolor=blue,
    citecolor=blue,
    linkcolor=blue,
  }%
}

\begin{document}

\title{\Large \bf{Optics Optimization for the D(e,e'p)n Experiment (E12-10-003)}}

\author{Carlos Yero}

\date{\today}
\maketitle

%*****************************************************************************************************************************************************
\section{Introduction}
\noindent The commissioning of the HMS/SHMS optics took place on the 2017-18 run period and underwent multiple revisions of the reconstruction
matrix elements for both spectrometers during that period.\cite{HMS_Optics, SHMS_Optics} This document presents the optics optimization checks
and procedures done on the High Momentum Spectrometer (HMS) and superHMS (SHMS) for the Deuteron Electro-Disintegration Commissioning Experiment
(E12-10-003) on April 2018. At the time, this experiment also served as part of the general optics commissioning as during data-taking, it was found that
the SHMS Q3 magnet had an un-ncecessary correction in the matrix elements. As a result, the data for this experiment is divided into two sections.
Only the section after the fix in the SHMS optics was used in the optimization procedure.\\
\indent The problem of optics optimization can be approached in different ways, depending on the circumstances
of the experiment. In this particular experiment, a series of H(e,e'p) elastic runs were taken at different
configurations such as to cover the entire HMS momentum range in the D(e,e'p)n reaction kinematics. The original
and corrected H(e,e'p) kinematics are summarized below.

\begin{table}[ht]
\begin{tabular}{c c c c c}
\hline\hline
Run  & \shortstack{HMS \\ Angle [deg]} & \shortstack{HMS \\ Momentum [GeV]} & \shortstack{SHMS \\ Angle [deg]} & \shortstack{SHMS \\ Momentum [GeV]} \\
\hline
3288 & 37.338 & 2.938 & 12.194 & 8.7 \\
3371 & 33.545 & 3.48 & 13.93 & 8.7 \\
3374 & 42.9 & 2.31 & 9.928 & 8.7 \\
3377 & 47.605 & 1.8899 & 8.495 & 8.7 \\
\hline
\end{tabular}
\label{table:original_heep_kin}
\caption{Original H(e,e'p) Elastic Kinematics in E12-10-003.}
\end{table}
\begin{table}[ht]
\begin{tabular}{c c c c c}
\hline\hline
Run  & \shortstack{HMS \\ Angle [deg]} & \shortstack{HMS \\ Momentum [GeV]} & \shortstack{SHMS \\ Angle [deg]} & \shortstack{SHMS \\ Momentum [GeV]} \\
\hline
3288 & 37.338 & 2.9355 & 12.194 & 8.5342 \\
3371 & 33.545 & 3.4758 & 13.93 & 8.5342 \\
3374 & 42.9 & 2.3103 & 9.928 & 8.5342 \\
3377 & 47.605 & 1.8912 & 8.495 & 8.5342 \\
\hline
\end{tabular}
\label{table:corr_heep_kin}
\caption{Corrected H(e,e'p) Elastic Kinematics in E12-10-003.}
\end{table}
\begin{table}[ht]
\begin{tabular}{c c c c c}
\hline\hline
Spec  & $\delta\theta$[rad] & $\delta\phi$[rad] & $X'_{tar}$-offset[rad] & $Y'_{tar}$-offset[rad] \\
\hline
HMS & 0.0 & \num{1.521e-3} & \num{2.852e-3} & \num{9.5e-4} \\
SHMS & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}
\label{table:spec_offsets}
\caption{Spectrometer Offsets determined from H(e,e'p) Elastic Run 3288 in E12-10-003. See Section \ref{sec:spec_off_sec} of this document for more information.}
\end{table}
Since this is a coincidence experiment, the spectrometers are highly correlated which makes the optics optimization more complicated, as changes in
one spectrometer can affect the other. Based on the kinematics, it was determined to focus on the HMS first, as the momentum is well below the Dipole
saturation ($\sim$5 GeV), and the optics are much better understood from the 6 GeV era.

\section{HMS Optics Check} \label{sec:hms_optics_sec}
\noindent The procedure to check the HMS Optics involves determining whether a central momentum correction is needed and check that the
HMS $\delta$ as a function of the HMS focal plane variables looks OK.

\subsection{Central Momentum Correction}
Since the H(e,e'p) reaction is used and the HMS is set to detect protons, one can use the formula for the calculated proton momentum
\begin{equation}
  P_{calc} = \frac{2M_{p}E_{b}(E_{b}+M_{p})\cos(\theta_{p})}{M^{2}_{p} + 2M_{p}E_{b} + E^{2}_{b}\sin^{2}(\theta_{p})}
  \label{eq:1}
\end{equation}
which only depends on the beam energy $E_{b}$ and the proton angle $\theta_{p}$, but does \textbf{NOT} depend on $\delta$,
whereas the measured proton momentum, $P_{mes} = P_{meas}(\delta)$, does depend on the HMS-$\delta$ from the following definition:
\begin{equation}
  \frac{\delta}{100} = \frac{P_{meas} - P_{0}}{P_{0}} \rightarrow \boxed{P_{meas} = P_{0}(1 + \frac{\delta}{100})}
  \label{eq:2}
\end{equation}
where $P_{0}$ is the central momentum of the spectrometer.

From the measured and calculated momentum,
the momentum difference can be defined as
\begin{equation}
  \Delta P = P_{calc}-P_{meas}
  \label{eq:3}
\end{equation}
To use this formula, it is assumed that the beam energy and HMS angle are well known, which may \textbf{NOT} entirely be true, however,
one needs a starting point, and this is the best we have for now. The momentum difference, $\Delta P$, is determined for DATA and
SIMC\footnote{SIMC is the Hall C Simulation Software for Coincidence Experiments.} independently on an event-by-event basis in terms of
($\theta_{p}$, $\delta$). It is expected that $\Delta P$ be near zero in SIMC, as the $\delta$-reconstruction is well described by the TOSCA models, however in
data, this may not be the case, as the NMR probe location in the HMS has changed since the 6 GeV era and the momentum may be different from what is expected. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/hms_Pdiff.png}
  \caption{Comparison of HMS momentum difference ($\Delta P$) between DATA and SIMC. The subplot shows the calculated and measured
  HMS momentum distribution for DATA.}
  \label{fig:hms_Pdiff}
\end{figure}\\
From the mean of the fit in Figure \ref{fig:hms_Pdiff}, $\Delta P_{DATA}$ is $\sim$8 MeV smaller than $\Delta P_{SIMC}$, or equivalently,
$P_{DATA}^{meas} > P_{DATA}^{calc}$. The data momentum correction factor can be determined from the following formula:
\begin{equation}
  f^{hms}_{corr} = 1 - \frac{\Delta P_{SIMC} - \Delta P_{DATA}}{P_{0}}
  \label{eq:4}
\end{equation}
and the corrected HMS momentum can be expressed as
\begin{equation}
  P^{HMS}_{corr} = P^{HMS}_{uncorr} \cdot f^{hms}_{corr}
  \label{eq:5}
\end{equation}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.6]{plots/hms_Pcorr.png}
  \caption{HMS momentum difference, $\Delta P_{diff}=\Delta P_{SIMC} - \Delta P_{DATA}$, before and after applying the momentum correction to data.}
  \label{fig:hms_Pcorr}
\end{figure}\\
Figure \ref{fig:hms_Pcorr} shows the difference in the mean of the fit for DATA and SIMC before and after the HMS momentum
corrections. After correction, the difference between DATA and SIMC is within $\sim$1 MeV for the four elastic runs. It is important to note
that the corrections applied are after a second iteration, once the spectrometer offsets were determined. \\
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/hms_dataPdiff_compare.png}
  \caption{HMS momentum difference for DATA, before (\textcolor{blue}{blue}) and after (\textcolor{green}{green}) applying the momentum correction ($2^{nd}$ iteration) to data.}
  \label{fig:hms_dataPdiff}
\end{figure}

\subsection{HMS $\delta$ Check }
To check the HMS Delta ($\delta$) reconstruction matrix, we plot the HMS fractional momentum difference defined as
\begin{equation}
\Delta P_{frac} = \frac{P_{calc} - P_{meas}}{P_{meas}}
\end{equation}
as a function of the HMS focal plane variables.

\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/HMS_hPdiff_vs_FP.png}
  \caption{HMS fractional momentum difference vs. focal plane variables for the four H(e,e'p) Elastic runs.}
  \label{fig:hms_hPdiff_vs_FP}
\end{figure}
\noindent Figure \ref{fig:hms_hPdiff_vs_FP} shows the fractional HMS momentum is un-correlated across each of the
HMS focal plane variables, which demonstrates that the $\delta$-reconstruction matrix is already optimized
for the HMS. Now that we claim the HMS momentum and optics are well understood, we move on to the SHMS Checks.

\section{SHMS Optics Check}
Similarly to the HMS, the procedure to check the SHMS Optics involves determining the central momentum correction
and checking the SHMS $\delta$-reconstruction matrix is un-correlated with the SHMS focal plane variables. Additional
checks on the $Y_{tar}, Y'_{tar}$ and $X'_{tar}$ reconstruction variables may be needed as the SHMS Optics are still \textbf{NOT}
completely well understood.

\subsection{Central Momentum Correction}
To determine the SHMS central momentum correction, we start with the missing energy definition of H(e,e'p)
\begin{equation}
  E_{miss} = (E_{b} - E') + M_{p} - E_{p}
\end{equation}
where $E'$ and $E_{p}$ are the electron and proton final energies, respectively. Since it was assumed that
the beam energy is well known, and the HMS momentum has been corrected, any deviation from the expected missing
energy is attributed to the electron momentum in the SHMS. The expected location of the $E_{miss}$ ideally would
be at zero since H(e,e'p) is a completely determined system. However, due to the energy loss and radiative effects,
the peak has a small offset from zero ($\lesssim$10 MeV), which can only be simulated. The measured and simulated
$E_{miss}$ are then compared to determined if the SHMS central momentum needs to be corrected.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.2]{plots/Emiss_3288_UnCorr.png}
  \caption{Missing Energy Spectrum for H(e,e'p) Elastic run 3288 before central momentum correction.}
  \label{fig:Emiss_UnCorr}
\end{figure} \\
The SHMS central momentum was kept fixed during the entire experiment, which would suggest that the missing
energy offset would be the same for the four elastic runs after the HMS momentum correction. This was found
\textbf{NOT} to be the case, however, due to the fact that the spectrometer offsets have not been determined
at this stage. Alternatively, it was decided to only focus on finding the central momentum correction
for run 3288, as it was the closest kinematic setting to the D(e,e'p) 80 MeV setting. This correction would then
be applied to the remaining elastic runs. \\
\indent Assuming any variation in missing energy between DATA and SIMC was due to the electron momentum, $E'$,
\begin{equation}
  \frac{\delta E_{miss}}{\delta E'} = -1 \rightarrow \delta E_{miss} = -\delta E' \\
\end{equation}
where $\delta E_{miss} = E^{SIMC}_{miss} - E^{DATA}_{miss}$ from the missing energy peak fit.
The electron momentum correction is then
\begin{align}
  E'_{corr} & =  E'_{uncorr} + \delta E' \nonumber \\
  & = E'_{uncorr}(1 - \frac{\delta E_{miss}}{E'_{uncorr}})
\end{align}
where the correction factor is
\begin{equation}
f^{shms}_{corr} = 1 - \frac{\delta E_{miss}}{E'_{uncorr}}
\end{equation}
After correcting the SHMS central momentum, the SHMS $\delta$-reconstruction also needs to be checked as a function
of the SHMS focal plane variables, as it may need to be optimized.
\subsection{SHMS $\delta$ Optimization}
To check the SHMS $\delta$-reconstruction matrix, similarly to the HMS, one needs to determined if there exists any
correlation of across the focal plane, as each of the reconstructed variables ($Y_{tar}$, $X'_{tar}$, $Y'_{tar}$, $\delta$) in general,
depends on a linear combination of the focal plane variables ($X_{fp}$, $X'_{fp}$, $Y_{fp}$, $Y'_{fp}$).
In general, the $\delta$ component can be expressed as
\begin{equation}
  \delta = \sum_{ijklm} D_{ijklm}x^{i}_{fp}x'^{j}_{fp}y^{k}_{fp}y'^{l}_{fp}x^{m}_{tar}
  \label{eq:11}
\end{equation}
where $i,j,k,l,m$ are the powers of the focal plane quantities and $D_{ijklm}$ are the matrix
coefficients for a particular combination of powers. \\
\indent To optimize the $\delta$-component, we define calculated $\delta$ as
\begin{equation}
  \delta_{calc} = \frac{P_{calc} - P_{0}}{P_{0}} 
\end{equation}
where the calculated electron momentum is determined from momentum conservation to be
\begin{equation}
  P_{calc} = E_{b} + M_{p} - E_{p}, \text{ where } E_{p} = \sqrt{P_{meas}^{2} + M_{p}^{2} } \text{   and   } E_{calc} \sim P_{calc}
\end{equation}
The measured proton momentum, $P_{meas}$, is the corrected HMS momentum determined in the previous
section.
Taking the difference between the calculated and measured momentum,
\begin{equation}
  \chi^{2} \equiv (\delta_{calc} (E_{b}, P_{meas}) - \delta_{meas} (x_{fp}, x'_{fp}, y_{fp}, y'_{fp}))^{2}
  \label{eq:14}
\end{equation}
From Equation \ref{eq:14}, the SHMS $\delta$-optimization is now a $\chi^{2}$-minimization problem, where the goal is
to find a set of matrix coefficients,  $D_{ijklm}$, that minimizes the difference between the calculated and measured
$\delta$. For more further details, see Section 6 of \cite{HMS_notes} \\
\indent The $\chi^{2}$-minimization was done on all four elastics simultaneously, as each of them covered
a different (also overlapping) region of the SHMS $\delta$-reconstructed variable, such that the D(e,e'p)n data would be
inside the coverage. Additionally, \text{ONLY} the $(x_{fp}, x'_{fp})$ focal plane terms were used in the fit since
with elastic events there is a kinematic correlation between the momentum and scattering angle which translates into a correlation
between $x_{fp}$ and $(y'_{fp}, y_{fp})$. So if one fits $(y'_{fp}, y_{fp})$ then one can be fitting this kinematic
correlation and not an optics correlation \cite{priv_comm}.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.34]{plots/SHMS_DeltaDiff_BeforeOptim3288.png}
  \caption{SHMS $(\delta_{calc}-\delta_{meas})$ vs. focal plane variables for H(e,e'p) Elastic run 3288 before $\delta$-optimization.}
  \label{fig:shmsDelta_beforeOptim}
\end{figure}
\newpage
\indent The $\delta$ terms that were used in the fit can be expanded from Eq. \ref{eq:11},
\begin{equation}
  \delta_{meas} = D_{10000}\cdot x_{fp} + D_{01000}\cdot x'_{fp} + D_{11000}\cdot x_{fp}\cdot x'_{fp} + D_{20000}\cdot x^{2}_{fp} + D_{02000}\cdot x'^{2}_{fp}
\end{equation}
The coefficents were optimized for the first and second order $(x_{fp}, x'_{fp})$ terms as well as for the cross terms, as the correlations
observed were not completely linear, as shown in the Figure \ref{fig:shmsDelta_beforeOptim}. After fitting the correlations and determining
the optimum coefficients, these were updated in the SHMS optics parameter file, and the data was replayed again.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.34]{plots/SHMS_DeltaDiff_AfterOptim3288.png}
  \caption{SHMS $(\delta_{calc}-\delta_{meas})$ vs. focal plane variables for H(e,e'p) Elastic run 3288 after $\delta$-optimization.}
  \label{fig:shmsDelta_afterOptim}
\end{figure}\\
From Figure \ref{fig:shmsDelta_afterOptim}, there is a noticeable improvement in the $(x_{fp}, x'_{fp})$, as the correlations have
been corrected, whereas in the $(y_{fp}, y'_{fp})$, the effect is less noticeable as these were not involved in the fit. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.3]{plots/Emiss_3288_FullOptim.png}
  \caption{Missing Energy Spectrum for H(e,e'p) Elastic run 3288 after central momentum correction and $\delta$-optimization.}
  \label{fig:shmsEm_afterOptim}
\end{figure}
\newpage
\indent From Figure \ref{fig:shmsEm_afterOptim}, after the SHMS central momentum correction and optimization, there
is a clear improvement in the missing energy spectrum. The improvents observed are
\begin{itemize}
\item Alignment of DATA Missing Energy to SIMC from the central momentum correction
\item Narrower width in DATA Missing Energy from $\delta$-optimization of the matrix coefficients.
\end{itemize}
The first bullet point is easy to understand, as the alignment is simply due to a change in the SHMS central momentum.
The second bullet point can be understood from the fact that since the SHMS $\delta_{meas}$ matrix coefficients
\footnote{The SHMS $\delta$ matrix coefficients are directly associated with the SHMS measured momentum on an event-by-event
  basis, so if these coefficients are optimized, the measured SHMS momentum is optimized, which directly affects where the
  Missing Energy event will be reconstructed.}
have been optimized, an event in the missing energy spectrum that would otherwise be reconstructed far away from the
main peak, is now reconstructed underneath the main peak resulting in an improvement in the resolution as well as in
the recovered events. 
\subsection{SHMS $(Y_{tar}, Y'_{tar}, X'_{tar})$ Optimization}
During the E12-10-003 experiment, an Optics run with the Centered Sieve was taken after the optics in SHMS Q3 were fixed. This data was used to
optimize the $(Y_{tar}, Y'_{tar}, X'_{tar})$ components of the reconstruction matrix. The target consists of three Carbon foils positioned at
(-10, 0, 10) cm to mimic the target Hall C target edges and center. The reconstructed the events back to each of the foils serve to check the optics.
The optimization code used is located at github repository \cite{shmsOpt_git_repo}. \\
\indent To check the optics, the SHMS $\delta$ vs. $Y_{tar}$ was plotted to verify how well is the $Y_{tar}$ reconstructed across $\delta$ for each of the
three foils. Below are the plots showing before and after the optimization.
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/SHMS_delta_vs_ytar_3286_beforeOptim.png}
  \caption{SHMS $\delta$ vs. $Y_{tar}$ for Carbon Sieve run 3286 before $Y_{tar}$-optimization.}
  \label{fig:shmsYtar_beforeOptim}
\end{figure}
\newpage
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/SHMS_delta_vs_ytar_3286_afterOptim.png}
  \caption{SHMS $\delta$ vs. $Y_{tar}$ for Carbon Sieve run 3286 after $Y_{tar}$-optimization.}
  \label{fig:shmsYtar_afterOptim}
\end{figure}
After the optimization, it is clear from Figure \ref{fig:shmsYtar_afterOptim} that there is almost no
correlation as compared to before optimization. The variables optimized, $(Y_{tar}, Y'_{tar}, X'_{tar})$ are
related to the in-plane and out-of-plane angles relative to the spectrometer central ray, so removing the correlation
in $Y_{tar}$ affects the the SHMS electron scattering angle. This in turn affects the location of the invariant mass peak as it depends
on the electron angle.
\section{Spectrometer Offstes} \label{sec:spec_off_sec}
\noindent The optics optimization was originally done assuming there were no spectrometer offsets. This is not true,
however, as there were still some small mis-alignments observed in the missing energy spectrum. An extensive study
of the spectrometer offsets in Hall C has not been done yet. For now, we have made a rough estimate on these
offsets based on observations in H(e,e'p) elastic run 3288, as it is closest in kinematic to the Deuteron 80 MeV setting.
\subsection{Central Angle Offsets}
\noindent The central angle offsets refer to the central ray spectrometer offsets in two cases:
\begin{itemize}
\item \textit{In-plane central angle offset} \texttt{[h(p)thetacentral\_offset]\footnote{The spectrometer offsets parameters can be found on \texttt{hallc\_replay/PARAM/(S)HMS/GEN/(s)hmsflags.param} \\ In general, it is not possible to know from which spectrometer is the offset originating, so the HMS was chosen in this case.}}
\item \textit{Out-of-plane central angle offset} \texttt{[h(p)\_oopcentral\_offset]}
\end{itemize}
The \textit{in-plane} is parallel to the Hall C floor, whereas the \textit{out-of-plane} is perpendicular to the Hall C floor.
The central angle offsets can be determined from the missing momentum components for H(e,e'p) elastics, as these should ideally be centered around
zero. In Hall Coordinate System (HCS), the in-plane central angle offset can be determined by taking the fractional dfference between
the measured (DATA) and expected (SIMC) X missing momentum component as follows:
\begin{equation}
  \delta \theta = \frac{P_{mx}^{SIMC} - P_{mx}^{DATA}}{P_{0}}
\end{equation}
The out-of-plane central angle offset can be determined by taking the fractional dfference between
the measured (DATA) and expected (SIMC) Y missing momentum component as follows:
\begin{equation}
  \delta \phi = \frac{P_{my}^{SIMC} - P_{my}^{DATA}}{P_{0}}
\end{equation}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.9]{plots/ORIGINAL_Pm_NOSpecOffsets.pdf}
  \caption{Missing Momentum components with NO spectrometer offsets applied.}
  \label{fig:PmComp_noOffsets}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.9]{plots/Oop_Pm_Offset.pdf}
  \caption{Missing Momentum components with Out-of-plane central offset applied.}
  \label{fig:PmComp_OopOffset}
\end{figure}\\

\noindent After applying the \textit{out-of-plane} offset, the Y-component of the missing momentum agrees with simulation as shown in Figure \ref{fig:PmComp_OopOffset}.
With respect to the X-component of the missing momentum, it was decided not to apply an \textit{in-plane} angle offset as
this would directly impact the location of the invariant mass peak. Alternatively, it was decided to apply a relative in-plane
angle offset which would align the X-component. This is discussed in the next sub-section.\\
\newpage
\subsection{Relative Angle Offsets}
The relative angle offsets refer to the angle offset relative to the spectrometer central ray. The two cases are:
\begin{itemize}
\item \textit{In-plane relative angle ($Y'_{tar}$) offset} \texttt{[h(p)theta\_offset]}
\item \textit{Out-of-plane relative angle ($X'_{tar}$) offset} \texttt{[h(p)phi\_offset]}
\end{itemize}
The $Y'_{tar}$ offset if directly related to the spectrometer angle, and therefore has a direct impact on the electron/hadron kinematics, depending on which
spectrometer is associated with the particle type. In the E12-10-003, this offset was determined for the HMS in order to align the X-component of the missing
momentum as well as to improved the HMS central momentum correction. Recall that in Section \ref{sec:hms_optics_sec} it was assumed that the proton (HMS) angle
was well known, which was not completely true. 
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.8]{plots/hxptar_offset_3288.pdf}
  \caption{HMS $X'_{tar}$ for run 3288 before (Left) and after (Right) applying the offset correction.}
  \label{fig:hxptar_Offset}
\end{figure} \\
Figure \ref{fig:hxptar_Offset} shows the relative out-of-plane angle distributions for all events within the spectrometer acceptance. The 'zero' value in the distribution
represents events whose trajectory was parallel to the central ray, whereas events away from the 'zero' value represents events that are at an out-of-plane angle relative
to the central ray. The $X'_{tar}$ offset was determined by 'eye', using the mean of the distribution. \\
\indent Similarly to the relative out-of-plane angle, the relative in-plane angles in the $Y'_{tar}$ distribution (not shown) represent angles relative to the central ray, with the
'zero' value representing particles parallel to the central ray. The $Y'_{tar}$ offset was determined based on how well the X-component of the missing momentum matched
the simulation, as well as how well did the HMS momentum from data matched that of simulation (See Figure \ref{fig:hms_Pcorr}). \\
\indent After determining the spectrometer offsets, a second iteration of the HMS and SHMS Optics check procedure was performed to obtain
improved results. Finally, the four H(e,e'p) elastic runs were used to determine the HMS momentum corrections for the D(e,e'p) data, to be discussed in the next section.
\section{HMS Momentum Calibration}
During the E12-10-003 experiment, the four H(e,e'p) elastics analyzed covered the HMS momentum range such that the D(e,e'p) data
momentum was within the range covered by the elastics. From this knowledge, one can determine the D(e,e'p) data momentum correction
from a simple linear fit of the H(e,e'p) data. 
\newpage
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.4]{plots/HMS_Pcorr_Fit.pdf}
  \caption{HMS Momentum Correction for H(e,e'p) and D(e,e'p)n. }
  \label{fig:hms_Pcorr}
\end{figure} 
\indent From Figure \ref{fig:hms_Pcorr}, the momentum correction factor is plotted against the original HMS central momentum and the
four data points are fitted with a straight line. Using the line fit, the D(e,e'p)n momentum correction for the three missing
momentum settings are determined from the D(e,e'p)n original HMS momentum setting. The table below summarizes the
correction to the D(e,e'p)n data HMS momentum settings.
\begin{table}[ht]
\begin{tabular}{c c c c c}
\hline\hline
\shortstack{$P_{m}$ \\ Setting [GeV]}  & \shortstack{HMS \\ Angle [deg]} & \shortstack{HMS \\ Momentum [GeV]} & \shortstack{SHMS \\ Angle [deg]} & \shortstack{SHMS \\ Momentum [GeV]} \\
\hline
80 & 38.896 & 2.8438 & 12.194 & 8.7 \\
580 (set1) & 54.992 & 2.194 & 12.194 & 8.7 \\
580 (set2) & 55.000 & 2.194 & 12.194 & 8.7 \\
750 (set1) & 58.391 & 2.091 & 12.194 & 8.7 \\
750 (set2) & 58.394 & 2.091 & 12.194 & 8.7 \\
750 (set3) & 58.391 & 2.091 & 12.210 & 8.7 \\
\hline
\end{tabular}
\label{table:original_deep_kin}
\caption{Original D(e,e'p)n Kinematics for E12-10-003.}
\end{table}
\begin{table}[h!]
\begin{tabular}{c c c c c}
\hline\hline
\shortstack{$P_{m}$ \\ Setting [GeV]}  & \shortstack{HMS \\ Angle [deg]} & \shortstack{HMS \\ Momentum [GeV]} & \shortstack{SHMS \\ Angle [deg]} & \shortstack{SHMS \\ Momentum [GeV]} \\
\hline
80 & 38.896 & 2.840 & 12.194 & 8.5342 \\
580 (set1) & 54.992 & 2.1925 & 12.194 & 8.5342 \\
580 (set2) & 55.000 & 2.1925 & 12.194 & 8.5342 \\
750 (set1) & 58.391 & 2.0915 & 12.194 & 8.5342 \\
750 (set2) & 58.394 & 2.0915 & 12.194 & 8.5342 \\
750 (set3) & 58.391 & 2.0915 & 12.210 & 8.5342 \\
\hline
\end{tabular}
\label{tab:corr_deep_kin}
\caption{Corrected D(e,e'p)n Kinematics for E12-10-003.}
\end{table}\\
The Table above shows the corrected HMS momentum for the deuteron kinematics. Since the SHMS momentum was un-changed during the experiment,
the single correction factor determined from the H(e,e')p data analysis applies for all runs. 
%Bibliography
\newpage
\onecolumn
\bibliography{d2_optim.bib}
\bibliographystyle{abbrv}

%APPENDIX
%\newpage
%\begin{appendices}
%\appendix
%\section{Appdx Section 1}
%\subsection{SubSection 1 . . .}
%\label{appendix:AppxA1}
%\end{appendices}

\end{document}

### 2019-08-29 MY_PUBLICATIONS/PRL/prl.tex
updated PRL format

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math

% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

\begin{document}

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version xx as of \today}
\leftline{Primary authors: Carlos Yero}
\leftline{To be submitted to (PRL, PRD-RC, PRD, PLB; choose one.)}
\leftline{Comment to {\tt d0-run2eb-nnn@fnal.gov} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

% the following line is for submission, including submission to the arXiv!!
%\hspace{5.2in} \mbox{Fermilab-Pub-04/xxx-E}

\title{Template for PRL/PRD Papers}
\input author_list.tex       % D0 authors (remove the first 3 lines
                             % of this file prior to submission, they
                             % contain a time stamp for the authorlist)
                             % (includes institutions and visitors)
\date{\today}

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. It is used for
secondary publications and for information retrieval purposes.
For PRL, the rule of thumb is that the abstract should be less than
8 lines and the text (excluding authors, abstract but including tables,
figures and references) should be less than 4 pages (leave about 20 lines
empty on page 4) in two-column format.
PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
relevant to your paper. A set of standard references can be found at the
end of this example paper.
\end{abstract}

\pacs{}
\maketitle

%\section{\label{sec:level1}First-level heading}
% sections are not used for PRL papers

This sample document demonstrates proper use of REV\TeX~4 (and
\LaTeXe) in mansucripts prepared for submission to APS
journals. Further information can be found in the REV\TeX~4
documentation included in the distribution or available at
\url{http://publish.aps.org/revtex4/}.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended. Note that top-level section headings are
automatically uppercased. If a specific letter or word should appear in
lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
in the word ``via'' above.

%\subsection{\label{sec:level2}Second-level heading: Formatting}
% subsections are not used for PRL papers

This file may be formatted in both the \texttt{preprint} and
\texttt{twocolumn} styles. \texttt{twocolumn} format may be used to
mimic final journal output. Either format may be used for submission
purposes; however, for peer review and production, APS will format the
article using the \texttt{preprint} class option. Hence, it is
essential that authors check that their manuscripts format acceptably
under \texttt{preprint}. Manuscripts submitted to APS that do not
format correctly under the \texttt{preprint} option may be delayed in
both the editorial and production processes.

The \texttt{widetext} environment will make the text the width of the
full page.  The width-changing commands only take effect in \texttt{twocolumn}
formatting. It has no effect if \texttt{preprint} formatting is chosen
instead.

To cite bibliography entries, use the \verb+\cite{#1}+ command. Most
journal styles will display the corresponding number(s) in square
brackets: \cite{d0det}. To avoid the square brackets, use
\verb+\onlinecite{#1}+: Refs.~\onlinecite{d0det} and
\onlinecite{geant,pythia}. REV\TeX\ ``collapses'' lists of
consecutive reference numbers where possible. We now cite everyone
together \cite{geant, pythia, cteq}, and once again
(Refs.~\onlinecite{geant, pythia, cteq}). Note that the references
were also sorted into the correct numerical order as well.

Footnotes are produced using the \verb+\footnote{#1}+ command. Most
APS journal styles put footnotes into the bibliography. REV\TeX~4 does
this as well, but instead of interleaving the footnotes with the
references, they are listed at the end of the references. Because the correct
numbering of the footnotes must occur after the numbering of the
references, an extra pass of \LaTeX\ is required in order to get the
numbering correct.

Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations; this is the most common
type of equation in \textit{Physical Review}:
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within a narrow column this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}.
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

Figures may be inserted by using either the \texttt{graphics} or
\texttt{graphicx} packages. These packages both define the
\verb+\includegraphics{#1}+ command, but they differ in how optional
arguments for specifying the orientation, scaling, and translation of the
figure. Fig.~\ref{fig:epsart} shows a figure that is small enough to
fit in a single column. It is embedded using the \texttt{figure}
environment which provides both the caption and the imports the figure
file.

\begin{figure}
\includegraphics[scale=0.8]{fig_1.ps}
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}

Fig.~\ref{fig:wide} is a figure that is too wide for a single column,
so instead the \texttt{figure*} environment has been used.
\begin{figure*}
\includegraphics{fig_2.ps}% Here is how to import EPS art
\caption{\label{fig:wide}Use the figure* environment to get a wide
figure that spans the page in \texttt{twocolumn} formatting.}
\end{figure*}

The heart of any table is the \texttt{tabular} environment which gives
the rows of the tables. Each row consists of column entries separated
by \verb+&+'s and terminates with \textbackslash\textbackslash. The
required argument for the \texttt{tabular} environment
specifies how data are displayed in the columns. For instance, entries
may be centered, left-justified, right-justified, aligned on a decimal
point. Extra column-spacing may be be specified as well, although
REV\TeX~4 sets this spacing so that the columns fill the width of the
table. Horizontal rules are typeset using the \verb+\hline+
command. The doubled (or Scotch) rules that appear at the top and
bottom of a table can be achieved enclosing the \texttt{tabular}
environment within a \texttt{ruledtabular} environment. Rows whose
columns span multiple columns can be typeset using the
\verb+\multicolumn{#1}{#2}{#3}+ command (for example, see the first
row of Table~\ref{tab:table3}).

Tables~\ref{tab:table1}-\ref{tab:table4} show various effects. Tables
that fit in a narrow column are contained in a \texttt{table}
environment. Table~\ref{tab:table3} is a wide table set with the
\texttt{table*} environment. Long tables may need to break across
pages. The most straightforward way to accomplish this is to specify
the \verb+[H]+ float placement on the \texttt{table} or
\texttt{table*} environment. However, the standard \LaTeXe\ package
\texttt{longtable} will give more control over how tables break and
will allow headers and footers to be specified for each page of the
table. A simple example of the use of \texttt{longtable} can be found
in the file \texttt{summary.tex} that is included with the REV\TeX~4
distribution.

There are two methods for setting footnotes within a table (these
footnotes will be displayed directly below the table rather than at
the bottom of the page or in the bibliography). The easiest
and preferred method is just to use the \verb+\footnote{#1}+
command. This will automatically enumerate the footnotes with
lowercase roman letters. However, it is sometimes necessary to have
multiple entries in the table share the same footnote. In this case,
there is no choice but to manually create the footnotes using
\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
\texttt{\#1} is a numeric value. Each time the same value for
\texttt{\#1} is used, the same mark is produced in the table. The
\verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
environment. Examine the \LaTeX\ source and output for
Tables~\ref{tab:table1} and \ref{tab:table2} for examples.

\begin{table}
\caption{\label{tab:table1}This is a narrow table which fits into a
narrow column when using \texttt{twocolumn} formatting. Note that
REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically. This table illustrates left-aligned, centered, and
right-aligned columns.  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
\hline
1 & 2 & 3\\
10 & 20 & 30\\
100 & 200 & 300\\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}
\caption{\label{tab:table2}A table with more columns still fits
properly in a column. Note that several entries share the same
footnote. Inspect the \LaTeX\ input for this table to see
exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{pdg}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}

\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the page
width in \texttt{twocolumn} mode. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

\begin{table}
\caption{\label{tab:table4}Numbers in columns Three--Five have been
aligned by using the ``d'' column specifier (requires the
\texttt{dcolumn} package). Non-numeric entries (those entries without
a ``.'') in a ``d'' column are aligned on the decimal point. Use the
``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}

\textit{Physical Review} style requires that the initial citation of
figures or tables be in numerical order in text, so don't cite
Fig.~\ref{fig:wide} until Fig.~\ref{fig:epsart} has been cited.

%\input acknowledgement.tex   % input acknowledgement

\begin{thebibliography}{99}

  \bibitem{d0det}
    Standard D\O\ detector reference:  \\
V.M.~Abazov {\sl et al.} (D0 Collaboration),
Nucl. Instrum. Methods Phys. Res. A {\bf 565}, 463  (2006).

  \bibitem{d0lumi}
    ** New ** D\O\ luminosity reference: \\
T.~Andeen {\sl et al.}, FERMILAB-TM-2365 (2007).

  \bibitem{pdg}
   Particle Data Group reference: \\
   W.-M.~Yao {\sl et al.}, Journal of Physics G {\bf 33}, 1 (2006).

  \bibitem{geant}
    {\sc Geant} reference: \\
    R. Brun and F. Carminati, CERN Program Library Long Writeup W5013, 1993 (unpublished).

  \bibitem{pythia}
    {\sc Pythia} reference: \\
    T. Sj\"{o}strand {\sl et al.}, Comput. Phys. Commun. {\bf 135}, 238 (2001).

  \bibitem{cteq}
    {\sc Cteq6} reference: \\
    J. Pumplin {\sl et al.}, JHEP {\bf 0207} 012 (2002) and
    D. Stump {\sl et al.}, JHEP {\bf 0310} 046 (2003).

  \bibitem{cls}
    LEP CL$_S$ reference: \\
    T. Junk, Nucl. Instrum. Methods A {\bf 434}, 435 (1999).

  \bibitem{d0limit}
   D\O\ Bayesian reference: \\
   I. Bertram {\sl et al.}, FERMILAB-TM-2104 (2000).

  \bibitem{d0jets}
  D\O\ cone-jet reference: \\
G.C.~Blazey {\it et al.}, in
{\sl Proceedings of the Workshop: QCD and Weak Boson
Physics in Run II,} edited by U.~Baur, R.K.~Ellis, and
D. Zeppenfeld, Fermilab-Pub-00/297 (2000).

\end{thebibliography}

\end{document}
%
% ****** End of file template.aps ******

### 2019-09-16 MY_THESIS/SYSTEMATICS/syst.tex
add deuteron articles

\documentclass[11pt]{article}

\usepackage{url}
\usepackage[hyperfootnotes=false]{hyperref}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage[usenames, dvipsnames]{color}
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
\usepackage{graphicx}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[top=0.6 in, bottom=0.7 in, left=0.7in, right=0.7in]{geometry}
\usepackage{setspace}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tgtermes}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

\usepackage{epstopdf}

\title{\textbf{Systematics from Correction Factors}}

\begin{document}
\maketitle

Starting from the experimental cross section,

\begin{equation}
  \sigma^{exp} = \sigma^{exp}_{uncorr} \cdot f_{1} \cdot f_{2} . . . \cdot f_{n}
\end{equation}
where $\sigma^{exp}_{uncorr}$ is the uncorrected Yield divided by the SIMC phase space, and $f_{n}'s$ are the correction factors,

\begin{align*}
  f_{1} &= \frac{1}{1-m\cdot I_{avg}}   \hspace{2cm}  \text{        target boiling factor, where $m$ is the slope} \\
  f_{2} &= \frac{1}{p_{T}}              \hspace{4cm}   \text{proton transmission factor}  \\
  f_{3} &= \frac{1}{\epsilon_{eTrk}}   \hspace{4cm}   \text{e-  tracking efficiency} \\
  f_{4} &= \frac{1}{\epsilon_{hTrk}}   \hspace{4cm}   \text{h  tracking efficiency} \\
  f_{5} &= \frac{1}{\epsilon_{tLT}}   \hspace{4cm}   \text{total live time} \\
  f_{6} &= \frac{1}{Q_{tot}}          \hspace{4cm}   \text{total charge} \\
  f_{7} &= f_{rad} \hspace{4cm}   \text{radiative correction factor} \\
  f_{8} &= f_{bc}  \hspace{4cm}   \text{bin-centering correction factor} \\
\end{align*}
The systematic uncertainty on the cross section due to the uncertainty in each of these correction factors is
\begin{align}
  (d\sigma^{exp}_{syst})^{2} = \sum_{i=1}^{8} \Big( \frac{\partial\sigma^{exp}}{\partial f_{i}}\Big)^{2} df_{i}^{2}
\end{align}
If the derivative with respect to factor $f_{i}$ is
\begin{equation}
  \frac{\partial\sigma^{exp}}{\partial f_{i}} = \frac{\sigma^{exp}}{f_{i}}
\end{equation}
Substituting (3) in (2), one obtains
\begin{align}
  (d\sigma^{exp}_{syst})^{2} = (\sigma^{exp})^{2}\sum_{i=1}^{8} \Big( \frac{df_{i}}{f_{i}}\Big)^{2}
\end{align}
For a given data set with multiple runs, the correction factor might differ from run to run, for example, the tracking efficiencies or total
live time might be slightly different. In this case, the correction factor and its uncertainty is calculated for each run.  The weighted average is
then determined as follows: \\
Define a weight, $w$, 
\begin{equation}
  w_{i} \equiv \frac{1}{df_{i}^{2}}
\end{equation}
where the sum is over all run numbers, and $\sigma_{i}$ is the uncertainty in the correction factor $f_{i}$ for the $i$ run.
The weighted average and its uncertainty on the correction factor can then be expressed as
\begin{align}
  f_{w} &= \frac{\sum_{i}f_{i}w_{i}}{\sum_{i}w_{i}} \\
  d_{fw} &= \frac{1}{\sqrt{\sum_{i}w_{i}}}
\end{align}
where (6) and (7) are the correction factor and its uncertainty for a given experimental data set.
Substituting (6) and (7) in (4) would then give the total systematic uncertainty for  that particular data set.
Each of the $(P_{m}, \theta_{nq})$ for that data set would have a specific cross section, $\sigma_{exp}$, but all
bins would have the same systematic error, $d_{fw}$.

\end{document}

### 2019-10-09 DNP_Meetings/abstract/abstract.tex
updated DNP

--- 2019-06-30 DNP_Meetings/abstract_corrected.tex
@@
 \small
-for the Hall C Collaboration
+Spokespeople: Drs. Werner U. Boeglin and Mark K. Jones
 
@@
 
-\noindent Preliminary D(e,e'p)n electro-disintegration cross sections at $Q^{2} = 4.25$ GeV$^{2}$ with recoil
-momenta up to 900 MeV/c will be presented. The experiment ran for a total of 6 days of beam time in April 2018
-at Jefferson Lab in Hall C and it seeks to study the short range structure of the deuteron by probing its high
-momentum components beyond 500 MeV/c, where currently no data exists. The experiment was part of a group of Hall C
-experiemnts that commissioned the new Hall C Super High Momentum Spectrometer (SHMS). At the selected kinematics,
-Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. Final State Interactions (FSI) have also
-been suppressed by choosing a kinematic region where the neutron recoil angle is between 35 and 45 degrees with respect
-to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment (Boeglin et al. Phys Rev Lett. 2011)
-and is also predicted in modern theoretical calculations (W. Boeglin \& M. Sargsian Int.J.Mod.Phys. 2015). In this region,
-the Plane Wave Impulse Approximation (PWIA) dominates and comparisions between measured and predicted cross sections are
-sensitive to the deuteron momentum distributions. Comparisons between data and different calculations with different NN
-potentials will be shown.
+\noindent Preliminary D(e,e'p)n electro-disintegration cross sections at $Q^{2} = 4.25$ GeV$^{2}$ with recoil momenta up to 900 MeV/c will be
+presented. The experiment ran for a total of 6 days of beam time in April 2018 at Jefferson Lab in Hall C
+and it seeks to study the short range structure of the deuteron by probing its high momentum tails
+beyond 500 MeV/c, where currently no data exists. The experiment was part of a group of Hall C experiemnts that commissioned the
+the new Hall C Super High Momentum Spectrometer (SHMS). At these kinematics, Meson Exchange Currents (MEC) and Isobar Configurations (IC)
+are suppressed. Final State Interactions (FSI), however, can be important. From theoretical calculations by M. Sargsian in
+"Modern Studies of the Deuteron: from the Lab Frame to the Light Front" (Boeglin, W.U. and Sargsian, M.M. Int.J.Mod.Phys. 2015),
+FSI can be suppressed by choosing a kinematic region where the neutron recoil angle is between 35 and 45 degrees. This suppression
+was seen in a previous D(e,e'p)n experiment that went to recoil momentum of 500 MeV/c. See for example, "Probing the High Momentum Component
+of the Deuteron at High Q2" (Boeglin, W.U. et al. Phys Rev Lett. 2011). In this region, the Plane Wave Impulse Approximation (PWIA) is valid
+and comparisions between measured and predicted cross sections have a sensitivity to the different NN potentials. Comparisons between the data
+and different theory calculations with different NN potentials will be shown.
 

### 2019-10-09 MY_PUBLICATIONS/latex_templates/prl.tex
updated DNP

--- 2019-08-29 MY_PUBLICATIONS/PRL/prl.tex
@@
 \usepackage{amssymb}   % for math
-
+\usepackage[hidelinks]{hyperref}
+\usepackage{xcolor}
+\hypersetup{
+    colorlinks,
+    linkcolor={red!50!black},
+    citecolor={blue!80!black},
+    urlcolor={blue!80!black}
+}
 % avoids incorrect hyphenation, added Nov/08 by SSR
@@
 were also sorted into the correct numerical order as well.
+\cite{einstein}
 
@@
 
-%\input acknowledgement.tex   % input acknowledgement
+\input acknowledgement.tex   % input acknowledgement
 
-\begin{thebibliography}{99}
-
-  \bibitem{d0det}
-    Standard D\O\ detector reference:  \\
-V.M.~Abazov {\sl et al.} (D0 Collaboration),
-Nucl. Instrum. Methods Phys. Res. A {\bf 565}, 463  (2006).
-
-  \bibitem{d0lumi}
-    ** New ** D\O\ luminosity reference: \\
-T.~Andeen {\sl et al.}, FERMILAB-TM-2365 (2007).
-
-  \bibitem{pdg}
-   Particle Data Group reference: \\
-   W.-M.~Yao {\sl et al.}, Journal of Physics G {\bf 33}, 1 (2006).
-
-  \bibitem{geant}
-    {\sc Geant} reference: \\
-    R. Brun and F. Carminati, CERN Program Library Long Writeup W5013, 1993 (unpublished).
-
-  \bibitem{pythia}
-    {\sc Pythia} reference: \\
-    T. Sj\"{o}strand {\sl et al.}, Comput. Phys. Commun. {\bf 135}, 238 (2001).
-
-  \bibitem{cteq}
-    {\sc Cteq6} reference: \\
-    J. Pumplin {\sl et al.}, JHEP {\bf 0207} 012 (2002) and
-    D. Stump {\sl et al.}, JHEP {\bf 0310} 046 (2003).
-
-  \bibitem{cls}
-    LEP CL$_S$ reference: \\
-    T. Junk, Nucl. Instrum. Methods A {\bf 434}, 435 (1999).
-
-  \bibitem{d0limit}
-   D\O\ Bayesian reference: \\
-   I. Bertram {\sl et al.}, FERMILAB-TM-2104 (2000).
-
-  \bibitem{d0jets}
-  D\O\ cone-jet reference: \\
-G.C.~Blazey {\it et al.}, in
-{\sl Proceedings of the Workshop: QCD and Weak Boson
-Physics in Run II,} edited by U.~Baur, R.K.~Ellis, and
-D. Zeppenfeld, Fermilab-Pub-00/297 (2000).
-
-\end{thebibliography}
+\bibliography{prl}
 

### 2019-10-10 MY_PUBLICATIONS/PRL/prl.tex
add deuteron articles
update PRL

@@
 \leftline{Version xx as of \today}
-\leftline{Primary authors: Carlos Yero}
-\leftline{To be submitted to (PRL, PRD-RC, PRD, PLB; choose one.)}
-\leftline{Comment to {\tt d0-run2eb-nnn@fnal.gov} by xxx, yyy}
+\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
+\leftline{To be submitted to PRL}
+\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
 \centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
 
-\title{Template for PRL/PRD Papers}
+\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}}
 \input author_list.tex       % D0 authors (remove the first 3 lines
@@
 \begin{abstract}
-An article usually includes an abstract, a concise summary of the work
-covered at length in the main body of the article. It is used for
-secondary publications and for information retrieval purposes.
-For PRL, the rule of thumb is that the abstract should be less than
-8 lines and the text (excluding authors, abstract but including tables,
-figures and references) should be less than 4 pages (leave about 20 lines
-empty on page 4) in two-column format.
-PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
-Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
-relevant to your paper. A set of standard references can be found at the
-end of this example paper.
+  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
+  neutron recoil momenta from 0.460 GeV/c up to 1.14 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
+  Configurations (IC) are suppressed. Final State Interactions have also been suppressed by choosing a kinematic region where the neutron recoil
+  angle is between 35 and 45 degrees with respect to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment \cite{halla_deut_2011}
+  and is also predicted in modern theoretical calculations \cite{sargsian_2015}. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and
+  comparisons between measured and predicted cross sections become sensitive to the deuteron momentum distributions.
+
+%  momentum distribution has been determined from measured for neutron recoil momenta up to 1.14 GeV/c.
+
+  %An article usually includes an abstract, a concise summary of the work
+%covered at length in the main body of the article. It is used for
+%secondary publications and for information retrieval purposes.
+%For PRL, the rule of thumb is that the abstract should be less than
+%8 lines and the text (excluding authors, abstract but including tables,
+%figures and references) should be less than 4 pages (leave about 20 lines
+%empty on page 4) in two-column format.
+%PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
+%Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
+%relevant to your paper. A set of standard references can be found at the
+%end of this example paper.
 \end{abstract}
@@
 
-\begin{table}
-\caption{\label{tab:table1}This is a narrow table which fits into a
-narrow column when using \texttt{twocolumn} formatting. Note that
-REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
-entire width of the column. Table captions are numbered
-automatically. This table illustrates left-aligned, centered, and
-right-aligned columns.  }
-\begin{ruledtabular}
-\begin{tabular}{lcr}
-Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
-\hline
-1 & 2 & 3\\
-10 & 20 & 30\\
-100 & 200 & 300\\
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-
-\begin{table}
-\caption{\label{tab:table2}A table with more columns still fits
-properly in a column. Note that several entries share the same
-footnote. Inspect the \LaTeX\ input for this table to see
-exactly how it is done.}
-\begin{ruledtabular}
-\begin{tabular}{cccccccc}
- &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
- &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
-\hline
-Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
-& 0.680 & 1.870 & 3.700 \\
-Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
-& 0.450 & 1.930 & 3.760 \\
-Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
-& 0.750 & 2.170 & 3.560 \\
-Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
-& 0.900 & 2.370 & 3.720 \\
-Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
-& 0.380 & 1.730 & 2.830 \\
-Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
-& 0.760 & 2.110 & 3.120 \\
-Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
-&  1.120 & 2.620 & 3.480 \\
-Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
-& 1.330 & 2.800 & 3.590 \\
-Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
-& 1.420 & 3.030 & 3.740 \\
-In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
-& 0.960 & 2.460 & 3.780 \\
-Tl& 0.480 & 18.90 & 3.550 & & & & \\
-\end{tabular}
-\end{ruledtabular}
-\footnotetext[1]{Here's the first, from Ref.~\onlinecite{pdg}.}
-\footnotetext[2]{Here's the second.}
-\footnotetext[3]{Here's the third.}
-\footnotetext[4]{Here's the fourth.}
-\footnotetext[5]{And etc.}
-\end{table}
-
-\begin{table*}
-\caption{\label{tab:table3}This is a wide table that spans the page
-width in \texttt{twocolumn} mode. It is formatted using the
-\texttt{table*} environment. It also demonstates the use of
-\textbackslash\texttt{multicolumn} in rows with entries that span
-more than one column.}
-\begin{ruledtabular}
-\begin{tabular}{ccccc}
- &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
- Ion&1st alternative&2nd alternative&lst alternative
-&2nd alternative\\ \hline
- K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
- Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
- &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
- Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
- &$(4e)^{\text{a}}$\\
- He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
- Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
-\end{tabular}
-\end{ruledtabular}
-\end{table*}
-
-\begin{table}
-\caption{\label{tab:table4}Numbers in columns Three--Five have been
-aligned by using the ``d'' column specifier (requires the
-\texttt{dcolumn} package). Non-numeric entries (those entries without
-a ``.'') in a ``d'' column are aligned on the decimal point. Use the
-``D'' specifier for more complex layouts. }
-\begin{ruledtabular}
-\begin{tabular}{ccddd}
-One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
-\hline
-one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
-He&2& 2.77234 & 45672. & 0.69 \\
-C\footnote{Some tables require footnotes.}
-  &C\footnote{Some tables need more than one footnote.}
-  & 12537.64 & 37.66345 & 86.37 \\
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-
 \textit{Physical Review} style requires that the initial citation of

### 2019-10-19 MY_PUBLICATIONS/PRL/prl.tex
updated

@@
 \begin{abstract}
-  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
-  neutron recoil momenta from 0.460 GeV/c up to 1.14 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
-  Configurations (IC) are suppressed. Final State Interactions have also been suppressed by choosing a kinematic region where the neutron recoil
-  angle is between 35 and 45 degrees with respect to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment \cite{halla_deut_2011}
-  and is also predicted in modern theoretical calculations \cite{sargsian_2015}. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and
-  comparisons between measured and predicted cross sections become sensitive to the deuteron momentum distributions.
+  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
+  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
+  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
+  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
+  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.
 
@@
 % sections are not used for PRL papers
+
+%--------------MOTIVATION / introduction (from my proposal)--------------
 

### 2019-10-19 MY_THESIS/Heep_Minimization/code/genfit.py

@@ -1,0 +1,127 @@
+import numpy as np
+import LT.box as B
+import LT.datafile as dfile
+import LT_Fit.parameters as P
+import LT_Fit.linear_fit as gen_linfit 
+#import LT_fit.gen_fit as G
+
+dtr = np.pi / 180.
+
+Mp = 938.272
+kin = B.get_file('hms_kin-2.txt')
+run = kin['Run']
+
+Eb = np.array(kin['beam_e']) * 1e3
+Ef = np.array(kin['nmr_P']) * 1e3
+th_e = np.array(kin['hms_Angle']) * dtr 
+dataW = np.array(kin['data_W_mean']) * 1e3
+simcW = np.array(kin['simc_W_mean']) * 1e3
+
+Q2 = 4.*Eb*Ef*np.sin(th_e/2.)**2
+omega = Eb - Ef
+W = np.sqrt(Mp**2 + 2.*Mp*omega - Q2)
+
+
+dW_obs = dataW - simcW
+dW_obs_err = Eb * 8000. *2.5e-5 / Ef
+
+
+
+#x = np.arange(16) + 1  #array of 1-16
+#derivative of W with respect to beam energy
+dW_dEb = Ef / Eb *Eb      
+#derivative of W with respect to final e- energy
+dW_dEf = -Eb / Ef * Ef    
+#derivative of W with respect to e- angle
+dW_dthe = -2.*Eb*Ef/Mp * np.sin(th_e/2.) * np.cos(th_e/2.)
+
+#Get Initial Relative uncertainties based on dW observations
+#These are used to estimate the boundary, or how large should 
+#we set the rel. uncertainty. (pmin, pmax) in the chi2Min code
+F0 = dW_dEb        #p1 = dEb / Eb    
+F1 = dW_dEf 
+F2 = dW_dthe    
+
+
+#--------------------------------------------------------------------------------------------------------------------
+#FIT FUNCTION
+# dW = a0*dW_dEb + a1*dE_dEf + a2*dW_dthe
+#
+# the a0, a1 and a2 are the common offsets that get the best fit for all data
+
+#dW/dEb * Eb
+def f0(x):
+    return F0[np.floor((x+0.5)).astype(int)]
+
+#dW/dE' * E'
+def f1(x):
+    return F1[np.floor((x+0.5)).astype(int)]
+
+#dW/dth_e 
+def f2(x):
[…]

### 2019-10-19 MY_THESIS/Heep_Minimization/code/heep_svd_hms.C

@@ -1,0 +1,314 @@
+#include <TMatrixD.h>
+#include <TVectorD.h>
+#include <TDecompSVD.h>
+
+//This code uses equations W, Em and Pmx, Pmz to sole a linear system to determine the
+//parameters dEf/Ef and dth_e that minimizes the observed and predicted quantities
+
+void heep_svd_hms()
+{
+
+  ifstream ifile;
+
+  const int runs = 11;
+  const int sel = 8;
+  
+  int run[runs] = {6595, 6601, 6602, 6609, 6611, 6634, 6871, 6875, 6876, 6879, 6881};
+  
+  //Define the variables
+  Double_t dtr = TMath::Pi() / 180.;
+  Double_t Mp = 0.938272;
+  Double_t Eb[runs] = {3.83350, 3.83350, 3.83350, 3.83350, 3.83350, 3.83350, 4.93090, 4.93090, 4.93090, 4.93090, 4.93090};
+  
+  Double_t Ef[runs] = {3.007, 2.834, 2.713, 2.583, 2.478, 2.026, 4.371, 4.184, 3.923, 2.583, 3.124};	      
+  Double_t th_e[runs] = {21.12, 23.980, 25.970, 29.185, 29.985, 38.60, 12.710, 15.00, 18.02, 34.23, 27.17};  
+
+  //assume out of plane angles in e- and p are zero. (variations are only due to in-plane quantities)
+  Double_t ph_e = 0;  
+
+  //Define the measured DATA, SIMC variables
+  Double_t Wdata[runs] = {
+    0.936719, 
+    0.935986, 
+    0.93657,  
+    0.936574, 
+    0.936519, 
+    0.939933, 
+    0.927885, 
+    0.929253, 
+    0.928928, 
+    0.931178, 
+    0.929532 
+  };
+  
+  Double_t Wdata_err[runs] = {
+    4.99386e-05,
+    6.69785e-05,
+    5.48703e-05,
+    6.96459e-05,
+    6.25866e-05,
+    0.000157911,
+    5.70411e-05,
+    8.05051e-05,
+    7.80849e-05,
+    0.000290841,
+    0.00026315 
+  };
+  
+  Double_t Wsimc[runs] = {
+    0.942444, 
+    0.942659, 
+    0.942793, 
+    0.942835, 
+    0.942942, 
+    0.943459, 
+    0.942053, 
+    0.94229,  
+    0.942498, 
+    0.943798, 
+    0.943418 
[…]

### 2019-10-19 MY_THESIS/Heep_Minimization/code/heep_svd_v3.C

@@ -1,0 +1,380 @@
+#include <TMatrixD.h>
+#include <TVectorD.h>
+#include <TDecompSVD.h>
+
+//This code uses equations W, Em and Pmx, Pmz to sole a linear system to determine the
+//parameters dEf/Ef and dth_e that minimizes the observed and predicted quantities
+
+void heep_svd_v3()
+{
+
+  ifstream ifile;
+
+
+  
+  int runs[4] = {3288, 3371, 3374, 3377};
+
+  //Define the variables
+  Double_t dtr = TMath::Pi() / 180.;
+  Double_t Mp = 0.938272;
+  Double_t Eb = 10.6005;
+  Double_t Ef = 8.5342488;
+  Double_t Pp[4] = {2.935545, 3.47588, 2.310387, 1.891227};
+  Double_t th_e[4] = {12.194, 13.930, 9.928, 8.495};
+  Double_t th_p[4] = {37.338, 33.545, 42.9, 47.605};
+  //assume out of plane angles in e- and p are zero. (variations are only due to in-plane quantities)
+  Double_t ph_e = 0;  
+  Double_t ph_p = 0;
+
+  //Define the measured DATA, SIMC variables
+  Double_t Wdata[4] = {9.42152e-01, 9.40229e-01, 9.43825e-01, 9.55773e-01};
+  Double_t Wdata_err[4] = {9.71583e-05,  3.77469e-04, 6.01623e-05, 4.13486e-05};
+
+  Double_t Wsimc[4] = {9.44690e-01, 9.44480e-01, 9.43591e-01, 9.42933e-01};
+  Double_t Wsimc_err[4] = {1.38566e-04, 6.68696e-05,  2.81437e-05, 2.23158e-05};
+
+  Double_t Emdata[4] = {6.58010e-03, 5.28983e-03, 6.26642e-03, 5.32021e-03};
+  Double_t Emdata_err[4] = {4.69566e-05,  1.47900e-04,  3.65940e-05, 4.14000e-05}; 
+
+  Double_t Emsimc[4] = {5.51066e-03, 6.06886e-03, 6.58531e-03, 6.47356e-03};
+  Double_t Emsimc_err[4] = {9.05496e-05, 3.84833e-05,  1.74941e-05, 1.37620e-05}; 
+
+  Double_t PmXdata[4] = {-1.29097e-03, -9.93560e-04, -5.53961e-04, 7.13300e-03};
[…]

### 2019-10-19 MY_THESIS/Heep_Minimization/code/test.C

@@ -1,0 +1,12 @@
+void test()
+{
+  string file = "test.txt";
+  double cola, colb, colc;
+  ifstream in(file);
+
+  while(!in.eof()){
+    //in >> cola;
+    //in >> colb;
+    //in >> colc;
+  }
+}

### 2019-10-19 MY_THESIS/SYSTEMATICS/D2_Cut_Systematics/Kin_Syst/analyze_differ.py

@@ -1,0 +1,204 @@
+import numpy  as np
+dtr = np.pi/180.
+
+
+def get_sig_tot(differ_file='',  ftable_name='', ftable_bin = np.array([]), print_all = False):
+    data = open(differ_file).readlines()
+    found = 0
+    
+    # This is where you enter the estimated uncertainties
+    # sigma in mr 
+
+    #Values were taken from SHMS Coin. Chi2 Min. MODEL 01, where Eb, Ef, th_e, th_f are determined simultaneously
+    #electron arm uncertainties
+    sig_the = 0.1659    #electron theta_e (in-plane, horizontal) uncertainty in mr
+    sig_phe = 0.    #electron phi_e (out-of-plane, vertical) uncertainty in mr
+    
+    #proton (or hadron) arm uncertainties
+    sig_thp = 0.2369    #proton theta_p (in-plane, horizontal) uncertainty mr 
+    sig_php = 0.    #proton phi_p (out-of-plane, vertical) uncertainty mr
+    
+    #beam direction uncertainties (need to ask Mark Jones)
+    sig_thb = 0.     #beam theta_b (out-of-plane, vertical, YES! IT IS OPPOSITE) uncertainty
+    sig_phb = 0.     #beam phi_b (in-plane, horizontal, YES! IT IS OPPOSITE) uncertainty
+    
+    # relative sigma
+    #final electron energy relative uncertainty (dEf/Ef)
+    sig_ef = 9.132e-4
+    #beam energy relative uncertainty (dEb / Eb)
+    sig_E = 7.498e-4   
+    
+    #Covariance Errors (Errors due to the correlation between different kinematic variables)
+    #For now, I consider only uncertainties in th_e, th_p, dEf/Ef, dEb/Eb. Angle units are in [rad] or [rad**2]
+    sig_the_thp = 8.43255e-9     #dth_e * dth_p [rad**2]
+    sig_the_Ef = -1.48849e-7      #dth_e * dEf/Ef [rad]
+    sig_the_Eb = -1.21324e-7      #dth_e * dEb/Eb [rad]
+    sig_thp_Ef = -7.01424e-8      #dth_p * dEf/Ef [rad]
+    sig_thp_Eb = -6.26743e-8      #dth_p * dEb/Eb [rad]
+    sig_Ef_Eb = 6.83851e-7       #dEf/Ef * dEb/Eb [no units]
+
[…]

### 2019-10-21 MY_PUBLICATIONS/PRL/prl.tex
updated

@@
 
-This sample document demonstrates proper use of REV\TeX~4 (and
-\LaTeXe) in mansucripts prepared for submission to APS
-journals. Further information can be found in the REV\TeX~4
-documentation included in the distribution or available at
-\url{http://publish.aps.org/revtex4/}.
+Being the most simple $np$ bound state, the deuteron serves as a starting point to study the
+strong nuclear force at the subfermi level which is currently
+not well understood. At such small internucleon distances 
+the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which 
+the interacting nucleon pair begins to overlap. The overlap is 
+directly related to two-nucleon short range correlations (SRC) observed in $A\geq2$
+nuclei. Short-distance studies of the deuteron are
+also important in determining whether or to what extent the
+description of nuclei in terms of nucleon/meson degrees of 
+freedom must be supplemented by the inclusion of explicit
+quark effects, which is an issue of fundamental importance in
+nuclear physics\cite{pr01-020}. \\
+\indent The most direct way to study the short range structure (or equivalently, the high momentum components)
+of the deuteron wavefunction is via the exclusive deuteron electro-disintegration reaction within the
+PWIA kinematics. In this approximation, the virtual photon couples to the proton which is ejected from the nucleus without
+further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction to the ejected proton, $\vec{p}_{r} = -\vec{p}_{i,p}$.
+This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged. \\
+\indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering of the proton and neutron (FSIs).
+Another possibility is that the photon may couple to the virtual meson being exchanged between the nucleons (MECs), or the photon may excite either nucleon in the deuteron
+into a resonance state (ICs) which decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. The above-mentioned long-range processes
+alter the final neutron momentum making the deuteron momentum distributions unaccessible.\\
+\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab have helped dis-entangle and quantify the contributions from FSI, MEC and IC on the $^{2}H(e,e'p)n$ cross-section.
+The first of these was performed in Hall A at relatively low momentum transfers $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for
+$p_{r}>$ 300 MeV/c, the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory agreement between the theory and data. \\
+\indent The next experiment was performed in Hall B using the CEBAF Large Acceptance Spectrometer (CLAS) which took advantage of its large detector acceptance to simultaneously measure
+a wide variety of kinematic settings giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics.
+This was the first experiment to probe the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$)
+and presented angular distributions of cross-sections and confirmed the onset of the General Eikonal Approximation (GEA), which predicts a strong angular dependence of FSI with neutron recoil angles with FSI peaking at $\theta_{nq} \sim 70^{o}$.
+The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated over all neutron recoil angles to gain better statistical precision.
+As a result, it was not possible to choose kinematical regions
+regions in which FSI were minimal to extract the momentum distributions. \\
+\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A at $Q^{2} = 0.8, 2.5, 3.5$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c at kinematics which allowed the extraction of angular and momentum distributions for significantly
+smaller kinematical bins than in Hall B/CLAS.
+The angular distributions were presented as the cross-section ratio, $R = \sigma_{exp}/\sigma_{PWIA}$ versus $\theta_{nq}$, and verified the strong anisotropy of FSI with $\theta_{nq}$.
+Most importantly, for recoil neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental cross-section to FSI,
+in which, $\sigma_{exp}\sim\sigma_{PWIA}$.
+This kinematic window in which FSI are small can also be seen in the momentum distributions for $\theta_{nq}=35\pm5^{o}$ and $\theta_{nq}=45\pm5^{o}$, where data and theory agree well
+within the PWIA kinematics.
+The experiment concluded that this kinematic window found at $35^{o}\leq \theta_{nq}\leq45^{o}$ gives for the first time a direct access to the high momentum components of the deuteron momentum distribution.
 
-When commands are referred to in this example file, they are always
-shown with their required arguments, using normal \TeX{} format. In
-this format, \verb+#1+, \verb+#2+, etc. stand for required
-author-supplied arguments to commands. For example, in
-\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
-author's section heading, and in \verb+\title{#1}+ the \verb+#1+
-stands for the title text of the paper.
-
-Line breaks in section headings at all levels can be introduced using
-\textbackslash\textbackslash. A blank input line tells \TeX\ that the
-paragraph has ended. Note that top-level section headings are
-automatically uppercased. If a specific letter or word should appear in
-lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
-in the word ``via'' above.
-
-%\subsection{\label{sec:level2}Second-level heading: Formatting}
-% subsections are not used for PRL papers
-
-This file may be formatted in both the \texttt{preprint} and
-\texttt{twocolumn} styles. \texttt{twocolumn} format may be used to
-mimic final journal output. Either format may be used for submission
-purposes; however, for peer review and production, APS will format the
-article using the \texttt{preprint} class option. Hence, it is
-essential that authors check that their manuscripts format acceptably
-under \texttt{preprint}. Manuscripts submitted to APS that do not
-format correctly under the \texttt{preprint} option may be delayed in
-both the editorial and production processes.
-
-The \texttt{widetext} environment will make the text the width of the
-full page.  The width-changing commands only take effect in \texttt{twocolumn}
-formatting. It has no effect if \texttt{preprint} formatting is chosen
-instead.
-
-To cite bibliography entries, use the \verb+\cite{#1}+ command. Most
-journal styles will display the corresponding number(s) in square
-brackets: \cite{d0det}. To avoid the square brackets, use
-\verb+\onlinecite{#1}+: Refs.~\onlinecite{d0det} and
-\onlinecite{geant,pythia}. REV\TeX\ ``collapses'' lists of
-consecutive reference numbers where possible. We now cite everyone
-together \cite{geant, pythia, cteq}, and once again
-(Refs.~\onlinecite{geant, pythia, cteq}). Note that the references
-were also sorted into the correct numerical order as well.
-
-Footnotes are produced using the \verb+\footnote{#1}+ command. Most
-APS journal styles put footnotes into the bibliography. REV\TeX~4 does
-this as well, but instead of interleaving the footnotes with the
-references, they are listed at the end of the references. Because the correct
-numbering of the footnotes must occur after the numbering of the
-references, an extra pass of \LaTeX\ is required in order to get the
-numbering correct.
-
-Inline math may be typeset using the \verb+$+ delimiters. Bold math
-symbols may be achieved using the \verb+bm+ package and the
-\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
-be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
-Blackboard (or open face or double struck) characters should be
-typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
-respectively. Both are supplied by the \texttt{amssymb} package. For
-example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
-\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$
-
-In \LaTeX\ there are many different ways to display equations, and a
-few preferred ways are noted below. Displayed math will center by
-default. Use the class option \verb+fleqn+ to flush equations left.
-
-Below we have numbered single-line equations; this is the most common
-type of equation in \textit{Physical Review}:
-\begin{eqnarray}
-\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
-\left(
-\begin{array}{c}
-|{\bf p}|+p_z\\
-px+ip_y
-\end{array}\right)\;,
-\\
-\left\{%
- \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
- \frac{1\sum^{a}_{b}}{A^2}%
-\right\}%
-\label{eq:one}.
-\end{eqnarray}
-Note the open one in Eq.~(\ref{eq:one}).
-
-Not all numbered equations will fit within a narrow column this
-way. The equation number will move down automatically if it cannot fit
-on the same line with a one-line equation:
-\begin{equation}
-\left\{
- ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
- \frac{1\sum^{a}_{b}}{A^2}%
-\right\}.
-\end{equation}
-
-When the \verb+\label{#1}+ command is used [cf. input for
-Eq.~(\ref{eq:one})], the equation can be referred to in text without
-knowing the equation number that \TeX\ will assign to it. Just
-use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
-the \verb+\label{#1}+ command.
-
-Unnumbered single-line equations can be typeset
-using the \verb+\[+, \verb+\]+ format:
-\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
-q^+g^+g^+ \dots ~. \]
-
-Figures may be inserted by using either the \texttt{graphics} or
-\texttt{graphicx} packages. These packages both define the
-\verb+\includegraphics{#1}+ command, but they differ in how optional
-arguments for specifying the orientation, scaling, and translation of the
-figure. Fig.~\ref{fig:epsart} shows a figure that is small enough to
-fit in a single column. It is embedded using the \texttt{figure}
-environment which provides both the caption and the imports the figure
-file.
-
-\begin{figure}
-\includegraphics[scale=0.8]{fig_1.ps}
-\caption{\label{fig:epsart} A figure caption. The figure captions are
-automatically numbered.}
-\end{figure}
-
-Fig.~\ref{fig:wide} is a figure that is too wide for a single column,
-so instead the \texttt{figure*} environment has been used.
-\begin{figure*}
-\includegraphics{fig_2.ps}% Here is how to import EPS art
-\caption{\label{fig:wide}Use the figure* environment to get a wide
-figure that spans the page in \texttt{twocolumn} formatting.}
-\end{figure*}
-
-The heart of any table is the \texttt{tabular} environment which gives
-the rows of the tables. Each row consists of column entries separated
-by \verb+&+'s and terminates with \textbackslash\textbackslash. The
-required argument for the \texttt{tabular} environment
-specifies how data are displayed in the columns. For instance, entries
-may be centered, left-justified, right-justified, aligned on a decimal
-point. Extra column-spacing may be be specified as well, although
-REV\TeX~4 sets this spacing so that the columns fill the width of the
-table. Horizontal rules are typeset using the \verb+\hline+
-command. The doubled (or Scotch) rules that appear at the top and
-bottom of a table can be achieved enclosing the \texttt{tabular}
-environment within a \texttt{ruledtabular} environment. Rows whose
-columns span multiple columns can be typeset using the
-\verb+\multicolumn{#1}{#2}{#3}+ command (for example, see the first
-row of Table~\ref{tab:table3}).
-
-Tables~\ref{tab:table1}-\ref{tab:table4} show various effects. Tables
-that fit in a narrow column are contained in a \texttt{table}
-environment. Table~\ref{tab:table3} is a wide table set with the
-\texttt{table*} environment. Long tables may need to break across
-pages. The most straightforward way to accomplish this is to specify
-the \verb+[H]+ float placement on the \texttt{table} or
-\texttt{table*} environment. However, the standard \LaTeXe\ package
-\texttt{longtable} will give more control over how tables break and
-will allow headers and footers to be specified for each page of the
-table. A simple example of the use of \texttt{longtable} can be found
-in the file \texttt{summary.tex} that is included with the REV\TeX~4
-distribution.
-
-There are two methods for setting footnotes within a table (these
-footnotes will be displayed directly below the table rather than at
-the bottom of the page or in the bibliography). The easiest
-and preferred method is just to use the \verb+\footnote{#1}+
-command. This will automatically enumerate the footnotes with
-lowercase roman letters. However, it is sometimes necessary to have
-multiple entries in the table share the same footnote. In this case,
-there is no choice but to manually create the footnotes using
-\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
-\texttt{\#1} is a numeric value. Each time the same value for
-\texttt{\#1} is used, the same mark is produced in the table. The
-\verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
-environment. Examine the \LaTeX\ source and output for
-Tables~\ref{tab:table1} and \ref{tab:table2} for examples.
-
-\textit{Physical Review} style requires that the initial citation of
-figures or tables be in numerical order in text, so don't cite
-Fig.~\ref{fig:wide} until Fig.~\ref{fig:epsart} has been cited.
+%Depending on the kinematics chosen, however, PWIA may be overshadowed by
+%long-range processes such as final-state interactions (FSIs), meson-exchange currents (MECs) or isobar confgurations (ICs).
 

### 2019-10-30 MY_PUBLICATIONS/PRL/body.tex
update

\indent This experiment was part of a group of four experiments that commissioned the new Hall C Super High Momentum Spectrometer (SHMS) as part of the 12 GeV upgrade at JLab.
An electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the SHMS ans High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.
The beam currents delivered by the accelerator ranged between 40-60 $\mu$A due to frequent beam trips at higher currents and the beam was rastered over a 2x2 mm$^{2}$ area to reduce
the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\
\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for particle triggering, 2) a pair of drift chambers used for
tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}herenkov used for additional $e^{-}/\pi^{-}$ and $\pi^{+}/K^{+}$ (only Heavy Gas \u{C}herenkov in SHMS) discrimination.
Given the low trigger rates and absence of significant background on this experiment, the use of additional particle identification (PID) cuts was found to have little to no effect on the final
cross section.
\indent

### 2019-10-30 MY_PUBLICATIONS/PRL/introduction.tex
update

Being the most simple $np$ bound state, the deuteron serves as a starting point to study the strong nuclear force at the subfermi level which is currently
not well understood. At such small internucleon distances the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which the interacting
nucleon pair begins to overlap. The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}. Short-distance studies
of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom must be supplemented
by the inclusion of explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. To date, there are only a few nuclear experiments for
which a transition between nucleonic to quark degrees of freedom can be observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. This Letter presents
first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleoninc degrees of freedom is expected.\\
\indent The most direct way to study the short range structure of the deuteron wavefunction (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at very high neutron recoil (or missing) momenta and within the PWIA kinematics. In this approximation, the virtual photon couples to
the proton which is ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$. This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged. \\
\indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering of the proton and neutron (FSIs). Another possibility is that the
photon may couple to the virtual meson being exchanged between the nucleons (MECs), or the photon may excite either nucleon in the deuteron into a resonance state (ICs) which
decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. The above-mentioned long-range processes alter the final neutron
momentum making the deuteron momentum distributions difficult to access.\\
\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped dis-entangle and quantify the contributions from FSI, MEC and IC on
the $^{2}H(e,e'p)n$ cross-section and determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs). The first of these was performed in Hall A  \cite{PhysRevLett.89.062301} at a relatively low momentum transfer of $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta
up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory
agreement between the theory and data. \\
\indent The next experiment was performed in Hall B \cite{PhysRevLett.98.262502} using the CEBAF Large Acceptance Spectrometer (CLAS) which took advantage of its large detector acceptance to
simultaneously measure a wide variety of kinematic settings giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics. This was the first experiment to probe
the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$) and presented angular distributions of cross-sections that confirmed the onset of
the General Eikonal Approximation (GEA), predicting a strong angular dependence of FSI with neutron recoil angles with FSI peaking at $\theta_{nq} \sim 70^{o}$.
The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated neutron recoil angles in the range $20^{o}< \theta_{nq}<160^{o}$
to gain better statistical precision. As a result, it was not possible to choose kinematical regions binned in $\theta_{nq}$ in which FSI were minimal to extract the momentum distributions. \\
\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at $Q^{2} = 0.8, 2.5, 3.5$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c at kinematics
which allowed the extraction of angular and momentum distributions for significantly smaller kinematical bins than in Hall B/CLAS. The angular distributions were presented
as the cross-section ratio, $R = \sigma_{exp}/\sigma_{PWIA}$ versus $\theta_{nq}$, and verified the strong anisotropy of FSI with recoil angle previously observed in Hall B. Most importantly, for recoil
neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental
cross-section to FSI, in which, $\sigma_{exp}\sim\sigma_{PWIA}$.  This kinematic window in which FSI are small can also be seen in the momentum distributions for
$\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, where data and theory agree well within the PWIA kinematics. The experiment concluded that the kinematic window found
at $35^{o}\leq \theta_{nq}\leq45^{o}$ gives for the first time a direct access to the high momentum components of the deuteron momentum distribution. \\
\indent This experiment takes advantage of the kinematic window found previosuly in Hall A and extends the $^{2}H(e,e'p)n$ cross section measruements to $Q^{2}=4.5$ (GeV/c)$^{2}$
and neutron recoil momenta up to 1.18 GeV/c. In this configuration, MECs and ICs are suppressed and FSIs are under control for recoil angles between 35 and 45 degrees
giving access to unprecedented high momentum components of the deuteron wavefunction. \\

### 2019-10-30 MY_PUBLICATIONS/PRL/prl.tex
update

@@
 %  Add 'showpacs' option to make PACS codes appear
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
 %\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
@@
 \usepackage[hidelinks]{hyperref}
+\usepackage{fancyhdr}
 \usepackage{xcolor}
@@
 \maketitle
+%\thispagestyle{plain}
 
@@
 
-Being the most simple $np$ bound state, the deuteron serves as a starting point to study the
-strong nuclear force at the subfermi level which is currently
-not well understood. At such small internucleon distances 
-the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which 
-the interacting nucleon pair begins to overlap. The overlap is 
-directly related to two-nucleon short range correlations (SRC) observed in $A\geq2$
-nuclei. Short-distance studies of the deuteron are
-also important in determining whether or to what extent the
-description of nuclei in terms of nucleon/meson degrees of 
-freedom must be supplemented by the inclusion of explicit
-quark effects, which is an issue of fundamental importance in
-nuclear physics\cite{pr01-020}. \\
-\indent The most direct way to study the short range structure (or equivalently, the high momentum components)
-of the deuteron wavefunction is via the exclusive deuteron electro-disintegration reaction within the
-PWIA kinematics. In this approximation, the virtual photon couples to the proton which is ejected from the nucleus without
-further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction to the ejected proton, $\vec{p}_{r} = -\vec{p}_{i,p}$.
-This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged. \\
-\indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering of the proton and neutron (FSIs).
-Another possibility is that the photon may couple to the virtual meson being exchanged between the nucleons (MECs), or the photon may excite either nucleon in the deuteron
-into a resonance state (ICs) which decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. The above-mentioned long-range processes
-alter the final neutron momentum making the deuteron momentum distributions unaccessible.\\
-\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab have helped dis-entangle and quantify the contributions from FSI, MEC and IC on the $^{2}H(e,e'p)n$ cross-section.
-The first of these was performed in Hall A at relatively low momentum transfers $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for
-$p_{r}>$ 300 MeV/c, the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory agreement between the theory and data. \\
-\indent The next experiment was performed in Hall B using the CEBAF Large Acceptance Spectrometer (CLAS) which took advantage of its large detector acceptance to simultaneously measure
-a wide variety of kinematic settings giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics.
-This was the first experiment to probe the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$)
-and presented angular distributions of cross-sections and confirmed the onset of the General Eikonal Approximation (GEA), which predicts a strong angular dependence of FSI with neutron recoil angles with FSI peaking at $\theta_{nq} \sim 70^{o}$.
-The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated over all neutron recoil angles to gain better statistical precision.
-As a result, it was not possible to choose kinematical regions
-regions in which FSI were minimal to extract the momentum distributions. \\
-\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A at $Q^{2} = 0.8, 2.5, 3.5$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c at kinematics which allowed the extraction of angular and momentum distributions for significantly
-smaller kinematical bins than in Hall B/CLAS.
-The angular distributions were presented as the cross-section ratio, $R = \sigma_{exp}/\sigma_{PWIA}$ versus $\theta_{nq}$, and verified the strong anisotropy of FSI with $\theta_{nq}$.
-Most importantly, for recoil neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental cross-section to FSI,
-in which, $\sigma_{exp}\sim\sigma_{PWIA}$.
-This kinematic window in which FSI are small can also be seen in the momentum distributions for $\theta_{nq}=35\pm5^{o}$ and $\theta_{nq}=45\pm5^{o}$, where data and theory agree well
-within the PWIA kinematics.
-The experiment concluded that this kinematic window found at $35^{o}\leq \theta_{nq}\leq45^{o}$ gives for the first time a direct access to the high momentum components of the deuteron momentum distribution.
-
-%Depending on the kinematics chosen, however, PWIA may be overshadowed by
-%long-range processes such as final-state interactions (FSIs), meson-exchange currents (MECs) or isobar confgurations (ICs).
-
+\input introduction.tex
+\input body.tex
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
 \input acknowledgement.tex   % input acknowledgement
-
 \bibliography{prl}

### 2019-10-31 MY_PUBLICATIONS/PRL/body.tex
updated

@@
 the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\
-\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for particle triggering, 2) a pair of drift chambers used for
-tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}herenkov used for additional $e^{-}/\pi^{-}$ and $\pi^{+}/K^{+}$ (only Heavy Gas \u{C}herenkov in SHMS) discrimination.
-Given the low trigger rates and absence of significant background on this experiment, the use of additional particle identification (PID) cuts was found to have little to no effect on the final
-cross section.
-\indent
+\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for triggering,
+2) a pair of drift chambers used for tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov used also for $e^{-}/\pi^{-}$ and an additional
+Noble Gas \u{C}erenkov used in the SHMS for $e^{-}/\pi^{+}/K^{+}$ at momenta $>$ 6 GeV/c. Due to the absence of significant background on this experiment and the low coincidence trigger rates
+($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section. \\
+\indent The kinematics measured in our experiment consisted of three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
+The spectrometer settings were as follows: the SHMS central angle and momentum settings were kept fixed at (12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
+(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to (54.992 deg, 2.1925 GeV/c) and (58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. At these kinematics, the
+3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred to the proton.
+As a result, the ejected proton
+scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$.
+This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the neutron is struck and the proton is a spectator.
+\\
+\indent In addition to deuteron kinematics,  $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron 80 MeV setting for cross-checks with the spectrometer acceptance model as well as for normalization purposes using the  Hall C Monte Carlo
+simulation program, \texttt{SIMC}.
+Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings to cover the entire SHMS momentum acceptance range for spectrometer optics studies and
+calibration. \\
+\indent The event selection criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
+is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the edges, 3) a missing
+energy cut (peak $\sim$ 2.2 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
+SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a z-vertex difference cut between the HMS and SHMS $z$ reaction vertex difference to select events that truly
+originated from the same reaction vertex at the target.
+\indent The data yield was corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.

### 2019-10-31 MY_PUBLICATIONS/PRL/introduction.tex
updated

@@
 at $35^{o}\leq \theta_{nq}\leq45^{o}$ gives for the first time a direct access to the high momentum components of the deuteron momentum distribution. \\
-\indent This experiment takes advantage of the kinematic window found previosuly in Hall A and extends the $^{2}H(e,e'p)n$ cross section measruements to $Q^{2}=4.5$ (GeV/c)$^{2}$
-and neutron recoil momenta up to 1.18 GeV/c. In this configuration, MECs and ICs are suppressed and FSIs are under control for recoil angles between 35 and 45 degrees
+\indent The experiment presented on this Letter takes advantage of the kinematic window found previosuly in Hall A and extends the $^{2}H(e,e'p)n$ cross section measruements to $Q^{2}=4.5$ (GeV/c)$^{2}$
+and neutron recoil momenta up to 1.18 GeV/c. In this configuration, MECs and ICs are suppressed and FSIs are under control for neutron recoil angles between 35 and 45 degrees
 giving access to unprecedented high momentum components of the deuteron wavefunction. \\

### 2019-11-07 MY_PUBLICATIONS/PRL/body.tex
updated prl paper

--- 2019-10-30 MY_PUBLICATIONS/PRL/body.tex
@@
 the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\
-\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for particle triggering, 2) a pair of drift chambers used for
-tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}herenkov used for additional $e^{-}/\pi^{-}$ and $\pi^{+}/K^{+}$ (only Heavy Gas \u{C}herenkov in SHMS) discrimination.
-Given the low trigger rates and absence of significant background on this experiment, the use of additional particle identification (PID) cuts was found to have little to no effect on the final
-cross section.
-\indent
+\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for triggering,
+2) a pair of drift chambers used for tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov used also for $e^{-}/\pi^{-}$ and an additional
+Noble Gas \u{C}erenkov used in the SHMS for $e^{-}/\pi^{+}/K^{+}$ at momenta $>$ 6 GeV/c. Due to the absence of significant background on this experiment and the low coincidence trigger rates
+($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section. \\
+\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. In the high missing momentum settings the spectrometer configuration was changed
+multiple times resulting in either the spectrometer angle or momentum not being excactly the same.
+As a result, two separate data sets measured for the 580 MeV/c and three data sets for the 750 MeV/c setting.
+The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept fixed at (12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
+(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to (54.992 deg, 2.1925 GeV/c) and (58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. At these kinematics, the
+3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred to the proton.
+As a result, the ejected proton
+scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$.
+This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the neutron is struck and the proton is a spectator.
+\\
+\indent In addition to deuteron kinematics,  $^{1}H(e,e'p)$ elastic data was also taken at kinematics close to the deuteron 80 MeV setting for cross-checks with the spectrometer acceptance model as well as for normalization purposes using the  Hall C Monte Carlo
+simulation program, \texttt{SIMC}.
+Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics studies and
+calibration. \\
+\indent The event selection criteria for the hydrogen and deuteron data was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
+is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the edges, 3) a missing
+energy cut (peak $\sim$ 2.2 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
+SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a z-vertex difference cut between the HMS and SHMS $z$ reaction vertex difference to select events that truly
+originated from the same reaction vertex at the target. \\
+\indent The experimental data yield was normalized by the accumulated charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
+For $^{1}H(e,e'p)$, the corrected data yield was compared against SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
+model. The data to SIMC yield ratio was determined to be 1.0 within uncertainty, and there was no need to include an overall hydrogen normalization factor. For the $^{2}H(e,e'p)$ data,
+the theoretical cross section calculation from J.M. Laget using the Paris potential was incorporated into SIMC as a subroutine. The events generated
+over phase space were weighted by the theoretical cross sections using either the PWIA or FSI models and were compared to the corrected data yield for the 80 MeV setting. Variations
+of up to $\sim 20 \%$ for recoil momentum up to $\sim$ 250 MeV/c were observed which are typical for this setting. The 80 MeV data was also checked for reproducibility against the Hall A data
+at this setting. This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
+\indent The experimental sections were determined by dividing the normalized data yield by the phase space over the spectrometers acceptances generated in SIMC. The data was radiatively corrected
+by multiplying measured cross sections by the ratio of the SIMC yield (using the Paris potential, FSI model) without and with radiative effects for each bin in ($\theta_{nq}, p_{r}$).
+The data was also bin-centered corrected by multiplying the radiative corrected cross sections by the ratio of theoretical cross section at the averaged kinematics to the average SIMC model
+cross sections at the bin-centered value in ($\theta_{nq}, p_{r}$). The theoretical cross sections were determined external to SIMC using J.M. Laget's calculations at the averaged kinematics.\\
+\begin{figure}
+\includegraphics[scale=0.5]{prl_plots/PRL_plot2.pdf}
+\caption{\label{fig:fig1} The ratio R($p_{r}$) = $\sigma_{exp}/\sigma_{PWIA}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+                          The dashed reference (magenta) line refers to CD-Bonn PWIA for which the data and all models are divided. }
+\end{figure}
+\indent The systematic uncertainties on the measured cross sections are separated in two categories: 1) normalization and 2) kinematic uncertainties. The normalization uncertainties on
+the  $^{2}H(e,e'p)n$ cross section were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
+for an overall normalization uncertainty of $3.7 \%$ added in quadrature. \\
+\indent The kinematic uncertainties were determined point-to-point for ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
+of different data sets.
+The variations of the cross section with spectrometer kinematics in beam energy, electron angle and momentum and proton angle were determined from Laget PWIA model and the uncertainties
+in the kinematic variables were determined from a fit to the $^{1}H(e,e'p)$ elastic data.
+%For $\theta_{nq}=$ 35, 45 and 75 deg the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
+The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature
+to the statiscial uncertainty to obtain the final uncertainty in the cross section. \\
+\indent The $^{2}H(e,e'p)n$ reduced cross sections for each data set were determined within the PWIA by:
+\begin{equation}
+\sigma_{red} \equiv \frac{\sigma_{exp}}{Kf_{rec}\sigma_{cc1}}
+\label{eq:1}
+\end{equation}
+where $\sigma_{exp}$ is the 5-fold experimental (or model) cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
+integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section.
+In the PWIA, $\sigma_{red}$ is interpreted as the momentum distributions inside the deuteron where most of the kinematical dependencies that arise from the
+cross section have been factored out. \\
+\indent In Figure \ref{fig:fig1}, the ratio of the experimental to the PWIA reduced cross sections is plotted against neutron recoil momentum, $p_{r}$.

### 2019-11-07 MY_PUBLICATIONS/PRL/prl.tex
updated
updated prl paper

@@
     colorlinks,
-    linkcolor={red!50!black},
+    linkcolor={blue!80!black},
     citecolor={blue!80!black},
@@
 \input body.tex
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
+%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
 \input acknowledgement.tex   % input acknowledgement

### 2019-11-07 publications/supplemental_materials/get_Xsec_err.py

@@ -1,0 +1,94 @@
+import numpy as np
+from interpolate_ff import *
+
+#This code defined the H(e,e'p) elastic cross section in terms of
+#the electric and magnetic form factors. Then apply error propagation
+#in terms of the form factors to get uncertainty in cross section at thw
+#gven beam energy, elecrtron angle and momentum.
+#Finally, use the error in the Xsec as the error as the simc yield error
+#Define Physical Constnats
+
+
+hbarc = 197.327053 / 1000.       #GeV * fm
+alpha = 1./137.0359895    #structure constant
+dtr = np.pi / 180.
+
+#(1 GeV)^2 = (1000 MeV)^2 = 1e6 MeV^2
+
+#Masses in GeV
+MP = 938.272 / 1000.
+MN = 939.566 / 1000.
+MD = 1875.61 / 1000.
+me = 0.51099 / 1000.
+
+#Elastic Cross Section and its error
+def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
+
+    #Units: kf ~ Ef [GeV]   electron momentum  
+    #th_e[deg] electron angle  
+    #Q2[GeV2]   4-momentum transfer
+
+    mu_N = 3.1524512326 *1e-14 / 1000.   #nuclear magneton [GeV T^-1]
+    mu_p = 2.7928473508 * mu_N   #proton magnetic moment [GeV T^-1]
+
+    #Mott cross section
+    th_e = th_e * dtr    #convert degree to radians
+    sigM = (2.*alpha*hbarc*kf*np.cos(th_e/2.)/Q2 )**2   #GeV^2 * fm^2 *GeV^2/GeV^4--> fm2 / sr
+    sigMott = sigM * 1e4    #convert fm^2 -> microbarn
+
+    tau =  Q2 /(4.*MP)**2
+    L2 = 0.71   #Lambda parameter [GeV^2]
+    GD = 1. / (1 + Q2/L2)**2     #dipole form factor
+    muGD = mu_p * GD   #[GeV T^-1]
+    
+    #Get form factors
+    GEp = GEp_GD * GD
+    GMp = GMp_muGD * muGD
+
+    #Elastic H(e,e'p) Cross Section
[…]

### 2019-11-11 MY_PUBLICATIONS/PRL/body.tex
updated PRL

@@
 calibration. \\
-\indent The event selection criteria for the hydrogen and deuteron data was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
+\indent The event selection criteria was done exactly the same for the hydrogen and deuteron data.
+The criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
 is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the edges, 3) a missing
@@
 originated from the same reaction vertex at the target. \\
-\indent The experimental data yield was normalized by the accumulated charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
-For $^{1}H(e,e'p)$, the corrected data yield was compared against SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
-model. The data to SIMC yield ratio was determined to be 1.0 within uncertainty, and there was no need to include an overall hydrogen normalization factor. For the $^{2}H(e,e'p)$ data,
-the theoretical cross section calculation from J.M. Laget using the Paris potential was incorporated into SIMC as a subroutine. The events generated
-over phase space were weighted by the theoretical cross sections using either the PWIA or FSI models and were compared to the corrected data yield for the 80 MeV setting. Variations
-of up to $\sim 20 \%$ for recoil momentum up to $\sim$ 250 MeV/c were observed which are typical for this setting. The 80 MeV data was also checked for reproducibility against the Hall A data
-at this setting. This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
-\indent The experimental sections were determined by dividing the normalized data yield by the phase space over the spectrometers acceptances generated in SIMC. The data was radiatively corrected
-by multiplying measured cross sections by the ratio of the SIMC yield (using the Paris potential, FSI model) without and with radiative effects for each bin in ($\theta_{nq}, p_{r}$).
-The data was also bin-centered corrected by multiplying the radiative corrected cross sections by the ratio of theoretical cross section at the averaged kinematics to the average SIMC model
-cross sections at the bin-centered value in ($\theta_{nq}, p_{r}$). The theoretical cross sections were determined external to SIMC using J.M. Laget's calculations at the averaged kinematics.\\
+\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
+For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
+model.
+The data to SIMC yield ratio integrated over invariant mass $W$ was determined to be unity, so there was no need to include an overall hydrogen normalization factor.
+For the $^{2}H(e,e'p)n$ data,
+the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential. Variations
+of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential.
+The 80 MeV data was also checked for reproducibility against the Hall A data.
+This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
+\indent The systematic uncertainties on the measured cross sections were determined from 1) normalization and 2) kinematic uncertainties. The individual contributions from normalization uncertainties
+were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
+for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
+\indent The kinematic uncertainties were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
+of different data sets. For $\theta_{nq}=$ 35, 45 and 75 deg (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
+The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature
+to the statiscial uncertainty to obtain the final uncertainty in the cross section. \\
+\indent The data was radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
+Bin-centering
+corrections were also applied by multiplying the radiative corrected cross sections to the ratio of theoretical cross sections (external to SIMC) to the average cross sections calculated from SIMC.
+The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential. \\
+\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data of set independently and were averaged for overlapping bins in $p_{r}$,
+where the reduced cross sections are defined as follows:
+\begin{equation}
+\sigma_{red} \equiv \frac{\sigma_{exp(th)}}{Kf_{rec}\sigma_{cc1}}
+\label{eq:1}
+\end{equation}
+where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
+integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated from P.
+Bosted's form factor parametrization \cite{PhysRevC.51.409}.
+Only within the PWIA, $\sigma_{red}$ can be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
+cross section have been factored out by $\sigma_{cc1}$, leaving only a dependency on $p_{r}$. \\
 \begin{figure}
 \includegraphics[scale=0.5]{prl_plots/PRL_plot2.pdf}
-\caption{\label{fig:fig1} The ratio R($p_{r}$) = $\sigma_{exp}/\sigma_{PWIA}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
-                          The dashed reference (magenta) line refers to CD-Bonn PWIA for which the data and all models are divided. }
+\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
+\label{fig:fig1}
 \end{figure}
-\indent The systematic uncertainties on the measured cross sections are separated in two categories: 1) normalization and 2) kinematic uncertainties. The normalization uncertainties on
-the  $^{2}H(e,e'p)n$ cross section were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
-for an overall normalization uncertainty of $3.7 \%$ added in quadrature. \\
-\indent The kinematic uncertainties were determined point-to-point for ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
-of different data sets.
-The variations of the cross section with spectrometer kinematics in beam energy, electron angle and momentum and proton angle were determined from Laget PWIA model and the uncertainties
-in the kinematic variables were determined from a fit to the $^{1}H(e,e'p)$ elastic data.
-%For $\theta_{nq}=$ 35, 45 and 75 deg the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
-The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature
-to the statiscial uncertainty to obtain the final uncertainty in the cross section. \\
-\indent The $^{2}H(e,e'p)n$ reduced cross sections for each data set were determined within the PWIA by:
-\begin{equation}
-\sigma_{red} \equiv \frac{\sigma_{exp}}{Kf_{rec}\sigma_{cc1}}
-\label{eq:1}
-\end{equation}
-where $\sigma_{exp}$ is the 5-fold experimental (or model) cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
-integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section.
-In the PWIA, $\sigma_{red}$ is interpreted as the momentum distributions inside the deuteron where most of the kinematical dependencies that arise from the
-cross section have been factored out. \\
-\indent In Figure \ref{fig:fig1}, the ratio of the experimental to the PWIA reduced cross sections is plotted against neutron recoil momentum, $p_{r}$.
+\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
+to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
+CD-Bonn and Argonne $v_{18}$ (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
+in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
+the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
+up to $\sim$ 800 MeV/c before being overwhelmed by FSIs. The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
+with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}], both the data and
+CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn curves, whereas the data shows
+a similar behaviour as in Fig.
+\hyperref[fig:fig1]{1(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model.
+For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}], the
+onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
+at larger recoil angles. \\
+\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum, $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
+(GeV/c)$^{2}$.
+The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.
+The overlay of the Hall A data (cyan) in Fig.
+\ref{fig:fig2}
+provides a continutity to the data from this experiment in the transition region from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there was no data.
+There is also an overall good agreement between the two experiments
+in the regions in which there is an overlap in $p_{r}$. \\
+\indent Below $p_{r}\sim 300$ MeV/c, both Hall A and C data agree well with all theoretical models, as FSIs and other non-cucleonic 
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\onecolumngrid
+
+\begin{figure}[bh!]
+\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
+\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
+with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
+\label{fig:fig2}
+\end{figure}
+\newpage
+\twocolumngrid
+%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

### 2019-11-12 MY_PUBLICATIONS/PRL/body.tex
updated

@@
 There is also an overall good agreement between the two experiments
-in the regions in which there is an overlap in $p_{r}$. \\
-\indent Below $p_{r}\sim 300$ MeV/c, both Hall A and C data agree well with all theoretical models, as FSIs and other non-cucleonic 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+in the regions in which they overlap in $p_{r}$. \\
+\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
+\hyperref[fig:fig2]{2(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
+characteristic ``flattening'' (smaller falloff) with $p_{r}$. This behaviour of FSI with larger recoil angles was predicted by the GEA and was first verified by the Hall A experiment.
+This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
+As a result, our data at larger recoil angles
+is statistically limited. \\
+\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs.
+\hyperref[fig:fig2]{2(a)}] and  \hyperref[fig:fig2]{2(b)}],  all models predict similar behaviour of the momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies.
+At larger $p_{r}$,
+however, the momentum distributions become increasingly sensitive to the NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
+\indent In Fig.
+\hyperref[fig:fig2]{2(a)} for example, the data clearly favors the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models.
+For recoil angles in Fig.
+\hyperref[fig:fig2]{2(b)}, a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$
+as opposed to Fig.
+\hyperref[fig:fig2]{2(a)}.
+For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.
 \onecolumngrid
@@
 \end{figure}
-\newpage
+
 \twocolumngrid
-%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\indent We have measured the

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
update

--- 2019-11-11 MY_PUBLICATIONS/PRL/body.tex
@@
 \indent This experiment was part of a group of four experiments that commissioned the new Hall C Super High Momentum Spectrometer (SHMS) as part of the 12 GeV upgrade at JLab.
-An electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
-by the SHMS ans High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.
+A 10.6005 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
+by the SHMS and High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.
 The beam currents delivered by the accelerator ranged between 40-60 $\mu$A due to frequent beam trips at higher currents and the beam was rastered over a 2x2 mm$^{2}$ area to reduce
 the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\
-\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes (scintillator arrays) used for triggering,
-2) a pair of drift chambers used for tracking, 3) a calorimeter used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov used also for $e^{-}/\pi^{-}$ and an additional
-Noble Gas \u{C}erenkov used in the SHMS for $e^{-}/\pi^{+}/K^{+}$ at momenta $>$ 6 GeV/c. Due to the absence of significant background on this experiment and the low coincidence trigger rates
+\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes\cite{hodo_techreport} (scintillator arrays) used for triggering,
+2) a pair of drift chambers\cite{dc_techreport} used for tracking, 3) a calorimeter\cite{Mkrtchyan_2013} used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used also for $e^{-}/\pi^{-}$ separation.
+Due to the absence of significant background on this experiment and the low coincidence trigger rates
 ($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section. \\
@@
 multiple times resulting in either the spectrometer angle or momentum not being excactly the same.
-As a result, two separate data sets measured for the 580 MeV/c and three data sets for the 750 MeV/c setting.
-The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept fixed at (12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
-(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to (54.992 deg, 2.1925 GeV/c) and (58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. At these kinematics, the
-3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred to the proton.
-As a result, the ejected proton
-scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$.
-This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the neutron is struck and the proton is a spectator.
-\\
+As a result, two separate data sets were measured for the 580 MeV/c setting and three data sets for the 750 MeV/c setting.
+The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept ``fixed'' at ($\sim$12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
+(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to $\sim$(54.992 deg, 2.1925 GeV/c) and $\sim$(58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. \\
+\indent At these kinematics, the 3-momentum transfer is $|\vec{q}| \sim 2.88$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$) measured on this experiment. As a result
+one can infer that most of the virtual photon momentum is transferred to the proton. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
+neutron is struck while the detected proton is a spectator. FSIs are also expected to be largely reduced as compared to the ``perpendicular-kinematics'' in which the
+proton is detected almost perpendicular to $\vec{q}$ based on a calculation by Arenh\"{o}vel on Table 1 of Ref.\cite{pr01-020}.\\
+% (5) At these kinematics, the 3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred
+%to the proton. As a result, the ejected proton scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$. This configuration is known as the ``parallel-kinematics'' and suppresses
+%the process in which the neutron is struck and the proton is a spectator. \\
 \indent In addition to deuteron kinematics,  $^{1}H(e,e'p)$ elastic data was also taken at kinematics close to the deuteron 80 MeV setting for cross-checks with the spectrometer acceptance model as well as for normalization purposes using the  Hall C Monte Carlo
-simulation program, \texttt{SIMC}.
-Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics studies and
-calibration. \\
+simulation program, SIMC.
+Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics optimization,
+momentum calibration and determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\
 \indent The event selection criteria was done exactly the same for the hydrogen and deuteron data.
 The criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
-is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the edges, 3) a missing
-energy cut (peak $\sim$ 2.2 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
+is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the collimator edges, 3) a missing
+energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
 SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a z-vertex difference cut between the HMS and SHMS $z$ reaction vertex difference to select events that truly
 originated from the same reaction vertex at the target. \\
-\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
+\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption\cite{cyero_pAbs} and target boiling factors\cite{cyero_tgtBoil}.
 For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
@@
 of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential.
-The 80 MeV data was also checked for reproducibility against the Hall A data.
+The 80 MeV data was also checked for reproducibility against the Hall A data (See Fig.
+\ref{fig:fig2}).
 This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
-\indent The systematic uncertainties on the measured cross sections were determined from 1) normalization and 2) kinematic uncertainties. The individual contributions from normalization uncertainties
+\indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
+Determination of systematics on these quantities is a work in progress.
+(Private communication with D.
+Mack)} and kinematic uncertainties.
+The individual contributions from normalization uncertainties
 were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
@@
 corrections were also applied by multiplying the radiative corrected cross sections to the ratio of theoretical cross sections (external to SIMC) to the average cross sections calculated from SIMC.
-The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential. \\
-\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data of set independently and were averaged for overlapping bins in $p_{r}$,
+The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. \\
+\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were averaged for overlapping bins in $p_{r}$,
 where the reduced cross sections are defined as follows:
@@
 \end{equation}
-where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
-integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated from P.
+where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
+integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using P.
 Bosted's form factor parametrization \cite{PhysRevC.51.409}.
-Only within the PWIA, $\sigma_{red}$ can be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
+Only within the PWIA, can $\sigma_{red}$ be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
 cross section have been factored out by $\sigma_{cc1}$, leaving only a dependency on $p_{r}$. \\
 \begin{figure}
-\includegraphics[scale=0.5]{prl_plots/PRL_plot2.pdf}
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
 \caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
@@
 \indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
-to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
-CD-Bonn and Argonne $v_{18}$ (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
+relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001} is shown in Fig.
+\ref{fig:fig1}.
+The theoretical calculations for the
+CD-Bonn and Argonne $v_{18}$\cite{PhysRevC.51.38} (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
 in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
@@
 with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}], both the data and
-CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn curves, whereas the data shows
+CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
 a similar behaviour as in Fig.
@@
 \ref{fig:fig2}
-provides a continutity to the data from this experiment in the transition region from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there was no data.
-There is also an overall good agreement between the two experiments
-in the regions in which there is an overlap in $p_{r}$. \\
-\indent Below $p_{r}\sim 300$ MeV/c, both Hall A and C data agree well with all theoretical models, as FSIs and other non-cucleonic 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
+was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
+\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
+\hyperref[fig:fig2]{2(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
+smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
+This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{PhysRevC.56.1124,Sargsian_2001} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
+This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
+As a result, our data at larger recoil angles
+is statistically limited. \\
+\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)} and  \hyperref[fig:fig2]{2(b)},  all models predict similar behaviour of the
+momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
+NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
+\indent In Fig.
+\hyperref[fig:fig2]{2(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
+to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig2]{2(b)},
+a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start 
 \onecolumngrid
-
-\begin{figure}[bh!]
-\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
+\begin{center}
+\begin{figure}[hb!]
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
+\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
 with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
@@
 \end{figure}
-\newpage
+\end{center} \\
+%Begin text ON NEW PAGE after FIGURE 2. If Figure 2 changed position, move text from previous page (top) to this page (bottom)
 \twocolumngrid
-%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\noindent to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.
+For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
+\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
+%while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
+%experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
+%of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c.
+The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
+up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
+behavior that was not predicted by any of the models. \\
+\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days) of beam time and 3 out of the 8 kinematic settings approved in
+the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
+necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
+It would be highly desireable to perform the full experiment
+
+%We conclude that these results although very interesting, does not have the sufficient statistics and the
+%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\
+
+%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/introduction.tex
update

Being the only bound two-nucleon system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi level which is currently
not well understood. At such small internucleon distances the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which the interacting
nucleon pair begins to overlap. The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
Short-range studies of the deuteron are also important in determining whether or to what extent is the description of nuclei in terms of nucleon/meson degrees of freedom valid before
having to include explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
This Letter presents first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleonic degrees of freedom is expected.\\
\indent The most direct way to study the short range structure of the deuteron wavefunction (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at very high neutron recoil (or missing) momenta and within the PWIA kinematics. In this approximation, the virtual photon couples to
the proton which is ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$. This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged from its initial state. \\
\indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering between the proton and neutron (FSIs). Another possibility is that the
photon may couple to the virtual meson being exchanged between the nucleons (MECs), or the photon may excite either nucleon in the deuteron into a resonance state (ICs) which
decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. Both MECs and ICs in addition to FSIs can significantly alter the recoiling neutron
momentum thereby obscuring any possibility of directly accessing the deuteron momentum distributions. \\
%(1) The above-mentioned long-range processes alter the final neutron
%momentum making the deuteron momentum distributions difficult to access.\\
\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped constrain and quantify the contributions from FSIs, MECs and ICs on
the $^{2}H(e,e'p)n$ cross-section and determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs). The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
at a relatively low momentum transfer of $Q^{2}=0.665$ GeV$^{2}$ and neutron recoil momenta
up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and their inclusion was necessary in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}
for a satisfactory agreement between theory and data. \\
%(2) the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory
%agreement between the theory and data. \\
\indent The next experiment was performed in Hall B \cite{PhysRevLett.98.262502} using the CEBAF Large Acceptance Spectrometer (CLAS) which measured a wide variety of kinematic settings
giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics. This was the first experiment to probe
the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 GeV$^{2}$) and presented angular distributions of cross-sections that confirmed the onset of
the General Eikonal Approximation (GEA)\cite{sargsian_2001,PhysRevC.56.1124}, which predicts a strong angular dependence of FSI with neutron recoil angles with a peak at $\theta_{nq} \sim 70^{o}$.
The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, due to statistical limitations it was impossible to select kinematical bins in $\theta_{nq}$ where
FSIs were small to extract momentum distributions.\\
% (3) The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated neutron recoil angles in the range $20^{o}< \theta_{nq}<160^{o}$
%to gain better statistical precision. As a result, it was not possible to choose kinematical regions binned in $\theta_{nq}$ in which FSI were minimal to extract the momentum distributions. \\
\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at published $Q^{2} = 3.5\pm0.25$ GeV$^{2}$ and recoil momenta up to 550 MeV/c. The angular distributions of
the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) versus $\theta_{nq}$ presented verified the strong anisotropy of FSIs with recoil angle also observed in Hall B\cite{PhysRevLett.98.262502}. Most importantly, for recoil
neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio was found to be $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental
cross-section to FSIs. This kinematic window allowed for the first time the extraction of momentum distributions for neutron recoil momenta up to $p_{r}\sim$550 MeV/c. \\
% (4) This kinematic window in which FSI are small can also be seen in the momentum distributions for
%$\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, where data and theory agree well within the PWIA kinematics.
\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measruements
to $Q^{2}=4.5\pm0.5$ GeV$^{2}$ and neutron recoil momenta up to 1.18 GeV/c. At these kinematics, MECs and ICs are suppressed and FSIs are under control for neutron recoil angles between 35 and 45 degrees
giving access to unprecedented high momentum components of the deuteron wavefunction. \\

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/prl.tex
update

--- 2019-11-07 MY_PUBLICATIONS/PRL/prl.tex
@@
 \usepackage{xcolor}
+\usepackage{float}
+\usepackage{lipsum}
 \hypersetup{
@@
 \widetext
-\leftline{Version xx as of \today}
+\leftline{Version 00 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
 \begin{abstract}
-  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
-  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
-  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
-  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
-  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.
+  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ and
+  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
+  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the in-plane neutron recoil
+  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA)
+  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 700 MeV/c.
 
@@
 \input body.tex
-%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
 \input acknowledgement.tex    % input acknowledgement
 \bibliography{prl}
-
+.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \end{document}

### 2019-11-14 MY_PUBLICATIONS/PRL/pre_draft/body.tex
update

--- 2019-11-12 MY_PUBLICATIONS/PRL/body.tex
@@
 \begin{figure}
-\includegraphics[scale=0.5]{prl_plots/PRL_plot2.pdf}
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
 \caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
@@
 \begin{figure}[bh!]
-\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
@@
 \twocolumngrid
-\indent We have measured the
+\indent In summary, this commissioning experiment extends the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions
+while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
+experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
+of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c. The experimental reduced cross sections were extracted and found to
+be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$,
+respectively before the data transitioning to other theoretical models, which is a behavior that was not predicted by any of the models. We conclude that these results although
+very interesting, does not have the sufficient statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
+
+%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs

### 2019-11-14 MY_PUBLICATIONS/PRL/pre_draft/introduction.tex
update

--- 2019-10-31 MY_PUBLICATIONS/PRL/introduction.tex
@@
 The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
-Short-distance studies
-of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom must be supplemented
-by the inclusion of explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. To date, there are only a few nuclear experiments for
-which a transition between nucleonic to quark degrees of freedom can be observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. This Letter presents
-first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleoninc degrees of freedom is expected.\\
+Short-range studies of the deuteron are also important in determining whether or to what extent can nuclei be described in terms of nucleon/meson degrees of freedom before
+having to include explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
+which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
+This Letter presents first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleoninc degrees of freedom is expected.\\
 \indent The most direct way to study the short range structure of the deuteron wavefunction (or equivalently, its high momentum components) is via the exclusive deuteron

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
updated prl

@@
 \indent At these kinematics, the 3-momentum transfer is $|\vec{q}| \sim 2.88$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$) measured on this experiment. As a result
-one can infer that most of the virtual photon momentum is transferred to the proton. This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
+one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$, $\theta_{pq}\sim 0$.
+This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
 neutron is struck while the detected proton is a spectator. FSIs are also expected to be largely reduced as compared to the ``perpendicular-kinematics'' in which the
@@
 For the $^{2}H(e,e'p)n$ data,
-the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential. Variations
+the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. Variations
 of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential.
@@
 \ref{fig:fig2}).
-This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
+This agreement gives us confidence on the measurements made at higher missing momentum setting for which no previous data exists. \\
 \indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
@@
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature
-to the statiscial uncertainty to obtain the final uncertainty in the cross section. \\
+to the statiscial uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
 \indent The data was radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
@@
 \indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
-relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001} is shown in Fig.
+relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig.
 \ref{fig:fig1}.
 The theoretical calculations for the
-CD-Bonn and Argonne $v_{18}$\cite{PhysRevC.51.38} (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
+CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M.
+Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M.
+Laget.
+For $p_{r}\lesssim 300$ MeV/c, the data is
 in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
@@
 at larger recoil angles. \\
-\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum, $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
-(GeV/c)$^{2}$.
-The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.
+\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
+GeV$^{2}$.
+The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 GeV$^{2}$.
 The overlay of the Hall A data (cyan) in Fig.
@@
 smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
-This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{PhysRevC.56.1124,Sargsian_2001} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
+This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
 This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
@@
 to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig2]{2(b)},
-a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start 
+a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum dis-
 \onecolumngrid
@@
 \includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
-with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
+\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
+with a bin width of $\pm 5^{o}$.
+The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the Paris(blue), AV18(green) and CD-Bonn(magenta) theoretical reduced cross sections.}
 \label{fig:fig2}
@@
 \twocolumngrid
-\noindent to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.
+\noindent tributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.
 For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
@@
 behavior that was not predicted by any of the models. \\
-\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days) of beam time and 3 out of the 8 kinematic settings approved in
+\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
 the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
 necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
-It would be highly desireable to perform the full experiment
 

### 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/prl.tex
updated prl

@@
   angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA)
-  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 700 MeV/c.
+  dominates and comparison to recent theoretical calculations show data to be sensitive to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
 

### 2019-11-22 Miscellaneous_Presentations/beamer/pres.tex
updated

\documentclass{beamer}
\usepackage{etex}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{helvet,listings}
\usepackage{pgfpages}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{epsfig}
\usepackage{graphicx} % Allows including images
\usepackage{fancybox}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{caption}
\usepackage{subcaption}
\usepackage{vector}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclareGraphicsExtensions{.pdf,.png,.jpg, .eps}
\usepackage{epstopdf}
\usepackage{braket}
\usepackage{axodraw}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{amsmath,bm}
\usepackage{float}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\definecolor{darkpastelpurple}{rgb}{0.59, 0.44, 0.84}
\definecolor{darkpink}{rgb}{0.91, 0.33, 0.5}
\usepackage[font=scriptsize]{caption}
\usepackage{comment}
\usepackage{eso-pic}
\usetheme[compress]{Singapore}
\usepackage{transparent}

\title[Deuteron Electro-Disintegration]{Deuteron Electro-Disintegration At Very High Missing Momenta}
\author{Carlos Yero}
\institute[FIU]{Florida International University \\

\medskip
\textit{cyero002@fiu.edu} % Your email address
}

\date{\today}

% logo of my university
\titlegraphic{\includegraphics[width=2cm]{fiu_logo.jpg}\hspace*{1.5cm}~%
\includegraphics[width=3.5cm]{jlab_logo.jpg}\hspace*{1.8cm}~%
\includegraphics[width=2cm]{hallc_logo.png}

}

\setbeamertemplate{navigation symbols}{}

\setbeamertemplate{footline}[page number]

\begin{document}

\frame{\titlepage}

\section{Introduction}
\subsection{What is the Deuteron?}

\begin{frame}{What is the Deuteron?}
\begin{itemize}
\begin{footnotesize}
\item Discovered in 1931 by H. Urey
\item Starting point for studying NN interaction
\item Weakly bound state (2.22 MeV/pair)
\includegraphics[width=7.5cm]{BE_pernucleon.jpg}
\begin{figure}
\vspace{-3.9cm}\hspace{3.5cm}\includegraphics[width=1.9cm]{deuterium.jpg} \hspace{2cm} \includegraphics[width=2.2cm]{Harold_Urey.jpg} \\
\end{figure}
\end{footnotesize}
\end{itemize}
\vspace{0.2cm}
\begin{itemize}
\begin{footnotesize}
\item \textcolor{red}{Experiment:} Deuteron has + spatial parity $\implies$ L=0,2,4,$\dots$
\item \textcolor{red}{Experiment:} Total Angular Momentum $J=1\hbar$ $\implies S=s_{p}+s_{n}=\frac{1}{2}\otimes\frac{1}{2}=\textcolor{red}{\boxed{1}}\oplus 0$
\item $\ket{\psi_{D}}=a\ket{^{3}S_{1}(L=0)}+b\ket{^{3}D_{1}(L=2)}$
\item No observed nn or pp bound states (Pauli exclusion, only S=0 singlet state possible for identical fermions)
\item NN interaction is spin dependent 
\end{footnotesize}
\end{itemize}
\end{frame}

\subsection{Deuteron D-State Admixture}

\begin{frame}{Evidence of Deuteron D-state Admixture}
\begin{itemize}
\item Magnetic Dipole Moment \begin{small}$\mu_{d}=\mu^{\text{(orbital)}}_{p}+\mu^{\text{(spin)}}_{p}+\mu^{\text{(spin)}}_{n}$ \end{small} \\ 
\vspace{1mm}
\begin{footnotesize}$\mu^{\textcolor{blue}{tht}}_{d}(^{3}S_{1}(L=0))=\mu_{p}+\mu_{n}=0.879805\mu_{N}$ \hspace{ 1mm } $\mu^{\textcolor{blue}{tht}}_{d}(^{3}D_{1}(L=2))=0.310\mu_{N}$  \\
\vspace{1mm} 
$\mu^{\textcolor{red}{exp}}_{d}=0.85741 \pm 0.00002\mu_{N}$ \end{footnotesize}  
\vspace{3mm}
\item Electric Quadrupole Moment
\begin{itemize}
\item I.I. Rabi measured electric quadrupole moment in D (1939) \\
\item Multipole Expansion: \begin{footnotesize} $\phi(\mathbf{r}) = \phi_{m}(\mathbf{r}) + \phi_{d}(\mathbf{r}) + \phi_{q}(\mathbf{r}) + \cdots$ \\
$\phi(\mathbf{r}) = \sum\limits_{L}\sum\limits_{M=-L}^{L}C_{L}^{M}Y_{L}^{M}(\theta,\phi) = C_{0}^{0}Y_{0}^{0} + C_{2}^{M}Y_{2}^{M}(\theta,\phi)$ \end{footnotesize}  
\end{itemize}
\begin{footnotesize}
\begin{figure}[h!]
\vspace{-0.3cm}\hspace{0.0cm}\includegraphics[width=3.0cm]{multipole.jpg} \hspace{2.4cm} \includegraphics[width=3.1cm]{NN_potential.jpg}
\end{figure}
\hspace{0.7cm}$L=0$ \hspace{1.6cm} $L=2$ \\
\hspace{-0.2cm}$V_{int}=$\hspace{0.1cm}$V_{central}$ \hspace{0.4cm} + \hspace{0.6cm} $V_{non-central}$ $\implies$ tensor force 
\end{footnotesize}
\end{itemize}
\end{frame}

\section{Motivation}

\begin{frame}{Motivation}
\begin{itemize}
\begin{footnotesize}
\item Study Deuteron at short ranges ($\lesssim$ 1fm). \\
\vspace{0.2cm}
High momentum transfers ($Q^{2}$)$\implies$ probe the Deuteron at smaller distances. 
Smaller internucleon distances enables one to access the high momentum components of nucleons \\
\vspace{0.5cm}
\item Extract momentum distributions(not an observable) from cross sections
\vspace{0.5cm}
\item Study transition from hadronic to quark-gluon degrees of freedom \\
\end{footnotesize}
\end{itemize}
\includegraphics[width=8.0cm]{probe.png}
\end{frame}

\section{Theoretical Framework}

\begin{frame}{Theoretical Framework of D(e,e'p)n}
\begin{columns}
\column{.55\linewidth}
\begin{itemize}
\begin{footnotesize}
\item E.M. Interaction ($\alpha \sim \frac{1}{137}$) 
\vspace{0.5cm}
\item One Photon-Exchange Approximation is valid 
\vspace{0.5cm}
\item virtual photon interacts with Deuteron through a variety of processes
\vspace{0.5cm}
\item preferably, proton absorbs photon and is ejected while neutron recoils without
further interaction (missing neutron momenta is same
as internal momenta) \\
\end{footnotesize}
\end{itemize}
\column{.65\linewidth}
\includegraphics[width=5.0cm]{feynmann.jpg} \\
\begin{footnotesize}
$\mathit{k^{\mu} = (E, \mathbf{k}) \hspace{0.5cm} k^{\mu'}=(E',\mathbf{k'})}$ \\
\vspace{0.1cm}
$\mathit{q^{\mu}=(\omega, \mathbf{q})} $ \\
\vspace{0.1cm}
$\mathit{\omega=E'-E}$,  $\mathit{\mathbf{q}=\mathbf{k'}-\mathbf{k}}$ \\
\vspace{0.1cm}
$\mathit{P^{\mu}_{D}=(M_{D},\mathbf{P_{D}})}$ \\
\vspace{0.1cm}
$\mathit{\mathbf{P_{D}=p_{i,p}+p_{i,n}}=}0$ \\
\vspace{0.1cm}
$\mathit{Q^{2}\equiv-q_{\mu}q^{\mu}=4EE'\sin^{2}\Big(\frac{\theta_{e}}{2}\Big)}$
\end{footnotesize}
\end{columns}
\end{frame}

\subsection{Plane Wave Impulse Approximation}

\begin{frame}{Plane Wave Impulse Approximation (PWIA)}
\begin{columns}
\column{.55\linewidth}
\begin{itemize}
\begin{footnotesize}
\item virtual photon is completely absorbed by one of the nucleons
\vspace{0.5cm}
\item the other nucleon is a spectator
\vspace{0.5cm}
\item final state particles treated as plane waves (free particles)
\vspace{0.5cm}
\item \textcolor{darkpastelpurple}{process in which neutron absorbs photon (+PWBA) is suppressed only for
proton momenta significantly higher than missing momenta.}
\end{footnotesize}
\end{itemize}
\column{.85\linewidth}
\includegraphics[width=5.0cm]{PWIA.eps} \\
\vspace{1.0cm}
\textcolor{darkpastelpurple}{\boxed{\includegraphics[width=5.0cm]{PWBA.eps}}} \\
\end{columns}
\end{frame}

\subsection{Final State Interactions (FS1)}

\begin{frame}{Final State Interactions (FSI)}
\begin{columns}
\column{.55\linewidth}
\begin{itemize}
\begin{footnotesize}
\item in final state, the nucleons are at short enough distances ($\sim$ 2 fm)
and continue to interact 
\vspace{0.5cm}
\item eikonal approximation: infinite NN interactions are 
represented by an effective NN interaction amplitude
obtained from NN scattering experiments
\vspace{0.5cm}
\item nucleons re-scatter after interacting
\end{footnotesize}
\end{itemize}
\column{.85\linewidth}
\includegraphics[width=6.8cm]{FSI.eps} \\
\end{columns}
\end{frame}

\subsection{Meson Exchange Currents (MEC)}

\begin{frame}{Meson Exchange Currents (MEC)}
\begin{columns}
\column{.55\linewidth}
\begin{itemize}
\begin{footnotesize}
\item virtual photon couples with exchange meson between nucleons 
\vspace{0.5cm}
\item virtual meson may become real after photon absorption
\vspace{0.5cm}
\item meson exchange propagator is proportional
to $(1+\frac{Q^{2}}{m^{2}_{meson}})^{-1}$ \\
$\implies$ \textcolor{red}{MEC suppressed for $Q^{2}\gg m^{2}_{meson}$}
\end{footnotesize}
\end{itemize}
\column{.85\linewidth}
\includegraphics[width=5.0cm]{MEC.eps} \\
\end{columns}
\end{frame}

\subsection{Isobar Configuration Currents (IC)}

\begin{frame}{Isobar Configuration Currents (IC)}
\begin{columns}
\column{.50\linewidth}
\begin{itemize}
\begin{footnotesize}
\item virtual photon excites nucleon into resonance
\vspace{0.5cm}  
\item resonance de-excites through meson exchange with spectator nucleon
\vspace{0.5cm}
\item for high $Q^{2}$, and $x_{B_{j}}>1$
($x_{Bj}\equiv \frac{Q^{2}}{2M_{p}\omega}$) one is able to
probe the lower $\omega$ region of the quasi-elastic peak
to \textcolor{red}{suppress $\Delta$ or $N^{*}$  resonance production}

\end{footnotesize}
\end{itemize}
\column{.85\linewidth}
\includegraphics[width=5.0cm]{IC.eps} \\
\includegraphics[width=7.0cm]{crosssection_v_energy.png} \\
\end{columns}
\end{frame}

\section{D(e,e'p)n Data}
\subsection{Data from Mainz Microtron (MAMI)}

\begin{frame}
\begin{columns}
\column{.53\linewidth}
\tikz\draw[black,fill=black] (0,0) circle (.5ex); Data \\
\tikz{\draw[red,solid,line width=0.9pt](0,0) -- (10mm,0);} \small Arenh\"{o}vel (FSI+MEC+IC)\\
\tikz{\draw[red,dashed,line width=0.9pt](0,0) -- (10mm,0);} PWIA+FSI+MEC+IC+R  \\
\tikz{\draw[magenta,dotted,line width=0.9pt](0,0) -- (10mm,0);} PWIA+FSI+MEC  \\
\tikz{\draw[blue,dashed,line width=0.9pt](0,0) -- (10mm,0);} PWIA + PWBA  \\
\tikz{\draw[ao(english),dashdotted,line width=0.9pt](0,0) -- (10mm,0);} PWIA+FSI \\
\tikz{\draw[ao(english),dashed,line width=0.9pt](0,0) -- (10mm,0);} PWIA  \\
\vspace{5mm}
MAMI $Q^{2}=0.33$ (GeV/c)$^{2}$\\
Blomqvist et al. PLB 424 (1998) 33
\column{.50\linewidth}
\begin{figure}[t!]
\vspace{-0.5cm}
\hspace{-11.08mm}
\includegraphics[width=6.0cm]{MAMI.png} 
\end{figure}
\end{columns}
\end{frame}

\subsection{Data from Jefferson Lab (Hall A)}

\begin{frame}
\begin{columns}
\column{.53\linewidth}
\tikz\draw[black,fill=white] (0,0) circle (.5ex); Data (JLAB HallA) \\
\tikz{\draw[black,dashdotted,line width=1.3pt](0,0) -- (10mm,0);} JML (FSI+MEC+IC)  \\
\tikz{\draw[ao(english),dashed,line width=1.3pt](0,0) -- (10mm,0);} JML (FSI)  \\
\tikz{\draw[darkpastelpurple,solid,line width=1.3pt](0,0) -- (10mm,0);} MS using CD-Bonn potential\\
\tikz{\draw[darkpink,dashed,line width=1.3pt](0,0) -- (10mm,0);} JVO\\
\vspace{3mm}
$Q^{2}=3.5$ (GeV/c)$^{2}$ \\
\vspace{1mm}
(a)p$_{m}$=0.2 GeV/c \\
(b)p$_{m}$=0.4 GeV/c \\
(c)p$_{m}$=0.5 GeV/c \\
\vspace{5mm}
W.U. Boeglin et. al \\
PRL 107(2011) 262501
\column{.50\linewidth}
\begin{figure}[t!]
\vspace{-0.5cm}
\hspace{-11.08mm}
\includegraphics[width=5.5cm]{angular_dist.png} 
\end{figure}
\end{columns}
\end{frame}

\section{12 GeV Upgrade and D(e,e'p)n}
\subsection{High Momentum Spectrometer (HMS) and Super High Momentum Spectrometer (SHMS)}

\begin{frame}{{Hall C 12 GeV Upgrade and D(e,e'p)n}}
\centering
\hspace{1.0cm}\includegraphics[width=10.0cm]{HMS.pdf} 
\end{frame}

\subsection{Simulation of D(e,e'p)n at Hall C}

\begin{frame}
\begin{columns}
\column{.32\linewidth}
\footnotesize
\underline{D(e,e'p)n Kinematics}
$E_{e}=11$ GeV \\
$Q^{2}=4.25$ (GeV/c)$^{2}$ \\
$x_{B_{j}}=1.35$
$p_{m} = 0.5 - 1.0$ GeV/c \\
$\theta_{nq} = 35^{\circ} - 40^{\circ}$ \\
\vspace{5mm}
W.U. Boeglin et. al \\
Int.J.Mod.Phys. E24 \\
(2015) no.03, 1530003 
\column{.68\linewidth}
\begin{figure}[t!]
\hspace{-0.89cm}\includegraphics[width=8.18cm]{ang_dist2.png} 
\end{figure}
\end{columns} 
\end{frame}

\section{Conclusion and Future Outlook}

\begin{frame}{Conclusion and Future Outlook}
\begin{footnotesize}
\begin{itemize}
\item $np$ bound state serves as starting point to study the strong nuclear force
\vspace{0.5cm}
\item Investigate NN interaction at sub-fermi distances by using high energy $e^{-}$ probe
\vspace{0.5cm}
\item Previous experiments have shown that final state processes may be minimized in certain kinematic regions
\vspace{0.5cm}
\item There are theoretical expectations that at high $Q^{2}$ and $x_{Bj}>1$, soft two-body processes such as MEC and IC may be suppressed
\vspace{0.5cm}
\item With the 12 GeV Upgrade at HallC, the D(e,e'p)n experiment seeks to explore new kinematic regions (backed by experimental and theoretical support)  
that will enhance PWIA over other processes 
\end{itemize}
\end{footnotesize}
\end{frame}

\section{Acknowledgments}

\begin{frame}{Acknowledgments}
I would like to thank Drs. W. U. Boeglin and M.M. Sargsian for their experimental and theoretical contributions to the study of the Deuteron on this
presentation. \\
\vspace{2cm}
\begin{Huge}
\centerline{Thank You!}
\end{Huge}
\end{frame}

\end{document}

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/body.tex
updated

--- 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
@@
 \indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
-the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
-necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
-
-%We conclude that these results although very interesting, does not have the sufficient statistics and the
-%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\
-
-%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs
+the original proposal\cite{e12_10_003_proposal}, we conclude that additional beam time is required to measure the full kinematic coverage as the results presented on this Letter
+(although very interesting) do not have the necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed. \\
+\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
+to the equipment for the Hall C upgrade making all four commissioning experiments possible.

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/introduction.tex
updated

--- 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/introduction.tex
@@
-Being the only bound two-nucleon system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi level which is currently
+Being the only two-nucleon bound system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently
 not well understood. At such small internucleon distances the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which the interacting
@@
 The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
-Short-range studies of the deuteron are also important in determining whether or to what extent is the description of nuclei in terms of nucleon/meson degrees of freedom valid before
-having to include explicit quark effects, which is an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
-which a transition between nucleonic to quark degrees of freedom been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-This Letter presents first results of $^{2}H(e,e'p)n$ in which kinematics were taken to the limit where a transition to non-nucleonic degrees of freedom is expected.\\
+Short-range studies of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom is still valid before
+having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
+which a transition between nucleonic to quark degrees of freedom been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.\\
 \indent The most direct way to study the short range structure of the deuteron wavefunction (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at very high neutron recoil (or missing) momenta and within the PWIA kinematics. In this approximation, the virtual photon couples to
-the proton which is ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$.
-This gives direct access to the deuteron momentum distributions since the scattered neutron momentum remains unchanged from its initial state.
-\\
+electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA the virtual photon couples to
+the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
+to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
 \indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering between the proton and neutron (FSIs). Another possibility is that the
@@
 at a relatively low momentum transfer of $Q^{2}=0.665$ GeV$^{2}$ and neutron recoil momenta
-up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and their inclusion was necessary in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}
+up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}
 for a satisfactory agreement between theory and data. \\
@@
 the General Eikonal Approximation (GEA)\cite{sargsian_2001,PhysRevC.56.1124}, which predicts a strong angular dependence of FSI with neutron recoil angles with a peak at $\theta_{nq} \sim 70^{o}$.
-The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, due to statistical limitations it was impossible to select kinematical bins in $\theta_{nq}$ where
+The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it impossible to select kinematical bins in $\theta_{nq}$ where
 FSIs were small to extract momentum distributions.\\
@@
 The angular distributions of
-the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) versus $\theta_{nq}$ presented verified the strong anisotropy of FSIs with recoil angle also observed in Hall B\cite{PhysRevLett.98.262502}.
+the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented verified the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}.
 Most importantly, for recoil

### 2019-12-04 MY_PUBLICATIONS/PRL/draft_v1/prl.tex
updated

--- 2019-11-07 MY_PUBLICATIONS/PRL/prl.tex
@@
 \widetext
-\leftline{Version xx as of \today}
+\leftline{Version 01 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
 
+%CURRENTLY CORRECTING
 \begin{abstract}
-  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
-  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
-  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
-  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
-  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.
-
-%  momentum distribution has been determined from measured for neutron recoil momenta up to 1.14 GeV/c.
-
-  %An article usually includes an abstract, a concise summary of the work
-%covered at length in the main body of the article. It is used for
-%secondary publications and for information retrieval purposes.
-%For PRL, the rule of thumb is that the abstract should be less than
-%8 lines and the text (excluding authors, abstract but including tables,
-%figures and references) should be less than 4 pages (leave about 20 lines
-%empty on page 4) in two-column format.
-%PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
-%Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
-%relevant to your paper. A set of standard references can be found at the
-%end of this example paper.
+  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ for 
+  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c and neutron recoil angles ($\theta_{nq}$) of 35, 45 and 75 degrees are presented. At the selected kinematics,
+  Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. At recoil angles of 35 and 45 degrees, Final State Interactions (FSI) have been suppressed
+  and the Plane Wave Impulse Approximation (PWIA) provides the dominant cross section contribution. A comparison to recent theoretical calculations show the data to be sensitive
+  to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
 \end{abstract}
@@
 \input body.tex
-%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\   %This space must remain here to keep the acknowledgemn section in place
 \input acknowledgement.tex    % input acknowledgement
 \bibliography{prl}
-
+%.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \end{document}

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/body.tex
updated

--- 2019-11-14 MY_PUBLICATIONS/PRL/draft_v0/body.tex
@@
 \indent This experiment was part of a group of four experiments that commissioned the new Hall C Super High Momentum Spectrometer (SHMS) as part of the 12 GeV upgrade at JLab.
-A 10.6005 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
-by the SHMS and High Momentum Spectrometer (HMS), respectivly. The ``missing'' (undetected) neutron was reconstructed from momentum conservation laws.
-The beam currents delivered by the accelerator ranged between 40-60 $\mu$A due to frequent beam trips at higher currents and the beam was rastered over a 2x2 mm$^{2}$ area to reduce
-the effects of localized boiling on the cryogenic targets (hydrogen and deuterium). \\
+A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
+by the SHMS and the High Momentum Spectrometer (HMS), respectively. The ``missing'' (undetected) neutron was reconstructed from energy-momentum conservation laws:
+$\vec{p_{r}} = \vec{q} - \vec{p_{f}}$ (missing momentum) and $E_{m} = \omega - T_{p} - T_{r}$ (missing energy), where $\vec{p_{f}}$ is the final proton momentum, $(T_{p}, T_{r})$ are the
+final proton and neutron kinetic energies, and $E_{m}$ is the binding (missing) energy of the deuteron.
+The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).
+\\
 \indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes\cite{hodo_techreport} (scintillator arrays) used for triggering,
@@
 ($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section. \\
-\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. In the high missing momentum settings the spectrometer configuration was changed
-multiple times resulting in either the spectrometer angle or momentum not being excactly the same.
-As a result, two separate data sets were measured for the 580 MeV/c setting and three data sets for the 750 MeV/c setting.
-The spectrometer central settings are approximately as follows: the SHMS central angle and momentum settings were kept ``fixed'' at ($\sim$12.194 deg, 8.5342 GeV/c) and the HMS central angle and momentum settings were changed from
-(38.896 deg, 2.840 GeV/c) at the 80 MeV setting to $\sim$(54.992 deg, 2.1925 GeV/c) and $\sim$(58.391 deg, 2.0915 GeV/c) at the 580 and 750 MeV/c settings, respectively. \\
-\indent At these kinematics, the 3-momentum transfer is $|\vec{q}| \sim 2.88$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$) measured on this experiment. As a result
-one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$, $\theta_{pq}\sim 0$.
-This configuration is known as the ``parallel-kinematics'' and suppresses the process in which the
-neutron is struck while the detected proton is a spectator. FSIs are also expected to be largely reduced as compared to the ``perpendicular-kinematics'' in which the
-proton is detected almost perpendicular to $\vec{q}$ based on a calculation by Arenh\"{o}vel on Table 1 of Ref.\cite{pr01-020}.\\
-% (5) At these kinematics, the 3-momentum transfer is $|\vec{q}| = 2.86$ GeV/c and is on the order of the final proton momentum indicating that most of the energy and momentum are transferred
-%to the proton. As a result, the ejected proton scatters at angles $\theta_{pq}\sim 0$, relative to the $\vec{q}$. This configuration is known as the ``parallel-kinematics'' and suppresses
-%the process in which the neutron is struck and the proton is a spectator. \\
-\indent In addition to deuteron kinematics,  $^{1}H(e,e'p)$ elastic data was also taken at kinematics close to the deuteron 80 MeV setting for cross-checks with the spectrometer acceptance model as well as for normalization purposes using the  Hall C Monte Carlo
+\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
+At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) moved from smaller to larger angles corresponding the
+the lower and higher missing momentum settings, respectively.
+At these kinematics, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$)
+measured on this experiment.
+As a result one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
+At these forward angles and large momentum transferred to the proton, the additional process in which the recoiling neutron is struck by the vitrual photon is suppressed. \\
+\indent Hydrogen elastic ($^{1}H(e,e'p)$) data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
-Additional $^{1}H(e,e'p)$ data was also taken at three other kinematic settings that covered the entire SHMS momentum acceptance range and were used for spectrometer optics optimization,
-momentum calibration and determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\
-\indent The event selection criteria was done exactly the same for the hydrogen and deuteron data.
-The criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
-is well known, 2) an HMS collimator cut to restrict the spectrometer solid angle acceptance to events that only passed through the collimator and not by re-scattering from the collimator edges, 3) a missing
-energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $ep$ coincidences and not events from the radiative tail, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
-SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a z-vertex difference cut between the HMS and SHMS $z$ reaction vertex difference to select events that truly
+Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
+momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}. \\
+\indent Identical event selection criteria were used for the hydrogen and deuteron data.
+The criteria were determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
+is well known, 2) a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, 3) a missing
+energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, 4) a coincidence time cut to select true coincidence events and not accidentals,  5) a PID cut on the
+SHMS calorimeter to select electrons and not other sources of background, mostly pions and 6) a cut on the reconstructed HMS and SHMS reaction vertices to select events that truly
 originated from the same reaction vertex at the target. \\
-\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption\cite{cyero_pAbs} and target boiling factors\cite{cyero_tgtBoil}.
-For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
+\indent The experimental data yield for both hydrogen and deuteron data was normalized by the total charge and corrected for various inefficiencies.
+For $^{2}H(e,e'p)n$ the corrections were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS),
+total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}. \\
+\indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
 model.
-The data to SIMC yield ratio integrated over invariant mass $W$ was determined to be unity, so there was no need to include an overall hydrogen normalization factor.
-For the $^{2}H(e,e'p)n$ data,
-the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. Variations
-of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential.
-The 80 MeV data was also checked for reproducibility against the Hall A data (See Fig.
-\ref{fig:fig2}).
-This agreement gives us confidence on the measurements made at higher missing momentum setting for which no previous data exists. \\
+The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$.
+For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig.
+\ref{fig:fig1}).
+The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist. \\
 \indent The systematic uncertainties on the measured cross sections were determined from normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
@@
 (Private communication with D.
-Mack)} and kinematic uncertainties.
-The individual contributions from normalization uncertainties
-were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
+Mack)} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings.
+The individual
+contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
 for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
-\indent The kinematic uncertainties were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
+\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
 of different data sets. For $\theta_{nq}=$ 35, 45 and 75 deg (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
-The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This results was then added in quadrature
+The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
 to the statiscial uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
-\indent The data was radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
-Bin-centering
-corrections were also applied by multiplying the radiative corrected cross sections to the ratio of theoretical cross sections (external to SIMC) to the average cross sections calculated from SIMC.
-The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential\cite{PhysRevC.21.861}. \\
-\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were averaged for overlapping bins in $p_{r}$,
-where the reduced cross sections are defined as follows:
+\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
+For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated. The ratio between the calculated cross section at the averaged kinematics and the averaged
+cross section for this bin has also been determined and used to compare theoretical models to the experimental cross sections.
+The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
+\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were 
+\onecolumngrid
+\begin{center}
+\begin{figure}[hb!]
+\includegraphics[scale=0.45]{../prl_plots/PRL_plot1.pdf}
+\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
+with a bin width of $\pm 5^{o}$.
+The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
+AV18(green) and CD-Bonn(magenta) NN potentials}
+\label{fig:fig1}
+\end{figure}
+\end{center}
+\twocolumngrid
+\noindent averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
-integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using P.
-Bosted's form factor parametrization \cite{PhysRevC.51.409}.
-Only within the PWIA, can $\sigma_{red}$ be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
-cross section have been factored out by $\sigma_{cc1}$, leaving only a dependency on $p_{r}$. \\
-\begin{figure}
-\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
-\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
-                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
-\label{fig:fig1}
-\end{figure}
-\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
-relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig.
-\ref{fig:fig1}.
+where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor that arises from the
+integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
+Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. \\
+%--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
+\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
+(GeV/c)$^{2}$.
+The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.
+The overlay of the Hall A data (cyan) in Fig.
+\ref{fig:fig1}
+provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
+was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
+\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
+smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
+This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
+This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
+As a result, our data at larger recoil angles
+is statistically limited. \\
+\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
+momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
+NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
+\indent In Fig.
+\hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
+to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
+a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig.
+\hyperref[fig:fig1]{1(a)}.
+For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
+
+%---------------------------------------------------------------------------------------------------------------------
+
+%------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
+
+%\begin{figure}
+%\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
+%\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+%                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
+%\label{fig:fig2}
+%\end{figure}
+%\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
+%relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig.
+\ref{fig:fig2}.
 The theoretical calculations for the
-CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M.
+%CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M.
 Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M.
@@
 For $p_{r}\lesssim 300$ MeV/c, the data is
-in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
-the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
-up to $\sim$ 800 MeV/c before being overwhelmed by FSIs. The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
-with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}], both the data and
-CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
-a similar behaviour as in Fig.
-\hyperref[fig:fig1]{1(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model.
+%in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig2}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}],
+%the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
+%up to $\sim$ 800 MeV/c before being overwhelmed by FSIs.
+The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
+%with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(b)}], both the data and
+%CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
+%a similar behaviour as in Fig.
+\hyperref[fig:fig2]{2(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model.
 For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}], the
-onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
-at larger recoil angles. \\
-\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
-GeV$^{2}$.
-The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 GeV$^{2}$.
-The overlay of the Hall A data (cyan) in Fig.
-\ref{fig:fig2}
-provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
-was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
-\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
-\hyperref[fig:fig2]{2(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
-smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
-This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
-This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
-As a result, our data at larger recoil angles
-is statistically limited. \\
-\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig2]{2(a)} and  \hyperref[fig:fig2]{2(b)},  all models predict similar behaviour of the
-momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
-NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
-\indent In Fig.
-\hyperref[fig:fig2]{2(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
-to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig2]{2(b)},
-a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum dis-
-\onecolumngrid
-\begin{center}
-\begin{figure}[hb!]
-\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
-with a bin width of $\pm 5^{o}$.
-The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the Paris(blue), AV18(green) and CD-Bonn(magenta) theoretical reduced cross sections.}
-\label{fig:fig2}
-\end{figure}
-\end{center} \\
-%Begin text ON NEW PAGE after FIGURE 2. If Figure 2 changed position, move text from previous page (top) to this page (bottom)
-\twocolumngrid
-\noindent tributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig. \hyperref[fig:fig2]{2(a)}.
-For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
-\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
-unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
-%while suppressing long-range processes such as MECs or ICs. FSIs have also been largely suppressed by selecting a kinematic window found in the previous Hall A 
-%experiment where FSIs were found to be reduced and independent of missing momentum at recoil angles $35^{o}\leq\theta_{nq}\leq45^{o}$. This experiment took advantage
-%of that kinematic window and extended the cross section measurements beyond $p_{r}\sim$500 MeV/c.
-The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
-up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
-behavior that was not predicted by any of the models. \\
-\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
-the original proposal\cite{e12_10_003_proposal}, we conclude that the results presented on this Letter (although very interesting) do not have the
-necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed.
+\hyperref[fig:fig2]{2(c)}], the
+%onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
+%at larger recoil angles. \\
 
-%We conclude that these results although very interesting, does not have the sufficient statistics and the
-%required number of high missing momentum settings to make a definitive argument about the underlying physics observed.\\
+%-------------------------------------------------------------------------------------------------------------------------------
 
-%high momentum components of the deuteron wavefunction by suppressing other reaction mechanisms such as MECs or ICs
+%----------CONCLUSION----------
+
+%\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+%unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
+%The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
+%up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
+%behavior that was not predicted by any of the models. \\
+%\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
+%the original proposal\cite{e12_10_003_proposal}, we conclude that additional beam time is required to measure the full kinematic coverage as the results presented on this Letter
+%(although very interesting) do not have the necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed. \\
+%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
+%to the equipment for the Hall C upgrade making all four commissioning experiments possible.
+
+%-------------------------------

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/introduction.tex
updated

@@
 the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
+to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\
 \indent In reality, the ejected particles undergo subsequent interactions resulting in re-scattering between the proton and neutron (FSIs). Another possibility is that the
 photon may couple to the virtual meson being exchanged between the nucleons (MECs), or the photon may excite either nucleon in the deuteron into a resonance state (ICs) which
-decays back into the ground state nucleon causing futher re-scattering between the proton and neutron. Both MECs and ICs in addition to FSIs can significantly alter the recoiling neutron
+decays back into the ground state nucleon causing further re-scattering between the proton and neutron. Both MECs and ICs in addition to FSIs can significantly alter the recoiling neutron
 momentum thereby obscuring any possibility of directly accessing the deuteron momentum distributions. \\
-%(1) The above-mentioned long-range processes alter the final neutron
-%momentum making the deuteron momentum distributions difficult to access.\\
-\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped constrain and quantify the contributions from FSIs, MECs and ICs on
-the $^{2}H(e,e'p)n$ cross-section and determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).
+\indent Theoretically, MECs and ICs are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
+The suppression of MECs can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ (GeV/c)$^{2}$ and
+$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}.
+The ICs can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
+electro-production threshold. \\
+\indent For FSIs at large $Q^{2}$, the onset of the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} is expected which predicts a strong angular dependence of the FSIs with neutron recoil angles where FSI peaks at $\theta_{nq}\sim70^{o}$.
+The
+most important prediction from GEA, however, is that at large recoil momenta $p_{r}$ where FSIs are expected to be large, there is an approximate cancellation of the PWIA/FSI interference (screening term) with the
+modulus-squared of the FSI amplitude (rescattering term).
+This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$,
+opening a kinematic window to study the short-range structure of the deuteron. \\
+\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped confirmed various of the abovementioned theoretical predictions as well as constrain and quantify the contributions from FSIs, MECs and ICs on
+the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).
 The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
-at a relatively low momentum transfer of $Q^{2}=0.665$ GeV$^{2}$ and neutron recoil momenta
-up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs played a significant role and had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214}
-for a satisfactory agreement between theory and data. \\
-%(2) the inclusion of FSI, MEC and IC was necessary in Arenhovel's calculations for a satisfactory
-%agreement between the theory and data. \\
+at a relatively low momentum transfer of $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs dominate the cross section and
+had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214} for a satisfactory agreement between theory and data. \\
 \indent The next experiment was performed in Hall B \cite{PhysRevLett.98.262502} using the CEBAF Large Acceptance Spectrometer (CLAS) which measured a wide variety of kinematic settings
 giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics. This was the first experiment to probe
-the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 GeV$^{2}$) and presented angular distributions of cross-sections that confirmed the onset of
-the General Eikonal Approximation (GEA)\cite{sargsian_2001,PhysRevC.56.1124}, which predicts a strong angular dependence of FSI with neutron recoil angles with a peak at $\theta_{nq} \sim 70^{o}$.
-The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it impossible to select kinematical bins in $\theta_{nq}$ where
-FSIs were small to extract momentum distributions.\\
-% (3) The cross-sections versus neutron recoil momenta up to 2 GeV/c were also presented with integrated neutron recoil angles in the range $20^{o}< \theta_{nq}<160^{o}$
-%to gain better statistical precision. As a result, it was not possible to choose kinematical regions binned in $\theta_{nq}$ in which FSI were minimal to extract the momentum distributions. \\
-\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at published $Q^{2} = 3.5\pm0.25$ GeV$^{2}$ and recoil momenta up to 550 MeV/c.
+the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$) and presented angular distributions of cross-sections that exhibited a strong angular dependence of FSI with neutron recoil angles peaking
+at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}.
+The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it necessary to integrate over a wide angular range making it impossible to control
+contributions from FSIs, MECs and ICs. \\
+\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at $Q^{2} = 3.5\pm0.25$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c.
 The angular distributions of
-the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented verified the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}.
+the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented confirmed the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}.
 Most importantly, for recoil
@@
 cross-section to FSIs. This kinematic window allowed for the first time the extraction of momentum distributions for neutron recoil momenta up to $p_{r}\sim$550 MeV/c. \\
-% (4) This kinematic window in which FSI are small can also be seen in the momentum distributions for
-%$\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, where data and theory agree well within the PWIA kinematics.
-\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measruements
-to $Q^{2}=4.5\pm0.5$ GeV$^{2}$ and neutron recoil momenta up to 1.18 GeV/c.
+\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.18 GeV/c.
 At these kinematics, MECs and ICs are suppressed and FSIs are under control for neutron recoil angles between 35 and 45 degrees

### 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/prl.tex
updated

@@
 
-%CURRENTLY CORRECTING
 \begin{abstract}
-  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 GeV$^{2}$ for 
-  neutron recoil momenta up to $p_{r}\sim$1.18 GeV/c and neutron recoil angles ($\theta_{nq}$) of 35, 45 and 75 degrees are presented. At the selected kinematics,
-  Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. At recoil angles of 35 and 45 degrees, Final State Interactions (FSI) have been suppressed
-  and the Plane Wave Impulse Approximation (PWIA) provides the dominant cross section contribution. A comparison to recent theoretical calculations show the data to be sensitive
-  to momentum distributions up to $p_{r}\sim$ 750 MeV/c.
+  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+  for neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c at several fixed neutron recoil angles ($\theta_{nq}$)
+  with respect to the 3-momentum transfer, $\vec{q}$. At neutron angles of 35 and 45 degrees final state interactions (FSIs) as well as
+  meson exchange currents (MECs) and isobar configurations (ICs) are expected to be suppressed and the plane wave impulse
+  approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent theoretical
+  calculations where significant disagreement at very high missing momenta has been observed.
 \end{abstract}

### 2019-12-09 MY_PUBLICATIONS/PRL/draft_v1/body.tex
updated

@@
 ($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section. \\
-\indent We measured three missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
-At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) moved from smaller to larger angles corresponding the
+\indent We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
+At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding the
 the lower and higher missing momentum settings, respectively.
@@
 %--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
-\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
+\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
 (GeV/c)$^{2}$.
-The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.
+The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
 The overlay of the Hall A data (cyan) in Fig.
@@
 For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
-
 %---------------------------------------------------------------------------------------------------------------------
-
 %------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
-
-%\begin{figure}
-%\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
-%\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
-%                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
-%\label{fig:fig2}
-%\end{figure}
-%\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
-%relative to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001} potential is shown in Fig.
+\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions (n$(p_{r})$) is shown in Fig.
 \ref{fig:fig2}.
-The theoretical calculations for the
-%CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} potentials were performed by M.
-Sargsian and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M.
-Laget.
-For $p_{r}\lesssim 300$ MeV/c, the data is
-%in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig2}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}],
-%the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
-%up to $\sim$ 800 MeV/c before being overwhelmed by FSIs.
-The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
-%with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig2]{2(b)}], both the data and
-%CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn, whereas the data shows
-%a similar behaviour as in Fig.
-\hyperref[fig:fig2]{2(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model.
-For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig.
-\hyperref[fig:fig2]{2(c)}], the
-%onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
-%at larger recoil angles. \\
-
+As a reference we selected the
+deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
+The theoretical calculations for the CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38}
+potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget\cite{LAGET2005}.
+\begin{figure}[h!]
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
+\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided.
+}
+\label{fig:fig2}
+\end{figure} \\
+\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for
+all theoretical calculations as compared to the reference.
+In this region, our experiment is statistically limited as we focused on kinematics at lower recoil angles where FSIs are small.
+The overlayed
+Hall A data, however, shows excellent agreement with the Paris FSI.
+For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the data follows.
+The
+small dip observed in this region (R$<1$) is indicative of the approximate cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in the cross section.
+\\
+\indent For $\theta_{nq}=45^{o}$ [Fig.
+\hyperref[fig:fig2]{2(b)}] at $p_{r}<300$ MeV/c, all theoretical calculations agree with each other and are sensitive to the momentum distribution inside the deuteron which
+the data confirms. At $p_{r}\gtrsim300$ MeV/c, the Paris/AV18 calculations start to deviate from the CD-Bonn calculations, with the most substantial deviations observed at $p_{r}\sim 1$ GeV/c.
+The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
+The data is clearly sensitive to the momentum distributions using the CD-Bonn calculations and show an earlier rise than predicted by theory, a behaviour which is not described by any of the models.
+\\
+\indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig.
+\hyperref[fig:fig2]{2(a)}], where the CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c before being
+overwhelmed by FSIs, whereas the Paris/AV18 calculations start to deviate from the CD-Bonn at $p_{r}\sim300$ MeV/c.
+The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
+transitioning ($R>1$) to other models. \\ 
+\indent The $\theta_{nq}=35^{o}$ [Fig.
+\hyperref[fig:fig2]{2(a)}] is clearly the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
+distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\
 %-------------------------------------------------------------------------------------------------------------------------------
-
 %----------CONCLUSION----------
-
-%\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
-%unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhances the high momentum components of the deuteron wavefunctions.
-%The experimental reduced cross sections were extracted and found to be best described by the CD-Bonn potential with sensitivity to the CD-Bonn momentum distributions
-%up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
-%behavior that was not predicted by any of the models. \\
-%\indent Given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
-%the original proposal\cite{e12_10_003_proposal}, we conclude that additional beam time is required to measure the full kinematic coverage as the results presented on this Letter
-%(although very interesting) do not have the necessary statistics and the required number of high missing momentum settings to make a definitive argument about the underlying physics observed. \\
-%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
-%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-%to the equipment for the Hall C upgrade making all four commissioning experiments possible.
+\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
+The experimental reduced cross sections were extracted and found to be best described by M. Sargsian's calculations using the CD-Bonn potential with sensitivity to the momentum distributions
+up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
+behavior that was not predicted by any of the models. The early transition observed in both the 35 ad 45 degrees kinematic settings gives a hint that 
+there might be additional degrees of freedom (transition to quark-gluon degrees of freedom) that might not be accounted for in NN potentials presented. \\
+\indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
+the original proposal\cite{e12_10_003_proposal}, additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
+in order to make any definitive arguments about the underlying physics observed. \\
+\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
+to the equipment for the Hall C upgrade making all four commissioning experiments possible.
 

### 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

--- 2019-12-09 MY_PUBLICATIONS/PRL/draft_v1/body.tex
@@
 \\
-\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four sets of hodoscope planes\cite{hodo_techreport} (scintillator arrays) used for triggering,
+\indent Both spectrometers at Hall C have similar standard detector packages, each with 1) four scintillator planes\cite{hodo_techreport} used for triggering,
 2) a pair of drift chambers\cite{dc_techreport} used for tracking, 3) a calorimeter\cite{Mkrtchyan_2013} used for $e^{-}/\pi^{-}$ discrimination and 4) a gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used also for $e^{-}/\pi^{-}$ separation.
@@
 measured on this experiment.
-As a result one can infer that most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
-At these forward angles and large momentum transferred to the proton, the additional process in which the recoiling neutron is struck by the vitrual photon is suppressed. \\
-\indent Hydrogen elastic ($^{1}H(e,e'p)$) data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
+As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
+At these forward angles and large momentum transferred to the proton, the additional process in which the neutron is struck by the virtual photon is suppressed. \\
+\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
@@
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects.
-For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated. The ratio between the calculated cross section at the averaged kinematics and the averaged
-cross section for this bin has also been determined and used to compare theoretical models to the experimental cross sections.
-The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
+For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has also been calculated and used in the bin centering correction factor defined as:
+$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross
+section averaged over the kinematic bin. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
 \indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were 
@@
 \begin{figure}[hb!]
-\includegraphics[scale=0.45]{../prl_plots/PRL_plot1.pdf}
+\includegraphics[scale=0.50]{../prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
@@
 (GeV/c)$^{2}$.
-The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
+The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
+The data is compared to theoretical reduced
+cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials.
+The theoretical calculations
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
+\indent At recoil angles $\theta_{nq}=75^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}], all models agree and are sensitive to momentum distributions up to $p_{r}\sim$300 MeV/c.
+Beyond $p_{r}\sim$300 MeV/c, FSIs become
+dominant and all models exhibit a similar behaviour which obscures any possibility of extracting the momentum distributions at these angles.
+At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ shown in
+Figs.
+\hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)}, all models are sensitive to momentum distributions to some extent beyond $300$ MeV/c before FSIs start to appear.
+The Paris and AV18 calculations
+exhibit a similar behaviour in the momentum distributions as opposed to the CD-Bonn calculation, where FSIs start to show up earlier than the other models predict.
+
+%The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
 The overlay of the Hall A data (cyan) in Fig.
 \ref{fig:fig1}
-provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
-was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
-\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
+%provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
+%was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
+%\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
 \hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
-smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
+%smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
 This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
-This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
+%This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
 As a result, our data at larger recoil angles
-is statistically limited. \\
-\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
-momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
-NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
-\indent In Fig.
+%is statistically limited. \\
+%\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
+%momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
+%NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
+%\indent In Fig.
 \hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
-to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
-a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig.
+%to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
+%a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig.
 \hyperref[fig:fig1]{1(a)}.
-For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
+%For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
 %---------------------------------------------------------------------------------------------------------------------

### 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/introduction.tex
update

--- 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/introduction.tex
@@
-Being the only two-nucleon bound system, the deuteron serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently
+The deuteron is the only two-nucleon bound system. Therefore, it serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently
 not well understood. At such small internucleon distances the NN (nucleon-nucleon) potential is expected to exhibit a repulsive core in which the interacting
@@
 \indent The most direct way to study the short range structure of the deuteron wavefunction (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA the virtual photon couples to
-the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron, which carries a momentum equal in magnitude but opposite in direction
+electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA, the virtual photon couples to
+the proton which is subsequently ejected from the nucleus without further interaction with the recoiling neutron. The neutron carries a momentum equal in magnitude but opposite in direction
 to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\
@@
 modulus-squared of the FSI amplitude (rescattering term).
-This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$,
-opening a kinematic window to study the short-range structure of the deuteron. \\
+This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
+\\
 \indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped confirmed various of the abovementioned theoretical predictions as well as constrain and quantify the contributions from FSIs, MECs and ICs on
@@
 The angular distributions of
-the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented confirmed the strong anisotropy of FSIs with recoil angle $\theta_{nq}$ also observed in Hall B\cite{PhysRevLett.98.262502}.
-Most importantly, for recoil
-neutron momentum bins, $p_{r}=0.4\pm0.02$ and $0.5\pm0.02$ GeV/c, the ratio was found to be $R\sim1$ for $35^{o}\leq \theta_{nq}\leq45^{o}$ indicating a reduced sensitivity of the experimental
-cross-section to FSIs. This kinematic window allowed for the first time the extraction of momentum distributions for neutron recoil momenta up to $p_{r}\sim$550 MeV/c. \\
-\indent The experiment presented on this Letter takes advantage of the kinematic window previosuly found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements
+the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented saw agreement in shape with the angular distributions in Hall B\cite{PhysRevLett.98.262502} with FSI peaking at $\theta_{nq}\sim70^{o}$.
+With the increased statistics in Hall A, a direct comparison of the momentum distributions between data and theory could be made for specific $\theta_{nq}$ bins.
+For the first time, at $\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\
+\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements
 to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.18 GeV/c.

### 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

@@
 model.
-The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$.
+The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).
 For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig.
@@
 Beyond $p_{r}\sim$300 MeV/c, FSIs become
-dominant and all models exhibit a similar behaviour which obscures any possibility of extracting the momentum distributions at these angles.
-At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ shown in
-Figs.
-\hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)}, all models are sensitive to momentum distributions to some extent beyond $300$ MeV/c before FSIs start to appear.
-The Paris and AV18 calculations
-exhibit a similar behaviour in the momentum distributions as opposed to the CD-Bonn calculation, where FSIs start to show up earlier than the other models predict.
+dominant and exhibit a similar behaviour among all models which obscures any possibility of extracting the momentum distributions at these angles.
+At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$
+[Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 calculations show sensitivity to momentum distributions and are within good agreement whereas the CD-Bonn calculation exhibits
+a different behaviour beyond $p_{r}\sim$300 MeV/c which indicates a larger sensitivity to the different NN-potentials at higher missing momenta.
 
@@
 deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
-The theoretical calculations for the CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38}
-potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget\cite{LAGET2005}.
 \begin{figure}[h!]
@@
 Hall A data, however, shows excellent agreement with the Paris FSI.
-For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the data follows.
-The
-small dip observed in this region (R$<1$) is indicative of the approximate cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in the cross section.
-\\
+For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
+data follows.
+The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
+the cross section. \\
 \indent For $\theta_{nq}=45^{o}$ [Fig.
@@
 The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
-The data is clearly sensitive to the momentum distributions using the CD-Bonn calculations and show an earlier rise than predicted by theory, a behaviour which is not described by any of the models.
-\\
+The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\
 \indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig.
@@
 The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
-transitioning ($R>1$) to other models. \\ 
+exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
 \indent The $\theta_{nq}=35^{o}$ [Fig.
-\hyperref[fig:fig2]{2(a)}] is clearly the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
+\hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
 distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\
@@
 %----------CONCLUSION----------
-\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
 unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
-The experimental reduced cross sections were extracted and found to be best described by M. Sargsian's calculations using the CD-Bonn potential with sensitivity to the momentum distributions
-up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
-behavior that was not predicted by any of the models. The early transition observed in both the 35 ad 45 degrees kinematic settings gives a hint that 
-there might be additional degrees of freedom (transition to quark-gluon degrees of freedom) that might not be accounted for in NN potentials presented. \\
+The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
+were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
+up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.
+Given that this is a commissioning experiment that ran
+
 \indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
@@
 in order to make any definitive arguments about the underlying physics observed. \\
+
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab

### 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

@@
 \indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were
+averaged for overlapping bins in $p_{r}$. 
 \onecolumngrid
@@
 \begin{figure}[hb!]
-\includegraphics[scale=0.50]{../prl_plots/PRL_plot1.pdf}
+\includegraphics[scale=0.46]{../prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
@@
 \twocolumngrid
-\noindent averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
+\noindent The reduced cross sections are defined as follows:
 \begin{equation}
@@
 were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
-up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.
-Given that this is a commissioning experiment that ran
-
-\indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
-the original proposal\cite{e12_10_003_proposal}, additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
+up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\
+\indent Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
+additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
 in order to make any definitive arguments about the underlying physics observed. \\
-
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab

### 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/prl.tex
update

--- 2019-12-06 MY_PUBLICATIONS/PRL/draft_v1/prl.tex
@@
 %  Add 'showpacs' option to make PACS codes appear
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress, preprint]{revtex4-2}  % for review and submission
 %\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
@@
 \widetext
-\leftline{Version 01 as of \today}
+\leftline{Version 02 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
 \leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
-\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
+\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
 
@@
 \input body.tex
-\input acknowledgement.tex    % input acknowledgement
+%\input acknowledgement.tex    % input acknowledgement
 \bibliography{prl}

### 2019-12-19 MY_PUBLICATIONS/PRL/draft_v2/prl.tex
updated

@@
 %  Add 'showpacs' option to make PACS codes appear
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress, preprint]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
 %\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
@@
 \begin{abstract}
-  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-  for neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c at several fixed neutron recoil angles ($\theta_{nq}$)
-  with respect to the 3-momentum transfer, $\vec{q}$. At neutron angles of 35 and 45 degrees final state interactions (FSIs) as well as
-  meson exchange currents (MECs) and isobar configurations (ICs) are expected to be suppressed and the plane wave impulse
-  approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent theoretical
-  calculations where significant disagreement at very high missing momenta has been observed.
+  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c. The data have been obtained at fixed neutron recoil angles
+($\theta_{nq}$) of 35$^\circ$ and 45$^\circ$  with respect to the 3-momentum
+transfer, $\vec q$. At these kinematic settings final state interactions (FSIs),
+meson exchange currents (MECs) and isobar configurations (ICs) are expected to 
+be suppressed and the plane wave impulse approximation (PWIA) provides the
+dominant cross section contribution. The new data are compared to recent
+theoretical calculations where a significant disagreement at very high
+missing momenta has been observed.
+
 \end{abstract}

### 2020-01-03 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated draft 3

--- 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/body.tex
@@
 section averaged over the kinematic bin. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
-\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently and were
-averaged for overlapping bins in $p_{r}$. 
+\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross 
 \onecolumngrid
@@
 \twocolumngrid
-\noindent The reduced cross sections are defined as follows:
+\noindent sections for each data set independently and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
 \begin{equation}
@@
 for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
-\indent At recoil angles $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}], all models agree and are sensitive to momentum distributions up to $p_{r}\sim$300 MeV/c.
-Beyond $p_{r}\sim$300 MeV/c, FSIs become
-dominant and exhibit a similar behaviour among all models which obscures any possibility of extracting the momentum distributions at these angles.
-At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$
-[Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 calculations show sensitivity to momentum distributions and are within good agreement whereas the CD-Bonn calculation exhibits
-a different behaviour beyond $p_{r}\sim$300 MeV/c which indicates a larger sensitivity to the different NN-potentials at higher missing momenta.
-
-%The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
-The overlay of the Hall A data (cyan) in Fig.
-\ref{fig:fig1}
-%provides a continutity to the data from this experiment in the transition from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there
-%was no data. There is also an overall good agreement between the two experiments in the regions in which they overlap in $p_{r}$. \\
-%\indent At larger neutron recoil angles of $\theta_{nq}\sim75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}], the data follows the CD-Bonn PWIA (momentum distributions) up to $p_{r}\sim $100 MeV/c, and at $p_{r}\gtrsim$300 MeV/c, the FSIs become the dominat process and exhibit a
-%smaller falloff with $p_{r}$ which obscures any possibility of extracting the momentum distributions.
-This behaviour of FSI with larger recoil angles was predicted by the GEA\cite{Sargsian_2001,PhysRevC.56.1124} and was verified in previous experiments\cite{PhysRevLett.107.262501,PhysRevLett.98.262502}.
-%This experiment kinematics moves away from larger recoil angles and focuses on fowards angles at $\theta_{nq}\sim 40^{o}$ where the momentum distributions become accessible.
-As a result, our data at larger recoil angles
-%is statistically limited. \\
-%\indent For recoil angles at $\theta_{nq}=35^{o}$ and $45^{o}$ shown in Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)},  all models predict similar behaviour of the
-%momentum distribution for recoil momenta up to $p_{r}\sim$300 MeV/c which the data verifies. At larger $p_{r}$, however, the momentum distributions become increasingly sensitive to the different
-%NN potentials, mainly a difference between the CD-Bonn and either the Paris or AV18 is observed. \\
-%\indent In Fig.
-\hyperref[fig:fig1]{1(a)} for example, the data is clearly sensitive to the CD-Bonn momentum distributions between recoil momenta of $300\lesssim p_{r}\lesssim750$ MeV/c before transitioning
-%to the Paris/AV18 potentials which is a behaviour that is not well described by any of the models. For recoil angles in Fig. \hyperref[fig:fig1]{1(b)},
-%a similar behaviour can be observed, as the data is sensitive to the CD-Bonn momentum distributions but only up to $p_{r}\sim 580$ MeV/c as FSIs start to dominate at lower $p_{r}$ as opposed to Fig.
-\hyperref[fig:fig1]{1(a)}.
-%For $p_{r}>580$ MeV/c, the data again exhibits a behaviour at the high momentum tails which either the CD-Bonn, Paris or AV18 potentials are unable to describe.\\
+\indent For the recoil angles shown in Fig.
+\hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
+of the NN-potential which is well understood.
+Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
+\hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
+the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
+at higher missing momenta.
+At recoil angles $\theta_{nq}=75^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
+of extracting the momentum distributions at these angles. \\
 %---------------------------------------------------------------------------------------------------------------------

### 2020-01-03 MY_PUBLICATIONS/PRL/draft_v3/introduction.tex
updated draft 3

--- 2019-12-13 MY_PUBLICATIONS/PRL/draft_v2/introduction.tex
@@
 This cancellation results in only the PWIA term remaining in the deuteron cross section and is expected to occur at netron recoil angles $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
+Since at $\theta_{nq}\sim120^{o}$ ICs are not negligible, $x_{Bj}>1$ is required to suppress ICs which leaves $\theta_{nq}\sim40^{o}$ as the only choice where FSIs are reduced.
 \\
-\indent Previous deuteron electro-disintegration experiments performed at Jefferson Lab (JLab) have helped confirmed various of the abovementioned theoretical predictions as well as constrain and quantify the contributions from FSIs, MECs and ICs on
-the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).
-The first of these was performed in Hall A \cite{PhysRevLett.89.062301}
-at a relatively low momentum transfer of $Q^{2}=0.665$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r} = $ 550 MeV/c where it was shown that for $p_{r}>$ 300 MeV/c, FSIs, MECs and ICs dominate the cross section and
-had to be included in Arenh\"{o}vel's calculations \cite{PhysRevC.43.1022, PhysRevC.46.455, PhysRevC.52.1232, PhysRevC.55.2214} for a satisfactory agreement between theory and data. \\
-\indent The next experiment was performed in Hall B \cite{PhysRevLett.98.262502} using the CEBAF Large Acceptance Spectrometer (CLAS) which measured a wide variety of kinematic settings
-giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics. This was the first experiment to probe
-the deuteron at high momentum transfers ( 1.75 $\leq Q^{2}\leq$ 5.5 (GeV/c)$^{2}$) and presented angular distributions of cross-sections that exhibited a strong angular dependence of FSI with neutron recoil angles peaking
-at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}.
-The cross sections versus neutron recoil momenta up to $p_{r}\sim$2 GeV/c were also presented, however, statistical limitations made it necessary to integrate over a wide angular range making it impossible to control
-contributions from FSIs, MECs and ICs. \\
-\indent Finally, a third $^{2}H(e,e'p)n$ experiment was performed in Hall A \cite{PhysRevLett.107.262501} at $Q^{2} = 3.5\pm0.25$ (GeV/c)$^{2}$ and recoil momenta up to 550 MeV/c.
-The angular distributions of
-the cross-section ratio ($R = \sigma_{exp}/\sigma_{PWIA}$) presented saw agreement in shape with the angular distributions in Hall B\cite{PhysRevLett.98.262502} with FSI peaking at $\theta_{nq}\sim70^{o}$.
-With the increased statistics in Hall A, a direct comparison of the momentum distributions between data and theory could be made for specific $\theta_{nq}$ bins.
-For the first time, at $\theta_{nq}=35\pm5^{o}$ and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\
+%---------D(e,e'p) Experiments at Q2 < 1-------- 
+\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)\cite{sargsian_2015} have helped quantify the contributions from FSIs, MECs and ICs on
+the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).  At $p_{r}<300$ MeV/c, theoretical
+calculations by Arenhovel\cite{Arenhovel_1976} showed that FSIs, MECs and ICs contributions mutually cancel leaving the PWIA as the dominant contribution to the cross section which
+the data confirmed. Beyond $p_{r}\sim300$ MeV/c, however, the data showed that these processes do not mutually cancel and had to be included in the theory for a satisfactory agreement. \\
+\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
+experiments concluded that the cross-sections exhibited a strong angular dependence of FSI with neutron recoil angles peaking
+at $\theta_{nq} \sim 70^{o}$ which confirmed the onset of the GEA\cite{Sargsian_2001,PhysRevC.56.1124}. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured a wide variety
+of kinematic settings giving an overview of the $^{2}H(e,e'p)n$ reaction kinematics, however, statistical limitations made it necessary to integrate over a wide angular range making
+it impossible to control contributions from FSIs, MECs and ICs. \\
+\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the dependence of the cross section
+with recoil momenta up to $p_{r}=550$ MeV/c at a variety of neutron recoil angles ($\theta_{nq}$). For the first time, at $\theta_{nq}=35\pm5^{o}$
+and $45\pm5^{o}$, theoretical models showed a sensitivity to the NN-potential used in the deuteron wavefunction that was not obscured by FSI contributions to the cross section data.\\
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in Hall A\cite{PhysRevLett.107.262501} and extends the $^{2}H(e,e'p)n$ cross section measurements

### 2020-01-06 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated

@@
 %--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
+%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential.
+Above 300 MeV/c, corresponding to the medium and short
+% range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18.
+%no model describes the data over the entire range--the data has a different shape than any of the models."
+
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
@@
 \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
-the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
+the PWIA and are within good agreement up $p_{r}\sim750$ MeV/c, whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity on the momentum distribution to the different NN-potentials
 at higher missing momenta.
-At recoil angles $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
+At recoil angle $\theta_{nq}=75^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}], FSIs become dominant at $p_{r}>300$MeV/c and exhibit a similar behaviour among all models which obscures any possibility
 of extracting the momentum distributions at these angles. \\
+
+% Make a transition between plot 1 and plot 2 to indicate the reason why we take the ratio: Since the shape of the data does not fully agree with any of the models >300 MeV/c, a ratio is taken to
+% make sense out of the discrepancy obsevred, and try to understand why are the shapes different.
+More information can be obtained from a ratio plot, by comparing different calculations relative to the CD-Bonn.
+
 %---------------------------------------------------------------------------------------------------------------------
+
 %------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
-\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions (n$(p_{r})$) is shown in Fig.
+
+%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.
+Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.
+
+\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions ($\sigma^{\textrm{\small CD-Bonn PWIA}}_{red}$) is shown in Fig.
 \ref{fig:fig2}.
-As a reference we selected the
-deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
+As a reference we selected the deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
 \begin{figure}[h!]
 \includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
-\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
-The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided.
-}
+\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{\textrm{\small CD-Bonn PWIA}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
 \label{fig:fig2}
 \end{figure} \\
+\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Fig.
+\hyperref[fig:fig2]{2(a)-(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim580$ MeV/c, respectively.
+The data shows a larger sensitivity to the CD-Bonn deuteron momentum distributions at smaller neutron recoil angles ($\theta_{nq}=35^{o}$) which indicates this is the optimal kinematic setting to probe the deuteron
+wavefunction larger missing momenta.
+Furthermore, the agreement between the Halls A and C data solidifies the approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
+At larger recoil momenta where the ratio is $R>1$ and FSIs dominate the cross section models, the data is not well described by any of the models and exhibits a rise in the ratio which is not well understood.
+This hign missing momentum region is statistically limited and additional data would be required before any conclusions can be made. \\
 \indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for
-all theoretical calculations as compared to the reference.
-In this region, our experiment is statistically limited as we focused on kinematics at lower recoil angles where FSIs are small.
-The overlayed
-Hall A data, however, shows excellent agreement with the Paris FSI.
-For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
-data follows.
-The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
-the cross section. \\
-\indent For $\theta_{nq}=45^{o}$ [Fig.
-\hyperref[fig:fig2]{2(b)}] at $p_{r}<300$ MeV/c, all theoretical calculations agree with each other and are sensitive to the momentum distribution inside the deuteron which
-the data confirms. At $p_{r}\gtrsim300$ MeV/c, the Paris/AV18 calculations start to deviate from the CD-Bonn calculations, with the most substantial deviations observed at $p_{r}\sim 1$ GeV/c.
-The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
-The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\
-\indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig.
-\hyperref[fig:fig2]{2(a)}], where the CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c before being
-overwhelmed by FSIs, whereas the Paris/AV18 calculations start to deviate from the CD-Bonn at $p_{r}\sim300$ MeV/c.
-The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
-exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
-\indent The $\theta_{nq}=35^{o}$ [Fig.
-\hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
-distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\
+
 %-------------------------------------------------------------------------------------------------------------------------------

### 2020-01-07 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated

@@
 %--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
-%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential.
-Above 300 MeV/c, corresponding to the medium and short
-% range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18.
-%no model describes the data over the entire range--the data has a different shape than any of the models."
+%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
+%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
+%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."
 
@@
 for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
+
 \indent For the recoil angles shown in Fig.
-\hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
-of the NN-potential which is well understood.
-Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
-\hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
-the PWIA and are within good agreement up $p_{r}\sim750$ MeV/c, whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity on the momentum distribution to the different NN-potentials
-at higher missing momenta.
-At recoil angle $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}], FSIs become dominant at $p_{r}>300$MeV/c and exhibit a similar behaviour among all models which obscures any possibility
-of extracting the momentum distributions at these angles. \\
+\hyperref[fig:fig1]{1(a)-(c)}, at recoil momenta up to $p_{r}\sim$300 MeV/c the cross sections are dominated by the PWIA and within agreement between all models.
+The agreement at $p_{r}<300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and commonly
+used by high-quality potentials. Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
+AV18 models significantly differs from the CD-Bonn.
+The Paris/AV18 are dominated by the PWIA and within good agreement of each other up $p_{r}\sim750$ MeV/c, while the CD-Bonn exhibits a completely different
+behaviour where the cross sections are smaller and dominated by the PWIA up to $p_{r}\sim800$ MeV/c for $theta_{nq}=35^{o}$\hyperref[fig:fig1]{1(a)}] and $p_{r}\sim580$ MeV/c for $\theta_{nq}=45^{o}$\hyperref[fig:fig1]{1(a)}].\\
+The difference between the CD-Bonn and Paris/AV18
 

### 2020-01-08 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated draft 3

--- 2020-01-03 MY_PUBLICATIONS/PRL/draft_v3/body.tex
@@
 section averaged over the kinematic bin. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.\\
-\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross 
+\indent  Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data set independently
+and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
 \onecolumngrid
@@
 \begin{figure}[hb!]
-\includegraphics[scale=0.46]{../prl_plots/PRL_plot1.pdf}
+\includegraphics[scale=0.5]{../prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
@@
 \twocolumngrid 
-\noindent sections for each data set independently and were averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
 \begin{equation}
@@
 %--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
+%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
+%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
+%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
@@
 for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
-\indent For the recoil angles shown in Fig.
-\hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
-of the NN-potential which is well understood.
-Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
-\hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
-the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
-at higher missing momenta.
-At recoil angles $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
-of extracting the momentum distributions at these angles. \\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are dominated by the PWIA and in agreement between all models.
+The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and commonly
+used by modern potentials. \\
+\indent Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
+AV18 models significantly differ from the CD-Bonn.
+In this region, the Paris/AV18 are dominated by the PWIA and within good agreement of each other up $p_{r}\sim700$ MeV/c, while the CD-Bonn exhibits a completely different
+behaviour where the cross sections are smaller and dominated by the PWIA up to $p_{r}\sim800$ MeV/c for $\theta_{nq}=35^{o}$ [Fig.
+\hyperref[fig:fig1]{1(a)}] and $p_{r}\sim580$ MeV/c for $\theta_{nq}=45^{o}$ [Fig.
+\hyperref[fig:fig1]{1(b)}].
+The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
+to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\indent At $\theta_{nq}=75^{o}$ [Fig.
+\hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSIs become the dominant contributions to the cross sections for all models which exhibit a similar behaviour (smaller falloff)
+that overshadows any possibility of extracting the momentum distributions. \\
 %---------------------------------------------------------------------------------------------------------------------
 %------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
-\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions (n$(p_{r})$) is shown in Fig.
+%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.
+Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.
+\indent To quantify the discrepancy observed between data and theory in Fig.
+\ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions ($\sigma^{\text{CD-Bonn PWIA}}_{red}$) is shown in Fig.
 \ref{fig:fig2}.
-As a reference we selected the
-deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
+As a reference we selected the deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
 \begin{figure}[h!]
 \includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
-\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
-The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided.
-}
+\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{{\text{CD-Bonn PWIA}}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
 \label{fig:fig2}
 \end{figure} \\
-\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for
-all theoretical calculations as compared to the reference.
-In this region, our experiment is statistically limited as we focused on kinematics at lower recoil angles where FSIs are small.
-The overlayed
-Hall A data, however, shows excellent agreement with the Paris FSI.
-For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
-data follows.
-The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
-the cross section. \\
-\indent For $\theta_{nq}=45^{o}$ [Fig.
-\hyperref[fig:fig2]{2(b)}] at $p_{r}<300$ MeV/c, all theoretical calculations agree with each other and are sensitive to the momentum distribution inside the deuteron which
-the data confirms. At $p_{r}\gtrsim300$ MeV/c, the Paris/AV18 calculations start to deviate from the CD-Bonn calculations, with the most substantial deviations observed at $p_{r}\sim 1$ GeV/c.
-The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
-The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\
-\indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig.
-\hyperref[fig:fig2]{2(a)}], where the CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c before being
-overwhelmed by FSIs, whereas the Paris/AV18 calculations start to deviate from the CD-Bonn at $p_{r}\sim300$ MeV/c.
-The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
-exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
-\indent The $\theta_{nq}=35^{o}$ [Fig.
-\hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
-distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\
+\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
+\hyperref[fig:fig2]{2(a),(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim580$ MeV/c, respectively.
+Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
+At larger recoil momenta where the ratio is $R>1$, FSIs dominate the cross section models and the data is not well described by any of the models. This behaviour of the data is not well understood
+and additional data on this statistically limited region would be required before any conclusions can be made. \\
+\indent At $\theta_{nq}=75^{o}$ [Fig.
+\hyperref[fig:fig2]{2(c)}], the FSIs are small below $p_{r}\sim$300 MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
+At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles.
+The Hall A data, however, shows a reasonable agreement with the FSIs from all models which gives us confidence in our understanding
+of FSIs at the smaller recoil angles.
+This opens a question on whether there might be additional effects needed in the CD-Bonn model that would account for the discrepancy between data and CD-Bonn FSI at smaller angles.
+\\
 %-------------------------------------------------------------------------------------------------------------------------------
@@
 unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
-The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
-were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
-up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\
+The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn model was found to be
+significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
+At higher missing momentum, however, all models were unable to describe the data. In addition, at these large momentum settings statistical limitations were encountered as well.\\
 \indent Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,

### 2020-01-08 MY_PUBLICATIONS/PRL/draft_v3/introduction.tex
updated draft 3

@@
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
-\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)\cite{sargsian_2015} have helped quantify the contributions from FSIs, MECs and ICs on
+\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref.
+\cite{sargsian_2015}] have helped quantify the contributions from FSIs, MECs and ICs on
 the $^{2}H(e,e'p)n$ cross-section to determine the kinematics at which they are either suppressed (MECs and ICs) or under control (FSIs).  At $p_{r}<300$ MeV/c, theoretical

### 2020-02-04 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/body.tex
updated

%This experiment was part of a group of four experiments that commissioned the new Hall C Super High Momentum Spectrometer (SHMS) as part of the 12 GeV upgrade at JLab.
A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
by the new Super High Momentum Spectrometer (SHMS) and the High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The missing momentum is defined as 
$\vec{p_{r}} = \vec{q} - \vec{p_{f}}$ and the missing  energy as $E_{m} = \omega - T_{p} - T_{r}$ where $\vec{p_{f}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{r})$ are the
final proton and neutron kinetic energies respectively.
The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).

Both  Hall spectrometers C have similar standard detector packages, each with four scintillator planes\cite{hodo_techreport} used for triggering, a pair of drift chambers\cite{dc_techreport} used for tracking, a calorimeter\cite{Mkrtchyan_2013} used for $e^{-}/\pi^{-}$ discrimination and a gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used to improve  for $e^{-}/\pi^{-}$ separation.
Due to the absence of significant background on this experiment and the low coincidence trigger rates
($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) measures was found to have little to no effect on the final cross section.

We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
the lower and higher missing momentum settings, respectively. At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$)
measured on this experiment. As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.

Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
simulation program, SIMC. Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 
momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}.

Identical event selection criteria were used for the hydrogen and deuteron data. The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
is well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a missing
energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the
SHMS calorimeter to select electrons and not other sources of background, mostly pions and a cut on the reconstructed HMS and SHMS reaction vertices to select events that 
originated from the same reaction vertex at the target.

The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS),
total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}.

For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only). For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).
The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist.

The systematic uncertainties of the measured cross sections were determined from 
normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
Determination of systematics on these quantities is a work in progress. (Private communication with D. Mack)} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
for an overall normalization uncertainty added in quadrature of $3.7 \%$.

The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
of different data sets. For $\theta_{nq}=$ 35, 45 and 75 deg (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
to the statistical uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section.

The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged over the kinematic bin. The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.

Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

\begin{equation}
\sigma_{red} \equiv \frac{\sigma_{exp(th)}}{Kf_{rec}\sigma_{cc1}}
\label{eq:1}
\end{equation}

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor  and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. 
%--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."

Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$
(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data are compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.

\begin{center}
\begin{figure*}[htp!]
\includegraphics[scale=0.5]{./prl_plots/PRL_plot1.pdf}
\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
AV18(green) and CD-Bonn(magenta) NN potentials}
\label{fig:fig1}
\end{figure*}
\end{center}

For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are well reproduced  by  all models when FSI are included. The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and common to all modern potentials.

Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
AV18 models significantly differ from the CD-Bonn. In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{r}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{r}\sim800$ MeV/c [Fig. \hyperref[fig:fig1]{1(a)}]  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c [Fig. \hyperref[fig:fig1]{1(b)}].
The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.

At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSIs become the dominant contributions to the cross sections for all models which exhibit a similar behaviour (smaller falloff) 
that overshadows any possibility of extracting the momentum distributions.

%---------------------------------------------------------------------------------------------------------------------
%------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.  Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.
To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}.

\begin{figure}[h!]
\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{{\text{CD-Bonn PWIA}}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
\label{fig:fig2}
\end{figure}

For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively.
Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
At larger recoil momenta where the ratio is $R>1$ and increasing.  At $\theta_{nq}=35^{o}$ FSI start to dominate for missing moment above typically above 800 MeV/c for the CD-Bonn calculation while the other models predict still relatively small FSI below 900 MeV/c. At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c.

Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small (<30\%).  This behavior of the data is new and 
and additional data in this kinematic region are necessary to improve the statistics.

At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], FSI are small below $p_{r}\sim150$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSIs from all models which gives us confidence in our understanding
of FSIs at the smaller recoil angles.

%-------------------------------------------------------------------------------------------------------------------------------
%----------CONCLUSION----------
This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn model was found to be
significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
At higher missing momentum, however, all models were unable to describe the data. In addition, at these large momentum settings statistical limitations were encountered as well.

Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed.

We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.

%-------------------------------

### 2020-02-04 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
updated

The deuteron is the only bound two-nucleon  system and serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently
not well understood. At such small internucleon distances the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
nucleons begin to overlap. 
%The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
Short-range studies of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom is still valid before
having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.

The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the plane wave impulse approximation (PWIA), the virtual photon couples to
the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron). The neutron carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.

In reality, the ejected nucleon undergoes final state interactions (FSI) corresponding to subsequent interactions with the recoiling system. Another possibility is that the
photon couples to the virtual meson being exchanged between nucleons (meson exchange currents), or that the photon excites a bound nucleon into a resonance state which subsequently
decays back into its ground state (isobar configurations).  FSI, meson exchange currents (MEC) and isobar configurations (IC)  can significantly alter the recoiling neutron
momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution.

Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ (GeV/c)$^{2}$ and
$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}. IC can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
electro-production threshold.

At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles. GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$. 
%The most important prediction from GEA, however, is that at large recoil momenta $p_{r}$ where FSIs are expected to be large, there is an approximate cancellation of the PWIA/FSI interference (screening term) with the modulus-squared of the FSI amplitude (rescattering term). 
This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ and, equivalently,  $\theta_{nq}\sim40^{o}$ is the preferred choice to suppress IC as well as FSI. \\
%---------D(e,e'p) Experiments at Q2 < 1-------- 
\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref. \cite{sargsian_2015}] have helped quantify the contributions from FSI, MEC and IC on
the $^{2}H(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  
%At $p_{r}<300$ MeV/c, and very low momentum transfers, theoretical
%calculations by Arenhovel\cite{Arenhovel_1976} showed that FSI, MEC and IC contributions mutually cancel leaving the PWIA as the dominant contribution to the cross section which
%the data confirmed. Beyond $p_{r}\sim300$ MeV/c, however, the data showed that these processes do not mutually cancel and had to be included in the theory for a satisfactory agreement. \\

The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles peaking
at $\theta_{nq} \sim 70^{o}$ in agreement with GEA\cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular distributions for  a range of $Q^2$ values as well as momentum distributions. However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c

In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{r}=550$ MeV/c. For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$
and $45\pm5^{o}$ compared to  $\theta_{nq}=75\pm5^{o}$. Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{o}$) compared to FSI dominance at $\theta_{nq}=75^{o}$\cite{PhysRevLett.107.262501}.

The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}H(e,e'p)n$ cross section measurements
to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.18 GeV/c. At the selected kinematic settings, MEC and IC are suppressed and FSI are under control for neutron recoil angles between 35 and 45 degrees giving access to high momentum components of the deuteron wave function.

### 2020-02-05 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/body.tex
updated

@@
-%This experiment was part of a group of four experiments that commissioned the new Hall C Super High Momentum Spectrometer (SHMS) as part of the 12 GeV upgrade at JLab.
-A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
+\indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
 by the new Super High Momentum Spectrometer (SHMS) and the High Momentum Spectrometer (HMS), respectively.
@@
 final proton and neutron kinetic energies respectively.
-The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).
-
-Both  Hall spectrometers C have similar standard detector packages, each with four scintillator planes\cite{hodo_techreport} used for triggering, a pair of drift chambers\cite{dc_techreport} used for tracking, a calorimeter\cite{Mkrtchyan_2013} used for $e^{-}/\pi^{-}$ discrimination and a gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used to improve  for $e^{-}/\pi^{-}$ separation.
-Due to the absence of significant background on this experiment and the low coincidence trigger rates
-($\sim 1-3$ Hz) at the higher missing momentum settings, the use of additional particle identification (PID) measures was found to have little to no effect on the final cross section.
-
-We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
+The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\
+\indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes\cite{hodo_techreport} used for triggering, a pair of drift chambers\cite{dc_techreport} used for tracking, and a calorimeter\cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
+The trigger setup for this experiment required a minimum of 3/4 hodoscope planes for data readout in each spectrometer. Due to the absence of significant background and the negligible
+accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) measures was found to have little to no effect on the final cross section.\\
+\indent We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
 At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
@@
 As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
-At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.
-
-Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
+At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
+\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
 Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
-momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}.
-
-Identical event selection criteria were used for the hydrogen and deuteron data.
+momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}.\\
+\indent Identical event selection criteria were used for the hydrogen and deuteron data.
 The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
@@
 energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the
-SHMS calorimeter to select electrons and not other sources of background, mostly pions and a cut on the reconstructed HMS and SHMS reaction vertices to select events that 
-originated from the same reaction vertex at the target.
-
-The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies.
-For $^{2}H(e,e'p)n$ the corrections were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS),
-total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}.
-
-For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
+SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions) and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
+originated from the same reaction vertex at the target.\\
+\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections
+were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and
+target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}. The values in parentheses were averaged over all data sets. \\
+\indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
+Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
 model.
@@
 \ref{fig:fig1}).
-The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist.
-
-The systematic uncertainties of the measured cross sections were determined from 
+The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist. \\
+\indent The systematic uncertainties of the measured cross sections were determined from 
 normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
@@
 contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
-for an overall normalization uncertainty added in quadrature of $3.7 \%$.
-
-The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
-of different data sets. For $\theta_{nq}=$ 35, 45 and 75 deg (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
+for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
+\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
+of different data sets. For $\theta_{nq}= 35^{o}, 45^{o} and 75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
-to the statistical uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section.
-
-The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
+to the statistical uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
+\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
 The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
 For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
-$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged over the kinematic bin.
-The calculations were based on the Laget model including FSI\cite{LAGET2005, PhysRevC.21.861}.
-
-Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged for overlapping bins in $p_{r}$.
-The reduced cross sections are defined as follows:
-
+$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
+over the kinematic bin.\\
+\indent Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged
+for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
 \begin{equation}
@@
 \end{equation}
-
 where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor  and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
-Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. 
-%--------------------------------------EXPLANATION  OF 1ST PLOT (MOMENTUM DISTRIBUTIONS)----------------------------------------
-%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
-%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
-%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."
-
-Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$
-(GeV/c)$^{2}$.
-The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
-The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials.
-The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.
-
+Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. \\
+\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
+$p_{r}$ for three recoil angle settings at
+\onecolumngrid
 \begin{center}
-\begin{figure*}[htp!]
-\includegraphics[scale=0.5]{./prl_plots/PRL_plot1.pdf}
+\begin{figure}[hb!]
+\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
@@
 \label{fig:fig1}
-\end{figure*}
+\end{figure}
 \end{center}
-
-For all recoil angles shown in Fig.
-\hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are well reproduced  by  all models when FSI are included.
-The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and common to all modern potentials.
-
-Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
+\twocolumngrid
+\noindent $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
+The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
+The data are compared to theoretical reduced
+cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials.
+The theoretical calculations
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.\\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are well reproduced  by  all models when FSI are included.
+The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+is well known and common to all modern potentials. \\
+\indent Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
 AV18 models significantly differ from the CD-Bonn.
@@
 The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
-to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.
-
-At $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSIs become the dominant contributions to the cross sections for all models which exhibit a similar behaviour (smaller falloff)
-that overshadows any possibility of extracting the momentum distributions.
-
-%---------------------------------------------------------------------------------------------------------------------
-%------------The Ratio plot should be shown and explained ONLY after the momentum distribution plot has been shown.--------------
-%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.
-Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.
-To quantify the discrepancy observed between data and theory in Fig.
-\ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig.
-\ref{fig:fig2}.
-
+to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
+behaviour (smaller falloff) that overshadows any possibility of extracting the momentum distributions.\\
+\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the
+deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}.
 \begin{figure}[h!]
@@
 \end{figure}
-
-For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
-\hyperref[fig:fig2]{2(a),(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively.
-Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
-At larger recoil momenta where the ratio is $R>1$ and increasing.
-At $\theta_{nq}=35^{o}$ FSI start to dominate for missing moment above typically above 800 MeV/c for the CD-Bonn calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c.
-
-Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small (<30\%).
+\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
+\hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively.
+Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSI are reduced.
+At larger recoil momenta where the ratio is $R>1$ and increasing.  At $\theta_{nq}=35^{o}$ FSI start to dominate for missing moment above typically above 800 MeV/c for the CD-Bonn calculation
+while the other models predict still relatively small FSI below 900 MeV/c. At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based
+calculation above 600 MeV/c. \\
+\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small (<30\%).
 This behavior of the data is new and
-and additional data in this kinematic region are necessary to improve the statistics.
-
-At $\theta_{nq}=75^{o}$ [Fig.
+and additional data in this kinematic region are necessary to improve the statistics. \\
+\indent At $\theta_{nq}=75^{o}$ [Fig.
 \hyperref[fig:fig2]{2(c)}], FSI are small below $p_{r}\sim150$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
 At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles.
-The Hall A data, however, shows a reasonable agreement with the FSIs from all models which gives us confidence in our understanding
-of FSIs at the smaller recoil angles.
-
-%-------------------------------------------------------------------------------------------------------------------------------
-%----------CONCLUSION----------
-This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
-unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
-The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn model was found to be
-significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
-At higher missing momentum, however, all models were unable to describe the data. In addition, at these large momentum settings statistical limitations were encountered as well.
-
-Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
-additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
-in order to make any definitive arguments about the underlying physics observed.
-
-We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
+of FSI at the smaller recoil angles. \\
+\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+very high neutron recoil momenta at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
+short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
+Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
+At higher missing momentum, however, all models were unable to describe the data. \\
+\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
 as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed

### 2020-02-05 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
updated

@@
 nucleons begin to overlap. 
-%The overlap is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
 This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
@@
 having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
-which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-
-The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
+which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
+\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
 electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the plane wave impulse approximation (PWIA), the virtual photon couples to
@@
 to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
-
 In reality, the ejected nucleon undergoes final state interactions (FSI) corresponding to subsequent interactions with the recoiling system. Another possibility is that the
@@
 decays back into its ground state (isobar configurations).  FSI, meson exchange currents (MEC) and isobar configurations (IC)  can significantly alter the recoiling neutron
-momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution.
-
-Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
+momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
+\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
 The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ (GeV/c)$^{2}$ and
@@
 IC can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
-electro-production threshold.
-
-At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles.
+electro-production threshold.\\
+\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref. \cite{sargsian_2015}] have helped quantify the contributions
+from FSI, MEC and IC on the $^{2}H(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
 GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$.
-%The most important prediction from GEA, however, is that at large recoil momenta $p_{r}$ where FSIs are expected to be large, there is an approximate cancellation of the PWIA/FSI interference (screening term) with the modulus-squared of the FSI amplitude (rescattering term).
 This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
@@
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
-\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref.
-\cite{sargsian_2015}] have helped quantify the contributions from FSI, MEC and IC on
-the $^{2}H(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  
-%At $p_{r}<300$ MeV/c, and very low momentum transfers, theoretical
-%calculations by Arenhovel\cite{Arenhovel_1976} showed that FSI, MEC and IC contributions mutually cancel leaving the PWIA as the dominant contribution to the cross section which
-%the data confirmed. Beyond $p_{r}\sim300$ MeV/c, however, the data showed that these processes do not mutually cancel and had to be included in the theory for a satisfactory agreement. \\
-
-The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
+\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
 experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles peaking
-at $\theta_{nq} \sim 70^{o}$ in agreement with GEA\cite{Sargsian_2001,PhysRevC.56.1124} calculations.
-In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular distributions for  a range of $Q^2$ values as well as momentum distributions.
-However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c
-
-In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{r}=550$ MeV/c.
+at $\theta_{nq} \sim 70^{o}$ in agreement with GEA\cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
+distributions for  a range of $Q^2$ values as well as momentum distributions.
+However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions
+which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c. \\
+\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{r}=550$ MeV/c.
 For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$
-and $45\pm5^{o}$ compared to  $\theta_{nq}=75\pm5^{o}$.
-Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{o}$) compared to FSI dominance at $\theta_{nq}=75^{o}$\cite{PhysRevLett.107.262501}.
-
-The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}H(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.18 GeV/c.
-At the selected kinematic settings, MEC and IC are suppressed and FSI are under control for neutron recoil angles between 35 and 45 degrees giving access to high momentum components of the deuteron wave function.
+and $45\pm5^{o}$ compared to  $\theta_{nq}=75\pm5^{o}$. Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{o}$) compared to FSI
+dominance at $\theta_{nq}=75^{o}$\cite{PhysRevLett.107.262501}. \\
+\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}H(e,e'p)n$ cross section measurements
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.01 GeV/c. At the selected kinematic settings with neutron recoil angles between $35^{o}$ and $45^{o}$, MEC and IC are
+suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

### 2020-02-05 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/prl.tex
updated

--- 2019-12-19 MY_PUBLICATIONS/PRL/draft_v2/prl.tex
@@
 \hyphenation{PYTHIA}
+%
 
@@
 \widetext
-\leftline{Version 02 as of \today}
+\leftline{Version 03 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
 
-\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}}
+\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
 \input author_list.tex       % D0 authors (remove the first 3 lines
@@
   New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.18 GeV/c. The data have been obtained at fixed neutron recoil angles
-($\theta_{nq}$) of 35$^\circ$ and 45$^\circ$  with respect to the 3-momentum
-transfer, $\vec q$. At these kinematic settings final state interactions (FSIs),
-meson exchange currents (MECs) and isobar configurations (ICs) are expected to 
+  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
+$\theta_{nq} = 35^\circ$ and $45^\circ$  with respect to the 3-momentum
+transfer, $\vec q$. At these kinematic settings final state interactions (FSI),
+meson exchange currents (MEC) and isobar configurations (IC) are expected to 
 be suppressed and the plane wave impulse approximation (PWIA) provides the

### 2020-02-06 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/body.tex
updated

@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes\cite{hodo_techreport} used for triggering, a pair of drift chambers\cite{dc_techreport} used for tracking, and a calorimeter\cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-The trigger setup for this experiment required a minimum of 3/4 hodoscope planes for data readout in each spectrometer. Due to the absence of significant background and the negligible
-accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) measures was found to have little to no effect on the final cross section.\\
+The trigger setup for this experiment required a minimum of 3/4 hodoscope planes to detect a signal for data readout in each spectrometer. Due to the absence of significant background and the low
+accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\
 \indent We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
@@
 At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
-\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}$=80 MeV setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
+\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
 Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
-momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_specKinUnc,cyero_SHMSOptics}.\\
+momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_phdthesis}.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
@@
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections
-were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_pAbs} and
-target boiling factors ($4.2 \%$)\cite{cyero_tgtBoil}. The values in parentheses were averaged over all data sets. \\
+were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_phdthesis} and
+target boiling factors ($4.2 \%$)\cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\
 \indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
@@
 \indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
-of different data sets. For $\theta_{nq}= 35^{o}, 45^{o} and 75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
+of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
-to the statistical uncertainty(25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
+to the statistical uncertainty (25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
@@
 for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq$300 MeV/c the cross sections are well reproduced  by  all models when FSI are included.
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
 The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
+\indent Beyond $p_{r}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
 AV18 models significantly differ from the CD-Bonn.
@@
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the
-deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}.
-\begin{figure}[h!]
+deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
+\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
+to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
+region where recoil angles are small and FSI are reduced. \\
+\indent At larger recoil momenta where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{o}$ FSI start to dominate for
+missing momenta typically above 800 MeV/c for the CD-Bonn
+\begin{figure}[t!]
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
@@
 \end{figure}
-\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs.
-\hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively.
-Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic region where recoil angles are small and FSI are reduced.
-At larger recoil momenta where the ratio is $R>1$ and increasing.  At $\theta_{nq}=35^{o}$ FSI start to dominate for missing moment above typically above 800 MeV/c for the CD-Bonn calculation
-while the other models predict still relatively small FSI below 900 MeV/c. At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based
-calculation above 600 MeV/c. \\
-\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small (<30\%).
-This behavior of the data is new and
+calculation while the other models predict still relatively small FSI below 900 MeV/c.
+At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
+\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
+This behavior of the data is new
 and additional data in this kinematic region are necessary to improve the statistics. \\

### 2020-02-06 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
updated

@@
 This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
-Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ and, equivalently,  $\theta_{nq}\sim40^{o}$ is the preferred choice to suppress IC as well as FSI.
+Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI.
 \\

### 2020-02-07 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
updated

@@
 Short-range studies of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom is still valid before
-having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{pr01-020}. As of the present time, there are only a few nuclear physics experiments for
+having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{sargsian_2015}.
+As of the present time, there are only a few nuclear physics experiments for
 which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
@@
 \indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
-The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ (GeV/c)$^{2}$ and
+The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ GeV/c$^{2}$ and
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}.
@@
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
-\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.89.062301} and B\cite{PhysRevLett.98.262502}. Both
+\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both
 experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles peaking

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

--- 2020-02-06 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/body.tex
@@
 The missing momentum is defined as
-$\vec{p_{r}} = \vec{q} - \vec{p_{f}}$ and the missing  energy as $E_{m} = \omega - T_{p} - T_{r}$ where $\vec{p_{f}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{r})$ are the
+$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the missing  energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
 final proton and neutron kinetic energies respectively.
@@
 accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\
-\indent We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c.
+\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80,580$ and $750$ MeV/c.
 At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
 the lower and higher missing momentum settings, respectively.
-At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$)
+At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{\mathrm{r}}$)
 measured on this experiment.
@@
 At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
-\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
+\indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
-Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
+Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_phdthesis}.\\
@@
 is well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a missing
-energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the
+energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions) and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
 originated from the same reaction vertex at the target.\\
-\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections
+\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$ the corrections
 were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_phdthesis} and
 target boiling factors ($4.2 \%$)\cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\
-\indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
+\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
 Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).
-For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig.
+For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig.
 \ref{fig:fig1}).
@@
 for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
-\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
-of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
+\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each data set independently, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins
+of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\leq1.01$ GeV/c.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
 to the statistical uncertainty (25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
-\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
+\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
 The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
-For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
-$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
+For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
+$f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
 over the kinematic bin.\\
 \indent Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged
-for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:
+for overlapping bins in $p_{\mathrm{r}}$. The reduced cross sections are defined as follows:
 \begin{equation}
-\sigma_{red} \equiv \frac{\sigma_{exp(th)}}{Kf_{rec}\sigma_{cc1}}
+\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}}
 \label{eq:1}
 \end{equation}
-where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor  and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
-Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. \\
+where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor  and $\sigma_{\mathrm{cc1}}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
+Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
-$p_{r}$ for three recoil angle settings at
+$p_{\mathrm{r}}$ for three recoil angle settings at
 \onecolumngrid
@@
 \includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
+\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
 with a bin width of $\pm 5^{o}$.
@@
 for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
-The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
+The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{r}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
+\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
 AV18 models significantly differ from the CD-Bonn.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{r}\sim700$ MeV/c.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{\mathrm{r}}\sim700$ MeV/c.
 The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
-In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{r}\sim800$ MeV/c [Fig.
-\hyperref[fig:fig1]{1(a)}]  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c [Fig.
-\hyperref[fig:fig1]{1(b)}].
+In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
+\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c (Fig.
+\hyperref[fig:fig1]{1(b)}).
 The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
 to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
-\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
+\indent At $\theta_{nq}=75^{o}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
 behaviour (smaller falloff) that overshadows any possibility of extracting the momentum distributions.\\
-\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the
-deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
-\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
-to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
+\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
+deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{\mathrm{red}}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
+\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}) the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
+to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\
@@
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
-\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{{\text{CD-Bonn PWIA}}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+\caption{The ratio $R(p_{\mathrm{r}}$) = $\sigma_{\mathrm{red}}/\sigma^{{\text{CD-Bonn PWIA}}}_{\mathrm{red}}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
 The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
@@
 and additional data in this kinematic region are necessary to improve the statistics. \\
-\indent At $\theta_{nq}=75^{o}$ [Fig.
-\hyperref[fig:fig2]{2(c)}], FSI are small below $p_{r}\sim150$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
-At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles.
+\indent At $\theta_{nq}=75^{o}$ (Fig.
+\hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
+At $p_{\mathrm{r}}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles.
 The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
 of FSI at the smaller recoil angles. \\
-\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
+\indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
 very high neutron recoil momenta at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
 short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
-Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.
+Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
 At higher missing momentum, however, all models were unable to describe the data. \\
@@
 as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade making all four commissioning experiments possible.
+to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
+was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+under grant No. D2-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
+under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.
 

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

--- 2020-02-07 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/introduction.tex
@@
 \indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the plane wave impulse approximation (PWIA), the virtual photon couples to
+electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA, the virtual photon couples to
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
 The neutron carries a momentum equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
-In reality, the ejected nucleon undergoes final state interactions (FSI) corresponding to subsequent interactions with the recoiling system. Another possibility is that the
-photon couples to the virtual meson being exchanged between nucleons (meson exchange currents), or that the photon excites a bound nucleon into a resonance state which subsequently
-decays back into its ground state (isobar configurations).  FSI, meson exchange currents (MEC) and isobar configurations (IC)  can significantly alter the recoiling neutron
+to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
+In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
+photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state which subsequently
+decays back into its ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
-\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
-The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ GeV/c$^{2}$ and
+\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
+The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}.
-IC can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
+IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
 electro-production threshold.\\
-\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref. \cite{sargsian_2015}] have helped quantify the contributions
-from FSI, MEC and IC on the $^{2}H(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions
+from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
 \indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
@@
 This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
-Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI.
+Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{\mathrm{Bj}}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI.
 \\
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
-\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both
+\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both
 experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles peaking
@@
 which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c. \\
-\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{r}=550$ MeV/c.
+\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c.
 For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$
@@
 dominance at $\theta_{nq}=75^{o}$\cite{PhysRevLett.107.262501}. \\
-\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}H(e,e'p)n$ cross section measurements
+\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
 to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.01 GeV/c. At the selected kinematic settings with neutron recoil angles between $35^{o}$ and $45^{o}$, MEC and IC are

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

--- 2020-02-05 MY_PUBLICATIONS/PRL/prl_files_WBCorrections/prl.tex
@@
 \leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
+\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
 \centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
 \begin{abstract}
-  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
+  New $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+  reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
 $\theta_{nq} = 35^\circ$ and $45^\circ$  with respect to the 3-momentum
-transfer, $\vec q$. At these kinematic settings final state interactions (FSI),
+transfer $\vec q$. At these kinematic settings final state interactions (FSI),
 meson exchange currents (MEC) and isobar configurations (IC) are expected to 

### 2020-02-12 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/author_listv2.tex
updated

\author{C.~Yero$^{1}$}
\author{W.U.~Boeglin$^{1}$}
\author{M.K.~Jones$^{2}$}

\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
\affiliation{$^{2}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\collaboration{for the Hall C Collaboration}
\noaffiliation

### 2020-02-12 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/author_listv2.tex
updated

@@
-\author{C.~Yero$^{1}$}
-\author{W.U.~Boeglin$^{1}$}
-\author{M.K.~Jones$^{2}$}
+%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
+%Comment / Uncomment accordingly
+\author{C.~Yero$^{1}$}       %Main author for E12-10-003 experiment
+\author{D.~Abrams}           %Commissioning ONLY
+\author{Z.~Ahmed}            %Commissioning ONLY
+\author{B.~Aljawrneh}        %Commissioning ONLY
+\author{S.~Alsalmi}          %Commissioning ONLY
+\author{R.~Ambrose}          %Commissioning + SIDIS
+%\author{D.~Androic}         %Color Transparency ONLY
+\author{W.~Armstrong}        %Commissioning ONLY
+\author{A.~Asaturyan}        %Commissioning ONLY
+\author{K.~Assumin-Gyimah}   %Commissioning ONLY
+\author{A.~Bandari}          %Commissioning + SIDIS
+\author{J.~Bane}             %Deuteron Experiment ONLY
+\author{S.~Basnet}           %Commissioning + SIDIS
+\author{V.~Berdnikov}        %Commissioning + SIDIS
+\author{H.~Bhatt}            %Commissioning + SIDIS
+\author{D.~Bhetuwal}         %Commissioning + SIDIS
+\author{D.~Biswas}           %Commissioning + SIDIS
+\author{W.~Boeglin}          %Commissioning ONLY (Deuteron Spokesperson)
+\author{P.~Bosted}           %Commissioning ONLY (SIDIS Spokesperson)
+\author{E.~Brash}            %Commissioning ONLY
+\author{M.~Bukhari}          %Commissioning ONLY
+%\author{M.~Carmignotto}     %NO MINIMUM SHIFTS
+\author{H.~Chen}             %Commissioning ONLY
+\author{J.P.~Chen}           %Commissioning ONLY
+\author{M.~Chen}             %Commissioning ONLY
+\author{E.~Christy}          %Commissioning ONLY
+\author{S.C.~Dusa}           %Commissioning + SIDIS               
+\author{K.~Craycraft}        %Commissioning + SIDIS
+%\author{S.~Danagoulian}     %NO MINIMUM SHIFTS
+%\author{D.~Day}             %ONLY DEC. 2017 Spec. Commissioning ?????? (should be included?)
+\author{M.~Diefenthaler}     %Commissioning + SIDIS
+\author{M.~Dlamini}          %Commissioning ONLY
+\author{J.~Dunne}            %Commissioning ONLY
+\author{B.~Duran}            %Commissioning + SIDIS
+\author{D.~Dutta}            %Commissioning + SIDIS  (CT Spokesperson)
+\author{R.~Ent}              %NO MINIMUM SHIFTS JLab Physics Division Leader (SIDIS Co-Spokesperson) (should be included)??????
+\author{R.~Evans}            %Commissioning ONLY
+\author{H.~Fenker}           %Commissioning + SIDIS
+%\author{I.~Fernando}        %NO MINIMUM SHIFTS
+\author{N.~Fomin}            %Commissioning ONLY
+\author{E.~Fuchey}           %Commissioning ONLY
+\author{D.~Gaskell}          %Commissioning + SIDIS
+\author{T.N.~Gautam}         %Commissioning ONLY
+\author{C.A.~Gayoso}         %Commissioning + SIDIS
+\author{F.A.~Gonzalez}       %Commissioning + SIDIS
+\author{O.~Hansen}           %Commissioning ONLY
+\author{F.~Hauenstein}       %Commissioning ONLY
+\author{T.~Horn}             %Commissioning ONLY
+\author{G.~Huber}            %Commissioning ONLY
+\author{M.K.~Jones}          %Commissioning + SIDIS
+\author{S.~Joosten}          %Commissioning ONLY
+\author{M.L.~Kabir}          %Commissioning + SIDIS           
+%\author{N.~Kalantarians}    %NO MINIMUM SHIFTS
+\author{A.~Karki}            %Commissioning + SIDIS  
+\author{C.~Keppel}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
+\author{A.~Khanal}           %Commissioning ONLY
+\author{P.~King}             %Commissioning ONLY
+\author{E.~Kinney}           %Commissioning ONLY (SIDIS Co-Spokesperson)
+%\author{H.S.~Ko}            %Color Transparency ONLY
+%\author{M.~Khol}            %NO MINIMUM SHIFTS
+\author{N.~Lashley-Colthirst}      %Commissioning ONLY
+\author{S.~Li}               %Commissioning ONLY
+\author{W.~Li}               %Commissioning ONLY
+\author{A.H.~Liyanage}       %Commissioning + SIDIS
+\author{D.~Mack}             %Commissioning + SIDIS
+\author{S.~Malace}           %Commissioning + SIDIS (F2 Spokesperson)
+%\author{P.~Markowitz}       %NO MINIMUM SHIFTS
+\author{J.~Matter}           %Commissioning + SIDIS
+\author{D.~Meekins}          %NO MINIMUM SHIFTS (TARGET WORK DURING COMMISSIONING+SIDIS. (INCLUDED AS AUTHOR!)
+\author{R.~Michaels}         %Commissioning + SIDIS
+\author{H.~Mkrtchyan}        %Commissioning ONLY
+\author{S.J.~Nazeer}         %Commissioning ONLY
+%\author{S.~Nanda}           %Spec. commissioning only Dec. 14-17 shifts
+\author{D.~Nguyen}           %Commissioning ONLY (Took 10 shifts) 
+\author{G.~Niculescu}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{M.~Niculescu}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{N.~Nuruzzaman}       %Commissioning ONLY
+\author{B.~Pandey}           %NO MINIMUM SHIFTS (WORKED ON HMS DCs for 1 year. INCLUDED AS AUTHOR!)
+\author{S.~Park}             %Commissioning + SIDIS
+\author{E.~Pooser}           %Commissioning + SIDIS
+%\author{A.~Puckett}         %NO MINIMUM SHIFTS
+\author{M.~Rehfuss}          %Commissioning ONLY
+\author{J.~Reinhold}         %Commissioning ONLY
+%\author{N.~Santiesteban}     %Color Transparency ONLY
+\author{B.~Sawatzky}          %Color Transparency ONLY (Worked on DAQ/Detector. INCLUDED AS AUTHOR!)
+\author{G.~Smith}             %Commissioning ONLY
+\author{A.~Sun}               %Commissioning + SIDIS
+\author{H.~Szumila-Vance}     %Commissioning + SIDIS
+%\author{A.~Tadepalli}        %F2 ONLY
+\author{V.~Tadevosyan}        %Commissioning + SIDIS
+%\author{R.~Trotta}           %NO MINIMUM SHIFTS
+\author{A.V.~Hernandez}       %Commissioning ONLY
+\author{S.A.~Wood}            %NO MINIMUM SHIFTS (Hall C Deputy + Worked on Hall C 12 GeV software + hardware work) (INCLUDED AS AUTHOR!)
+\author{Jinlong~Zhang}        %Commissioning ONLY How to distinguish between J. Zhang and J.Zhang (below) ?????? Middle names?             
+\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
+
+%Spokespeople
+%\author{W.U.~Boeglin$^{1}$}
+%\author{M.K.~Jones$^{2}$}
 
 \affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
-\affiliation{$^{2}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
+
+%\affiliation{$^{2}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
+
 \collaboration{for the Hall C Collaboration}

### 2020-02-12 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/author_listv2.tex
updated

--- 2020-02-12 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/author_listv2.tex
@@
-\author{C.~Yero$^{1}$}
-\author{W.U.~Boeglin$^{1}$}
-\author{M.K.~Jones$^{2}$}
+%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
+%Comment / Uncomment accordingly
+\author{C.~Yero$^{1}$}       %Main author for E12-10-003 experiment
+\author{D.~Abrams$^{2}$}           %Commissioning ONLY
+\author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
+\author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
+\author{S.~Alsalmi$^{5}$}          %Commissioning ONLY
+\author{R.~Ambrose$^{3}$}          %Commissioning + SIDIS
+%\author{D.~Androic}         %Color Transparency ONLY
+\author{W.~Armstrong$^{6}$}        %Commissioning ONLY
+\author{A.~Asaturyan$^{7}$}        %Commissioning ONLY
+\author{K.~Assumin-Gyimah$^{8}$}   %Commissioning ONLY
+\author{C.~Ayerbe Gayoso$^{9}$}    %Commissioning + SIDIS
+\author{A.~Bandari$^{9}$}          %Commissioning + SIDIS
+\author{J.~Bane$^{10}$}             %Deuteron Experiment ONLY
+\author{S.~Basnet$^{3}$}           %Commissioning + SIDIS
+\author{V.~Berdnikov$^{11}$}        %Commissioning + SIDIS
+\author{H.~Bhatt$^{8}$}            %Commissioning + SIDIS
+\author{D.~Bhetuwal$^{8}$}         %Commissioning + SIDIS
+\author{D.~Biswas$^{12}$}           %Commissioning + SIDIS
+\author{W.~Boeglin$^{1}$}          %Commissioning ONLY (Deuteron Spokesperson)
+\author{P.~Bosted$^{9}$}           %Commissioning ONLY (SIDIS Spokesperson)
+\author{E.~Brash$^{13}$}            %Commissioning ONLY
+\author{M.~Bukhari$^{14}$}          %Commissioning ONLY
+%\author{M.~Carmignotto}     %NO MINIMUM SHIFTS
+\author{H.~Chen$^{2}$}             %Commissioning ONLY
+\author{J.P.~Chen$^{15}$}           %Commissioning ONLY
+\author{M.~Chen$^{2}$}             %Commissioning ONLY
+\author{E.M.~Christy$^{12}$}          %Commissioning ONLY
+\author{S.~Covrig$^{15}$}           %Commissioning + SIDIS               
+\author{K.~Craycraft$^{10}$}        %Commissioning + SIDIS
+%\author{S.~Danagoulian}     %NO MINIMUM SHIFTS
+%\author{D.~Day}             %ONLY DEC. 2017 Spec. Commissioning ?????? (should be included?)
+\author{M.~Diefenthaler$^{15}$}     %Commissioning + SIDIS
+\author{M.~Dlamini$^{16}$}          %Commissioning ONLY
+\author{J.~Dunne$^{8}$}            %Commissioning ONLY
+\author{B.~Duran$^{6}$}            %Commissioning + SIDIS
+\author{D.~Dutta$^{8}$}            %Commissioning + SIDIS  (CT Spokesperson)
+\author{R.~Ent$^{15}$}              %NO MINIMUM SHIFTS JLab Physics Division Leader (SIDIS Co-Spokesperson) (should be included)??????
+\author{R.~Evans$^{3}$}            %Commissioning ONLY
+\author{H.~Fenker$^{15}$}           %Commissioning + SIDIS
+%\author{I.~Fernando}        %NO MINIMUM SHIFTS
+\author{N.~Fomin$^{10}$}            %Commissioning ONLY
+\author{E.~Fuchey$^{17}$}           %Commissioning ONLY
+\author{D.~Gaskell$^{15}$}          %Commissioning + SIDIS
+\author{T.N.~Gautam$^{12}$}         %Commissioning ONLY
+\author{F.A.~Gonzalez$^{18}$}       %Commissioning + SIDIS
+\author{O.~Hansen$^{15}$}           %Commissioning ONLY
+\author{F.~Hauenstein$^{19}$}       %Commissioning ONLY
+\author{A.V.~Hernandez$^{11}$}       %Commissioning ONLY
+\author{T.~Horn$^{11}$}             %Commissioning ONLY
+\author{G.~Huber$^{3}$}            %Commissioning ONLY
+\author{M.K.~Jones$^{15}$}          %Commissioning + SIDIS
+\author{S.~Joosten$^{6}$}          %Commissioning ONLY
+\author{M.L.~Kabir$^{8}$}          %Commissioning + SIDIS           
+%\author{N.~Kalantarians}    %NO MINIMUM SHIFTS
+\author{A.~Karki$^{8}$}            %Commissioning + SIDIS  
+\author{C.~Keppel$^{15}$}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
+\author{A.~Khanal$^{1}$}           %Commissioning ONLY
+\author{P.~King$^{16}$}             %Commissioning ONLY
+\author{E.~Kinney$^{20}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)
+%\author{H.S.~Ko}            %Color Transparency ONLY
+%\author{M.~Khol}            %NO MINIMUM SHIFTS
+\author{N.~Lashley-Colthirst$^{12}$}      %Commissioning ONLY
+\author{S.~Li$^{21}$}               %Commissioning ONLY
+\author{W.~Li$^{9}$}               %Commissioning ONLY
+\author{A.H.~Liyanage$^{12}$}       %Commissioning + SIDIS
+\author{D.~Mack$^{15}$}             %Commissioning + SIDIS
+\author{S.~Malace$^{15}$}           %Commissioning + SIDIS (F2 Spokesperson)
+%\author{P.~Markowitz}       %NO MINIMUM SHIFTS
+\author{J.~Matter$^{2}$}           %Commissioning + SIDIS
+\author{D.~Meekins$^{15}$}          %NO MINIMUM SHIFTS (TARGET WORK DURING COMMISSIONING+SIDIS. (INCLUDED AS AUTHOR!)
+\author{R.~Michaels$^{15}$}         %Commissioning + SIDIS
+\author{H.~Mkrtchyan$^{7}$}        %Commissioning ONLY
+\author{S.J.~Nazeer$^{12}$}         %Commissioning ONLY
+%\author{S.~Nanda}           %Spec. commissioning only Dec. 14-17 shifts
+\author{G.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{M.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{D.~Nguyen$^{2}$}           %Commissioning ONLY (Took 10 shifts) 
+\author{N.~Nuruzzaman$^{23}$}       %Commissioning ONLY
+\author{B.~Pandey$^{12}$}           %NO MINIMUM SHIFTS (WORKED ON HMS DCs for 1 year. INCLUDED AS AUTHOR!)
+\author{S.~Park$^{18}$}             %Commissioning + SIDIS
+\author{E.~Pooser$^{15}$}           %Commissioning + SIDIS
+%\author{A.~Puckett}         %NO MINIMUM SHIFTS
+\author{M.~Rehfuss$^{6}$}          %Commissioning ONLY
+\author{J.~Reinhold$^{1}$}         %Commissioning ONLY
+%\author{N.~Santiesteban}     %Color Transparency ONLY
+\author{B.~Sawatzky$^{15}$}          %Color Transparency ONLY (Worked on DAQ/Detector. INCLUDED AS AUTHOR!)
+\author{G.~Smith$^{15}$}             %Commissioning ONLY
+\author{A.~Sun$^{24}$}               %Commissioning + SIDIS
+\author{H.~Szumila-Vance$^{15}$}     %Commissioning + SIDIS
+%\author{A.~Tadepalli}        %F2 ONLY
+\author{V.~Tadevosyan$^{7}$}        %Commissioning + SIDIS
+%\author{R.~Trotta}           %NO MINIMUM SHIFTS
+\author{S.A.~Wood$^{15}$}            %NO MINIMUM SHIFTS (Hall C Deputy + Worked on Hall C 12 GeV software + hardware work) (INCLUDED AS AUTHOR!)
+\author{J.~Zhang$^{18}$}        %Commissioning ONLY 
+%\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
+\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
+\affiliation{$^{2}$University of Virginia, Charlottesville, Virginia 22903, USA}
+\affiliation{$^{3}$University of Regina, Regina, Saskatchewan S4S 0A2, Canada}
+\affiliation{$^{4}$North Carolina Agricultural and Technical State University, Greensboro, North Carolina 27411, USA}
+\affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
+\affiliation{$^{6}$Temple University, Philadelphia, Pennsylvania 19122, USA}
+\affiliation{$^{7}$Yerevan Physics Institute, 375036 Yerevan, Armenia}
+\affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
+\affiliation{$^{9}$The College of William \& Mary, Williamsburg, Virginia 23185, USA}
+\affiliation{$^{10}$University of Tennessee, Knoxville, Tennessee 37996, USA}
+\affiliation{$^{11}$Catholic University of America, Washington, DC 20064, USA}
+\affiliation{$^{12}$Hampton University, Hampton, Virginia 23669, USA}
+\affiliation{$^{13}$Christopher Newport University, Newport News, Virginia 23606, USA}
+\affiliation{$^{14}$Jazan University, Jazan 45142, Saudi Arabia}
+\affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
+\affiliation{$^{16}$Ohio University, Athens, Ohio 45701, USA}
+\affiliation{$^{17}$University of Connecticut, Storrs, Connecticut 06269, USA}
+\affiliation{$^{18}$Stony Brook University, Stony Brook, New York 11794, USA}
+\affiliation{$^{19}$Old Dominion University, Norfolk, Virginia 23529, USA}
+\affiliation{$^{20}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
+\affiliation{$^{21}$University of New Hampshire, Durham, New Hampshire 03824, USA}
+\affiliation{$^{22}$James Madison University, Harrisonburg, Virginia 22807, USA}
+\affiliation{$^{23}$Rutgers University, New Brunswick, New Jersey 08854, USA}
+\affiliation{$^{24}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}
 
-\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
-\affiliation{$^{2}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
 \collaboration{for the Hall C Collaboration}

### 2020-02-21 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

@@
 \widetext
-\leftline{Version 03 as of \today}
+\leftline{Version 04 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
 
-\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
-\input author_list.tex       % D0 authors (remove the first 3 lines
-                             % of this file prior to submission, they
-                             % contain a time stamp for the authorlist)
-                             % (includes institutions and visitors)
+%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
+\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}=1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
+\input authorlist.tex
+
 \date{\today}

### 2020-03-05 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
-\indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD2). The scattered electron and knocked-out proton were detected in coincidence
+\indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
 by the new Super High Momentum Spectrometer (SHMS) and the High Momentum Spectrometer (HMS), respectively.
 The recoiling neutron was reconstructed using energy-momentum conservation.
-The missing momentum is defined as
-$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the missing  energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
-final proton and neutron kinetic energies respectively.
+The recoil momentum is defined as
+$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
+final proton and recoil system kinetic energies, respectively, where the recoil system is assumed to be a neutron.
 The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\
-\indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes\cite{hodo_techreport} used for triggering, a pair of drift chambers\cite{dc_techreport} used for tracking, and a calorimeter\cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
+\indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
 The trigger setup for this experiment required a minimum of 3/4 hodoscope planes to detect a signal for data readout in each spectrometer. Due to the absence of significant background and the low
 accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\
-\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80,580$ and $750$ MeV/c.
+\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
 At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
 the lower and higher missing momentum settings, respectively.
-At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{\mathrm{r}}$)
-measured on this experiment.
-As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{o}\lesssim \theta_{pq}\lesssim21.4^{o}$.
-At these forward angles and large momentum transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
-\indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
+At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c, which is more than twice the highest neutron recoil momentum
+measured in this experiment.
+As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.
+At these forward angles and large momenta transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
+\indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
 simulation program, SIMC.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
-momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties\cite{cyero_phdthesis}.\\
+momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
-The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics
-is well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a missing
-energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the
-SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions) and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target.\\
-\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$ the corrections
-were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$)\cite{cyero_phdthesis} and
-target boiling factors ($4.2 \%$)\cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\
+The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region for which the reconstruction optics
+are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''
+energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a PID cut on the
+SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
+originated from the same reaction vertex at the target. See Supplemental Material \cite{Suppl_Mat} for details of the analysis cuts.\\
+\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
+were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$) \cite{cyero_phdthesis} and
+target boiling factors ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
-Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
+Arrington's proton form factor parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
 model.
@@
 \ref{fig:fig1}).
-The good agreement gives us confidence on the measurements made at higher missing momentum settings for which no previous data exist. \\
+The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
 \indent The systematic uncertainties of the measured cross sections were determined from 
-normalization\footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
-Determination of systematics on these quantities is a work in progress.
-(Private communication with D.
-Mack)} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings.
-The individual
+normalization \footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
+Determination of systematics on these quantities is a work in progress.} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
 contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
@@
 \indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each data set independently, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins
-of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\leq1.01$ GeV/c.
+of different data sets.
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\lesssim 1$ GeV/c.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
@@
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
-The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
-For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
+The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.
+Laget including FSI \cite{LAGET2005}.
+For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics was calculated and used in the bin centering correction factor defined as:
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
@@
 \indent Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged
-for overlapping bins in $p_{\mathrm{r}}$. The reduced cross sections are defined as follows:
+over overlapping bins in $p_{\mathrm{r}}$. The reduced cross sections are defined as follows:
 \begin{equation}
-\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}}
+\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
 \label{eq:1}
 \end{equation}
-where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor  and $\sigma_{\mathrm{cc1}}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
+where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor  and $\sigma_{\mathrm{cc1}}$ is the de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.
+\cite{PhysRevC.69.022201}.
 Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\
@@
 \includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
-with a bin width of $\pm 5^{o}$.
-The data is compared to the previous Hall A experiment (cyan) results\cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
-AV18(green) and CD-Bonn(magenta) NN potentials}
+\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
+with a bin width of $\pm 5^{\circ}$.
+The data is compared to the previous Hall A experiment (cyan) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
+AV18(green) and CD-Bonn(magenta) NN potentials.}
 \label{fig:fig1}
@@
 \noindent $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
+The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
 The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials.
+cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials.
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget\cite{LAGET2005}.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget \cite{LAGET2005}.\\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
 The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
+\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
 AV18 models significantly differ from the CD-Bonn.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{\mathrm{r}}\sim700$ MeV/c.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
 The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
-In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
-\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c (Fig.
+In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
+\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
 \hyperref[fig:fig1]{1(b)}).
@@
 to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
-\indent At $\theta_{nq}=75^{o}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
+\indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
 behaviour (smaller falloff) that overshadows any possibility of extracting the momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
-deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{\mathrm{red}}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
-\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}) the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
+deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{\mathrm{red}}$) \cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
+\indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
 to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\
-\indent At larger recoil momenta where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{o}$ FSI start to dominate for
+\indent At larger recoil momenta, where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
 missing momenta typically above 800 MeV/c for the CD-Bonn
@@
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
-\caption{The ratio $R(p_{\mathrm{r}}$) = $\sigma_{\mathrm{red}}/\sigma^{{\text{CD-Bonn PWIA}}}_{\mathrm{red}}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
+\caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
 The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
@@
 calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{o}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
-\indent Overall it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
+At $\theta_{nq}=45^{\circ}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
+\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
 This behavior of the data is new
 and additional data in this kinematic region are necessary to improve the statistics. \\
-\indent At $\theta_{nq}=75^{o}$ (Fig.
+\indent At $\theta_{nq}=75^{\circ}$ (Fig.
 \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
@@
 \indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
-very high neutron recoil momenta at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
+very high neutron recoil momenta ($p_{r}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
 short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
 Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momentum, however, all models were unable to describe the data. \\
+At higher missing momenta, however, all models were unable to describe the data. \\
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab

### 2020-03-05 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

@@
-The deuteron is the only bound two-nucleon  system and serves as a starting point to study the strong nuclear force at the subfermi distance scale, a region which is currently
-not well understood. At such small internucleon distances the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
-nucleons begin to overlap. 
-This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017}.
-Short-range studies of the deuteron are also important in determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of freedom is still valid before
-having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics\cite{sargsian_2015}.
+The deuteron is the only bound two-nucleon  system and serves as a starting point to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
+not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
+nucleons begin to 
+This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
+Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
+having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
 As of the present time, there are only a few nuclear physics experiments for
@@
 \indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA, the virtual photon couples to
+electro-disintegration reaction at $p_{r}>300$ MeV/c neutron recoil (or ``missing'') momenta. Within the PWIA, the virtual photon couples to
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
 The neutron carries a momentum equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
-In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
+to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\
+\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
 photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state which subsequently
@@
 The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
-$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}.
+$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
 IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
@@
 from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
-\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA)\cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
-GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$.
-This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$.
-Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{\mathrm{Bj}}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI.
+\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
+GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$.
+This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{\circ}$ and $\theta_{nq}\sim120^{\circ}$.
+Since at $\theta_{nq}\sim120^{\circ}$ IC are not negligible, $x_{\mathrm{Bj}}>1$ (or equivalently $\theta_{nq}\sim40^{\circ}$) is the preferred choice to suppress IC as well as FSI.
 \\
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
-\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both
-experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles peaking
-at $\theta_{nq} \sim 70^{o}$ in agreement with GEA\cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
+\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at Jefferson Lab (JLab) in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}.
+Both
+experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
+at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
 distributions for  a range of $Q^2$ values as well as momentum distributions.
@@
 which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c. \\
-\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c.
-For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$
-and $45\pm5^{o}$ compared to  $\theta_{nq}=75\pm5^{o}$. Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{o}$) compared to FSI
-dominance at $\theta_{nq}=75^{o}$\cite{PhysRevLett.107.262501}. \\
+\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
+For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
+and $45\pm5^{\circ}$ compared to  $\theta_{nq}=75\pm5^{\circ}$.
+Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{\circ}$) compared to FSI
+dominance at $\theta_{nq}=75^{\circ}$ \cite{PhysRevLett.107.262501}. \\
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to 1.01 GeV/c. At the selected kinematic settings with neutron recoil angles between $35^{o}$ and $45^{o}$, MEC and IC are
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are
 suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

### 2020-03-05 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

@@
 %\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
-\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}=1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
+\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
 \input authorlist.tex
@@
 \begin{abstract}
-  New $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+$^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
 reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
-$\theta_{nq} = 35^\circ$ and $45^\circ$  with respect to the 3-momentum
-transfer $\vec q$. At these kinematic settings final state interactions (FSI),
+$\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
+transfer $\vec q$. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
 meson exchange currents (MEC) and isobar configurations (IC) are expected to 
@@
 dominant cross section contribution. The new data are compared to recent
-theoretical calculations where a significant disagreement at very high
-missing momenta has been observed.
-
+theoretical calculations, where a significant disagreement for
+missing momenta $p_{r}>700$ MeV/c has been observed. 
 \end{abstract}

### 2020-03-06 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
-were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss due to nuclear interactions in the HMS ($4.7 \%$) \cite{cyero_phdthesis} and
-target boiling factors ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all data sets. \\
+were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) \cite{cyero_phdthesis} and
+target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
 Arrington's proton form factor parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
-model.
-The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).
-For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig.
-\ref{fig:fig1}).
-The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
+model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).\\
+%For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).
+%The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
 \indent The systematic uncertainties of the measured cross sections were determined from 
@@
 Determination of systematics on these quantities is a work in progress.} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
-contributions from normalization uncertainties were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
-for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
-\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each data set independently, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins
-of different data sets.
+contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), proton loss in HMS ($0.49 \%$), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
+for an overall normalization uncertainty added in quadrature of about 3.7 $\%$ per setting. \\
+\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
+and added in quadrature for overlapping $p_{r}$ bins.
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\lesssim 1$ GeV/c.
@@
 over the kinematic bin.\\
-\indent Both experimental and theoretical reduced cross sections were extracted from the measured and calculated cross sections for each data set independently and subsequently averaged
-over overlapping bins in $p_{\mathrm{r}}$. The reduced cross sections are defined as follows:
+\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 with a bin width of $\pm 5^{\circ}$.
-The data is compared to the previous Hall A experiment (cyan) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
+The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
 AV18(green) and CD-Bonn(magenta) NN potentials.}
@@
 \noindent $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan).
+For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ .
+The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
+The good agreement between the Hall A and C data at lower $p_{r}$
+gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
 The data are compared to theoretical reduced

### 2020-03-07 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
-simulation program, SIMC.
+simulation program, SIMC \cite{PhysRevC.64.054610}.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
@@
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target. See Supplemental Material \cite{Suppl_Mat} for details of the analysis cuts.\\
+originated from the same reaction vertex at the target (See Supplemental Material \cite{Suppl_Mat}).\\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
@@
 \indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
-and added in quadrature for overlapping $p_{r}$ bins.
-For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\lesssim 1$ GeV/c.
+and added in quadrature for overlapping $p_{r}$ bins. For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
@@
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
-The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.
+The SIMC simulation code was used for these calculations with the Deuteron Model by J.M.
 Laget including FSI \cite{LAGET2005}.
@@
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin.\\
+over the kinematic bin.
+The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the J.M.
+Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
 \indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:

### 2020-03-16 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target (See Supplemental Material \cite{Suppl_Mat}).\\
+originated from the same reaction vertex at the target.\\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
@@
 \end{equation}
-where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.
-\cite{PhysRevC.69.022201}.
-Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\
-\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
-$p_{\mathrm{r}}$ for three recoil angle settings at
+where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K=E_{\mathrm{f}}p_{\mathrm{f}}$ is a kinem-
 \onecolumngrid
 \begin{center}
-\begin{figure}[hb!]
+\begin{figure}[ht!]
 \includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
@@
 \twocolumngrid
-\noindent $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
+\noindent atical factor, $f_{\mathrm{rec}}=\frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the
+de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
+Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\
+\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
+$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
 For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ .

### 2020-03-16 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/make_plots.C

@@ -4,10 +4,10 @@ void make_plot(int set, int pm, string model, string rad)
   //gROOT->SetBatch(kTRUE);  
   gStyle->SetOptStat(1001111);
 
-  string thnq_set = "all_thnq_Q2_4to5GeV";
+  //string thnq_set = "all_thnq_Q2_4to5GeV";
   //string thnq_set = "thnq35_Q2_4to5GeV";
   //string thnq_set = "thnq45_Q2_4to5GeV";
-  //string thnq_set = "thnq75_Q2_4to5GeV";
+  string thnq_set = "thnq75_Q2_4to5GeV";
   
   
   TString root_dir = Form("../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 \indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
-by the new Super High Momentum Spectrometer (SHMS) and the High Momentum Spectrometer (HMS), respectively.
-The recoiling neutron was reconstructed using energy-momentum conservation.
-The recoil momentum is defined as
+by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as 
 $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
@@
 \end{equation}
-where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K=E_{\mathrm{f}}p_{\mathrm{f}}$ is a kinem-
 \onecolumngrid
+\newpage
 \begin{center}
@@
 \twocolumngrid
-\noindent atical factor, $f_{\mathrm{rec}}=\frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the
+\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor\footnote{The kinematical factor in Eq.\ref{eq:1} is defined as $K\equiv E_{\mathrm{f}}p_{\mathrm{f}}$, where $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.},
+$f_{\mathrm{rec}}$ is a recoil factor\footnote{The recoil factor in Eq.\ref{eq:1} is obtained by integrating over the deuteron binding energy in the 6-fold differential cross section and is defined as $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$, where
+          $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.} and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
@@
 At higher missing momenta, however, all models were unable to describe the data. \\
+\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
+momentum region ($p_{r}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
@@
 was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
-under grant No. D2-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
+under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
 under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

@@
 to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
-At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are
-suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.
+Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
+At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

@@
 \leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
+\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by April 10, 2020}
 \centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
 %\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
-\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
+%\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
+\title{Deuteron Electro-Disintegration at Very High Missing Momenta}
 \input authorlist.tex

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/make_plots.C

@@ -5,9 +5,9 @@ void make_plot(int set, int pm, string model, string rad)
   gStyle->SetOptStat(1001111);
 
   //string thnq_set = "all_thnq_Q2_4to5GeV";
-  //string thnq_set = "thnq35_Q2_4to5GeV";
+  string thnq_set = "thnq35_Q2_4to5GeV";
   //string thnq_set = "thnq45_Q2_4to5GeV";
-  string thnq_set = "thnq75_Q2_4to5GeV";
+  //string thnq_set = "thnq75_Q2_4to5GeV";
   
   
   TString root_dir = Form("../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 \indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
-by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as 
-$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
-final proton and recoil system kinetic energies, respectively, where the recoil system is assumed to be a neutron.
+by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively.
 The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\
@@
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
+\indent The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
+and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
+4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
@@
 \indent The systematic uncertainties of the measured cross sections were determined from 
-normalization \footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
-Determination of systematics on these quantities is a work in progress.} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
+normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
 contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), proton loss in HMS ($0.49 \%$), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
@@
 Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
-\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
-\begin{equation}
-\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
-\label{eq:1}
-\end{equation}
+\indent The experimental and theoretical reduced cross 
 \onecolumngrid
-\newpage
 \begin{center}
@@
 \twocolumngrid
-\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor\footnote{The kinematical factor in Eq.\ref{eq:1} is defined as $K\equiv E_{\mathrm{f}}p_{\mathrm{f}}$, where $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.},
-$f_{\mathrm{rec}}$ is a recoil factor\footnote{The recoil factor in Eq.\ref{eq:1} is obtained by integrating over the deuteron binding energy in the 6-fold differential cross section and is defined as $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$, where
-          $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.} and $\sigma_{\mathrm{cc1}}$ is the
+\noindent sections were extracted and are defined as follows:
+\begin{equation}
+\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
+\label{eq:1}
+\end{equation}
+\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
+$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+is a recoil factor obtained by integrating over the deuteron binding energy in the 6-fold differential cross section, and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

@@
 not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
-nucleons begin to 
+nucleons begin to overlap.
 This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
@@
 which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
-\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at $p_{r}>300$ MeV/c neutron recoil (or ``missing'') momenta. Within the PWIA, the virtual photon couples to
+\indent  Within the PWIA, the virtual photon couples to
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
-The neutron carries a momentum equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\
+The neutron carries a recoil momentum, $p_{r}$, equal in magnitude but opposite in direction
+to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
+The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
+electro-disintegration reaction at $p_{r}>300$ MeV/c.\\
 \indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
@@
 IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
-electro-production threshold.\\
-\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions
+electro-production threshold.
+Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref.
+\cite{sargsian_2015}) have helped quantify the contributions
 from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

@@
 $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
+reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.0 GeV/c. The data have been obtained at fixed neutron recoil angles
 $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
-transfer $\vec q$. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
-meson exchange currents (MEC) and isobar configurations (IC) are expected to 
-be suppressed and the plane wave impulse approximation (PWIA) provides the
+transfer $\vec q$. The new data agrees well with previous data which reached $p_{r}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
+meson exchange currents (MEC) and isobar configurations (IC) are
+suppressed and the plane wave impulse approximation (PWIA) provides the
 dominant cross section contribution. The new data are compared to recent

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-The trigger setup for this experiment required a minimum of 3/4 hodoscope planes to detect a signal for data readout in each spectrometer. Due to the absence of significant background and the low
-accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\
+For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
+\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
 and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
@@
 Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
-\indent The experimental and theoretical reduced cross 
 \onecolumngrid
@@
 \twocolumngrid
-\noindent sections were extracted and are defined as follows:
+\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 \end{equation}
-\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
+\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section, $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
 $E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
-is a recoil factor obtained by integrating over the deuteron binding energy in the 6-fold differential cross section, and $\sigma_{\mathrm{cc1}}$ is the
+is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.

### 2020-04-08 MY_THESIS/Hodoscope_Calib_Doc/hodo_calib.tex
updated

@@
   \includegraphics[scale=0.5]{HodoPaddle.pdf}
-  \caption{Cartoon of individual scintillator paddles to illustrate the various timing corrections applied. (Graph Source: E. Pooser)}
+  \caption{Cartoon of individual scintillator paddles to illustrate the various timing corrections applied.}
   \label{fig:Paddle}
@@
   at a particular time, depending on the signal \textit{amplitude}, the leading edge of the signal is discriminated,
-  which causes the dscriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the
+  which causes the discriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the
   same time. Analog-to-Digital Converters (ADCs), do not have this disadvantage, since they correct for time-walk internally,
@@
   the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the ADC amplitude. A model
-  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time. (See Figure \ref{fig:TWFit}) The function that is currently
-  being used in Hall C has the form:
-  \begin{equation}
-    f_{TW}(a) = c_{1} + \frac{1}{(\frac{a}{TDC_{Thrs.}})^{c_{2}}}
-  \end{equation}
-  where $a$ is the ADC amplitude,  $TDC_{Thrs}$ is the TDC threshold which is currently set to 120 mV. \newpage
+  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time.
 \begin{figure}[H]

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/codes/combine_data.py

@@ -1,0 +1,285 @@
+import LT.box as B
+from LT.datafile import dfile
+import numpy as np
+import numpy.ma as ma
+import sys           
+import os                                                      
+from sys import argv  
+
+#This Code:
+#This code assumes the systematics errors have been calculated on the Xsec and red Xsec, and reads them 
+#to combine the data. When combining data, ONLY used statistical weight.  To combine the systematic errors
+#from different data sets, take the normal average of the systematic errors for now (Mark Jones)
+#When plotting combined reduced Xsec, plot statistical and total error bars (two error bars per data point)
+
+# **NOTE** ONLY Reduced Cross Sections (Momentum Distributions) can be combined. Cross Sections CANNOT be combined, 
+#          as they depend on spectrometer the kinematic setting, whereas in momentum distribution, that depenency has
+#          been factored out by dividing by K*sig_cc1(GEp, GMp)
+# ** combines (takes average) different data sets of a given kinematic setting and writes to file
+# ** combines different kinematic settings
+
+def convert2NaN(arr=np.array([]), value=0):
+    #method to convert a specified value in a array to nan (not a number)
+
+    for i in enumerate(arr):
+        if arr[i[0]]==value:
+            arr[i[0]] = np.nan
+    return arr
+
+MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
+
+#===========User Input (Dir. Name to store output)==================
+#ipython combine_data.py Em_final40MeV
+sys_ext = sys.argv[1]   
+#===================================================================
+
+#check if directory exists, else creates it.
+if not os.path.exists(sys_ext):
+    os.makedirs(sys_ext)
+
+output_file='./%s/redXsec_combined.txt'%(sys_ext)
+
+fout = open(output_file, 'w') 
+
+#------------------------------------------------------------                   
+# header information for the output file    
[…]

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/deep_codes/make_plots.C

@@ -1,0 +1,304 @@
+void make_plot(int set, int pm, int thnq)
+{
+
+  //gROOT->SetBatch(kTRUE);  
+  //gStyle->SetOptStat(1001111);
+  gStyle->SetOptStat(0000000);
+
+  string thnq_set = "all_thnq_Q2_4to5GeV";
+  //string thnq_set = Form("thnq%d_Q2_4to5GeV", thnq);
+  //string thnq_set = "thnq45_Q2_4to5GeV";
+  //string thnq_set = "thnq75_Q2_4to5GeV";
+  
+
+  TString root_dir = Form("../../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());
+  TString simc_fname = Form("deep_simc_histos_pm%d_lagetfsi_rad_set%d.root", pm, set);
+  TString data_fname = Form("deep_data_histos_pm%d_set%d_combined.root", pm, set);
+    
+  TString simc_filename_fsi = root_dir+simc_fname;
+  TString data_filename = root_dir+data_fname;
+  
+  //Open SIMC/data ROOT files;
+  TFile *simc_file_fsi = new TFile(simc_filename_fsi);
+  TFile *data_file = new TFile(data_filename);
+
+
+  //-------------Spectrometer Acceptance Plots--------
+  
+  //FSI
+  TH1F *simc_eytar_fsi =  0;
+  TH1F *simc_exptar_fsi =  0;
+  TH1F *simc_eyptar_fsi =  0;
+  TH1F *simc_edelta_fsi =  0;
+
+  TH1F *simc_hytar_fsi =  0;
+  TH1F *simc_hxptar_fsi =  0;
+  TH1F *simc_hyptar_fsi =  0;
+  TH1F *simc_hdelta_fsi =  0;
+
+  
+  //Define data histos
+  TH1F *data_eytar = 0;
+  TH1F *data_exptar =  0;
+  TH1F *data_eyptar =  0;
+  TH1F *data_edelta =  0;
+
+  TH1F *data_hytar = 0;
+  TH1F *data_hxptar =  0;
+  TH1F *data_hyptar =  0;
+  TH1F *data_hdelta =  0;
+
+
+  //------------------ANALYSIS PLOTS------------------
+
+  //SIMC Analysis Cuts (FSI)
+  TH1F *simc_Q2_fsi =  0;
+  TH1F *simc_thnq_fsi = 0;
+  TH1F *simc_emiss_fsi = 0;
[…]

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/heep_codes/compare_heep.C

@@ -1,0 +1,914 @@
+//Script to make comparison between SIMC and Commissioning Data from HallC Spring 2018
+//The comparisons are weighted
+
+//Compare Target Reconstruction/FOCAL PLANE/ Kinematics Variables
+
+void compare_heep(int run)
+{
+
+  //gROOT->SetBatch(kTRUE);  
+  gStyle->SetOptStat(0000000);
+
+
+  TString root_dir = "../../root_files/pre_HEEP_ELASTICS/";
+  //Pre-defined SIMC/data root file names containing histogram object to comapare
+  TString simc_filename =  Form("heep_simc_histos_%d_rad.root", run);                      
+  TString data_filename = Form("heep_data_histos_%d_combined.root",run); 
+
+  TString simc_f = root_dir + simc_filename;
+  TString data_f = root_dir + data_filename;
+  
+  //Where to store plots
+  string plots_dir = "./";
+  string plots_path;
+  
+  //Open SIMC/data ROOT files;
+  TFile *simc_file = new TFile(simc_f);
+  TFile *data_file = new TFile(data_f);
+
+  //---------------Target ----------------
+  //Define SIMC histos ('h'-->hadron arm,  'e'-->electron arm)
+  
+  TH1F *simc_xtar =  0;
+  TH1F *simc_ytarH =  0;
+  TH1F *simc_ztarH =  0;
+
+  TH1F *simc_ytarP =  0;
+  TH1F *simc_ztarP =  0;  
+
+  //Define data histos
+  TH1F *data_xtarH = 0;
+  TH1F *data_ytarH = 0;
+  TH1F *data_ztarH = 0;
+
+  TH1F *data_xtarP = 0;                                                                                                     
+  TH1F *data_ytarP = 0;                                                                                                                                   
+  TH1F *data_ztarP = 0; 
+
+  //---------------Target Reconstruction Variables----------------
+  //Define SIMC histos ('h'-->hadron arm,  'e'-->electron arm)
+  TH1F *simc_eytar =  0;
[…]

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/heep_codes/plot_ratio.py

@@ -1,0 +1,17 @@
+import numpy as np
+from LT.datafile import dfile
+import LT.box as B
+
+kin = dfile('heep_yield.dat')
+
+
+run = kin['Run']
+shms_rate = kin['shms_3of4_rate']   #kHz
+R = kin['R']
+R_err = kin['R_err']
+
+B.plot_exp(shms_rate, R, R_err, marker='o', color='red', label='Yield Ratio')
+B.pl.xlabel('SHMS 3/4 Rate [kHz]')
+B.pl.ylabel(r'Y$_{Data}$/Y$_{SIMC}$')
+B.pl.title('H(e,e\'p) Elastic Yield Rtaio')
+B.pl.show()

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/make_plots.C

@@ -1,315 +1,0 @@
-void make_plot(int set, int pm, string model, string rad)
-{
-
-  //gROOT->SetBatch(kTRUE);  
-  gStyle->SetOptStat(1001111);
-
-  //string thnq_set = "all_thnq_Q2_4to5GeV";
-  string thnq_set = "thnq35_Q2_4to5GeV";
-  //string thnq_set = "thnq45_Q2_4to5GeV";
-  //string thnq_set = "thnq75_Q2_4to5GeV";
-  
-  
-  TString root_dir = Form("../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());
-  TString simc_fname = Form("deep_simc_histos_pm%d_lagetfsi_rad_set%d.root", pm, set);
-  TString data_fname = Form("deep_data_histos_pm%d_set%d_combined.root", pm, set);
-    
-  TString simc_filename_fsi = root_dir+simc_fname;
-  TString data_filename = root_dir+data_fname;
-  
-  //Open SIMC/data ROOT files;
-  TFile *simc_file_fsi = new TFile(simc_filename_fsi);
-  TFile *data_file = new TFile(data_filename);
-
-
-  //-------------Spectrometer Acceptance Plots--------
-  
-  //FSI
-  TH1F *simc_eytar_fsi =  0;
-  TH1F *simc_exptar_fsi =  0;
-  TH1F *simc_eyptar_fsi =  0;
-  TH1F *simc_edelta_fsi =  0;
-
-  TH1F *simc_hytar_fsi =  0;
-  TH1F *simc_hxptar_fsi =  0;
-  TH1F *simc_hyptar_fsi =  0;
-  TH1F *simc_hdelta_fsi =  0;
-
-  
-  //Define data histos
-  TH1F *data_eytar = 0;
-  TH1F *data_exptar =  0;
-  TH1F *data_eyptar =  0;
-  TH1F *data_edelta =  0;
-
-  TH1F *data_hytar = 0;
-  TH1F *data_hxptar =  0;
-  TH1F *data_hyptar =  0;
-  TH1F *data_hdelta =  0;
-
-
-  //------------------ANALYSIS PLOTS------------------
-
-  //SIMC Analysis Cuts (FSI)
-  TH1F *simc_Q2_fsi =  0;
-  TH1F *simc_thnq_fsi = 0;
-  TH1F *simc_emiss_fsi = 0;
-  TH1F *simc_ztar_diff_fsi = 0; 
[…]

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/norm_systematics.py

@@ -1,309 +1,0 @@
-import numpy as np
-from LT.datafile import dfile
-import LT.box as B
-import shutil as sh
-import os
-
-#This code has utilities functions that calculates the systematics 
-#due to the correction factors in the data yield for each data set
-
-#If, FullWeight = f_tgt * f_pAbs * f_tLT  * f_eTrkEff * f_pTrkEff * f_Qtot
-#Experimental Xsec: sig_exp = Y_corr / P.S. = (Y_uncorr / P.S.) *  f_tgt * f_pAbs * f_tLT  * f_eTrkEff * f_pTrkEff * f_Qtot
-
-#Each of the corrections has an associated uncertainty, df/f, therefore, the
-#systematic error on the cross section (sig_exp ) is:  dsig_exp_syst2 = [sig_exp**2 * (df/f)**2 ]_tgtBoil + . . . +  [sig_exp**2 * (df/f)**2 ]_pAbs + ...
-#A derivative has to be takem to determine the uncertainty in f.
-
-#***IMPORTANT***: Each of the utilities functions saves a copy of the average kinematics file with the dsig_i (contributions to the cross section systematics error)
-#                 The errors are written to file as relative error, df/f. To get the absolute error, one would multiply by the cross section to get: df = (df/f)*f
-#                 A special utility function calculates the total dsig2 from the sum in quadrature of the norm systematics: dsig2_norm_tot = dsig2_hEtrk + dsig2_Qtot + dsig2_tLT + . . .
-#                 The utilities functions also return their respective the dsig_2 contributions as well as the relative error df/f, which gives an idea of how large is the error relative to the Xsec
-                  #(The model='' input parameter refers to the model used for the radiative corrections. We use Laget FSI, as it closely represents data in all kinematical regions)
-
-#Tracking efficiencies
-def get_trkEff_syst(pm_set=0, model='', data_set=0):
-    
[…]

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

@@
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
-contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), proton loss in HMS ($0.49 \%$), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
-for an overall normalization uncertainty added in quadrature of about 3.7 $\%$ per setting. \\
+contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ),
+and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
+proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
+as an overall normalization constant to the final result.\\
 \indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
@@
 Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
+\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \onecolumngrid
 \begin{center}
-\begin{figure}[ht!]
+\begin{figure}
 \includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
@@
 \twocolumngrid
-\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/codes/combine_data.py

@@ -1,285 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import numpy.ma as ma
-import sys           
-import os                                                      
-from sys import argv  
-
-#This Code:
-#This code assumes the systematics errors have been calculated on the Xsec and red Xsec, and reads them 
-#to combine the data. When combining data, ONLY used statistical weight.  To combine the systematic errors
-#from different data sets, take the normal average of the systematic errors for now (Mark Jones)
-#When plotting combined reduced Xsec, plot statistical and total error bars (two error bars per data point)
-
-# **NOTE** ONLY Reduced Cross Sections (Momentum Distributions) can be combined. Cross Sections CANNOT be combined, 
-#          as they depend on spectrometer the kinematic setting, whereas in momentum distribution, that depenency has
-#          been factored out by dividing by K*sig_cc1(GEp, GMp)
-# ** combines (takes average) different data sets of a given kinematic setting and writes to file
-# ** combines different kinematic settings
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-#===========User Input (Dir. Name to store output)==================
-#ipython combine_data.py Em_final40MeV
-sys_ext = sys.argv[1]   
-#===================================================================
-
-#check if directory exists, else creates it.
-if not os.path.exists(sys_ext):
-    os.makedirs(sys_ext)
-
-output_file='./%s/redXsec_combined.txt'%(sys_ext)
-
-fout = open(output_file, 'w') 
-
-#------------------------------------------------------------                   
-# header information for the output file    
[…]

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/codes/rad_bc_systematics/plot_ratio.py

@@ -1,25 +1,0 @@
-from LT.datafile import dfile
-import LT.box as B
-import numpy as np
-
-f = dfile('pm580_laget_bc_corr_set1.txt')
-
-th_nq = np.array(f['xb'])
-pm = np.array(f['yb'])
-
-a = np.array(f['pwiaRC_dataXsec'])
-sig_a = np.array(f['pwiaRC_dataXsec_err'])
-b = np.array(f['fsiRC_dataXsec'])
-sig_b = np.array(f['fsiRC_dataXsec_err'])
-
-    
-R =  a / b
-
-dR_da = 1./b
-dR_db = -a/b**2
-
-dR = np.sqrt( (dR_da)**2 * (sig_a)**2 + (dR_db)**2 * (sig_b)**2 )
-
-B.plot_exp(pm, R, dR)
-B.pl.ylim(-10, 10)
-B.pl.show()

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/rad_bc_systematics/check_bc_corr.py

@@ -1,0 +1,136 @@
+#This code checks the Bin-Centering corrections are done properly and make
+#sense. 
+#The code makes plots of: 
+#1) BC corr. ratio for PWIA, FSI
+#2) dataXsec before/after FSI BC. Corrected
+#3) fsiXsec_avg_simc, fsiXsec_theory  (the two cross sections ratio give bc corr. factor)
+
+from LT.datafile import dfile
+import LT.box as B
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.ticker as tic
+import sys
+import os
+
+def convert2NaN(arr=np.array([]), value=0):
+    #method to convert a specified value in a array to nan (not a number)
+    
+    for i in enumerate(arr):
+        if arr[i[0]]==value:
+            arr[i[0]] = np.nan
+    return arr
+
+
+#User Input (Usage: python check_bc_corr.py 80 1 )
+pm_set = int(sys.argv[1])
+data_set = int(sys.argv[2])
+sys_ext = sys.argv[3]  
+
+
+#Make relevant directories to store plots
+dir_name = sys_ext+"_plots"
+
+#check if directory exists, else creates it.
+if not os.path.exists(dir_name):
+    os.makedirs(dir_name)
+
+#Read data file
+if pm_set==80:
+    fname = sys_ext + '/pm%i_laget_bc_corr.txt' % (pm_set)
+else:
+    fname = sys_ext + '/pm%i_laget_bc_corr_set%i.txt' %(pm_set, data_set)
+
+f = dfile(fname)
+
+#Get Relevant headers to plot
+pm = f['yb']    #missing momentum bin
+thnq = f['xb']  #theta_nq bin 
+
+#Get Bin-Centering Factors
+bc_fact_fsi = f['bc_fact_fsi']
+bc_fact_fsi_err = f['bc_fact_fsi_err']
+
+bc_fact_pwia = f['bc_fact_pwia']
+bc_fact_pwia_err = f['bc_fact_pwia_err']
+
+#Get Data Xsec
+fsiRC_dataXsec = f['fsiRC_dataXsec']               #only rad. corrected  data
+fsiRC_dataXsec_err = f['fsiRC_dataXsec_err']
[…]

### 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/supplementary_material/codes/rad_bc_systematics/plot_ratio.py

@@ -1,0 +1,25 @@
+from LT.datafile import dfile
+import LT.box as B
+import numpy as np
+
+f = dfile('pm580_laget_bc_corr_set1.txt')
+
+th_nq = np.array(f['xb'])
+pm = np.array(f['yb'])
+
+a = np.array(f['pwiaRC_dataXsec'])
+sig_a = np.array(f['pwiaRC_dataXsec_err'])
+b = np.array(f['fsiRC_dataXsec'])
+sig_b = np.array(f['fsiRC_dataXsec_err'])
+
+    
+R =  a / b
+
+dR_da = 1./b
+dR_db = -a/b**2
+
+dR = np.sqrt( (dR_da)**2 * (sig_a)**2 + (dR_db)**2 * (sig_b)**2 )
+
+B.plot_exp(pm, R, dR)
+B.pl.ylim(-10, 10)
+B.pl.show()

### 2020-04-10 UTILITIES_CODES/latex_files/supp.tex
updated

\title{\small \textbf{Supplemental Material: $^{2}$H$(e,e'p)n$ Cross Section Measurements \\for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ }}

\documentclass[12pt]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\maketitle

\section{\small Spectrometer Acceptance}
In Hall C, the spectrometer acceptance is defined by the variables reconstructed at the target: $\delta, Y_{\mathrm{tar}}, X'_{\mathrm{tar}}$ and $Y'_{\mathrm{tar}}$, where

\end{document}

### 2020-04-10 UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -1,0 +1,132 @@
+//Utility function that takes as argument 2 histogram objects, and the xlabel, ylabel (assume same range) and plots their ratio
+//Used to plot data/simc comparison and their ratio
+void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", TString title="")
+{
+
+  gStyle->SetOptStat(0);
+  gStyle->SetTitleFontSize(0.08);
+  gStyle->SetTitleFont(22, "");
+  gStyle->SetLegendBorderSize(0);
+  gStyle->SetLegendFont(22);
+  gStyle->SetLegendTextSize(0.06);
+
+  //Create Canvas
+  auto c = new TCanvas("c", "c", 700, 700);
+  c->Divide(1,2, 0., 0.0);
+
+  //VARIABLES TO Normalize histogram (if desired)
+  Double_t scale; //Used to scale SIMC histograms by 1./h->Integral(data)
+  int dataI;  //data integral
+  int simcI;  //simc integral
+  
+  //Set Histo Aesthetics
+  hsimc->SetLineWidth(2);
+  hsimc->SetLineColor(kRed);
+
+  hdata->SetFillColorAlpha(kBlue, 0.35);
+  hdata->SetFillStyle(3004);
+
+  //Create new histo to store ratio
+  TH1F *hratio = (TH1F*) hdata->Clone();
+
+  //Set Histos Axis Label Size
+  hdata->GetYaxis()->SetLabelSize(0.06);
+  hratio->GetYaxis()->SetLabelSize(0.05);
+  hratio->GetXaxis()->SetLabelSize(0.06);
+  hdata->SetTitleSize(0.06, "XY");
+  hratio->SetTitleSize(0.06, "XY");
+
+  hratio->SetLineWidth(2);
+  hratio->SetLineColor(kBlack);
+
+  
+  c->cd(1);
+  //auto leg = new TLegend(0.1,0.8,0.28,0.9); 
+  auto leg = new TLegend(0.14,0.85,0.25,0.65); 
+
+  TPad* pad1 = (TPad*)c->GetPad(1);
+  pad1->SetBottomMargin(0.02);
+  pad1->SetRightMargin(0.02);
+  pad1->SetLeftMargin(0.1);
+  pad1->SetTopMargin(0.1);
[…]

### 2020-04-15 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/authorlist.tex
updated

--- 2020-02-12 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/author_listv2.tex
@@
 \author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
+\author{A.~Ahmidouch$^{4}$}        % . . .
 \author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
@@
 \author{S.~Basnet$^{3}$}           %Commissioning + SIDIS
-\author{V.~Berdnikov$^{11}$}        %Commissioning + SIDIS
+\author{V.V.~Berdnikov$^{11}$}        %Commissioning + SIDIS
+\author{J.~Bericic$^{15}$}          %SHMS Optics Contributor
 \author{H.~Bhatt$^{8}$}            %Commissioning + SIDIS
@@
 \author{M.~Chen$^{2}$}             %Commissioning ONLY
-\author{E.M.~Christy$^{12}$}          %Commissioning ONLY
+\author{M.E.~Christy$^{12}$}          %Commissioning ONLY
 \author{S.~Covrig$^{15}$}           %Commissioning + SIDIS               
 \author{K.~Craycraft$^{10}$}        %Commissioning + SIDIS
-%\author{S.~Danagoulian}     %NO MINIMUM SHIFTS
-%\author{D.~Day}             %ONLY DEC. 2017 Spec. Commissioning ?????? (should be included?)
+\author{S.~Danagoulian$^{4}$}            %NO MINIMUM SHIFTS. Contributed to detectros
+\author{D.~Day$^{2}$}             %ONLY DEC. 2017 Spec. Commissioning Contributed to Noble Gas Detector
 \author{M.~Diefenthaler$^{15}$}     %Commissioning + SIDIS
@@
 \author{A.~Karki$^{8}$}            %Commissioning + SIDIS  
-\author{C.~Keppel$^{15}$}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
+\author{C.E.~Keppel$^{15}$}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
 \author{A.~Khanal$^{1}$}           %Commissioning ONLY
@@
 \author{S.~Li$^{21}$}               %Commissioning ONLY
-\author{W.~Li$^{9}$}               %Commissioning ONLY
+\author{W.B.~Li$^{9}$}               %Commissioning ONLY
 \author{A.H.~Liyanage$^{12}$}       %Commissioning + SIDIS
@@
 \author{R.~Michaels$^{15}$}         %Commissioning + SIDIS
+\author{A.~Mkrtchyan$^{7}$}        %Commissioning ONLY
 \author{H.~Mkrtchyan$^{7}$}        %Commissioning ONLY
@@
 \author{S.~Park$^{18}$}             %Commissioning + SIDIS
+\author{C.F.~Perdrisat$^{9}$}            %College of William & Mary
 \author{E.~Pooser$^{15}$}           %Commissioning + SIDIS
@@
 %\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
+
 \affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
@@
 \affiliation{$^{6}$Temple University, Philadelphia, Pennsylvania 19122, USA}
-\affiliation{$^{7}$Yerevan Physics Institute, 375036 Yerevan, Armenia}
+\affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
 \affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
@@
 \affiliation{$^{24}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}
-
-\collaboration{for the Hall C Collaboration}
-\noaffiliation

### 2020-04-15 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/introduction.tex
updated

--- 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
@@
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
-The neutron carries a recoil momentum, $p_{r}$, equal in magnitude but opposite in direction
+The neutron carries a recoil momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction
 to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
 The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at $p_{r}>300$ MeV/c.\\
+electro-disintegration reaction at $p_{\mathrm{r}}>300$ MeV/c.\\
 \indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
-photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state which subsequently
-decays back into its ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
+photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state ($N^{\ast}$) which subsequently
+decays ($N^{\ast}N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
@@
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
-IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
+IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
 electro-production threshold.
@@
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
 Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).

### 2020-04-15 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/suggestions/simple.tex
updated

\title{E12-10-003 Hall C Collaborators Comments/Suggestions for PRL}
\author{
        Carlos Yero \\
                Department of Physics\\
        Florida International University\\
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\maketitle

\section{Collaborator: Douglas Higinbotham}
Dear Carlos, \\
\newline
\noindent Congratulations on getting this together! I suspect you are going to need to tighten up the comments about the plots on page 4 to meet the PRL length limit, but in general it look good.
One important comment, the colors in the plots are impossible for someone who is red-green color blind.  (i.e. 8$\%$ of men and  $\sim$1$\%$ of women).
Try copying (using a color picker) the colors from this games made by our own Huey-Wen Lin et al.:\\
\newline
\url{https://play.google.com/store/apps/details?id=com.gellab.quantum3}  \\
\newline
While they don’t look red, green, blue to the color blind, they are three distinct shades which means everyone will be able to tell the three curves apart.
\newline
For the data points, please use two different shapes along with the color and that should be fine.
(e.g. circle and square)
\newline
Best Wishes,
Douglas

\textcolor{blue}{\section{Collaborator: Dave Mack}}
\textcolor{blue}{
        0. KUDOS - What a great draft! It was hard work to find even one typo. \\
        \newline
        1.  GETTING INTO PRL - To increase the chance of getting accepted by PRL, you should add a few points to make a stronger case that
      	  this measurement is a qualitative advance over the Hall A data.  (You made that case already well wrt the Hall B data.) On page
	  2 when you compare the C measurements vs A/B, while you do give the specific Pmiss values, I would emphasize that you're "almost 
	  doubling the maximum Pmiss  compared to the Hall A measurement".  Also, you should mention in this same section the Hall A Q2 of 3.5
	  since that question is begged. (Unfortunately, the higher Q2 of the new C data sounds more like a quantitative than a qualitative
	  improvement, a fact echoed in your title.)  You could also try playing the "new facility" card,  adding one sentence to point out
	  that these are the first results using the new SHMS in Hall C. \\
          \newline
        2. SYSTEMATIC UNCERTAINTIES - The uncertainty analysis on page 3 assumes that SIMC 1) reproduces all the data resolutions for both
      	 spectrometers, and 2) reproduces the acceptance for both spectrometers. That might have been ~true for Hall C in 2005. My impression
	 is that both are optimistic for the SHMS at this time.  This could add another few percent plus another few percent in quadrature to
	 your total systematic error. No shame in that for a commissioning experiment, especially one with even larger statistical errors. \\
         \newline
        3. MISSING ENERGY CUT QUESTIONS - I'd like some clarification on the missing energy (ME) cut for the larger Pmiss settings. This seems to
     	be an exclusivity cut to suppress inelasticities like n+pi0 for example. Carlos showed a lot of representative plots for the 80 MeV/c
	settings in his recent talk, and said on slide 29 the non-PID plots would be the same at higher Pmiss.  But the ME cut is not a PID cut
	per se, and would have to be adjusted for each range of Pmiss .  Can I see those ME plots for the higher Pmiss settings? 
}

\textcolor{violet}{\section{Collaborator: Garth Huberg}}
\textcolor{violet}{
Dear Carlos, Werner and Mark, \\
\newline
Thanks for the opportunity to comment on the draft manuscript.  Overall, the 
data look very nice. Congratulations on getting this done so quickly. \\
\newline
Some comments/questions I have:\\
\newline
1. Since this is the first SHMS+HMS physics paper, I wonder if some additional 
analysis details, such as maybe a coincidence time or missing mass spectrum 
would be helpful, provided there is room. \\
\newline
2. Similarly, more information should be given on the ``standard cuts'' on page 2, 
lower right, given this is a new spectrometer.  e.g. how wide is the missing 
energy cut around the 2.22 MeV peak?  How wide is the coincidence time cut?  How 
large is the region in which SHMS reconstruction optics are well known? \\
\newline
3. Most readers prefer information to be quantitative than qualitative.  Thus, I 
suggest ``Very High'' and ``Large'' in the title be replaced with numeric ranges. 
Similarly, in the second last paragraph "very high neutron recoil momentum" 
should be quantified.\\
\newline
4. why is the 75deg setting not mentioned in the Abstract?\\
\newline
5. I'm kind of confused by the definition of missing energy at bottom left of 
page 2, Em=omega-Tp-Tr.  Since Tr is not measured, I was expecting Em=omega-Tp. 
How is Tr determined in this case?  Do you need to assume knowledge of the 
missing momentum and an exclusive reaction when computing Tr?\\
\newline
6. Fig 2, there is wasted space at the tops of panels a,c.  Can the y-axis ranges 
be reduced for these?\\
\newline
There are quite a few places where the English could be improved.  They are 
listed at the bottom of this message.\\
\newline
Regards, Garth \\
\newline
\underline{GRAMMATICAL CORRECTIONS}\\
\newline
TITLE: D in D(e,e'p)n should not be capitalized.  Either use 2H (as in the rest 
of the paper), or d.\\
\newline
ABSTRACT:\\
Remove New in the first line.
At these kinematic settings COMMA final state interactions...
to recent theoretical calculations COMMA where...\\
\newline
Page 1, LHS:\\
at the sub-Fermi distance (i.e. Fermi must be capitalized)
At such small inter-nucleon distances COMMA the...
are also important in determining whether COMMA or to what extent COMMA the...
nucleon/meson degrees of freedom is still valid COMMA before having...\\
\newline
Page 2, LHS:\\
a strong angular dependence with neutron recoil angles COMMA peaking at...
liquid deuterium target (LD2) --> shouldn't the 2 be subscripted? \\
\newline
Page 2, RHS:\\
covered a range of 2.4<q<3.2 GeV/c COMMA which is...
neutron recoil momentum (pr) measured (BY or IN, not ON) this experiment.
At these forward angles and large momentum --> both angles and momentum need to 
be plural, so change momentum to momentA
data WERE also taken at kinematics close to the deutron...
for which the reconstruction optics ARE well known...
true coincidence events and not ACCIDENTAL COINCIDENCES (accidentals is jargon)
background (mostly pions) COMMA and a...
For 2H(e,e'p)n COMMA the corrections were \\
\newline
Page 3, LHS:\\
The good agreement gives us confidence (IN not ON)\\
\newline
Page 3, RHS:\\
by J.M. SPACE Laget including FSI...
kinematics WAS calculated and used in the bin centering...
averaged OVER overlapping bins in pr.
Eqn 1: needs a COMMA\\
\newline
Page 4, LHS:\\
Hall A experiment [11] at Q2=3.5 (i.e. remove A)
at recoil momenta pr<300 MeV/c COMMA the cross sections...
In addition COMMA for theta\_nq=35deg COMMA they are dominated...
For theta\_nq=35 and 45 (Figs. 2a,b) COMMA the data...
At larger recoil momenta COMMA where...\\
\newline
Page 4, RHS:\\
Overall COMMA it is interesting...\\
\newline
Page 5, LHS:\\
At higher missing momentA, ...
Ref 6: 4.0 GeV (not gev)\\
}
\textcolor{red}{\section{Collaborator: Florian Hauenstein}}
\textcolor{red}{
1. The HallA data is hard to distinguish in color code from the lines. Maybe try some orange/red color and also 'boxes' instead of 'circles'
   to indicate that it is a different data. Maybe also open boxes.\\
\newline
2. You describe the radiative and bin-centering corrections but not their corresponding systematic uncertainties.\\
\newline
3. Is pr=1.01GeV/c exactly the upper limit? If so it would be good to indicate it in the plots by using the horizontal size of the last bin
   or so. If not can't you write p\_r$\sim$1GeV/c?\\
\newline
4. I hope you will add a Table with all data points and their individual uncertainties in an extended information for the paper. The same holds
   for an equation with all corrections.\\
\newline
5. In a lot of cases in the text, there is a space missing between text and citation.\\
\newline
6. The explanation of the correction for efficiencies is weird given the numbers: tracking and live time is high but loss and boiling is low.
   I assume that the corrections are applied differently - some per division and some per multiplication? It is difficult to understand what
   is meant.\\
\newline
7. The recoil factor f\_Rec is not really explained. Maybe add a reference.\\
\newline
8.  It is not completely clear what one 'data set' is where you add later errors in quadrature.\\
\newline
9. Missing Reference to SIMC and HMS/SHMS spectrometers\\
\newline
10. When GEA is described, I would think more of $\theta_{nq} < 40$ than $\theta_{nq} \sim 40$ for low FSI. The same holds for $\theta_{nq} > 120$ instead
    of $\theta_{nq} \sim 120$\\
\newline
11. In the beginning when you cite references 1-4, you probably should add Barak's Nature paper (B. Schmookle, Nature 566, 354 (2019)) and
    Or's and Larry's Review (O. Hen et al., Rev.Mod Phys 89, 045002 (2017))\\
\newline
12. I would add one more sentence at the end, given an outlook on the next steps/experiments.\\
}
\end{document}

### 2020-04-15 UTILITIES_CODES/codes/deep_codes/compare_deep.C

@@ -148,7 +148,7 @@ void compare_deep(int pm, int set, int thnq)
   //hist_ratio(data_hdelta, simc_hdelta_fsi, "HMS #delta [%]", "Counts", "HMS #delta");
 
   //Plot Only Data Histos
-  plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts", "SHMS Calorimeter Total Normalized Energy", "logy");
+  //plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts", "SHMS Calorimeter Total Normalized Energy", "logy");
   //plot_hist(data_CoinTime, "Coincidence Time [ns]", "Counts", "Coincidence Time", "logy");
 
 

### 2020-04-15 UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -129,7 +129,7 @@ void plot_hist(TH1F *hist, TString xlabel="", TString ylabel="", TString title="
   gStyle->SetLegendTextSize(0.03);
 
   //Create Canvas
-  TCanvas *c = new TCanvas("c", "c", 900, 700);
+  TCanvas *c = new TCanvas(title, "c", 900, 700);
   c->SetFrameLineWidth(2);
   //VARIABLES TO Normalize histogram (if desired)
   Double_t scale; //Used to scale SIMC histograms by 1./h->Integral(data)
@@ -185,7 +185,7 @@ void plot_hist(TH1F *hist, TString xlabel="", TString ylabel="", TString title="
 
 //---------------------
 
-void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", TString title="")
+void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", TString title="", TString set_logy="")
 {
 
   gStyle->SetOptStat(0);
@@ -215,25 +215,27 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
   hdata->GetYaxis()->SetLabelSize(0.04);
   hdata->GetXaxis()->SetLabelSize(0.04);
   hdata->SetTitleSize(0.04, "XY");
-
- 
-  //auto leg = new TLegend(0.1,0.8,0.28,0.9); 
-  TLegend *leg = new TLegend(0.14,0.88,0.25,0.73); 
-
-  hdata->Draw("samehistE0");
-  hsimc->Draw("samesE0");
+  
   hdata->SetTitle(title);
 
   hdata->GetYaxis()->SetTitle(ylabel);
   hdata->GetXaxis()->SetTitle(xlabel);
   hdata->GetYaxis()->CenterTitle();
   hdata->GetXaxis()->CenterTitle();
-  hdata->GetYaxis()->SetRangeUser(0,hdata->GetMaximum()+0.6*hdata->GetMaximum());
+  hdata->GetYaxis()->SetRangeUser(0.001,hdata->GetMaximum()+0.6*hdata->GetMaximum());
   hdata->GetXaxis()->SetTitleOffset(1.);  
   hdata->GetYaxis()->SetTitleOffset(1.);
   hdata->SetLabelFont(22, "XY");
   hdata->SetTitleFont(22, "XY");
 
[…]

### 2020-05-07 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated

--- 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the the coincidence of these two signals. \\
+For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 measured in this experiment.
-As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.
+As a result, most of the virtual photon momentum is transferred to the proton, which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.
 At these forward angles and large momenta transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
@@
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
-and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
+and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
@@
 target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all momentum settings. \\
-\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using J.
-Arrington's proton form factor parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
+\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
 model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).\\
@@
 as an overall normalization constant to the final result.\\
-\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
-and added in quadrature for overlapping $p_{r}$ bins. For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
+%\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
+%and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
+\indent The systematic uncertainties on the cross section due to systematic error on the absolute beam energy and spectrometer angle/momentum settings were
+determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
@@
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
-The SIMC simulation code was used for these calculations with the Deuteron Model by J.M.
-Laget including FSI \cite{LAGET2005}.
+The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.
 For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics was calculated and used in the bin centering correction factor defined as:
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin.
-The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the J.M.
-Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
-\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
+over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and 
 \onecolumngrid
@@
 \twocolumngrid
+\noindent FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
-Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\
+Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the PWIA cross section from the scattering of a proton in the deuteron. \\
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
 $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ .
+For the two highest settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
-The good agreement between the Hall A and C data at lower $p_{r}$
+The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$
 gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
@@
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential  (blue) were  by J.M. Laget \cite{LAGET2005}.\\
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential (blue) were by Laget \cite{LAGET2005}.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
@@
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
-behaviour (smaller falloff) that overshadows any possibility of extracting the momentum distributions.\\
+behavior (smaller fall-off) that overshadows any possibility of extracting the momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
@@
 missing momenta typically above 800 MeV/c for the CD-Bonn
-\begin{figure}[t!]
+\begin{figure}[!t]
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
@@
 calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{\circ}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
-\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
+At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
+\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
 This behavior of the data is new
@@
 \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
-At $p_{\mathrm{r}}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles.
+At $p_{\mathrm{r}}>300$ MeV/c, the data were statistically limited as our focus was on the smaller recoil angles.
 The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
@@
 \indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
-very high neutron recoil momenta ($p_{r}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
-short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
+very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
+short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
 Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
@@
 \indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
-momentum region ($p_{r}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
+momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
@@
 under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
-under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.
+under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
 

### 2020-05-07 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/introduction.tex
updated

@@
 Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-having to include explicit quark degree of freedoms, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
+having to include explicit quark degrees of freedoms, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
 As of the present time, there are only a few nuclear physics experiments for
@@
 \cite{sargsian_2015}) have helped quantify the contributions
-from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
-\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015} which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
+from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
 GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$.
@@
 Both
-experiments determined that the cross-sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
+experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
 at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
@@
 \indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
-For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
+For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
 and $45\pm5^{\circ}$ compared to  $\theta_{nq}=75\pm5^{\circ}$.
@@
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
-Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
 At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

### 2020-05-07 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/prl.tex
updated

--- 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
@@
 \widetext
-\leftline{Version 04 as of \today}
+\leftline{Version 05 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
 \leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by April 10, 2020}
+\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by May 01, 2020}
 \centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
 %\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
-\title{Deuteron Electro-Disintegration at Very High Missing Momenta}
+%\title{Deuteron Electro-Disintegration up to $\sim$ 1 GeV/c Missing Momentum}
+\title{Deuteron Cross Section Measurements up to $p_{\mathrm{r}}\sim1$ GeV/c Recoil Momentum}
+
 \input authorlist.tex
@@
 $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
-transfer $\vec q$. The new data agrees well with previous data which reached $p_{r}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
+transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
 meson exchange currents (MEC) and isobar configurations (IC) are
@@
 theoretical calculations, where a significant disagreement for
-missing momenta $p_{r}>700$ MeV/c has been observed. 
+missing momenta $p_{\mathrm{r}}>700$ MeV/c has been observed. 
 \end{abstract}

### 2020-05-07 UTILITIES_CODES/codes/THESIS_plots/Rad_BC_corr_plots/check_RCBC_ratio.py

@@ -1,0 +1,327 @@
+#This code check the ratio of norad / rad for PWIA and FSI
+
+from LT.datafile import dfile
+import LT.box as B
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import rc
+import matplotlib.ticker as tic
+import sys
+import os
+import numpy.ma as ma
+
+'''
+#Set Global Param
+params = {'legend.fontsize': 14,
+          'lines.markersize': 9.0,
+           'legend.markerscale':1.,
+          'figure.figsize': (9, 7),
+         'axes.labelsize': 20,
+         'axes.labelweight': 'bold',          
+         'axes.titlesize':22,
+          'axes.titleweight':'bold',
+          'axes.linewidth':2,
+         'xtick.major.width':2,
+          'ytick.major.width':2,          
+         'xtick.labelsize':20,
+          'ytick.labelsize':20} 
+           
+plt.rcParams.update(params)
+'''
+#Use latex commands (e.g. \textit ot \textbf)
+rc('text', usetex=True)
+#Set default font to times new roman
+font = {'family' : 'Times New Roman',
+        'weight' : 'bold',
+        'size'   : 14
+}
+plt.rc('font', **font)
+
+def convert2NaN(arr=np.array([]), value=0):
+    #method to convert a specified value in a array to nan (not a number)
+    
+    for i in enumerate(arr):
+        if arr[i[0]]==value:
+            arr[i[0]] = np.nan
+    return arr
+
+
+#User Input (Usage: python check_RC_ratio.py 80 1 )
+pm_set = int(sys.argv[1])
+data_set = int(sys.argv[2])
+
+#csfont = {'fontname':'Times New Roman'}
+
+plt.rcParams["font.family"] = "Times New Roman"
+
+#Read data file
+if pm_set==80:
+    fname = './pm%i_laget_RCratio.txt' % (pm_set)
+else:
[…]

### 2020-05-07 UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -201,8 +201,8 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
 
   //VARIABLES TO Normalize histogram (if desired)
   Double_t scale; //Used to scale SIMC histograms by 1./h->Integral(data)
-  int dataI;  //data integral
-  int simcI;  //simc integral
+  double dataI;  //data integral
+  double simcI;  //simc integral
   
   //Set Histo Aesthetics
   hsimc->SetLineWidth(2);
@@ -227,12 +227,13 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
   hdata->GetYaxis()->SetTitleOffset(1.);
   hdata->SetLabelFont(22, "XY");
   hdata->SetTitleFont(22, "XY");
-
+  
   //auto leg = new TLegend(0.1,0.8,0.28,0.9); 
   TLegend *leg = new TLegend(0.14,0.88,0.25,0.73); 
   if(set_logy=="logy"){
     c->SetLogy();
   }
+  
   hdata->Draw("samehistE0");
   hsimc->Draw("samesE0");
   
@@ -243,9 +244,9 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
   double R = (float)dataI / simcI;
   double R_err = R * sqrt(pow(dataI_err/dataI,2) + pow(simcI_err/simcI,2));
   
-  leg->AddEntry(hdata,Form("Data | Integral: %d", dataI),"f");
-  leg->AddEntry(hsimc,Form("SIMC | Integral: %d", simcI));
-  leg->AddEntry((TObject*)0, Form("Ratio: %.3f #pm %.3f", R, R_err), "");
+  leg->AddEntry(hdata,Form("Data | Integral: %.5f", dataI),"f");
+  leg->AddEntry(hsimc,Form("SIMC | Integral: %.5f", simcI));
+  leg->AddEntry((TObject*)0, Form("Ratio: %.5f #pm %.5f", R, R_err), "");
   leg->Draw();
 
 

### 2020-05-07 UTILITIES_CODES/codes/radiative_corr_ratio/check_RCBC_ratio.py

@@ -1,313 +1,0 @@
-#This code check the ratio of norad / rad for PWIA and FSI
-
-from LT.datafile import dfile
-import LT.box as B
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.ticker as tic
-import sys
-import os
-import numpy.ma as ma
-
-#Set Global Param
-params = {'legend.fontsize': 'large',
-          'lines.markersize': 9.0,
-           'legend.markerscale':1.,
-          'figure.figsize': (9, 7),
-         'axes.labelsize': 20,
-         'axes.labelweight': 'bold',          
-         'axes.titlesize':22,
-          'axes.titleweight':'bold',
-          'axes.linewidth':2,
-         'xtick.major.width':2,
-          'ytick.major.width':2,          
-         'xtick.labelsize':20,
-          'ytick.labelsize':20} 
-           
-plt.rcParams.update(params)
-
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#User Input (Usage: python check_RC_ratio.py 80 1 )
-pm_set = int(sys.argv[1])
-data_set = int(sys.argv[2])
-
-#csfont = {'fontname':'Times New Roman'}
-
-plt.rcParams["font.family"] = "Times New Roman"
-
-#Read data file
-if pm_set==80:
-    fname = './pm%i_laget_RCratio.txt' % (pm_set)
-else:
-    fname = './pm%i_laget_RCratio_set%i.txt' %(pm_set, data_set)
-
-f = dfile(fname)
-
-#Get Relevant headers to plot
-pm = np.array(f['yb'])    #missing momentum bin
-thnq = np.array(f['xb'])  #theta_nq bin
-
-
-
-#define function to get RC ratio
-def get_RC_ratio(pm_set, data_set, model=''):
-
-    
[…]

### 2020-05-07 publications/supplemental_materials/get_Xsec_err.py

@@ -1,7 +1,7 @@
 import numpy as np
 from interpolate_ff import *
 
-#This code defined the H(e,e'p) elastic cross section in terms of
+#This code defines the H(e,e'p) elastic cross section in terms of
 #the electric and magnetic form factors. Then apply error propagation
 #in terms of the form factors to get uncertainty in cross section at thw
 #gven beam energy, elecrtron angle and momentum.
@@ -52,6 +52,7 @@ def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
     #derivatives of cross sectio w.r.to form factors
     dsig_dGEp = sigMott * ( (2.*GEp + tau*GMp**2) / (1. + tau))
     dsig_dGMp = sigMott * ( (GEp**2 + 2.*tau*GMp) / (1. + tau) + 4.*tau*GMp*np.tan(th_e/2.)**2 )
+
     #uncertainty in form factors
     dGEp = dGEp_GD * GD
     dGMp = dGMp_muGD * muGD
@@ -65,15 +66,21 @@ def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
 #Heep Kinematics
 dtr = np.pi / 180.
 Eb = 10.6005   #beam
-Ef = 8.5342488  #e- momentum
+#Ef = 8.5342488  #e- momentum
 th_e = np.array([12.194, 13.93, 9.928, 8.495])  #e- angle
+
+#This selection of e- final momentum is determined by selectin
+#the th_e bin +/- 0.01 deg, i.e. for [13.92,13.94], 
+Ef = np.array([8.4407, 7.951, 9.0603, 9.425])
+
 Q2 = 4.*Eb*Ef*np.sin(th_e*dtr/2.)**2   #central Q2 for given kinematics
+
 run = np.array([3288, 3371, 3374, 3377])
 
 for i in range(len(th_e)):
     
     ith_e = th_e[i]
-    kf = Ef
+    kf = Ef[i]
     iQ2 = Q2[i] 
 
     
@@ -87,7 +94,7 @@ for i in range(len(th_e)):
     print('Run Number: %i'%(run[i]))
 
     print('Beam Energy: ', Eb,' GeV')
-    print('electron momentum: ', Ef, ' GeV')
+    print('electron momentum: ', kf, ' GeV')
[…]

### 2020-05-18 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/introduction.tex
updated

@@
-The deuteron is the only bound two-nucleon  system and serves as a starting point to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
-not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
+The deuteron is the only bound two-nucleon system and serves as an ideal framework to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
+practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
 nucleons begin to overlap.
-This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
+The dynamics in this short distance region is directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
 Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
@@
 which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
-\indent  Within the PWIA, the virtual photon couples to
+\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
+electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the PWIA, the virtual photon couples to
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
 The neutron carries a recoil momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
-The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at $p_{\mathrm{r}}>300$ MeV/c.\\
+to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
 \indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
-photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state ($N^{\ast}$) which subsequently
-decays ($N^{\ast}N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
+photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
+decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
-\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
+\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively\cite{sargsian_2015}.
 The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
-IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance
+IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
 electro-production threshold.
@@
 This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{\circ}$ and $\theta_{nq}\sim120^{\circ}$.
-Since at $\theta_{nq}\sim120^{\circ}$ IC are not negligible, $x_{\mathrm{Bj}}>1$ (or equivalently $\theta_{nq}\sim40^{\circ}$) is the preferred choice to suppress IC as well as FSI.
-\\
+Because at
+$\theta_{nq}\sim120^{\circ}$ ($x_{\mathrm{Bj}}<1$) IC are not negligible, the $x_{\mathrm{Bj}}>1$ ($\theta_{nq}\sim40^{\circ}$) kinematics are the preferred choice to suppress IC as well as FSI. \\
 %---------D(e,e'p) Experiments at Q2 < 1-------- 
@@
 However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions
-which are therefore dominated by  FSI, MEC and IC for missing momenta above $\sim 300$ MeV/c. \\
-\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$.
-For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
+which are therefore dominated by  FSI, MEC and IC for $p_{\mathrm{r}}$ above $\sim 300$ MeV/c. \\
+\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$)
+reaching recoil momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$. For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
 and $45\pm5^{\circ}$ compared to  $\theta_{nq}=75\pm5^{\circ}$.
@@
 dominance at $\theta_{nq}=75^{\circ}$ \cite{PhysRevLett.107.262501}. \\
-\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
+\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment \cite{PhysRevLett.107.262501} and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
 to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.

### 2020-05-19 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/latexdiff/body.tex
added latexdiff: utility to compare different versions of a latex file to track changes

--- 2020-05-07 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
+For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
@@
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential (blue) were by Laget \cite{LAGET2005}.\\
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models significantly differ from the CD-Bonn.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
+AV18 models increasingly differ from the CD-Bonn.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
 The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
@@
 \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).
-The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
-to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\hyperref[fig:fig1]{1(b)}).\\
+\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18  potentials is 
+how the NN potential is modeled based on the empirical NN scattering data.
+The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
+nucleon-neson-meson couplings are constrained to describe the NN scattering phase shifts
+extracted from the data. The interaction potential represents the static limit of 
+this potential. Paris and AV18 potentials are phenomenological in which the 
+Yukawa type interaction is introduced and parameters are fitted to describe the 
+same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
+potentials is that the former predicts much softer repulsive interaction at short distance which 
+results in a less high momentum component in the deuteron wave function in the momentum space.
+%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
+%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
+%groups to describe the NN potential.
+The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
-behavior (smaller fall-off) that overshadows any possibility of extracting the momentum distributions.\\
+behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
@@
 region where recoil angles are small and FSI are reduced. \\
-\indent At larger recoil momenta, where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
+\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
 missing momenta typically above 800 MeV/c for the CD-Bonn
@@
 \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
-At $p_{\mathrm{r}}>300$ MeV/c, the data were statistically limited as our focus was on the smaller recoil angles.
+At $p_{\mathrm{r}}>300$ MeV/c and $\theta_{nq}=75^{\circ}$, the data were statistically limited as our focus was on the smaller recoil angles.
 The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
 of FSI at the smaller recoil angles. \\
-\indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
+\indent To summarize, this experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
 very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
@@
 Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momenta, however, all models were unable to describe the data. \\
+At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. \\
 \indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing

### 2020-05-19 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/latexdiff/bodyold.tex
added latexdiff: utility to compare different versions of a latex file to track changes

--- 2020-04-09 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
@@
 \indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
-and added in quadrature for overlapping $p_{r}$ bins. For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
+and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
@@
 $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest settings ($p_{r}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{r}$ .
+For the two highest settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
-The good agreement between the Hall A and C data at lower $p_{r}$
+The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$
 gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
@@
 At $\theta_{nq}=45^{\circ}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
-\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_r$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
+\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
 This behavior of the data is new
@@
 \indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
-very high neutron recoil momenta ($p_{r}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
+very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
 short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.

### 2020-05-19 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated PRL

@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential (blue) were by Laget \cite{LAGET2005}.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
+The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models significantly differ from the CD-Bonn.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
+AV18 models increasingly differ from the CD-Bonn.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
 The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
@@
 \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).
-The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
-to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\hyperref[fig:fig1]{1(b)}).\\
+\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
+how the NN potential is modeled based on the empirical NN scattering data.
+The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
+nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
+extracted from the data. The interaction potential represents the static limit of 
+this potential. Paris and AV18 potentials are phenomenological in which the 
+Yukawa type interaction is introduced and parameters are fitted to describe the 
+same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
+potentials is that the former predicts much softer repulsive interaction at short distance which 
+results in a smaller high momentum component in the deuteron wave function in momentum space.
+%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
+%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
+%groups to describe the NN potential.
+The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
-behavior (smaller fall-off) that overshadows any possibility of extracting the momentum distributions.\\
+behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
@@
 \indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
-to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
+to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\
-\indent At larger recoil momenta, where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
+\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
 missing momenta typically above 800 MeV/c for the CD-Bonn
@@
 Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momenta, however, all models were unable to describe the data. \\
-\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
-momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
+At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
+Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
+momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab

### 2020-05-19 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/prl.tex
updated PRL

@@
 \leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by May 01, 2020}
+\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by June 01, 2020}
 \centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
 %\title{Deuteron Electro-Disintegration up to $\sim$ 1 GeV/c Missing Momentum}
-\title{Deuteron Cross Section Measurements up to $p_{\mathrm{r}}\sim1$ GeV/c Recoil Momentum}
+\title{Probing the Deuteron at Very Large Internal Momenta}
 
@@
 \begin{abstract}
-$^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.0 GeV/c. The data have been obtained at fixed neutron recoil angles
-$\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
-transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
-meson exchange currents (MEC) and isobar configurations (IC) are
-suppressed and the plane wave impulse approximation (PWIA) provides the
-dominant cross section contribution. The new data are compared to recent
-theoretical calculations, where a significant disagreement for
-missing momenta $p_{\mathrm{r}}>700$ MeV/c has been observed. 
+  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
+  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
+  transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
+  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
+  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
+  theoretical calculations, where a significant disagreement for missing momenta $p_{\mathrm{r}}>700$ MeV/c is observed. 
 \end{abstract}

### 2020-06-13 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
added J.W.V.Orden calculations

@@
 \indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models increasingly differ from the CD-Bonn.
+AV18 models increasingly differ from the CD-Bonn calculation.
 In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
@@
 as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
-was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
+thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful
+discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
 under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship

### 2020-06-13 UTILITIES_CODES/codes/THESIS/Rad_BC_corr_plots/check_RCBC_ratio.py

@@ -296,6 +296,8 @@ for i, ithnq in enumerate(thnq_arr):
     B.pl.figure(i)
 
     #Plot BC ratio PWIA and FSI
+    B.pl.hlines(1.1, 0., 1.2, linestyles='dashed', label=r'$\pm 10\%$' )
+    B.pl.hlines(0.9,0., 1.2, linestyles='dashed')
     B.plot_exp(pm[thnq==ithnq], BC_fact_pwia_80[thnq==ithnq], BC_fact_pwia_80_err[thnq==ithnq], marker='o', color='k', label='PWIA')
     B.plot_exp(pm[thnq==ithnq], BC_fact_pwia_580s1[thnq==ithnq], BC_fact_pwia_580s1_err[thnq==ithnq], marker='s', color='b', logy=False, label='PWIA')
     B.plot_exp(pm[thnq==ithnq], BC_fact_pwia_580s2[thnq==ithnq], BC_fact_pwia_580s2_err[thnq==ithnq], marker='^', color='r', logy=False, label='PWIA')
@@ -303,7 +305,8 @@ for i, ithnq in enumerate(thnq_arr):
     B.plot_exp(pm[thnq==ithnq], BC_fact_pwia_750s2[thnq==ithnq], BC_fact_pwia_750s2_err[thnq==ithnq], marker='p', color='m', logy=False, label='PWIA')
     B.plot_exp(pm[thnq==ithnq], BC_fact_pwia_750s3[thnq==ithnq], BC_fact_pwia_750s3_err[thnq==ithnq], marker='D', color='c', logy=False, label='PWIA')
 
-     
+    B.pl.hlines(1.2, 0., 1.2, linestyles='dashdot', color='r', label=r'$\pm 20\%$')
+    B.pl.hlines(0.8,0., 1.2, linestyles='dashdot', color='r')
     B.plot_exp(pm[thnq==ithnq], BC_fact_fsi_80[thnq==ithnq],  BC_fact_fsi_80_err[thnq==ithnq], marker='o', markerfacecolor='w', color='k', label='FSI, 80 (set1)')
     B.plot_exp(pm[thnq==ithnq], BC_fact_fsi_580s1[thnq==ithnq],  BC_fact_fsi_580s1_err[thnq==ithnq], marker='s',  markerfacecolor='w',color='b', label='FSI, 580 (set1)')
[…]

### 2020-06-13 UTILITIES_CODES/codes/THESIS/make_prl_plots.py

@@ -192,7 +192,75 @@ def read_digitized_data():
     return[pm_pwia_dgt_lower, pm_fsi_dgt_lower, f_pwia_lower(pm_pwia_dgt_lower), f_pwia_upper(pm_pwia_dgt_lower), f_fsi_lower(pm_fsi_dgt_lower), f_fsi_upper(pm_fsi_dgt_lower)]
 
     
+
+def read_JWVO_data(ithnq=0, theory='', fofa='', model='', pmavg=np.array([])):
     
+    #Read theoretical cross sections from W.V.Orden
+    #The cross sections used the WJC2, AV18 and CD-Bonn models
+
+    fname = '../deep_data_files/JWVOrden_calculations/JWV_Orden_redXsec_%i_deg_AVERAGE.txt' % (ithnq)
+
+    f = dfile(fname)
+    
+    pm_avg = np.array(f['pm_avg'])                       #average missing momentum (GeV/c)
+    WJC2_GKex05_PWBA_red = np.array(f['WJC2_GKex05_PWBA_red'])
+    WJC2_GKex05_DWBA_red = np.array(f['WJC2_GKex05_DWBA_red'])
+    WJC2_AMT_PWBA_red = np.array(f['WJC2_AMT_PWBA_red'])
+    WJC2_AMT_DWBA_red = np.array(f['WJC2_AMT_DWBA_red'])
+
+    AV18_GKex05_PWBA_red = np.array(f['AV18_GKex05_PWBA_red'])
+    AV18_GKex05_DWBA_red = np.array(f['AV18_GKex05_DWBA_red'])
+    AV18_AMT_PWBA_red = np.array(f['AV18_AMT_PWBA_red'])
+    AV18_AMT_DWBA_red = np.array(f['AV18_AMT_DWBA_red'])
+
+    CD_GKex05_PWBA_red = np.array(f['CD_GKex05_PWBA_red'])
+    CD_GKex05_DWBA_red = np.array(f['CD_GKex05_DWBA_red'])
+    CD_AMT_PWBA_red = np.array(f['CD_AMT_PWBA_red'])
+    CD_AMT_DWBA_red = np.array(f['CD_AMT_DWBA_red'])
+    
+    #interpolate
+    f_WJC2_GKex05_PWBA_red = interp1d(pm_avg, WJC2_GKex05_PWBA_red, fill_value='extrapolate', kind='linear')  
[…]

### 2020-06-13 UTILITIES_CODES/codes/THESIS/plot_momentum_dist.py

@@ -13,8 +13,8 @@ from matplotlib import *
 from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
 
 
-matplotlib.use('Agg')
-plt.ioff() # prevent plots froms displaying
+#matplotlib.use('Agg')
+#plt.ioff() # prevent plots froms displaying
 #Use latex commands (e.g. \textit ot \textbf)
 rc('text', usetex=True)
 #Set default font to times new roman
@@ -37,10 +37,10 @@ def convert2NaN(arr=np.array([]), value=0):
     return arr
 
 
-#Conversion factor:  1 fm = 1/ (197 MeV),   
+#Conversion factor:  1 fm = 1/ (197.3 MeV),   
 #The reduced cross section is in MeV^-3 units
 MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
+GeV2fm = 0.1973**3   #conver GeV^-3 to fm^3
 #========User Input (Dir. Name to store output)=======
 #usage: ipython plot_momentum_dist.py
 
@@ -157,6 +157,18 @@ tot_err_4to5 = np.array(dfile(fname_Q2_4to5)['tot_err'])              #overall e
 
 
 #Read Digitized Data from W.V.Orden (2014) article
+fname_digit_CDBonn = './digitized_data/CD_Bonn_digitized.data'
+fname_digit_WJC1 = './digitized_data/WJC1_digitized.data'
+
+CDBonn_dgt = dfile(fname_digit_CDBonn)
+WJC1_dgt = dfile(fname_digit_WJC1)
+
+pm_cd_dgt = np.array(CDBonn_dgt['xpw'])                       #digitized CD-Bonn missing momentum [GeV/c]
+rho_cdbonn = np.array(CDBonn_dgt['ypw']) * GeV2fm / (8.*np.pi**3)   
+
+pm_wjc1_dgt = np.array(WJC1_dgt['xpw'])                       #digitized WJC1 missing momentum [GeV/c]
+rho_wjc1 = np.array(WJC1_dgt['ypw']) * GeV2fm / (8.*np.pi**3)
+
 #This data shows a band with lower/upper limits of calculations for PWIA and FSI
 fname_digit_pwia = './digitized_data/PWIA_digitized_final.txt'
 fname_digit_fsi = './digitized_data/FSI_digitized_final.txt'
[…]

### 2020-06-13 UTILITIES_CODES/codes/deep_data_files/JWVOrden_calculations/calc_redXsec.py

@@ -1,0 +1,207 @@
+import LT.box as B
+from LT.datafile import dfile
+import numpy as np
+from deForest_Xsec import *   #import deForest sig_cc1, mott, GMp, GEp functs.
+from itertools import groupby
+
+# some constants
+dtr = np.pi/180.
+hbarc = 197.327053       #MeV * fm
+
+#particle masses (MeV)
+MP = 938.272 
+MN = 939.566 
+MD = 1875.61 
+me = 0.51099 
+
+
+thnq = 75
+#read data from Wally V. Orden calculations
+f = dfile('./%i_deg.data' % (thnq) )
+
+#read avg. kinematics to calculate the recoil factors to determine the reduced cross sections
+ib = np.array(f['Nr'])
+pm_avg = np.array(f['pm_avg']) * 1000.  #recoil neutron momentum [MeV/c]
+Eb = np.array(f['Eb']) #beam energy, MeV
+Q2 = np.array(f['Q2']) * 1e6   #Q2, MeV^2
+x = np.array(f['x'])   #X-Bjorken
+nu = Q2 / (2*MP*x)    #nu = Eb - kf, energy transfer MeV
+kf = Eb - nu          #final electron energy (or momentum), MeV
+th_e = np.array(f['th_e'])  #e- scattering angle (deg)
+q = np.sqrt(Q2 + nu*nu)  #magnitude of 3-momentum transfer, MeV
+pf = np.array(f['pf'])    #final proton momentum , MeV
+ph_pq = np.array(f['phi'])   #deg
+
+cphi_pq = np.cos(ph_pq * dtr)
+theta_q = np.arccos((Eb**2 + q**2 - kf**2) / (2.*Eb*q))   #radians
+theta_pq = np.arccos((pf**2 + q**2 - pm_avg**2)/(2.*pf*q))   #radians
+theta_nq = np.arccos((q - pf*np.cos(theta_pq))/pm_avg)       #radians
+theta_p = theta_q + theta_pq                             #radians
+
[…]

### 2020-06-26 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
updated

--- 2020-06-13 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 \begin{figure}
-\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
+\includegraphics[scale=0.46]{prl_plots/PRL_plot1_WJC2.pdf}
 \caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
 with a bin width of $\pm 5^{\circ}$.
-The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
-AV18(green) and CD-Bonn(magenta) NN potentials.}
+The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
+AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}
 \label{fig:fig1}
@@
 The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials.
+cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
+For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
+used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
+WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
@@
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models increasingly differ from the CD-Bonn calculation.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
-The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
-In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
-\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).\\
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
+AV18 and WJC2 models increasingly differ from the CD-Bonn calculation.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
+the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$.
+The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
+In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
+(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
+\indent Moreover, in spite of the partial agreement between data and theory, between $p_{\mathrm{r}} \sim 0.55$ and 1.0 GeV/c, all models exhibit a
+steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
+4.241 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation.
+\\
 \indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
@@
 \begin{figure}[!t]
-\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
+\includegraphics[scale=0.5]{./prl_plots/PRL_plot2_WJC2.pdf}
 \caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
@@
 At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
-\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
-This behavior of the data is new
-and additional data in this kinematic region are necessary to improve the statistics. \\
+\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a
+region where FSI are still relatively small $(<30\%)$. This behavior of the data is new and additional data in this kinematic region are necessary
+to improve the statistics. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig.
@@
 short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
-Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
+Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
 At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 

### 2020-06-26 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/latexdiff/body.tex
updated

@@
 The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials.
+cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
+For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
+used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
+WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
 The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models increasingly differ from the CD-Bonn.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
-The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
-In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
-\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).\\
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
+AV18 and WJC2 models increasingly differ from the CD-Bonn calculation.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
+the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$.
+The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
+In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
+(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
+\indent Moreover, in spite of the partial agreement between data and theory, at $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, the data exhibits a smaller
+fall-off compared to all models which was quantified by a linear fit to both the data and each of the PWIA calculations. A difference of at least
+4.241 standard deviations was found which corresponds to a probability of $1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 
 \indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
@@
 The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
-nucleon-neson-meson couplings are constrained to describe the NN scattering phase shifts
+nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
 extracted from the data. The interaction potential represents the static limit of 
@@
 potentials is that the former predicts much softer repulsive interaction at short distance which 
-results in a less high momentum component in the deuteron wave function in the momentum space.
+results in a smaller high momentum component in the deuteron wave function in momentum space.
 %The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
@@
 \indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
-to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
+to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\
@@
 short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
-Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. \\
-\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
-momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
+Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
+At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
+Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
+momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
 as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
-was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
+thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful
+discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
 under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
updated

@@
 \begin{figure}
-\includegraphics[scale=0.46]{prl_plots/PRL_plot1_WJC2.pdf}
+\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
@@
 The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
+cross sections using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
-For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
-used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
-WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
-is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
-AV18 and WJC2 models increasingly differ from the CD-Bonn calculation.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
-the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$.
-The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
-In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
-(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
-\indent Moreover, in spite of the partial agreement between data and theory, between $p_{\mathrm{r}} \sim 0.55$ and 1.0 GeV/c, all models exhibit a
-steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
-4.241 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation.
-\\
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA, referred to as MS, and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach, referred to as JML.
+For the WJC2 (orange) potential, the calculations were carried out by Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
+The calculations
+used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
+JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
 \indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
@@
 extracted from the data. The interaction potential represents the static limit of 
-this potential. Paris and AV18 potentials are phenomenological in which the 
+this potential. Paris and AV18 are purely phenomenological potentials where a 
 Yukawa type interaction is introduced and parameters are fitted to describe the 
-same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
-potentials is that the former predicts much softer repulsive interaction at short distance which 
+same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18 
+potentials is that the former predicts a much softer repulsive interaction at short distance which 
 results in a smaller high momentum component in the deuteron wave function in momentum space.
-%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
-%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
-%groups to describe the NN potential.
 The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
+The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+is well known and common to all modern potentials. \\
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the JML,
+MS AV18 and JVO models increasingly differ from the MS CD-Bonn calculation.
+In this region, the JML and MS AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
+the JVO PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$.
+The MS CD-Bonn cross sections in contrast are generally smaller than the JML, MS AV18 and JVO in this region.
+In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
+(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
+\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a
+steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
+4.2 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation.
+\\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
@@
 deuteron momentum distribution calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{\mathrm{red}}$) \cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
-\indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
+\indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the MS CD-Bonn PWIA calculation for recoil momenta up
 to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic
@@
 \indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
-missing momenta typically above 800 MeV/c for the CD-Bonn
+missing momenta typically above 800 MeV/c for the MS CD-Bonn
 \begin{figure}[!t]
-\includegraphics[scale=0.5]{./prl_plots/PRL_plot2_WJC2.pdf}
+\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
 \caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
-The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
+The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
 \label{fig:fig2}
@@
 calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
+At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the MS CD-Bonn based calculation above 600 MeV/c. \\
 \indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a
@@
 short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
-Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
+Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
 At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/intro-rev.tex
updated

--- 2020-05-18 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/introduction.tex
@@
 nucleons begin to overlap.
-The dynamics in this short distance region is directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
+The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
 Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-having to include explicit quark degrees of freedoms, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
+having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
 As of the present time, there are only a few nuclear physics experiments for
@@
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment \cite{PhysRevLett.107.262501} and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
 Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).

### 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated

@@
 with a bin width of $\pm 5^{\circ}$.
-The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
-AV18(green) and CD-Bonn(magenta) NN potentials.}
+The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
+AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}
 \label{fig:fig1}
@@
 $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
+For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
@@
 gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
-The data are compared to theoretical reduced
-cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials.
+The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA, referred to as MS, and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach, referred to as JML.
+For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
+The calculations
+used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
+JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
+\indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
+how the NN potential is modeled based on the empirical NN scattering data.
+The CD-Bonn model is based on the One-Boson-Exchange Potential (OBEP) approach in which the 
+nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
+extracted from the data. The interaction potential represents the static limit of 
+this potential. In contrast, the WJC2 is a OBEP derived within the Covariant Spectator Theory (CST) \cite{PhysRev.186.1448, PhysRevD.10.223, PhysRevC.26.2203, PhysRevC.26.2226}
+which require comparatively few parameters while still producing a high-precision fit to the NN scattering data.
+The Paris and AV18 are purely phenomenological potentials where a 
+Yukawa type interaction is introduced and parameters are fitted to describe the 
+same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
+potentials is that the former predicts a much softer repulsive interaction at short distance which 
+results in a smaller high momentum component in the deuteron wave function in momentum space.
+The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
@@
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models increasingly differ from the CD-Bonn calculation.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
-The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
-In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig.
-\hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).\\
-\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
-how the NN potential is modeled based on the empirical NN scattering data.
-The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
-nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
-extracted from the data. The interaction potential represents the static limit of 
-this potential. Paris and AV18 potentials are phenomenological in which the 
-Yukawa type interaction is introduced and parameters are fitted to describe the 
-same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
-potentials is that the former predicts much softer repulsive interaction at short distance which 
-results in a smaller high momentum component in the deuteron wave function in momentum space.
-%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
-%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
-%groups to describe the NN potential.
-The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the JML,
+MS AV18 and JVO models increasingly differ from the MS CD-Bonn calculation.
+In this region, the JML and MS AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
+the JVO PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$.
+The MS CD-Bonn cross sections in contrast are generally smaller than the JML, MS AV18 and JVO in this region.
+In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
+(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
+\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a
+steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
+4.2 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation.
+\\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
@@
 \indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
-missing momenta typically above 800 MeV/c for the CD-Bonn
+missing momenta typically above 800 MeV/c for the MS CD-Bonn
 \begin{figure}[!t]
@@
 \caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
-The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
+The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
 \label{fig:fig2}
@@
 calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
-\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
-This behavior of the data is new
-and additional data in this kinematic region are necessary to improve the statistics. \\
+At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the MS CD-Bonn based calculation above 600 MeV/c. \\
+\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a
+region where FSI are still relatively small $(<30\%)$. This behavior of the data is new and additional data in this kinematic region are necessary
+to improve the statistics. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig.
@@
 short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
-Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
+Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
 At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
@@
 to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
-thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful
+thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. van Orden for providing the theoretical calculations as well as the useful
 discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics

### 2020-06-30 UTILITIES_CODES/codes/THESIS/make_prl_plots.py

@@ -546,7 +546,7 @@ def make_prl_plots():
     #line_labels=['This Experiment (Hall C)', 'Hall A Data', 'Paris (Galster) PWIA', 'Paris (Galster) FSI', 'AV18 (JJK) PWIA', 'AV18 (JJK) FSI', 'CD-Bonn (JJK) PWIA', 'CD-Bonn (JJK) FSI', 'WJC2 (GKex05) PWIA', 'WJC2 (GKex05) FSI', 'WJC2 (AMT) PWIA', 'WJC2 (AMT) FSI', 'AV18 (GKex05) PWIA', 'AV18 (GKex05) FSI', 'AV18 (AMT) PWIA', 'AV18 (AMT) FSI', 'CD-Bonn (GKex05) PWIA', 'CD-Bonn (GKex05) FSI', 'CD-Bonn (AMT) PWIA', 'CD-Bonn (AMT) FSI']   #define legend labels
     #ax2.legend([l1, l2, l3, l4, l5, l6, l7, l8, WJC2_GK_PWBA, WJC2_GK_DWBA, WJC2_AMT_PWBA, WJC2_AMT_DWBA, AV18_GK_PWBA, AV18_GK_DWBA, AV18_AMT_PWBA, AV18_AMT_DWBA, CD_GK_PWBA, CD_GK_DWBA, CD_AMT_PWBA, CD_AMT_DWBA], line_labels, loc='upper right', frameon=False, fontsize=9)      #subplot to use for common legend
 
-    line_labels=['This Experiment (Hall C)', 'Hall A Data', 'Paris PWIA', 'Paris FSI', 'AV18 PWIA', 'AV18 FSI', 'CD-Bonn PWIA', 'CD-Bonn FSI', 'WJC2 PWIA', 'WJC2 FSI']
+    line_labels=['This Experiment (Hall C)', 'Hall A Data', 'JML Paris PWIA', 'JML Paris FSI', 'MS AV18 PWBA', 'MS AV18 FSI', 'MS CD-Bonn PWBA', 'MS CD-Bonn FSI', 'JVO WJC2 PWBA', 'JVO WJC2 FSI']
     ax2.legend([l1, l2, l3, l4, l5, l6, l7, l8, WJC2_GK_PWBA, WJC2_GK_DWBA], line_labels, loc='upper right', frameon=False, fontsize=12)      #subplot to use for common legend
            
 
@@ -995,24 +995,24 @@ def make_prl_plots():
 
[…]

### 2020-07-18 UTILITIES_CODES/codes/THESIS/plot_momentum_dist.py
updated

@@ -569,6 +569,7 @@ def plot_momentum_dist():
         #======================END PRL PLOTS==============
 
 
+        '''
         
         #----------------------PRODUCE PLOTS FOR THESIS----------
         
@@ -824,7 +825,9 @@ def plot_momentum_dist():
         B.pl.savefig(dir_name1+'/redXsec_thnq%i_deg.pdf'%(ithnq))
 
         #B.pl.show()
+        '''
 
+        
         '''
         #----------------------------PLOT RELATIVE ERRORS------------------------
         B.pl.figure(figsize=(10,7))
@@ -947,7 +950,10 @@ def plot_momentum_dist():
         
         #=============================END CODE TO PRODUCE THESIS PLOTS================================
         '''
-        '''
+
+
+        #DO LINE FITS OF Pr = 550 - 1000 MeV/c
+        
         #Require ONLY thnq = 35, 45 deg
         if (ithnq==35 or ithnq==45):
             #-------FIT data and model reduced cross sections directly----------
@@ -1062,6 +1068,7 @@ def plot_momentum_dist():
                 return y
             
             #--------Fit data----------
+            print('DATA')
             xd =pm_avg_data[ (~np.isnan(sig_exp)) & (pm_avg_data>=0.55) & (pm_avg_data<=1.0)]
             yd = sig_exp[(~np.isnan(sig_exp)) & (pm_avg_data>=0.55) & (pm_avg_data<=1.0)]
             yd_err = sig_exp_err[(~np.isnan(sig_exp)) & (pm_avg_data>=0.55) & (pm_avg_data<=1.0)]
@@ -1070,11 +1077,12 @@ def plot_momentum_dist():
             F = B.genfit(f,[m,b], xd, yd, yd_err)            
             mp = m.get()[1] ; mp_err=m.get()[2]
             bp = np.log(b.get()[1]) ; bp_err=np.log(b.get()[2])
-            B.plot_line(F.xpl, F.ypl, color='r', lw=2, label='DATA FIT \n slope: %.4E $\pm$ %.4E'%(mp, mp_err))
[…]

### 2020-07-20 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body-rev.tex
updated

--- 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all momentum settings. \\
-\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
+\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
 model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).\\
@@
 The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
-to the statistical uncertainty (25-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
+to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
@@
 is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
-de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref. \cite{PhysRevC.69.022201}.
+de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the FF parametrization of Ref. \cite{PhysRevC.69.022201}.
 Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the PWIA cross section from the scattering of a proton in the deuteron. \\
@@
 For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
-The calculations
-used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
+%-----Mention the fofa parametrizations used in each of the calculations------
+The MS calculations used the FF parametrization of Ref.
+\cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
+for the neutron electric FF, and the results from the Hall A experiment of Ref.
+\cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
+The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
 JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
@@
 (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
-\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a
+\indent For recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), all models exhibit a
 steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
@@
 to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
-thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. van Orden for providing the theoretical calculations as well as the useful
+thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
 discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics

### 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body-rev.tex
updated

@@
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and 
+over the kinematic bin.
+The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections
 \onecolumngrid
@@
 \twocolumngrid
-\noindent FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
+\noindent were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}

### 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated

@@
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
-behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\
+behavior (smaller fall-off) that overshadows any possibility of extracting the approximate momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/authorlist-rev.tex
added directory with final PRL draft

--- 2020-04-15 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/authorlist.tex
@@
 \author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
-\author{A.~Ahmidouch$^{4}$}        % . . .
+\author{A.~Ahmidouch$^{4}$}        % . . .----> HOLLY
 \author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
@@
 %\author{D.~Androic}         %Color Transparency ONLY
+
 \author{W.~Armstrong$^{6}$}        %Commissioning ONLY
@@
 \author{S.~Basnet$^{3}$}           %Commissioning + SIDIS
-\author{V.V.~Berdnikov$^{11}$}        %Commissioning + SIDIS
-\author{J.~Bericic$^{15}$}          %SHMS Optics Contributor
+\author{V.V.~Berdnikov$^{11}$}        %Commissioning + SIDIS  (tell HOLLY name change)
+\author{J.~Bericic$^{15}$}          %SHMS Optics Contributor  HOLLY
 \author{H.~Bhatt$^{8}$}            %Commissioning + SIDIS
@@
 \author{D.~Biswas$^{12}$}           %Commissioning + SIDIS
-\author{W.~Boeglin$^{1}$}          %Commissioning ONLY (Deuteron Spokesperson)
+\author{W.U.~Boeglin$^{1}$}          %Commissioning ONLY (Deuteron Spokesperson)
 \author{P.~Bosted$^{9}$}           %Commissioning ONLY (SIDIS Spokesperson)
 \author{E.~Brash$^{13}$}            %Commissioning ONLY
-\author{M.~Bukhari$^{14}$}          %Commissioning ONLY
+\author{M.H.S.~Bukhari$^{14}$}          %Commissioning ONLY
 %\author{M.~Carmignotto}     %NO MINIMUM SHIFTS
@@
 \author{M.~Diefenthaler$^{15}$}     %Commissioning + SIDIS
-\author{M.~Dlamini$^{16}$}          %Commissioning ONLY
-\author{J.~Dunne$^{8}$}            %Commissioning ONLY
-\author{B.~Duran$^{6}$}            %Commissioning + SIDIS
+\author{M.~Dlamini$^{17}$}          %Commissioning ONLY
+\author{J.~Dunne$^{8}$}
+%Commissioning ONLY
+\author{B.~Duran$^{16}$}            %Commissioning + SIDIS
 \author{D.~Dutta$^{8}$}            %Commissioning + SIDIS  (CT Spokesperson)
@@
 \author{N.~Fomin$^{10}$}            %Commissioning ONLY
-\author{E.~Fuchey$^{17}$}           %Commissioning ONLY
+\author{E.~Fuchey$^{18}$}           %Commissioning ONLY
 \author{D.~Gaskell$^{15}$}          %Commissioning + SIDIS
 \author{T.N.~Gautam$^{12}$}         %Commissioning ONLY
-\author{F.A.~Gonzalez$^{18}$}       %Commissioning + SIDIS
-\author{O.~Hansen$^{15}$}           %Commissioning ONLY
-\author{F.~Hauenstein$^{19}$}       %Commissioning ONLY
+\author{F.A.~Gonzalez$^{19}$}       %Commissioning + SIDIS
+\author{J.O.~Hansen$^{15}$}           %Commissioning ONLY
+\author{F.~Hauenstein$^{20}$}       %Commissioning ONLY
 \author{A.V.~Hernandez$^{11}$}       %Commissioning ONLY
 \author{T.~Horn$^{11}$}             %Commissioning ONLY
-\author{G.~Huber$^{3}$}            %Commissioning ONLY
+\author{G.M.~Huber$^{3}$}            %Commissioning ONLY
+\homepage[ORCiD: ]{http://orcid.org/0000-0002-5658-1065}
 \author{M.K.~Jones$^{15}$}          %Commissioning + SIDIS
@@
 \author{A.~Khanal$^{1}$}           %Commissioning ONLY
-\author{P.~King$^{16}$}             %Commissioning ONLY
-\author{E.~Kinney$^{20}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)
+\author{P.~King$^{17}$}             %Commissioning ONLY
+\author{E.~Kinney$^{21}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)
 %\author{H.S.~Ko}            %Color Transparency ONLY
@@
 \author{N.~Lashley-Colthirst$^{12}$}      %Commissioning ONLY
-\author{S.~Li$^{21}$}               %Commissioning ONLY
-\author{W.B.~Li$^{9}$}               %Commissioning ONLY
+\author{S.~Li$^{22}$}               %Commissioning ONLY
+\author{W.B.~Li$^{9}$}               %Commissioning ONLY  tell HOLLY name change
 \author{A.H.~Liyanage$^{12}$}       %Commissioning + SIDIS
-\author{D.~Mack$^{15}$}             %Commissioning + SIDIS
-\author{S.~Malace$^{15}$}           %Commissioning + SIDIS (F2 Spokesperson)
+\author{D.J.~Mack$^{15}$}             %Commissioning + SIDIS
+\author{S.P.~Malace$^{15}$}           %Commissioning + SIDIS (F2 Spokesperson)
 %\author{P.~Markowitz}       %NO MINIMUM SHIFTS
@@
 \author{R.~Michaels$^{15}$}         %Commissioning + SIDIS
-\author{A.~Mkrtchyan$^{7}$}        %Commissioning ONLY
+\author{A.~Mkrtchyan$^{7}$}        %Commissioning ONLY     HOLLY
 \author{H.~Mkrtchyan$^{7}$}        %Commissioning ONLY
 \author{S.J.~Nazeer$^{12}$}         %Commissioning ONLY
-%\author{S.~Nanda}           %Spec. commissioning only Dec. 14-17 shifts
-\author{G.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
-\author{M.~Niculescu$^{22}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{S.~Nanda$^{8}$}           %Spec. commissioning only Dec. 14-17 shifts
+\author{G.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
+\author{M.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
 \author{D.~Nguyen$^{2}$}           %Commissioning ONLY (Took 10 shifts) 
-\author{N.~Nuruzzaman$^{23}$}       %Commissioning ONLY
+\author{N.~Nuruzzaman$^{24}$}       %Commissioning ONLY
 \author{B.~Pandey$^{12}$}           %NO MINIMUM SHIFTS (WORKED ON HMS DCs for 1 year. INCLUDED AS AUTHOR!)
-\author{S.~Park$^{18}$}             %Commissioning + SIDIS
-\author{C.F.~Perdrisat$^{9}$}            %College of William & Mary
+\author{S.~Park$^{19}$}             %Commissioning + SIDIS
+\author{C.F.~Perdrisat$^{9}$}            %College of William & Mary   HOLLY
 \author{E.~Pooser$^{15}$}           %Commissioning + SIDIS
 %\author{A.~Puckett}         %NO MINIMUM SHIFTS
-\author{M.~Rehfuss$^{6}$}          %Commissioning ONLY
+\author{M.~Rehfuss$^{16}$}          %Commissioning ONLY
 \author{J.~Reinhold$^{1}$}         %Commissioning ONLY
@@
 \author{G.~Smith$^{15}$}             %Commissioning ONLY
-\author{A.~Sun$^{24}$}               %Commissioning + SIDIS
+\author{A.~Sun$^{25}$}               %Commissioning + SIDIS
 \author{H.~Szumila-Vance$^{15}$}     %Commissioning + SIDIS
@@
 \author{S.A.~Wood$^{15}$}            %NO MINIMUM SHIFTS (Hall C Deputy + Worked on Hall C 12 GeV software + hardware work) (INCLUDED AS AUTHOR!)
-\author{J.~Zhang$^{18}$}        %Commissioning ONLY 
+\author{J.~Zhang$^{19}$}        %Commissioning ONLY 
 %\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
@@
 \affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
-\affiliation{$^{6}$Temple University, Philadelphia, Pennsylvania 19122, USA}
+\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}   %fixed address for Whit and Sylvester
 \affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
@@
 \affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
-\affiliation{$^{16}$Ohio University, Athens, Ohio 45701, USA}
-\affiliation{$^{17}$University of Connecticut, Storrs, Connecticut 06269, USA}
-\affiliation{$^{18}$Stony Brook University, Stony Brook, New York 11794, USA}
-\affiliation{$^{19}$Old Dominion University, Norfolk, Virginia 23529, USA}
-\affiliation{$^{20}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
-\affiliation{$^{21}$University of New Hampshire, Durham, New Hampshire 03824, USA}
-\affiliation{$^{22}$James Madison University, Harrisonburg, Virginia 22807, USA}
-\affiliation{$^{23}$Rutgers University, New Brunswick, New Jersey 08854, USA}
-\affiliation{$^{24}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}
+\affiliation{$^{16}$Temple University, Philadelphia, Pennsylvania 19122, USA}
+\affiliation{$^{17}$Ohio University, Athens, Ohio 45701, USA}
+\affiliation{$^{18}$University of Connecticut, Storrs, Connecticut 06269, USA}
+\affiliation{$^{19}$Stony Brook University, Stony Brook, New York 11794, USA}
+\affiliation{$^{20}$Old Dominion University, Norfolk, Virginia 23529, USA}
+\affiliation{$^{21}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
+\affiliation{$^{22}$University of New Hampshire, Durham, New Hampshire 03824, USA}
+\affiliation{$^{23}$James Madison University, Harrisonburg, Virginia 22807, USA}
+\affiliation{$^{24}$Rutgers University, New Brunswick, New Jersey 08854, USA}
+\affiliation{$^{25}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
added directory with final PRL draft

--- 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 this potential. In contrast, the WJC2 is a OBEP derived within the Covariant Spectator Theory (CST) \cite{PhysRev.186.1448, PhysRevD.10.223, PhysRevC.26.2203, PhysRevC.26.2226}
-which require comparatively few parameters while still producing a high-precision fit to the NN scattering data.
+which requires comparatively few parameters while still producing a high-precision fit to the NN scattering data.
 The Paris and AV18 are purely phenomenological potentials where a 

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-diff.tex
added directory with final PRL draft

--- 2020-06-30 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/intro-rev.tex
@@
 from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
-\indent At large $Q^{2}$, FSI are described by the General Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
+\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
 GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$.

### 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/prl-rev.tex
added directory with final PRL draft

--- 2020-05-19 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/prl.tex
@@
 \leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by June 01, 2020}
+\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
 \centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
@@
   been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
-  transfer $\vec q$. The new data agrees well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
+  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
   and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
   the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
-  theoretical calculations, where a significant disagreement for missing momenta $p_{\mathrm{r}}>700$ MeV/c is observed. 
+  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
 \end{abstract}

### 2020-07-27 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
added directory with final PRL draft

--- 2020-06-13 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 measured in this experiment.
-As a result, most of the virtual photon momentum is transferred to the proton, which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.
+As a result, most of the virtual photon momentum is transferred to the proton which scatters at angles relative to $\vec{q}$ in the range $0.4^{\circ}\lesssim \theta_{pq}\lesssim21.4^{\circ}$.
 At these forward angles and large momenta transferred to the proton, the  process where the neutron is struck by the virtual photon is suppressed.\\
@@
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
-and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
+and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
@@
 \indent The systematic uncertainties on the cross section due to systematic error on the absolute beam energy and spectrometer angle/momentum settings were
-determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
+determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping pr bins. 
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
@@
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and 
+over the kinematic bin.
+The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
+\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \onecolumngrid
@@
 \twocolumngrid
-\noindent FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
+For the two highest settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$ .
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
@@
 The theoretical calculations
-for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
-\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} and those for the Paris potential (blue) were by Laget \cite{LAGET2005}.\\
+\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.
+The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
-\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
-AV18 models increasingly differ from the CD-Bonn calculation.
-In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
+\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
+AV18 models significantly differ from the CD-Bonn.
+In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c.
 The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.
@@
 \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig.
-\hyperref[fig:fig1]{1(b)}).\\
-\indent The difference between the deuteron wave functions with CD-Bonn and Paris/AV18 potentials is 
-how the NN potential is modeled based on the empirical NN scattering data.
-The CD-Bonn model is based on the One-Boson-Exchange approach in which the 
-nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
-extracted from the data. The interaction potential represents the static limit of 
-this potential. Paris and AV18 potentials are phenomenological in which the 
-Yukawa type interaction is introduced and parameters are fitted to describe the 
-same NN scattering phase-shifts. The major difference between CD-Bonn and Paris/AV18 
-potentials is that the former predicts much softer repulsive interaction at short distance which 
-results in a smaller high momentum component in the deuteron wave function in momentum space.
-%The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant
-%(original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18
-%groups to describe the NN potential.
-The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
+\hyperref[fig:fig1]{1(b)}).
+The main difference between the CD-Bonn and Paris/AV18 models is the use of Feynman amplitudes in covariant (original) form by the Bonn group as opposed to local (static) approximations of these amplitudes used by Paris/AV18 groups
+to describe the NN potential. The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
-behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\
+behaviour (smaller fall-off) that overshadows any possibility of extracting the momentum distributions.\\
 \indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
@@
 \indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
-to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic
+to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\
-\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
+\indent At larger recoil momenta, where the ratio is $R>1$ and increasing, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
 missing momenta typically above 800 MeV/c for the CD-Bonn
-\begin{figure}[!t]
+\begin{figure}[t!]
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
@@
 calculation while the other models predict still relatively small FSI below 900 MeV/c.
-At $\theta_{nq}=45^{\circ}$, the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
+At $\theta_{nq}=45^{\circ}$ the FSI dominance starts earlier for all models above 800 MeV/c and for the CD-Bonn based calculation above 600 MeV/c. \\
 \indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.
@@
 \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
-At $p_{\mathrm{r}}>300$ MeV/c and $\theta_{nq}=75^{\circ}$, the data were statistically limited as our focus was on the smaller recoil angles.
+At $p_{\mathrm{r}}>300$ MeV/c, the data were statistically limited as our focus was on the smaller recoil angles.
 The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
 of FSI at the smaller recoil angles. \\
-\indent To summarize, this experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
+\indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
 very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
-short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
+short range part of the deuteron wavefunction. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
 Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
-Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
-momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
+At higher missing momenta, however, all models were unable to describe the data. \\
+\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
+momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.
 \indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
 as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
-thank Misak Sargsian, Sabine Jeschonnek and J.W.Van Orden for providing the theoretical calculations as well as the useful
-discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
+was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
 under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
-under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
+under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.
 

### 2020-07-29 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
added corrections and created a submission directory to store the final .tex and .pdf files to be submitted to PRL

@@
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
-At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
+At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to
 the lower and higher missing momentum settings, respectively.
@@
 are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''
-energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a PID cut on the
+energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a particle identification (PID) cut on the
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
@@
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
-contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ),
+contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
 and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
-proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
+proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
 as an overall normalization constant to the final result.\\
@@
 %and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
-\indent The systematic uncertainties on the cross section due to systematic error on the absolute beam energy and spectrometer angle/momentum settings were
+\indent The systematic uncertainties on the cross sections due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
 determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
-The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
-to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
+The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
+to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
@@
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin.
-The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections
-\onecolumngrid
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
+over the kinematic bin. The
+%\onecolumngrid
+%\begin{center}
+\begin{figure*}[t]
+\centering        
+\includegraphics[scale=0.45]{prl_plots/PRL_plot1.pdf}
 \caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
 with a bin width of $\pm 5^{\circ}$.
-The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
+The data are compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
 AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}
 \label{fig:fig1}
-\end{figure}
-\end{center}
-\twocolumngrid
-\noindent were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
+\end{figure*}
+%\end{center}
+%\twocolumngrid
+\noindent systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.
+The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 \end{equation}
-\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section, $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
+\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
 $E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
@@
 results in a smaller high momentum component in the deuteron wave function in momentum space.
-The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
+The effects of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
@@
 At $p_{\mathrm{r}}>300$ MeV/c and $\theta_{nq}=75^{\circ}$, the data were statistically limited as our focus was on the smaller recoil angles.
-The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding
+The Hall A data, however, show a reasonable agreement with the FSI from all models which gives us confidence in our understanding
 of FSI at the smaller recoil angles. \\
 \indent To summarize, this experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
-very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross section was dominated by PWIA and sensitive to the
-short range part of the deuteron wave function. The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data.
+very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross sections were dominated by PWIA and sensitive to the
+short range part of the deuteron wave function.
+The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data at lower recoil momenta where they overlap.
 Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
+At the higher missing momenta provided by this experiment ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
 Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing

### 2020-07-29 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-rev.tex
added corrections and created a submission directory to store the final .tex and .pdf files to be submitted to PRL

--- 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-diff.tex
@@
 electro-production threshold.
-Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref.
+Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$) (see Section 5 of Ref.
 \cite{sargsian_2015}) have helped quantify the contributions
-from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+from FSI, MEC and IC to the $^{2}\mathrm{H}(e,e'p)n$ cross sections and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
 \indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
@@
 which are therefore dominated by  FSI, MEC and IC for $p_{\mathrm{r}}$ above $\sim 300$ MeV/c. \\
-\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$)
+\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross sections for fixed neutron recoil angles ($\theta_{nq}$)
 reaching recoil momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$. For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$

### 2020-07-29 MY_PUBLICATIONS/PRL/FINAL_DRAFT/submission_docs/prl.tex
added corrections and created a submission directory to store the final .tex and .pdf files to be submitted to PRL

--- 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/prl-rev.tex
@@
 \usepackage{graphicx}  % needed for figures
+\usepackage{ragged2e}
 \usepackage{dcolumn}   % needed for some tables
@@
 \begin{document}
-
 % The following information is for internal review, please remove them for submission
-\widetext
-\leftline{Version 05 as of \today}
-\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
-\leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
-\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
+%\widetext
+%\leftline{Version 06 as of \today}
+%\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
+%\leftline{To be submitted to PRL}
+%\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
+%\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
 
@@
   $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
-  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
+  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data were
+  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
   transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$

### 2020-07-31 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updated PRL by including M. Sargsian corections

--- 2020-07-29 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
@@
 to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
-\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
-The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.
-For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics was calculated and used in the bin centering correction factor defined as:
-$f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin. The
 %\onecolumngrid
@@
 The data are compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
-AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}
+AV18 (green), CD-Bonn (magenta) and WJC2 (orange) $NN$ potentials.}
 \label{fig:fig1}
@@
 %\twocolumngrid
-\noindent systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.
+\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
+The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.
+For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics was calculated and used in the bin centering correction factor defined as:
+$f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
+over the kinematic bin.
+The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.
 The experimental and theoretical reduced cross sections were extracted and are defined as follows:
@@
 gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
-The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials.
+The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} $NN$ potentials.
 The theoretical calculations
@@
 \indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
-how the NN potential is modeled based on the empirical NN scattering data.
+how the $NN$ potential is modeled based on the empirical $NN$ scattering data.
 The CD-Bonn model is based on the One-Boson-Exchange Potential (OBEP) approach in which the 
-nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
+nucleon-meson-meson couplings are constrained to describe the $NN$ scattering phase shifts
 extracted from the data. The interaction potential represents the static limit of 
 this potential. In contrast, the WJC2 is a OBEP derived within the Covariant Spectator Theory (CST) \cite{PhysRev.186.1448, PhysRevD.10.223, PhysRevC.26.2203, PhysRevC.26.2226}
-which requires comparatively few parameters while still producing a high-precision fit to the NN scattering data.
+which requires comparatively few parameters while still producing a high-precision fit to the $NN$ scattering data.
 The Paris and AV18 are purely phenomenological potentials where a 
 Yukawa type interaction is introduced and parameters are fitted to describe the 
-same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
+same $NN$ scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
 potentials is that the former predicts a much softer repulsive interaction at short distance which 
 results in a smaller high momentum component in the deuteron wave function in momentum space.
-The effects of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
+The effects of these local approximations on the $NN$ potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the $NN$ potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\
@@
 \indent For $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}), the data are best described by the MS CD-Bonn PWIA calculation for recoil momenta up
-to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data confirm the Hall A approach of selecting a kinematic
+to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data validates the Hall A approach of selecting a kinematic
 region where recoil angles are small and FSI are reduced. \\

### 2020-07-31 MY_PUBLICATIONS/PRL/FINAL_DRAFT/prl.tex
updated PRL by including M. Sargsian corections

--- 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/prl-rev.tex
@@
 \widetext
-\leftline{Version 05 as of \today}
+\leftline{Version 06 as of \today}
 \leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
@@
   $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
-  over a range of neutron recoil momenta, $p_{\mathrm{r}}$, with $p_{\mathrm{r}}$ reaching up to $\sim1.0$ GeV/c. The data have
-  been obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
+  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
+  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
   transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
-  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar configurations (IC) are suppressed and
+  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
   the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent

### 2020-08-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction.tex
updated

--- 2020-07-29 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-rev.tex
@@
 The deuteron is the only bound two-nucleon system and serves as an ideal framework to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
-practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
+practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
 nucleons begin to overlap.
-The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.
+The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
 Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
@@
 As of the present time, there are only a few nuclear physics experiments for
-which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
-\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
-electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the PWIA, the virtual photon couples to
+which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
+However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
+\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum component) is via the exclusive deuteron
+electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to
 the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
@@
 to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
-\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
-photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
-decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
+%\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
+%photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
+%decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).
+\indent In addition to PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
+the photon coupling to the exchanged mesons in the $pn$ system, generating meson exchange currents (MEC), or the photon exciting the bound nucleon into the
+resonating state (mainly $\Delta$-isobar) with subsequent $\Delta N \to NN$ rescattering, referred to as isobar currents (IC). FSI, MEC and IC can significantly alter the recoiling neutron
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
@@
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
+Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the detueron.
 IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance

### 2020-08-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updated

@@
 contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
-and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
-proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
-as an overall normalization constant to the final result.\\
+and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
+the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
+to define the overall normalization uncertainty ($\leq$ 8.4$\%$).\\
 %\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
@@
 determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
-For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
-The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
-to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 8.4$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties
+to obtain the final uncertainty on the cross sections.\\
+%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
+%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
 %\onecolumngrid

### 2020-08-07 publications/supplemental_materials/get_Xsec_err.py

@@ -5,15 +5,11 @@ from interpolate_ff import *
 #the electric and magnetic form factors. Then apply error propagation
 #in terms of the form factors to get uncertainty in cross section at thw
 #gven beam energy, elecrtron angle and momentum.
-#Finally, use the error in the Xsec as the error as the simc yield error
 #Define Physical Constnats
-
 
 hbarc = 197.327053 / 1000.       #GeV * fm
 alpha = 1./137.0359895    #structure constant
 dtr = np.pi / 180.
-
-#(1 GeV)^2 = (1000 MeV)^2 = 1e6 MeV^2
 
 #Masses in GeV
 MP = 938.272 / 1000.
@@ -21,7 +17,7 @@ MN = 939.566 / 1000.
 MD = 1875.61 / 1000.
 me = 0.51099 / 1000.
 
-#Elastic Cross Section and its error
+#Template function that returns the H(e,e'p) cross section and its absolute uncertainty in units of ub / sr
 def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
 
     #Units: kf ~ Ef [GeV]   electron momentum  
@@ -41,7 +37,7 @@ def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
     GD = 1. / (1 + Q2/L2)**2     #dipole form factor
     muGD = mu_p * GD   #[GeV T^-1]
     
-    #Get form factors
+    #Calculate the form factors
     GEp = GEp_GD * GD
     GMp = GMp_muGD * muGD
 
@@ -63,39 +59,33 @@ def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
     return sig, dsig
 
 
-#Heep Kinematics
-dtr = np.pi / 180.
-Eb = 10.6005   #beam
-#Ef = 8.5342488  #e- momentum
-th_e = np.array([12.194, 13.93, 9.928, 8.495])  #e- angle
 
-#This selection of e- final momentum is determined by selectin
-#the th_e bin +/- 0.01 deg, i.e. for [13.92,13.94], 
[…]

### 2020-08-11 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
updated

@@
-\indent A 10.6 GeV electron beam was incident on a 10 cm long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
+\indent A 10.6 GeV electron beam was incident on a 10-cm-long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
 by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively.
@@
 were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) \cite{cyero_phdthesis} and
-target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all momentum settings. \\
+target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all missing momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 %The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
-\indent The systematic uncertainties of the measured cross sections were determined from 
+\indent The systematic uncertainties on the measured cross sections were determined from 
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
 contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
-and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
-proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
-as an overall normalization constant to the final result.\\
+and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
+the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
+to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
 %\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
 %and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
-\indent The systematic uncertainties on the cross sections due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
+\indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
 determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
-For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
-The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
-to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
-\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
-The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.
-For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics was calculated and used in the bin centering correction factor defined as:
-$f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin. The
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
+%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
+%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
 %\onecolumngrid
@@
 \\
-\indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar
+\indent At $\theta_{nq}=75^{\circ}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contribution to the cross sections for all models which exhibit a similar
 behavior (smaller fall-off) that overshadows any possibility of extracting the approximate momentum distributions.\\

### 2020-08-11 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body.tex
added corrections and created a submission directory to store the final .tex and .pdf files to be submitted to PRL
updated

--- 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
@@
 \indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
-For each spectrometer, a logical signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
-At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
+At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to
 the lower and higher missing momentum settings, respectively.
@@
 %The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
-\indent The systematic uncertainties of the measured cross sections were determined from 
+\indent The systematic uncertainties on the measured cross sections were determined from 
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
-contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ),
-and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
-proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
-as an overall normalization constant to the final result.\\
+contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
+and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
+the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
+to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
 %\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
 %and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
-\indent The systematic uncertainties on the cross section due to systematic error on the absolute beam energy and spectrometer angle/momentum settings were
+\indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
 determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
-For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
-The overall systematic uncertainty in the cross section was determined by the quadrature sum of the normalization and kinematic uncertainties. This result was then added in quadrature
-to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty in the cross section. \\
+For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
+%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
+%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
+%\onecolumngrid
+%\begin{center}
+\begin{figure*}[t]
+\centering        
+\includegraphics[scale=0.45]{prl_plots/PRL_plot1.pdf}
+\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
+with a bin width of $\pm 5^{\circ}$.
+The data are compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
+AV18 (green), CD-Bonn (magenta) and WJC2 (orange) $NN$ potentials.}
+\label{fig:fig1}
+\end{figure*}
+%\end{center}
+%\twocolumngrid
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
@@
 over the kinematic bin.
-The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections
-\onecolumngrid
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
-with a bin width of $\pm 5^{\circ}$.
-The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
-AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}
-\label{fig:fig1}
-\end{figure}
-\end{center}
-\twocolumngrid
-\noindent were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:
+The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.
+The experimental and theoretical reduced cross sections were extracted and are defined as follows:
 \begin{equation}
@@
 \indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
-how the NN potential is modeled based on the empirical NN scattering data.
+how the $NN$ potential is modeled based on the empirical $NN$ scattering data.
 The CD-Bonn model is based on the One-Boson-Exchange Potential (OBEP) approach in which the 
-nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts
+nucleon-meson-meson couplings are constrained to describe the $NN$ scattering phase shifts
 extracted from the data. The interaction potential represents the static limit of 
 this potential. In contrast, the WJC2 is a OBEP derived within the Covariant Spectator Theory (CST) \cite{PhysRev.186.1448, PhysRevD.10.223, PhysRevC.26.2203, PhysRevC.26.2226}
-which require comparatively few parameters while still producing a high-precision fit to the NN scattering data.
+which requires comparatively few parameters while still producing a high-precision fit to the $NN$ scattering data.
 The Paris and AV18 are purely phenomenological potentials where a 
 Yukawa type interaction is introduced and parameters are fitted to describe the 
-same NN scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
+same $NN$ scattering phase-shifts. The major difference between the CD-Bonn and Paris/AV18/WJC2 
 potentials is that the former predicts a much softer repulsive interaction at short distance which 
 results in a smaller high momentum component in the deuteron wave function in momentum space.
-The effect of these local approximations on the NN potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
+The effects of these local approximations on the $NN$ potential are shown in Fig. 2 of Ref. \cite{PhysRevC.63.024001}.\\
 \indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.
-The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)
+The agreement at $p_{\mathrm{r}}\leq250$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the $NN$ potential where the One Pion Exchange Potential (OPEP)
 is well known and common to all modern potentials. \\

### 2020-08-11 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction-diff.tex
updated

@@
 to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
-\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
-photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
-decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron
+%\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
+%photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
+%decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).
+\indent In addition to the PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
+the photon coupling to the exchanged mesons in the $pn$ system, generating meson exchange currents (MEC), or the photon exciting the bound nucleon into the
+resonating state (mainly $\Delta$-isobar) with subsequent $\Delta N \to NN$ rescattering, referred to as isobar currents (IC). FSI, MEC and IC can significantly alter the recoiling neutron
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
@@
 $\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
+Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron.
 IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
 electro-production threshold.
-Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref.
+Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$) (see Section 5 of Ref.
 \cite{sargsian_2015}) have helped quantify the contributions
-from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+from FSI, MEC and IC to the $^{2}\mathrm{H}(e,e'p)n$ cross sections and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
 \indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.

### 2020-08-11 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/prl-rev.tex
updated

@@
 % The following information is for internal review, please remove them for submission
-\widetext
-\leftline{Version 05 as of \today}
-\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
-\leftline{To be submitted to PRL}
-\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
-\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
+%\widetext
+%\leftline{Version 06 as of \today}
+%\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
+%\leftline{To be submitted to PRL}
+%\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by July 31, 2020}
+%\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}
 

### 2020-08-11 UTILITIES_CODES/codes/THESIS/make_prl_plots.py

@@ -54,7 +54,9 @@ MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
      
 
 #Get Reduced Xsec Data File
-fname = '../deep_data_files/Q2_4to5GeV/redXsec_combined.txt'
+fname = '../deep_data_files/Q2_4to5GeV/redXsec_combined_wrongNormalization.txt'
+#fname = '../deep_data_files/Q2_4to5GeV/redXsec_combined.txt'
+#redXsec_combined.txt'
 f = B.get_file(fname)
 
 #Get Bin Information (Same info for all files)                                                                                                  

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/cover_letter/cl.tex
updateed PRL submission docs

%basic cover letter template
\documentclass{letter}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

%\address{Mathematics Department\\University of Illinois\\
%1409 W. Green St\\Urbana, Illinois 61801}

\newcommand {\qed}{\mbox{$\Box$}}
\renewcommand {\iff}{\Longleftrightarrow}
\newcommand {\R}{\mathbb{R}}
\newcommand {\N}{\mathbb{N}}
\newcommand {\Q}{\mathbb{Q}}
\newcommand {\Z}{\mathbb{Z}}

\newcommand {\sub}{\mbox{SB}}

\begin{document}
\begin{letter}{Carlos Yero\\
Thomas Jefferson National Accelerator Facility\\
12000 Jefferson Avenue \\
Newport News, VA 23602\\
(786) 387-8667 \\
cyero@jlab.org
  }

\opening{Dear Editors,\\}

I hereby submit a manuscript entitled ``Probing the Deuteron at Very Large Internal Momenta'' to be considered
for publication by \textit{Physical Review Letters}. There are eight files in all: the main manuscript file (prl.tex), 2 figure files (.pdf),
a biblipgraphy file (.bbl), an author list file (.tex), and three supplementary (.txt) files with the numerical results of the
cross sections evaluated at the relevant kinematics described in the manuscript.\\

We report cross-section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
double the maximum recoil momentum measured in a previous deuteron electro-disintegration experiment carried out in Hall A at Jefferson Lab. 
That experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
reduced and the plane wave impulse approximation (PWIA) provided the dominant contribution to the cross section. This experiment focused
on the kinematic window (where FSI are small) found by the Hall A experiment and extended the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
access to the high momentum component of the deuteron wave-function, or equivalently, the nucleon-nucleon ($NN$) interaction at the sub-Fermi
distance scale which is currently poorly understood.\\

This Letter summarizes the experimental results of cross-section measurements that extended the neutron recoil momentum measured up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c giving a direct access
to the shot-range structure of the deuteron wave-function which is a crucial step forward in the understanding the $NN$ interaction at very small ($\leq$1 fm) distances. We believe these
findings will be of general interest to the readers of your journal.\\

We declare that this manuscript is original, has not been published before and is not currently being considered for publication elsewhere.\\
\\
\closing{Sincerely,
%\includegraphics[width=6cm]{signature.pdf}
}
%I made a pdf file of my signature using the scanner, so that all the cover letters I sent
%electronically were "signed."

Carlos Yero\\
Hall C Postdoctoral Fellow\\
\end{letter}

\end{document}

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl.tex
updateed PRL submission docs

--- 2020-08-11 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/body-rev.tex
@@
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
+\pdfoutput=1 
+\usepackage{graphicx}  % needed for figures
+\usepackage{ragged2e}
+\usepackage{dcolumn}   % needed for some tables
+\usepackage{bm}        % for math
+\usepackage{amssymb}   % for math
+\usepackage[hidelinks]{hyperref}
+\usepackage{fancyhdr}
+\usepackage{xcolor}
+\usepackage{float}
+\usepackage{lipsum}
+\hypersetup{
+    colorlinks,
+    linkcolor={blue!80!black},
+    citecolor={blue!80!black},
+    urlcolor={blue!80!black}
+}
+\hyphenation{ALPGEN}
+\hyphenation{EVTGEN}
+\hyphenation{PYTHIA}
+
+\begin{document}
+
+\title{Probing the Deuteron at Very Large Internal Momenta}
+
+\input authorlist.tex
+
+\date{\today}
+
+\begin{abstract}
+  $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
+  over a range of neutron recoil momenta, $p_{\mathrm{r}}$,  reaching up to $\sim1.0$ GeV/c. The data were
+  obtained at fixed neutron recoil angles $\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
+  transfer $\vec q$. The new data agree well with previous data which reached $p_{\mathrm{r}}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$
+  and $45^\circ$, final state interactions (FSI), meson exchange currents (MEC) and isobar currents (IC) are suppressed and
+  the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
+  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
+\end{abstract}
+
+\pacs{25.30.Fj, 25.60.Gc}
+\maketitle
+
+The deuteron is the only bound two-nucleon system and serves as an ideal framework to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
+practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
+nucleons begin to overlap.
+The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
+Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
+having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
+As of the present time, there are only a few nuclear physics experiments for
+which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
+However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
+\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum component) is via the exclusive deuteron
+electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to
+the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
+The neutron carries a recoil momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction
+to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
+\indent In addition to the PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
+the photon coupling to the exchanged mesons in the $pn$ system, generating meson exchange currents (MEC), or the photon exciting the bound nucleon into the
+resonating state (mainly $\Delta$-isobar) with subsequent $\Delta N \to NN$ rescattering, referred to as isobar currents (IC). FSI, MEC and IC can significantly alter the recoiling neutron
+momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
+\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively\cite{sargsian_2015}.
+The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
+$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
+Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron.
+IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance
+electro-production threshold.
+Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$) (see Section 5 of Ref.
+\cite{sargsian_2015}) have helped quantify the contributions
+from FSI, MEC and IC to the $^{2}\mathrm{H}(e,e'p)n$ cross sections and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
+\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
+GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$.
+This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{\circ}$ and $\theta_{nq}\sim120^{\circ}$.
+Because at
+$\theta_{nq}\sim120^{\circ}$ ($x_{\mathrm{Bj}}<1$) IC are not negligible, the $x_{\mathrm{Bj}}>1$ ($\theta_{nq}\sim40^{\circ}$) kinematics are the preferred choice to suppress IC as well as FSI. \\
+\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at Jefferson Lab (JLab) in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}.
+Both
+experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
+at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
+distributions for  a range of $Q^2$ values as well as momentum distributions.
+However, statistical limitations made it necessary to integrate over a wide angular range to determine momentum distributions
+which are therefore dominated by  FSI, MEC and IC for $p_{\mathrm{r}}$ above $\sim 300$ MeV/c. \\
+\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$)
+reaching recoil momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$. For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
+and $45\pm5^{\circ}$ compared to  $\theta_{nq}=75\pm5^{\circ}$.
+Theoretical models attributed this difference  to the suppression of FSI at the smaller angles ($\theta_{nq}=35, 45^{\circ}$) compared to FSI
+dominance at $\theta_{nq}=75^{\circ}$ \cite{PhysRevLett.107.262501}. \\
+\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment \cite{PhysRevLett.107.262501} and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
+At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.\\
 \indent A 10.6 GeV electron beam was incident on a 10-cm-long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
@@
 model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only).\\
-%For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).
-%The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
 \indent The systematic uncertainties on the measured cross sections were determined from 
@@
 to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
-%\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
-%and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
 \indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
@@
 The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
-%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
-%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
-%\onecolumngrid
-%\begin{center}
 \begin{figure*}[t]
 \centering        
-\includegraphics[scale=0.45]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
+\includegraphics[scale=0.45]{PRL_plot1.pdf}
+\caption{(Color online).
+The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
 with a bin width of $\pm 5^{\circ}$.
@@
 \end{figure*}
-%\end{center}
-%\twocolumngrid
 \indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
@@
 For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
-%-----Mention the fofa parametrizations used in each of the calculations------
 The MS calculations used the FF parametrization of Ref.
@@
 \begin{figure}[!t]
-\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
-\caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
+\includegraphics[scale=0.5]{PRL_plot2.pdf}
+\caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
 The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
@@
 
-%-------------------------------
+\bibliography{prl}
+\end{document}

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updateed PRL submission docs

@@
 %The good agreement gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist. \\
-\indent The systematic uncertainties of the measured cross sections were determined from 
+\indent The systematic uncertainties on the measured cross sections were determined from 
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
@@
 the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
-to define the overall normalization uncertainty ($\leq$ 8.4$\%$).\\
+to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
 %\indent The systematic uncertainties due to our finite knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each missing momentum setting,
 %and added in quadrature for overlapping $p_{\mathrm{r}}$ bins.
-\indent The systematic uncertainties on the cross sections due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
+\indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
 determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
-The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 8.4$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties
-to obtain the final uncertainty on the cross sections.\\
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
 %The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
@@
 \includegraphics[scale=0.45]{prl_plots/PRL_plot1.pdf}
-\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
+\caption{(Color online).
+The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively,
 with a bin width of $\pm 5^{\circ}$.
@@
 \includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}
-\caption{The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
+\caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
 The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}

### 2020-08-18 UTILITIES_CODES/codes/THESIS/plot_momentum_dist.py

@@ -569,7 +569,7 @@ def plot_momentum_dist():
         #======================END PRL PLOTS==============
 
 
-        '''
+        
         
         #----------------------PRODUCE PLOTS FOR THESIS----------
         
@@ -825,7 +825,7 @@ def plot_momentum_dist():
         B.pl.savefig(dir_name1+'/redXsec_thnq%i_deg.pdf'%(ithnq))
 
         #B.pl.show()
-        '''
+       
 
         
         '''
@@ -878,6 +878,7 @@ def plot_momentum_dist():
         #B.pl.show()
         B.pl.tight_layout()
 
+        '''
 
         #-----------------------------WRITE DATA REDUCED XSEC TO WRITE IN THESIS KINEMATICS TABLE----------------------------------
         #Create output files to write relative uncertainties for (Pm) bins for each th_nq setting for kinematic bin Q2 = 3.5 +/- 0.5
@@ -927,7 +928,7 @@ def plot_momentum_dist():
             fout_4to5.write(line)
         fout_4to5.close()
 
-
+        '''
         
         #-----------------------------WRITE DATA 5-FOLD DIFFERENTIAL XSEC (PER DATASET) TO WRITE IN THESIS KINEMATICS TABLE----------------------------------
         #Create output files to write relative uncertainties for (Pm) bins for each th_nq setting for kinematic bin Q2 = 3.5 +/- 0.5
@@ -949,7 +950,7 @@ def plot_momentum_dist():
         fout_3to4.close()
         
         #=============================END CODE TO PRODUCE THESIS PLOTS================================
-        '''
+       
 
 
         #DO LINE FITS OF Pr = 550 - 1000 MeV/c
@@ -1384,10 +1385,10 @@ def plot_momentum_dist():
             B.pl.legend(loc='upper right', fontsize='small')
             B.pl.show()
             
-            '''
-            #-------FITTING: Plot the Ratio  sig_red_exp(pm) / sig_red_exp(p0=0.5 GeV/c) for pm >=0.5 GeV/c (same for models), to compare shapes------
+        '''
+        #-------FITTING: Plot the Ratio  sig_red_exp(pm) / sig_red_exp(p0=0.5 GeV/c) for pm >=0.5 GeV/c (same for models), to compare shapes------
             
-            
+        '''
             fp = np.array([0.5, 0.82])
             for j in range(len(fp)):
                 B.pl.clf()                                                                                                          

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/authorlist.tex
updated article submission docs

--- 2020-07-27 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/authorlist-rev.tex
@@
 %Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
-%Comment / Uncomment accordingly
-\author{C.~Yero$^{1}$}       %Main author for E12-10-003 experiment
-\author{D.~Abrams$^{2}$}           %Commissioning ONLY
-\author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
-\author{A.~Ahmidouch$^{4}$}        % . . .----> HOLLY
-\author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
-\author{S.~Alsalmi$^{5}$}          %Commissioning ONLY
-\author{R.~Ambrose$^{3}$}          %Commissioning + SIDIS
-%\author{D.~Androic}         %Color Transparency ONLY
+\author{C.~Yero$^{1,15}$}       %Main author for E12-10-003 experiment
+\homepage[ORCiD: ]{https://orcid.org/0000-0003-2822-7373}
+\email[email: ]{cyero@jlab.org}
+\author{D.~Abrams$^{2}$}           
+\author{Z.~Ahmed$^{3}$}            
+\author{A.~Ahmidouch$^{4}$}        
+\author{B.~Aljawrneh$^{4}$}        
+\author{S.~Alsalmi$^{5}$}          
+\author{R.~Ambrose$^{3}$}          
+\author{W.~Armstrong$^{6}$}        
+\author{A.~Asaturyan$^{7}$}        
+\author{K.~Assumin-Gyimah$^{8}$}   
+\author{C.~Ayerbe Gayoso$^{9}$}    
+\author{A.~Bandari$^{9}$}          
+\author{J.~Bane$^{10}$}            
+\author{S.~Basnet$^{3}$}           
+\author{V.V.~Berdnikov$^{11}$}     
+\author{J.~Bericic$^{15}$}         
+\author{H.~Bhatt$^{8}$}            
+\author{D.~Bhetuwal$^{8}$}         
+\author{D.~Biswas$^{12}$}          
+\author{W.U.~Boeglin$^{1}$}        
+\author{P.~Bosted$^{9}$}           
+\author{E.~Brash$^{13}$}           
+\author{M.H.S.~Bukhari$^{14}$}     
+\author{H.~Chen$^{2}$}             
+\author{J.P.~Chen$^{15}$}          
+\author{M.~Chen$^{2}$}             
+\author{M.E.~Christy$^{12}$}       
+\author{S.~Covrig$^{15}$}          
+\author{K.~Craycraft$^{10}$}       
+\author{S.~Danagoulian$^{4}$}      
+\author{D.~Day$^{2}$}             
+\author{M.~Diefenthaler$^{15}$}    
+\author{M.~Dlamini$^{17}$}         
+\author{J.~Dunne$^{8}$}
+\author{B.~Duran$^{16}$}          
+\author{D.~Dutta$^{8}$}          
+\author{R.~Ent$^{15}$}            
+\author{R.~Evans$^{3}$}           
+\author{H.~Fenker$^{15}$}         
+\author{N.~Fomin$^{10}$}          
+\author{E.~Fuchey$^{18}$}         
+\author{D.~Gaskell$^{15}$}        
+\author{T.N.~Gautam$^{12}$}       
+\author{F.A.~Gonzalez$^{19}$}     
+\author{J.O.~Hansen$^{15}$}       
+\author{F.~Hauenstein$^{20}$}     
+\author{A.V.~Hernandez$^{11}$}    
+\author{T.~Horn$^{11}$}           
+\author{G.M.~Huber$^{3}$}         
+\homepage[ORCiD: ]{http://orcid.org/0000-0002-5658-1065}
+\author{M.K.~Jones$^{15}$}         
+\author{S.~Joosten$^{6}$}          
+\author{M.L.~Kabir$^{8}$}            
+\author{A.~Karki$^{8}$}           
+\author{C.E.~Keppel$^{15}$}          
+\author{A.~Khanal$^{1}$}       
+\author{P.~King$^{17}$}             
+\author{E.~Kinney$^{21}$}           
+\author{N.~Lashley-Colthirst$^{12}$}     
+\author{S.~Li$^{22}$}               
+\author{W.B.~Li$^{9}$}              
+\author{A.H.~Liyanage$^{12}$}       
+\author{D.J.~Mack$^{15}$}           
+\author{S.P.~Malace$^{15}$}         
+\author{J.~Matter$^{2}$}           
+\author{D.~Meekins$^{15}$}          
+\author{R.~Michaels$^{15}$}         
+\author{A.~Mkrtchyan$^{7}$}        
+\author{H.~Mkrtchyan$^{7}$}        
+\author{S.J.~Nazeer$^{12}$}         
+\author{S.~Nanda$^{8}$}           
+\author{G.~Niculescu$^{23}$}        
+\author{M.~Niculescu$^{23}$}        
+\author{D.~Nguyen$^{2}$}           
+\author{N.~Nuruzzaman$^{24}$}       
+\author{B.~Pandey$^{12}$}           
+\author{S.~Park$^{19}$}             
+\author{C.F.~Perdrisat$^{9}$}       
+\author{E.~Pooser$^{15}$}           
+\author{M.~Rehfuss$^{16}$}          
+\author{J.~Reinhold$^{1}$}         
+\author{B.~Sawatzky$^{15}$}         
+\author{G.R.~Smith$^{15}$}          
+\author{A.~Sun$^{25}$}              
+\author{H.~Szumila-Vance$^{15}$}    
+\author{V.~Tadevosyan$^{7}$}        
+\author{S.A.~Wood$^{15}$}           
+\author{J.~Zhang$^{19}$}
 
-\author{W.~Armstrong$^{6}$}        %Commissioning ONLY
-\author{A.~Asaturyan$^{7}$}        %Commissioning ONLY
-\author{K.~Assumin-Gyimah$^{8}$}   %Commissioning ONLY
-\author{C.~Ayerbe Gayoso$^{9}$}    %Commissioning + SIDIS
-\author{A.~Bandari$^{9}$}          %Commissioning + SIDIS
-\author{J.~Bane$^{10}$}             %Deuteron Experiment ONLY
-\author{S.~Basnet$^{3}$}           %Commissioning + SIDIS
-\author{V.V.~Berdnikov$^{11}$}        %Commissioning + SIDIS  (tell HOLLY name change)
-\author{J.~Bericic$^{15}$}          %SHMS Optics Contributor  HOLLY
-\author{H.~Bhatt$^{8}$}            %Commissioning + SIDIS
-\author{D.~Bhetuwal$^{8}$}         %Commissioning + SIDIS
-\author{D.~Biswas$^{12}$}           %Commissioning + SIDIS
-\author{W.U.~Boeglin$^{1}$}          %Commissioning ONLY (Deuteron Spokesperson)
-\author{P.~Bosted$^{9}$}           %Commissioning ONLY (SIDIS Spokesperson)
-\author{E.~Brash$^{13}$}            %Commissioning ONLY
-\author{M.H.S.~Bukhari$^{14}$}          %Commissioning ONLY
-%\author{M.~Carmignotto}     %NO MINIMUM SHIFTS
-\author{H.~Chen$^{2}$}             %Commissioning ONLY
-\author{J.P.~Chen$^{15}$}           %Commissioning ONLY
-\author{M.~Chen$^{2}$}             %Commissioning ONLY
-\author{M.E.~Christy$^{12}$}          %Commissioning ONLY
-\author{S.~Covrig$^{15}$}           %Commissioning + SIDIS               
-\author{K.~Craycraft$^{10}$}        %Commissioning + SIDIS
-\author{S.~Danagoulian$^{4}$}            %NO MINIMUM SHIFTS. Contributed to detectros
-\author{D.~Day$^{2}$}             %ONLY DEC. 2017 Spec. Commissioning Contributed to Noble Gas Detector
-\author{M.~Diefenthaler$^{15}$}     %Commissioning + SIDIS
-\author{M.~Dlamini$^{17}$}          %Commissioning ONLY
-\author{J.~Dunne$^{8}$}
-%Commissioning ONLY
-\author{B.~Duran$^{16}$}            %Commissioning + SIDIS
-\author{D.~Dutta$^{8}$}            %Commissioning + SIDIS  (CT Spokesperson)
-\author{R.~Ent$^{15}$}              %NO MINIMUM SHIFTS JLab Physics Division Leader (SIDIS Co-Spokesperson) (should be included)??????
-\author{R.~Evans$^{3}$}            %Commissioning ONLY
-\author{H.~Fenker$^{15}$}           %Commissioning + SIDIS
-%\author{I.~Fernando}        %NO MINIMUM SHIFTS
-\author{N.~Fomin$^{10}$}            %Commissioning ONLY
-\author{E.~Fuchey$^{18}$}           %Commissioning ONLY
-\author{D.~Gaskell$^{15}$}          %Commissioning + SIDIS
-\author{T.N.~Gautam$^{12}$}         %Commissioning ONLY
-\author{F.A.~Gonzalez$^{19}$}       %Commissioning + SIDIS
-\author{J.O.~Hansen$^{15}$}           %Commissioning ONLY
-\author{F.~Hauenstein$^{20}$}       %Commissioning ONLY
-\author{A.V.~Hernandez$^{11}$}       %Commissioning ONLY
-\author{T.~Horn$^{11}$}             %Commissioning ONLY
-\author{G.M.~Huber$^{3}$}            %Commissioning ONLY
-\homepage[ORCiD: ]{http://orcid.org/0000-0002-5658-1065}
-\author{M.K.~Jones$^{15}$}          %Commissioning + SIDIS
-\author{S.~Joosten$^{6}$}          %Commissioning ONLY
-\author{M.L.~Kabir$^{8}$}          %Commissioning + SIDIS           
-%\author{N.~Kalantarians}    %NO MINIMUM SHIFTS
-\author{A.~Karki$^{8}$}            %Commissioning + SIDIS  
-\author{C.E.~Keppel$^{15}$}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
-\author{A.~Khanal$^{1}$}           %Commissioning ONLY
-\author{P.~King$^{17}$}             %Commissioning ONLY
-\author{E.~Kinney$^{21}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)
-%\author{H.S.~Ko}            %Color Transparency ONLY
-%\author{M.~Khol}            %NO MINIMUM SHIFTS
-\author{N.~Lashley-Colthirst$^{12}$}      %Commissioning ONLY
-\author{S.~Li$^{22}$}               %Commissioning ONLY
-\author{W.B.~Li$^{9}$}               %Commissioning ONLY  tell HOLLY name change
-\author{A.H.~Liyanage$^{12}$}       %Commissioning + SIDIS
-\author{D.J.~Mack$^{15}$}             %Commissioning + SIDIS
-\author{S.P.~Malace$^{15}$}           %Commissioning + SIDIS (F2 Spokesperson)
-%\author{P.~Markowitz}       %NO MINIMUM SHIFTS
-\author{J.~Matter$^{2}$}           %Commissioning + SIDIS
-\author{D.~Meekins$^{15}$}          %NO MINIMUM SHIFTS (TARGET WORK DURING COMMISSIONING+SIDIS. (INCLUDED AS AUTHOR!)
-\author{R.~Michaels$^{15}$}         %Commissioning + SIDIS
-\author{A.~Mkrtchyan$^{7}$}        %Commissioning ONLY     HOLLY
-\author{H.~Mkrtchyan$^{7}$}        %Commissioning ONLY
-\author{S.J.~Nazeer$^{12}$}         %Commissioning ONLY
-\author{S.~Nanda$^{8}$}           %Spec. commissioning only Dec. 14-17 shifts
-\author{G.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
-\author{M.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
-\author{D.~Nguyen$^{2}$}           %Commissioning ONLY (Took 10 shifts) 
-\author{N.~Nuruzzaman$^{24}$}       %Commissioning ONLY
-\author{B.~Pandey$^{12}$}           %NO MINIMUM SHIFTS (WORKED ON HMS DCs for 1 year. INCLUDED AS AUTHOR!)
-\author{S.~Park$^{19}$}             %Commissioning + SIDIS
-\author{C.F.~Perdrisat$^{9}$}            %College of William & Mary   HOLLY
-\author{E.~Pooser$^{15}$}           %Commissioning + SIDIS
-%\author{A.~Puckett}         %NO MINIMUM SHIFTS
-\author{M.~Rehfuss$^{16}$}          %Commissioning ONLY
-\author{J.~Reinhold$^{1}$}         %Commissioning ONLY
-%\author{N.~Santiesteban}     %Color Transparency ONLY
-\author{B.~Sawatzky$^{15}$}          %Color Transparency ONLY (Worked on DAQ/Detector. INCLUDED AS AUTHOR!)
-\author{G.~Smith$^{15}$}             %Commissioning ONLY
-\author{A.~Sun$^{25}$}               %Commissioning + SIDIS
-\author{H.~Szumila-Vance$^{15}$}     %Commissioning + SIDIS
-%\author{A.~Tadepalli}        %F2 ONLY
-\author{V.~Tadevosyan$^{7}$}        %Commissioning + SIDIS
-%\author{R.~Trotta}           %NO MINIMUM SHIFTS
-\author{S.A.~Wood$^{15}$}            %NO MINIMUM SHIFTS (Hall C Deputy + Worked on Hall C 12 GeV software + hardware work) (INCLUDED AS AUTHOR!)
-\author{J.~Zhang$^{19}$}        %Commissioning ONLY 
-%\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
-
+\collaboration{for the Hall C Collaboration}
 \affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
@@
 \affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
-\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}   %fixed address for Whit and Sylvester
+\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}  
 \affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/cover_letter/cl.tex
updated article submission docs

@@
 \begin{document}
-\begin{letter}{Carlos Yero\\
-Thomas Jefferson National Accelerator Facility\\
-12000 Jefferson Avenue \\
-Newport News, VA 23602\\
-(786) 387-8667 \\
-cyero@jlab.org
+\begin{letter}{
+    Dr. Michael Thoennessen\\
+    Editor-in-Chief, APS Editorial Office \\
+    \textit{Physical Review Letters} (PRL)\\
     }
 
-\opening{Dear Editors,\\}
+\opening{Dear Dr. Thoennessen,\\}
 
-I hereby submit a manuscript entitled ``Probing the Deuteron at Very Large Internal Momenta'' to be considered
-for publication by \textit{Physical Review Letters}. There are eight files in all: the main manuscript file (prl.tex), 2 figure files (.pdf),
-a biblipgraphy file (.bbl), an author list file (.tex), and three supplementary (.txt) files with the numerical results of the
-cross sections evaluated at the relevant kinematics described in the manuscript.\\
+I hereby submit a manuscript entitled ``Probing the Deuteron at Very Large Internal Momenta'' to be considered for publication by \textit{Physical Review Letters}.
+There are eight files in all: the main manuscript file (ms.tex), 2 figure files (.pdf), a bibliography file (.bbl), an author list file (.tex), and three supplementary (.txt)
+files with the numerical results of the cross sections evaluated at the relevant kinematics described in the manuscript.\\
 
-We report cross-section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
+We report cross section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
 double the maximum recoil momentum measured in a previous deuteron electro-disintegration experiment carried out in Hall A at Jefferson Lab. 
-That experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
-reduced and the plane wave impulse approximation (PWIA) provided the dominant contribution to the cross section. This experiment focused
-on the kinematic window (where FSI are small) found by the Hall A experiment and extended the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
-access to the high momentum component of the deuteron wave-function, or equivalently, the nucleon-nucleon ($NN$) interaction at the sub-Fermi
-distance scale which is currently poorly understood.\\
+The Hall A experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
+reduced and the plane wave impulse approximation (PWIA) provides the dominant contribution to the cross section. This experiment focuses
+on the kinematic window (where FSI are small) previously found in Hall A and extends the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
+direct access to the high momentum component of the deuteron wave-function. This is a crucial step forward in the understanding the nucleon-nucleon ($NN$) interaction at
+the sub-Fermi distance scale which is currently poorly understood. We believe these findings will be of general interest to the readers of your journal.\\
 
-This Letter summarizes the experimental results of cross-section measurements that extended the neutron recoil momentum measured up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c giving a direct access
-to the shot-range structure of the deuteron wave-function which is a crucial step forward in the understanding the $NN$ interaction at very small ($\leq$1 fm) distances. We believe these
-findings will be of general interest to the readers of your journal.\\
-
-We declare that this manuscript is original, has not been published before and is not currently being considered for publication elsewhere.\\
+We declare that this manuscript is original, has not been published before in a peer-reviewed journal and is not currently being considered for publication elsewhere.\\
 \\
@@
 %electronically were "signed."  
+Carlos Yero\\
+Hall C Postdoctoral Research Fellow\\
+Thomas Jefferson National Accelerator Facility\\
+12000 Jefferson Avenue \\
+Newport News, VA 23602\\
+e-mail: cyero@jlab.org\\
+phone: (786) 387-8667
 
-Carlos Yero\\
-Hall C Postdoctoral Fellow\\
 \end{letter}

### 2020-08-19 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/cover_letter/cl.tex
updated

@@
 
-We report cross section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
+We report cross-section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
 double the maximum recoil momentum measured in a previous deuteron electro-disintegration experiment carried out in Hall A at Jefferson Lab.
-The Hall A experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
-reduced and the plane wave impulse approximation (PWIA) provides the dominant contribution to the cross section. This experiment focuses
-on the kinematic window (where FSI are small) previously found in Hall A and extends the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
-direct access to the high momentum component of the deuteron wave-function. This is a crucial step forward in the understanding the nucleon-nucleon ($NN$) interaction at
+That experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are significantly
+smaller and the plane wave impulse approximation (PWIA) provides the dominant contribution to the cross section. This experiment focuses
+on the kinematic window (where FSI are small) found in Hall A and extends the neutron recoil momentum range beyond $p_{\mathrm{r}}\sim500$ MeV/c, giving
+direct access to the short-range structure of the deuteron. This is a crucial step forward in the understanding the nucleon-nucleon ($NN$) interaction at 
 the sub-Fermi distance scale which is currently poorly understood. We believe these findings will be of general interest to the readers of your journal.\\

### 2020-08-19 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/word_count/ms.tex
updated

--- 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl.tex
@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootinbib]{revtex4-1}  % for review and submission
 \pdfoutput=1 
@@
 \pacs{25.30.Fj, 25.60.Gc}
-\maketitle
+%\maketitle
 
@@
 The experimental and theoretical reduced cross sections were extracted and are defined as follows:
-\begin{equation}
-\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
-\label{eq:1}
-\end{equation}
+%\begin{equation}
+%\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
+%\label{eq:1}
+%\end{equation}
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
@@
 momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
-\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
-as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
-thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
-discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
-under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
-under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
+%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
+%to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
+%thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
+%discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+%under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
+%under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
 
-\bibliography{prl}
 \end{document}
+\bibliography{ms}

### 2020-08-30 MY_THESIS/HallC_12GeV_Trigger/version3/trigger_v3.tex
updated trigger doc

--- 2019-07-17 MY_THESIS/HallC_12GeV_Trigger/version2/trigger_v2.tex
@@
 \usepackage{float}
+\usepackage{xcolor}
 
@@
 \newcommand{\comment}[1]{}
+
+\begin{center}
+  \vspace*{\stretch{1}}
+  \textbf{\noindent \large \textcolor{red}{DISCLOSURE: \\ THE ELECTRONIC DIAGRAMS SHOWN IN THE MAIN TEXT ARE UPDATED AND CORRESPOND TO THE ELECTRONICS DIAGRAMS USED IN A1N/D2N EXPERIMENTS AS OF FALL 2019 - FALL 2020.
+THE CHANGES ARE MINOR, HOWEVER, IF YOUR EXPERIMENT RAN BEFORE FALL 2019, PLEASE REFER TO SECTION 6 (PAGE 17) OF THIS DOCUMENT FOR CLARIFICATION OF THE CHANGES MADE.}}
+  \vspace*{\stretch{1}}
+\end{center}
+\newpage
 
@@
 \end{figure}
+
 \newpage
@@
 Additional particle detectors may also be incorporated into the HMS trigger as required by different experiments. The Gas \v{C}erenkov and Calorimeter triggers will be
-used for e/$\pi$ separation, whereas the Aerogel \v{C}erenkov trigger will be used for $\pi$/K/p separation.
+used for $e/\pi$ separation, whereas the Aerogel \v{C}erenkov trigger will be used for $\pi/K/p$ separation.
 
@@
   \centering
-  \includegraphics[scale=0.5]{hHODO_diagram.png}
+  \includegraphics[scale=0.35]{./hHODO_diagram.png}
   \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}
@@
   \centering
-  \includegraphics[scale=0.5]{hCAL_diagram.png}
+  \includegraphics[scale=0.35]{./hCAL_diagram.png}
   \caption{HMS Calorimeter Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA2}}
@@
 \noindent The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
-read out 13 signals/layer on one side. The first two layers form the Pre-Shower Counter while all four layers (A, B, C and D) form the Shower Counter.  
+read out 13 signals/layer on one side. The first layer form the Pre-Shower counter while all four layers (A, B, C and D) form the Shower counter.  
 Each layer is read out in the Counting Room patch and fed into 50:50 splitters. One output of the splitter is fed to fADCs via a Ribbon-to-BNC converter (same as hodoscopes)
@@
 A copy of each layer sum is sent to fADCs.
-The Pre-Shower SUM is then made from the sum of layers A and B, while the Shower SUM is made by summing all four layers.
-A copy of the PreShower and Shower sums is also sent to fADCs.
+The Pre-Shower SUM is then made from the sum of layer A, while the Shower SUM is made by summing all four layers.
+A copy of the Pre-Shower and Shower sums is also sent to fADCs.
 The Pre-Shower and Shower sums are then sent to a P/S Model 715
@@
   \centering
-  \includegraphics[scale=0.5]{hCER_diagram.png}
+  \includegraphics[scale=0.35]{./hCER_diagram.png}
   \caption{HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov. For original diagram, see Appendix \ref{appendix:Appx3} }
@@
   \centering
-  \includegraphics[scale=0.5]{HMS_SingleArm_diagram.png}
+  \includegraphics[scale=0.35]{HMS_SingleArm_diagram.png}
   \caption{HMS Single Arm Pre-Trigger Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx5}}
@@
   \centering
-  \includegraphics[scale=0.5]{pHODO_diagram.png}
+  \includegraphics[scale=0.35]{pHODO_diagram.png}
   \caption{SHMS Hodoscopes Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx6}}
@@
 \end{figure}
-
 Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:shms_stack}), so each bar reads out two signals.
@@
 & \text{S2X = S2XL (13-fold OR) \textit{AND} S2XR (13-fold OR)} \\ 
-  & \text{S2Y = \big\{S2Y[1-16]T OR S2Y[17-21]T\big\} \textit{AND} \big\{S2Y[1-16]B OR S2Y[17-21]B\big\}}
+  & \text{S2Y = \big\{S2Y[1-16]T OR S2Y[17-21]T\big\} \textit{AND} \big\{S2Y[1-16]B OR S2Y[17-21]B\big\}}\footnotemark
 \end{empheq}
-
+\footnotetext{The SHMS S2Y (quartz) plane has 5 non-functional PMT channels on each side of the plane. In other words, it had up to 16 functional channels/side.}
 \indent Once a pre-trigger has been made for each plane, they are sent to a NIM/ECL converter (Level Translator - Phillips Scientific (or P/S) Model 7126) via twisted pair cables to convert the ECL signal
@@
   \centering
-  \includegraphics[scale=0.5]{pCAL_diagram.png}
+  \includegraphics[scale=0.35]{pCAL_diagram.png}
   \caption{SHMS PreShower / Shower Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx7}}
@@
   \centering
-  \includegraphics[scale=0.5]{pCER_diagram.png}
+  \includegraphics[scale=0.35]{pCER_diagram.png}
   \caption{SHMS Gas \v{C}erenkovs Electronics Diagram.}
@@
   \centering
-  \includegraphics[scale=0.5]{SHMS_SingleArm_diagram.png}
+  \includegraphics[scale=0.35]{SHMS_SingleArm_diagram.png}
   \caption{SHMS Single Arm Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx8}.}
@@
   \centering
-  \includegraphics[scale=0.5]{Coin_diagram.png}
+  \includegraphics[scale=0.35]{Coin_diagram.png}
   \caption{Coincidence Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx9}}
@@
 The TIs then distribute the accepted trigger to all modules of their respective crates.
+
+\section{Electronic Dead Time Monitoring (EDTM)}\label{sec:edtm}
+\noindent The EDTM system is a new method used in Hall C to measure the total dead time of the data acquisition (DAQ) system. It consists of introducing a controlled (fixed frequency) pulse
+as near as possible to the detectors that form part of the trigger. Ideally, one would send the EDTM pulses at the detector level in the hut such that both the real physics and EDTM signals
+pass through the same electronics. Since this is not easy or practical to do, the EDMT logic pulses are injected at the trigger logic level in the Counting Room.\\
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.54]{EDTM_diagram.png}
+  \caption{EDTM electronics diagram.}
+  \label{fig:EDTM_diagram}
+\end{figure}
+\indent By design, the EDTM is a \textit{real} trigger as measured by the electronics and readout systems. Since the EDTM is invasive to the trigger electronics, its frequency should be small
+enough to minimize the probability of blocking actual physics triggers, but sufficiently large to gather the necessary statistics for a precise \textit{dead time} measurement during the course of a run.
+\\
+\indent Figure \ref{fig:EDTM_diagram} shows a simplified diagram of the EDTM signal distribution through the trigger electronics. The EDTM logic signals (purple) are injected into the trigger logic
+where they mix with the physics pre-triggers (magenta). A separate copy of the EDTM is also sent to scalers/TDCs to be used in the dead time calculation. If the
+EDTM makes it to the front-end of the Trigger Interface (TI) module and gets accepted (L1 Accept), it has esentially measured both the electronics and computer dead time.\\
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.40]{EDTM_TI.png}
+  \caption{Cartoon representation of EDTM (purple) and physics (magenta) pre-triggers at the TI module front-end.}
+  \label{fig:EDTM_TI}
+\end{figure}\\
+\indent Figure \ref{fig:EDTM_TI} shows the random physics (magenta) and clocked (purple) EDTM pulses at an input channel of the TI front-end where the EDTM has
+been set to a sufficiently large frequency ($1/T_{\mathrm{clk}}$) to ensure that enough EDTM signals get accepted in order to make a statistically significant and
+reliable dead time calculation.
+In this example, an EDTM signal has been accepted by the TI which triggered a \textit{BUSY} signal for a time $\tau$ during which all other incoming pre-triggers are blocked
+contributing to the DAQ computer dead time. The accepted pre-triggers are distributed to all ROCs for data readout. \\
+\indent Over the course of a run, the total dead time ($T_{\mathrm{TDT}}$), or alternatively, the total live time ($T_{\mathrm{TLT}}$) in terms of the EDTM is defined as
+\begin{equation}
+ T_{\mathrm{TDT}} \equiv 1 - T_{\mathrm{TLT}} = 1 - \frac{N_{\mathrm{edtm,acc}}}{N_{\mathrm{edtm,scl}}},
+  \label{eq:3.24}
+\end{equation}
+where $N_{\mathrm{edtm,acc}}$ is the number of accepted EDTM counts obtained by requiring a non-zero hit on the EDTM TDC spectrum, and $N_{\mathrm{edtm,scl}}$ is the number of EDTM scaler counts regardless of whether or not
+the EDTM was accepted.
+In reality, frequent beam trips occur during the course of a run which makes this calculation biased since one can measure live times of $\sim$100$\%$ during beam-off periods as only
+the EDTM signal (and cosmic rays) are measured. To eliminate this bias, the live time calculation was done by making a software cut on the beam current above a certain threshold.
+Furthermore, since the EDTM events are generated by a clock, rather than a poisson source, it introduces an additional bias since the EDTM cannot block itself.
+To account for this bias, an additional correction
+to the total live time was derived and can be found in Ref.\cite{DMack_livetime_2019}.
+This correction, however, is negligible provided that the EDTM rate is sufficiently low as was the case for this experiment ($\sim 2$ Hz).
+\\
+\indent Even though only the total live time is required as a correction factor in the measured cross section, one may also calculate the computer live time defined as
+\begin{equation}
+  T_{\mathrm{CLT}} = \frac{N_{\mathrm{phy,acc}}}{N_{\mathrm{phy,scl}}},
+  \label{eq:3.25}
+\end{equation}
+where $N_{\mathrm{phy,acc}}$ is the number of accepted physics triggers obtained by requiring a zero hit on the EDTM TDC spectrum (EDTM rejected by TI) and $N_{\mathrm{phy,scl}}$ is the number of physics trigger scaler counts after
+having subtracted the EDTM scaler counts. The electronic live time can then be obtained from the following formula:
+\begin{equation}
+  T_{\mathrm{TLT}} = T_{\mathrm{CLT}} \cdot T_{\mathrm{ELT}},
+  \label{eq:3.26}
+\end{equation}
+where $T_{\mathrm{ELT}}$ is the electroninc live time expressed as a fraction (not percent). \\
+\indent For a more detailed discussion on the live time calculations and its correction factors
+see Refs.\cite{pooser_livetime_2019,DMack_livetime_2019}.
+\newpage
+\textcolor{red}{\section{Notes on Changes to the Trigger}}\label{sec:trg_ch}
+\indent In Hall C, each spectrometer has multiple pre-triggers (HODO 3/4, STOF, EL-REAL, EL-CLEAN) that may change depending on the nature of the experiment.
+The base pre-trigger is the HODO 3/4, which requires at least 3 of 4 hodoscope planes to fire. Since the commissioning phase (Fall 2017) of the spectrometers, the trigger
+electronics has had three major modifications up to the present time (Fall 2020) described below.\\
+\indent During the commissioning phase of the spectrometers, the reference time logic was initially defined to be:
+\begin{align}
+  T^{\mathrm{logic}}_{\mathrm{reftime,init}} \equiv &\textbf{ p(h)HODO 3/4} \text{ OR } \textbf{p(h)STOF} \nonumber  \\
+  &\text{ OR } \textbf{p(h)EL-REAL} \text{ OR } \textbf{p(h)EL-CLEAN}
+  \label{eq:refTime_def1}
+\end{align}
+where the logic pre-trigger signals described in Eq.
+\ref{eq:refTime_def1} have been delayed in time relative to each other and the \textbf{p(h)} refers to prefix used in the software to denote the SHMS (HMS).\\
+\subsection{January, 2018: Removal of STOF from Reference Time Definition}\label{ssec:jan2018}
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.38]{./Jan2018_trigger_change.png}
+  \caption{The STOF was removed from the reference time definition in both spectrometers (HMS/SHMS) on January 23, 2018.
+See HC-Log Entry (for HMS):\url{https://logbooks.jlab.org/entry/3519686}.
+Note: The trigger
+  electronics is shown for HMS, but also applies to the SHMS.}
+  \label{fig:stof_refTime_remove}
+\end{figure}
+On January 2018, the STOF reference time was removed from the original reference time definition (see Eq.\ref{eq:refTime_def1}), and the reference time was redefined as
+\begin{align}
+  T^{\mathrm{logic}}_{\mathrm{reftime,Jan18}} \equiv &\textbf{ p(h)HODO 3/4} \text{ OR } \textbf{p(h)EL-REAL} \text{ OR } \textbf{p(h)EL-CLEAN}
+  \label{eq:refTime_def2}
+\end{align}
+\subsection{August, 2018: Removal of EL-CLEAN from Reference Time Definition}\label{ssec:aug2018}
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.38]{./Aug2018_trigger_change.png}
+  \caption{The EL-CLEAN was removed from the reference time definition in both spectrometers (HMS/SHMS) on August 09, 2018.
+See HC-Log Entry:\url{https://logbooks.jlab.org/entry/3585301}.
+Note: The trigger
+  electronics is shown for HMS, but also applies to the SHMS.}
+  \label{fig:elclean_refTime_remove}
+\end{figure}
+On August 2018, EL-CLEAN was removed from the reference time definition. It was determined that any pre-trigger that required the HODO 3/4 was unnecessary and redundant to have in the
+reference time definition so it was removed. The reference time was redefined once again as follows:
+\begin{align}
+  T^{\mathrm{logic}}_{\mathrm{reftime,Aug18}} \equiv &\textbf{ p(h)HODO 3/4} \text{ OR } \textbf{p(h)EL-REAL}
+  \label{eq:refTime_def3}
+\end{align}
+\subsection{December, 2019: Removal of STOF from trigger / Removal of EL-REAL from Reference Time Definition}\label{ssec:dec2019}
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.38]{./Dec2019_trigger_change.png}
+  \caption{The STOF was removed from electronics trigger and EL-REAL was removed from the reference time definition in both spectrometers (HMS/SHMS) on Dec 06, 2019.
+See the \textit{highlights} section of
+    HC-Log Entry:\url{https://logbooks.jlab.org/entry/3747761}. Note: The trigger
+  electronics is shown for HMS, but also applies to the SHMS.}
+  \label{fig:elreal_refTime_remove}
+\end{figure}
+\indent On early December 2019, before the start of the A1n/d2n experimental run periods, the STOF was removed from the trigger definition in both spectrometers.
+Since STOF trigger was removed, the EL-REAL now requires a HODO 3/4 and it was determined that this reference time (EL-REAL) was no longer needed so it was removed
+from the reference time definition as well. The reference time was redefined as follows:
+\begin{align}
+  T^{\mathrm{logic}}_{\mathrm{reftime,Dec19}} \equiv &\textbf{ p(h)HODO 3/4}
+  \label{eq:refTime_def4}
+\end{align}
+\newpage
+\subsection{Electronics Trigger Oscilloscope Traces}\label{ssec:traces}
+For a visual representation of the trigger logic signals discussed, see a summary of the various trigger oscilloscope traces taken since the start of the commissioning phase:\\
+\newline
+\noindent \textbf{December 2017:}\\
+SHMS: \url{https://logbooks.jlab.org/entry/3508587}\\
+HMS: \url{https://logbooks.jlab.org/entry/3504470}\\
+
+\noindent \textbf{September 2018:}\\
+SHMS: \url{https://logbooks.jlab.org/entry/3599311}\\
+HMS: \url{https://logbooks.jlab.org/entry/3599283}\\
+
+\noindent \textbf{February 2019:}\\
+SHMS: \url{https://logbooks.jlab.org/entry/3655622}\\
+HMS: \url{https://logbooks.jlab.org/entry/3655644}\\
+
+\noindent \textbf{December 2019:}\\
+SHMS: \url{https://logbooks.jlab.org/entry/3752072}\\
+HMS: \url{https://logbooks.jlab.org/entry/3752087}\\
+
 \newpage
 \onecolumn
-\bibliography{trigger_v2}
+\bibliography{trigger_v3}
 \bibliographystyle{acm}

### 2020-08-30 UTILITIES_CODES/codes/THESIS/make_prl_plots.py

@@ -549,7 +549,9 @@ def make_prl_plots():
     #ax2.legend([l1, l2, l3, l4, l5, l6, l7, l8, WJC2_GK_PWBA, WJC2_GK_DWBA, WJC2_AMT_PWBA, WJC2_AMT_DWBA, AV18_GK_PWBA, AV18_GK_DWBA, AV18_AMT_PWBA, AV18_AMT_DWBA, CD_GK_PWBA, CD_GK_DWBA, CD_AMT_PWBA, CD_AMT_DWBA], line_labels, loc='upper right', frameon=False, fontsize=9)      #subplot to use for common legend
 
     line_labels=['This Experiment (Hall C)', 'Hall A Data', 'JML Paris PWIA', 'JML Paris FSI', 'MS AV18 PWBA', 'MS AV18 FSI', 'MS CD-Bonn PWBA', 'MS CD-Bonn FSI', 'JVO WJC2 PWBA', 'JVO WJC2 FSI']
+    #line_labels=['This Experiment (Hall C)', 'Hall A Data', 'JML Paris PWIA', 'JML Paris FSI', 'MS AV18 PWBA', 'MS AV18 FSI', 'MS CD-Bonn PWBA', 'MS CD-Bonn FSI']
     ax2.legend([l1, l2, l3, l4, l5, l6, l7, l8, WJC2_GK_PWBA, WJC2_GK_DWBA], line_labels, loc='upper right', frameon=False, fontsize=12)      #subplot to use for common legend
+    #ax2.legend([l1, l2, l3, l4, l5, l6, l7, l8], line_labels, loc='upper right', frameon=False, fontsize=12)      #subplot to use for common legend
            
 
     #B.pl.show()

### 2020-09-17 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/response_email.txt
added PRL response

Sep 16, 2020   8:16 pm

Re: LV16805
    Probing the deuteron at very large internal momenta
    by C. Yero, D. Abrams, Z. Ahmed, et al.

Dear Dr. Yero,

Your manuscript has been reviewed by our referees. We ask you to
consider the enclosed comments.

While we cannot make a definite commitment, we will probably return
your revised manuscript to the previous referees.

Please accompany your resubmittal with a summary of the changes made,
and a brief response to all recommendations and criticisms.

Yours sincerely,

Kevin Dusling
Associate Editor
Physical Review Letters
Email: prl@aps.org
https://journals.aps.org/prl/

NEWS FROM THE PHYSICAL REVIEW JOURNALS

Announcing a new Physical Review journal: PRX Quantum
https://go.aps.org/2Q0uVwP

Celebrating 50 years of Physical Review A, B, C, and D
https://go.aps.org/2IDjVBM

APS is offering promotional open access fee discounts on most
journals in 2020
https://go.aps.org/3388lYG

P.S. We estimate your paper is too long; see appended form.

WORD COUNT

   The guidelines used to determine the word count can be found at
   http://journals.aps.org/authors/length-guide

  Figure   Aspect Ratio   Wide?   Word Equivalent
     1         2.25        Yes        306
     2         0.66         No        247

WORD COUNT SUMMARY
    Note: Text word count excludes title, abstract, byline, PACS,
          receipt date, acknowledgments, and references.

              Text word count   3428 
        Equations word equiv.     16 
          Figures word equiv.    553
           Tables word equiv.      0
                              ------
                       TOTAL    3997 (Maximum length is 3750)

----------------------------------------------------------------------
Report of Referee A -- LV16805/Yero
----------------------------------------------------------------------

See Attachment: lv16805_report_1_a.pdf

----------------------------------------------------------------------
Report of Referee B -- LV16805/Yero
----------------------------------------------------------------------

This letter gives results on the Deuterium dissociation cross section,
and suggests that there may be a transition to a new regime at
transverse momenta of the order of 1 GeV. This is a very interesting
puzzle lying at the border of nuclear physics and QCD. I did not find
any flaw in the analysis presented, and recommend that this letter be
published in PRL.

### 2020-09-28 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added supplementary plots

%\title{\small \textbf{Supplemental Material: $^{2}$H$(e,e'p)n$ Cross Section Measurements \\for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ }}

%\documentclass[12pt]{article}
%\usepackage{xcolor}
%\usepackage[margin=1in]{geometry}
%\usepackage{hyperref}

%\begin{document}
%\maketitle

%\section{\small Spectrometer Acceptance}
%In Hall C, the spectrometer acceptance is defined by the variables reconstructed at the target: $\delta, Y_{\mathrm{tar}}, X'_{\mathrm{tar}}$ and $Y'_{\mathrm{tar}}$, where

%\end{document}

%----------------------------------------
\documentclass[aps,prl,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\pdfoutput=1 
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}
%

\begin{document}
\title{Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta}
\maketitle

\section{Spectrometer Acceptance}
\section{Event Selection Cuts}
\section{Radiative Corrections}
\section{Bin-Centering Corrections}
\section{Systematic Uncertainty Studies}
\section{Cross-Section Extraction}

%\bibliography{}

\end{document}

### 2020-09-29 PRL_UTILITIES_CODES/codes/deep_codes/add_hist.C
added additional prl plots including Al target background studies, ans syst. effects plots

@@ -3,145 +3,98 @@
 //Script to make comparison between SIMC and Commissioning Data from HallC Spring 2018
 //The comparisons are all charge normalized and corrected for all inefficiencies
 
-void add_hist(int thnq)
+void add_hist()
 {
-
+  
   //gROOT->SetBatch(kTRUE);  
   //gStyle->SetOptStat(1001111);
   gStyle->SetOptStat(0000000);
   string thnq_set;
-  string root_dir_0;
   string root_dir_1;
   string root_dir_2;
+
   string root_dir_3;
   string root_dir_4;
-  string root_dir_5;
 
+  //Deep 580 MeV,  Em_cut (-0.1, -0.04)  -- draw background
+  root_dir_1 = "../../root_files/bkg_study_deep_580set1_Em_cut2/deep_data_histos_pm580_set1_combined.root";
+  root_dir_2 = "../../root_files/bkg_study_deep_580set2_Em_cut2/deep_data_histos_pm580_set2_combined.root";
 
-  if(thnq==-1){
-    //thnq_set = "all_thnq_Q2_4to5";
-    thnq_set = "all_thnq_Q2_4to5_WideEmBINS";
-  }
-  else{thnq_set = Form("thnq%d_Q2_4to5", thnq);}
+  //Deep 580 MeV em_cut (-0.02, 0.04)  -- draw data+background
+  root_dir_3 = "../../root_files/bkg_study_deep_580set1_Em_cut1/deep_data_histos_pm580_set1_combined.root";
+  root_dir_4 = "../../root_files/bkg_study_deep_580set2_Em_cut1/deep_data_histos_pm580_set2_combined.root";
 
-  
-  
-  if(thnq==-1){
-    //root_dir_0 = Form("../../root_files/pm80_fsiXsec_set1_%s/deep_data_histos_pm80_set1_combined.root", thnq_set.c_str());
-    //root_dir_1 = Form("../../root_files/pm580_fsiXsec_set1_%s/deep_data_histos_pm580_set1_combined.root", thnq_set.c_str());
-    //root_dir_2 = Form("../../root_files/pm580_fsiXsec_set2_%s/deep_data_histos_pm580_set2_combined.root", thnq_set.c_str());
-    //root_dir_3 = Form("../../root_files/pm750_fsiXsec_set1_%s/deep_data_histos_pm750_set1_combined.root", thnq_set.c_str());
[…]

### 2020-09-29 PRL_UTILITIES_CODES/root_files/pm80_fsiXsec_set1_all_thnq_Q2_4to5/histproj.C

@@ -1,38 +1,0 @@
-void histproj()
-{
-  TString fname1 = "deep_data_histos_pm80_set1_combined.root";
-  TString fname2 = "deep_data_histos_pm80_set1_combined_radcorr.root";
-  TString fname3 = "deep_simc_histos_pm80_lagetfsi_RadCorrRatio_set1.root";
-
-  TFile *file1 = new TFile(fname1);
-  TFile *file2 = new TFile(fname2);
-  TFile *file3 = new TFile(fname3);
-
-  
-  //Before rad. corr
-  file1->cd();
-  TH2F *h1 = 0;
-  file1->GetObject("H_Pm_vs_thnq", h1);
-  //h1->Draw("colz");
-  TH1D *histo1= h1->ProjectionY("name1",h1->GetXaxis()->FindBin(30.1),h1->GetXaxis()->FindBin(39.9),"");
-  histo1->Draw();
-
-  
-  //After rad corr
-  file2->cd();
-  TH2F *h2 = 0;
-  file2->GetObject("H_Pm_vs_thnq", h2);
-  //h2->Draw("colz");
-  TH1D *histo2= h2->ProjectionY("name2",h2->GetXaxis()->FindBin(30.1),h2->GetXaxis()->FindBin(39.9),"");
-  histo2->Draw("sames");
-  
-  /*
-  //rad corr. ratio
-  file3->cd();
-  TH2F *h3 = 0;
-  file3->GetObject("H_Pm_vs_thnq_ratio", h3);
-  //h3->Draw("colz");
-  TH1D *histo3= h3->ProjectionY("name2",h3->GetXaxis()->FindBin(30.1),h3->GetXaxis()->FindBin(39.9),"");
-  histo3->Draw();
-  */
-}

### 2020-10-02 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added additional prl plots including Al target background studies, ans syst. effects plots
added supplementary materials to PRL

@@
-%\title{\small \textbf{Supplemental Material: $^{2}$H$(e,e'p)n$ Cross Section Measurements \\for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ }}
+%----------------------------------------
+\documentclass[aps, prl]{revtex4-2}  % for review and submission
+%\usepackage{graphicx}  % needed for figures
+%\usepackage{dcolumn}   % needed for some tables
+%\usepackage{bm}        % for math
+%\usepackage{amssymb}   % for math
+%\usepackage[hidelinks]{hyperref}
+%\usepackage{fancyhdr}
+%\usepackage{xcolor}
+%\usepackage{grffile}
+%\usepackage[top=1in,left=0.8in, right=0.8in, bottom=0.8in]{geometry}
+%\usepackage{float}
+%\usepackage[compact]{titlesec}
+%\titlespacing{\section}{0pt}{2ex}{2ex}
 
-%\documentclass[12pt]{article}
-%\usepackage{xcolor}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{hyperref}
-
-%\begin{document}
-%\maketitle
-
-%\section{\small Spectrometer Acceptance}
-%In Hall C, the spectrometer acceptance is defined by the variables reconstructed at the target: $\delta, Y_{\mathrm{tar}}, X'_{\mathrm{tar}}$ and $Y'_{\mathrm{tar}}$, where
-
-%\end{document}
-
-%----------------------------------------
-\documentclass[aps,prl,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
-%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
-\pdfoutput=1 
 \usepackage{graphicx}  % needed for figures
@@
 \usepackage{amssymb}   % for math
+\usepackage{amsmath}   % for math
+\usepackage[top=0.85in,left=0.9in, right=0.9in, bottom=0.9in]{geometry}
 \usepackage[hidelinks]{hyperref}
@@
 \usepackage{lipsum}
+\usepackage[compact]{titlesec}
+
 \hypersetup{
@@
 \maketitle
-
-\section{Spectrometer Acceptance}
-\section{Event Selection Cuts}
-\section{Radiative Corrections}
-\section{Bin-Centering Corrections}
-\section{Systematic Uncertainty Studies}
-\section{Cross-Section Extraction}
-
-%\bibliography{}
+\section{\large Spectrometer Acceptance}
+\noindent The $^{1}$H$(e,e'p)$ coincidence elastic reaction was used (at kinematics very similar to the deuteron 80 MeV/c setting) to check of the spectrometers'
+acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} were used. \\
+\indent Figures \ref{fig:fig1} and \ref{fig:fig2} show the spectrometers' reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$)
+where $\delta$ is the momentum fraction defined as $\delta = \frac{P-P_{0}}{P_{p}}$, where $P$ is the particle momentum and $P_{0}$ is the spectrometer central momentum.
+The $Y_{\mathrm{tar}}$ is the reconstructed trajectory along the spectrometer $y-$coordinate, and ($Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) are the reconstructed trajectories
+tangent to the spectrometer central axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.
+See Section 4.4 of Ref.\cite{cyero_phdthesis} for a more detailed description of these quantities.\\
+\begin{figure}[h]
+\includegraphics[scale=0.36]{plots/hms_acc_3288.png}
+\caption{HMS reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) at the target reaction vertex using $^{1}$H$(e,e'p)$.
+  For each reconstructed quantity, the top panel shows a comparison between data (blue) and SIMC (red) with their respective integrated charge-normalized yields
+  and the data-to-SIMC ratio numerical values (top-left).
+The bottom panel shows the ratio of the data (Y$_{\mathrm{data}}$) to SIMC (Y$_{\mathrm{SIMC}}$) on a bin-by-bin basis, where the inner (black)
+and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
+\label{fig:fig1}
+\end{figure}
+\clearpage
+\begin{figure}[!ht]
+\includegraphics[scale=0.36]{plots/shms_acc_3288.png}
+\caption{Same as Fig. \ref{fig:fig1}, but for SHMS. }
+\label{fig:fig2}
+\end{figure}
+\section{\large Event Selection Cuts}
+\noindent Figures \ref{fig:fig3}-\ref{fig:fig7} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
+The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
+The exact same cuts were also applied to the 580 and 750 MeV/c settings. The data yield has been normalized by the total charge and corrected for the inefficiencies described in the Letter.
+The FSI model from J.M. Laget was used in the simulation for the plots shown below.
+\begin{figure}[!h]
+\includegraphics[scale=0.30]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
+\label{fig:fig3}
+\end{figure}
+\clearpage
+\begin{figure}
+\includegraphics[scale=0.30]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
+  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS specifications of  $-10 \leq \delta \leq22 \%$}
+\label{fig:fig4}
+\includegraphics[scale=0.30]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\caption{Event selection cuts on the $ep$ coincidence time (left) and total deposited energy on calorimeted normalized by the track momentum (right).}
+\label{fig:fig5}
+\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_data.png}
+\caption{Geometrical acceptance cut on reconstructed events projected at the HMS collimator (left). The SHMS events (in coincidence with HMS events) were projected at the SHMS collimator (right)
+  which clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
+\label{fig:fig6}
+\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
+\caption{Same as Fig. \ref{fig:fig6}, but for simulation.}
+\label{fig:fig7}
+\end{figure}
+\clearpage
+\section{\large Estimate of the Target Cell Endcaps Contribution to the Data Yield}
+\noindent To estimate the contribution to the yield due to the electron interaction with the aluminum endcaps of the target cell,
+a sample of events were selected in the negative part of the missing energy spectrum using the deuteron high missing momentum settings (580 and 750 MeV/c).
+%This was only made possible due to the high recoil kinetic energies reconstructed at these kinematics. For electron interactions with the aluminum target endcaps,
+%the reconstructed events extended to the negative part of the missing energy spectrum since we assume the mass of the deuteron in the missing energy definition.\\
+We assume that the contribution due to the target endcaps is constant across the missing energy spectrum, therefore, by selecting a sample in the
+negative part of the spectrum over a specific range, we can estimate the endcaps contribution beneath the deuteron missing energy peak over the same range.\\
+\indent Figure \ref{fig:fig8} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
+range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls is 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
+which is negligible.
+\begin{figure}[!h]
+\includegraphics[scale=0.35]{plots/tgt_bkg_d2_pm580_allthnq.png}
+\caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
+  a 40 MeV range, each. (right) The SHMS $z$-reaction vertex corresponding to the specified region in the missing energy spectrum. Inset (left): Missing energy spectrum on a logarithmic
+  scale.}
+\label{fig:fig8}
+\end{figure}
+\section{\large Radiative \& Bin-Centering Corrections}
+\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$,$p_{\mathrm{r}}$)
+kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig9}. The calculation was done using the
+Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield.
+\begin{figure}[!h]
+\includegraphics[scale=0.40]{plots/RC_factor.png}
+\caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
+\label{fig:fig9}
+\end{figure}\\
+The bin centering corrections were applied by multiplying the ratio, $f_{bc} \equiv \sigma_{avg.kin}/\bar{\sigma}$, to the average data cross section over each ($\theta_{nq}$,$p_{\mathrm{r}}$)
+kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
+Fig. \ref{fig:fig10}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
+\begin{figure}[!h]
+\includegraphics[scale=0.40]{plots/BC_factor.png}
+\caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
+  The inner (black dashed) and outer (red dash-dotted) lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
+\label{fig:fig10}
+\end{figure}
+\section{\large Systematic Uncertainty Studies on Event Selection Cuts}
+A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
+To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
+enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
+\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
+statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}$)
+where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
+\begin{subequations}
+  \begin{align}
+    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{bc,1}} - \sigma^{\mathrm{exp}}_{\mathrm{bc,2}}, \\
+    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}})^{2},
+  \end{align}
+\end{subequations}
+where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
+error accounts for the possible correlation between the two measurements. By taking the ratio
+\begin{equation}
+  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
+\end{equation}
+a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
+ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
+the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
+For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
+\indent Figure \ref{fig:fig11} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
+In Fig. \ref{fig:fig11}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
+the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
+studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
+Similar plots for the other event selection
+cuts can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
+\clearpage
+\begin{figure}[!ht]
+\includegraphics[scale=0.45]{plots/Em_syst.png}
+\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
+  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
+\label{fig:fig11}
+\end{figure}
+\section{\large Cross-Section Extraction}
+\noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig12} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
+A detailed discussion of how the experimental and reduced cross sections were extracted can be
+found in Sections 5.1 and 6.1 of Ref. \cite{cyero_phdthesis}.
+\begin{figure}[!h]
+\includegraphics[scale=0.38]{plots/Pr_and_Ps.png}
+\caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
+  the spectrometers' phase space volume binned in missing momentum.}
+\label{fig:fig12}
+\end{figure}
+\clearpage
+\bibliography{supp}
 

### 2020-10-02 PRL_UTILITIES_CODES/codes/deep_codes/add_hist.C

@@ -15,7 +15,9 @@ void add_hist()
 
   string root_dir_3;
   string root_dir_4;
-
+  string root_dir_10;
+  string root_dir_20;
+  /*
   //Deep 580 MeV,  Em_cut (-0.1, -0.04)  -- draw background
   root_dir_1 = "../../root_files/bkg_study_deep_580set1_Em_cut2/deep_data_histos_pm580_set1_combined.root";
   root_dir_2 = "../../root_files/bkg_study_deep_580set2_Em_cut2/deep_data_histos_pm580_set2_combined.root";
@@ -23,10 +25,21 @@ void add_hist()
   //Deep 580 MeV em_cut (-0.02, 0.04)  -- draw data+background
   root_dir_3 = "../../root_files/bkg_study_deep_580set1_Em_cut1/deep_data_histos_pm580_set1_combined.root";
   root_dir_4 = "../../root_files/bkg_study_deep_580set2_Em_cut1/deep_data_histos_pm580_set2_combined.root";
+  */
+  //Deep 750 MeV,  Em_cut (-0.1, -0.04)  -- draw background
+  root_dir_1 = "../../root_files/bkg_study_deep_750set1_Em_cut1/deep_data_histos_pm750_set1_combined.root";
+  root_dir_2 = "../../root_files/bkg_study_deep_750set2_Em_cut1/deep_data_histos_pm750_set2_combined.root";
+  root_dir_10 = "../../root_files/bkg_study_deep_750set3_Em_cut1/deep_data_histos_pm750_set3_combined.root";
+
+  
+  //Deep 750 MeV em_cut (-0.02, 0.04)  -- draw data+background
+  root_dir_3 = "../../root_files/bkg_study_deep_750set1_Em_cut2/deep_data_histos_pm750_set1_combined.root";
+  root_dir_4 = "../../root_files/bkg_study_deep_750set2_Em_cut2/deep_data_histos_pm750_set2_combined.root";
+  root_dir_20 = "../../root_files/bkg_study_deep_750set3_Em_cut2/deep_data_histos_pm750_set3_combined.root";
 
 
   //TFile *data_file_80_set1 = new TFile(root_dir_0.c_str());
-  
+  /*
   TFile *data_file_580_set1_bkg = new TFile(root_dir_1.c_str());
[…]

### 2020-10-02 PRL_UTILITIES_CODES/codes/deep_codes/compare_deep.C

@@ -143,16 +143,16 @@ void compare_deep(int pm, int set, int thnq)
 
   //-------EVENT SELECTION CUTS
   //Plot Only Data Histos
-  //plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts / mC", "SHMS Calorimeter Total Normalized Energy"); 
-  //plot_hist(data_CoinTime, "Coincidence Time [ns]", "Counts / mC", "Coincidence Time"); 
+  plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts / mC", "SHMS Calorimeter Energy"); 
+  plot_hist(data_CoinTime, "Coincidence Time [ns]", "Counts / mC", "Coincidence Time"); 
 
   //ONLY PLOT DATA-2-SIMC COMPARISONS (NOT RATIOS)
-  //compare_hist(data_hdelta, simc_hdelta_fsi, "HMS #delta [%]", "Counts / mC", "HMS #delta");
-  //compare_hist(data_edelta, simc_edelta_fsi, "SHMS #delta [%]", "Counts / mC", "SHMS #delta");
+  compare_hist(data_hdelta, simc_hdelta_fsi, "HMS #delta [%]", "Counts / mC", "HMS #delta");
+  compare_hist(data_edelta, simc_edelta_fsi, "SHMS #delta [%]", "Counts / mC", "SHMS #delta");
 
-  //compare_hist(data_Q2, simc_Q2_fsi, "Q^{2} [GeV^{2}]", "Counts / mC", "4-Momentum Transfer, Q^{2}"); 
+  compare_hist(data_Q2, simc_Q2_fsi, "Q^{2} [GeV^{2}]", "Counts / mC", "4-Momentum Transfer, Q^{2}"); 
   //compare_hist(data_thnq, simc_thnq_fsi, "#theta_{nq} [deg]", "Counts", "Neutron Recoil Angles, #theta_{nq}");
-  //compare_hist(data_ztar_diff, simc_ztar_diff_fsi, "Z_{tar} Difference [cm]", "Counts / mC", "Z_{tar} Difference"); 
+  compare_hist(data_ztar_diff, simc_ztar_diff_fsi, "Z_{tar} Difference [cm]", "Counts / mC", "Z_{tar} Difference"); 
[…]

### 2020-10-02 PRL_UTILITIES_CODES/codes/heep_codes/compare_heep.C

@@ -10,8 +10,8 @@ void compare_heep(int run)
   gStyle->SetOptStat(0000000);
 
 
-  TString root_dir = "../../root_files/pre_HEEP_ELASTICS/";
-  //TString root_dir = "../../root_files/HEEP_ELASTICS/";
+  //TString root_dir = "../../root_files/pre_HEEP_ELASTICS/";
+  TString root_dir = "../../root_files/HEEP_ELASTICS/";
 
   //NO CUT and Ztar Diff Cut
   //TString data_filename = "../../root_files/heep_data_histos_3288_combined.root";    
@@ -23,13 +23,13 @@ void compare_heep(int run)
   //TString simc_filename = "heep_simc_histos_3288_rad_Q2_4to5.root";       
 
   //Full Q2 range
-  //TString data_filename = Form("heep_data_histos_%d_combined_Q2full.root", run);    
-  //TString simc_filename = Form("heep_simc_histos_%d_rad_Q2full.root", run);       
+  TString data_filename = Form("heep_data_histos_%d_combined_Q2full.root", run);    
+  TString simc_filename = Form("heep_simc_histos_%d_rad_Q2full.root", run);       
 
   
   //Pre-defined SIMC/data root file names containing histogram object to comapare
-  TString simc_filename =  Form("heep_simc_histos_%d_rad.root", run);                      
-  TString data_filename = Form("heep_data_histos_%d_combined.root",run); 
+  //TString simc_filename =  Form("heep_simc_histos_%d_rad.root", run);                      
+  //TString data_filename = Form("heep_data_histos_%d_combined.root",run); 
 
   TString simc_f = root_dir + simc_filename;
   TString data_f = root_dir + data_filename;
@@ -337,10 +337,10 @@ void compare_heep(int run)
   //hist_ratio(data_edelta, simc_edelta, "SHMS #delta [%]", "Counts / mC", "SHMS #delta");
 
   //Plot the HMS Recon Ratio
-  //hist_ratio(data_hytar, simc_hytar, "HMS Y_{tar} [cm]", "Counts / mC", "HMS Y_{tar}");
[…]

### 2020-10-02 PRL_UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -2,12 +2,13 @@
 //Used to plot data/simc comparison and their ratio
 void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", TString title="")
 {
-
+  int font_type = 132;
+  
   gStyle->SetOptStat(0);
   gStyle->SetTitleFontSize(0.08);
-  gStyle->SetTitleFont(22, "");
+  gStyle->SetTitleFont(font_type, "");
   gStyle->SetLegendBorderSize(0);
-  gStyle->SetLegendFont(22);
+  gStyle->SetLegendFont(font_type);
   gStyle->SetLegendTextSize(0.06);
 
   //Create Canvas
@@ -46,7 +47,7 @@ void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", 
 
   TPad* pad1 = (TPad*)c->GetPad(1);
   pad1->SetBottomMargin(0.02);
-  pad1->SetRightMargin(0.03);
+  pad1->SetRightMargin(0.05);
   pad1->SetLeftMargin(0.1);
   pad1->SetTopMargin(0.13);
   pad1->SetFrameLineWidth(2);
@@ -59,8 +60,8 @@ void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", 
   hdata->GetYaxis()->CenterTitle();
   hdata->GetYaxis()->SetRangeUser(0,hdata->GetMaximum()+0.6*hdata->GetMaximum());
   hdata->GetYaxis()->SetTitleOffset(0.6);
-  hdata->SetLabelFont(22, "XY");
-  hdata->SetTitleFont(22, "XY");
+  hdata->SetLabelFont(font_type, "XY");
+  hdata->SetTitleFont(font_type, "XY");
 
   double dataI_err, simcI_err;
   double nbins = hdata->GetNbinsX();  //Get total number of bins (excluding overflow)
@@ -77,8 +78,8 @@ void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", 
   c->cd(2);
   TPad* pad = (TPad*)c->GetPad(2);
   pad->SetTopMargin(0.01);
-  pad->SetBottomMargin(0.5);
-  pad->SetRightMargin(0.03);
+  pad->SetBottomMargin(0.2);
+  pad->SetRightMargin(0.05);
   pad->SetLeftMargin(0.1);
[…]

### 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/ms_wordcnt.tex
added direcotry to test prl plots size and word count limit

--- 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl.tex
@@
 However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
-\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum component) is via the exclusive deuteron
+\indent The most direct way to study the short range structure of the deuteron wave function %(or equivalently, its high momentum component)
+is via the exclusive deuteron
 electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to
@@
 momentum thereby obscuring the original momentum of the bound nucleon and reducing the possibility of directly probing the deuteron momentum distribution. \\
-\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively\cite{sargsian_2015}.
+\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively \cite{sargsian_2015}.
 The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
@@
 Both
-experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with neutron recoil angles, peaking
+experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking
 at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
@@
 which are therefore dominated by  FSI, MEC and IC for $p_{\mathrm{r}}$ above $\sim 300$ MeV/c. \\
-\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the missing momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$)
+\indent In the Hall A experiment \cite{PhysRevLett.107.262501}, the pair of high resolution spectrometers (HRS) made it possible to measure the $p_{\mathrm{r}}$ dependence of the cross section for fixed $\theta_{nq}$
 reaching recoil momenta up to $p_{\mathrm{r}}=550$ MeV/c at $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$. For the first time, very different momentum distributions were found for $\theta_{nq}=35\pm5^{\circ}$
@@
 \indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment \cite{PhysRevLett.107.262501} and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements
-to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
-Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
-At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.\\
+to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and recoil momenta up to $p_{\mathrm{r}}\sim 1$ GeV/c, which is almost double the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
+Measurements at such large $Q^{2}$ and high $p_{\mathrm{r}}$ required scattered electrons to be detected at $\sim 8.5$ GeV/c, which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
+At the selected kinematic settings with $35^{\circ} \leq \theta_{nq} \leq45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.\\
 \indent A 10.6 GeV electron beam was incident on a 10-cm-long liquid deuterium target (LD$_{2}$). The scattered electron and knocked-out proton were detected in coincidence
 by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively.
-The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\
-\indent Both Hall C spectrometers have similar standard detector packages, each with four scintillator planes \cite{hodo_techreport} used for triggering, a pair of drift chambers \cite{dc_techreport} used for tracking, and a calorimeter \cite{Mkrtchyan_2013} and gas \u{C}erenkov \cite{Li_Wenliang_mthesis,ngc_techreport} used for electron identification.
+The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets.\\ %(hydrogen and deuterium).\\
+\indent Both Hall C spectrometers have similar standard detector packages \cite{cyero_phdthesis}, each with four scintillator planes used for triggering, a pair of drift chambers used for tracking, and a calorimeter and gas \u{C}erenkov used for electron identification.
 For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
@@
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
-were as follows: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) \cite{cyero_phdthesis} and
-target boiling inefficiency ($4.2 \%$) \cite{cyero_phdthesis}. The values in parentheses were averaged over all missing momentum settings. \\
+were as follows\cite{cyero_phdthesis}: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) and
+target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all missing momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual
-contributions from normalization uncertainties for each setting were determined to be (on average): tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
+contributions from normalization uncertainties for each setting were determined to be (on average)\cite{cyero_phdthesis}: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS),
 and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
@@
 Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the PWIA cross section from the scattering of a proton in the deuteron. \\
-\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum
-$p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
+\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
 For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
-The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$
-gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
+%The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$ gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
 The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} $NN$ potentials.
@@
 \indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
-missing momenta typically above 800 MeV/c for the MS CD-Bonn
+$p_{\mathrm{r}} \gtrsim 800$ MeV/c for the MS CD-Bonn
 \begin{figure}[!t]
@@
 \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
-At $p_{\mathrm{r}}>300$ MeV/c and $\theta_{nq}=75^{\circ}$, the data were statistically limited as our focus was on the smaller recoil angles.
-The Hall A data, however, show a reasonable agreement with the FSI from all models which gives us confidence in our understanding
-of FSI at the smaller recoil angles. \\
+At $p_{\mathrm{r}}>300$ MeV/c ($\theta_{nq}=75^{\circ}$), the data were statistically limited as our focus was on the smaller recoil angles.
+The Hall A data, however, show a reasonable agreement with the FSI from all models
+which gives us confidence in our understanding of FSI at the smaller recoil angles. \\
 \indent To summarize, this experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 
-very high neutron recoil momenta ($p_{\mathrm{r}}>500$ MeV/c) at kinematics where FSI were expected to be small and the cross sections were dominated by PWIA and sensitive to the
+$p_{\mathrm{r}}>500$ MeV/c at kinematics where FSI were expected to be small and the cross sections were dominated by PWIA and sensitive to the
 short range part of the deuteron wave function.
@@
 
-\bibliography{prl}
+\bibliography{ms}
 \end{document}

### 2020-10-03 PRL_UTILITIES_CODES/codes/PRL_plots_codes/make_prl_plots_smallplots.py

@@ -1,0 +1,508 @@
+import LT.box as B
+from LT.datafile import dfile
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy.ma as ma
+import sys                                     
+import os                                                                                                       
+from sys import argv  
+import matplotlib
+from matplotlib import rc
+from matplotlib import *
+from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
+from prl_utilities import *
+
+
+#Use latex commands (e.g. \textit ot \textbf)
+rc('text', usetex=True)
+#Set default font to times new roman
+font = {'family' : 'Times New Roman',
+        'weight' : 'normal',
+        'size'   : 12
+}
+plt.rc('font', **font)
+
+#Set font
+csfont = {'fontname':'Times New Roman'}
+
+def make_prl_plots(plot2_inset=0):
+  
+    #Read Hall C (E12-10-003) experimental data (requires <=50% statistical uncertainty, units: fm^3, GeV/c)
+    pm_avg35, red_dataXsec_avg_masked35, red_dataXsec_avg_tot_err35 = read_hallc_data(35)
+    pm_avg45, red_dataXsec_avg_masked45, red_dataXsec_avg_tot_err45 = read_hallc_data(45)
+    pm_avg75, red_dataXsec_avg_masked75, red_dataXsec_avg_tot_err75 = read_hallc_data(75)
+
+    #Read Hall A experimental data
+    pm_ha35, red_dataXsec_ha35, red_dataXsec_err_ha35 = read_halla_data(35)
+    pm_ha45, red_dataXsec_ha45, red_dataXsec_err_ha45 = read_halla_data(45)  
+    pm_ha75, red_dataXsec_ha75, red_dataXsec_err_ha75 = read_halla_data(75) 
+
+    #Read Theoretical calculations
[…]

### 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/ms_wordcnt.tex
added prl_plot_tests directory where PRL word count is carefully monitored while is being updated. I also added additional plots to the supplemental material (rad./bc systematic plots)

@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610}.
+simulation program, SIMC \cite{PhysRevC.64.054610}(see Supplemental Material).
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
@@
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target.\\
+originated from the same reaction vertex at the target (See Supplemental Material). \\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
@@
 over the kinematic bin.
-The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found.
+The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material).
 The experimental and theoretical reduced cross sections were extracted and are defined as follows:
@@
 
+%---include references that are not mentioned in the main text
+%---but are included in the supplemental material
+%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
+%\nocite{COSY}
+
 \bibliography{ms}

### 2020-10-03 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added prl_plot_tests directory where PRL word count is carefully monitored while is being updated. I also added additional plots to the supplemental material (rad./bc systematic plots)

@@
 \end{figure}
-\section{\large Systematic Uncertainty Studies on Event Selection Cuts}
+\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
 A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
@@
 \begin{figure}[!ht]
-\includegraphics[scale=0.45]{plots/Em_syst.png}
+\includegraphics[scale=0.4]{plots/Em_syst.png}
 \caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
@@
 \end{figure}
+\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated using the Barlow ratio approach described above.
+In this case, the ratio was calculated from the difference between the experimental cross sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections.
+\begin{figure}[!h]
+\includegraphics[scale=0.33]{plots/rad_sys.png}
+\caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
+The inner (black dashed) and outer (black solid) lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.
+}
+\label{fig:fig12}
+\includegraphics[scale=0.33]{plots/bc_sys.png}
+\caption{Same as Fig. \ref{fig:fig12} but for bin-centering corrections.}
+\label{fig:fig13}
+\end{figure}
+\clearpage
+Figures \ref{fig:fig12} and \ref{fig:fig13} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
+the model dependency on the correction factors have a negligible effect on the experimental cross sections.
 \section{\large Cross-Section Extraction}
 \noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig12} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig14} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
 missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
@@
   the spectrometers' phase space volume binned in missing momentum.}
-\label{fig:fig12}
+\label{fig:fig14}
 \end{figure}

### 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/MARKED_PRL/ms.tex
finalized supp. materials and modifications of prl text / images

--- 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/ms_wordcnt.tex
@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610}(see Supplemental Material).
+simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material).
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
@@
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target (See Supplemental Material). \\
+originated from the same reaction vertex at the target (see Supplemental Material). \\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
@@
 region where recoil angles are small and FSI are reduced. \\
-\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for
+\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate at
 $p_{\mathrm{r}} \gtrsim 800$ MeV/c for the MS CD-Bonn
@@
 %---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
-%\nocite{COSY}
+\nocite{COSY}
+\nocite{barlow2002systematic}
+\nocite{barlow2017}
 

### 2020-10-03 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
finalized supp. materials and modifications of prl text / images

--- 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/ms_wordcnt.tex
@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootbib]{revtex4-2}  % for review and submission
 \pdfoutput=1 
@@
 momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
-\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
-as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
-to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
-thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
-discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
-under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
-under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
+%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
+%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
+%to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
+%thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
+%discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
+%under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
+%under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).
 
@@
 %\nocite{COSY}
-
+\end{document}
 \bibliography{ms}
-\end{document}
+%\end{document}

### 2020-10-03 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
finalized supp. materials and modifications of prl text / images

@@
 \noindent The $^{1}$H$(e,e'p)$ coincidence elastic reaction was used (at kinematics very similar to the deuteron 80 MeV/c setting) to check of the spectrometers'
-acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} were used. \\
+acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} was used. \\
 \indent Figures \ref{fig:fig1} and \ref{fig:fig2} show the spectrometers' reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$)
@@
 The $Y_{\mathrm{tar}}$ is the reconstructed trajectory along the spectrometer $y-$coordinate, and ($Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) are the reconstructed trajectories
-tangent to the spectrometer central axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.
+tangent to the spectrometer central optics axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.
 See Section 4.4 of Ref.\cite{cyero_phdthesis} for a more detailed description of these quantities.\\
@@
   For each reconstructed quantity, the top panel shows a comparison between data (blue) and SIMC (red) with their respective integrated charge-normalized yields
-  and the data-to-SIMC ratio numerical values (top-left).
-The bottom panel shows the ratio of the data (Y$_{\mathrm{data}}$) to SIMC (Y$_{\mathrm{SIMC}}$) on a bin-by-bin basis, where the inner (black)
-and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
+  and the data-to-SIMC ratio numerical values (top-left corner). The bottom panel shows the data to SIMC yield ratio (Y$_{\mathrm{data}}$/Y$_{\mathrm{SIMC}}$) on a
+  bin-by-bin basis, where the inner (black) and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
 \label{fig:fig1}
@@
 \caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
-  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS specifications of  $-10 \leq \delta \leq22 \%$}
+  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$}
 \label{fig:fig4}
 \includegraphics[scale=0.30]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
-\caption{Event selection cuts on the $ep$ coincidence time (left) and total deposited energy on calorimeted normalized by the track momentum (right).}
+\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
 \label{fig:fig5}
 \includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_data.png}
-\caption{Geometrical acceptance cut on reconstructed events projected at the HMS collimator (left). The SHMS events (in coincidence with HMS events) were projected at the SHMS collimator (right)
-  which clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
+\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
+  The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
 \label{fig:fig6}
@@
 \section{\large Radiative \& Bin-Centering Corrections}
-\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$,$p_{\mathrm{r}}$)
+\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)
 kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig9}. The calculation was done using the
@@
 \end{figure}\\
-The bin centering corrections were applied by multiplying the ratio, $f_{bc} \equiv \sigma_{avg.kin}/\bar{\sigma}$, to the average data cross section over each ($\theta_{nq}$,$p_{\mathrm{r}}$)
+The bin centering corrections were applied by multiplying the ratio, $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}}/\bar{\sigma}$, to the average data cross section over each ($\theta_{nq}$, $p_{\mathrm{r}}$)
 kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
@@
 Similar plots for the other event selection
-cuts can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
+cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
 \clearpage
@@
 Figures \ref{fig:fig12} and \ref{fig:fig13} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
-the model dependency on the correction factors have a negligible effect on the experimental cross sections.
+the model dependency of the correction factors have a negligible effect on the experimental cross sections.
 \section{\large Cross-Section Extraction}
@@
 \end{figure}
-\clearpage
+%\clearpage
 \bibliography{supp}

### 2020-10-03 PRL_UTILITIES_CODES/codes/PRL_plots_codes/get_words.py

@@ -11,10 +11,12 @@ def get_words(w=0, h=0, ncol=0):
     if(ncol==1):
         #For single column figures, the word estimate for a figure size is:
         one_column_fig_words = (150./aspect_ratio) + 20.  #units: number of words
+        print('aspect ratio = ', aspect_ratio)
         print('(single column) # of words equivalent for figsize: (w=',w,' h=', h,') in. -----> ',one_column_fig_words,' words')
     elif(ncol==2):
         #For figures that occupy both columns of the paper, the word estimate for a figsize is:
         two_column_fig_words = (300./(0.5*aspect_ratio) ) + 40. 
+        print('aspect ratio = ', aspect_ratio)
         print('(two columns) # of words equivalent for figsize: (w=',w,' h=', h,') in. -----> ',two_column_fig_words,' words')
 
 

### 2020-10-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/reply_to_RefereeA.txt
added PRL reply

--------------------------------
Reply to: Report of Referee A
--------------------------------

A concise, point-by-point response for each of the recommendations and criticisms made by referee A is shown below:

-------------
Referee A:
-------------
1) Universality: The nuclear-factorization assumption put forward by Ciofi and Frankfurt & Strikman, and more recently
developed to a quantitative approach using the generalized contact formalism, directly connect the high momentum
measurement of the deuteron to all atomic nuclei and nuclear systems. This universality steam from the dominance of
SRC pairs in the high momentum tail of nuclear wave-function. A discussion of this connection, with proper reference
to the theoretical works mention above, and to the experimental works that show the important of np-SRC pairs with the
deuteron quantum number (Subedi et al., Korover et al., Duer et al., etc.), is missing.
----------
Response:
----------
The introductory (1st) paragraph was re-written in accordance with the suggestions made above.

-------------
Referee A:
-------------
2) Relativity: The current manuscript does not discuss relativistic effects even though one could expect them to be
significant in the measured momenta range. Questions that immediately come to mind include to what extend the new data
supports a non-relativistic description of the deuteron wave function relevant for the high momenta measured here? If
they do, why? What can one learn about how to properly account for relativistic corrections and relativity in general
for nuclear systems? Do the new data constrain our limited ability to describe the relativistic aspects of nuclear structure
at short distance / high momenta? For example, Schmidt et al. [Nature 578 (2020) 540] recently utilized the light-cone formalism
of Frankfurt & Strikman to gain quantitative insight into these issues. The formalism they follow seem to be quite simple, perhaps
too simplistic, but still provide valuable insight. Can the authors of the present work study the impact of relativistic corrections
to the PWIA cross-section in a similar manner?
----------
Response:
----------
Our analysis demonstrated that there is no simplistic way of estimating relativistic effects since even in the kinematics
in which FSI are small they are still comparable with the expected relativistic effects. The current calculations are based on
the virtual nucleon approximation in which  relativistic effects are accounted for in the propagator of the bound nucleon, for the
vertex of electron-bound nucleon interaction as well as for FSI. To switch off relativistic effects means to remove all these effects
which will return us to the standard Glauber theory.  But in our previous paper [Phys.Rev.Lett. 107, 262501 (2011)],  we already
demonstrated that Glauber theory will not describe the main feature of the reaction. For example at 400 MeV/c it will predict maximum FSI
to occur at 90 degrees of the spectator angle, while the experiment clearly shows that maximum FSI is at 70 degrees.

The current limitation of the virtual nucleon approximation is that it still uses a non-relativistic deuteron
wave function [M. Sargsian, Private communication, Oct. 2020] and assumes that vacuum fluctuation effects are not significant.
It is expected that the latter will grow with the increase of the recoil momentum of the spectator nucleon. 
One approach that addresses this issue is the Light-Front approximation, however, the implementation of this approximation 
requires a consistent calculation of all the above discussed factors (i.e. propagator, vertex, FSI and wave function).
Hence, relativistic effects cannot simply be "turned off", since they contribute in different components of 
the scattering amplitude.

Light-front calculations are currently underway [M.Sargsian, Private communication, Oct. 2020) which we hope will be used 
to compare with our data for the large paper.

-------------
Referee A:
-------------
3) Nucleon-Nucleon interaction: Here the authors make the connection clear. However no modern EFT calculations are compared
with the new data. It is true that these are limited by strong regulators are high-momenta, however there are several interactions
such as the Norfolk potentials [M. Piarulli] that do suffer letter from such effects. In addition, even with high-momentum
regulators, it is interesting to observe out to what momenta can these interactions be coupled with a high- resolution one-body
interaction model and still explain experimental data. Recent analysis of nuclear form-factor data suggest this can be quite high.

In addition, there is no reference to relevant previous works that study nuclei heavier than deuterium. These include
A=3 [124 (2020) 212501; PRL 94 (2005) 082305; 94 (2005) 192302] and 12 [Nature 578 (2020) 540] that study the NN force
to short distance structure of SRC deuteron like pairs.
----------
Response:
----------
Similar to the above comment (2) regarding relativistic calculations to account for the effects of different
wave functions, it requires a complete calculation including the FSI effects, which is out of scope of the current paper. 
We hope that the theory groups who are collaborating with us will be able to provide such calculations which will be
presented in a larger paper. These studies are currently in progress.

-------------
Referee A:
-------------
4) More general comment: Not enough information is given on the measurements. The data was taken using a new detection system
(SHMS at Hall C in 12 GeV setting) and the reader is referred only to unpublished thesis (with no Web link) for details.
In addition, the analysis itself is not transparent enough to the reader. More information should be provided in the form of
supplementary materials or similar. See details below.
----------
Response:
----------
I have published my thesis on arXiv and reference it in the PRL manuscript. I also added supplementary materials.

-------------
Referee A:
-------------
5) The scale of Fig. 2 is misleading as it is very hard to assess the quality of the agreement between the data and
theory in the 0 – 700 MeV/c region. Please add an insert with a blowup on that region.
----------
Response:
----------
I have added an inset with a blowup for Fig. 2, subplots (a) and (b).

-------------
Referee A:
-------------
6) I noticed (and appreciate) the availability of the crosse-section data in txt format and the same should be done
for the relevant calculations so that the interested reader can examine the results in more detail.
----------
Response:
----------
I have added additional raw data files with the theoretical calculations as part of the
supplemental material.

-------------
Referee A:
-------------
7) Page 1 introduction: Should place more emphasis on the importance to the broader physics community, as suggested above.
Elucidating the short-distance structure of nuclei and nuclear force via deuteron measurements is a fascinating problem of
a broad interest. However, the present work does not, in my opinion, meet this criterion.
----------
Response:
----------
As mentioned in response to (1), I re-wrote the introductory paragraph.

-------------
Referee A:
-------------
8) Page 2 introduction "determining whether or to what extent the description of nuclei in terms of nucleon/meson degrees of
freedom is still valid before having to include explicit quark degrees of freedom”. Do the authors really think that (e,e’p)
measurement can address the question of nucleon/meson and partonic degrees of freedom? At the end of the day the data are compared
with calculations that have large freedom in their description of the off-shell electron-nucleon cross-section and even more so in
the modeling of the short-distance part of the NN interaction. Therefore, even if partonic physics becomes important at high-momenta,
it can probably be masked by effective nucleon- based interaction that will fit the data. In any case, it is ok if the authors want
to make such connections, however, it will probably be better to do so as part of a broader discussion of the relation between SRC
studies and the partonic structure of nuclei, e.g. by referencing the EMC effect and the EMC-SRC connections published in the last years.
----------
Response:
----------
This part the referee refers to was removed in the introductory paragraph.

-------------
Referee A:
-------------
9) The distributions of the fundamental measured quantities such as Q2, xB , ω, Pp should be shown. The measurements were done in 3 momentum bins.
The overlap and the matching between the bins should be shown. This can be a part of a supplementary materials document that allow the referees
and the reader to assess the quality of the data.
----------
Response:
----------
I have added Q2 distribution (for 80 MeV/c setting) in the Supplemental Material. I have also
added the missing momentum distributions for each of the central settings (80, 580 and 750 MeV/c) *** Maybe I can add Q2, xB, w and Pp for each setting (smaller plots)

-------------
Referee A:
-------------
10) How the was the contribution of the target walls removed / subtracted?
----------
Response:
----------
The background from target cell wall was found to be negligible at the deuteron kinematics
(See Supplemental Material)

-------------
Referee A:
-------------
11) “hits in three of the four scintillator planes.” At least three?
----------
Response:
----------
Yes, at least 3/4 planes. I have clarified this in the manuscript.

-------------
Referee A:
-------------
12) What about systematic uncertainties due to software cuts, acceptance corrections etc.?
----------
Response:
----------
See Supplemental Materials.

-------------
Referee A:
-------------
13) What is the size of the radiation correction? Please detail on its calculation procedure.
----------
Response:
----------
See Supplemental Materials.

-------------
Referee A:
-------------
14) “a weighted average of the cross sections were taken in the overlapping regions of pr”. Show consistency. 
----------
Response:
----------
To clarify, a weighted average of the reduced cross sections were taken for overlapping regions in pr. See example
of overlapping pr bins in Fig. 14 of Supplemental Materials.

-------------
Referee A:
-------------
15) “cach” should be “each”.
----------
Response:
----------
I did not find this typo in the manuscript.

-------------
Referee A:
-------------
16) Fig. 2 and relevant discussion on Page 5: what about EFT calculations below and above their cutoffs?

Pages 5-6 include extensive phenomenological verbal description of Fig 2. However, what it misses a discussion
of the possible meaning of what is actually observed? For example: “the MS CD-Bonn model was able to partially
describe the data over a larger range...” – what does it mean? “all models were unable to describe the data”
above some momentum-what that means?
----------
Response:
----------
The comparison between the measured (reduced) cross sections and the currently available
complete and state of the art calculations illustrates the limit to which a non-relativistic
wave function that is the solution of the Schroedinger equation is valid and able to describe
experimental data that probe the high momentum region of the np system in the most direct way
possible.

As was mentioned before, the theoretical interpretation of these results is
out of the scope of this paper and is currently being investigated by the theory
groups we are collaborating with. Our goal was to simply present these new and
interesting results.

### 2020-10-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised.tex
added PRL reply

--- 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/MARKED_PRL/ms.tex
@@
 The deuteron is the only bound two-nucleon system and serves as an ideal framework to study the strong nuclear force at the sub-Fermi distance scale, a region which is currently
-practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
-nucleons begin to overlap.
+practically unexplored and not well understood. Understanding the high momentum structure of the proton-neutron ($pn$) system is highly important for nuclear physics due to the observed 
+dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
+carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions
+have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
+Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
+(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\
+%===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
+%At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
+%nucleons begin to overlap.
 The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
-Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
+%Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
+%having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
 As of the present time, there are only a few nuclear physics experiments for
-which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
+%which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
+%However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
 \indent The most direct way to study the short range structure of the deuteron wave function %(or equivalently, its high momentum component)
-is via the exclusive deuteron
-electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to
-the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron).
-The neutron carries a recoil momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction
-to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.\\
+is via the exclusive deuteron electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA),
+the virtual photon couples to the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron). The neutron carries a recoil
+momentum, $p_{\mathrm{r}}$, equal in magnitude but opposite in direction to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum
+of the bound nucleon and its momentum distribution.\\
 \indent In addition to the PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
@@
 $\theta_{nq}\sim120^{\circ}$ ($x_{\mathrm{Bj}}<1$) IC are not negligible, the $x_{\mathrm{Bj}}>1$ ($\theta_{nq}\sim40^{\circ}$) kinematics are the preferred choice to suppress IC as well as FSI. \\
-\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at Jefferson Lab (JLab) in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}.
-Both
+\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at JLab in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}. Both
 experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking

### 2020-10-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
added PRL reply

--- 2020-10-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised.tex
@@
 \indent Both Hall C spectrometers have similar standard detector packages \cite{cyero_phdthesis}, each with four scintillator planes used for triggering, a pair of drift chambers used for tracking, and a calorimeter and gas \u{C}erenkov used for electron identification.
-For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logic signal was created from  the coincidence of hits in at least three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
+For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the reduced cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).

### 2020-10-07 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
added PRL reply

@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootbib]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootinbib]{revtex4-2}  % for review and submission
 \pdfoutput=1 
@@
 momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
+
 %\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
@@
 %---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
-%\nocite{COSY}
+\nocite{COSY}
+\nocite{barlow2002systematic}
+\nocite{barlow2017}
+
 \end{document}
 \bibliography{ms}
-%\end{document}

### 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
added supp mat. section

@@
 \caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
-The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
+  The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.
+  Insets: A blowup of the corresponding subfigure in the range $p_{\mathrm{r}}=0 - 0.7$ GeV/c.}
 \label{fig:fig2}

### 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_original.tex
added supp mat. section

--- 2020-10-03 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
@@
 \begin{figure}
-\includegraphics[scale=0.30]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
 \caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
@@
 \label{fig:fig7}
+\end{figure}
+\clearpage
+\section{\large Deuteron Kinematic Distributions }
+\noindent Figures show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}, 45^{\circ}$.
+The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter.  
+\begin{figure}[!h]
+\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
+\caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
+\label{fig:fig8}
+\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
+\caption{Same as Fig. \ref{}, but for $\theta_{nq}=45^{\circ}$}
+\label{fig:fig9}
 \end{figure}

### 2020-10-08 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added PRL reply
added supp mat. section

@@
 \clearpage
+\section{\large Deuteron Kinematic Distributions }
+\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
+The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
+The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
+Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 
+\begin{figure}[!h]
+\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
+\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
+\label{fig:fig8}
+\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
+\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}
+\label{fig:fig9}
+\end{figure}
+\clearpage
 \section{\large Estimate of the Target Cell Endcaps Contribution to the Data Yield}
@@
 negative part of the spectrum over a specific range, we can estimate the endcaps contribution beneath the deuteron missing energy peak over the same range.\\
-\indent Figure \ref{fig:fig8} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
+\indent Figure \ref{fig:fig10} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
 range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls is 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
@@
   scale.}
-\label{fig:fig8}
+\label{fig:fig10}
 \end{figure}
@@
 \noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)
-kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig9}. The calculation was done using the
+kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig11}. The calculation was done using the
 Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield.
@@
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
-\label{fig:fig9}
+\label{fig:fig11}
 \end{figure}\\
@@
 kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
-Fig. \ref{fig:fig10}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
+Fig. \ref{fig:fig12}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
 \begin{figure}[!h]
@@
   The inner (black dashed) and outer (red dash-dotted) lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
-\label{fig:fig10}
+\label{fig:fig12}
 \end{figure}
@@
 For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
-\indent Figure \ref{fig:fig11} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
-In Fig. \ref{fig:fig11}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
+\indent Figure \ref{fig:fig13} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
+In Fig. \ref{fig:fig13}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
 the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
@@
   lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
-\label{fig:fig11}
+\label{fig:fig13}
 \end{figure}
@@
 }
-\label{fig:fig12}
+\label{fig:fig14}
 \includegraphics[scale=0.33]{plots/bc_sys.png}
-\caption{Same as Fig. \ref{fig:fig12} but for bin-centering corrections.}
-\label{fig:fig13}
+\caption{Same as Fig. \ref{fig:fig14} but for bin-centering corrections.}
+\label{fig:fig15}
 \end{figure}
 \clearpage
-Figures \ref{fig:fig12} and \ref{fig:fig13} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
+Figures \ref{fig:fig14} and \ref{fig:fig15} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
 the model dependency of the correction factors have a negligible effect on the experimental cross sections.
@@
 \noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig14} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig16} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
 missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
@@
   the spectrometers' phase space volume binned in missing momentum.}
-\label{fig:fig14}
+\label{fig:fig16}
 \end{figure}

### 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised.tex
prepared PRL package before re-submittal

@@
 \caption{(Color online). The ratio $R(p_{\mathrm{r}}$) is shown in (a)-(c) for $\theta_{nq}=35^{\circ}, 45^{\circ}$ and $75^{\circ}$, respectively, each with a bin width of $\pm 5^{\circ}$.
-The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
+  The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.
+  Insets: Blowup of the subfigures below $p_{\mathrm{r}}=$0.7 GeV/c.}
 \label{fig:fig2}
@@
 %---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
-\nocite{COSY}
-\nocite{barlow2002systematic}
-\nocite{barlow2017}
+%\nocite{COSY}
+%\nocite{barlow2002systematic}
+%\nocite{barlow2017}
 

### 2020-10-08 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
prepared PRL package before re-submittal

@@
 (Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\
-%===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
-%At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
-%nucleons begin to overlap.
-The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
-%Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-%having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
-As of the present time, there are only a few nuclear physics experiments for
-%which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-%However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
-\indent The most direct way to study the short range structure of the deuteron wave function %(or equivalently, its high momentum component)
+\indent The most direct way to study the short range structure of the deuteron wave function 
 is via the exclusive deuteron electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA),
@@
 by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively.
-The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets.\\ %(hydrogen and deuterium).\\
+The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets.\\
 \indent Both Hall C spectrometers have similar standard detector packages \cite{cyero_phdthesis}, each with four scintillator planes used for triggering, a pair of drift chambers used for tracking, and a calorimeter and gas \u{C}erenkov used for electron identification.
-For each spectrometer, a logic signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
+For each spectrometer, a logic signal was created from  the coincidence of hits in at least three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
 \indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
@@
 \indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of $p_{\mathrm{r}}$ for three recoil angle settings at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$.
-For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
+For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the reduced cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$.
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
-%The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$ gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
 The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} $NN$ potentials.
@@
 momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
-
 %\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
@@
 
-%---include references that are not mentioned in the main text
-%---but are included in the supplemental material
-%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
 \nocite{COSY}

### 2020-10-08 PRL_UTILITIES_CODES/codes/PRL_plots_codes/make_prl_plots_smallplots.py

@@ -11,7 +11,8 @@ import matplotlib
 from matplotlib import rc
 from matplotlib import *
 from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-from prl_utilities import *
+#from prl_utilities import *
+from prl_utilities_test import *
 
 
 #Use latex commands (e.g. \textit ot \textbf)
@@ -71,7 +72,12 @@ def make_prl_plots(plot2_inset=0):
     pm_jml_75_fsi, f_red_fsiXsec_JML_75 = read_theoretical_models("JML", "FSI", 75)
     pm_wjc2_75_fsi, f_red_fsiXsec_WJC2_75 = read_JWVO_theory(75, "WJC2", "GKex05", "DWBA")
 
-
+    print('=========MSV18 (35 deg)=========')
+    print('pr(pwia) = ',  pm_v18_35_pwia)
+    print('redXsec_pwia = ', f_red_pwiaXsec_V18_35( pm_v18_35_pwia) )
+    print('pr(fsi) = ',  pm_v18_35_fsi)
+    print('redXsec_fsi = ', f_red_fsiXsec_V18_35( pm_v18_35_fsi) )
+    print('=========MSV18 (35 deg)=========')
 
     #======== Define Ratios of Reduced Cross Sections (to be used in PRL PLOT 2)=====
     
@@ -500,29 +506,6 @@ def make_prl_plots(plot2_inset=0):
 
 
 
-def write_Xsec(ithnq=0, ipm=np.array([])):
-
-    
-    fout_name = 'redXsec_theory_thnq%d_deg.txt' % (int(ithnq))
-    fout = open(fout_name, 'w')
-    comment1='#theoretical reduced cross sections as a function of missing momentum \n
-    all reduced cross sections have been MS_CD-Bonn, MS_AV18, JML_Paris, JVO_WJC2 using  PWIA and FSI. \n
-    '
-
-
-
-    
-    comment2='#Units: pm_avg [GeV/c] :: redXsec [fm^3],   theta_nq = 35 +\- 5 deg \n'
-    header='#!pm_avg[f,0]/   data_redXsec[f,1]/   data_redXsec_tot_err[f,2]/   stats_rel_err[f,3]/  kin_rel_err[f,4]/   norm_rel_err[f,5]   tot_rel_syst_err[f,6]/   tot_rel_err[f,7]/   \n'
[…]

### 2020-10-11 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updates supp.tex

@@
 %\titlespacing{\section}{0pt}{2ex}{2ex}
-
+\usepackage{comment}
 \usepackage{graphicx}  % needed for figures
@@
 \maketitle
-\section{\large Spectrometer Acceptance}
-\noindent The $^{1}$H$(e,e'p)$ coincidence elastic reaction was used (at kinematics very similar to the deuteron 80 MeV/c setting) to check of the spectrometers'
-acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} was used. \\
-\indent Figures \ref{fig:fig1} and \ref{fig:fig2} show the spectrometers' reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$)
-where $\delta$ is the momentum fraction defined as $\delta = \frac{P-P_{0}}{P_{p}}$, where $P$ is the particle momentum and $P_{0}$ is the spectrometer central momentum.
-The $Y_{\mathrm{tar}}$ is the reconstructed trajectory along the spectrometer $y-$coordinate, and ($Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) are the reconstructed trajectories
-tangent to the spectrometer central optics axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.
-See Section 4.4 of Ref.\cite{cyero_phdthesis} for a more detailed description of these quantities.\\
-\begin{figure}[h]
-\includegraphics[scale=0.36]{plots/hms_acc_3288.png}
-\caption{HMS reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) at the target reaction vertex using $^{1}$H$(e,e'p)$.
-  For each reconstructed quantity, the top panel shows a comparison between data (blue) and SIMC (red) with their respective integrated charge-normalized yields
-  and the data-to-SIMC ratio numerical values (top-left corner). The bottom panel shows the data to SIMC yield ratio (Y$_{\mathrm{data}}$/Y$_{\mathrm{SIMC}}$) on a
-  bin-by-bin basis, where the inner (black) and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
-\label{fig:fig1}
-\end{figure}
-\clearpage
-\begin{figure}[!ht]
-\includegraphics[scale=0.36]{plots/shms_acc_3288.png}
-\caption{Same as Fig. \ref{fig:fig1}, but for SHMS. }
-\label{fig:fig2}
-\end{figure}
 \section{\large Event Selection Cuts}
-\noindent Figures \ref{fig:fig3}-\ref{fig:fig7} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
+\noindent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
 The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
-The exact same cuts were also applied to the 580 and 750 MeV/c settings. The data yield has been normalized by the total charge and corrected for the inefficiencies described in the Letter.
-The FSI model from J.M. Laget was used in the simulation for the plots shown below.
+The exact same cuts were also applied to the 580 and 750 MeV/c settings. Each histogram has all the other event selection cuts described except a self cut.
+The integrated counts (within the cut boundary) for data and simulation as well as the data-to-simulation yield ratio is shown (top left) for each selection cut.
+The data yield has been normalized by the total charge and corrected for the inefficiencies described in the Letter. The FSI model from J.M. Laget was used in the simulation for the plots shown below.
 \begin{figure}[!h]
-\includegraphics[scale=0.30]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.25]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
-\label{fig:fig3}
-\end{figure}
-\clearpage
+\label{fig:Em_Q2_cuts}
+\includegraphics[scale=0.25]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
+  Inset (left): The SHMS momentum acceptance range.}
+\label{fig:delta_Ztar_cuts}
+\end{figure}\\
+\indent Figure \ref{fig:Em_Q2_cuts} (left) shows the primary cut used to select true $^{2}\mathrm{H}(e,e'p)n$ coincidence events by requiring a missing
+energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
+recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
+been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
+to select events only at the highest possible momentum transfers to further suppress MEC and IC. \\
+\indent Figure \ref{fig:delta_Ztar_cuts} (left) shows a momentum acceptance ($\delta$) cut made on the HMS in the range $8\%\leq\delta\leq8\%$, where the optics reconstruction
+is reliable and well understood from previous experiments in the 6 GeV era. The inset shows the SHMS momentum acceptance which was constrained by that of the HMS to be
+$|\delta|\lesssim$3$\%$ which is well within the reliable SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$. Figure \ref{fig:delta_Ztar_cuts} (right) shows reaction vertex cut
+on the difference between the HMS and SHMS reconstructed reaction vertices along the $z$-coordinate (target length). The cut is made at $\pm2$ cm relative to the histogram peak.
+If the events originated from the same reaction vertex (i.e., true coincidences), the difference should peak at zero with a finite resolution width. If the events are uncorrelated
+(i.e., accidental coincidences), however, the reconstruction along the $z_{\mathrm{v}}$-vertex can vary significantly between the two spectrometers, which contribute to the tails of the
+distribution.
+
 \begin{figure}
-\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
-\caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
-  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$}
-\label{fig:fig4}
-\includegraphics[scale=0.30]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.25]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
-\label{fig:fig5}
-\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_data.png}
+\label{fig:coin_ecal_cuts}
+\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
   The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
-\label{fig:fig6}
-\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
-\caption{Same as Fig. \ref{fig:fig6}, but for simulation.}
-\label{fig:fig7}
+\label{fig:data_coll_cuts}
+\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
+\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}
+\label{fig:simc_coll_cuts}
 \end{figure}
@@
 \section{\large Deuteron Kinematic Distributions }
-\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
+\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
 The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
+\includegraphics[scale=0.3]{plots/d2_kin_thnq35.png}
 \caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
-\label{fig:fig8}
-\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
-\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}
-\label{fig:fig9}
+\label{fig:d2_kin_35deg}
+\includegraphics[scale=0.3]{plots/d2_kin_thnq45.png}
+\caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}
+\label{fig:d2_kin_45deg}
 \end{figure}
@@
 negative part of the spectrum over a specific range, we can estimate the endcaps contribution beneath the deuteron missing energy peak over the same range.\\
-\indent Figure \ref{fig:fig10} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
+\indent Figure \ref{fig:tgt_wall} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
 range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls is 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.35]{plots/tgt_bkg_d2_pm580_allthnq.png}
+\includegraphics[scale=0.3]{plots/tgt_bkg_d2_pm580_allthnq.png}
 \caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
@@
   scale.}
-\label{fig:fig10}
+\label{fig:tgt_wall}
 \end{figure}
@@
 \noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)
-kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig11}. The calculation was done using the
+kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:RC_factor}. The calculation was done using the
 Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield.
 \begin{figure}[!h]
-\includegraphics[scale=0.40]{plots/RC_factor.png}
+\includegraphics[scale=0.30]{plots/RC_factor.png}
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
-\label{fig:fig11}
+\label{fig:RC_factor}
 \end{figure}\\
@@
 kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
-Fig. \ref{fig:fig12}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
+Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
 \begin{figure}[!h]
-\includegraphics[scale=0.40]{plots/BC_factor.png}
+\includegraphics[scale=0.30]{plots/BC_factor.png}
 \caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
   The inner (black dashed) and outer (red dash-dotted) lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
-\label{fig:fig12}
+\label{fig:BC_factor}
 \end{figure}
@@
   \begin{align}
-    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{bc,1}} - \sigma^{\mathrm{exp}}_{\mathrm{bc,2}}, \\
-    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}})^{2},
+    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
+    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
   \end{align}
@@
 For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
-\indent Figure \ref{fig:fig13} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
-In Fig. \ref{fig:fig13}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
+\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
+In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
 the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
@@
 \begin{figure}[!ht]
-\includegraphics[scale=0.4]{plots/Em_syst.png}
+\includegraphics[scale=0.3]{plots/Em_syst.png}
 \caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
   lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
-\label{fig:fig13}
+\label{fig:Em_sys}
 \end{figure}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.33]{plots/rad_sys.png}
+\includegraphics[scale=0.3]{plots/rad_sys.png}
 \caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 }
-\label{fig:fig14}
-\includegraphics[scale=0.33]{plots/bc_sys.png}
-\caption{Same as Fig. \ref{fig:fig14} but for bin-centering corrections.}
-\label{fig:fig15}
+\label{fig:rad_sys}
+\includegraphics[scale=0.3]{plots/bc_sys.png}
+\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering corrections.}
+\label{fig:bc_sys}
 \end{figure}
 \clearpage
-Figures \ref{fig:fig14} and \ref{fig:fig15} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
+Figures \ref{fig:rad_sys} and \ref{fig:bc_sys} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
 the model dependency of the correction factors have a negligible effect on the experimental cross sections.
@@
 \noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig16} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
 missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.38]{plots/Pr_and_Ps.png}
+\includegraphics[scale=0.3]{plots/Pr_and_Ps.png}
 \caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
   the spectrometers' phase space volume binned in missing momentum.}
-\label{fig:fig16}
+\label{fig:Pm_Ps}
 \end{figure}
+
 %\clearpage

### 2020-10-11 PRL_UTILITIES_CODES/codes/THESIS/Rad_BC_corr_plots/check_RCBC_ratio.py

@@ -267,18 +267,18 @@ for i, ithnq in enumerate(thnq_arr):
     #Plot RC ratio PWIA and FSI
     B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_80[thnq==ithnq], RC_fact_pwia_80_err[thnq==ithnq], marker='o', color='k', label='PWIA')
     B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_580s1[thnq==ithnq], RC_fact_pwia_580s1_err[thnq==ithnq], marker='s', color='b', logy=False, label='PWIA')
-    B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_580s2[thnq==ithnq], RC_fact_pwia_580s2_err[thnq==ithnq], marker='^', color='r', logy=False, label='PWIA')
-    B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_750s1[thnq==ithnq], RC_fact_pwia_750s1_err[thnq==ithnq], marker='v', color='g', logy=False, label='PWIA')
-    B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_750s2[thnq==ithnq], RC_fact_pwia_750s2_err[thnq==ithnq], marker='p', color='m', logy=False, label='PWIA')
-    B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_750s3[thnq==ithnq], RC_fact_pwia_750s3_err[thnq==ithnq], marker='D', color='c', logy=False, label='PWIA')
+    #B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_580s2[thnq==ithnq], RC_fact_pwia_580s2_err[thnq==ithnq], marker='^', color='g', logy=False, label='PWIA')
+    B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_750s1[thnq==ithnq], RC_fact_pwia_750s1_err[thnq==ithnq], marker='v', color='r', logy=False, label='PWIA')
+    #B.plot_exp(pm[thnq==ithnq], RC_fact_pwia_750s2[thnq==ithnq], RC_fact_pwia_750s2_err[thnq==ithnq], marker='p', color='m', logy=False, label='PWIA')
[…]

### 2020-10-11 PRL_UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -297,3 +297,89 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
 
 
 }
+
+
+
+//-----------------------------------------------
+void combine_sets(TH1F *hist80, TH1F *hist_580set1, TH1F *hist_580set2, TH1F *hist_750set1, TH1F *hist_750set2, TH1F *hist_750set3, TString xlabel="", TString ylabel="", TString title="", Double_t scale_factor=1)
+{
+
+  //This function adds histograms of multiple data sets from the same kinematic setting (i.e., 580_set1 + 580_set2)
+ 
+
+  //Clone histograms and rename them total
+  TH1F *hist_580tot = (TH1F*)hist_580set1->Clone("hist_580tot");
+  TH1F *hist_750tot = (TH1F*)hist_750set1->Clone("hist_750tot");
+
+  //Add remaining histograms to total
+  hist_580tot->Add(hist_580set2);
+
+  hist_750tot->Add(hist_750set2);
+  hist_750tot->Add(hist_750set3);
+
+  
+  int font_type = 132;
+
+  gStyle->SetOptStat(0);
+  gStyle->SetTitleFontSize(0.05);
+  gStyle->SetTitleFont(font_type, "");
+  gStyle->SetLegendBorderSize(0);
+  gStyle->SetLegendFont(font_type);
+  gStyle->SetLegendTextSize(0.03);
+
+  //Create Canvas
+  TCanvas *c = new TCanvas(title, "c", 900, 700);
+  c->SetFrameLineWidth(2);
+  c->cd();
+
+  //Set Frame Margin spacing (smaller spacing->tighter frame)
+  gPad->SetLeftMargin(0.13);
+  gPad->SetRightMargin(0.05);
+  gPad->SetTopMargin(0.1);
+  gPad->SetBottomMargin(0.12);
+  
+  hist80->SetLineColor(kBlue);
+  hist80->SetLineWidth(2);
+  hist80->SetFillColorAlpha(kBlue, 0.6);
+  hist80->SetFillStyle(3004);
+
+  hist_580tot->SetLineColor(kRed);
+  hist_580tot->SetLineWidth(2);
+  hist_580tot->SetFillColorAlpha(kRed, 0.6);
+  hist_580tot->SetFillStyle(3004);
+
+  hist_750tot->SetLineColor(kMagenta);
[…]

### 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updated supplementary doc

@@
 \begin{figure}[!h]
-\includegraphics[scale=0.25]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.24]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
 \label{fig:Em_Q2_cuts}
-\includegraphics[scale=0.25]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\includegraphics[scale=0.24]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
 \caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
@@
 (i.e., accidental coincidences), however, the reconstruction along the $z_{\mathrm{v}}$-vertex can vary significantly between the two spectrometers, which contribute to the tails of the
-distribution.
-
-\begin{figure}
-\includegraphics[scale=0.25]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+distribution.\\
+\begin{figure}[!h]
+\includegraphics[scale=0.24]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
 \label{fig:coin_ecal_cuts}
-\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}
+\end{figure}\\
+\indent Figure \ref{fig:coin_ecal_cuts} (left) shows a coincidence time cut on the $ep$ coincidence time spectrum formed by requiring a logic signal of
+at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 2 ns beam bunch structure due to accidental
+coincidences is not observed. The out-of-time events observed at the tails can originate from the radiation in the Hall partially entering the detector huts and forming
+a trigger in coincidence with the other arm. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
+deposited normalized by the particle track momentum. This cut was used to separate electrons from background (pions), however, the spectrum shows a very clean distribution
+with a peak at about one indicating the detected particles were electrons.
+\begin{figure}[!h]
+\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
@@
 \label{fig:data_coll_cuts}
-\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
+\end{figure}
+\begin{figure}[!h]
+\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
 \caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}
 \label{fig:simc_coll_cuts}
-\end{figure}
+\end{figure}\\
+\indent Figure \ref{fig:data_coll_cuts} (left) shows
+
 \clearpage
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{plots/d2_kin_thnq35.png}
+\includegraphics[scale=0.25]{plots/d2_kin_thnq35.png}
 \caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
 \label{fig:d2_kin_35deg}
-\includegraphics[scale=0.3]{plots/d2_kin_thnq45.png}
+\includegraphics[scale=0.25]{plots/d2_kin_thnq45.png}
 \caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}

### 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updates supp

@@
 \includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
-\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
-  The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
+\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
+  projected at the SHMS collimator.}
 \label{fig:data_coll_cuts}
 \end{figure}
+\clearpage
+\indent Figure \ref{fig:data_coll_cuts} (left) shows a geometrical (red octogon) cut on the reconstructed events projected at the HMS collimator to ensure
+that all events that enter the spectrometer pass through the collimator, and not re-scatter at the edges. This cut is needed since protons that enter the
+HMS can punch through the collimator with a probability that is related to the proton-Aluminum total cross section. Figure \ref{fig:data_coll_cuts} (right)
+shows the correlated events projected at the SHMS collimator which clearly shows that the events are well within the collimator which indicates that the SHMS
+acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation.\\
 \begin{figure}[!h]
@@
 \label{fig:simc_coll_cuts}
-\end{figure}\\
-\indent Figure \ref{fig:data_coll_cuts} (left) shows
-
-\clearpage
+\end{figure}
 \section{\large Deuteron Kinematic Distributions }
-\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
-The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
-The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
-Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 
+\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the
+central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$. The data has been normalized by the total charge and corrected
+for the inefficiencies described in the Letter. The same event selection cuts mentioned in the previous section were applied. 
 \begin{figure}[!h]
-\includegraphics[scale=0.25]{plots/d2_kin_thnq35.png}
-\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
+\includegraphics[scale=0.18]{plots/d2_kin_thnq35.png}
+\caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c setting at $\theta_{nq}=35^{\circ}$.}
 \label{fig:d2_kin_35deg}
-\includegraphics[scale=0.25]{plots/d2_kin_thnq45.png}
+\end{figure}
+\begin{figure}[!h]
+\includegraphics[scale=0.18]{plots/d2_kin_thnq45.png}
 \caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}
@@
 \end{figure}
-\clearpage
 \section{\large Estimate of the Target Cell Endcaps Contribution to the Data Yield}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{plots/tgt_bkg_d2_pm580_allthnq.png}
+\includegraphics[scale=0.33]{plots/tgt_bkg_d2_pm580_allthnq.png}
 \caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
@@
 \label{fig:tgt_wall}
+\end{figure}
+\section{\large Cross-Section Extraction}
+\noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
+A detailed discussion of how the experimental and reduced cross sections were extracted can be
+found in Sections 5.1 and 6.1 of Ref. \cite{cyero_phdthesis}.
+\begin{figure}[!h]
+\includegraphics[scale=0.3]{plots/Pr_and_Ps.png}
+\caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
+  the spectrometers' phase space volume binned in missing momentum.}
+\label{fig:Pm_Ps}
 \end{figure}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.30]{plots/RC_factor.png}
+\includegraphics[scale=0.27]{plots/RC_factor.png}
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.30]{plots/BC_factor.png}
+\includegraphics[scale=0.27]{plots/BC_factor.png}
 \caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 \end{figure}
-\clearpage
 Figures \ref{fig:rad_sys} and \ref{fig:bc_sys} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
 the model dependency of the correction factors have a negligible effect on the experimental cross sections.
-\section{\large Cross-Section Extraction}
-\noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
-missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
-A detailed discussion of how the experimental and reduced cross sections were extracted can be
-found in Sections 5.1 and 6.1 of Ref. \cite{cyero_phdthesis}.
-\begin{figure}[!h]
-\includegraphics[scale=0.3]{plots/Pr_and_Ps.png}
-\caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
-  the spectrometers' phase space volume binned in missing momentum.}
-\label{fig:Pm_Ps}
-\end{figure}
 

### 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
finished corrections on supp

@@
 kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:RC_factor}. The calculation was done using the
-Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield.
+Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. The uncertainty in the radiative
+correction factor was determined by the Monte-Carlo statistics from the simulation. The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can
+be understood from the fact that statistics were limited in this phase space region as indicated by the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 
 \begin{figure}[!h]
-\includegraphics[scale=0.27]{plots/RC_factor.png}
+\includegraphics[scale=0.26]{plots/RC_factor.png}
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
@@
 kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
-Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.
+Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. The
+uncertainty in the bin-centering correction factor was determined from the standard error propagation of a ratio between two quantities. 
 \begin{figure}[!h]
-\includegraphics[scale=0.27]{plots/BC_factor.png}
+\includegraphics[scale=0.26]{plots/BC_factor.png}
 \caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 \label{fig:BC_factor}
-\end{figure}
+\end{figure}\\
 \section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
@@
 \indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
-statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}$)
+statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
 where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
@@
 \begin{figure}[!ht]
-\includegraphics[scale=0.3]{plots/Em_syst.png}
+\includegraphics[scale=0.4]{plots/Em_syst.png}
 \caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
@@
 \end{figure}
-\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated using the Barlow ratio approach described above.
-In this case, the ratio was calculated from the difference between the experimental cross sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections.
+\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
+using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross
+sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections. Figures \ref{fig:rad_sys} and \ref{fig:bc_sys}
+show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
+the model dependency of the correction factors have a negligible effect on the experimental cross sections.
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{plots/rad_sys.png}
+\includegraphics[scale=0.31]{plots/rad_sys.png}
 \caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 \label{fig:rad_sys}
-\includegraphics[scale=0.3]{plots/bc_sys.png}
-\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering corrections.}
+\includegraphics[scale=0.31]{plots/bc_sys.png}
+\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering correction systematics.}
 \label{fig:bc_sys}
 \end{figure}
-Figures \ref{fig:rad_sys} and \ref{fig:bc_sys} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
-the model dependency of the correction factors have a negligible effect on the experimental cross sections.
 

### 2020-10-13 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v2.tex
updated PRL revised

--- 2020-10-08 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised.tex
@@
 dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
-carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions
+carried out at Jefferson Lab (JLab) and Brookhaven National Lab (BNL). In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
 have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
-Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
-(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\
+Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
+(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. \\
 %===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v3.tex
updated PRL to reduce wordcount

--- 2020-10-13 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v2.tex
@@
 Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
-(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. \\
+(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.
+Due to FSI effects, the measurement of certain missing momentum does not yet guarantee that the initial
+bound nucleon with the same momentum is being measured.\\
 %===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material).
+simulation program, SIMC \cite{PhysRevC.64.054610}\cite{cyero_phdthesis}.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
-and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
-3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
-4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
+%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
+%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
+%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
 The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region for which the reconstruction optics
-are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''
+are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a reconstructed binding
 energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a particle identification (PID) cut on the
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target (see Supplemental Material). \\
+originated from the same reaction vertex at the target (see online Supplemental Material). \\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
@@
 $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged
-over the kinematic bin.
-The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material).
+over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects
+on the cross sections were found (see online Supplemental Material).
 The experimental and theoretical reduced cross sections were extracted and are defined as follows:
@@
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
-$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
 is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
@@
 For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
-The MS calculations used the FF parametrization of Ref.
-\cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
-for the neutron electric FF, and the results from the Hall A experiment of Ref.
-\cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
-The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
-JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
+The calculations use different FF parametrizations which can lead to a 6$\%$ change of the theortical cross section.\\
+%----REMOVED ON 10/14/2020----------
+%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
+%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
+%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
+%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
+%difference of $\sim5.8-6.6 \%$ was found between the respective
+%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
 \indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
@@
 %\nocite{COSY}
-%\nocite{barlow2002systematic}
-%\nocite{barlow2017}
+\nocite{barlow2002systematic}
+\nocite{barlow2017}
 

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/MARKED/supp_revised.tex
updated PRL to reduce wordcount

--- 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
@@
 \indent Figure \ref{fig:Em_Q2_cuts} (left) shows the primary cut used to select true $^{2}\mathrm{H}(e,e'p)n$ coincidence events by requiring a missing
-energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
-recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
-been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
+energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula, $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where
+$\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy,
+$T_{\mathrm{r}}$, is calculated from the electron and proton 4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.
+The peak is not exactly at the deuteron binding energy because energy loss corrections have not been applied to the data nor SIMC. \\
+\indent Figure \ref{fig:Em_Q2_cuts} (right) shows a
+kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
 to select events only at the highest possible momentum transfers to further suppress MEC and IC. \\
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
+\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),

### 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_original.tex
updated PRL to reduce wordcount

@@
 \section{\large Event Selection Cuts}
-\noindent Figures \ref{fig:fig3}-\ref{fig:fig7} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
+\noindent Figures \ref{fig:fig1}-\ref{fig:fig5} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
 The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.30]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.35]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
-\label{fig:fig3}
+\label{fig:fig1}
 \end{figure}
-\clearpage
 \begin{figure}
@@
   Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$}
-\label{fig:fig4}
+\label{fig:fig2}
 \includegraphics[scale=0.30]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
-\label{fig:fig5}
+\label{fig:fig3}
 \includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_data.png}
@@
   The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}
-\label{fig:fig6}
+\label{fig:fig4}
 \includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
-\caption{Same as Fig. \ref{fig:fig6}, but for simulation.}
-\label{fig:fig7}
+\caption{Same as Fig. \ref{fig:fig4}, but for simulation.}
+\label{fig:fig5}
 \end{figure}
@@
 \section{\large Deuteron Kinematic Distributions }
-\noindent Figures show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}, 45^{\circ}$.
-The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter.  
+\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
+The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
+The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
+Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 
 \begin{figure}[!h]
 \includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}
-\caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
+\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}
 \label{fig:fig8}
 \includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
-\caption{Same as Fig. \ref{}, but for $\theta_{nq}=45^{\circ}$}
+\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}
 \label{fig:fig9}
@@
   the spectrometers' phase space volume binned in missing momentum.}
-\label{fig:fig14}
+\label{fig:fig16}
 \end{figure}
+
 %\clearpage

### 2020-10-14 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated PRL to reduce wordcount

--- 2020-10-07 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootinbib]{revtex4-2}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
 \pdfoutput=1
@@
 dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
-carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions
+carried out at Jefferson Lab (JLab) and Brookhaven National Lab (BNL). In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
 have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
-Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
-(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\
+Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
+(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.
+Due to FSI effects, the measurement of certain missing momentum does not yet guarantee that the initial
+bound nucleon with the same momentum is being measured.\\
 %===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material).
+simulation program, SIMC \cite{PhysRevC.64.054610}\cite{cyero_phdthesis}.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
-and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
-3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
-4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
+%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
+%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
+%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
 The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region for which the reconstruction optics
-are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''
+are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a reconstructed binding
 energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a particle identification (PID) cut on the

### 2020-10-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_revised.tex
update supp

--- 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/MARKED/supp_revised.tex
@@
 energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula, $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where
-$\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy,
-$T_{\mathrm{r}}$, is calculated from the electron and proton 4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.
-The peak is not exactly at the deuteron binding energy because energy loss corrections have not been applied to the data nor SIMC. \\
+$T_{p}$ is the final proton kinetic energy and $T_{\mathrm{r}}$ is the recoil particle kinetic energy which is calculated from the electron and proton
+4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron. The peak is not exactly at the deuteron binding energy because
+energy loss corrections have not been applied to the data nor SIMC. \\
 \indent Figure \ref{fig:Em_Q2_cuts} (right) shows a

### 2020-10-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v4.tex
updated prl

--- 2020-10-14 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/MARKED/ms_revised_v3.tex
@@
   the plane wave impulse approximation (PWIA) provides the dominant cross section contribution. The new data are compared to recent
-  theoretical calculations, where we observe a significant discrepancy for missing momenta $p_{\mathrm{r}}>700$ MeV/c. 
+  theoretical calculations, where we observe a significant discrepancy for recoil momenta $p_{\mathrm{r}}>700$ MeV/c. 
 \end{abstract}
@@
 dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
-carried out at Jefferson Lab (JLab) and Brookhaven National Lab (BNL). In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
+carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}.
+In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
 have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
@@
 (Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.
-Due to FSI effects, the measurement of certain missing momentum does not yet guarantee that the initial
+Due to FSI effects, the measurement of a certain missing momentum does not yet guarantee that the initial
 bound nucleon with the same momentum is being measured.\\
@@
 from FSI, MEC and IC to the $^{2}\mathrm{H}(e,e'p)n$ cross sections and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\
-\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$.
+\indent At large $Q^{2}$, FSI can be described by the Generalized Eikonal Approximation (GEA) \cite{Sargsian_2001,PhysRevC.56.1124,sargsian_2015}, which predicts a strong dependence of FSI on neutron recoil angles $\theta_{nq}$ (relative angles between recoil momenta $\vec{p}_{\mathrm{r}}$ and 3-momentum transfers $\vec{q}$).
 GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{\circ}$.
@@
 \indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ ($>1$ (GeV/c)$^{2}$) were carried out at JLab in Halls A \cite{PhysRevLett.107.262501} and B \cite{PhysRevLett.98.262502}. Both
-experiments determined that the cross sections for fixed missing momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking
+experiments determined that the cross sections for fixed recoil momenta indeed exhibited a strong angular dependence with $\theta_{nq}$, peaking
 at $\theta_{nq} \sim 70^{\circ}$ in agreement with GEA \cite{Sargsian_2001,PhysRevC.56.1124} calculations. In Hall B, the CEBAF Large Acceptance Spectrometer (CLAS) measured angular
@@
 For each spectrometer, a logic signal was created from  the coincidence of hits in at least three of the four scintillator planes. The event trigger was the coincidence of these two signals. \\
-\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
+\indent We measured three central recoil momentum settings: $p_{\mathrm{r}}=80, 580$ and $750$ MeV/c.
 At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to
-the lower and higher missing momentum settings, respectively.
+the lower and higher recoil momentum settings, respectively.
 At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c, which is more than twice the highest neutron recoil momentum
@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610}\cite{cyero_phdthesis}.
+simulation program, SIMC \cite{PhysRevC.64.054610}.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
@@
 were as follows\cite{cyero_phdthesis}: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) and
-target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all missing momentum settings. \\
+target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all recoil momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 \indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
-determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
+determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each recoil momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
@@
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
-($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
-is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
+($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the FF parametrization of Ref. \cite{PhysRevC.69.022201}.
@@
 For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
-The calculations use different FF parametrizations which can lead to a 6$\%$ change of the theortical cross section.\\
+The calculations use different FF parametrizations which can lead to a $\sim$5.8 -6.6$\%$ variation of the theortical cross section.\\
 %----REMOVED ON 10/14/2020----------
@@
 Furthermore, the MS CD-Bonn model was found to be significantly different than the JML, MS AV18 or JVO models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
-At the higher missing momenta provided by this experiment ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
-Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
+At the higher recoil momenta provided by this experiment ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data,
+potentially illustrating the limit to which a non-relativistic wave function from the solution to the Schr\"{o}dinger equation is valid and able to describe
+experimental data that probe the high momentum region of the $np$ system in the most direct way possible.
+Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high recoil
 momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\

### 2020-10-15 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated prl

@@
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target (see Supplemental Material). \\
+originated from the same reaction vertex at the target (see online Supplemental Material). \\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
 were as follows\cite{cyero_phdthesis}: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) and
-target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all missing momentum settings. \\
+target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all recoil momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
-($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
-is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
+($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+is a recoil factor \ref{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the FF parametrization of Ref. \cite{PhysRevC.69.022201}.

### 2020-10-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp.tex
updated PRL

--- 2020-10-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp_revised.tex
@@
 \section{\large Event Selection Cuts}
-\noindent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
+\indent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
 The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
@@
 \section{\large Deuteron Kinematic Distributions }
-\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the
+\indent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the
 central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$. The data has been normalized by the total charge and corrected
@@
 \section{\large Estimate of the Target Cell Endcaps Contribution to the Data Yield}
-\noindent To estimate the contribution to the yield due to the electron interaction with the aluminum endcaps of the target cell,
+\indent To estimate the contribution to the yield due to the electron interaction with the aluminum endcaps of the target cell,
 a sample of events were selected in the negative part of the missing energy spectrum using the deuteron high missing momentum settings (580 and 750 MeV/c).
@@
 \section{\large Cross-Section Extraction}
-\noindent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
+\indent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
 kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
@@
 \section{\large Radiative \& Bin-Centering Corrections}
-\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)
+\indent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)
 kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:RC_factor}. The calculation was done using the
@@
 \section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
-A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
+\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
 To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant

### 2020-10-18 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
updated PRL

@@
 ($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
-is a recoil factor \ref{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
+is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the FF parametrization of Ref. \cite{PhysRevC.69.022201}.

### 2020-10-19 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
updated supp

@@
 dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
-carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions
+carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}.
+In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
 have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
-Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
-(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\
+Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
+(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.
+Due to FSI effects, the measurement of a certain missing momentum does not yet guarantee that the initial
+bound nucleon with the same momentum is being measured.\\
 %===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
@@
 \indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data were also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the Hall C Monte Carlo
-simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material).
+simulation program, SIMC \cite{PhysRevC.64.054610}.
 Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization,
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
-and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
-3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
-4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
+%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
+%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
+%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
+%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
 The criteria were determined by making standard cuts on the spectrometer momentum fraction ($\delta$) to select a region for which the reconstruction optics
-are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a ``missing''
+are well known,  a cut to restrict the HMS solid angle acceptance to events that passed directly through the collimator and not by re-scattering from the collimator edges, a reconstructed binding
 energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events, a particle identification (PID) cut on the
 SHMS calorimeter normalized total track energy to select electrons and not other sources of background (mostly pions), and a cut on the reconstructed HMS and SHMS reaction vertices to select events that
-originated from the same reaction vertex at the target (see Supplemental Material). \\
+originated from the same reaction vertex at the target (see online Supplemental Material). \\
 \indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$, the corrections
 were as follows\cite{cyero_phdthesis}: tracking efficiencies ($98.9 \%$-HMS, $96.4 \%$-SHMS), total live time ($92.3 \%$), proton loss inefficiency due to nuclear interactions in the HMS ($4.7 \%$) and
-target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all missing momentum settings. \\
+target boiling inefficiency ($4.2 \%$). The values in parentheses were averaged over all recoil momentum settings. \\
 \indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using Arrington's proton form factor (FF) parametrization \cite{PhysRevC.69.022201} to check the spectrometer acceptance
@@
 and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
-the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
-to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
+the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), total charge ($2.0\%$), target wall contributions ($\leq2.9\%$) and spectrometer acceptance ($1.4\%$),  which were the same for every setting,
+to define the overall normalization uncertainty ($\leq5.3\%$).\\
 \indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
-determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each missing momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
+determined point-to-point in ($\theta_{nq}$, $p_{\mathrm{r}}$) bins for each recoil momentum setting, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins. 
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
-The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 5.3$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
 \begin{figure*}[t]
@@
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
-$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
-is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the
+($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
 de Forest \cite{DEFOREST1983} electron-proton off-shell cross section calculated using the FF parametrization of Ref. \cite{PhysRevC.69.022201}.
@@
 For the WJC2 (orange) potential, the calculations were carried out by Ford, Jeschonnek and Van Orden \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states, which will be labeled JVO.
-The MS calculations used the FF parametrization of Ref.
-\cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
-for the neutron electric FF, and the results from the Hall A experiment of Ref.
-\cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
-The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
-JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
+The calculations use different FF parametrizations which can lead to a $\sim$5.8 -6.6$\%$ variation of the theortical cross section.\\
+%----REMOVED ON 10/14/2020----------
+%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
+%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
+%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
+%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
+%difference of $\sim5.8-6.6 \%$ was found between the respective
+%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
 \indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
@@
   The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.
-  Insets: A blowup of the corresponding subfigure in the range $p_{\mathrm{r}}=0 - 0.7$ GeV/c.}
+  Insets: Blowup of the subfigures below $p_{\mathrm{r}}=$0.7 GeV/c.}
 \label{fig:fig2}
@@
 %---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
-\nocite{COSY}
+%\nocite{COSY}
 \nocite{barlow2002systematic}

### 2020-10-19 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updated supp

@@
 \indent Figure \ref{fig:Em_Q2_cuts} (left) shows the primary cut used to select true $^{2}\mathrm{H}(e,e'p)n$ coincidence events by requiring a missing
-energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
-recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
-been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
+energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula, $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where
+$T_{p}$ is the final proton kinetic energy and $T_{\mathrm{r}}$ is the recoil particle kinetic energy which is calculated from the electron and proton
+4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron. The peak is not exactly at the deuteron binding energy because
+energy loss corrections have not been applied to the data nor SIMC. \\
+\indent Figure \ref{fig:Em_Q2_cuts} (right) shows a
+kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
 to select events only at the highest possible momentum transfers to further suppress MEC and IC. \\
@@
 that all events that enter the spectrometer pass through the collimator, and not re-scatter at the edges. This cut is needed since protons that enter the
-HMS can punch through the collimator with a probability that is related to the proton-Aluminum total cross section. Figure \ref{fig:data_coll_cuts} (right)
+HMS can punch through the collimator with a probability that is related to the proton-Tungsten total cross section. Figure \ref{fig:data_coll_cuts} (right)
 shows the correlated events projected at the SHMS collimator which clearly shows that the events are well within the collimator which indicates that the SHMS
-acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation.\\
+acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation. The colored
+$z$-axis in both figures is given in arbitrary units.\\
 \begin{figure}[!h]
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.18]{plots/d2_kin_thnq35.png}
+\includegraphics[scale=0.17]{plots/d2_kin_thnq35.png}
 \caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c setting at $\theta_{nq}=35^{\circ}$.}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.18]{plots/d2_kin_thnq45.png}
+\includegraphics[scale=0.17]{plots/d2_kin_thnq45.png}
 \caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}
@@
 \indent Figure \ref{fig:tgt_wall} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified
-range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls is 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
-which is negligible.
+range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls has an upper limit of 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
+as the integral was done over all recoil angles, $\theta_{nq}$. This result was added quadratically to the overall normalization error.
 \begin{figure}[!h]
@@
 \end{figure}\\
-\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
-A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
-To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
-enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
-\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
-statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
-where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
-\begin{subequations}
-  \begin{align}
-    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
-    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
-  \end{align}
-\end{subequations}
-where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
-error accounts for the possible correlation between the two measurements. By taking the ratio
-\begin{equation}
-  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
-\end{equation}
-a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
-ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
-the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
+\section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }
+%\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
+%To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
+%enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
+%\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
+%statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
+%where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
+%\begin{subequations}
+%  \begin{align}
+%    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
+%    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
+%  \end{align}
+%\end{subequations}
+%where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
+%error accounts for the possible correlation between the two measurements. By taking the ratio
+%\begin{equation}
+%  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
+%\end{equation}
+%a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
+%ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
+%the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
 For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
-\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
-In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
-the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
-studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
+%\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
+%In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
+%the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
+%studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
 Similar plots for the other event selection
-cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
-\clearpage
-\begin{figure}[!ht]
-\includegraphics[scale=0.4]{plots/Em_syst.png}
-\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
-  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
-\label{fig:Em_sys}
-\end{figure}
-\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
-using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross
+%cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
+%\clearpage
+%\begin{figure}[!ht]
+%\includegraphics[scale=0.4]{plots/Em_syst.png}
+%\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
+%  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
+%\label{fig:Em_sys}
+%\end{figure}
+\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref.\cite{cyero_phdthesis})
+using the Barlow ratio approach \cite{barlow2002systematic,barlow2017}. In this case, the ratio was calculated from the difference between the experimental cross
 sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections. Figures \ref{fig:rad_sys} and \ref{fig:bc_sys}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.31]{plots/rad_sys.png}
-\caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
-The inner (black dashed) and outer (black solid) lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.
-}
+\includegraphics[scale=0.37]{plots/rad_sys.png}
+\caption{Systematic effects of the radiative corrections model dependency on the data cross sections
+  for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
+  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.  }
 \label{fig:rad_sys}
-\includegraphics[scale=0.31]{plots/bc_sys.png}
+\end{figure}
+\begin{figure}[!ht]
+\includegraphics[scale=0.37]{plots/bc_sys.png}
 \caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering correction systematics.}
 \label{fig:bc_sys}
-\end{figure}
-
-%\clearpage
+\end{figure}\\
+\indent Systematic studies of the event selection cuts described above were also carried out using the R. Barlow approach. The studies demonstrated that variations in the software had a negligible
+effect in the measured cross sections and thus no systematic uncertainties due to software cuts were included in the final result.
+For a detailed discussion of these studies see Section 5.10 of Ref.\cite{cyero_phdthesis}.
+\\\\
 \bibliography{supp}

### 2020-10-19 PRL_UTILITIES_CODES/codes/deep_data_files/Q2_4to5GeV/plot_rel_err.py

@@ -1,0 +1,31 @@
+import LT.box as B
+import numpy as np
+from LT.datafile import dfile
+
+f1 = dfile('redXsec_combined_original.txt')
+f2 = dfile('redXsec_combined.txt')
+
+thnq1 = f1['xb']
+p_miss1 = (f1['pm_avg'])[thnq1==35]
+norm_syst_tot1 = (f1['norm_syst_tot'])[thnq1==35]
+y1 = 0. * p_miss1
+
+thnq2 = f2['xb']
+p_miss2 = (f2['pm_avg'])[thnq2==35]
+norm_syst_tot2_35 = (f2['norm_syst_tot'])[thnq2==35]
+norm_syst_tot2_45 = (f2['norm_syst_tot'])[thnq2==45]
+norm_syst_tot2_75 = (f2['norm_syst_tot'])[thnq2==75]
+
+y2 = 0. * p_miss2
+
+
+print('norm_rel_err_35 = ',norm_syst_tot2_35)
+print('norm_rel_err_45 = ',norm_syst_tot2_45)
+print('norm_rel_err_75 = ',norm_syst_tot2_75)
+
+
+#B.plot_exp(p_miss2, y2, norm_syst_tot2*100, marker='s', color='r', label='with tgt. wall / spec. acc systematics')
+#B.plot_exp(p_miss1, y1, norm_syst_tot1*100, marker='o', color='b', label='original')
+
+#B.pl.legend()
+#B.pl.show('same')

### 2020-10-20 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp.tex
updated PRL/supp/reply

@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.33]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
 \label{fig:Em_Q2_cuts}
-\includegraphics[scale=0.24]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
 \caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
-\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
+\includegraphics[scale=0.33]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeter normalized by the particle track momentum (right).}
 \label{fig:coin_ecal_cuts}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}
+\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
-  projected at the SHMS collimator.}
+  projected at the SHMS collimator. The $z$-axis (color palette) is in arbitrary units.}
 \label{fig:data_coll_cuts}
@@
 that all events that enter the spectrometer pass through the collimator, and not re-scatter at the edges. This cut is needed since protons that enter the
-HMS can punch through the collimator with a probability that is related to the proton-Aluminum total cross section. Figure \ref{fig:data_coll_cuts} (right)
+HMS can punch through the collimator with a probability that is related to the proton-Tungsten total cross section. Figure \ref{fig:data_coll_cuts} (right)
 shows the correlated events projected at the SHMS collimator which clearly shows that the events are well within the collimator which indicates that the SHMS
-acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation.\\
+acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation. The colored
+$z$-axis in both figures is given in arbitrary units.\\
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
-\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}
+\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
+\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.  The $z$-axis (color palette) is in arbitrary units.}
 \label{fig:simc_coll_cuts}
@@
 \caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
-  a 40 MeV range, each. (right) The SHMS $z$-reaction vertex corresponding to the specified region in the missing energy spectrum. Inset (left): Missing energy spectrum on a logarithmic
-  scale.}
+  a 40 MeV range, each.  Inset (left): Missing energy spectrum on a logarithmic scale. (right) The SHMS $z$-reaction vertex corresponding to
+  the specified region in the missing energy spectrum.}
 \label{fig:tgt_wall}
@@
 \end{figure}\\
-\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
-\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
-To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
-enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
-\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
-statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
-where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
-\begin{subequations}
-  \begin{align}
-    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
-    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
-  \end{align}
-\end{subequations}
-where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
-error accounts for the possible correlation between the two measurements. By taking the ratio
-\begin{equation}
-  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
-\end{equation}
-a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
-ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
-the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
+\section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }
+%\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
+%To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
+%enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
+%\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
+%statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
+%where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
+%\begin{subequations}
+%  \begin{align}
+%    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
+%    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
+%  \end{align}
+%\end{subequations}
+%where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
+%error accounts for the possible correlation between the two measurements. By taking the ratio
+%\begin{equation}
+%  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
+%\end{equation}
+%a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
+%ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
+%the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
 For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
-\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
-In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
-the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
-studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
+%\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
+%In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
+%the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
+%studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
 Similar plots for the other event selection
-cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
-\clearpage
-\begin{figure}[!ht]
-\includegraphics[scale=0.4]{plots/Em_syst.png}
-\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
-  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
-\label{fig:Em_sys}
-\end{figure}
-\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
-using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross
+%cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
+%\clearpage
+%\begin{figure}[!ht]
+%\includegraphics[scale=0.4]{plots/Em_syst.png}
+%\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
+%  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
+%\label{fig:Em_sys}
+%\end{figure}
+\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref. \cite{cyero_phdthesis})
+using the Barlow ratio approach \cite{barlow2002systematic,barlow2017}. In this case, the ratio was calculated from the difference between the experimental cross
 sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections. Figures \ref{fig:rad_sys} and \ref{fig:bc_sys}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.31]{plots/rad_sys.png}
-\caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
-The inner (black dashed) and outer (black solid) lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.
-}
+\includegraphics[scale=0.37]{plots/rad_sys.png}
+\caption{Systematic effects of the radiative corrections model dependency on the data cross sections
+  for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
+  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.  }
 \label{fig:rad_sys}
-\includegraphics[scale=0.31]{plots/bc_sys.png}
+\end{figure}
+\begin{figure}[!ht]
+\includegraphics[scale=0.37]{plots/bc_sys.png}
 \caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering correction systematics.}
 \label{fig:bc_sys}
-\end{figure}
-
-%\clearpage
+\end{figure}\\
+\indent Systematic studies of the event selection cuts described above were also carried out using the R. Barlow approach. The studies demonstrated that variations in the software had a negligible
+effect in the measured cross sections and thus no systematic uncertainties due to software cuts were included in the final result.
+For a detailed discussion of these studies see Section 5.10 of Ref.
+\cite{cyero_phdthesis}.
+\\\\
 \bibliography{supp}

### 2020-10-21 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updated supp

@@
 \begin{figure}[!h]
-\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.23]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
@@
 \indent Figure \ref{fig:coin_ecal_cuts} (left) shows a coincidence time cut on the $ep$ coincidence time spectrum formed by requiring a logic signal of
-at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 2 ns beam bunch structure due to accidental
-coincidences is not observed. The out-of-time events observed at the tails can originate from the radiation in the Hall partially entering the detector huts and forming
-a trigger in coincidence with the other arm. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
+at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 4 ns beam bunch structure due to accidental
+coincidences is not observed. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
 deposited normalized by the particle track momentum. This cut was used to separate electrons from background (pions), however, the spectrum shows a very clean distribution
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}
+\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
@@
 kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:RC_factor}. The calculation was done using the
-Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. The uncertainty in the radiative
-correction factor was determined by the Monte-Carlo statistics from the simulation. The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can
-be understood from the fact that statistics were limited in this phase space region as indicated by the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 
+Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. \\
+\indent The uncertainty in the radiative
+correction factor was determined for each ($\theta_{nq}$, $p_{\mathrm{r}}$) bin by the Monte-Carlo statistics from the simulation and was propagated to the final cross section error.
+The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can be understood from the fact that statistics were limited in this phase space region as indicated by
+the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 
 \begin{figure}[!h]
-\includegraphics[scale=0.26]{plots/RC_factor.png}
+\includegraphics[scale=0.27]{plots/RC_factor.png}
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
@@
 kinematic bin, as described in the Letter. The bin centering correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in
-Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. The
-uncertainty in the bin-centering correction factor was determined from the standard error propagation of a ratio between two quantities. 
-\begin{figure}[!h]
-\includegraphics[scale=0.26]{plots/BC_factor.png}
+Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. \\
+\begin{figure}[!ht]
+\includegraphics[scale=0.27]{plots/BC_factor.png}
 \caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 \end{figure}\\
+\indent The uncertainty in the bin-centering correction factor was determined for each  ($\theta_{nq}$, $p_{\mathrm{r}}$) bin
+using the standard error propagation for a ratio of two quantities and the result was propagated to the final cross section error. \\
 \section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }

### 2020-10-21 PRL_UTILITIES_CODES/codes/deep_codes/compare_deep.C

@@ -143,17 +143,17 @@ void compare_deep(int pm, int set, int thnq)
 
   //-------EVENT SELECTION CUTS
   //Plot Only Data Histos
-  plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts / mC", "SHMS Calorimeter Energy"); 
+  //plot_hist(data_pid_eCal, "SHMS Calorimeter E_{dep}/P_{trk}", "Counts / mC", "SHMS Calorimeter Energy"); 
   plot_hist(data_CoinTime, "Coincidence Time [ns]", "Counts / mC", "Coincidence Time"); 
 
   //ONLY PLOT DATA-2-SIMC COMPARISONS (NOT RATIOS)
-  compare_hist(data_hdelta, simc_hdelta_fsi, "HMS #delta [%]", "Counts / mC", "HMS #delta");
-  compare_hist(data_edelta, simc_edelta_fsi, "SHMS #delta [%]", "Counts / mC", "SHMS #delta");
+  //compare_hist(data_hdelta, simc_hdelta_fsi, "HMS #delta [%]", "Counts / mC", "HMS #delta");
+  //compare_hist(data_edelta, simc_edelta_fsi, "SHMS #delta [%]", "Counts / mC", "SHMS #delta");
 
-  compare_hist(data_Q2, simc_Q2_fsi, "Q^{2} [GeV^{2}]", "Counts / mC", "4-Momentum Transfer, Q^{2}"); 
+  //compare_hist(data_Q2, simc_Q2_fsi, "Q^{2} [GeV^{2}]", "Counts / mC", "4-Momentum Transfer, Q^{2}"); 
   //compare_hist(data_thnq, simc_thnq_fsi, "#theta_{nq} [deg]", "Counts", "Neutron Recoil Angles, #theta_{nq}");
-  compare_hist(data_ztar_diff, simc_ztar_diff_fsi, "Z_{tar} Difference [cm]", "Counts / mC", "Z_{tar} Difference"); 
-  compare_hist(data_emiss, simc_emiss_fsi, "Missing Energy, E_{m} [GeV]", "Counts / mC", "Nuclear Missing Energy", 1); 
+  //compare_hist(data_ztar_diff, simc_ztar_diff_fsi, "Z_{tar} Difference [cm]", "Counts / mC", "Z_{tar} Difference"); 
[…]

### 2020-10-21 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/reply_to_RefereeA.txt

@@
 ----------
-As mentioned in response to (1), I re-wrote the introductory paragraph.
+As mentioned in response to (1), the introductory paragraph was re-written.
 
@@
 ----------
-I have added Q2 distribution (for 80 MeV/c setting) in the Supplemental Material. I have also
-added the missing momentum distributions for each of the central settings (80, 580 and 750 MeV/c) *** Maybe I can add Q2, xB, w and Pp for each setting (smaller plots)
+I have added the missing momentum distributions as well as the kinematic distributions for Q2, xB, w and Pp 
+for each of the central settings (80, 580 and 750 MeV/c).  See Supplemental Material.
 
@@
 ----------
-The background from target cell wall was found to be negligible at the deuteron kinematics
+The background from target cell wall was accounted for as an overall normalization systematic uncertainty.
 (See Supplemental Material)
@@
 ----------
-See Supplemental Materials.
+A study of the systematic effects on the cross-section due to software cuts was carried out in Section 5.10 of Ref. https://arxiv.org/abs/2009.11343
+The results showed that a reasonable variation of the software cuts had a negligible effect on the cross section.
+
+An additional study on the spectrometers acceptance systematic error was carried out by M.K. Jones where systematic error of ~1.4 % was determined
+and added quadratically to the final resut.
 

### 2020-10-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/reply_to_RefereeA_revised.txt
created version 2 of arXiv PRL submittal package

--- 2020-10-21 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/reply_to_RefereeA.txt
@@
 ----------
-I have published my thesis on arXiv and reference it in the PRL manuscript. I also added supplementary materials.
+The authors' thesis has been published on the arXiv and a reference has been added to the PRL manuscript.
+In addition supplementary materials have been added.
 
@@
 ----------
-I have added an inset with a blowup for Fig. 2, subplots (a) and (b).
+An inset with a blowup for Fig. 2, subplots (a) and (b) has been added.
 
@@
 ----------
-I have added additional raw data files with the theoretical calculations as part of the
-supplemental material.
+Additional raw data files with the theoretical calculations as part of the supplemental material have been added.
 
@@
 ----------
-This part the referee refers to was removed in the introductory paragraph.
+The authors believe that (e, e'p) data can contribute significantly to this difficult question, however, given the word limit of this paper, 
+this section was removed in the introductory paragraph.
 
@@
 ----------
-I have added the missing momentum distributions as well as the kinematic distributions for Q2, xB, w and Pp 
-for each of the central settings (80, 580 and 750 MeV/c).  See Supplemental Material.
+The missing momentum distributions as well as the kinematic distributions for Q2, xB, w and Pp 
+for each of the central settings (80, 580 and 750 MeV/c) have been added to the Supplemental Material.
 
@@
 ----------
-Yes, at least 3/4 planes. I have clarified this in the manuscript.
+Yes, at least 3/4 planes. This has been clarified this in the manuscript.
 
@@
 
-An additional study on the spectrometers acceptance systematic error was carried out by M.K. Jones where systematic error of ~1.4 % was determined
-and added quadratically to the final resut.
+An additional study on the spectrometers acceptance systematic error was carried out by M.K. Jones where a systematic error of ~1.4 % was determined
+and added quadratically to the final result.
 
@@
 To clarify, a weighted average of the reduced cross sections were taken for overlapping regions in pr. See example
-of overlapping pr bins in Fig. 14 of Supplemental Materials.
+of overlapping pr bins in Fig. 9 of Supplemental Materials.
 
@@
 ----------
-I did not find this typo in the manuscript.
+This typo was not found in the manuscript.
 
@@
 
-As was mentioned before, the theoretical interpretation of these results is
+As was mentioned before, the complete theoretical interpretation of these results is
 out of the scope of this paper and is currently being investigated by the theory
-groups we are collaborating with. Our goal was to simply present these new and
-interesting results.
+groups we are collaborating with. Our goal was to present these new and
+interesting results and make them accessible to the general public.

### 2020-10-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/arXiv_PRLsubmission_v2/supplemental.tex
created version 2 of arXiv PRL submittal package

--- 2020-10-21 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.33]{Em_and_Q2_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
 \label{fig:Em_Q2_cuts}
-\includegraphics[scale=0.24]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
+\includegraphics[scale=0.33]{deltaAcc_and_ZtarCUT_80MeV_35deg.png}
 \caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
@@
 to select events only at the highest possible momentum transfers to further suppress MEC and IC. \\
-\indent Figure \ref{fig:delta_Ztar_cuts} (left) shows a momentum acceptance ($\delta$) cut made on the HMS in the range $8\%\leq\delta\leq8\%$, where the optics reconstruction
+\indent Figure \ref{fig:delta_Ztar_cuts} (left) shows a momentum acceptance ($\delta$) cut made on the HMS in the range $-8\%\leq\delta\leq8\%$, where the optics reconstruction
 is reliable and well understood from previous experiments in the 6 GeV era. The inset shows the SHMS momentum acceptance which was constrained by that of the HMS to be
-$|\delta|\lesssim$3$\%$ which is well within the reliable SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$. Figure \ref{fig:delta_Ztar_cuts} (right) shows reaction vertex cut
+$|\delta|\lesssim$3$\%$ which is well within the reliable SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$. \\
+\indent Figure \ref{fig:delta_Ztar_cuts} (right) shows a reaction vertex cut
 on the difference between the HMS and SHMS reconstructed reaction vertices along the $z$-coordinate (target length). The cut is made at $\pm2$ cm relative to the histogram peak.
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.23]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\includegraphics[scale=0.23]{coin_and_eCal_CUT_80MeV_35deg.png}
 \caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
@@
 at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 4 ns beam bunch structure due to accidental
-coincidences is not observed. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
+coincidences is not observed. \\
+\indent Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
 deposited normalized by the particle track momentum. This cut was used to separate electrons from background (pions), however, the spectrum shows a very clean distribution
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
+\includegraphics[scale=0.24]{collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
-  projected at the SHMS collimator.}
+  projected at the SHMS collimator. The $z$-axis (color palette) is in arbitrary units.}
 \label{fig:data_coll_cuts}
@@
 that all events that enter the spectrometer pass through the collimator, and not re-scatter at the edges. This cut is needed since protons that enter the
-HMS can punch through the collimator with a probability that is related to the proton-Tungsten total cross section. Figure \ref{fig:data_coll_cuts} (right)
+HMS can punch through the collimator with a probability that is related to the proton-Tungsten total cross section.\\
+\indent Figure \ref{fig:data_coll_cuts} (right)
 shows the correlated events projected at the SHMS collimator which clearly shows that the events are well within the collimator which indicates that the SHMS
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
-\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}
+\includegraphics[scale=0.25]{collimator_CUT_80MeV_35deg_SIMC.png}
+\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.  The $z$-axis (color palette) is in arbitrary units.}
 \label{fig:simc_coll_cuts}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.17]{plots/d2_kin_thnq35.png}
+\includegraphics[scale=0.17]{d2_kin_thnq35.png}
 \caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c setting at $\theta_{nq}=35^{\circ}$.}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.17]{plots/d2_kin_thnq45.png}
+\includegraphics[scale=0.17]{d2_kin_thnq45.png}
 \caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.33]{plots/tgt_bkg_d2_pm580_allthnq.png}
+\includegraphics[scale=0.33]{tgt_bkg_d2_pm580_allthnq.png}
 \caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
-  a 40 MeV range, each. (right) The SHMS $z$-reaction vertex corresponding to the specified region in the missing energy spectrum. Inset (left): Missing energy spectrum on a logarithmic
-  scale.}
+  a 60 MeV range, each.  Inset (left): Missing energy spectrum on a logarithmic scale. (right) The SHMS $z$-reaction vertex corresponding to
+  the specified region in the missing energy spectrum.}
 \label{fig:tgt_wall}
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{plots/Pr_and_Ps.png}
+\includegraphics[scale=0.3]{Pr_and_Ps.png}
 \caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.27]{plots/RC_factor.png}
+\includegraphics[scale=0.27]{RC_factor.png}
 \caption{Radiative correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). }
@@
 \begin{figure}[!ht]
-\includegraphics[scale=0.27]{plots/BC_factor.png}
+\includegraphics[scale=0.27]{BC_factor.png}
 \caption{Bin centering correction factor versus neutron recoil momenta, $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right).
@@
 \section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }
-%\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
-%To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
-%enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
-%\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
-%statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
-%where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
-%\begin{subequations}
-%  \begin{align}
-%    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
-%    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
-%  \end{align}
-%\end{subequations}
-%where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
-%error accounts for the possible correlation between the two measurements. By taking the ratio
-%\begin{equation}
-%  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
-%\end{equation}
-%a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
-%ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
-%the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error.
-For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
-%\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
-%In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
-%the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
-%studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible.
-Similar plots for the other event selection
-%cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
-%\clearpage
-%\begin{figure}[!ht]
-%\includegraphics[scale=0.4]{plots/Em_syst.png}
-%\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
-%  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
-%\label{fig:Em_sys}
-%\end{figure}
-\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref.\cite{cyero_phdthesis})
+\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref. \cite{cyero_phdthesis})
 using the Barlow ratio approach \cite{barlow2002systematic,barlow2017}. In this case, the ratio was calculated from the difference between the experimental cross
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.37]{plots/rad_sys.png}
+\includegraphics[scale=0.37]{rad_sys.png}
 \caption{Systematic effects of the radiative corrections model dependency on the data cross sections
@@
 \begin{figure}[!ht]
-\includegraphics[scale=0.37]{plots/bc_sys.png}
+\includegraphics[scale=0.37]{bc_sys.png}
 \caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering correction systematics.}
@@
 effect in the measured cross sections and thus no systematic uncertainties due to software cuts were included in the final result.
-For a detailed discussion of these studies see Section 5.10 of Ref.\cite{cyero_phdthesis}.
+For a detailed discussion of these studies see Section 5.10 of Ref.
+\cite{cyero_phdthesis}.
 \\\\

### 2020-10-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp.tex
created version 2 of arXiv PRL submittal package

@@
 \begin{figure}[!h]
-\includegraphics[scale=0.33]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
-\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeter normalized by the particle track momentum (right).}
+\includegraphics[scale=0.23]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
+\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}
 \label{fig:coin_ecal_cuts}
@@
 \indent Figure \ref{fig:coin_ecal_cuts} (left) shows a coincidence time cut on the $ep$ coincidence time spectrum formed by requiring a logic signal of
-at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 2 ns beam bunch structure due to accidental
-coincidences is not observed. The out-of-time events observed at the tails can originate from the radiation in the Hall partially entering the detector huts and forming
-a trigger in coincidence with the other arm. Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
+at least 3 out of 4 scintillator planes between both spectrometers. The spectrum is very clean as the typical 4 ns beam bunch structure due to accidental
+coincidences is not observed. \\
+\indent Figure \ref{fig:coin_ecal_cuts} (right) shows a particle identification cut on the SHMS calorimeter total energy
 deposited normalized by the particle track momentum. This cut was used to separate electrons from background (pions), however, the spectrum shows a very clean distribution
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}
+\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_data.png}
 \caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
@@
 \caption{(left) Missing energy spectrum for the deuteron 580 MeV/c setting with event selection region corresponding to Aluminum endcaps (in red) and deuteron missing energy peak over
-  a 40 MeV range, each.  Inset (left): Missing energy spectrum on a logarithmic scale. (right) The SHMS $z$-reaction vertex corresponding to
+  a 60 MeV range, each.  Inset (left): Missing energy spectrum on a logarithmic scale. (right) The SHMS $z$-reaction vertex corresponding to
   the specified region in the missing energy spectrum.}

### 2020-10-23 PRL_UTILITIES_CODES/prl_wordcount/ms_withcites.tex
updated

--- 2020-10-18 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
@@
 In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions
-have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.
+have been compared to the high momentum part of theoretical deuteron momentum distributions.
 Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
@@
 bound nucleon with the same momentum is being measured.\\
-%===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
-%At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
-%nucleons begin to overlap.
-The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
-%Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-%having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
-As of the present time, there are only a few nuclear physics experiments for
-%which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-%However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
-\indent The most direct way to study the short range structure of the deuteron wave function %(or equivalently, its high momentum component)
+\indent The most direct way to study the short range structure of the deuteron wave function 
 is via the exclusive deuteron electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA),
@@
 by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively.
-The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets.\\ %(hydrogen and deuterium).\\
+The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets.\\
 \indent Both Hall C spectrometers have similar standard detector packages \cite{cyero_phdthesis}, each with four scintillator planes used for triggering, a pair of drift chambers used for tracking, and a calorimeter and gas \u{C}erenkov used for electron identification.
@@
 momentum calibration and the determination of the spectrometer offsets and kinematic uncertainties \cite{cyero_phdthesis}.\\
-%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
-%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
-%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
-%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\
 \indent Identical event selection criteria were used for the hydrogen and deuteron data.
@@
 and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
-the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
-to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\
+the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), total charge ($2.0\%$), target wall contributions ($\leq2.9\%$) and spectrometer acceptance ($1.4\%$),  which were the same for every setting,
+to define the overall normalization uncertainty ($\leq5.3\%$).\\
 \indent The systematic uncertainties due to the systematic error on the absolute beam energy and spectrometer angle/momentum settings were
@@
 For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
-The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
+The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 5.3$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\
 \begin{figure*}[t]
@@
 \noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
-($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
+($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ 
 is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the
@@
 The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square).
-%The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$ gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.
 The data are compared to theoretical calculations using wave functions determined from the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} $NN$ potentials.
@@
 The calculations use different FF parametrizations which can lead to a $\sim$5.8 -6.6$\%$ variation of the theortical cross section.\\
-%----REMOVED ON 10/14/2020----------
-%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
-%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
-%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
-%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
-%difference of $\sim5.8-6.6 \%$ was found between the respective
-%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\
 \indent The difference between the deuteron wave functions with CD-Bonn, Paris, AV18 and WJC2 potentials is 
@@
 %---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
-%\nocite{COSY}
+
+\end{document}
 \nocite{barlow2002systematic}
@@
 
-\end{document}
 \bibliography{ms}

### 2020-10-23 PRL_UTILITIES_CODES/codes/PRL_plots_codes/make_prl_plots_smallplots.py

@@ -273,7 +273,7 @@ def make_prl_plots(plot2_inset=0):
     #= SUBPLOTS SIZE / SPACING / LEGEND =
     #====================================
 
-    leg_font_size = 9
+    leg_font_size = 9.2
     #Remove spacing between subplots
     plt.subplots_adjust(wspace = 0.0000000001, bottom=0.16, top=0.97, left=0.085, right=0.98) #, hspace = 0.001, wspace = 0.001)
     line_labels=['This Experiment (Hall C)', 'Hall A Data', 'JML Paris PWIA', 'JML Paris FSI', 'MS AV18 PWBA', 'MS AV18 FSI', 'MS CD-Bonn PWBA', 'MS CD-Bonn FSI', 'JVO WJC2 PWBA', 'JVO WJC2 FSI']
@@ -281,7 +281,7 @@ def make_prl_plots(plot2_inset=0):
 
 
     #B.pl.show()
-    B.pl.savefig('./PRL_plot1.pdf')
+    B.pl.savefig('./PRL_plot1.pdf', format='pdf')
 
 
 
@@ -501,7 +501,7 @@ def make_prl_plots(plot2_inset=0):
     B.pl.legend(loc='upper right', fontsize=7.5, frameon=False)
 
     #B.pl.show()
-    B.pl.savefig('./PRL_plot2.pdf')
+    B.pl.savefig('./PRL_plot2.pdf', format='pdf')
     
 
 

### 2020-10-29 HALLC_ANALYSIS_GENERAL_NOTES/analysis_notes.tex
updated Hall C analysis procedure by adding a new section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to writeLaTeX --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you give 
% someone the link to this page, they can edit at the same
% time. See the help menu above for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------

\documentclass[14pt]{article}

\usepackage[margin=0.5in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage{hyperref}
\usepackage{color,soul}
\usepackage{caption}
\usepackage{courier}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor} % for setting colors
\usepackage[bookmarksnumbered=true, citebordercolor={1 0 0}]{hyperref} 
\usepackage[title]{appendix}
\hypersetup{colorlinks=true, linkcolor=blue,urlcolor=blue}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}

\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
\newenvironment{courier}{\ttfamily}{\par}

% set the default code style
\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{orange}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red} % string color
}

\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------

\title{\textbf{General Hall C Analysis Procedure in 12 GeV Era}}%replace X with the appropriate number
\author{Carlos Yero \\ email \href{mailto:cyero002@fiu.edu}{cyero002@fiu.edu}} %if necessary, replace with your course title

\maketitle
\noindent The general Hall C analysis procedure for experiments in the 12 GeV era is discussed. The procedure
outlines the first necessary steps in the data analysis regardless of the nature of the experiment. These include, but are not
limited to: \\ \textit{1. reference time cuts}, \textit{2. detector time window cuts}, \textit{3. detector calibrations}.
Additional necessary procedures will be added in subsequent sections as updates to this document are made.

\section{Set Reference Time Cuts}\label{sec:ref_time_cuts}
\noindent The first step in Hall C Data Analysis is to make sure the \textit{reference time}  cuts are set properly,
as one needs to make sure the reference times correlated with the trigger are selected. The \textit{reference time}
is a copy of the pre-trigger which is distributed to all ADCs/TDCs in all detectors Read-Out Crontrollers (ROCs)\footnote{Refer to \url{https://hallcweb.jlab.org/DocDB/0010/001028/002/trigger_v2.pdf} for a detailed discussion on the Hall C trigger}. When the pre-trigger
is accepted, all crates read-out detector signals associated with the trigger, including the reference time itself (copy of pre-trigger). The
reference time is subtracted from the detector signal later on during the analysis replay. When using the reference time,
the Hall C analyzer, \textit{hcana}, choses the first hit in the time window if multiple hits are present per event. In this scenario, the first hit may NOT
necessarily be the \textit{good hit}, and the wrong reference time would be chosen resulting in the wrong time being subtracted in the ADC/TDC spectra.
By placing a reference time cut, the analyzer then considers the first hit after the cut, which is likely to be a \textit{good hit}. \\
\indent As an example, consider the H(e,e')p Elastic coincidence run 3377 which had the highest SHMS rate of elastics taken during the E12-10-003 experiment.

\begin{figure}[H]
  \centering
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.3]{plots/pDCREF_Prob.png}
  \caption{SHMS Reference Time Spectrum for Coincidence Run 3377 of E12-10-003 experiment.}
  \label{fig:pDCref_time_prob}
\end{figure}
Following the poissonian behavior of physics triggers, the probability that 2 hits (\textit{background} and \textit{good hit}) fall within a certain
time window $\Delta T$ at a given physics rate $R$ is given by:
\begin{equation}
  P(\lambda; k) = e^{-\lambda}\frac{\lambda^{k}}{k!}, \text{ where $\lambda=R \Delta T$ and $k=\# \text{ hits}$}
  \label{eq:1}
\end{equation}
From the multiplicity in Figure \ref{fig:pDCref_time_prob}, the reference time had 3 good hits (3/4, EL-REAL, EL-CLEAN, \textcolor{red}{read further}).
For simplicity of the calculation, \textbf{redefine 3 good hits as a single good hit}. Then, from Eq. \ref{eq:1} and Figure \ref{fig:pDCref_time_prob},
the probability of finding 2 hits within the Drift Chamber Time Window is
\begin{align}
  P(\lambda;k) = e^{-R\Delta T}\frac{(R\Delta T)^{2}}{2!} = 0.1865
\end{align}
From Figure \ref{fig:pDCref_time_prob}, this probability is given by taking the ratio of the \textcolor{blue}{background} to the total number of events and divding by
3 to normalize to a single good hit, one obtains
\begin{align}
  P_{data} = \frac{1}{3}\frac{346600}{602000} = 0.1919
\end{align}
The two results agree to $\leq 1\% $. These results indicate that if the reference time had \textbf{NOT} been set for this run, then $\sim 19\%$ of the
events would have the \textbf{WRONG} reference time and a lower tracking efficiency by $\sim 19\%$, hence, \\ \textbf{\textcolor{red}{THE IMPORTANCE OF SETTING THE REFERENCE TIMES!}}
\\ \\
\indent In Hall C, each spectrometer has multiple pre-triggers (3/4, STOF, EL-REAL, EL-CLEAN) which may change depending on the nature of the experiment.
The base pre-trigger is the 3/4, which requires at least 3 of 4 hodoscope planes to fire. During the commissioning phase of the spectrometers, the
reference times was initially defined to be:
\begin{align}
 \text{ref. time} \equiv 3/4 \textit{ \textbf{OR} } \text{STOF} \textit{ \textbf{OR} } \text{EL-REAL} \textit{ \textbf{OR} } \text{EL-CLEAN}
\end{align}
See December 2017 HC-Log Entry \url{https://logbooks.jlab.org/entry/3501198}.  On January 2018, the STOF trigger was removed from this definition,
See HC-Log Entry \url{https://logbooks.jlab.org/entry/3519686}. Finally, on August 2018, EL-CLEAN was removed from the reference time definition, See
HC-Log Entry \url{https://logbooks.jlab.org/entry/3585301}. It was determined that any pre-trigger that require the 3/4 was un-necessary and redundant
to have in the reference time definition, and so they were removed. As of the present day, the reference time definition in Hall C is:
\begin{align}
 \text{ref. time} \equiv 3/4 \textit{ \textbf{OR} } \text{EL-REAL} 
\end{align}
The list of reference time variables is summarized in Tables \ref{tab:Table 1} and \ref{tab:Table 2}.
\begin{table}[h!]
\begin{tabular}{l l l}
Ref. Time Name               & Physical Location & \textit{hcana} Leaf Name  \\
\hline
hFADC\_TREF\_ROC1 & ROC1::SLOT18::Ch11 & \texttt{T.\{spec\}.hFADC\_TREF\_ROC1\_adcPulseTimeRaw}    \\
hTref1            & ROC1::SLOT02::Ch06 & \texttt{T.\{spec\}.hT1\_tdcTimeRaw} \\
hTref2            & ROC1::SLOT20::Ch127 & \texttt{T.\{spec\}.hT2\_tdcTimeRaw} \\
hDCREF1           & ROC3::SLOT08::Ch15 & \texttt{T.\{spec\}.hDCREF1\_tdcTimeRaw} \\
hDCREF2           & ROC3::SLOT16::Ch63 & \texttt{T.\{spec\}.hDCREF2\_tdcTimeRaw} \\
hDCREF3           & ROC3::SLOT04::Ch111 & \texttt{T.\{spec\}.hDCREF3\_tdcTimeRaw} \\
hDCREF4           & ROC3::SLOT13::Ch95 & \texttt{T.\{spec\}.hDCREF4\_tdcTimeRaw} \\
hDCREF5\footnotemark[3]          & ROC3::SLOT02::Ch127 & \texttt{T.\{spec\}.hDCREF5\_tdcTimeRaw} \\

\end{tabular}
\caption{List of HMS Reference Times. Single-Arm DAQ, \textbf{spec=hms}, else if Coincidence Mode DAQ, \textbf{spec=coin}.}
\label{tab:Table 1}
\end{table}
\footnotetext[3]{hDCREF5 reference time signal was added on July 2018. Experiments after this date must also check this reference time.}

\begin{table}[h!]
\begin{tabular}{l l l}
Ref. Time Name               & Physical Location & \textit{hcana} Leaf Name  \\
\hline
pFADC\_TREF\_ROC2 & ROC2::SLOT14::Ch11 & \texttt{T.\{spec\}.pFADC\_TREF\_ROC2\_adcPulseTimeRaw}    \\
pTref1            & ROC2::SLOT20::Ch15 & \texttt{T.\{spec\}.pT1\_tdcTimeRaw} \\
pTref2            & ROC2::SLOT19::Ch31 & \texttt{T.\{spec\}.pT2\_tdcTimeRaw} \\
pDCREF1           & ROC6::SLOT06::Ch79 & \texttt{T.\{spec\}.pDCREF1\_tdcTimeRaw} \\
pDCREF2           & ROC6::SLOT07::Ch79 & \texttt{T.\{spec\}.pDCREF2\_tdcTimeRaw} \\
pDCREF3           & ROC6::SLOT08::Ch79 & \texttt{T.\{spec\}.pDCREF3\_tdcTimeRaw} \\
pDCREF4           & ROC6::SLOT09::Ch79 & \texttt{T.\{spec\}.pDCREF4\_tdcTimeRaw} \\
pDCREF5           & ROC6::SLOT10::Ch79 & \texttt{T.\{spec\}.pDCREF5\_tdcTimeRaw} \\
pDCREF6           & ROC6::SLOT11::Ch47 & \texttt{T.\{spec\}.pDCREF6\_tdcTimeRaw} \\
pDCREF7           & ROC6::SLOT12::Ch47 & \texttt{T.\{spec\}.pDCREF7\_tdcTimeRaw} \\
pDCREF8           & ROC6::SLOT13::Ch47 & \texttt{T.\{spec\}.pDCREF8\_tdcTimeRaw} \\
pDCREF9           & ROC6::SLOT14::Ch15 & \texttt{T.\{spec\}.pDCREF9\_tdcTimeRaw} \\
pDCREF10          & ROC6::SLOT15::Ch47 & \texttt{T.\{spec\}.pDCREF10\_tdcTimeRaw} \\

\end{tabular}
\caption{List of SHMS Reference Times. Single-Arm DAQ, \textbf{spec=shms}, else if Coincidence Mode DAQ, \textbf{spec=coin}.}
\label{tab:Table 2}
\end{table}

\newpage

Associated with each physical detector and pseudo-detector \texttt{(TRIG)}, are specific reference times from the Tables \ref{tab:Table 1} and \ref{tab:Table 2}.
The reference times associated with each detector are summarized below.

\begin{table}[h!]
\begin{tabular}{l l l}
SPEC  & DETEC & Ref. Time Name  \\
\hline
HMS & AERO[adc] & hFADC\_TREF\_ROC1 \\
& CAL[adc] & hFADC\_TREF\_ROC1 \\
& CER[adc] & hFADC\_TREF\_ROC1 \\
& DC[tdc] & hDCREF1, hDCREF5 \\
& HODO[adc] & hFADC\_TREF\_ROC1 \\
& HODO[tdc] & hTref2 \\
& TRIG[adc] &  hFADC\_TREF\_ROC1 \\
& TRIG[tdc] & hTref1 \\
\\
SHMS & AERO[adc] & pFADC\_TREF\_ROC2 \\
& CAL[adc] & pFADC\_TREF\_ROC2 \\
& HGCER[adc] & pFADC\_TREF\_ROC2 \\
& NGCER[adc] & pFADC\_TREF\_ROC2 \\
& DC[tdc] & pDCREF 1-10 \\
& HODO[adc] & pFADC\_TREF\_ROC2 \\
& HODO[tdc] & pTref1, pTRef2 \\
& TRIG[adc] & pFADC\_TREF\_ROC2 \\
& TRIG[tdc] & pTref2 \\
\end{tabular}
\caption{List of Detector Reference Times, which applies for both Singles and Coin DAQ modes. The table shows which reference times are being subtracted from each
detector or pseudo-detector signal.}
\label{tab:Table 3}
\end{table}
\noindent From the summary Table \ref{tab:Table 3} above, it is important to note that the all detectors in HMS / SHMS use the same ADC reference time signal in their respective spectrometers (indicating all ROCs FADCs appear to be synchronized),
however, with respect to the TDCs, each TDC receives a distinct copy of the reference times with the exception of the Drift Chambers in ROC3, as this crate has the capability to synchronize all TDCs it holds. \\
\\
\noindent To determine what values to set the reference time cuts, it is recommended that a multiplicity cut be made on the variable being looked at. The
multiplicity of a given variable refers to the total number of adc or tdc hits per event. If the event was a true physics event, most likely the
total number of reference time hits will be one. If the reference time was OR'ed from \textit{n} pre-triggers, and the pre-triggers are assumed to be
almost 100\% efficient, then a true physics event will most likely have \textit{n} hits. In this case, it is recommended that a multiplicity cut requiring
\textit{n} hits be made in order to clean the reference time spectrum and better select a reference time cut value. It is easier to look a the multiplicity
leaf variable itself, and determine which multiplicity cut to make.
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.5]{plots/shms_ref_times.pdf}
  \caption{SHMS Reference Time Cuts for Coincidence Run 3289 of E12-10-003 experiment. The conversion from TDC Channel to time is $\sim$ 0.1 ns/Ch. The conversion from ADC Channel to time is 0.0625 ns/Ch. }
  \label{fig:shms_ref_times}
\end{figure}
Figure \ref{fig:shms_ref_times} shows the reference times used in the analysis. The
multiplicity cut reduces the background, although not completely so a judgement of where to place the cut has to be made. The shapes of the reference times may change
depending on the experiment trigger used. To the left of the cut, are the reference times from various sources of background. 
Once the reference time cut has been determined, the corresponding parameter files must be updated with the cut values. The parameter files to be modified are
located at: 
\begin{flushleft}
  \texttt{hallc\_replay/PARAM/HMS/GEN/h\_reftime\_cut.param} \\
  \texttt{hallc\_replay/PARAM/SHMS/GEN/p\_reftime\_cut.param} \\
  \texttt{hallc\_replay/PARAM/TRIG/t[daq\_mode].param\footnote{If the experiment uses the DAQ in single arm mode (separate HMS/SHMS CODA GUI), the \texttt{TRIG} parameter file
    modified must be \texttt{thms.param} or \texttt{tshms.param}},  [daq\_mode]=hms, shms, coin} 
\end{flushleft}
and the parameter files look as follows:
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
\begin{center}
  \includegraphics[scale=0.5]{plots/reftime_parm.png}
\end{center}
\caption{HMS (top), SHMS (middle), COIN TRIG[bottom] reference time parameter files. The set cut values have a negative sign as opposed to the histograms in Figure \ref{fig:shms_ref_times}.
  The ADC ref. time is common to the Calorimeter, Cherenkovs and Hodoscopes.}
  \label{fig:reftime_parm}
\end{figure}
\noindent Once the reference time parameter file has been updated, the the data must be replayed so that the correct reference time is selected before moving to the
next step in the analysis procedure. In principle, the reference time should be relatively stable, but it is worth checking for different kinematics as well as different
trigger configurations. It is recommended that for each kinematic setting a single (or combined) run with enough statistics ($\sim$ 1 M events) is selected to set (or check) the
reference time cuts.
\section{\textbf{Set Detector Time Window Cuts}}
The next step in the analysis procedure is setting up the detector time window cuts. These are necessary to reduce sources of background that slips into the detector
time windows when detecting the physics signals of interest. The time window cut is made on a time difference between the ADC and TDC times on a PMT basis  for all the detectors
except the Drift Chamber, which cut on the raw drift times for each plane.  The time difference is defined in \textit{hcana} as
\begin{align}
  &\texttt{AdcTdcDiffTime} = \texttt{TdcTime[ipmt] - AdcPulseTime[ipmt]} \text{ HODO} \\
  &\texttt{AdcTdcDiffTime} = \texttt{HodoStartTime - AdcPulseTime[ipmt]} \text{ CER, HGCER, NGCER, CAL, AERO}
\end{align}
where the \texttt{HodoStartTime} is the Hodoscope time projected at the focal plane, and the \texttt{TdcTime, AdcPulseTime} is the detector (TDC,ADC) pulse time for a given PMT in that detector.
If the event is truly a physics event originating from the target, then in principle, the time difference should be a $\delta$-function, however due to the finite
detector resolutions, it has a finite width and gaussian in shape. Events that are far away from the main peak are clearly out-of-time indicating that the ADC pulse time and
TDC Time are NOT correlated with the same event, and a time window cut must be made. With respect to the Drift Chambers, a cut on the raw drift time spectrum to reduce the background
from multiple hits. Similarly to the reference time cuts, the detector time window cuts are set via a parameter cut file associated with the detector.
The detector variable names used as well as the parameter files used to set the cuts are summarized below.
\begin{table}[h!]
  \small
\begin{tabular}{l l l}
\textbf{Detector} & \textit{hcana} \textbf{Leaf Name} & \textbf{Place-Holders} \\
\hline
Hodoscopoes &  \texttt{H.hod.[pl].Good[side]AdcTdcDiffTime[ipmt]} & \texttt{[pl]:1x|1y|2x|2y [side]:Pos|Neg} \\
& \texttt{H.hod.[pl].Good[side]AdcMult[ipmt]} & \\ \\
Calorimeter &  \texttt{H.cal.[pl].good[side]AdcTdcDiffTime[ipmt]} & \texttt{[pl]:1pr|2ta|3ta|4ta [side]:Pos|Neg} \\
& \texttt{H.cal.[pl].good[side]AdcMult[ipmt]} & \\ \\
Cherenkov   &  \texttt{H.cer.goodAdcTdcDiffTime[ipmt]} & \\
& \texttt{H.cer.goodAdcMult[ipmt]} & \\ \\
Drift Chamber & \texttt{H.dc.[pl].rawtdc} & \texttt{[pl]:1u1|1u2|...2x2|2v1|...} \\
& \texttt{H.dc.[pl].nhit} &
\end{tabular}
\caption{HMS detectors variable names are summarized. The \texttt{[impt]} index emphasizes the leaf variables are arrays whose indices are the PMTs, but do NOT
form part of the leaf name. }
\label{tab:Table 4}
\end{table}
\begin{table}[h!]
  \small
\begin{tabular}{l l l}
\textbf{Detector} & \textit{hcana} \textbf{Leaf Name} & \textbf{Place-Holders} \\
\hline
Hodoscopoes &  \texttt{P.hod.[pl].Good[side]AdcTdcDiffTime[ipmt]} & \texttt{[pl]:1x|1y|2x|2y [side]:Pos|Neg} \\
& \texttt{P.hod.[pl].Good[side]AdcMult[ipmt]} & \\ \\
Pre-Shower & \texttt{P.cal.pr.good[side]AdcTdcDiffTime} & \texttt{[side]:Pos|Neg} \\
& \texttt{P.cal.pr.good[side]AdcMult[ipmt]} & \\ \\
Calorimeter &  \texttt{P.cal.fly.goodAdcTdcDiffTime[ipmt]} &  \\
& \texttt{P.cal.fly.goodAdcMult[ipmt]} & \\ \\
Cherenkov   &  \texttt{P.[det].goodAdcTdcDiffTime[ipmt]} & \texttt{[det]:hgcer|ngcer} \\
& \texttt{P.[det].goodAdcMult[ipmt]} & \\ \\
Drift Chamber & \texttt{P.dc.[pl].rawtdc} & \texttt{[pl]:1u1|1u2|...2x2|2v1|...} \\
& \texttt{P.dc.[pl].nhit} & 
\end{tabular}
\caption{SHMS detectors variable names are summarized. The \texttt{[impt]} index emphasizes the leaf variables are arrays whose indices are the PMTs, but do NOT
form part of the leaf name. }
\label{tab:Table 5}
\end{table} 
\begin{table}[h!]
\begin{tabular}{l l l}
\textbf{Detector} & \textit{hcana} \textbf{Leaf Name} & \textbf{Place-Holders} \\
\hline
TRIG & \texttt{T.[spec].*} & \texttt{[spec]: hms | shms | coin} \\
\end{tabular}
\caption{Trigger detector variable names are summarized. The \texttt{[spec]} refers to the DAQ mode. If single-arm mode or coincidence mode. NOTE: singles in
coincidence mode DAQ is considered \texttt{coin}.}
\label{tab: Table 6}
\end{table} 
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.3]{plots/tcoin_parm.png}
  \caption{\texttt{TRIG} Detector parameter file for coincidence mode DAQ. The \textcolor{red}{rectangles} highlight a variable of interest (hT2), and the Min/Max
  Time Window Cut for that variable, indexed at 17.}
  \label{fig:tcoin_parm}
\end{figure}
\noindent Setting the \texttt{TRIG} pseudo-detector Time Window cuts is \textbf{NOT} as obvious as a normal detector. First, the variables from the \texttt{TRIG} that
will be used in the analysis need to be determined. Then, the index corresponding to the variables of interest need to be determined from the \texttt{TRIG} parameter file.
Finally, once the Time Window cut values have been determined, they need to be updated in the parameter file. See Figure \ref{fig:tcoin_parm} for reference.
\\

\indent Similarly to the reference time histograms, it might be useful to put a multiplicity cut on the detector time variables in Tables \ref{tab:Table 4}, \ref{tab:Table 5} and
\ref{tab: Table 6}. An important point to make is the variables with \texttt{nhit} in their name. This represents the maximum number of hits per event, and so when filling
the raw tdc time in the Drift Chambers, this histogram must be filled by looping over all possible \texttt{nhit} hits per event entry. Some examples of the detector time
difference and raw time histograms are shown below.
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.95]{plots/pHodo_1xGoodNeg.pdf}
  \caption{SHMS Hodoscope 1X Neg Time Difference. Coincidence Run 3289 of E12-10-003 experiment.}
  \label{fig:shms_hodo_difftime}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.95]{plots/pCal_Row9.pdf}
  \caption{SHMS Calorimeter Row9 Channels Time Difference. Coincidence Run 3289 of E12-10-003 experiment.}
  \label{fig:shms_cal_difftime}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.95]{plots/pDC_rawTDC_window.pdf}
  \caption{SHMS Drift Cambers Raw TDC Time. Coincidence Run 3289 of E12-10-003 experiment.}
  \label{fig:shms_dc_rawtime}
\end{figure}
\begin{figure}[H]
  \begin{center}
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/pNGCER_timeWindow.pdf}
  \caption{SHMS Noble Gas Cherenkov Time Difference. Coincidence Run 3289 of E12-10-003 experiment.}
  \label{fig:shms_ngcer_difftime}
  \end{center}
\end{figure}

\noindent From the plots shown above, the \textcolor{red}{red histograms}, have a multplicity cut, and the \textcolor{blue}{blue histograms} have no multiplicity cut. A main
peak is clearly distiguishable in all plots. 
Once the detector time window cuts have been determined, they are set in the detector cuts parameter files located at:
\begin{flushleft}
  \texttt{hallc\_replay/PARAM/HMS/\{DETEC\}/h\{detec\}\_cuts.param} \\
  \texttt{hallc\_replay/PARAM/SHMS/\{DETEC\}/p\{detec\}\_cuts.param} \\
  \texttt{hallc\_replay/PARAM/TRIG/t\{spec\}.param} 
\end{flushleft}
where \texttt{DETEC(HMS): CAL, CER, DC, HODO, AERO}, \texttt{DETEC(SHMS): CAL, HGCER, NGCER, DC, HODO, AERO}, and
\texttt{spec: hms, shms, coin}.
For the aerogel, no examples were shown, but in principle, in terms of setting the time window cuts should be similar procedure.
For examples of how the parameter file to be modified looks like for all the detectors, see Appendix \ref{appendix:AppxA}.
\section{Detector Calibrations}
After selecting the right reference times and setting proper detector time window cuts, detector calibrations can be started. Ideally, one would
use specific runs for calibrations in which most of the focal plane is illuminated. Sometimes, a magnet de-focused run is used, however, one has to be
careful as some calibrations actually depend on the reconstructed quantities at the target (Calorimeter), and hence knowledge of the reconstruction
spectrometer optics. In this case, it is recommended to use single-arm runs over coincidence runs, as the latter will be more constrained. In this section,
I will point to more detailed documentation on the Hall C Document Database (DocDB), as well as the document with the instructions to run the calibration.

\subsection{Hodoscopes}
The hodoscopoes Calibration code and README files with the instructions on how to do the calibration is found on:
\begin{center}
  \url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/hms_hodo_calib} \\
   \url{ https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/shms_hodo_calib}
\end{center}

Additional documentation on the Hodoscope calibration can be found on the Hall C Document DataBase:
\begin{center}
  \url{https://hallcweb.jlab.org/DocDB/0009/000970/001/hodo_calib.pdf}
\end{center}

\subsection{Drift Chambers}
The Drift Chambers Calibration code and README files with the instructions on how to do the calibration is found on:
\begin{center}
\url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/dc_calib/scripts}  
\end{center}

Additional documentation on the Drift Chamber calibration can be found on the Hall C Document DataBase:
\begin{center}
  \url{https://hallcweb.jlab.org/DocDB/0008/000863/003/HallC-Software-Workshop_pdf.pdf}\\
  \url{https://hallcweb.jlab.org/DocDB/0008/000842/003/report.pdf}
\end{center}
\subsection{Calorimeters}
The Calorimeter Calibration code and README (howto.txt) files with the instructions on how to do the calibration is found on:
\begin{center}
  \url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/hms_cal_calib} \\
  \url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/shms_cal_calib}
\end{center}

Additional documentation on the Calorimeter can be found on the Hall C Document DataBase:
\begin{center}
\url{https://hallcweb.jlab.org/DocDB/0008/000809/001/NIMarticleOverview.pdf}
\end{center}
\subsection{Cherenkovs}
The Cherenkovs Calibration code and README files with instructions on how to do the calibration is found on:
\begin{center}
  \url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/hms_cer_calib} \\
  \url{https://github.com/JeffersonLab/hallc_replay/tree/master/CALIBRATION/shms_hgcer_calib}
\end{center}
Additional documentation on the Cherenkovs can be found on the Hall C Document DataBase:
\begin{center}
\url{https://hallcweb.jlab.org/DocDB/0008/000893/001/HGC_Calibration.pdf}
\end{center}
\section{Summary of Analysis Procedure}
\textbf{STEP 1:} Set the reference time cut parameters, as they are needed to select the correct pre-trigger correlated with each event (see Section \ref{sec:ref_time_cuts}).
\begin{itemize}
\item You can select a representative run for each kinematic setting of the experiment to check and set the reference time cut parameters. Check if the reference time histograms per
  kinematic setting shift significantly, in which case, you may need to set the reference time parameters per setting.  
\item After the reference time parameters have been set, make sure to replay the data before moving on to the next step (detector time windows) to ensure
  that the correct reference times (determined by the reference time parameter file in step 1) are selected per event. 
\end{itemize}
\textbf{STEP 2:} Set the detector time window cut parameters, as they are needed to reduce sources of background that slips into the detector readout windows when detecting the physics signals of interest.
\begin{itemize}
  \item Similarly to step 1, you can select a representative run for each kinematic setting of the experiment to check whether the relevant histograms shift per setting, in which case the detectors time window cuts
    may need to be determined for each setting.
  \item After the detector time window cut parameters have been set, make sure to replay the data before moving on to the next step (detector calibrations) to ensure that the sources of background are reduced.
\end{itemize}
\textbf{STEP 3}: Do the detector calibrations relevant only for your experiment. You DO NOT need to calibrate a detector that was NOT used in your experiment. The particular order of detector calibrations does
NOT matter for ``particle identification'' (PID) detectors such as the calorimeters, gas and aerogel cherenkovs. For the standard hodoscope (determines the trigger) and drift chambers (track reconstruction),
however, the calibration of one of these detectors affects the other.
\begin{itemize}
\item It is recommended to do the hodoscopes calibration first in order to determine the correct signal timing (hodoscope start time) which is used
  by the drift chambers to determine the drift times (replay the data after hodoscope calibration). Then do the drift chamber calibration in order to improve the tracking (smaller residuals $\rightarrow$ more tracks). 
\item After a first iteration of hodoscope and drift chamber calibrations (and remembering to replay the data after each calibration), check the hodoscopes characteristic plot ($\beta$) as a sanity check that the drift chamber
calibration has not negatively impacted that of the hodoscopes. You should NOT need to do a second calibration of the hodoscopes if the hodoscope $\beta$ is centered at $\beta = p/\sqrt{m^{2} + p^{2}}$, where $p$ is the
central spectrometer momentum and $m$ is the particle mass.  
\end{itemize}

\newpage 
\begin{appendices}
\appendix
\section{Examples of Cut Parameter Files}
\label{appendix:AppxA}
The values in the parameter files are read in as arrays starting with indez zero from left to right. For example,\\ \texttt{hhodo\_PosAdcTimeWindowMin[0]=-61.,
  hhodo\_PosAdcTimeWindowMin[1]=-64.}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/hdc_parm_cut.png}
  \caption{HMS DC TimeWindow cut parameter file.}
  \label{fig:hms_dc_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/hhodo_parm_cut.png}
  \caption{HMS Hodo TimeWindow cut parameter file.}
  \label{fig:hms_hod_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/hcer_parm_cut.png}
  \caption{HMS Cherenkov TimeWindow cut parameter file.}
  \label{fig:hms_cer_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/hcal_parm_cut.png}
  \caption{HMS Calorimeter TimeWindow cut parameter file.}
  \label{fig:hms_cal_parm_cut}
\end{figure}

\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/pdc_parm_cut.png}
  \caption{SHMS DC TimeWindow cut parameter file.}
  \label{fig:shms_dc_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/phodo_parm_cut.png}
  \caption{SHMS Hodo TimeWindow cut parameter file.}
  \label{fig:shms_hod_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/phgcer_parm_cut.png}
  \caption{SHMS HG Cherenkov TimeWindow cut parameter file.}
  \label{fig:shms_hgcer_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/pngcer_parm_cut.png}
  \caption{SHMS NG Cherenkov TimeWindow cut parameter file.}
  \label{fig:shms_ngcer_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/pprsh_parm_cut.png}
  \caption{SHMS PreShower TimeWindow cut parameter file.}
  \label{fig:shms_prsh_parm_cut}
\end{figure}
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.4]{plots/pcal_parm_cut.png}
  \caption{SHMS Calorimeter TimeWindow cut parameter file.}
  \label{fig:shms_cal_parm_cut}
\end{figure}

\end{appendices}
%Equations $\beta = \frac{v}{c}$.

%The general expression is
%\begin{equation} \label{eq1}
%\begin{split}
%A & = \frac{\pi r^2}{2} \\
% & = \frac{1}{2} \pi r^2
%\end{split}
%\end{equation}
%See Equation \ref{eq1}

%See Figure \ref{fig:Hodo}
%\begin{figure}[H]
%  \captionsetup{justification=raggedright,singlelinecheck=false}
%  \includegraphics[scale=0.3]{}
%  \caption{HMS Hodoscope 1X and 1Y Planes.}
%  \label{fig:Hodo}
%\end{figure}

% --------------------------------------------------------------
%     You don't have to mess with anything below this line.
% --------------------------------------------------------------

\end{document}

### 2020-11-17 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/referee_reply_templates.txt
updated prl response 2

===========================
Hi Carlos,

attached are some replies for the referee comments and suggestions for additions/replacements for the introduction.

kind regards

Werner
===========================

1) Understanding the high momentum structure of pn system is highly important for nuclear physics due to the observed 
dominance of short range correlations in nuclei at nucleon momenta above the fermi momentum. This dominance has
been well established by a series of recent experiments carried out at Jefferson Lab and BNL. In these experiments nucleon
momenta up to 1 GeV/c have been probed and recoil momentum distributions have been compared to 
the high momentum part of theoretical deuteron momentum distributions. (cite Piasetky, Korover, Duer and Cruz-Torres)

Recoil momenta up to about 1 GeV/c have also been probed
in a 3He(e,e'p) experiment however at a relatively low momentum transfer of 1.5 (GeV/c)^2 and at a kinematic region (x_b ~1)
where the cross section is dominated by final state interaction. (cite Benmokhtar and Rvachev)

Citations:

E. Piasetzky et al., PRL 97, 162504 (2006)
I. Korover et al, PRL 113, 022501 (2014)
M. Duer et al., PRL 122, 172502 (2019)
R. Cruz-Torre, PRL 124, 212501 (2020)

3He experiments:

F. Benmokhtar, PRL 94, 082305 (2005)
M. M. Rvachev, PRL 94, 192302 (2005)

---------REPLY TO REFEREE COMMENTS---------

2) Our analysis demonstrated that there is no simplistic way of 
estimating relativistic effects since even in the kinematics in which FSI are small 
they are still comparable with the expected relativistic effects. The current calculations
are based on the virtual nucleon approximation in which  relativistic effects are accounted for 
in the propagator of the bound nucleon, for the vertex of electron-bound nucleon interaction as well as
for FSI.  To switch off relativistic effects means to remove all these effects which will return us to the 
standard Glauber theory.  But in our previous paper\cite{2011 PRL paper}  we already demonstrated that Glauber theory 
will not describe the main feature of the reaction. For example at 400 MeV/c it will predict maximum FSI to occur at 90 degrees of 
the spectator angle, while the experiment clearly shows that maximum FSI is at 70 degrees.
The current limitation of the virtual nucleon approximation is that it still uses a non-relativistic deuteron wave 
function(cite Sargsian “private communication”) and assumes that vacuum fluctuation effects are not significant.  It is expected that the latter will grow with the increase 
of the recoil momentum of the spectator nucleon. 
One approach that addresses this issue is the Light-Front approximation, however the implementation of this approximation 
requires a consistent calculation of all the above discussed factors (i.e. propagator, vertex, FSI and wave function).
Hence relativistic effects cannot simply be 'turned off, since they contribute in different components of 
the scattering amplitude.

Light-front calculations are currently underway (M.Sargsian “Private Communication”) which we hope  will be used 
to compare with our data for the large paper.

3) Similar to the above comment regarding relativistic calculations to account for the
effects of different  wave functions, it requires a complete 
calculation including the FSI effects which is out of scope of the current paper. 
We hope that the theory groups who are collaborating with us will be able to provide such 
calculations which will be presented in a larger paper. These studies are currently in progress.

Comment for page 5-6:

The comparison between the measured (reduced) cross sections and the currently available
complete and state of the art calculations illustrates the limit to which a non-relativistic
wave function that is the solution of the Schroedinger equation is valid and able to describe
experimental data that probe the high momentum region of the np system in the most direct way
possible.

### 2020-11-17 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/manuscript/ms.tex
updated prl response 2

--- 2020-10-19 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
@@
 bound nucleon with the same momentum is being measured.\\
-%===Original introguction (replaced by above intro, suggested by W. Boeglin, in response to referee. comments)====
-%At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
-%nucleons begin to overlap.
-The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.
-%Short-range studies of the deuteron are also important in determining whether, or to what extent, the description of nuclei in terms of nucleon/meson degrees of freedom is still valid, before
-%having to include explicit quark degrees of freedom, an issue of fundamental importance in nuclear physics \cite{sargsian_2015}.
-As of the present time, there are only a few nuclear physics experiments for
-%which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
-%However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
-\indent The most direct way to study the short range structure of the deuteron wave function %(or equivalently, its high momentum component)
+\indent The most direct way to study the short range structure of the deuteron wave function
 is via the exclusive deuteron electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA),

### 2020-11-22 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/supplemental/supplemental.tex
updated

--- 2020-10-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/arXiv_PRLsubmission_v2/supplemental.tex
@@
 \documentclass[aps, prl]{revtex4-2}  % for review and submission
-%\usepackage{graphicx}  % needed for figures
-%\usepackage{dcolumn}   % needed for some tables
-%\usepackage{bm}        % for math
-%\usepackage{amssymb}   % for math
-%\usepackage[hidelinks]{hyperref}
-%\usepackage{fancyhdr}
-%\usepackage{xcolor}
-%\usepackage{grffile}
-%\usepackage[top=1in,left=0.8in, right=0.8in, bottom=0.8in]{geometry}
-%\usepackage{float}
-%\usepackage[compact]{titlesec}
-%\titlespacing{\section}{0pt}{2ex}{2ex}
 \usepackage{comment}
@@
 a sample of events were selected in the negative part of the missing energy spectrum using the deuteron high missing momentum settings (580 and 750 MeV/c).
-%This was only made possible due to the high recoil kinetic energies reconstructed at these kinematics. For electron interactions with the aluminum target endcaps,
-%the reconstructed events extended to the negative part of the missing energy spectrum since we assume the mass of the deuteron in the missing energy definition.\\
 We assume that the contribution due to the target endcaps is constant across the missing energy spectrum, therefore, by selecting a sample in the
@@
 \indent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
-missing momentum and integrated over all $\theta_{nq}$ bins for each of the three central momentum settings.
-A detailed discussion of how the experimental and reduced cross sections were extracted can be
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$).
+For illustration purposes, Figs.
+\ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+missing momentum and $\theta_{nq} = 35^{\circ}$ and  $45^{\circ}$ bins for each of the three central momentum settings.
+Figure \ref{fig:RedXsec_overlap} shows the reduced cross section overlap for the high
+$p_{\mathrm{r}}$ region. A detailed discussion of how the experimental and reduced cross sections were extracted can be
 found in Sections 5.1 and 6.1 of Ref. \cite{cyero_phdthesis}.
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{Pr_and_Ps.png}
-\caption{(left) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right) Monte Carlo (un-weighted) events generated over
+\includegraphics[scale=0.3]{Pr_and_Ps_35deg.png}
+\includegraphics[scale=0.3]{Pr_and_Ps_45deg.png}
+%\includegraphics[scale=0.31]{Pr_and_Ps_75deg.png}
+\caption{(left column) Experimental neutron recoil (``missing'') momentum distribution for each of the three central settings. (right column) Monte Carlo (un-weighted) events generated over
   the spectrometers' phase space volume binned in missing momentum.}
 \label{fig:Pm_Ps}
+\includegraphics[scale=0.3]{RedXsec_overlap.png}
+\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings.}
+\label{fig:RedXsec_overlap}
 \end{figure}

### 2020-11-22 PRL_UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -301,22 +301,22 @@ void compare_hist(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel=""
 
 
 //-----------------------------------------------
-void combine_sets(TH1F *hist80, TH1F *hist_580set1, TH1F *hist_580set2, TH1F *hist_750set1, TH1F *hist_750set2, TH1F *hist_750set3, TString xlabel="", TString ylabel="", TString title="", Double_t scale_factor=1)
+void combine_sets(TH1F *hist80, TH1F *hist_580set1, TH1F *hist_580set2, TH1F *hist_750set1, TH1F *hist_750set2, TH1F *hist_750set3, TString xlabel="", TString ylabel="", TString title="", Double_t scale_factor=1, Bool_t combine=0)
 {
 
   //This function adds histograms of multiple data sets from the same kinematic setting (i.e., 580_set1 + 580_set2)
  
 
   //Clone histograms and rename them total
-  TH1F *hist_580tot = (TH1F*)hist_580set1->Clone("hist_580tot");
+  TH1F *hist_580tot = (TH1F*)hist_580set2->Clone("hist_580tot");
   TH1F *hist_750tot = (TH1F*)hist_750set1->Clone("hist_750tot");
 
-  //Add remaining histograms to total
-  hist_580tot->Add(hist_580set2);
+    //Add remaining histograms to total
+    //hist_580tot->Add(hist_580set2);
 
-  hist_750tot->Add(hist_750set2);
-  hist_750tot->Add(hist_750set3);
-
+    //hist_750tot->Add(hist_750set2);
+    //hist_750tot->Add(hist_750set3);
+  
   
   int font_type = 132;
 

### 2020-11-22 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/make_plot.py

@@ -63,8 +63,8 @@ ax1.errorbar(pm_avg_80[thnq_80==35], red_Xsec_80[thnq_80==35], red_Xsec_sys_err_
 ax1.errorbar(pm_avg_580[thnq_580==35], red_Xsec_580[thnq_580==35], red_Xsec_tot_err_580[thnq_580==35], marker='o', linestyle='none', color='r', mfc='r', ecolor='r', capsize=0, label=r'580 MeV/c setting' )
 ax1.errorbar(pm_avg_580[thnq_580==35], red_Xsec_580[thnq_580==35], red_Xsec_sys_err_580[thnq_580==35], marker='o', linestyle='none', color='r', mfc='r', ecolor='lightgray', elinewidth=3, capsize=0)
 
-ax1.errorbar(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_tot_err_750[thnq_750==35], marker='^', linestyle='none', color='g', mfc='g', ecolor='g', capsize=0, label=r'750 MeV/c setting' )
-ax1.errorbar(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_sys_err_750[thnq_750==35], marker='^', linestyle='none', color='g', mfc='g', ecolor='lightgray', elinewidth=3, capsize=0)
+ax1.errorbar(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_tot_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='magenta', capsize=0, label=r'750 MeV/c setting' )
+ax1.errorbar(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_sys_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='lightgray', elinewidth=3, capsize=0)
 
 ax1.set_yscale('log')
 
@@ -81,7 +81,7 @@ plt.yticks(fontsize=16)
 y_dummy = np.zeros(len(red_Xsec_80[thnq_80==35]))
 l1, = ax2.plot([], [], c='b')
 l2, = ax2.plot([], [], c='r')
-l3, = ax2.plot([], [], c='g')
+l3, = ax2.plot([], [], c='magenta')
 l4, = ax2.plot([], [], c='gray', label='Systematic Uncerainty')
 
[…]

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/MARKED/ms.tex
updated PRL

--- 2020-11-17 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/manuscript/ms.tex
@@
 dominance of short-range correlations (SRC) in nuclei at nucleon momenta above the fermi momentum. This dominance has been well established by a series of recent experiments
-carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}.
+carried out at Jefferson Lab (JLab) \cite{Subedi1476, PhysRevLett.113.022501,PhysRevLett.122.172502, Schmidt_2020} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}.
 In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/MARKED/ms_revised.tex
updated

--- 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/MARKED/ms.tex
@@
 The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
-$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}.
+$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}, this results in an additional $1/Q^{4}$ suppression as compared to the quasi-elastic contribution.
 Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron.
@@
   The dashed reference (magenta) line refers to MS CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.
-  Insets: Blowup of the subfigures below $p_{\mathrm{r}}=$0.7 GeV/c.}
+  Insets: Blowup of the subfigures for $p_{\mathrm{r}}\leq$0.7 GeV/c.}
 \label{fig:fig2}
@@
 region where FSI are still relatively small $(<30\%)$. This behavior of the data is new and additional data in this kinematic region are necessary
-to improve the statistics. \\
+to improve the statistics. Furthermore, the new data set is ideal for testing fully relativistic deuteron models based on light-front or covariant formalisms.
+In this respect the current effective field theories (EFT) based models \cite{Reinert_EFT2018} are non-relativistic and might not have direct relevance to our data. \\
 \indent At $\theta_{nq}=75^{\circ}$ (Fig.

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/supplemental/supplemental.tex
updated

@@
 \begin{figure}[!h]
-\includegraphics[scale=0.3]{Pr_and_Ps_35deg.png}
-\includegraphics[scale=0.3]{Pr_and_Ps_45deg.png}
+\includegraphics[scale=0.29]{Pr_and_Ps_35deg.png}
+\includegraphics[scale=0.29]{Pr_and_Ps_45deg.png}
 %\includegraphics[scale=0.31]{Pr_and_Ps_75deg.png}
@@
 \label{fig:Pm_Ps}
-\includegraphics[scale=0.3]{RedXsec_overlap.png}
-\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings.}
+\includegraphics[scale=0.23]{RedXsec_overlap.png}
+\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings. The 750 MeV/c setting has been offset (right) by +0.01 GeV/c for ease of comparison.}
 \label{fig:RedXsec_overlap}

### 2020-11-23 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/make_plot.py

@@ -117,13 +117,13 @@ fig1 = B.pl.figure(figsize=(8,6))
 B.plot_exp(pm_avg_580[thnq_580==35], red_Xsec_580[thnq_580==35], red_Xsec_tot_err_580[thnq_580==35], marker='o', linestyle='none', color='r', mfc='r', ecolor='r', capsize=0, logy='true', label=r'580 MeV/c setting' )
 B.plot_exp(pm_avg_580[thnq_580==35], red_Xsec_580[thnq_580==35], red_Xsec_sys_err_580[thnq_580==35], marker='o', linestyle='none', color='r', mfc='r', ecolor='lightgray', elinewidth=3, capsize=0, logy='true')
 
-B.plot_exp(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_tot_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='magenta', capsize=0, logy='true', label=r'750 MeV/c setting' )
-B.plot_exp(pm_avg_750[thnq_750==35], red_Xsec_750[thnq_750==35], red_Xsec_sys_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='lightgray', elinewidth=3, capsize=0, logy='true')
+B.plot_exp(pm_avg_750[thnq_750==35]+0.01, red_Xsec_750[thnq_750==35], red_Xsec_tot_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='magenta', capsize=0, logy='true', label=r'750 MeV/c setting' )
+B.plot_exp(pm_avg_750[thnq_750==35]+0.01, red_Xsec_750[thnq_750==35], red_Xsec_sys_err_750[thnq_750==35], marker='^', linestyle='none', color='magenta', mfc='magenta', ecolor='lightgray', elinewidth=3, capsize=0, logy='true')
 
 plt.subplots_adjust(left=0.12, right=0.96, top=0.93, bottom=0.11)
 
 #Set X-limits
-B.pl.xlim(0.4, 1.2)
+B.pl.xlim(0.4, 1.3)
 #Set Y-limits
 B.pl.ylim(2e-6, 2e-4)
 
@@ -148,13 +148,13 @@ fig2 = B.pl.figure(figsize=(8,6))
[…]

### 2020-11-25 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/reply_to_RefereeA.txt
updated prl for re-submission

--------------------------------
Reply to: Report of Referee A
--------------------------------

A concise, point-by-point response for each of the recommendations and criticisms made by referee A is shown below:

-------------
Referee A:
-------------
1) The connection to SRC is now mentioned. However the references chosen by the authors do not make sense to me.
The standard (general) reference to SRC experimental study is: Subedi et al., Science 320, 1476 (2008). The two
SRC studies highly relevant to this work (emphasizing high momentum) are Korover et al. and A. Schmidt et al. ,
Nature volume 578, 540 (2020). Korover et al. is Ref 1 in the new manuscript but the other two are not mentioned.
Moreover, Ref 3 is an odd choice, since it is not directly related to the subject.
----------
Response:
----------
The authors have corrected the references to SRC experimental studies accordingly.

-------------
Referee A:
-------------
2) Relativity (no reference to light-cone formalism), Nucleon-Nucleon interaction (no modern EFT calculations).
I accept the authors response that these theoretical calculations are out of the scope of this experimental paper.
However, to my opinion they should at least be mentioned and discussed in some reasonable way.
----------
Response:
----------
A brief explanation of the light-cone / EFT formalism along with the corresponding references have been added to
the concluding paragraph of the PRL manuscript.

-------------
Referee A:
-------------
3) Their description of why MEC are suppressed is incomplete. The authors give the MEC amplitude, but do not show
that it is smaller than the QE amplitude.
----------
Response:
----------
The description of MEC suppression has been extended to address the QE amplitude.
See page 2 (left colum), last paragraph of the PRL manuscript.

-------------
Referee A:
-------------
4) “a weighted average of the cross sections were taken in the overlapping regions of pr”. Show consistency.
They should show the cross section calculated for each setup in the overlap region before they were averaged.
The new manuscript shows the raw data and the corrections in the overlap regions (Supp. Figs 9-11) but not the
cross sections which would allow the reader to verify their consistency and whether the systematic uncertainties
are reasonable.
----------
Response:
----------
The authors have added Fig. 10 in Supplemental Materials to show the reduced cross sections in the overlap
region before being averaged.

-------------
Referee A:
-------------
5) I did not see the requested tables of kinematics and cross sections in the supplemental material.
----------
Response:
----------
The authors did previously inlcude the raw experimental cross-section data (with kinematics)
as well as raw data files with the theroretical cross sections in the form of .txt files.
In addition to the raw data previously submitted, a .pdf version of the datafiles will also
be submitted in this instance.

### 2020-11-25 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/supplemental/supplemental.tex
updated prl for re-submission

@@
 \indent The average experimental cross section was extracted by taking the ratio of the radiative corrected data yield ($Y_{\mathrm{corr}}$) to the Monte Carlo generated phase space volume for each
-kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$).
-For illustration purposes, Figs.
-\ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
+kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in
 missing momentum and $\theta_{nq} = 35^{\circ}$ and  $45^{\circ}$ bins for each of the three central momentum settings.
@@
 \begin{figure}[!h]
-\includegraphics[scale=0.29]{Pr_and_Ps_35deg.png}
-\includegraphics[scale=0.29]{Pr_and_Ps_45deg.png}
+\includegraphics[scale=0.30]{Pr_and_Ps_35deg.png}
+\includegraphics[scale=0.30]{Pr_and_Ps_45deg.png}
 %\includegraphics[scale=0.31]{Pr_and_Ps_75deg.png}
@@
 \label{fig:Pm_Ps}
-\includegraphics[scale=0.23]{RedXsec_overlap.png}
-\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings. The 750 MeV/c setting has been offset (right) by +0.01 GeV/c for ease of comparison.}
+\includegraphics[scale=0.30]{RedXsec_overlap.png}
+\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings. The 750 MeV/c setting data points have been offset right by +0.01 GeV/c for ease of comparison.}
 \label{fig:RedXsec_overlap}

### 2020-11-25 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/make_plot.py

@@ -123,7 +123,7 @@ B.plot_exp(pm_avg_750[thnq_750==35]+0.01, red_Xsec_750[thnq_750==35], red_Xsec_s
 plt.subplots_adjust(left=0.12, right=0.96, top=0.93, bottom=0.11)
 
 #Set X-limits
-B.pl.xlim(0.4, 1.3)
+B.pl.xlim(0.4, 1.2)
 #Set Y-limits
 B.pl.ylim(2e-6, 2e-4)
 
@@ -134,7 +134,7 @@ B.pl.ylabel('$\sigma_{\mathrm{red}}$ [fm$^{3}$]', fontsize=20)
 
 plt.xticks(fontsize=18)
 plt.yticks(fontsize=18)
-B.pl.legend(fontsize=16)
+B.pl.legend(fontsize=18)
 
 #B.pl.show()
 B.pl.savefig('redXsec_35.pdf')
@@ -154,7 +154,7 @@ B.plot_exp(pm_avg_750[thnq_750==45]+0.01, red_Xsec_750[thnq_750==45], red_Xsec_s
 plt.subplots_adjust(left=0.12, right=0.96, top=0.93, bottom=0.11)
 
 #Set X-limits
-B.pl.xlim(0.4, 1.5)
+B.pl.xlim(0.4, 1.2)
 #Set Y-limits
 B.pl.ylim(2e-6, 2e-4)
 
@@ -165,7 +165,7 @@ B.pl.ylabel('$\sigma_{\mathrm{red}}$ [fm$^{3}$]', fontsize=20)
 
 plt.xticks(fontsize=18)
 plt.yticks(fontsize=18)
-B.pl.legend(fontsize=16)
+B.pl.legend(fontsize=18)
 
 #B.pl.show()
 B.pl.savefig('redXsec_45.pdf')

### 2020-11-26 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/reply_to_RefereeA.txt
updated PRL manuscript replay to referee and created a .zip file package for submission

@@
 The standard (general) reference to SRC experimental study is: Subedi et al., Science 320, 1476 (2008). The two
-SRC studies highly relevant to this work (emphasizing high momentum) are Korover et al. and A. Schmidt et al. ,
+SRC studies highly relevant to this work (emphasizing high momentum) are Korover et al. and A. Schmidt et al.,
 Nature volume 578, 540 (2020). Korover et al. is Ref 1 in the new manuscript but the other two are not mentioned.
@@
 ----------
-The authors did previously inlcude the raw experimental cross-section data (with kinematics)
-as well as raw data files with the theroretical cross sections in the form of .txt files.
+The authors did previously include the raw experimental cross-section data (with kinematics)
+as well as raw data files with the theoretical cross sections in the form of .txt files.
 In addition to the raw data previously submitted, a .pdf version of the datafiles will also

### 2021-05-15 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/prl_submission_v3/reply_to_RefereeA.txt

--- 2020-11-26 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/reply_to_RefereeA.txt
@@
 The description of MEC suppression has been extended to address the QE amplitude.
-See page 2 (left colum), last paragraph of the PRL manuscript.
+See page 2 (left column), last paragraph of the PRL manuscript.
 
@@
 as well as raw data files with the theoretical cross sections in the form of .txt files.
-In addition to the raw data previously submitted, a .pdf version of the datafiles will also
+In addition to the raw data previously submitted, a .pdf version of the data files will also
 be submitted in this instance.

### 2021-12-03 MY_THESIS/HallC_12GeV_Trigger/version3/trigger_v3_source/trigger_v3.tex
added dir. with source code of v.3 of document.

--- 2020-08-30 MY_THESIS/HallC_12GeV_Trigger/version3/trigger_v3.tex
@@
 \usepackage{setspace}
-\usepackage{vector}
 \usepackage{amsmath}
@@
   \centering
-  \includegraphics[width=5.0in, height=4.0in]{../HMS_stack.pdf}
+  \includegraphics[width=5.0in, height=4.0in]{images/HMS_stack.pdf}
   \caption{HMS detector stack.}
@@
   \centering
-  \includegraphics[width=5.0in, height=4.0in]{../HMS_Hut_Rack.pdf}
+  \includegraphics[width=5.0in, height=4.0in]{images/HMS_Hut_Rack.pdf}
   \caption{HMS detector hut electronic rack and patch panels.}
@@
   \centering
-  \includegraphics[width=6.0in, height=2.0in]{../HMS_patch.pdf}
+  \includegraphics[width=6.0in, height=2.0in]{images/HMS_patch.pdf}
   \caption{HMS Patch Diagram from detectors to Counting Room.}
@@
   \centering
-  \includegraphics[width=6.0in, height=4.0in]{../SHMS_stack.pdf}
+  \includegraphics[width=6.0in, height=4.0in]{images/SHMS_stack.pdf}
   \caption{SHMS detector stack.}
@@
 \begin{minipage}{.5\textwidth}
-  \includegraphics[width=3.0in, height=4.0in]{../SHMS_Hut_Rack01.pdf}
+  \includegraphics[width=3.0in, height=4.0in]{images/SHMS_Hut_Rack01.pdf}
   \captionof{figure}{SHMS Hut Patch Panel (left) and Electronics Rack (right).}
@@
 \begin{minipage}{.5\textwidth}
-  \includegraphics[width=2.0in, height=4.0in]{../SHMS_Hut_Rack02.pdf}
+  \includegraphics[width=2.0in, height=4.0in]{images/SHMS_Hut_Rack02.pdf}
   \caption{SHMS Drift Chamber Electronics Rack.}
@@
   \centering
-  \includegraphics[scale=0.8]{../SHMS_patch.pdf}
+  \includegraphics[scale=0.8]{images/SHMS_patch.pdf}
   \caption{SHMS Patch Diagram from detectors to Counting Room.}
@@
 \begin{figure}[h!]
-  \includegraphics[scale=0.5]{../CR_patch_combined.png}
+  \includegraphics[scale=0.5]{images/CR_patch_combined.png}
   \caption{(A) Counting Room Patch Panels (left 2 racks). (B) Counting Room main
@@
   \centering
-  \includegraphics[scale=0.35]{./hHODO_diagram.png}
+  \includegraphics[scale=0.35]{images/hHODO_diagram.png}
   \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}
@@
   \centering
-  \includegraphics[scale=0.35]{./hCAL_diagram.png}
+  \includegraphics[scale=0.35]{images/hCAL_diagram.png}
   \caption{HMS Calorimeter Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA2}}
@@
   \centering
-  \includegraphics[scale=0.35]{./hCER_diagram.png}
+  \includegraphics[scale=0.35]{images/hCER_diagram.png}
   \caption{HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov. For original diagram, see Appendix \ref{appendix:Appx3} }
@@
   \centering
-  \includegraphics[scale=0.35]{HMS_SingleArm_diagram.png}
+  \includegraphics[scale=0.35]{images/HMS_SingleArm_diagram.png}
   \caption{HMS Single Arm Pre-Trigger Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx5}}
@@
   \centering
-  \includegraphics[scale=0.35]{pHODO_diagram.png}
+  \includegraphics[scale=0.35]{images/pHODO_diagram.png}
   \caption{SHMS Hodoscopes Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx6}}
@@
   \centering
-  \includegraphics[scale=0.35]{pCAL_diagram.png}
+  \includegraphics[scale=0.35]{images/pCAL_diagram.png}
   \caption{SHMS PreShower / Shower Electronics Diagram. For original diagram, see Appendix \ref{appendix:Appx7}}
@@
   \centering
-  \includegraphics[scale=0.35]{pCER_diagram.png}
+  \includegraphics[scale=0.35]{images/pCER_diagram.png}
   \caption{SHMS Gas \v{C}erenkovs Electronics Diagram.}
@@
   \centering
-  \includegraphics[scale=0.35]{SHMS_SingleArm_diagram.png}
+  \includegraphics[scale=0.35]{images/SHMS_SingleArm_diagram.png}
   \caption{SHMS Single Arm Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx8}.}
@@
   \centering
-  \includegraphics[scale=0.35]{Coin_diagram.png}
+  \includegraphics[scale=0.35]{images/Coin_diagram.png}
   \caption{Coincidence Trigger Electronics Diagram. For the original diagram, see Appendix \ref{appendix:Appx9}}
@@
   \centering
-  \includegraphics[scale=0.54]{EDTM_diagram.png}
+  \includegraphics[scale=0.54]{images/EDTM_diagram.png}
   \caption{EDTM electronics diagram.}
@@
   \centering
-  \includegraphics[scale=0.40]{EDTM_TI.png}
+  \includegraphics[scale=0.40]{images/EDTM_TI.png}
   \caption{Cartoon representation of EDTM (purple) and physics (magenta) pre-triggers at the TI module front-end.}
@@
   \centering
-  \includegraphics[scale=0.38]{./Jan2018_trigger_change.png}
+  \includegraphics[scale=0.38]{images/Jan2018_trigger_change.png}
   \caption{The STOF was removed from the reference time definition in both spectrometers (HMS/SHMS) on January 23, 2018.
@@
   \centering
-  \includegraphics[scale=0.38]{./Aug2018_trigger_change.png}
+  \includegraphics[scale=0.38]{images/Aug2018_trigger_change.png}
   \caption{The EL-CLEAN was removed from the reference time definition in both spectrometers (HMS/SHMS) on August 09, 2018.
@@
   \centering
-  \includegraphics[scale=0.38]{./Dec2019_trigger_change.png}
+  \includegraphics[scale=0.38]{images/Dec2019_trigger_change.png}
   \caption{The STOF was removed from electronics trigger and EL-REAL was removed from the reference time definition in both spectrometers (HMS/SHMS) on Dec 06, 2019.
@@
   \centering
-  \includegraphics[width=7.0in, height=3.2in]{../HMS_HODO_TRIGGER.pdf}
+  \includegraphics[width=7.0in, height=3.2in]{images/HMS_HODO_TRIGGER.pdf}
   \caption{Original HMS Hodoscopes Electronics Diagram.}
@@
   \centering
-  \includegraphics[width=6.in, height=4.in]{../HMS_Cal_Trigger.pdf}
+  \includegraphics[width=6.in, height=4.in]{images/HMS_Cal_Trigger.pdf}
   \caption{Original HMS Calorimeter Electronics Diagram.}
@@
   \centering
-  \includegraphics[width=7.0in, height=2.0in]{../HMS_Cer_trig.pdf}
+  \includegraphics[width=7.0in, height=2.0in]{images/HMS_Cer_trig.pdf}
   \caption{Original HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
@@
   \centering
-  \includegraphics[width=6.5in, height=2.1in]{../HMS_Aero_trig.pdf}
+  \includegraphics[width=6.5in, height=2.1in]{images/HMS_Aero_trig.pdf}
   \caption{Original HMS Gas \v{C}erenkov Electronics Diagram. Same electronics diagram applies for SHMS Gas \v{C}erenkov.}
@@
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{../HMS_SingleArm_Trigger.pdf}
+  \includegraphics[width=7.0in, height=3.8in]{images/HMS_SingleArm_Trigger.pdf}
   \caption{Original HMS Single Arm Trigger Electronics Diagram.}
@@
   \centering
-  \includegraphics[width=6.8in, height=3.9in]{../SHMS_HODO_TRIGGER.pdf}
+  \includegraphics[width=6.8in, height=3.9in]{images/SHMS_HODO_TRIGGER.pdf}
   \caption{Original SHMS Hodoscope Electronics Diagram.}
@@
   \centering
-  \includegraphics[width=7.0in, height=3.0in]{../SHMS_preSh_trigger.pdf}
+  \includegraphics[width=7.0in, height=3.0in]{images/shms_preSh_trigger.pdf}
   \caption{Original SHMS PreShower Electronics Diagram}
@@
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{../SHMS_SingleArm_Trigger.pdf}
+  \includegraphics[width=7.0in, height=3.8in]{images/SHMS_SingleArm_Trigger.pdf}
   \caption{Original SHMS Single Arm Trigger Electronics Diagram}
@@
   \centering
-  \includegraphics[width=7.0in, height=3.8in]{../Coincidence_Trigger.pdf}
+  \includegraphics[width=7.0in, height=3.8in]{images/Coincidence_Trigger.pdf}
   \caption{Original Coincidence Trigger Electronics Diagram}

### 2022-01-18 MY_THESIS_DOCS/D2_Optics_Optim/d2_optim.tex
re-structure

--- 2019-07-29 MY_THESIS/D2_Optics_Optim/d2_optim.tex
@@
 of the spectrometer offsets in Hall C has not been done yet. For now, we have made a rough estimate on these
-offsets based on observations in H(e,e'p) elastic run 3288, as it is closest in kinematic to the Deuteron 80 MeV setting.
+offsets based on observations in H(e,e'p) elastic run 3288, as it is closest in kinematic to the deuteron 80 MeV setting.
 \subsection{Central Angle Offsets}
@@
 The \textit{in-plane} is parallel to the Hall C floor, whereas the \textit{out-of-plane} is perpendicular to the Hall C floor.
-The central angle offsets can be determined from the missing momentum components for H(e,e'p) elastics, as these should ideally be centered around
-zero. In Hall Coordinate System (HCS), the in-plane central angle offset can be determined by taking the fractional dfference between
+The central angle offsets can be determined from the missing momentum components for H(e,e'p) elastics, as these should ideally
+be centered around zero. In Hall Coordinate System (HCS), the in-plane central angle offset can be determined by taking the fractional dfference between
 the measured (DATA) and expected (SIMC) X missing momentum component as follows:

### 2022-01-18 MY_THESIS_DOCS/DETECTORS/Hodoscope_Calib_Doc/hodo_calib.tex
re-structure

--- 2020-04-08 MY_THESIS/Hodoscope_Calib_Doc/hodo_calib.tex
@@
 \maketitle
-\noindent The Hall C Scintillaror Hodoscopes consists on four planes (per spectrometer) of scintillator arrays oriented perpendicular
+\noindent The Hall C Scintillaror Hodoscopes consists of four planes (per spectrometer) of scintillator arrays oriented perpendicular
 to the beam direction(See Figure \ref{fig:Hodo}). Each spectrometer has two sets of planes, each set oriented along the +X and +Y in the hut coordinate system.
 The hodoscopes form the standard HMS/SHMS trigger in Hall C due to the fast signal rise time produced from the scintillating material.
-For a thorough discussion of how the trigger is formed, see . . . \\
+For a thorough discussion of how the trigger is formed, see \url{https://hallcweb.jlab.org/doc-private/ShowDocument?docid=1028}  \\
 \begin{figure}[H]
@@
 When a particle traverses a plane, depending on the trajectory, any paddle could in principle be hit,
-the paddle then scintillates light, which propagates to them photomultiplier tubes (PMTs) at the two ends. The PMTs
+the paddle then scintillates light, which propagates to the photomultiplier tubes (PMTs) at the two ends. The PMTs
 convert the incident light to photoelectrons in the photocathode. The photoelectrons then are guided through the various dynodes in the PMT, knocking
@@
   which causes the discriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the
-  same time. Analog-to-Digital Converters (ADCs), do not have this disadvantage, since they correct for time-walk internally,
-  and as a result, the ADC Pulse Time is not correlated with the signal amplitude. To correct for this correlation in the TDCs,
-  the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the ADC amplitude. A model
-  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time.
+  same time. Flash Analog-to-Digital Converters (fADCs), do not have this disadvantage, since they correct for time-walk internally,
+  and as a result, the ADC Pulse Time is not correlated with the signal amplitude. To correct for this correlation in the high resolution TDCs,
+  the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the fADC amplitude. A model
+  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time. (See Figure \ref{fig:TWFit}) The function that is currently
+  being used in Hall C analyzer, \texttt{hcana}, has the form:
+  \begin{equation}
+    f_{TW}(a) = \frac{1}{(\frac{a}{TDC_{Thrs.}})^{c_{2}}} - \frac{1}{(\frac{200}{TDC_{Thrs.}})^{c_{2}}}
+  \end{equation}
+  where $a$ is the ADC amplitude,  $TDC_{Thrs}$ is the TDC threshold which is currently set to 120 mV. \textbf{ONLY} the fit parameter, $c_{2}$, and the
+  TDC Threshold ($TDC_{Thrs.}$), are read in by \texttt{hcana}, where the time-walk correction is applied to the raw TDC to obtain the corrected tdc time as shown in Figure \ref{fig:TWCorr}.
+  Even though the baseline parameter, $c_{1}$, is extracted in the calibration code, it is actually \textbf{NOT} used in \texttt{hcana} as it is highly correlated with the parameter $c_{2}$.
+  As a solution, an empirical baseline:  $-\frac{1}{(\frac{200}{TDC_{Thrs.}})^{c_{2}}}$, is used in \texttt{hcana} to replace $c_{1}$.
+  \newpage
   \begin{figure}[H]
@@
 \newpage
-The plot in Figure \ref{fig:TWFit} shows the correlation between TDC Pulse Time and ADC Pulse Amplitude.  The fit parameters, $c_{1}$, TDC Threshold are read in by hcana, where
-the time-walk correction is applied to the raw TDC to obtain the corrected tdc time as shown in Figure \ref{fig:TWCorr}.
+The plot in Figure \ref{fig:TWFit} shows the correlation between TDC Pulse Time and ADC Pulse Amplitude.
 \item Cable Time Corrections, $t_{Cable}$: This correction takes into account the fact that the analog signal has
@@
 time and distance is fitted to extract the propagation velocity and the cable time difference between the two ends. (See Figure \ref{fig:Vp_fit})
-The cable time offset parameter is determined for all paddles and the parameter is read by hcana, and added as a correction
+The cable time offset parameter is determined for all paddles and the parameter is read by \texttt{hcana}, and added as a correction
 factor to the time-walk corrected TDC time. 
@@
   time across both ends of the scintillator paddle from the particle hit location. The corrections is
-  done in the Hall C Analyzer, \textit{hcana}. Some of the geometrical parameters that are used are shown
+  done in the Hall C Analyzer, \texttt{hcana}. Some of the geometrical parameters that are used are shown
   in Figure \ref{fig:propTime}. \\
@@
   \end{figure}
-  To derive how this correction is done in hcana, let the time-walk and cable length corrected time be
+  To derive how this correction is done in \texttt{hcana}, let the time-walk and cable length corrected time be
   defined as
@@
     \end{align}
-    The equations used in hcana are
+    The equations used in \texttt{hcana} are
     \begin{align}\label{eq:11}
@@
   \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_TWcalib\_runNUM.param}}
-  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
+  This parameter file name has to be manually changed to exclude the run number, since \texttt{hcana} reads in the parameter file as
   \texttt{(p)hhodo\_TWcalib.param} .
@@
   \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_Vpcalib\_runNUM.param}} \\
-  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
+  This parameter file name has to be manually changed to exclude the run number, since \texttt{hcana} reads in the parameter file as
   \texttt{(p)hhodo\_Vpcalib.param} .

### 2022-01-18 MY_THESIS_DOCS/HallC_12GeV_Trigger/version2/trigger_v2.tex
re-structure

--- 2019-07-17 MY_THESIS/HallC_12GeV_Trigger/version2/trigger_v2.tex
@@
   \centering
-  \includegraphics[scale=0.5]{hHODO_diagram.png}
+  \includegraphics[scale=0.5]{../hHODO_diagram.png}
   \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}

### 2022-01-18 PRL_UTILITIES_CODES/PRL_addendum/JVO_datafiles/deForest_Xsec.py

@@ -1,209 +1,0 @@
-#Code to calculate the deForest Cross Sections from the proton GMp, GEp form
-#factors
-
-import LT.box as B
-import numpy as np
-    
-#Define Physical Constnats
-hbarc = 197.327053       #MeV * fm
-alpha = 1./137.0359895    #structure constant
-dtr = np.pi / 180.
-
-#Masses in MeV
-MP = 938.272
-MN = 939.566
-MD = 1875.61
-me = 0.51099; 
-
-#define the proton magnetic form factor (See physics_proton.f)
-#Assumes Q2 is in MeV2
-def GMp(Q2, param=''):
-    
-    Q2 = Q2*1e-6    #convert from MeV2 to GeV2
-    #Four momentum transfer to various powers (units GeV^{power})
-    Q = np.sqrt(Q2)
-    mu_p = 2.793      #proton magnetic moment
-    
-    #Peter Bosted Parametrization
-    if param=='bosted':
-        Q3 = Q**3
-        Q4 = Q**4
-        Q5 = Q**5    
-        denom =  1. + 0.35*Q + 2.44*Q2 + 0.5*Q3 + 1.04*Q4 + 0.34*Q5
-        GMp = mu_p / denom
-        
-    #John R. Arrington Parametrization
-    if param=='JRA':
-        Q22 = Q2**2 
-        Q23 = Q2**3 
-        Q24 = Q2**4 
-        Q25 = Q2**5 
-        Q26 = Q2**6 
-        
-        GMp = mu_p/(1. + Q2 * (3.19) + Q22 * (1.355) + Q23 * (0.151) + Q24 * (-0.114E-01) + Q25 * (0.533E-03) + Q26 * (-0.900E-05) )
-        
-    return GMp
-
-#define the proton electric form factor
-#Assumes Q2 input is in MeV2
-def GEp(Q2, param=''):
-    #print ('Calculating Electric Form factor')
-    
-    Q2 = Q2*1e-6    #convert from MeV2 to GeV2
-    
-    #Four momentum transfer to various powers (units GeV^{power})
-    Q = np.sqrt(Q2)
-    
-    #Peter Bosted Parametrization
-    if param=='bosted':
-        Q3 = Q**3
[…]

### 2022-01-18 PRL_UTILITIES_CODES/PRL_addendum/MS_datafiles/make_prl_addendum.py

@@ -1,79 +1,0 @@
-#This script prepares the PRL addendum data files in the correct formats / units
-
-
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-
-def make_prl_addendum(model='', thnq=0):
-
-    #input file to read
-    fname = 'theoryXsec_%sFSI_thnq%.2f.data' % (model, thnq)
-
-    #output file to write
-    fname_out = 'theory_MS%s_thnq%d_test.txt' % (model, thnq)
-    
-    #open file to write results:
-    ofile = open(fname_out, 'w')
-    header = """ 
-    # Misak Sargsian (MS %s) theoretical cross sections and reduced cross sections as a function of missing momentum
-    # 
-    # theta_nq = %d (deg)
-    #
-    # header definitions
-    #
-    # pm_bin            : missig momentum bin center (GeV/c) (bin width from center is +/- 0.02 GeV)
-    # pm_avg            : average missing momentum over pm_bin (GeV/c)
-    # theory_pwiaXsec      : theoretical cross section using the MS CD-Bonn PWIA model ( nb / (MeV Sr^2) ) 
-    # theory_fsiXsec       : theoretical cross section using the MS CD-Bonn FSI model ( nb / (MeV Sr^2) )
-    # theory_red_pwiaXsec  : theoretical reduced cross section using the MS CD-Bonn PWIA model (fm^3) 
-    # theory_red_fsiXsec   : theoretical reduced cross section using the MS CD-Bonn FSI model (fm^3)
-    
-    #! pm_bin[f,0]/ pm_avg[f,1]/ theory_pwiaXsec[f,2]/ theory_fsiXsec[f,3]/  theory_red_pwiaXsec[f,4]/ theory_red_fsiXsec[f,5]/  setting[s,6]/ 
-    """
-
-    ofile.write(header % (model, thnq))
-
-    # Conversion factor:  1 fm = 1/ (197 MeV),   
-    # The reduced cross section is in MeV^-3 units
[…]

### 2022-01-18 PRL_UTILITIES_CODES/PRL_addendum/compare.py

@@ -1,180 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-MeV2fm = 197.3**3 
-GeV2fm = 0.1973**3 
-#1 fm = (1/197.3) MeV^-1
-
-
-#READ WB pm_35 deg
-#Conversion factor: 1 fm = 1 / (0.1973 GeV)  or  1 fm^-1 = 0.1973 GeV
-fminv2GeV = 1./(1./0.1973)
-GeV2fm = 0.1973**3  #inverse fermi^3 to GeV^3
-
-fname_wb = "WB_PRLaddendum_Xsec/pm_distribution_results_q4_35.00.data"
-#kin = dfile(fname_wb)
-
-#p_miss = np.array(kin['p_miss'])/1000.   # in GeV
-#th_e = np.array(kin['th_e'])                #in deg
-#Ei = np.array(kin['Ei'])              #in MeV
-#omega = np.array(kin['omega'])        #in MeV
-#qlab = np.array(kin['qlab'])         #in MeV
-#pf = np.array(kin['pf'])             #in MeV
-#sig_red_exp = np.array(kin['sig_red_exp']) 
-#y = np.zeros(len(th_e))
-
-#Read addendum data from WB
-def get_avg_kinWB(header, ithnq):
-    fname = 'WB_PRLaddendum_Xsec/pm_distribution_results_q4_%i.00.data'%(ithnq)
-    kin = dfile(fname)
-    arr = (np.array(kin[header]))
-    return arr
-
-#-------READ CURRENT FILE-------
-#Get average kinematics
-def get_avg_kin(header, pm, data_set, ithnq ):
-    if pm==80:
-        fname = 'pm%i_laget_bc_corr.txt'%(pm)
-    else:
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/HallA_data/sig_deutpwia/relkin.f

@@ -1,75 +1,0 @@
-      subroutine relkin(omega,qlab,cth, 
-     &                 conv,cthnpc,enp,qc,ppp,ppi,lerr)
-      implicit double precision (a-h,o-z)
-c
-c 
-c calculates the relevant kinematic variables in the center of 
-c mass system and the final and initial proton momenta in the 
-c laboratory frame. 
-c 
-c the input varable cth = cos (theta) where theta is the angle 
-c between q and the out coming proton. 
-c cthnpc is the cosine of the theta-np angle in the cms frame 
-c 
-      real*8 ml,kl2sq 
-      logical lerr
-      
-      include 'constants.h'
-
-      dtr=pi/180. 
-      rtd=180./pi 
-c 
-c calcualate final momentum 
-c 
-      ql=qlab
-      e0=md+omega 
-      a0=ql**2-e0**2-mp**2+mn**2 
-      a=4*e0**2-4*ql**2*cth**2 
-      b=4*ql*a0*cth 
-      c=4*e0**2*mp**2-a0**2 
-      discr=b**2-4*a*c
-      if (discr.lt.0) then
-         lerr=.true.
-         return
-      endif
-      ppp=(-b+sqrt(b**2-4*a*c))/2/a 
-c other solution
-      ppp2=(-b-sqrt(b**2-4*a*c))/2/a 
-c      print *, ' sol. 1 :', ppp, ' sol2 : ', ppp2
-c 
-c calculate theta-np lab and the initial momentum 
-c 
-      fak1=-0.5*(ql-2*ppp*cth)
-      fak2=sqrt(ppp**2+(ql/2)**2-ppp*ql*cth)
-      cthnpl=fak1/fak2
-      kl2sq=ppp**2+(ql/2)**2-ppp*ql*cth
-      ppi=sqrt(kl2sq+(ql/2)**2-sqrt(kl2sq)*ql*cthnpl)
-c
-c make a Lorentz tranformation to the CMS frame
-c
-      beta=ql/(md+omega)
-      gamma= 1/sqrt(1-beta**2)
-c
-      qc=gamma*(ql-beta*omega)
-      wc=gamma*(omega-beta*ql)
-c
-      cthnpc=md*cthnpl/sqrt(md**2+qc**2-qc**2*cthnpl**2)
-c 
-c calculate invariant mass
-c
-      et=sqrt((omega+md)**2-ql**2)
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/HallA_data/test.py

@@ -1,21 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-
-
-#1 fm^-1 = 0.1973 GeV
-
-GeV2fm = 0.197**3    #convert GeV^-3 to fm^3
-
-kin = dfile('new_halla/mom_dist_cdbonn_mevc.data')
-
-pm = kin['pm']   #pmiss is in MeV/c
-rho = kin['rho'] * GeV2fm  #momentum distributions in 1 / GeV^3
-

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/get_words.py

@@ -1,29 +1,0 @@
-import numpy as np
-import sys
-
-def get_words(w=0, h=0, ncol=0):
-    #PRL counts figure sizes as words, for which there is a conversion factor.
-    
-    fig_w = float(w)  #figure width (inches)
-    fig_h = float(h)  #figure height (inches)
-    aspect_ratio = fig_w / fig_h;
-
-    if(ncol==1):
-        #For single column figures, the word estimate for a figure size is:
-        one_column_fig_words = (150./aspect_ratio) + 20.  #units: number of words
-        print('aspect ratio = ', aspect_ratio)
-        print('(single column) # of words equivalent for figsize: (w=',w,' h=', h,') in. -----> ',one_column_fig_words,' words')
-    elif(ncol==2):
-        #For figures that occupy both columns of the paper, the word estimate for a figsize is:
-        two_column_fig_words = (300./(0.5*aspect_ratio) ) + 40. 
-        print('aspect ratio = ', aspect_ratio)
-        print('(two columns) # of words equivalent for figsize: (w=',w,' h=', h,') in. -----> ',two_column_fig_words,' words')
-
-
-if __name__ == '__main__':
-    w = float(sys.argv[1])
-    h = float(sys.argv[2])
-    ncol = int(sys.argv[3])
-    
-    #print('w = ',w, 'h=',h, 'ncol=',ncol)
-    get_words(w, h, ncol)

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/main.py

@@ -1,3 +1,0 @@
-from test import *
-
-printName()

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/make_prl_plots.py

@@ -1,827 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-from scipy.optimize import least_squares
-from scipy.optimize import curve_fit
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-from prl_utilities import *
-#from prl_utilities_test import *
-
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def make_prl_plots(plot2_inset=0):
-
-    #Read projected relative errors for full deuteron experiment (from simulations, at 120, 700,800,900 MeV/c)
-    #  (to compare with PRL data and see how much improvement there is.
-    kin35 = dfile('d2_projected_errors_thnq35deg.txt')
-    kin45 = dfile('d2_projected_errors_thnq45deg.txt')
-    kin75 = dfile('d2_projected_errors_thnq75deg.txt')
-    rel_stats_err35 = kin35['rel_stats_err']
-    rel_stats_err45 = kin45['rel_stats_err']
-    rel_stats_err75 = kin75['rel_stats_err']
-
-    pm_bin_35_proj = kin35['pm_bin']
-    pm_bin_45_proj = kin45['pm_bin']
-    pm_bin_75_proj = kin75['pm_bin']
-    
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/make_prl_plots_smallplots.py

@@ -1,1139 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-#from prl_utilities import *
-from prl_utilities_test import *
-
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def make_prl_plots(plot2_inset=0):
-  
-    #Read Hall C (E12-10-003) experimental data (requires <=50% statistical uncertainty, units: fm^3, GeV/c)
-    pm_bin35, pm_avg35, red_dataXsec_avg_masked35, red_dataXsec_avg_tot_err35 = read_hallc_data(35)
-    pm_bin45, pm_avg45, red_dataXsec_avg_masked45, red_dataXsec_avg_tot_err45 = read_hallc_data(45)
-    pm_bin75, pm_avg75, red_dataXsec_avg_masked75, red_dataXsec_avg_tot_err75 = read_hallc_data(75)
-
-    #Read Hall A experimental data
-    pm_ha35, red_dataXsec_ha35, red_dataXsec_err_ha35 = read_halla_data(35)
-    pm_ha45, red_dataXsec_ha45, red_dataXsec_err_ha45 = read_halla_data(45)  
-    pm_ha75, red_dataXsec_ha75, red_dataXsec_err_ha75 = read_halla_data(75) 
-
-    #Read Theoretical calculations
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/prl_utilities_test.py

@@ -1,227 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-#Define utility functions for generating PRL plots
-
-
-#Conversion factor:  1 fm = 1/ (197 MeV),   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-#___________________________________________________
-def convert2NaN(arr=np.array([]), value=0):
-
-    #Function to convert a specified value in a array to nan (not a number)
-
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-#___________________________________________________
-def read_halla_data(thnq=0):
-
-    #Function to read data files containing momentum distributions from Hall A
-
-    #Conversion factor: 1 fm = 1 / (0.1973 GeV)  or  1 fm^-1 = 0.1973 GeV
-    #fminv2GeV = 1./(1./0.1973)
-    ifm2GeV = 0.1973  #inverse fermi to GeV
-
-    thnq_f = '%.1f' % (thnq)
-
-    #Hall A data filename
-    fname = './HallA_data/pm_distribution_results_q3_1_%s.data' % (thnq_f) 
-    kin = dfile(fname)
-
-    #Pm here is not the central bin value, but an average over that bin
-    p_miss = np.array(kin['p_miss_av']) * ifm2GeV    
-    red_dataXsec = np.array(kin['rho'])             #units fm^3
-    red_dataXsec_err = np.array(kin['delta_rho'])
-
-    return p_miss, red_dataXsec, red_dataXsec_err
-
-
-#_____________________________________________________
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/theoretical_models/averages.py

@@ -1,109 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Thu Oct 10 10:46:02 2019
-
-Tools for calculating averages
-
-@author: boeglinw
-"""
-
-import numpy as np
-
-#---------------------------------------------------------------------- 
-def get_bin_id(d):
-    kins = d['kin']
-    ix = np.array(d['ix']).astype(int)
-    iy = np.array(d['iy']).astype(int)
-    id_s = []
-    for i, k in enumerate(kins): 
-        id_s.append( '{:d}_{:d}_{:s}'.format( ix[i], iy[i], k.strip()))
-    return np.array(id_s)
-# necessary tools to calculate averages and remove duplicates
-#----------------------------------------------------------------------
-def remove_duplicates(array):
-    na = []
-    for a in array:
-        try:
-            na.index(a)
-        except:
-            na.append(a)
-    return na
-
-#----------------------------------------------------------------------
-def find_duplicates(np_array):
-    # np_array is a numpy array
-    # return a list with np_array values that contain no duplicates and a
-    # corresponding list of indices pointing to identical values in np_array
-    array_no_duplicates = remove_duplicates( list(np_array) )
-    # sort the array 
-    array_no_duplicates.sort()
-    index_list = []
-    for a in array_no_duplicates:
-        in_dup = np.where(np_array == a)[0]
-        index_list.append( list(in_dup) )
-    return array_no_duplicates, index_list
-
-#----------------------------------------------------------------------
-def get_averages(pm, sig, dsig):
-    # calculate the weighted mean of sig and pm where the weight
-    # is given by 1./dsig**2
-    weight = 1./dsig**2
-    sig_av = np.sum(sig*weight)/np.sum(weight)
-    pm_av = np.sum(pm*weight)/np.sum(weight)
-    dsig_av_sq = 1./np.sum(weight)
-    dsig_av = np.sqrt( dsig_av_sq)
-    # include the chi2 of the weighted mean in the error
-    if (len(pm) > 1):
-        chi2 = (1./(len(pm) - 1.)) * np.sum( (sig-sig_av)**2*weight )
-        dsig1_av = np.sqrt( dsig_av_sq * chi2 )
-    else:
-        dsig1_av = dsig_av
-    return pm_av, sig_av, dsig_av, dsig1_av
-#----------------------------------------------------------------------
-   
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/PRL_plots_codes/theoretical_models/plot_pm_distribution_q4.py

@@ -1,641 +1,0 @@
-# compare the experimental red. cross sections as 
-# a function of pm with the calculated ones 
-#
-# 
-# plot for q1
-#
-# The script assumes that all calculations have been
-# based on the kinematics in the exp. file
-#
-
-
-from LT.datafile import dfile
-import numpy as np
-import plotting2 as pl
-
-import match_arrays as MA
-import match_string_arrays as MSA
-
-import pdb
-from itertools import cycle, islice
-
-hbarc = 197.33
-Mp = 0.93827
-
-# momentum distributions
-"""
-d_paris = dfile('../exp_results/nk_paris.data')
-d_cdbonn = dfile('../exp_results/nk_bonn.data')
-d_v18 = dfile('../exp_results/v18_mom_dist_short.data')
-"""
-
-fm_to_mev = 197.33
-
-# control dashes
-dashes0 = (10,3)  # 10 points on, 1 point off, 2 point on, 1 point off etc.
-dashes1 = (5,3)  # 5 points on, 1 point off
-dashes2 = (5,1)  # 5 points on, 1 point off
-dashdot1 = (5,1,1,1)  # 5 points on, 2 point off, 2 point on
-dashdot2 = (20,5,5,5)  # 
-dots1 = (1,1)  #
-dots2 = (2,1)  #
-dots3 = (5,2)  #
-# solid = (None,None)
-solid = []
-
-exp_color = 'k'
-CD_color = (0.0,0.,1.)
-V18_color= (1., 0., 1.)
-paris_color = (0.,.8, 0.)
-
-
-line_w = 1.75
-
-
-#---------------------------------------------------------------------- 
-# colors
-my_colors = ['b','g','r','c','m','y','k']
-
-my_markers_dict = {'circle':'o',\
-              'tri_down':'v',\
-              'tri_left':'<', \
-              'tri_right':'>', \
-              'tri_up':'^', \
-              'square':'s', \
-              'star':'*', \
-              'pentagon':'p', \
-              'hex1':'h', \
-              'hex2':'H', \
-              'diamond':'D', \
-              'diamond1':'d'}
-
-my_markers =  ['o',\
-              'v',\
-              '<', \
-              '>', \
-              '^', \
-              's', \
-              '*', \
-              'p', \
-              'h', \
-              'H', \
-              'D', \
-              'd']
-# markers for the various theta settings
-theta_markers = {'35':'o', \
-               '45':'^', \
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/HallA_data/sig_deutpwia/dlocate.f

@@ -1,18 +1,0 @@
-      SUBROUTINE DLOCATE(XX,N,X,J)
-      IMPLICIT REAL*8 (A-H,O-Z)
-      DIMENSION XX(N)
-      JL=0
-      JU=N+1
-10    IF(JU-JL.GT.1)THEN
-        JM=(JU+JL)/2
-        IF((XX(N).GT.XX(1)).EQV.(X.GT.XX(JM)))THEN
-          JL=JM
-        ELSE
-          JU=JM
-        ENDIF
-      GO TO 10
-      ENDIF
-      J=JL
-      RETURN
-      END
-

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/HallA_data/sig_deutpwia/sig_deutpwia.f

@@ -1,133 +1,0 @@
-c this program calculates the ee'p cross section in the PWIA for
-c deuterium. 
-c the parameterization of the paris potential momentum distribution
-c
-c this is the same basic code as the one for the deutpwia1 and deutpwia1_sub
-
-      real*8 function sig_deutpwia(
-c input
-     >     e0, omega, thee,
-     >     theta_p, phi_p, angle_type )
-
-
-      implicit real*8 (a-h,o-z)
-      real*8 md,mn,mp,mnp,klab,ml ,kfact,k1,k2
-      real*8 k_i(4), k_f(4), p_f(4)
-      logical first,lerr
-      integer angle_type, spec_pos
-      character nucleon*1,cread*1
-
-c output
-      common /results/
-     >     rho, kfact, sigep, sigma, f_rec,
-     >     thq, ppi, ppf, enp, qc, cthnpc, qlab
-      
-      data amu/931.48/,hbarc/197.33/,pi/3.1415927/,first/.true./
-      data rpa/1.75d-5/
-
-      data spec_pos/1/
-
-      md=2.014*amu 
-      mn=1.0087*amu 
-      mp=1.0073*amu 
-      dtr=pi/180. 
-      rtd=180./pi 
-c
-      einc=e0
-      thee=thee*dtr
-      nucleon = 'p'
-
-c
-c kinematic for deuterium
-c
-      k1=einc 
-      k2=(einc-omega) 
-c 
-      qnue2=4*k1*k2*(sin(thee/2))**2 
-      qlab2=k1**2+k2**2-2*k1*k2*cos(thee) 
-      qlab=sqrt(qlab2)
-c theta-q
-      cthq=(e0-(e0-omega)*cos(thee))/qlab
-      thq=acos(cthq)
-
-c handle angle types
-      if ( angle_type .eq. spec_pos) then
-         theta = theta_p
-         phi = phi_p
-         theta=theta*dtr
-         phi=phi*dtr 
-         cth=cos(phi)*cos(thq-theta)
-      else
-         thnp = theta_p
-         phinp = phi_p
-         thnp=thnp*dtr
-         phinp=phinp*dtr
-c
-         cth=cos(thnp)
-         phi=asin(sin(thnp)*sin(phinp))
-         beta=acos(cth/cos(phi))
-c
-         diff=phinp-pi/2
-c
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/Rad_BC_corr_plots/check_RCBC_ratio.py

@@ -1,339 +1,0 @@
-#This code check the ratio of norad / rad for PWIA and FSI
-
-from LT.datafile import dfile
-import LT.box as B
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.pyplot import rc
-import matplotlib.ticker as tic
-import sys
-import os
-import numpy.ma as ma
-
-'''
-#Set Global Param
-params = {'legend.fontsize': 14,
-          'lines.markersize': 9.0,
-           'legend.markerscale':1.,
-          'figure.figsize': (9, 7),
-         'axes.labelsize': 20,
-         'axes.labelweight': 'bold',          
-         'axes.titlesize':22,
-          'axes.titleweight':'bold',
-          'axes.linewidth':2,
-         'xtick.major.width':2,
-          'ytick.major.width':2,          
-         'xtick.labelsize':20,
-          'ytick.labelsize':20} 
-           
-plt.rcParams.update(params)
-'''
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'bold',
-        'size'   : 14
-}
-plt.rc('font', **font)
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#User Input (Usage: python check_RC_ratio.py 80 1 )
-pm_set = int(sys.argv[1])
-data_set = int(sys.argv[2])
-
-#csfont = {'fontname':'Times New Roman'}
-
-plt.rcParams["font.family"] = "Times New Roman"
-
-
-#Read data file
-if pm_set==80:
-    fname = './pm%i_laget_RCratio.txt' % (pm_set)
-else:
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/backup_old/make_prl_plots.py

@@ -1,775 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-
-matplotlib.use('Agg')
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#Conversion factor:  1 fm = 1/ (197 MeV),   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-#User Input (Dir. Name to store output)
-sys_ext = sys.argv[1]   
-    
-dir_name = sys_ext+"_plots"
-dir_name_misc = dir_name + "/misc_plots"        #directory to store miscellaneous plots (trigger rates, live time, etc. . .) #obtained from the report files
-print(dir_name)
-#check if directory exists, else creates it.
-if not os.path.exists(dir_name):
-    os.makedirs(dir_name)
-if not os.path.exists(dir_name_misc):
-    os.makedirs(dir_name_misc)
-     
-
-#Get Reduced Xsec Data File
-fname = './%s/redXsec_combined.txt'%(sys_ext)
-f = B.get_file(fname)
-
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/deep_utilities.py

@@ -1,1791 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-#Conversion factor:  1 fm = (1/197.3) MeV^-1,   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-matplotlib.use('Agg')
-plt.ioff() # prevent plots froms displaying
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'bold',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-
-def convert2NaN(arr=np.array([]), value=0):
-
-    #method to convert a specified value in a array to nan (not a number)
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#========User Input (Dir. Name to store output)=======
-#usage: ipython plot_momentum_dist.py
-
-dir_name1 = "thesis_redXsec_plots"
-dir_name2 = "thesis_relError_plots"
-dir_name3 = "thesis_kin_tables"
-
-#check if directory exists, else creates it.
-if not os.path.exists(dir_name1):
-    os.makedirs(dir_name1)
-if not os.path.exists(dir_name2):
-    os.makedirs(dir_name2)
-if not os.path.exists(dir_name3):
-    os.makedirs(dir_name3)     
-
-
-def get_kin_syst(header_name, pm_set, data_set, Q2_set, ithnq, ipm):
-    #Code to get any header and data array from the kin. systematic data files
-    #User: Q2 = '3to4', or '4to5'
-    
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/plot_momentum_dist.py

@@ -1,2102 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-
-#matplotlib.use('Agg')
-#plt.ioff() # prevent plots froms displaying
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'bold',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#Conversion factor:  1 fm = 1/ (197.3 MeV),   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-GeV2fm = 0.1973**3   #conver GeV^-3 to fm^3
-#========User Input (Dir. Name to store output)=======
-#usage: ipython plot_momentum_dist.py
-
-dir_name1 = "thesis_redXsec_plots"
-dir_name2 = "thesis_relError_plots"
-dir_name3 = "thesis_kin_tables"
-
-#check if directory exists, else creates it.
-if not os.path.exists(dir_name1):
-    os.makedirs(dir_name1)
-if not os.path.exists(dir_name2):
-    os.makedirs(dir_name2)
-if not os.path.exists(dir_name3):
-    os.makedirs(dir_name3)     
-
-
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/THESIS/theoretical_models/calc_redXsec.py

@@ -1,158 +1,0 @@
-#This code reads the theory data files (grouped in th_nq bins) and divided by
-#the corresponding Ksig_cc1 to get the reduced Xsec
-
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import sys           
-import os                                                      
-from sys import argv  
-
-
-#Conversion Factors
-dtr = np.pi / 180.
-nb2ub = 1./1000.    # 1ub = 1000 nb
-GeV2MeV = 1000.  # 1 GeV = 1000 MeV
-
-#-----------------USER INPUT-------------------------------------
-model_dir = "./FSI_models/"    #PWIA_models or FSI_models
-#-----------------------------------------------------------------
-
-if(model_dir=="./PWIA_models/"):
-    model_name = "2_1_1_0_1"  #2_1_1_0_1 = V18 Potential, 3_1_1_0_1 = CD-Bonn     #!!!!! USER SET BY HAND
-    
-    #Create Base Name & Directory to Store Update Files
-    if(model_name=="2_1_1_0_1"):
-        updated_model_name = "V18"
-    if(model_name=="3_1_1_0_1"):
-        updated_model_name = "CD-Bonn"
-    updated_base="theoryXsec_" + updated_model_name + "PWIA"
-
-    output_dir_name = "./updated_PWIA_models/"
-    if not os.path.exists(output_dir_name):
-        os.mkdir(output_dir_name)
-
-elif(model_dir == "./FSI_models/"):
-    model_name = "2_1_1_0_12"  #2_1_1_0_12 = V18 Potential, 3_1_1_0_12 = CD-Bonn,  12 -> PWIA+ FSI    #USER SET BY HAND
-
-    #Create Base Name & Directory to Store Update Files
-    if(model_name=="2_1_1_0_12"):
-        updated_model_name = "V18"
-    if(model_name=="3_1_1_0_12"):
-        updated_model_name = "CD-Bonn"
-    updated_base="theoryXsec_" + updated_model_name + "FSI"
-    output_dir_name = "./updated_FSI_models/"
-    if not os.path.exists(output_dir_name):
-        os.mkdir(output_dir_name)
-
-base = "csec_calc_theta_pm_"
-base2="_fsi_norad_avgkin_"
-
-
-thnq_arr = np.array([5, 15, 25, 35, 45, 55, 65, 75, 85, 95, 105])
-
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_codes/add_hist.C

@@ -1,182 +1,0 @@
-#include "../plotting_utilities/histUtils.C"   //load utilities code for histo plotting
-
-//Script to make comparison between SIMC and Commissioning Data from HallC Spring 2018
-//The comparisons are all charge normalized and corrected for all inefficiencies
-
-void add_hist()
-{
-  
-  //gROOT->SetBatch(kTRUE);  
-  //gStyle->SetOptStat(1001111);
-  gStyle->SetOptStat(0000000);
-  string thnq_set;
-  string root_dir_1;
-  string root_dir_2;
-
-  string root_dir_3;
-  string root_dir_4;
-  string root_dir_10;
-  string root_dir_20;
-  /*
-  //Deep 580 MeV,  Em_cut (-0.1, -0.04)  -- draw background
-  root_dir_1 = "../../root_files/bkg_study_deep_580set1_Em_cut2/deep_data_histos_pm580_set1_combined.root";
-  root_dir_2 = "../../root_files/bkg_study_deep_580set2_Em_cut2/deep_data_histos_pm580_set2_combined.root";
-
-  //Deep 580 MeV em_cut (-0.02, 0.04)  -- draw data+background
-  root_dir_3 = "../../root_files/bkg_study_deep_580set1_Em_cut1/deep_data_histos_pm580_set1_combined.root";
-  root_dir_4 = "../../root_files/bkg_study_deep_580set2_Em_cut1/deep_data_histos_pm580_set2_combined.root";
-  */
-  //Deep 750 MeV,  Em_cut (-0.1, -0.04)  -- draw background
-  root_dir_1 = "../../root_files/bkg_study_deep_750set1_Em_cut1/deep_data_histos_pm750_set1_combined.root";
-  root_dir_2 = "../../root_files/bkg_study_deep_750set2_Em_cut1/deep_data_histos_pm750_set2_combined.root";
-  root_dir_10 = "../../root_files/bkg_study_deep_750set3_Em_cut1/deep_data_histos_pm750_set3_combined.root";
-
-  
-  //Deep 750 MeV em_cut (-0.02, 0.04)  -- draw data+background
-  root_dir_3 = "../../root_files/bkg_study_deep_750set1_Em_cut2/deep_data_histos_pm750_set1_combined.root";
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_codes/compare_deep.C

@@ -1,189 +1,0 @@
-#include "../plotting_utilities/histUtils.C"   //load utilities code for histo plotting
-
-//Script to make comparison between SIMC and Commissioning Data from HallC Spring 2018
-//The comparisons are all charge normalized and corrected for all inefficiencies
-
-void compare_deep(int pm, int set, int thnq)
-{
-
-  //gROOT->SetBatch(kTRUE);  
-  //gStyle->SetOptStat(1001111);
-  gStyle->SetOptStat(0000000);
-  string thnq_set;
-  string root_dir;
-  if(thnq==-1){
-    thnq_set = "all_thnq_Q2_4to5";
-    //thnq_set = "all_thnq_Q2_4to5_WideEmBINS";
-  }
-
-  else{thnq_set = Form("thnq%d_Q2_4to5", thnq);}
-
-  
-  if(thnq==-1){root_dir = Form("../../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());}
-  else{root_dir = Form("../../root_files/pm%d_fsiXsec_set%d_%s/", pm, set, thnq_set.c_str());}
-  string simc_fname = Form("deep_simc_histos_pm%d_lagetfsi_rad_set%d.root", pm, set);
-  string data_fname = Form("deep_data_histos_pm%d_set%d_combined.root", pm, set);
-    
-  TString simc_filename_fsi = root_dir+simc_fname;
-  TString data_filename = root_dir+data_fname;
-  cout << simc_filename_fsi << endl;
-  cout << data_filename << endl;
-  //Open SIMC/data ROOT files;
-  TFile *simc_file_fsi = new TFile(simc_filename_fsi);
-  TFile *data_file = new TFile(data_filename);
-
-
-  //-------------Spectrometer Acceptance Plots--------
-  
-  //FSI
-  TH1F *simc_eytar_fsi =  0;
-  TH1F *simc_exptar_fsi =  0;
-  TH1F *simc_eyptar_fsi =  0;
-  TH1F *simc_edelta_fsi =  0;
-
-  TH1F *simc_hytar_fsi =  0;
-  TH1F *simc_hxptar_fsi =  0;
-  TH1F *simc_hyptar_fsi =  0;
-  TH1F *simc_hdelta_fsi =  0;
-
-  
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_codes/plot_combined_sets.C

@@ -1,87 +1,0 @@
-#include "../plotting_utilities/histUtils.C"   //load utilities code for histo plotting
-
-void plot_combined_sets(int thnq=0)
-{
- gStyle->SetOptStat(0000000);
-
- //set filenames for plotting kinematics
- /*
- string fname_80 = Form("root_files_combined/%d_deg/deep_data_histos_pm80_set1_combined.root", thnq);
- string fname_580_set1 = Form("root_files_combined/%d_deg/deep_data_histos_pm580_set1_combined.root",thnq);
- string fname_580_set2 = Form("root_files_combined/%d_deg/deep_data_histos_pm580_set2_combined.root", thnq);
-
- string fname_750_set1 = Form("root_files_combined/%d_deg/deep_data_histos_pm750_set1_combined.root", thnq);
- string fname_750_set2 = Form("root_files_combined/%d_deg/deep_data_histos_pm750_set2_combined.root", thnq);
- string fname_750_set3 = Form("root_files_combined/%d_deg/deep_data_histos_pm750_set3_combined.root", thnq);
- */
-
- /*
- //set filenames for plotting Missing Momentum yield (rad. corrected)
- string fname_80 = Form("../../root_files/pm80_fsiXsec_set1_thnq%d_Q2_4to5/deep_data_histos_pm80_set1_combined_radcorr.root", thnq);
-
- string fname_580_set1 = Form("../../root_files/pm580_fsiXsec_set1_thnq%d_Q2_4to5/deep_data_histos_pm580_set1_combined_radcorr.root",thnq);
- string fname_580_set2 = Form("../../root_files/pm580_fsiXsec_set2_thnq%d_Q2_4to5/deep_data_histos_pm580_set2_combined_radcorr.root",thnq);
-
- string fname_750_set1 = Form("../../root_files/pm750_fsiXsec_set1_thnq%d_Q2_4to5/deep_data_histos_pm750_set1_combined_radcorr.root",thnq);
- string fname_750_set2 = Form("../../root_files/pm750_fsiXsec_set2_thnq%d_Q2_4to5/deep_data_histos_pm750_set2_combined_radcorr.root",thnq);
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_data_files/JWVOrden_calculations/calc_redXsec.py

@@ -1,207 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-from deForest_Xsec import *   #import deForest sig_cc1, mott, GMp, GEp functs.
-from itertools import groupby
-
-# some constants
-dtr = np.pi/180.
-hbarc = 197.327053       #MeV * fm
-
-#particle masses (MeV)
-MP = 938.272 
-MN = 939.566 
-MD = 1875.61 
-me = 0.51099 
-
-
-thnq = 75
-#read data from Wally V. Orden calculations
-f = dfile('./%i_deg.data' % (thnq) )
-
-#read avg. kinematics to calculate the recoil factors to determine the reduced cross sections
-ib = np.array(f['Nr'])
-pm_avg = np.array(f['pm_avg']) * 1000.  #recoil neutron momentum [MeV/c]
-Eb = np.array(f['Eb']) #beam energy, MeV
-Q2 = np.array(f['Q2']) * 1e6   #Q2, MeV^2
-x = np.array(f['x'])   #X-Bjorken
-nu = Q2 / (2*MP*x)    #nu = Eb - kf, energy transfer MeV
-kf = Eb - nu          #final electron energy (or momentum), MeV
-th_e = np.array(f['th_e'])  #e- scattering angle (deg)
-q = np.sqrt(Q2 + nu*nu)  #magnitude of 3-momentum transfer, MeV
-pf = np.array(f['pf'])    #final proton momentum , MeV
-ph_pq = np.array(f['phi'])   #deg
-
-cphi_pq = np.cos(ph_pq * dtr)
-theta_q = np.arccos((Eb**2 + q**2 - kf**2) / (2.*Eb*q))   #radians
-theta_pq = np.arccos((pf**2 + q**2 - pm_avg**2)/(2.*pf*q))   #radians
-theta_nq = np.arccos((q - pf*np.cos(theta_pq))/pm_avg)       #radians
-theta_p = theta_q + theta_pq                             #radians
-
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_data_files/JWVOrden_calculations/read_digitized.py

@@ -1,109 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-from deForest_Xsec import *   #import deForest sig_cc1, mott, GMp, GEp functs.
-
-# some constants
-dtr = np.pi/180.
-hbarc = 197.327053       #MeV * fm
-
-#particle masses (MeV)
-MP = 938.272 
-MN = 939.566 
-MD = 1875.61 
-me = 0.51099 
-
-model = "PWIA"
-
-#Digitized data of PWIA 24 calculations from Wally V. Orden (2014 article)
-f = dfile('Digitize_Deepn/%s_digitized.data' % (model) )
-
-Pm = np.array(f['xpw'])  #recoil neutron momentum [GeV/c]
-theory_Xsec = np.array(f['ypw'])  #5-fold Xsec [GeV^-3 * sr^-2]
-
-#B.plot_exp(x[:13], y[:13], marker='None', linestyle='--', color='b', logy=True)  #lower PWIA
-#B.plot_exp(x[14:], y[14:], marker='None', linestyle='--', color='r', logy=True)  #upper PWIA
-
-#----next steps----
-#Use E12-10-003 kinematics as states in the W.V. Orden (2014) to evalueate K*f_rec*sig_cc1
-#Given the e- kinematics, the proton kinematics is completely defined by the choice of missing momentum
-#Eb = 12 GeV, Q2 = 4.25 GeV2, x = 1.35
-
-#-----FROM  ARTICLE-------
-Eb = 12.*1000.     #incident energy in MeV
-Q2 = 4.25*1e6    #Q2 = 4*Eb*kf*sin^2(theta_e/2) [MeV2]
-x = 1.35     #x = Q2 / 2*MD*nu
-#-------------------------
-
-nu = Q2 / (2*MP*x)    #nu = Eb - kf, energy transfer
-kf = Eb - nu          #final electron energy (or momentum)
-theta_e = 2.*np.arcsin( np.sqrt(Q2 / (4.*Eb*kf)) )
-th_e = theta_e/dtr  #convert to degrees
-q = np.sqrt(Q2 + nu*nu)  #magnitude of 3-momentum transfer
-
-
-print('Eb = ',Eb)
-print('Q2 = ',Q2)
-print('x = ',x)
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_data_files/Q2_4to5GeV/final_Xsec/compare.py

@@ -1,172 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-MeV2fm = 197.3**3 
-GeV2fm = 0.1973**3 
-#1 fm = (1/197.3) MeV^-1
-
-
-#READ WB pm_35 deg
-#Conversion factor: 1 fm = 1 / (0.1973 GeV)  or  1 fm^-1 = 0.1973 GeV
-fminv2GeV = 1./(1./0.1973)
-GeV2fm = 0.1973**3  #inverse fermi^3 to GeV^3
-
-fname_wb = "WB_PRLaddendum_Xsec/pm_distribution_results_q4_35.00.data"
-#kin = dfile(fname_wb)
-
-#p_miss = np.array(kin['p_miss'])/1000.   # in GeV
-#th_e = np.array(kin['th_e'])                #in deg
-#Ei = np.array(kin['Ei'])              #in MeV
-#omega = np.array(kin['omega'])        #in MeV
-#qlab = np.array(kin['qlab'])         #in MeV
-#pf = np.array(kin['pf'])             #in MeV
-#sig_red_exp = np.array(kin['sig_red_exp']) 
-#y = np.zeros(len(th_e))
-
-#Read addendum data from WB
-def get_avg_kinWB(header, ithnq):
-    fname = 'WB_PRLaddendum_Xsec/pm_distribution_results_q4_%i.00.data'%(ithnq)
-    kin = dfile(fname)
-    arr = (np.array(kin[header]))
-    return arr
-
-#-------READ CURRENT FILE-------
-#Get average kinematics
-def get_avg_kin(header, pm, data_set, ithnq ):
-    if pm==80:
-        fname = 'pm%i_laget_bc_corr.txt'%(pm)
-    else:
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/deep_data_files/Q2_4to5GeV/plot_rel_err.py

@@ -1,31 +1,0 @@
-import LT.box as B
-import numpy as np
-from LT.datafile import dfile
-
-f1 = dfile('redXsec_combined_original.txt')
-f2 = dfile('redXsec_combined.txt')
-
-thnq1 = f1['xb']
-p_miss1 = (f1['pm_avg'])[thnq1==35]
-norm_syst_tot1 = (f1['norm_syst_tot'])[thnq1==35]
-y1 = 0. * p_miss1
-
-thnq2 = f2['xb']
-p_miss2 = (f2['pm_avg'])[thnq2==35]
-norm_syst_tot2_35 = (f2['norm_syst_tot'])[thnq2==35]
-norm_syst_tot2_45 = (f2['norm_syst_tot'])[thnq2==45]
-norm_syst_tot2_75 = (f2['norm_syst_tot'])[thnq2==75]
-
-y2 = 0. * p_miss2
-
-
-print('norm_rel_err_35 = ',norm_syst_tot2_35)
-print('norm_rel_err_45 = ',norm_syst_tot2_45)
-print('norm_rel_err_75 = ',norm_syst_tot2_75)
-
-
-#B.plot_exp(p_miss2, y2, norm_syst_tot2*100, marker='s', color='r', label='with tgt. wall / spec. acc systematics')
-#B.plot_exp(p_miss1, y1, norm_syst_tot1*100, marker='o', color='b', label='original')
-
-#B.pl.legend()
-#B.pl.show('same')

### 2022-01-18 PRL_UTILITIES_CODES/codes/heep_codes/compare_heep.C

@@ -1,386 +1,0 @@
-#include "../plotting_utilities/histUtils.C"   //load utilities code for histo plotting
-
-//Script to make comparison between SIMC and Commissioning Data from HallC Spring 2018
-//The comparisons are all charge normalized and corrected for all inefficiencies
-
-void compare_heep(int run)
-{
-
-  //gROOT->SetBatch(kTRUE);  
-  gStyle->SetOptStat(0000000);
-
-
-  //TString root_dir = "../../root_files/pre_HEEP_ELASTICS/";
-  TString root_dir = "../../root_files/HEEP_ELASTICS/";
-
-  //NO CUT and Ztar Diff Cut
-  //TString data_filename = "../../root_files/heep_data_histos_3288_combined.root";    
-  //TString simc_filename = "../../root_files/heep_simc_histos_3288_rad.root";       
-
-  
-  //Q2 4,5 GeV2 CUT
-  //TString data_filename = "heep_data_histos_3288_combined_Q2_4to5.root";    
-  //TString simc_filename = "heep_simc_histos_3288_rad_Q2_4to5.root";       
-
-  //Full Q2 range
-  TString data_filename = Form("heep_data_histos_%d_combined_Q2full.root", run);    
-  TString simc_filename = Form("heep_simc_histos_%d_rad_Q2full.root", run);       
-
-  
-  //Pre-defined SIMC/data root file names containing histogram object to comapare
-  //TString simc_filename =  Form("heep_simc_histos_%d_rad.root", run);                      
-  //TString data_filename = Form("heep_data_histos_%d_combined.root",run); 
-
-  TString simc_f = root_dir + simc_filename;
-  TString data_f = root_dir + data_filename;
-  
-  //Where to store plots
-  string plots_dir = "./";
-  string plots_path;
-  
-  //Open SIMC/data ROOT files;
-  TFile *simc_file = new TFile(simc_f);
-  TFile *data_file = new TFile(data_f);
-
-  //---------------Target ----------------
-  //Define SIMC histos ('h'-->hadron arm,  'e'-->electron arm)
-  
-  TH1F *simc_xtar =  0;
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/heep_codes/plotYieldRatio.py

@@ -1,126 +1,0 @@
-import numpy as np
-from LT.datafile import dfile
-import LT.box as B
-import matplotlib.pyplot as plt
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid1.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-B.pl.rc('font', **font)
-
-
-kin = dfile('elasticsYield.txt')
-report = dfile('../../root_files/pre_HEEP_ELASTICS/report_heep.dat')
-etrkEff = report['eTrkEff']
-etrkEff_err = report['eTrkEff_err']
-shms_rate = report['ptrig1_rate'] #in kHz
-dataW = np.array(kin['dataW'])
-simcW = np.array(kin['simcW'])
-dataW_err = np.sqrt(kin['dataW_err'])
-simcW_err = np.sqrt(kin['simcW_err'])
-simcW_fofa_err = np.array([0.11178, 0.05785, 0.02722, 0.0029311]) #relative Xsec error dSig/Sig = dY / Y relative yield error
-simcW_tot_err = np.sqrt((simcW_err/simcW)**2 + simcW_fofa_err**2)
-R = dataW/simcW
-R_err = R * np.sqrt((dataW_err/dataW)**2 + (simcW_err/simcW)**2)  #SIMC Monte Carlo Error
-R_err_syst = R * np.sqrt((dataW_err/dataW)**2 + simcW_fofa_err**2)  #FOFA errors
-R_err_tot = R * np.sqrt((dataW_err/dataW)**2 + simcW_tot_err**2)  #total error
-
-fig = B.pl.figure(figsize=(7,4))
-ax1 = B.pl.subplot(1,1,1)
-
-print('>>>>> R = ', R, ' +/- ', R_err, ' +/- ', R_err_syst )
-#B.plot_exp(shms_rate, etrkEff, etrkEff_err, marker='o', color='r', label='SHMS tracking efficinecy', markersize=4.5)
-
-B.plot_exp(shms_rate, R, R_err, marker='o', color='r', label='Statistical Error', markersize=4.5)
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/plot_report/plot_pdist.py

@@ -1,1145 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-
-matplotlib.use('Agg')
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#Conversion factor:  1 fm = 1/ (197 MeV),   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-#User Input (Dir. Name to store output)
-sys_ext = sys.argv[1]   
-    
-dir_name = sys_ext+"_plots"
-dir_name_misc = dir_name + "/misc_plots"        #directory to store miscellaneous plots (trigger rates, live time, etc. . .) #obtained from the report files
-print(dir_name)
-#check if directory exists, else creates it.
-if not os.path.exists(dir_name):
-    os.makedirs(dir_name)
-if not os.path.exists(dir_name_misc):
-    os.makedirs(dir_name_misc)
-     
-
-#Get Reduced Xsec Data File
-fname = './%s/redXsec_combined.txt'%(sys_ext)
-f = B.get_file(fname)
-
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/plot_report/plot_report.py

@@ -1,404 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy.ma as ma
-import sys                                     
-import os                                                                                                       
-from sys import argv  
-import matplotlib
-from matplotlib import rc
-from matplotlib import *
-from mpl_toolkits.axes_grid.inset_locator import (inset_axes, InsetPosition, mark_inset)
-
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-matplotlib.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
-
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'bold',  #'normal', 'bold'
-        'size'   : 12
-}
-
-plt.rc('font', **font)
-
-#Set font
-csfont = {'fontname':'Times New Roman'}
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#Conversion factor:  1 fm = 1/ (197 MeV),   
-#The reduced cross section is in MeV^-3 units
-MeV2fm = 197.3**3    #convert MeV^-3 to fm^3
-
-#User Input (Dir. Name to store output)
-sys_ext = sys.argv[1]     #Em_final40MeV, all_thnq_Q2_3to4GeV
-    
-dir_name = sys_ext+"_plots"
-dir_name_misc = dir_name + "/misc_plots"        #directory to store miscellaneous plots (trigger rates, live time, etc. . .) #obtained from the report files
-#print(dir_name)
-#check if directory exists, else creates it.
-#if not os.path.exists(dir_name):
-#    os.makedirs(dir_name)
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/plotting_utilities/histUtils.C

@@ -1,390 +1,0 @@
-//Utility function that takes as argument 2 histogram objects, and the xlabel, ylabel (assume same range) and plots their ratio
-//Used to plot data/simc comparison and their ratio
-void hist_ratio(TH1F *hdata, TH1F *hsimc, TString xlabel="", TString ylabel="", TString title="")
-{
-  int font_type = 132;
-  
-  gStyle->SetOptStat(0);
-  gStyle->SetTitleFontSize(0.08);
-  gStyle->SetTitleFont(font_type, "");
-  gStyle->SetLegendBorderSize(0);
-  gStyle->SetLegendFont(font_type);
-  gStyle->SetLegendTextSize(0.06);
-
-  //Create Canvas
-  TCanvas *c = new TCanvas(title, "c", 700, 700);
-  c->Divide(1,2, 0., 0.0);
-
-  //VARIABLES TO Normalize histogram (if desired)
-  Double_t scale; //Used to scale SIMC histograms by 1./h->Integral(data)
-  double dataI;  //data integral
-  double simcI;  //simc integral
-  
-  //Set Histo Aesthetics
-  hsimc->SetLineWidth(2);
-  hsimc->SetLineColor(kRed);
-
-  hdata->SetFillColorAlpha(kBlue, 0.35);
-  hdata->SetFillStyle(3004);
-  hdata->SetLineWidth(2);
-  //Create new histo to store ratio
-  TH1F *hratio = (TH1F*) hdata->Clone();
-
-  //Set Histos Axis Label Size
-  hdata->GetYaxis()->SetLabelSize(0.06);
-  hratio->GetYaxis()->SetLabelSize(0.05);
-  hratio->GetXaxis()->SetLabelSize(0.06);
-  hdata->SetTitleSize(0.06, "XY");
-  hratio->SetTitleSize(0.06, "XY");
-
-  hratio->SetLineWidth(2);
-  hratio->SetLineColor(kBlack);
-
-  
-  c->cd(1);
-  //auto leg = new TLegend(0.1,0.8,0.28,0.9); 
-  auto leg = new TLegend(0.14,0.84,0.25,0.64); 
-
-  TPad* pad1 = (TPad*)c->GetPad(1);
-  pad1->SetBottomMargin(0.02);
-  pad1->SetRightMargin(0.05);
-  pad1->SetLeftMargin(0.1);
-  pad1->SetTopMargin(0.13);
[…]

### 2022-01-18 PRL_UTILITIES_CODES/codes/rad_bc_systematics/check_bc_corr.py

@@ -1,136 +1,0 @@
-#This code checks the Bin-Centering corrections are done properly and make
-#sense. 
-#The code makes plots of: 
-#1) BC corr. ratio for PWIA, FSI
-#2) dataXsec before/after FSI BC. Corrected
-#3) fsiXsec_avg_simc, fsiXsec_theory  (the two cross sections ratio give bc corr. factor)
-
-from LT.datafile import dfile
-import LT.box as B
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.ticker as tic
-import sys
-import os
-
-def convert2NaN(arr=np.array([]), value=0):
-    #method to convert a specified value in a array to nan (not a number)
-    
-    for i in enumerate(arr):
-        if arr[i[0]]==value:
-            arr[i[0]] = np.nan
-    return arr
-
-
-#User Input (Usage: python check_bc_corr.py 80 1 )
-pm_set = int(sys.argv[1])
-data_set = int(sys.argv[2])
-sys_ext = sys.argv[3]  
-
-
-#Make relevant directories to store plots
-dir_name = sys_ext+"_plots"
-
-#check if directory exists, else creates it.
-if not os.path.exists(dir_name):
-    os.makedirs(dir_name)
-
-#Read data file
-if pm_set==80:
-    fname = sys_ext + '/pm%i_laget_bc_corr.txt' % (pm_set)
-else:
-    fname = sys_ext + '/pm%i_laget_bc_corr_set%i.txt' %(pm_set, data_set)
-
-f = dfile(fname)
-
-#Get Relevant headers to plot
-pm = f['yb']    #missing momentum bin
-thnq = f['xb']  #theta_nq bin 
-
-#Get Bin-Centering Factors
-bc_fact_fsi = f['bc_fact_fsi']
-bc_fact_fsi_err = f['bc_fact_fsi_err']
-
-bc_fact_pwia = f['bc_fact_pwia']
-bc_fact_pwia_err = f['bc_fact_pwia_err']
-
-#Get Data Xsec
-fsiRC_dataXsec = f['fsiRC_dataXsec']               #only rad. corrected  data
-fsiRC_dataXsec_err = f['fsiRC_dataXsec_err']
[…]

### 2022-01-18 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/combine_data_sets.py

@@ -1,470 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import numpy.ma as ma
-import sys           
-import os                                                      
-from sys import argv  
-
-#This Code:  Only combines reduced cross sections from individual data sets of the same Pm setting, hence:
-#pm80,  pm580_set1 + pm580_set2,  pm750_set1 + pm750_set2 + pm750_set3, for the purpose of plotting
-#individual red. cross sections for each kin. setting
-
-#This code assumes the systematics errors have been calculated on the Xsec and red Xsec, and reads them 
-#to combine the data. When combining data, ONLY used statistical weight.  To combine the systematic errors
-#from different data sets, take the normal average of the systematic errors for now (Mark Jones)
-#When plotting combined reduced Xsec, plot statistical and total error bars (two error bars per data point)
-
-# **NOTE** ONLY Reduced Cross Sections (Momentum Distributions) can be combined. Cross Sections CANNOT be combined, 
-#          as they depend on spectrometer the kinematic setting, whereas in momentum distribution, that depenency has
-#          been factored out by dividing by K*sig_cc1(GEp, GMp)
-# ** combines (takes average) different data sets of a given kinematic setting and writes to file
-# ** combines different kinematic settings
-
-# some constants                                                                                                                                                     
-dtr = np.pi/180.                                                                                                                                                                               
-#GeV                                                                                                                                                                             
-MP = 938.272 / 1000.                                                                                                                                                                       
[…]

### 2022-01-18 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/make_Xsec_plots.py

@@ -1,184 +1,0 @@
-#Python script to plot cross-sections
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib import rc
-from matplotlib.legend_handler import HandlerTuple
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-
-dir_name = "./bin_centering_corrections/all_thnq_Q2_4to5/"
-
-fname_80 = dir_name + "pm80_laget_bc_corr.txt"
-fname_580_set1 = dir_name + "pm580_laget_bc_corr_set1.txt"
-fname_580_set2 = dir_name + "pm580_laget_bc_corr_set2.txt"
-
-fname_750_set1 = dir_name + "pm750_laget_bc_corr_set1.txt"
-fname_750_set2 = dir_name + "pm750_laget_bc_corr_set2.txt"
-fname_750_set3 = dir_name + "pm750_laget_bc_corr_set3.txt"
-
-kin_80 = dfile(fname_80)
-
-kin_580_s1 = dfile(fname_580_set1)
-kin_580_s2 = dfile(fname_580_set2)
-
-kin_750_s1 = dfile(fname_750_set1)
-kin_750_s2 = dfile(fname_750_set2)
-kin_750_s3 = dfile(fname_750_set3)
-
-
-#--Get 80 MeV/c setting--
-
-#determine rel stats error
-dataXsec_80         = np.array(kin_80['fsiRC_dataXsec_fsibc_corr'])    #data Xsec (corrected for rad. corr and bin-center corr. using  Laget FSI model
-dataXsec_80_err     = np.array(kin_80['fsiRC_dataXsec_fsibc_corr_err'])
-stats_80            = dataXsec_80_err / dataXsec_80                    #relative stats. error
-
-#require stats. error <= 50 %
-thnq_80             = np.array(kin_80['xb'])[stats_80<=0.50]
[…]

### 2022-01-18 PRL_UTILITIES_CODES/supplementary_materials/supp_codes/make_plot.py

@@ -1,275 +1,0 @@
-import LT.box as B
-from LT.datafile import dfile
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib import rc
-from matplotlib.legend_handler import HandlerTuple
-from prl_utilities import *
-
-#Use latex commands (e.g. \textit ot \textbf)
-rc('text', usetex=True)
-#Set default font to times new roman
-font = {'family' : 'Times New Roman',
-        'weight' : 'normal',
-        'size'   : 12
-}
-plt.rc('font', **font)
-
-
-fname_80 = "./red_dataXsec_pm80.txt"
-fname_580 = "./red_dataXsec_pm580.txt"
-fname_750 = "./red_dataXsec_pm750.txt"
-
-kin_80 = dfile(fname_80)
-kin_580 = dfile(fname_580)
-kin_750 = dfile(fname_750)
-
-#Get 80 MeV/c setting
-stats_80            = np.array(kin_80['tot_stats_err'])  #relative stats error
-thnq_80             = np.array(kin_80['thnq_bin'])[stats_80<=0.50]
-pm_avg_80           = np.array(kin_80['pm_avg'])[stats_80<=0.50]  #GeV/c
-red_Xsec_80         = np.array(kin_80['red_dataXsec_avg'])[stats_80<=0.50]  #avg. red Xsec [fm^3]
-red_Xsec_sys_err_80 = np.array(kin_80['red_dataXsec_avg_syst_err'])[stats_80<=0.50]  #avg. red Xsec systematic error [fm^3]
-red_Xsec_tot_err_80 = np.array(kin_80['red_dataXsec_avg_tot_err'])[stats_80<=0.50]  #avg. red Xsec tot error [fm^3]
-rel_syst_err_80 = np.array(kin_80['tot_syst_err'])[stats_80<=0.50]
-rel_tot_err_80 = np.array(kin_80['tot_err'])[stats_80<=0.50]
-
-#Get 580 MeV/c setting
-stats_580            = np.array(kin_580['tot_stats_err'])  #relative stats error
-thnq_580             = np.array(kin_580['thnq_bin'])[stats_580<=0.50]
[…]

### 2022-01-18 PRL_UTILITIES_CODES/supplementary_materials/supp_plots/dummy_contribution/al_thickness.py

@@ -1,37 +1,0 @@
-#codee to aacount for the difference in thickness
-#between Al. dummy an LH2 or LD2
-
-Al_density = 2.7 #g / cm^3
-
-#Aluminum wall of LH2 / LD2 cryotargets
-LH2_ent = 0.0150 #cm
-LH2_ent_err = 0.0011 #cm
-LH2_ext = (0.0191+0.0219)/2.  #cm: (tip + wall)/2
-
-LD2_ent = 0.0130 #cm
-LD2_ent_err = 0.0012 #cm
-LD2_ext = (0.0188+0.0184)/2.  #cm: (tip + wall)/2
-
-LH2_thick = Al_density * (LH2_ent + LH2_ext)/2. # g / cm^2
-LD2_thick = Al_density * (LD2_ent + LD2_ext)/2. # g / cm^2
-
-
-#Aluminum Dummy (al. foils at z = +/- 5 cm) to mimic cryotarget walls
-Al_ent = 0.1816 # g / cm^2
-Al_ext = 0.1815 # g / cm^2
-Al_thick = (Al_ent+Al_ext)/2.
-
-#RATIO
-LH2_factor =  LH2_thick / Al_thick
-LD2_factor =  LD2_thick / Al_thick
-
-#The ratio represents the thickness ratio of cryogenic as compared to Al. dummy target
-#This factor should be multiplied by the Al. dummy yield to convert the thickness from
-#Al DUMMY to CRYOTARGET END-CAPS THICKNESS
-
-print('LH2_thick = ',LH2_thick,' g/cm^2')
-print('LD2_thick = ',LD2_thick,' g/cm^2')
-print('Al_thick = ',Al_thick,' g/cm^2')
-
-print('LH2_factor = ', LH2_factor)
-print('LD2_factor = ', LD2_factor)

### 2022-01-18 publications/supplemental_materials/GetFF.C

@@ -1,101 +1,0 @@
-/////////////////////////////////////////////////////////
-/////////////////////////////////////////////////////////
-//// Parameterized Form Factor Central Value and Error
-/////////////////////////////////////////////////////////
-//// ID = 1 for GEp, 2 for GMp, 3 for GEn, 4 for GMn, 
-//// Q2 in GeV^2
-////
-// The parameterization formula returns the uncertainty devided by G(0)*GD, where 
-//  GD(Q2) = 1./(1+Q2/0.71)^2
-// and GEp(0) = 1, GMp(0) = 2.79284356, GEn(0) = 1, GMn(0) = -1.91304272,
-//
-// The parameterization formula for the Form Factor value is:
-//  $$ GN(z) = sum_{i=0}^{N=12}(a_i * z^i) 
-// Note that the return value has been divided by (G(Q2=0)*G_Dip)
-//
-// The parameterization formula for the Form Factor error is:
-// $$ log_{10}\frac{\delta G}{G_D} = (L+c_0)\Theta_a(L_1-L) 
-//                                 +\sum_{i=1}^{N}(c_i+d_i L)[\Theta_a(L_i-L)-\Theta_a(L_{i+1}-L)]
-//                                 +log_{10}(E_{\inf})\Theta_a(L-L_{N+1})$$
-// where $L=log_{10}(Q^2)$, $\Theta_{a}(x)=[1+10^{-ax}]^{-1}$. $a=1$.
-
-int GetFF(const int kID, const double kQ2, double *GNGD_Fit, double* GNGD_Err){/*{{{*/
-    // GEp->kID=1, GMp->kID=2, GEn->kID=3, GMn->kID=4
-    if (kID<1 || kID>4){
-        cerr<<"*** ERROR***, kID is not any of [1->GEp, 2->GMp, 3->GEn, 4->GMn]"<<endl;
-        GNGD_Fit[0] = -1000;  GNGD_Err[0] = -1000;
-        return -1;
-    }
-    ////////////////////////////////////////////////
-    //// z-Expansion Parameters for Form Factor Values
-    /////////////////////////////////////////////////*{{{*/
-    const double GN_Coef_Fit[4][13] ={
[…]

### 2022-01-18 publications/supplemental_materials/GetFF.py

@@ -1,98 +1,0 @@
-############################/
-############################/
-## Parameterized Form Factor Central Value and Error
-############################/
-## ID = 1 for GEp, 2 for GMp, 3 for GEn, 4 for GMn,
-## Q2 in GeV^2
-##
-# The parameterization formula returns the uncertainty devided by G(0)*GD, where
-#  GD(Q2) = 1./(1+Q2/0.71)^2
-# and GEp(0) = 1, GMp(0) = 2.79284356, GEn(0) = 1, GMn(0) = -1.91304272,
-#
-# The parameterization formula for the Form Factor value is:
-#  $$ GN(z) = sum_{i=0}^{N=12}(a_i * z^i)
-# Note that the return value has been divided by (G(Q2=0)*G_Dip)
-#
-# The parameterization formula for the Form Factor error is:
-# $$ log_{10}\frac{\delta G}{G_D} = (L+c_0)\Theta_a(L_1-L)
-#                                 +\sum_{i=1}^{N}(c_i+d_i L)[\Theta_a(L_i-L)-\Theta_a(L_{i+1}-L)]
-#                                 +log_{10}(E_{\inf})\Theta_a(L-L_{N+1})$$
-# where $L=log_{10}(Q^2)$, $\Theta_{a}(x)=[1+10^{-ax}]^{-1}$. $a=1$.
-import numpy as np
-from math import *
-def GetFF(kID, kQ2):# {{{
-    ### GEp->kID=1, GMp->kID=2, GEn->kID=3, GMn->kID=4
-    if kID<1 or kID>4:
-        print '*** ERROR***, kID is not any of [1->GEp, 2->GMp, 3->GEn, 4->GMn]'
-        return -1000, -1000
-
-    #################################################
-    #### z-Expansion Parameters for Form Factor Values
-    #################################################{{{
-    GN_Coef_Fit = np.zeros((4,13), dtype=float)
-    GN_Coef_Fit[0] = np.array([0.239163298067,  -1.10985857441,  1.44438081306,  0.479569465603,  -2.28689474187,  1.12663298498,  1.25061984354,  -3.63102047159,  4.08221702379,  0.504097346499,  -5.08512046051,  3.96774254395,  -0.981529071103]) #GEp
[…]

### 2022-01-18 publications/supplemental_materials/get_Xsec_err.py

@@ -1,91 +1,0 @@
-import numpy as np
-from interpolate_ff import *
-
-#This code defines the H(e,e'p) elastic cross section in terms of
-#the electric and magnetic form factors. Then apply error propagation
-#in terms of the form factors to get uncertainty in cross section at thw
-#gven beam energy, elecrtron angle and momentum.
-#Define Physical Constnats
-
-hbarc = 197.327053 / 1000.       #GeV * fm
-alpha = 1./137.0359895    #structure constant
-dtr = np.pi / 180.
-
-#Masses in GeV
-MP = 938.272 / 1000.
-MN = 939.566 / 1000.
-MD = 1875.61 / 1000.
-me = 0.51099 / 1000.
-
-#Template function that returns the H(e,e'p) cross section and its absolute uncertainty in units of ub / sr
-def sig(kf, th_e, Q2, GEp_GD, GMp_muGD, dGEp_GD, dGMp_muGD):
-
-    #Units: kf ~ Ef [GeV]   electron momentum  
-    #th_e[deg] electron angle  
-    #Q2[GeV2]   4-momentum transfer
-
-    mu_N = 3.1524512326 *1e-14 / 1000.   #nuclear magneton [GeV T^-1]
-    mu_p = 2.7928473508 * mu_N   #proton magnetic moment [GeV T^-1]
-
-    #Mott cross section
-    th_e = th_e * dtr    #convert degree to radians
-    sigM = (2.*alpha*hbarc*kf*np.cos(th_e/2.)/Q2 )**2   #GeV^2 * fm^2 *GeV^2/GeV^4--> fm2 / sr
-    sigMott = sigM * 1e4    #convert fm^2 -> microbarn
-
-    tau =  Q2 /(4.*MP)**2
-    L2 = 0.71   #Lambda parameter [GeV^2]
-    GD = 1. / (1 + Q2/L2)**2     #dipole form factor
-    muGD = mu_p * GD   #[GeV T^-1]
-    
-    #Calculate the form factors
-    GEp = GEp_GD * GD
-    GMp = GMp_muGD * muGD
-
-    #Elastic H(e,e'p) Cross Section
[…]

### 2022-01-18 publications/supplemental_materials/interpolate_ff.py

@@ -1,40 +1,0 @@
-import LT.box as B
-import numpy as np
-from LT.datafile import dfile
-from scipy.interpolate import interp1d
-
-
-#open proton form factor data with errors (see supplemental material for definitions of headers)
-f = dfile('proton_lookup_copy.data')
-
-Q2 = f['Q2']   #GeV2
-GEp_GD = f['GEp_GD']
-dGEp_GD = f['dGEp_GD']
-GMp_muGD = f['GMp_muGD']
-dGMp_muGD = f['dGMp_muGD']
-
-#Interpolate Form factors
-f_GEp_GD = interp1d(Q2, GEp_GD, fill_value='extrapolate') 
-f_dGEp_GD = interp1d(Q2, dGEp_GD, fill_value='extrapolate') 
-
-f_GMp_muGD = interp1d(Q2, GMp_muGD, fill_value='extrapolate') 
-f_dGMp_muGD = interp1d(Q2, dGMp_muGD, fill_value='extrapolate') 
-
-
-#define function to get form factors
-def get_GEp_GD(Q2):
-    result = f_GEp_GD(Q2)
-    return result
-
-def get_dGEp_GD(Q2):
-    result = f_dGEp_GD(Q2)
-    return result
-
-
-def get_GMp_muGD(Q2):
-    result = f_GMp_muGD(Q2)
-    return result
-
-def get_dGMp_muGD(Q2):
-    result = f_dGMp_muGD(Q2)
-    return result
